### 2017-06-06 thesis_outline.tex
initial commit

% This is file JFM2esam.tex
% first release v1.0, 20th October 1996
%       release v1.01, 29th October 1996
%       release v1.1, 25th June 1997
%       release v2.0, 27th July 2004
%       release v3.0, 16th July 2014
%   (based on JFMsampl.tex v1.3 for LaTeX2.09)
% Copyright (C) 1996, 1997, 2014 Cambridge University Press

\documentclass{jfm}
\usepackage{graphicx}
\usepackage{epstopdf, epsfig}

\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}

\shorttitle{Droplet electro-bounce}
\shortauthor{E. S. Schmidt and M. W. Weislogel}

\title{Spontaneous Droplet Jump with Electro-bouncing}

\author{Erin S. Schmidt\aff{1}
  \corresp{\email{esch2@pdx.edu}},
 \and M. W.  Weislogel\aff{1}}

\affiliation{\aff{1}Department of Mechanical Engineering, Portland State University,
Portland, OR 97211, USA
}

\begin{document}

\maketitle

\begin{abstract}
We investigate the dynamics of water droplet jumps from superhydrophobic surfaces in the presence of an electric field during a step reduction in gravity level. In the brief free-fall environment of a drop tower, when a strong non-homogeneous electric field (with a measured strength between $0.39$ and $2.36$ kV/cm) is imposed, body forces acting on the jumped droplets are primarily supplied by polarization stress and Coulombic attraction instead of gravity. The droplet charge, measured to be on the order of $2.3 \cdot(10^{-11})$ C, originates by electro-osmosis of charged species at the (PTFE coated) hydrophobic surface interface. This electric body force leads to a droplet bouncing behavior similar to well-known phenomena in 1-g, though occurring for larger drops $\sim \! \!$ 0.1 mL for a given range of impact Weber numbers, $\mathbf{We} < 20$. In 1-g, for $\mathbf{We} > 0.4$, impact recoil behavior on a super-hydrophobic surface is normally dominated by damping from contact line hysteresis and by air-layer interactions. However, in the strong electric field, the droplet bounce dynamics additionally include electrohydrodynamic effects on wettability and Cassie-Wenzel transition. This is qualitatively discussed in terms of coefficients of restitution and trends in contact time. \end{abstract}

\section{Introduction}\label{sec:intro}
\begin{itemize}
\item Bouncing droplets, impacts on S.H. surfaces
\item Motivation: phase change devices, substitute body force
\item Spontaneous droplet jump
\item DDT Spurrious forces
\end{itemize}

\subsection{Experiment description}
Study of the electrostatically bounced droplets in $/mu$-gravity conditions on square and rectangular superhydrophobic surfaces. Parametric variation in droplet volume, and surface charge density.

\section{Analytics}
\begin{itemize}
\item Full Navier-Stokes EHD
\item Low current assumptions
\item Charging time assumptions
\item Free surface damping assumptions
\item Water as a dielectric medium
\item Equation of motion
\item Far field: Coulombic with image charges
\item Near field: Spherical conductor, pane of charge
\item Near field: Legendre polynomials
\item Near field: Dielectrophoresis
\item Characteristic time scales
\item Poisson solver for potential, \emph{Gerris}
\item Reduced Bouncing model, stability, bifurcation
\item Mechanism for discharging, simulation
\end{itemize}

\section{Methods}
Description of drop tower operations.

\subsection{Superhydrophobic surfaces}
Wetting hystersis. Methods of fabrication, comparison of wetting properties. Methods for determination of properties, roll-off angle, contact angle using \emph{SE-FIT}. Cassie-wenzel transition. Damping.
\subsection{Charge}
Method of charging insulators. Surface charge density via electrostatic fieldmeter, transformations for finite surfaces, estimate of error. Milikans experient. Direct measurement of droplet charge using Faraday cup and high impedence electrometer. Sources of charge (electro-osmosis, induced charge). In-site high-precision techniques limited in drop tower context (15-g deceleration).
\subsection{Conductor experiment}
Measurement of fluid properties, red-dye, viscosity (per Al Jubari, un-published. Circuit diagrams. Microcontroller logic. Verification of low current $>>$ 1 $\mu$A. Filming at high speed. Camera, LED panel, high shutter speed. Machined Rayleigh-plateau breakup system.
\subsection{Data Reduction}
Particle tracking methods using ImageJ. Data reduction (filtering, polynomial fitting, finite derivatives).

\section{Results}
\begin{itemize}
\item Comparison of jump velocities between surfaces.
\item Qualitative discussion of bounces
\item Qualitative discussion of multi-drop interactions
\item Validity of the stability model
\item Composite images
\item ANOVA to compare variance of jump velocity to variance in charge or nonuniformity of field between tests.
\end{itemize}

\section{Notes}
\subsection{Bouncing on thin air}
\subsection{Electric field makes Leidenfrost droplets take a leap}
\subsection{Experimental Determination of the Charge Induced on Water Drops}
\begin{itemize}
\item Use of a ring shaped induction electrode. Droplet charges are a function of the electrode potential, as measured using a pico-ampmeter.
\item The electric field attracts free charge in a continuous conductor, which leads to net charged drops by mass separations (e.g. induced charge) during droplet breakup. This requires that the time interval between breakups is sufficient for charge redistribution in the source liquid. This is distinct from net charge separation by breakup of a electric double layer. So the net charged droplets are the result of the interplay between the external electric field, free charge in a conductive stream, and the Rayleigh-Plateau instability.
\item 
\end{itemize}
\citep{magarvey_experimental_1962}

\bibliographystyle{jfm}
%\citep{magarvey_experimental_1962}
% Note the spaces between the initials
\bibliography{test}

\end{document}

### 2017-06-07 thesis_outline.tex
insulator notes

@@
 \subsection{Experimental Determination of the Charge Induced on Water Drops}
+Some notes from \citep{magarvey_experimental_1962}.
 \begin{itemize}
@@
 \end{itemize}
-\citep{magarvey_experimental_1962}
+
+\subsection{Surface voltage and field strength: insulators}
+\begin{itemize}
+\item For a insulated conductor $A$ with charge $q$, the charge distribute in equilibrium will be such that the field on the interior of the conductor is zero, with field lines being normal to the surface and the integral of the field strength $E$ from any point $P$ in or on the conductor to a ground point $G$ is a constant given by
+\[ V = \int^G_P E \dot da \]
+where $V$ is the voltage or potential of the conductor.
+
+\end{itemize}
 

### 2017-06-12 ef_notes.tex
thesis ehd notes

\documentclass[a4paper, 12pt]{article}
\usepackage{changepage}
\usepackage{color,soul}
\usepackage{listings}
\lstset{
basicstyle=\small\ttfamily,
columns=flexible,
breaklines=true
}
\title{\textsf{\textbf{Droplet Electro-Bouncing in $\mu$-Gravity}}}
\vspace{-25mm}
\author{Erin S. Schmidt, Mark M. Weislogel}
\date{}

\usepackage{abstract}
\renewcommand{\abstractnamefont}{\normalfont\bfseries}
\renewcommand{\abstracttextfont}{\normalfont\small\itshape}

\begin{document}
\maketitle

\begin{abstract}
\noindent
Notes on electric fields `n stuff.
\end{abstract}

\section{Introduction}
\subsection{Spontaneous Droplet Jump}
When a nonwetting, gravity dominated sessile drop or puddle initially at rest in the Cassie-Baxter state on a surface undergoes a large step reduction in Bond number, $\mathbf{Bo} = \rho g V_d^{2/3}/\sigma$, where $\rho$ is the liquid density, $g$ is the acceleration of gravity, $V_d$ is the droplet volume, and $\sigma$ is the liquid surface tension, it will spontaneously jump away from the surface. This was first observed experimentally by Kirko \emph{et al.} in 1970 [ref] and later by Wollman \emph{et al.} in 2006 in a set of experiments conducted using a $\mu$-gravity drop tower \hl{[ref]}. The kinetic energy of the jump is supplied by the defect in free surface energy as the new minimum energy surface equilibrium has approximately constant curvature \hl{[ref]}. If the viscous energy losses by shear, and internal flows during roll up are neglected, as well as energy lost due to the hysteresis of the dynamic contact line, then the energy relation is given by 
\[KE = SE_2 -SE_1 = [(\sigma A)_{gl} + (\sigma A)_{sg}]_2 - [(\sigma A)_{ls} + (\sigma A)_{gl} + (\sigma A)_{sg}]_1. \]
From this is derived a simple model for the droplet initial jump velocity, given by
\[U_0 = \left(\frac{\sigma g}{\rho}\right)^{1/4}\left[1-\cos \theta + 2 \left(\frac{\pi H^3}{V_d} \right)^{1/2} - 6^{2/3} \left( \frac{\pi H^3}{V_d} \right)^{1/3} \right]^{1/2}, \]
where \hl{[etc, etc, etc...]}.

%\begin{figure}
%  \centerline{\includegraphics[height=7cm,width=7cm]%{e88_1_thumb.jpg}}
%  \caption{Droplet jump velocities, effect of hysteresis for small droplet size}
%\label{fig:jump_velocities}
%\end{figure}

The droplet `rolls up' as it jumps away from the surface due to radial motion of capillary wave away from the contact line. The characteristic time scale of the rolling up scales as $t_j \sim R_p/U ~(\rho H R^2_p/\sigma)^{1/2}$ [ref], which resembles the contact time, $\tau \approx 2.6(\rho R^3_d/\sigma)^{1/2}$ reported by Richard \emph{et al.} in 2002 for the related problem of droplets impacting hydrophobic surfaces in 1-g \hl{[ref]}. For droplets with radial symmetry and sufficiently high initial $\mathbf{Bo}$ these waves coalesce as a shock leading to geyersing and creation of satellite drops by the Rayleigh-Plateau breakup of the geyser. In the case of smaller jumping droplets, the capillary waves do not lead to geyersing, and are viscously damped to varying degrees during the brief freefall period of the drop tower.

The spontaneous droplet jump phenomenon provides a useful window though which to study the dynamics of large-lengthscale capillary dominated droplets. The governing physics of such massive droplets (far beyond the 1-g sub-millimetric capillary lengthscale) utterly defy terrestrial expectations about the ways in which liquid droplets `should' behave, and also are of critical importance in a space exploration setting where the design of practical $\mu$-gravity  multiphase fluidic systems will no doubt be needed as humankind gradually extends her domain into our solar system.
\section{Bouncing}
For the sake of bevity we will henceforth use the slightly confusing term `drop' as shorthand to refer to a single $\mu$-gravity drop tower experiment.
\section{Experimental Methods}
Superhydrophobic substrates were placed on a drop tower rig platform. The rig is released by a solenoid chucked pin at the same moment the exterior drag shield is allowed to fall. This decouples drag acceleration felt by the drag shield from the experiment which experiences approximately $1 \cdot 10^{-6}$g of high quality freefall for the 2.1s required for the rig/drag shield assembly to reach the bottom of drop tower 6 floors below.

The superhydrophobic surface was treated with PTFE spray for the first experiment of the day, and approximately every $3^{\mbox{rd}}$ drop following. The general properties and details of the fabrication of these superhydrophobic surfaces are discussed in Section \ref{sec.suphydro}. Shortly before each drop the surfaces were briefly rinsed with distilled water, and then dried under a fume hood for about 10 minutes. The drop rigs were balanced to prevent unintentional torques from contaminating the kinematics data (as angular velocity of the camera-fixed inertial reference with respect to the droplets during freefall would appear as a linear acceleration of the droplet). Surface charge density was measured on the superhydrophobic surface using a \emph{Simco-Ion} FMX-004 electrostatic fieldmeter. This measurement was done with the superhydrophobic surfaces connected by a conductive ground plane by conductive tape, far away from the presence of other conductors. Some additional notes on idiosyncrasies of determining surface voltages (and thence surface charge densities) on insulative dielectric surfaces are provided in Appendix \ref{sec.surface_charge}.

Droplets of distilled water, in a range of volumes ($0 \leq R_d \leq 1$mL), were very carefully deposited on the superhydrophobic surface in the final 1-5 minutes prior to the drop using an ungrounded glass syringe with $\pm 1\mu$L accuracy. Red tracer dye was added to improve trajectory digitization. During the drop, droplet trajectories were observed using a \emph{Panasonic} HC-WX970 Camera, shooting in high-speed mode at 120 fps and and 1/3000s shutter speed. In a few cases where higher frame rates were needed a \emph{Nikon} 1 J1 camera with a 30mm telephoto lens was used, shooting at 400 fps. The experimental test cell was illuminated with a 12V 6000K \emph{SEALIGHT} Chip-On-Board LED strip with a thin semi-opaque plastic film covering to make the light diffuse. The effect of static charges on spontaneously jumped droplet trajectories was studied in terms of the parameters droplet volume $V_d$, surface charge density $\sigma$, and a dependent variable, initial droplet jump velocity $U_0$. Since $q$ cannot be directly measured insitu during a drop (as high-input resistance electrometers, being notoriously fickle instruments, are not well suited to sudden 15-g decelerations), it was inferred from the statistical distribution determined in corollary experiments. The droplet charge determination is discussed in slightly more detail in Appendix \ref{sec.drop_charge}.

\subsection{Superhydrophobic surfaces} \label{sec.suphydro}
Wetting hysteresis. Methods of fabrication, comparison of wetting properties. Comparison of jump velocities between surfaces. Methods for determination of properties, roll-off angle, contact angle using \emph{SE-FIT}. Cassie-wenzel transition. Damping. Droplets are dyed red to improve the quality of image thresholding when digitizing the droplet trajectories during data reduction.

%\begin{figure}
%  \centerline{\includegraphics[height=7cm,width=13cm]{modes.eps}}
 % \centerline{\includegraphics[height=7cm,width=7cm]{e88_1_thumb.jpg}}
%  \caption{SEM images for sandpaper and laser etched acrylic surfaces}
%\label{fig:SEM}
%\end{figure}

\subsection{Data Reduction}
Digitization of droplet trajectories requires several steps of post-processing. Video is first decomposed into a sequence of still images. Trajectories are captured using the particle tracking module in \emph{Fiji}\hl{[ref]}, a derivative of the popular \emph{ImageJ}\hl{[ref]} package for scientific image analysis. The series of still images is cropped, and the background (that is, the low-entropy pixels) of the series are removed using a builtin ``rolling ball'' algorithm.  Each still is then split into its constituent RGB maps. In this case the green channel images contained the most information, so these were then globally thresholded using the Triangle algorithm to recover a map of the pixels corresponding to the droplet's approximate position in the original still. Finally ellipses are fitted to the pixel map stepping through the time series to determine the positions of the centroid, and the semi-major and minor axes of the droplets during the drop. The results of the particle capture in \emph{Fiji} are shown in Figure \ref{fig:fiji}. Droplet positional data was smoothed ex post facto using a Savitsky-Golay filter. Additional details regarding the data smoothing methodology are presented in Appendix \ref{sec.smoothing}.

\section{EHD Forces}
As previously speculated the the force acting on the droplets as a surrogate for gravity are likely electrohydrodynamical in origin. In the hopes of unraveling the underlying mechanism for the electro-bouncing we turn to the electrodynamical approximation of fluids under the influence of electric fields. To that effect, what follows is a condensed overview of mathematical description of basic electrohydrodynamic flows. We first assume a DC electric field, such that $Re \langle \epsilon \rangle \approx  \mbox{constant}$, where $\epsilon$ is the dielectric permittivity of the respective media. We also assume that currents are small such that the effects of magnetic fields can be neglected. For the validity of this assumption to hold the characteristic time scale for electrical phenomena $\tau_e = \epsilon \epsilon_0/\sigma_e \ll 1$, where we note that $\tau$ is the ratio of absolute dielectric permittivity $\kappa = \epsilon \epsilon_0$, to conductivity $\sigma_e$, of the medium [ref]. Given the respective conductivity, and permittivity of air ($\sigma_e = 2.5 \cdot 10^{-16}$ $\Omega^{-1} cm^{-1}$), we estimate $\tau_e \approx 400$s. This assumption also allows us to assume that the net charge present in the medium surrounding the droplets remains approximately constant during the typical time interval of a $\mu$-gravity experiment, and no transfers of charge occur after the droplet leaves the surface. \hl{[lol, check these numbers...]}

\subsection{Maxwell Stress}
If we suppose that electrical forces acting on free charges and dipoles in a fluid are transferred directly to the fluid itself, then this overall electrical body force will be the the divergence of the Maxwell stress tensor $\tau_m $, by

\[ \mathbf{F}_e = \nabla \cdot \tau_m = \nabla \cdot \left( \epsilon \epsilon_0 \mathbf{E} \mathbf{E} - \frac{1}{2} \epsilon \epsilon_0 \mathbf{E} \cdot \mathbf{E} \delta \right) ,\]
where $\mathbf{F}_e$ is the electric body force per unit volume, \hl{$\rho_f$ is the free charge density}, and $\delta$ is the delta function. The product of the electric field vectors is the dyadic product.

The classical Korteweg-Helmholtz force density formulation of the Maxwell stress tensor is usually expressed as 
\begin{equation}
\mathbf{F}_e = \rho_f \mathbf{E} + \frac{1}{2} \left| \mathbf{E} \right|^2 \nabla \epsilon - \nabla \left( \frac{1}{2} \rho \left( \frac{\partial \epsilon}{\partial \rho} \right)_T \left| \mathbf{E} \right|^2 \right) ,
\end{equation}
and $\rho$ is the density of the dielectric fluid[ref].

The first term in this expression, equivalently written as $q\mathbf{E}$, is the well known Coulombic force or electrophoretic force, which arises from the presence of free charge in an external electric field. The second term is the force arising from polarization stresses due to a nonuniform field acting across a gradient in permittivity. This force is widely termed the dielectrophoretic force (DEP). The third term describes forces due to electrostriction, however in our case $\left( \frac{\partial \epsilon}{\partial \rho} \right)_T = 0$ due to the  incompressibility of the fluid[ref]. While it is a relatively rigorous approach, and a useful conceptual model, evaluating the force density in this fashion can be somewhat onerous.

\subsection{Dielectrophoresis}
An alternative approximation for the polarization stress is to idealize the droplet as a simple dipole using the effective dipole moment method first suggested by Pohl and Jones\hl{[ref][ref]}. This approach can be related back to the force density by means of a Taylor series expansion of $\mathbf{E}$ in the limit of a small gradient \hl{[ref]}. The DEP force is distinct from the Coulombic force in that net charge is not required, and that the force vector goes in the direction of steepest descent of the field, $\nabla \left| \mathbf{E} \right|^2$, rather than in the direction of $\mathbf{E}$. The DEP force is related to the dipole moment (induced or polarized) of polarizable media which has a tendency to align the dipole with the electric field. If there is a gradient in the field then for a finite separation of charge one end of the dipole will feel a stronger electric field than the other, resulting in a net force. Whether the force is positive or negative in the direction of the electric field gradient depends on the difference of dielectric permittivites between the fluids, rather than on the polarity of $\mathbf{E}$. It bears repeating that droplets will polarize in a uniform field, but since there is no gradient in the field the forces felt by the dipoles are symmetric and there is no net force. The dipole moment of a spherical dielectric particle immersed in a dielectric medium is given by
\begin{equation} \label{dipole_m_1}
\mu = V_d \mathbf{P} = \frac{4}{3} \pi R_d^3 \mathbf{P},
\end{equation} 
where $\mathbf{P} = \left(\kappa_1 - 1 \right) \epsilon_0 \mathbf{E}_{iz}$ is the polarization moment, and $R_d$ is the particle radius, \hl{($\kappa_1$ being the relative dielectric constant of the medium}, and $\mathbf{E}_{iz}$ is the $z$-coordinate component of the electric field internal to the sphere, assuming the external electric field to be oriented parallel to the $z$-axis). The excess polarization $\mathbf{P}_e$, in the sphere is given by
\begin{equation} \label{polarization}
\mathbf{P}_e = \left( \kappa_2 - \kappa_1 \right) \epsilon_0 \mathbf{E}_{iz} = \frac{3 \kappa_1}{\kappa_2 +2\kappa_1}\mathbf{E}_{iz},
\end{equation}
where $\kappa_2$ is the dielectric constant of the particle. Taking together equations \ref{dipole_m_1}, and \ref{polarization} we find that the effective dipole moment of the particle is given by 
\begin{equation}\label{dipole_m_2}
\mu = 4 \pi R_d^3 \left( \frac{\kappa_2 - \kappa_1}{\kappa_2 + 2 \kappa_1} \right) \kappa_1 \epsilon_0 \mathbf{E},
\end{equation}
and the force felt by the dipole is 
\begin{eqnarray} \label{dep_force}
\mathbf{F}_{dep} &=& \left( \mathbf{P}_e \cdot \nabla \right) \mathbf{E}\\
&=& 2 \pi R_d^3 \kappa_1 \epsilon_0 \left( \frac{\kappa_2 - \kappa_1}{\kappa_2 + 2 \kappa_1} \right) \nabla E^2,
\end{eqnarray}
where it is a useful shorthand to refer to the permittivity ratio by $K = \frac{\kappa_2 - \kappa_1}{\kappa_2 + 2 \kappa_1}$, which is also known as the Clausius-Mossotti factor. In cases where $K < 0$, or $K>0$ the particle will be repelled or attracted to regions of strong field respectively. In our experiment, taking the relative dielectric constants to be $\kappa_1 \approx 1$ and $\kappa_2 \approx 80$, we have $K \approx 0.96$. One limitation of the effective dipole moment approximation of the DEP force is that it requires an assumption of small physical scale of the particle relative to the lengthscale of nonuniformity of the field, which in this case we take to be the length of the charged superhydrophobic surface ($L,H =25$mm $\gg a \approx 2.5$mm). Though the effective dipole moment is a successful model due in large part to its simplicity, it can be readily extended to include higher-order multipole effects, and non-spherical particles (oblate and prolate spheroids). An excellent summary of DEP theory in terms of the effective dipole moment is given in \hl{[ref]}. \hl{[Some notes on scaling ...]}

\subsection{Forces due to Image Charges in the Dielectric}

\section{The Electric Field}
Being thus armed with the assumption of a purely electrostatic problem (the electric field is conservative, that is $\nabla \times \mathbf{E} = 0$, where $\mathbf{E}$ is the electric field) we can describe the electric field by the Laplace equation for the electric potential. In the case of the volume charge density of the bulk medium to being zero, the divergence of the electric field is zero and we have

\begin{eqnarray}
\mathbf{E} &=& -\nabla \varphi \\
\nabla \cdot \mathbf{E} &=& 0\\
\nabla \cdot \mathbf{E} &=& - \nabla \cdot \nabla \varphi = \nabla^2 \varphi = 0,
\end{eqnarray}
it being convenient to solve the field in terms to $\varphi$ due to the form of the \emph{boundary conditions} usually given by
\begin{enumerate}
\item For finite charge distributions, the potential $\varphi$ goes to zero at infinity, is constant throughout a conductors, and is continuous across physical boundaries.
\item The normal component of the displacement vector $\mathbf{D}$, differs on two sides of a boundary by the free charge density $\rho_f$ residing on the boundary.
\item The tangential component of the field intensity $\mathbf{E}$ is continuous across a boundary.
\end{enumerate}

\section{A Simple Dynamical Model}
\subsection{Trajectory Equation}
\subsection{Numerical Methods}
\section{Comparisons}
\section{Stability}
\section{Future Directions}
\section{Conclusions}
\appendix
\section{\\Data Smoothing} \label{sec.smoothing}
In trying to recover the kinematic variables from the droplet trajectories we encounter a difficulty in the noise of the position data:

\begin{itemize}
\item Notes from Wood, ``Data smoothing and Differentiation procedures in Biomechanics''

\item Signal-to-noise ratio is $\mathcal{O}(f)$ for $\frac{df}{dt}$ and $\mathcal{O}(f^2)$ for $\frac{d^2f}{ft^2}$. Refs 5, 14, 49, 95.

\item Error sources include misalignment of the camera, perspective due to objects (subject or reference scale) being out of the photographic plane, precision limits in digitization. Some of these errors are systematic in origin and introduce consistent biases into the data (e.g. coherent spectral sources, rather than truly stochastic noise). These systematic sources of error include inaccurate scales among others. Data smoothing tends not to help with the systematic errors in that they are usually of lower frequency than the signal (and here we are trying specifically to filter high frequency noise).

\item Random errors are assumed to have a Gaussian distribution (by the central limit theorem), and are independent of the signal (which inherently results from a deterministic process).

\item Central differences are usually a better approximation of the instantaneous value of the true derivative of the signal, as compared to forward differences. The finite differences are mathematically equivalent to passing a quadratic interpolating polynomial through the three points of the central difference (assuming the window size of the central difference is $N=3$, larger windows are possible). To obtain an approximation for the $m^{th}$ derivative of $f(x)$ at least an $m^{th}$ order polynomial is required.

\item One straightforward approach to getting the position derivatives is to fit a least squares polynomial to the global position data, and analytically differentiate. This is a simple to apply, and therefore quite popular approach. The order of the polynomial is picked from theory, by ANOVA, or comparison of the residuals to determine goodness of fit for $m+1$. It should be stress that there are significant drawbacks with this approach: firstly is that when derived values depend on both accuracy of segmented displacement-time data and body segmental parameters (segmental masses and center of mass locations), then the errors are confounded and it is difficult to evaluate the accuracy of the derivative. Secondly, statistics used to asses agreement between curves are either in-appropriate because they aim to represent fundamentally deterministic processes in probabilistic ways (as would be the case using a product-moment correlation), or there is no test of significance (as is the case with a mean-errors correlation). Finally High order effects are easily lost by a global polynomial fit for time series containing multiple length scales or frequencies, as is the case here [ref].
\end{itemize}

In lieu of global polynomial fits we can attempt at finite differencing the data after the application of smoothing filters. Some of these approaches are global and/or recursive whereas other approaches are applied locally. Each approach has various natural advantages and disadvantages. A number of approaches were implimented in \emph{Python} or imported from the scientific computing package \emph{SciPy}[ref] and compared for a test set of trajectory data; these methods include convolution with the derivative of a Gaussian kernel, Wiener filtering, smoothing splines, Butterworth low-pass filtering, total-variance regularization, and Savitsky-Golay filtering. Qualitatively comparing these smoothing methods we find that we loose too many data points in the smoothing process, the variance remains large (especially in higher derivatives), large amplitudes are overly smoothed by repeated filtering passes, or there are significant end effects for most of these methods. A comparison of these smoothing approaches on a representative trajectory data set are shown in Figure \ref{fig:filters}. The power spectra for the same data are compared for these methods in Figure \ref{fig:power_spectra}.

%\begin{figure}
%  \centerline{\includegraphics[height=7cm,width=13cm]{modes.eps}}
 % \centerline{\includegraphics[height=7cm,width=7cm]{e88_1_thumb.jpg}}
  %\caption{Filtered or fitted droplet trajectories compared to raw data.}
%\label{fig:filters}
%\end{figure}

%\begin{figure}
%  \centerline{\includegraphics[height=7cm,width=13cm]{modes.eps}}
 % \centerline{\includegraphics[height=7cm,width=7cm]{e88_1_thumb.jpg}}
  %\caption{Power spectra of the filter methods compared.}
%\label{fig:power_spectra}
%\end{figure}

Savitsky-Golay filtering seems to produce the smoothest derivatives without overfitting of otherwise misrepresenting the underlying signal. The Savitsky-Golay algorithm

\section{\\Surface charge density}\label{sec.surface_charge}
Since the laser-etched acrylic, and sandpaper superhydrophobic surfaces are both dielectric materials there are some additional considerations for determining the surface charge density. Firstly, for an insulated conductor $A$ with charge $q$, the charge distribution in equilibrium will be such that the field on the interior of the conductor is zero, with field lines being normal to the surface and the integral of the field strength $\mathbf{E}$ from any point $P$ in or on the conductor to a ground point $G$ is a constant given by
\[ V = \int^G_P \mathbf{E} \cdot da, \]
where $V$ is the voltage or potential of the conductor (or alternatively, the surface voltage potential). The voltage $V$ and the charge $q$ are proportional and $q$ is usually given by
\[q = CV, \]
where $C$ is the capacitance of the insulated conductor and is determined by the conductor's size and shape, and its placement relative to the conductors and ground. However, the case of a charged insulator departs significantly from that of the insulated conductor. Here we have the possibility of the density and net polarity of the charge varying as a function of position about the surface. The field of the interior may not be zero, and the field lines are not necessarily normal to the the surface. The integral of the field strength from a point on or in the insulator to ground is usually different from point to point. In general the surface voltages will vary from point to point on an insulator (including point on the interior of the insulator. Therefore it is not possible to uniquely define the voltage of a charged insulator, except in certain contrived cases (notably the the potential of a uniformly charged sphere positioned infinitely far away from any conductors). It follows that there is no definition for the capacitance of an insulator as well. Though insulative sheets may store charge and discharge in the manner of capacitors, this discharge is never particularly complete.

There are two cases where we can make meaningful quantitative measurements of state variables for charged insulators: we can measure the electric field arising from the charge, and possible the total charge for uniformly charged free insulative sheets, and uniformly charged insulative sheets backed by a grounded conductor. To do this we can use field meters and non-contacting voltmeters. If the field strength indicated on the meter is $\mathbf{E}$, the charge density $\sigma$ on the part of the insulator in the front should be $\sigma = \epsilon_0 \mathbf{E}$. If a non-contacting voltmeter is placed a at a distance $d$ from the sheet, then the surface voltage $V_s$ indicated on the meter is given by 
\[V_s = d \mathbf{E} = d \frac{\sigma}{\epsilon_0}. \]

An ideal approach to determining surface charge on a dielectric surface is to screen perturbing effects of external electric fields. This is partly accomplished by grounding the fieldmeter, and by placing the dielectric sample on a grounded conductive plate backing. In this case the surface charge density is determined from

\[ \sigma = \frac{V_s \epsilon}{l}, \]

where $l$ and $\epsilon$ are the absolute permittivity and thickness of the dielectric surface respectively. The measured surface voltage is a function of position away from the charged dielectric. In most cases this function is relatively constant at a distance about 1-2 cm away from the surface (there is some measurement error in surface voltage due to small mispositioning of the electrostatic fieldmeter, say by $\pm$1 mm) and add it to the precision error of measurement in $V_s$. The measured surface voltage can also be compared to the analytically derived surface voltage determined from the analytical expression for the electric field from above, and to those determined from finite element solutions to poisson's equation on the domain in question. [Notes about \emph{Agros2D}] The surface voltage is shown schematically as a function of the measurement distance in Figure \ref{fig:surface_voltage} for a sample charge density $\sigma = $.

%\begin{figure}
%  \centerline{\includegraphics[height=7cm,width=13cm]{modes.eps}}
 % \centerline{\includegraphics[height=7cm,width=7cm]{e88_1_thumb.jpg}}
  %\caption{Measured surface voltage versus position.}
%\label{fig:surface_voltage}
%\end{figure}

A further consideration is the possibility of the change in total charge during a typical experimental timescale. If we consider the drop rig to be a ground (which seems reasonable given that the rig is isolated from true ground, but is at some reference voltage with respect to the surface charges on the dielectric, it also has an abundance of free charge carriers, that it, it is conductive), then there will be both bulk and surface decay of the charge on the dielectric. The evolution of the charge can be approximated by
\[ \sigma = \sigma_0 e^{\frac{-t}{\epsilon \rho}}, \]
where $\sigma_0$ is the initial surface charge density, and $\rho$ is the bulk resistivity (which can also be reframed in terms of conductivity by $\rho = 1/\gamma$, where $\gamma$ is the conductivity). For an example case of a surface with an initial surface charge density $\sigma = 2.4 \cdot (10^{-6})$ $C/m^2$, relative permittivity $\epsilon = 3.5$ and bulk resistivity $\rho = 1.6 \cdot (10^{16})$ $\Omega/cm$ such as with the case of 1/4'' continuous cast acrylic sheet, then the time constant $\tau = \epsilon \rho$ is approximately 5000 s, which is a great deal longer than the typical time period for of a drop tower experiment.

\section{\\Droplet Charge} \label{sec.drop_charge}
\subsection*{Parallel Plate Method}
Since, by the earlier scaling, we presuppose the source of the droplet bouncing behavior to be primarily Coulombic in origin (as opposed to dielectrophoretic), the droplet must have some net charge in addition to the charge induced by the electric field. To measure this charge concurrent methodologies were used. The first method of determining the droplet net charge is observation of the deflection of the droplets in the region of a known uniform field in a fashion inspired by Millikan's famous experiment to determine the fundamental charge of the electron [ref].

Droplets were jumped in freefall from a sandpaper superhydrophobic surface placed between the plates of a parallel plate capacitor of known uniform electric field. The surface was first deionized using a balanced \emph{Ptec} IN5120 DC air-ionizer to remove the effect of surface charge of the superhydrophobic surface from perturbing the otherwise uniform field set up between the parallel plates. A schematic of the parallel plate drop apparatus is shown in Figure \ref{fig:millikan}. Since the droplet initial velocity $U_0$ is parallel to the electric field, the droplets are inertial in the direction of the electric force, and neglecting the effect of image charges mirrored across the conductors, we can determine the magnitude of the droplet charge by a balance of Coulombic force and inertia given by the equation of motion

\[ \frac{d^2y}{dt^2} = q\mathbf{E}. \]

Since the drag is negligible in the inertial limit we can find the charge $q$ by fitting a second-order least squares polynomial to the measured droplet positions, equating the $t^2$ term to the constant acceleration, and dividing by the known, constant magnitude of the electric field. From a survey of literature we suppose the droplet charge, if they are indeed charged by contact with PTFE, to be some function of the droplet volume and the residence time on the superhydrophobic surface. However, sweeping though droplet volumes over a series of drop tower experiments we find little correlation between droplet volume  and net droplet charge. This is shown in figure \ref{fig:drop_charge}.

A 200-880 VAC source with a full wave bridge rectifier circuit was prototyped on perf-board for initial experiments to measure droplet charge. The circuit was analyzed on an laboratory oscilloscope to verify that the AC component of the signal was appropriately small (13 mV at 35 kHz). Current was determined to be a relatively low 80 $\mu$A. The high-voltage source terminals were led to two parallel polished 150x150 mm aluminum plate electrodes. The electrodes were mounted on an insulated 80/20 extruded aluminum rail for ease of adjustment. All droplet charge experiments were conducted with an electrode spacing of 28.30 mm. With this spacing the calibrated electric field between the plates was $\mathbf{E} \approx 35$kV/m. The electrodes were electrically isolated from the drop rig by two alternating layers of 4 mm thick laser cut acrylic sheet and Kapton tape. Potential across the plates was measured periodically with a load-impedance corrected multimeter to account for battery depletion. The typical capacitor rise time of the plates was measured to be 1.4 s, thus to make the most economical use of the brief window a micro-gravity a weighted switch was set by hand prior to the drop to close the high-voltage circuit, but which passively safed the system at the resumption of 1-g conditions in the tower. The drop apparatus is shown in Fig.

%\begin{figure}
%  \centerline{\includegraphics[height=7cm,width=13cm]{modes.eps}}
 % \centerline{\includegraphics[height=7cm,width=7cm]{e88_1_thumb.jpg}}
  %\caption{Parallel plate experimental apparatus.}
%\label{fig:millikan}
%\end{figure}

%\begin{figure}
%  \centerline{\includegraphics[height=7cm,width=13cm]{modes.eps}}
 % \centerline{\includegraphics[height=7cm,width=7cm]{e88_1_thumb.jpg}}
  %\caption{Parallel plates: Droplet net charge vs volume.}
%\label{fig:drop_charge}
%\end{figure}

A brief screening experiment was conducted which alternated the polarity of the field by switching the positive and negative terminal leads between plates. Qualitative observations of droplet electrode preference seem to indicate that the assumption of small polarization stress was well founded. Following this a orthogonal array $3^2$ factorial design experiment with two replicates was conducted to test the effect of varying droplet volume and surface stay time on net charge at the time of jumping. It was hypothesized in accordance with previous studies \cite{Choi:2013dg}, that net charge would increase for levels of both factors. The results of the factorial experiment are presented in Fig. \ref{fig:chart1}. ANOVA analysis in \emph{R} of the linear multiple regression model for the data set indicates that neither droplet volume ($p=0.105$), nor surface stay time ($p=0.358$) is significant at the 95\% confidence level. The overall model F-statistics (2.177 in 2 and 13 degrees of freedom), and coefficients of determination ($r^2 = 0.2509$) indicate that the linear model neither fits the data particularly well, nor does it offer an improvement over the mean model. The mean charge was determined to be positive $2.3 \cdot 10^{-11}$ C, with a standard deviation of $1.8 \cdot 10^{-11}$ C.

The failure of the model to describe the data raises interesting questions about the validity of our initial assumptions. Typical Reynolds numbers ($R_e=280$ average) indicate the general validity of the assumed quadratic drag model. The drag scale quantity given by Eqn. \ref{eqn:drag} was much less than 1 for all test runs, with mean value of $1.0\cdot 10^{-2}$ and a standard deviation of $2.0\cdot 10^{-3}$, which adds credence to a force balance of pure inertia and electrostatic force.

One obvious issue, in retrospect, is that while we know the characteristic charging time for the droplets to be some function of droplet volume, \hl{[it has been shown to have a time constant dramatically smaller than that of a typical experimental timescale]} so we might have looked only for the charge as a function of volume, both on physical grounds and due to the conflation of the variables.

Also of concern is that droplets in three of eighteen runs exhibited accelerations opposite to the expected direction. There is no pattern to the distribution of anomalous droplet accelerations, as they all occurred at unique level combinations. There are only four obvious ways of explaining this anomaly. The first is that the electric field is in fact non-uniform and polarization stress is non-negligible in this geometry. This option seems unlikely owing to the fundamental design of the experimental apparatus; \hl{[see figure from Agros2D FEM solution]}. A second possibility is that the few contrarian droplets actually accumulated net negative charge, instead of the net positive charge to be expected on the basis of evidence from some of the aforementioned studies. This is not impossible, and would also go some length to explain the variance in the measured charge generally. A third possibility is that another force neglected in this analysis, with some component in the direction opposite of the electric field, has an $\sim \mathcal{O}(1)$ magnitude. In principle this could for instance include the image charges which will subject the droplets to a force $\mathbf{F} = q^2/4 \pi \epsilon_0 d$ when ``close'' to one of the conductive plates (that is, when the plate can be treated as an infinite grounded conductor). However, this formulation of the image charge effect clearly does not describe the force close to the centerline where the Green's function needs to add additional sets of images to satisfy the boundary conditions of $\nabla^2 \varphi = 0$ in this geometry. To the knowledge of the author there is not a convergent series solution in the parallel plates geometry as yet.

The droplet positive net charge developed by contact with a PTFE surface corresponds to findings elsewhere in literature \cite{Choi:2013dg} \cite{Miljkovic:2013dg} \cite{Moreno-Villa:1998dg}. The smallest droplet size treated in the present work is several times larger than the largest in any of comparable study. The most relevant comparison found droplet static charge of 2.5e-10 C for 10 $\mu$L droplets charged by pipetting from a PTFE tipped needle \cite{Choi:2013dg}. The present results mean charge level of 2.3e-11 C is, within error, roughly six times smaller than the cited study.

\subsection*{Direct Measurement}
A second approach to determining the net droplet charge is by direct measurement in a shielded Faraday cup using an extremely high input resistance electrometer, specifically a \emph{Keithly} 616 digital electrometer. \hl{[note on operational philosophy, data collection]. Correlation of net charge to droplet volume is shown again for in figure} \ref{fig:electrometer}.

%\begin{figure}
%  \centerline{\includegraphics[height=7cm,width=13cm]{modes.eps}}
%  \centerline{\includegraphics[height=7cm,width=7cm]{e88_1_thumb.jpg}}
 % \caption{Electrometer: charge vs. volume.}
%\label{fig:electrometer}
%\end{figure}

[Discussion on discrepancy between the two approaches.]

\end{document}

### 2017-06-13 ef_notes.tex
csvs

@@
 \section{Bouncing}
-For the sake of bevity we will henceforth use the slightly confusing term `drop' as shorthand to refer to a single $\mu$-gravity drop tower experiment.
+For the sake of brevity we will henceforth use the slightly confusing term `drop' as shorthand to refer to a single $\mu$-gravity drop tower experiment.
 \section{Experimental Methods}
@@
 Trajectories are captured using the particle tracking module in \emph{Fiji}\hl{[ref]}, a derivative of the popular \emph{ImageJ}\hl{[ref]} package for scientific image analysis.
-The series of still images is cropped, and the background (that is, the low-entropy pixels) of the series are removed using a builtin ``rolling ball'' algorithm.
+The series is stabilized to remove the effect of drop transients from the kinetmatic data[ref].
+The series of still images is cropped, and the background (that is, the low-entropy pixels) of the series is removed using a builtin ``rolling ball'' algorithm.
 Each still is then split into its constituent RGB maps.
@@
 The results of the particle capture in \emph{Fiji} are shown in Figure \ref{fig:fiji}.
+Out of plane motion for `weakly 3D' trajectories is inferred from the change in tracked area of the droplet.
 Droplet positional data was smoothed ex post facto using a Savitsky-Golay filter.

### 2017-06-15 demo.py
added some scratch notebooks, trying to channel my inner natronics

@@ -1,0 +1,10 @@
+"""A demo module."""
+def prints_b():
+	#Prints b.
+	print('b')
+def print_a():
+	#Prints a
+	print('a')
+
+c = 2
+d = 2

### 2017-06-18 doc/deprecated/thesis_outline/jfm-instructions.tex
reorganized repo

--- 2017-06-06 thesis_outline.tex
@@
 \section{Introduction}\label{sec:intro}
-\begin{itemize}
-\item Bouncing droplets, impacts on S.H. surfaces
-\item Motivation: phase change devices, substitute body force
-\item Spontaneous droplet jump
-\item DDT Spurrious forces
-\end{itemize}
 
-\subsection{Experiment description}
-Study of the electrostatically bounced droplets in $/mu$-gravity conditions on square and rectangular superhydrophobic surfaces. Parametric variation in droplet volume, and surface charge density.
-
-\section{Analytics}
-\begin{itemize}
-\item Full Navier-Stokes EHD
-\item Low current assumptions
-\item Charging time assumptions
-\item Free surface damping assumptions
-\item Water as a dielectric medium
-\item Equation of motion
-\item Far field: Coulombic with image charges
-\item Near field: Spherical conductor, pane of charge
-\item Near field: Legendre polynomials
-\item Near field: Dielectrophoresis
-\item Characteristic time scales
-\item Poisson solver for potential, \emph{Gerris}
-\item Reduced Bouncing model, stability, bifurcation
-\item Mechanism for discharging, simulation
-\end{itemize}
-
-\section{Methods}
-Description of drop tower operations.
-
-\subsection{Superhydrophobic surfaces}
-Wetting hystersis.
-Methods of fabrication, comparison of wetting properties.
-Methods for determination of properties, roll-off angle, contact angle using \emph{SE-FIT}.
-Cassie-wenzel transition.
-Damping.
-\subsection{Charge}
-Method of charging insulators.
-Surface charge density via electrostatic fieldmeter, transformations for finite surfaces, estimate of error.
-Milikans experient.
-Direct measurement of droplet charge using Faraday cup and high impedence electrometer.
-Sources of charge (electro-osmosis, induced charge).
-In-site high-precision techniques limited in drop tower context (15-g deceleration).
-\subsection{Conductor experiment}
-Measurement of fluid properties, red-dye, viscosity (per Al Jubari, un-published.
-Circuit diagrams.
-Microcontroller logic.
-Verification of low current $>>$ 1 $\mu$A.
-Filming at high speed.
-Camera, LED panel, high shutter speed.
-Machined Rayleigh-plateau breakup system.
-\subsection{Data Reduction}
-Particle tracking methods using ImageJ. Data reduction (filtering, polynomial fitting, finite derivatives).
-
-\section{Results}
-\begin{itemize}
-\item Comparison of jump velocities between surfaces.
-\item Qualitative discussion of bounces
-\item Qualitative discussion of multi-drop interactions
-\item Validity of the stability model
-\item Composite images
-\item ANOVA to compare variance of jump velocity to variance in charge or nonuniformity of field between tests.
-\end{itemize}
-
-\section{Notes}
-\subsection{Bouncing on thin air}
-\subsection{Electric field makes Leidenfrost droplets take a leap}
-\subsection{Experimental Determination of the Charge Induced on Water Drops}
-\begin{itemize}
-\item Use of a ring shaped induction electrode. Droplet charges are a function of the electrode potential, as measured using a pico-ampmeter.
-\item The electric field attracts free charge in a continuous conductor, which leads to net charged drops by mass separations (e.g.
-induced charge) during droplet breakup.
-This requires that the time interval between breakups is sufficient for charge redistribution in the source liquid.
-This is distinct from net charge separation by breakup of a electric double layer.
-So the net charged droplets are the result of the interplay between the external electric field, free charge in a conductive stream, and the Rayleigh-Plateau instability.
-\item 
-\end{itemize}
-\citep{magarvey_experimental_1962}
-
-\bibliographystyle{jfm}
-%\citep{magarvey_experimental_1962}
+%\bibliographystyle{jfm}
 % Note the spaces between the initials
-\bibliography{test}
+%\bibliography{jfm-instructions}
 

### 2017-06-18 doc/deprecated/thesis_outline/thesis_outline.tex
reorganized repo

% This is file JFM2esam.tex
% first release v1.0, 20th October 1996
%       release v1.01, 29th October 1996
%       release v1.1, 25th June 1997
%       release v2.0, 27th July 2004
%       release v3.0, 16th July 2014
%   (based on JFMsampl.tex v1.3 for LaTeX2.09)
% Copyright (C) 1996, 1997, 2014 Cambridge University Press

\documentclass{jfm}
\usepackage{graphicx}
\usepackage{epstopdf, epsfig}

\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}

\shorttitle{Droplet electro-bounce}
\shortauthor{E. S. Schmidt and M. W. Weislogel}

\title{Spontaneous Droplet Jump with Electro-bouncing}

\author{Erin S. Schmidt\aff{1}
  \corresp{\email{esch2@pdx.edu}},
 \and M. W.  Weislogel\aff{1}}

\affiliation{\aff{1}Department of Mechanical Engineering, Portland State University,
Portland, OR 97211, USA
}

\begin{document}

\maketitle

\begin{abstract}
We investigate the dynamics of water droplet jumps from superhydrophobic surfaces in the presence of an electric field during a step reduction in gravity level. In the brief free-fall environment of a drop tower, when a strong non-homogeneous electric field (with a measured strength between $0.39$ and $2.36$ kV/cm) is imposed, body forces acting on the jumped droplets are primarily supplied by polarization stress and Coulombic attraction instead of gravity. The droplet charge, measured to be on the order of $2.3 \cdot(10^{-11})$ C, originates by electro-osmosis of charged species at the (PTFE coated) hydrophobic surface interface. This electric body force leads to a droplet bouncing behavior similar to well-known phenomena in 1-g, though occurring for larger drops $\sim \! \!$ 0.1 mL for a given range of impact Weber numbers, $\mathbf{We} < 20$. In 1-g, for $\mathbf{We} > 0.4$, impact recoil behavior on a super-hydrophobic surface is normally dominated by damping from contact line hysteresis and by air-layer interactions. However, in the strong electric field, the droplet bounce dynamics additionally include electrohydrodynamic effects on wettability and Cassie-Wenzel transition. This is qualitatively discussed in terms of coefficients of restitution and trends in contact time.

Electrostatic forces present opportunities for the study and control of unique $\mu$-gravity droplet dynamics. Unfortunately, in many cases such forces manifest as a complicating nuisance variable. In the present work, the sources and magnitudes of these effects are surveyed, and options for avoiding or mitigating them are presented. Additionally a scale quantity of concern is presented for rapid estimation of limiting behaviors for droplet kinematics dominated by electrostatic forces; pertinent terms in the scale quantity include droplet charge and electric field strength. The strength of electric fields originating from static charge on acrylic surfaces used in drop tower experiments was measured using an electrostatic field meter. The mean electric field strength sampled at 25 mm away from a population of surfaces is 150 V, however the field strength ranges from 10 V (at the limit of sensor accuracy) to over 3 kV. The electrostatic force, and thus the total charge in the droplet was revealed by observation of the accelerations of droplets in a homogeneous electric field of known strength. Typical droplet net charge, supposedly developed through electro-osmosis of charged ionic species from the PTFE treated hydrophobic surfaces, was measured to be 2.3e-11 C with a standard deviation of 1.8e-11 C.\end{abstract}

\section{Introduction}\label{sec:intro}
When a nonwetting, gravity dominated sessile drop or puddle initially at rest in the Cassie-Baxter state on a surface undergoes a large step reduction in Bond number, $\mathbf{Bo} = \rho g V_d^{2/3}/\sigma$, where $\rho$ is the liquid density, $g$ is the acceleration of gravity, $V_d$ is the droplet volume, and $\sigma$ is the liquid surface tension, it will spontaneously jump away from the surface. This was first observed experimentally by Kirko \emph{et al.} in 1970 [ref] and later by Wollman \emph{et al.} in 2006 in a set of experiments conducted using a $\mu$-gravity drop tower[ref]. The kinetic energy of the jump is supplied by the defect in free surface energy as the new minimum energy surface equilibrium has approximately constant curvature [ref]. If the viscous energy losses by shear, and internal flows during roll up are neglected, as well as energy lost due to the hysteresis of the dynamic contact line, then the energy relation is given by 
\[KE = SE_2 -SE_1 = [(\sigma A)_{gl} + (\sigma A)_{sg}]_2 - [(\sigma A)_{ls} + (\sigma A)_{gl} + (\sigma A)_{sg}]_1. \]
From this is derived a simple model for the droplet initial jump velocity, given by
\[U_0 = \left(\frac{\sigma g}{\rho}\right)^{1/4}\left[1-\cos \theta + 2 \left(\frac{\pi H^3}{V_d} \right)^{1/2} - 6^{2/3} \left( \frac{\pi H^3}{V_d} \right)^{1/3} \right]^{1/2}. \]

\begin{figure}
%  \centerline{\includegraphics[height=7cm,width=13cm]{modes.eps}}
  \centerline{\includegraphics[height=7cm,width=7cm]{e88_1_thumb.jpg}}
  \caption{Droplet jump velocities, effect of hysteresis for small droplet size}
\label{fig:jump_velocities}
\end{figure}

The droplet `rolls up' as it jumps away from the surface due to radial motion of capillary wave away from the contact line. The characteristic time scale of the rolling up scales as $t_j \sim R_p/U ~(\rho H R^2_p/\sigma)^{1/2}$ [ref], which resembles the contact time, $\tau \approx 2.6(\rho R^3_d/\sigma)^{1/2}$ reported by Richard \emph{et al.} in 2002 for the related problem of droplets impacting hydrophobic surfaces in 1-g. For droplets with radial symmetry and sufficiently high initial $\mathbf{Bo}$ these waves coalesce as a shock leading to geyersing and creation of satellite drops by the Rayleigh-Plateau breakup of the geyser. In the case of smaller jumping droplets, the capillary waves do not lead to geyersing, and are viscously damped to varying degrees during the brief freefall period of the drop tower.

The spontaneous droplet jump phenomenon provides a useful window though which to study the dynamics of large-lengthscale capillary dominated droplets. The governing physics of such massive droplets (far beyond the 1-g sub-millimetric capillary lengthscale) utterly defy terrestrial expectations about the ways in which liquid droplets `should' behave, and also are of critical importance in a space exploration setting where the design of practical $\mu$-gravity  multiphase fluidic systems will no doubt be needed as humankind gradually extends her domain into the rest of the solar system.

The $\mu$-gravity conditions useful for the study of droplet kinematics can be
accessed, albeit briefly, in a drop tower facility such as Portland State Uni-
versity’s Dryden Drop Tower. In drop tower experiments, as well as in
experiments conducted in a true space environment, anomalous accel-
erations are a potential subject of concern to experimentalists studying
droplet kinematics. This is especially true in the study of droplets of small
inertia which may be subject to environmental factors that are difficult to control empirically. While there is nothing overtly mysterious about
the underlying forces causing such droplets to accelerate, the forces must
nevertheless be mitigated or accounted for. Spontaneous droplet jump, droplet dynamics are usually dominated by inertia, however spurrious forces were occasionally observed.

\begin{figure}
%  \centerline{\includegraphics[height=7cm,width=13cm]{modes.eps}}
  \centerline{\includegraphics[height=7cm,width=7cm]{e88_1_thumb.jpg}}
  \caption{$\mu$-gravity drop tower}
\label{fig:ddt}
\end{figure}

Electrohydrodynamic forces, like thermocapillary forces, are useful in $\mu$-gravity where, due to the absence of bouyancy the locations of droplet and bubbles, and other stray interfaces need to be controlled by various means. This is the famous phase seperation problem of $\mu$-gravity.

Under $\mu$-gravity conditions unique force balances act on droplets revealing dynamics difficult to study at macro-scales in a terrestrial environment. The study of droplet dynamics in $\mu$-gravity is thus of interest to many areas of basic research. For acceleration of droplets in $\mu$-gravity forces other than gravity are required. Aerodynamic force contributions include drag and lift, virtual mass effects, Basset forces due to developing boundary layers, and additional exotic forms of drag that are encountered in dynamics of combusting droplets, such as Stefan drag, thermophoresis effects, and droplet-soot interactions \cite{Manzello:2004dg}. Droplets can also be entrained by large scale eddy and wake structures due to participating gas phase inertia. Surface forces can also be imposed by the presence of strong acoustic fields.

Water is one of the principle model fluids used in $\mu$-gravity droplet dynamics research. Body forces acting on water droplets may be imparted by the presence of an electric field. Water molecules are dipoles and are thus influenced by the presence of non-homogeneous electric fields. Additional forces may develop due to dielectrophoresis, and due to Coulombic forces arising from the presence of static charge on the surface of the droplets themselves. While aboard the International Space Station NASA Flight Engineer Pettit experimented with Coulombic orbiting of droplets charged to high voltage around a knitting needle similarly charged, but with the opposite polarity and using the triboelectric effect \cite{Stevenson:2015dg}.

Droplet dynamics which appear to be strongly influenced by electrostatic forces have also been observed at Portland State University's Dryden Drop Tower (DDT) facility. These experiments follow from earlier research done at the DDT measuring velocities of droplets jumped from hydrophobic surfaces during step-reductions in gravitational acceleration \cite{Attari:2015dg}. In this case the presence of strong forces beyond surface tension and droplet inertia are important nuisance variables that must be mitigated or otherwise properly accounted for. Previous experiments in the DDT examining aerodynamic effects on droplets jumped from hydrophobic surfaces noted the presence of anomalous accelerations for a large data set of 0.1 mL droplets. The source of these accelerations was not captured entirely by aerodynamic drag effects, though the presence of an acrylic 'eddy shield' did have a statistically significant effect on the mean droplet accelerations. The effect of static charge appeared, at least qualitatively, to be a significant confounding variable in determining the contribution of aerodynamics to droplet accelerations.

The Dryden Drop Tower, patterned on the 2.2 Second Drop Tower facility at NASA's Glenn Research Center in Cleveland, Ohio, is optimized for exceptionally fast drop turnaround times. The DDT is one of the most productive drop towers in the world for its class, with more than 7000 drops over its XX year history. The DDT's 2.1 seconds of free-fall conditions provide unique opportunities for the observation of phenomena that are usually masked at the macro-scale in 1-g gravity fields. In addition to the DDT itself, an institutionally ingrained rapid prototyping "Fail Fast, Fail Often" iterative design philosophy underpins much of this lab's productivity. In the context of the present study this rapid prototyping approach includes widespread use of lasercut acrylic surfaces, and in-house fabricated PTFE treated super-hydrophobic surfaces. Unfortunately, acrylic surfaces and PTFE spray treatments in particular lend themselves to accumulation of large amounts of static charge which affects droplet kinematics. The object of the current study then is to provide the DDT lab with a means of sanitizing droplet kinematic data from the confounding effects of electrostatic fields, and to identify regimes where there is some assurance that the effect of such fields is small. This can be aided by the empirical determination of scale quantities of concern for the flow.

%\begin{itemize}
%\item Bouncing droplets, figure tame lapse of droplets
%\item Composite images
%\item Qualitative discussion of bounces
%\item Qualitative discussion of multi-drop interactions
%\item Motivation: phase change devices, substitute body force
%\end{itemize}

\begin{figure}
%  \centerline{\includegraphics[height=7cm,width=13cm]{modes.eps}}
  \centerline{\includegraphics[height=7cm,width=7cm]{e88_1_thumb.jpg}}
  \caption{Composite photograph showing a bouncing droplet}
\label{fig:comp}
\end{figure}

\begin{figure}
%  \centerline{\includegraphics[height=7cm,width=13cm]{modes.eps}}
  \centerline{\includegraphics[height=7cm,width=7cm]{e88_1_thumb.jpg}}
  \caption{Comparison of droplet trajectories, as a function of mass}
\label{fig:trajectories}
\end{figure}

\begin{figure}
%  \centerline{\includegraphics[height=7cm,width=13cm]{modes.eps}}
  \centerline{\includegraphics[height=7cm,width=7cm]{e88_1_thumb.jpg}}
  \caption{3D plot of interacting droplet pair}
\label{fig:3d}
\end{figure}

\subsection{Force due to an electric field}
Electrohydrodynamic concerns the flow of liquid dielectrics subject to electric fields. These have have been studies with an eye towards space applications in [ref][ref][ref][ref].

The electric body forces acting on the droplets are
Laplace's equation
\[ \nabla^2 \phi = 0\]
Where the boundary conditions are given values of the potential in the far field, and the surface charge density of the dielectric surface. The electric field is defined as the negative of the gradient of the potential
\[ \mathbf{E} = - \nabla \phi \]
[notes on the field for the square geometry]

Momentum conservation confirms that the electric volumetric body force is the same obtained by integrating the momentum flux density over the surface confining the liquid. Thus the total body force for a fluid volume can be estimated by. The total force acting on the droplet can be calculated in the most rigerous fashion from the Maxwell stress tensor, where the total electric force is the obtained by integrating the stress tensor over the surface of the droplet,
\[ \mathbf{F}_{DEP} = \oint (\mathbf{\tau}_m  \cdot \mathbf{n})d\Gamma. \]
The Maxwell stress tensor $\tau_m$ is usually expressed as

The EHD approximation usually makes the fundamental assumption that currents in the medium are so weak that the magnetic field they induce is so weak as to be neglected. We also assume that the system is isothermal, and there is no gradient in the permittivity due to thermal gradient. What that assumption we have
\[ \mathbf{\tau}_m = \epsilon_0 \epsilon \left(\mathbf{E}_i \mathbf{E}_j - \frac{1}{2} \delta_{ij}E^2 \right) \]
The electric body force is then 
\[ \mathbf{F}_{elec} = \rho_c \mathbf{E} - \frac{1}{2}E^2 \nabla \epsilon \]
This is regarded as the most rigerous approach for deriving the forces induced by the electric field.

The equations governing the motion of the jumped droplet are the momentum equation and Maxwell's equations. The electrostatic forces described by Maxwell's equations are those arising from free charge in an external electric field (the Coulombic force), and those arising due to polarization effects. In the droplet bounce phenomenon described here we suppose first that dynamic currents are so low that the effect of magnetic fields can be safely neglected. For this approximation to apply the characteristic time scale for electrical phenomenon $\tau = \epsilon/\sigma$, must be small, where we note that $\tau$ is the ratio of dielectric permeability to conductivity of the medium. For the conductivity of air ($\sigma = 2.5 \cdot 10^{-16}$ $\Omega^{-1} cm^{-1}$), we estimate $\tau \approx 400$s. This assumption also allows us to assume that the net charge present in the sorrounding medium remains approximately constant during the typical time interval of a $\mu$-gravity experiment.

Once the electric potential has been calculated we find the body force density from the Korteweg-Helmholtz formulation of the Maxwell stress integral, given by
\[ \mathbf{F} = \rho \mathbf{E} - \frac{1}{2}E^2 \nabla \epsilon + \nabla \left( \frac{1}{2}\mathbf{E} \cdot \mathbf{E} \frac{\partial \epsilon}{\partial \rho} \right) \]
The final term is the electrostriction force density, which can be ignored for incompressible flows. Though this equation nominally adds a level of coupling between to momentum equation as the electric body force source term is a function of the electric field, but the field itself is perturbed as the droplet (and its accompanying net charge) is convected through space. We henceforth assume that the perturbed field due to the droplet charge is a high order correction to the basic field, and is neglected. The first term in xx is due to net charge residing on the droplet, where as the second term is due to polarization of the droplet in a nonuniform electric field, dielectrophoresis.

Dielectrophoresis is the motion of matter in a nonuniform electric field due to polarization of a dielectric. The most polar material migrates toward the region of greatest field intensity. The relative permittivity of the particle compared to the surrounding medium determines the direction of the induced dipole/multipole moment with respect to the applied field. Depeding on this alignment the particle will experience wither an attractive force or repelling force towards the regions of higher electric field. Unlike electrophoresis caused by the Coulombic force, dielectrophoresis does not require any net charge to be present on the droplet. Any dipole (whether induced or permanant) will have some finite, equal seperation of charge in it. The electric field will cause an alignment of the dipole with it; because the field is nonuniform, on end of the dipole will experience a weaker field than the other, resulting in a net force. The direction of the force does not depend on the direction (the polarity) of the electric field.

As the radius of the droplets $R_d \approx 2.5$mm is much less than the characteristic length of the idealized plane of charge $L,H \approx 25$mm, we assume that that the effective dipole moment method is valid for our case, and the multipolar effects can be ignored.

The translation force, $\mathbf{F}$ on a dipole $\mathbf{\mu}$ (whether induced or permanant) in a nununiform field is given by
\[F = \mu \cdot \nabla \mathbf{E} \]
where $\mathbf{E}$ is the field acting on the particle. The dipole moment of a spherical particle in a dielectric medium is 
\[ \mathbf{\mu}  = \nu \mathbf{P} = \frac{4}{3} \pi a^3 \mathbf{P} \]
where $\nu$ is the volume, $a$ is the radius of the paticle, $\mathbf{P} = \left(\epsilon_{air} -1 \right)\epsilon_0 \mathbf{E}$ is the polarization per unit volume, where $\epsilon_{air}$ is the relative dielectric constant of the medium. The excess polarization of the sphere is
\[ \mathbf{P}_e = \left(\epsilon_{sphere} - \epsilon_{air} \right) \epsilon_0 \mathbf{E}_{iz} = \frac{3 \epsilon_{air}}{\epsilon_{sphere} - 2 \epsilon_{air}}\]
Accordingly $\mathbf{\mu}$, the effective dipole moment of the sphere is 
\[ \mathbf{\mu} = 4 \pi a^3 \left( \frac{\epsilon_{sphere}- \epsilon_{air}}{\epsilon_{sphere} + 2 \epsilon_{air}}\right) \epsilon_{air} \epsilon_0 \mathbf{E} \]
and the translation force, $\mathbf{F}$ is
\begin{eqnarray}
\mathbf{F} &=& \mu \cdot \nabla \mathbf{E}\\
		   &=& 4 \pi a^3 \epsilon_{air} \epsilon_0 \left( \frac{\epsilon_{sphere}- \epsilon_{air}}{\epsilon_{sphere} + 2 \epsilon_{air}}\right) \mathbf{E} \cdot \nabla \mathbf{E}\\
		   &=& 2 \pi a^3 \epsilon_{air} \epsilon_0 \left( \frac{\epsilon_{sphere}- \epsilon_{air}}{\epsilon_{sphere} + 2 \epsilon_{air}}\right) \nabla E^2
\end{eqnarray}
So the dielectrophoretic force is proportional to the volume, to the difference between the dielectric constant and that of the sorrounding medium, and to the gradient of the square

where $\mathbf{E}_{iz}$ is the internal electric field of the sphere in the direction of the external field. [notes about interenal electric field of a sphere].

\[f_{EP} = qE$$ and $$f_{DEP} = 2 \pi  R_{drop}^3 \epsilon_{air}  K  \epsilon_0  \nabla |E|^2\]

\subsection{Droplet trajectories}
Scales for terminal velocity with Coulomb force, and DEP force. Going to a rigid body model from N-S.

By applying Newton's Second Law of Motion to a single spherical particle moving relative to the surrounding fluid, the differential equation describing the droplet trajectory can be derived
\[m\frac{d^2y}{dt^2} = \mathbf{F}_{EP} + \mathbf{F}_{DEP} + \mathbf{D}\]

%\begin{itemize}
%\item Free surface damping assumptions
%\item Water as a dielectric medium

%\item Electric field for a finite plane of charge, compared with

%\item Trajectory model, important parameters ($\sigma$, $\mathbf{E}$, $\nabla |\mathbf{E}|^2$, $m$, $q$, $L^2/D^2$, $K$)
%\end{itemize}

\begin{figure}
%  \centerline{\includegraphics[height=7cm,width=13cm]{modes.eps}}
  \centerline{\includegraphics[height=7cm,width=7cm]{e88_1_thumb.jpg}}
  \caption{Model outputs}
\label{fig:model_outputs}
\end{figure}

\section{Experimental methods}
Description of drop tower operations.

\subsection{Superhydrophobic surfaces}
Wetting hysteresis. Methods of fabrication, comparison of wetting properties. Comparison of jump velocities between surfaces. Methods for determination of properties, roll-off angle, contact angle using \emph{SE-FIT}. Cassie-wenzel transition. Damping. Droplets are dyed red to improve the quality of image thresholding when digitizing the droplet trajectories during data reduction.

\begin{figure}
%  \centerline{\includegraphics[height=7cm,width=13cm]{modes.eps}}
  \centerline{\includegraphics[height=7cm,width=7cm]{e88_1_thumb.jpg}}
  \caption{SEM images for sandpaper and laser etched acrylic surfaces}
\label{fig:SEM}
\end{figure}

\subsection{Data reduction}
Digitization of droplet trajectories requires several steps of post-processing. Video is first decomposed into a sequence of still images. Trajectories are captured using the particle tracking module in \emph{Fiji}[ref], a derivative of the popular \emph{ImageJ}[ref] package for scientific image analysis. The series of still images is cropped, and the background (that is, the low-entropy pixels) of the series are removed using a builtin ``rolling ball'' algorithm.  Each still is then split into its constituent RGB maps. In this case the green channel images contained the most information, so these were then globally thresholded using the Triangle algorithm to recover a map of the pixels corresponding to the droplet's approximate position in the original still. Finally ellipses are fitted to the pixel map stepping through the time series to determine the positions of the centroid, and the semi-major and minor axes of the droplets during the drop. The results of the particle capture in \emph{Fiji} are shown in Figure \ref{fig:fiji}.

\begin{figure}
%  \centerline{\includegraphics[height=7cm,width=13cm]{modes.eps}}
  \centerline{\includegraphics[height=7cm,width=7cm]{e88_1_thumb.jpg}}
  \caption{Particle tracking before and after}
\label{fig:fiji}
\end{figure}

\subsection{Surface charge density}
Surface potentials of the superhydrophobic surfaces were measured using a \emph{Simco-Ion} FMX-004 electrostatic fieldmeter, in low-range mode measured from 25 $\pm$1 mm above the axis of symmetry. In this mode the electrostatic fieldmeter can measure surface potentials of $\pm$3.00 kV with $\pm$10 $\%$ accuracy.

The superhydrophobic surfaces become charged when a new layer of PTFE is deposited on the surface, they are dried under a fume hood for a period of 30 minutes to an hour, and then are washed with distilled water. In this way surface potentials $\mu = 0.4$kV, $\sigma = 0.2$kV are attained, corresponding to surface charge densities of [numbers]. The exact charging mechanism acting in this case is unknown but the authors suppose the source of the charge is net charge separation by the breakup of an electrical double layer as water is washed off of the surface during their preparation, with trapped charges left on the pillars in the Cassie-Baxter area of the surface[ref]. Spontaneous contact charging of PTFE by water is a well known phenomenon[ref][ref][ref]. It is supposed that the functional mechanism forming the double layer is  electrosomosis of negatively charged ions across the droplet interface to the PTFE surface[ref], though there is apparently controversy[ref].

Variance within a single hydrophobic surface is sometimes very large (large shooters might have a typical strength distribution mode in the dozens of volts, but with 1-3 kV 'hotspots'). This tendency is exaggerated for non-symmetric shooter geometries.

Observed field strength (measured at 25 mm or 1" from any given surface)	was typically in the range of 10-150 V (with a negative polarity). Some outliers were found in the 1-3 kV range. PTFE treatments, and forced air without PTFE drying have the effect of increasing static charge on average. ABS, 3D printed resin and sandpaper surfaces have weaker fields on average than the acrylic, but often still in the low hundreds of volts range.

Field strength was observed to decay exponentially with time; one observation noted a laser etched acrylic hydrophobic surface with an initial uniform 3 kV field decay to 2 kV after about 1 hours time, and decay further to roughly 1 kV about 18 hours later. Air is slightly conductive when ions are present. This implications for the gradual process of charge redistribution across insulating surfaces. Good insulators leak and redistribute charge slowly without the presence of air ions. Theoretically this is true even in the presence of high humidity, as the conductance of most plastics is unaffected by humidity without condensation, due ultimately to the conservation of charge. With the presence of a water film any insulator will immediately discharge. The exponential behavior is also well evidenced for ionized air blower acquired for this research. Initially high voltages can be reduced to the hundreds of volts range in seconds, but further weakening the field to the tens of volts takes minutes.

\subsection{Droplet net charge}
Since, by the earlier scaling, we presuppose the source of the droplet bouncing behavior to be primarily Coulombic in origin (as opposed to dielectrophoretic), the droplet must have some net charge in addition to the charge induced by the electric field. To measure this charge concurrent methodologies were used. The first method of determining the droplet net charge is observation of the deflection of the droplets in the region of a known uniform field in a fashion inspired by Milikan's famous experiment to determine the fundamental charge of the electron [ref]. A uniform, non-rotating field $\mathbf{E}=$kV/m was set up between two parallel, insulated, 120X120mm polished aluminum plates, positioned [number] mm apart using a $\approx$ 700Vdc source. Something about the AC component. Droplets were jumped in freefall from a sandpaper superhydrophobic surface placed between the plates. The surface was first deionized using a balanced \emph{Ptec} IN5120 DC air-ionizer to remove the effect of surface charge of the superhydrophobic surface from perturbing the otherwise uniform field set up between the parallel plates. A schematic of the parallel plate drop apparatus is shown in Figure \ref{fig:millikan}. Since the droplet initial velocity $U_0$ is parallel to the electric field, the droplets are inertial in the direction of the electric force, and we can determine the magnitude of the droplet charge by a balance of Coulombic force and inertia given by the equation of motion

\[ \frac{d^2y}{dt^2} = q\mathbf{E}. \]

[plus image charges, green's function]

Since the drag is negligible in the inertial limit we can find the charge $q$ by fitting a second-order least squares polynomial to the measured droplet positions, equating the $y^2$ term to the constant acceleration, and dividing by the known, constant magnitude of the electric field. From a survey of literature we suppose the droplet charge, if they are indeed charged by contact with PTFE, to be some function of the droplet volume and the residence time on the superhydrophobic surface. But since the characteristic charging time for the droplets is also a function of droplet volume, and [is shown to have a time constant dramatically bigger smaller than that of a typical experimental timescale] we look only for the charge as a function of volume. However, sweeping though droplet volumes over a series of drop tower experiments we find little correlation between droplet volume  and net droplet charge. This is shown in figure \ref{fig:drop_charge}.

\begin{figure}
%  \centerline{\includegraphics[height=7cm,width=13cm]{modes.eps}}
  \centerline{\includegraphics[height=7cm,width=7cm]{e88_1_thumb.jpg}}
  \caption{Parallel plate experimental apparatus.}
\label{fig:millikan}
\end{figure}

\begin{figure}
%  \centerline{\includegraphics[height=7cm,width=13cm]{modes.eps}}
  \centerline{\includegraphics[height=7cm,width=7cm]{e88_1_thumb.jpg}}
  \caption{Parallel plates: Droplet net charge vs volume.}
\label{fig:drop_charge}
\end{figure}

All current hydrophobic surfaces in use in the DDT use PTFE spray treatments. However, sessile droplets can acquire net positive electrical charge by contact with PTFE surfaces through electro-osmosis of ion species. Even in the case of the hydrophobic surface being meticulously grounded with the use of a benchtop ionizer, droplets with non-zero net charge will repel each other dung the jump. Thus, to complete a survey of the typical electrostatic perturbations on droplet kinematics as experienced in the DDT an estimate of charge accumulation on droplets is needed.

The general approach to estimating the droplet charge is by jumping the droplet in the presence of a uniform electric field and measuring the acceleration towards the negative electrode of a parallel plate capacitor per Equation \ref{eq:charge}. This approach is similar to Robert Millikan's original experiment to determine the fundamental charge of an electron. Control of the plate spacing with a known voltage bias allows for an accurate calculation of the magnitude and direction of the electric field.

A 200-880 V AC source (an inexpensive electric flyswatter purchased at Harbor Freight) with a full wave bridge rectifier circuit was prototyped on perf-board for initial experiments to measure droplet charge. The circuit was analyzed on an laboratory oscilloscope to verify that the AC component of the signal was appropriately small (13 mV at 35 kHz). Current was determined to be a relatively safe 80 $\mu$A. The high-voltage source terminals were led to two parallel polished 150x150 mm aluminum plate electrodes. The electrodes were mounted on an extruded aluminum rail for ease of adjustment. All droplet charge experiments were conducted with an electrode spacing of 28.30 mm. With this spacing the calibrated electric field between the plates was 3.5e4 V/m. The electrodes were electrically isolated from the drop rig by two alternating layers of 4 mm thick laser cut acrylic sheet and Kapton tape. Potential across the plates was measured periodically with a load-impedance corrected multimeter to account for battery depletion. The typical capacitor rise time of the plates was measured to be 1.4 s, thus to make the most economical use of the brief window a micro-gravity a weighted switch was set by hand prior to the drop to close the high-voltage circuit, but which passively safed the system at the resumption of 1-g conditions in the tower. The drop apparatus is shown in Fig.

A brief screening experiment was conducted which alternated the polarity of the field by switching the positive and negative terminal leads between plates. Qualitative observations of droplet electrode preference seem to indicate that the assumption of small polarization stress was well founded. Following this a orthogonal array $3^2$ factorial design experiment with two replicates was conducted to test the effect of varying droplet volume and surface stay time on net charge at the time of jumping. It was hypothesized in accordance with previous studies \cite{Choi:2013dg}, that net charge would increase for levels of both factors. The results of the factorial experiment are presented in Fig. \ref{fig:chart1}. ANOVA analysis of the linear multiple regression model for the data set  indicates that neither droplet volume ($p=0.105$), nor surface stay time ($p=0.358$) is significant at the 95\% confidence level. The overall model F-statistics (2.177 in 2 and 13 degrees of freedom), and coefficients of determination ($r^2 = 0.2509$) indicate that the linear model neither fits the data particularly well, nor does it offer an improvement over the mean model. The mean charge was determined to be positive 2.3e-11 C, with a standard deviation of 1.8e-11 C.

The failure of the model to describe the data raises interesting questions about the validity of our initial assumptions. Typical Reynolds numbers ($R_e=280$ average) indicate the general validity of the assumed quadratic drag model. The drag scale quantity given by Eqn. \ref{eqn:drag} was much less than 1 for all test runs, with mean value of 1.0e-2 and a standard deviation of 2.0e-3, which adds credence to a force balance of pure inertia and electrostatic force.

An additional source of concern was that droplets in three of eighteen runs exhibited accelerations opposite to the expected direction. There is no pattern to the distribution of anomalous droplet accelerations, as they all occurred at unique level combinations. There are only four obvious ways of explaining this anomaly, and perhaps the problems of the general model as well. The first is that the electric field is in fact non-uniform and polarization stress is non-negligible. This option seems unlikely owing to the fundamental design of the experimental apparatus. If we ignore dielectric properties of the air between the plates, the electric field lines should be parallel and have equal magnitudes throughout the experimental area. A second possibility is that the few contrarian droplets actually accumulated net negative charge, instead of the net positive charge to be expected on the basis of evidence from some of the aforementioned studies. While this is not impossible in principle, it raises the spectre of new unknown confounding variables at work with the hydrophobic surfaces themselves. A third possibility is that another force neglected in the analysis, with some component in the direction opposite of the electric field, has an order one magnitude.

A final possibility lies with the means used to measure the acceleration of the droplets (and thence the electrostatic force). The droplet time variant position, measured using manual tracking methods in NASA Spotlight image analysis software, was used to calculate discretized instantaneous velocities for the length of the trajectory. The slope of the linear regression of instantaneous velocity versus time was taken to be the average acceleration of the droplet. Admittedly this approach does not lend itself well to accuracy as small errors during the manual tracking process are integrated twice in the final result. The average coefficient of determination for the population of instantaneous velocity regressions is 0.27 (with a range of 3.0e-4 to 0.75), and the anomalous data is generally more scattered than this mean value. If this is the source of the anomalous accelerations, and the error is random and normally distributed then the accelerations should, in principle, disappear with further repeated measures.

Use of concurrent methods for measuring the charge could resolve the question of the anomalous accelerations. This can be done by direct measurement of droplet using a field meter and Faraday cup. Unfortunately, such an approach requires specialized, highly-sensitive field meters. At present the expense of such sensors renders this approach impractical. Another possible approach is to compare experimental droplet interface curvature in the presence of a controlled electric field in 1-g to those computed using SE-Fit software find an equivalent elkectrostatic Bond number and thus the electrostatic body force acting on the droplet.

The droplet positive net charge developed by contact with a PTFE surface corresponds to findings elsewhere in literature \cite{Choi:2013dg} \cite{Miljkovic:2013dg} \cite{Moreno-Villa:1998dg}. The smallest droplet size treated in the present work is several times larger than the largest in any of comparable study. The most relevant comparison found droplet static charge of 2.5e-10 C for 10 $\mu$L droplets charged by pipetting from a PTFE tipped needle \cite{Choi:2013dg}. The present results mean charge level of 2.3e-11 C is, within error, roughly six times smaller than the cited study.

A second approach to determining the net droplet charge is by direct measurement in a shielded Faraday cup using an extremely high input resistance electrometer, specifically a \emph{Keithly} 616 digital electrometer. [note on operational philosophy, data collection]. Correlation of net charge to droplet volume is shown again for in figure \ref{fig:electrometer}.

\begin{figure}
%  \centerline{\includegraphics[height=7cm,width=13cm]{modes.eps}}
  \centerline{\includegraphics[height=7cm,width=7cm]{e88_1_thumb.jpg}}
  \caption{Electrometer: charge vs. volume.}
\label{fig:electrometer}
\end{figure}

Discussion on discrepancy between the two approaches. \citep{magarvey_experimental_1962}

\section{Results}
\begin{itemize}
\item Acceleration histories
\item ANOVA to compare variance of jump velocity to variance in charge or nonuniformity of field between tests... Electrowetting.
\item Comparison of the model to experimental data
\item Gravitational analog, validity of the stability model, bifurcation, linear stability
\end{itemize}

\begin{figure}
%  \centerline{\includegraphics[height=7cm,width=13cm]{modes.eps}}
  \centerline{\includegraphics[height=7cm,width=7cm]{e88_1_thumb.jpg}}
  \caption{Acceleration histories compared for different $q/m\sigma$}
\label{fig:acceleration}
\end{figure}

\begin{figure}
%  \centerline{\includegraphics[height=7cm,width=13cm]{modes.eps}}
  \centerline{\includegraphics[height=7cm,width=7cm]{e88_1_thumb.jpg}}
  \caption{Comparisons to the model}
\label{fig:model_comp}
\end{figure}

\begin{figure}
%  \centerline{\includegraphics[height=7cm,width=13cm]{modes.eps}}
  \centerline{\includegraphics[height=7cm,width=7cm]{e88_1_thumb.jpg}}
  \caption{Gravitational analog}
\label{fig:stability}
\end{figure}

\section{Further Work}
Concepts for other geometries. N-body interactions.

\begin{figure}
%  \centerline{\includegraphics[height=7cm,width=13cm]{modes.eps}}
  \centerline{\includegraphics[height=7cm,width=7cm]{e88_1_thumb.jpg}}
  \caption{Conductive S.H. surface apparatus schematic.}
\label{fig:conductive_SH_apparatus}
\end{figure}

\begin{figure}
%  \centerline{\includegraphics[height=7cm,width=13cm]{modes.eps}}
  \centerline{\includegraphics[height=7cm,width=7cm]{e88_1_thumb.jpg}}
  \caption{FEM solution in \emph{Agros2D}.}
\label{fig:FEM_DEP}
\end{figure}

\bibliographystyle{jfm}
%\citep{magarvey_experimental_1962}
% Note the spaces between the initials
\bibliography{test}

\appendix
\section{\\Surface charge density}
Since the laser-etched acrylic, and sandpaper superhydrophobic surfaces are both dielectric materials there are some additional considerations for determining the surface charge density. Firstly, for an insulated conductor $A$ with charge $q$, the charge distribution in equilibrium will be such that the field on the interior of the conductor is zero, with field lines being normal to the surface and the integral of the field strength $\mathbf{E}$ from any point $P$ in or on the conductor to a ground point $G$ is a constant given by
\[ V = \int^G_P \mathbf{E} \cdot da, \]
where $V$ is the voltage or potential of the conductor (or alternatively, the surface voltage potential). The voltage $V$ and the charge $q$ are proportional and $q$ is usually given by
\[q = CV, \]
where $C$ is the capacitance of the insulated conductor and is determined by the conductor's size and shape, and its placement relative to the conductors and ground. However, the case of a charged insulator departs significantly from that of the insulated conductor. Here we have the possibility of the density and net polarity of the charge varying as a function of position about the surface. The field of the interior may not be zero, and the field lines are not necessarily normal to the the surface. The integral of the field strength from a point on or in the insulator to ground is usually different from point to point. In general the surface voltages will vary from point to point on an insulator (including point on the interior of the insulator. Therefore it is not possible to uniquely define the voltage of a charged insulator, except in certain contrived cases (notably the the potential of a uniformly charged sphere positioned infinitely far away from any conductors). It follows that there is no definition for the capacitance of an insulator as well. Though insulative sheets may store charge and discharge in the manner of capacitors, this discharge is never particularly complete.

There are two cases where we can make meaningful quantitative measurements of state variables for charged insulators: we can measure the electric field arising from the charge, and possible the total charge for uniformly charged free insulative sheets, and uniformly charged insulative sheets backed by a grounded conductor. To do this we can use field meters and non-contacting voltmeters. If the field strength indicated on the meter is $\mathbf{E}$, the charge density $\sigma$ on the part of the insulator in the front should be $\sigma = \epsilon_0 \mathbf{E}$. If a non-contacting voltmeter is placed a at a distance $d$ from the sheet, then the surface voltage $V_s$ indicated on the meter is given by 
\[V_s = d \mathbf{E} = d \frac{\sigma}{\epsilon_0}. \]

An ideal approach to determining surface charge on a dielectric surface is to screen perturbing effects of external electric fields. This is partly accomplished by grounding the fieldmeter, and by placing the dielectric sample on a grounded conductive plate backing. In this case the surface charge density is determined from

\[ \sigma = \frac{V_s \epsilon}{l}, \]

where $l$ and $\epsilon$ are the absolute permittivity and thickness of the dielectric surface respectively. The measured surface voltage is a function of position away from the charged dielectric. In most cases this function is relatively constant at a distance about 1-2 cm away from the surface (there is some measurement error in surface voltage due to small mispositioning of the electrostatic fieldmeter, say by $\pm$1 mm) and add it to the precision error of measurement in $V_s$. The measured surface voltage can also be compared to the analytically derived surface voltage determined from the analytical expression for the electric field from above, and to those determined from finite element solutions to poisson's equation on the domain in question. [Notes about \emph{Agros2D}] The surface voltage is shown schematically as a function of the measurement distance in Figure \ref{fig:surface_voltage} for a sample charge density $\sigma = $.

\begin{figure}
%  \centerline{\includegraphics[height=7cm,width=13cm]{modes.eps}}
  \centerline{\includegraphics[height=7cm,width=7cm]{e88_1_thumb.jpg}}
  \caption{Measured surface voltage versus position.}
\label{fig:surface_voltage}
\end{figure}

A further consideration is the possibility of the change in total charge during a typical experimental timescale. If we consider the drop rig to be a ground (which seems reasonable given that the rig is isolated from true ground, but is at some reference voltage with respect to the surface charges on the dielectric, it also has an abundance of free charge carriers, that it, it is conductive), then there will be both bulk and surface decay of the charge on the dielectric. The evolution of the charge can be approximated by
\[ \sigma = \sigma_0 e^{\frac{-t}{\epsilon \rho}}, \]
where $\sigma_0$ is the initial surface charge density, and $\rho$ is the bulk resistivity (which can also be reframed in terms of conductivity by $\rho = 1/\gamma$, where $\gamma$ is the conductivity). For an example case of a surface with an initial surface charge density $\sigma = 2.4 \cdot (10^{-6})$ $C/m^2$, relative permittivity $\epsilon = 3.5$ and bulk resistivity $\rho = 1.6 \cdot (10^{16})$ $\Omega/cm$ such as with the case of 1/4'' continuous cast acrylic sheet, then the time constant $\tau = \epsilon \rho$ is approximately 5000 s, which is a great deal longer than the typical time period for of a drop tower experiment.

\section{\\Data smoothing}
In trying to recover the kinematic variables from the droplet trajectories we encounter a difficulty in the noise of the position data:

\begin{itemize}
\item Notes from Wood, ``Data smoothing and Differentiation procedures in Biomechanics''

\item Signal-to-noise ratio is $\mathcal{O}(f)$ for $\frac{df}{dt}$ and $\mathcal{O}(f^2)$ for $\frac{d^2f}{ft^2}$. Refs 5, 14, 49, 95.

\item Error sources include misalignment of the camera, perspective due to objects (subject or reference scale) being out of the photographic plane, precision limits in digitization. Some of these errors are systematic in origin and introduce consistent biases into the data (e.g. coherent spectral sources, rather than truly stochastic noise). These systematic sources of error include inaccurate scales among others. Data smoothing tends not to help with the systematic errors in that they are usually of lower frequency than the signal (and here we are trying specifically to filter high frequency noise).

\item Random errors are assumed to have a Gaussian distribution (by the central limit theorem), and are independent of the signal (which inherently results from a deterministic process).

\item Central differences are usually a better approximation of the instantaneous value of the true derivative of the signal, as compared to forward differences. The finite differences are mathematically equivalent to passing a quadratic interpolating polynomial through the three points of the central difference (assuming the window size of the central difference is $N=3$, larger windows are possible). To obtain an approximation for the $m^{th}$ derivative of $f(x)$ at least an $m^{th}$ order polynomial is required.

\item One straightforward approach to getting the position derivatives is to fit a least squares polynomial to the global position data, and analytically differentiate. This is a simple to apply, and therefore quite popular approach. The order of the polynomial is picked from theory, by ANOVA, or comparison of the residuals to determine goodness of fit for $m+1$. It should be stress that there are significant drawbacks with this approach: firstly is that when derived values depend on both accuracy of segmented displacement-time data and body segmental parameters (segmental masses and center of mass locations), then the errors are confounded and it is difficult to evaluate the accuracy of the derivative. Secondly, statistics used to asses agreement between curves are either in-appropriate because they aim to represent fundamentally deterministic processes in probabilistic ways (as would be the case using a product-moment correlation), or there is no test of significance (as is the case with a mean-errors correlation). Finally High order effects are easily lost by a global polynomial fit for time series containing multiple length scales or frequencies, as is the case here [ref].
\end{itemize}

In lieu of global polynomial fits we can attempt at finite differencing the data after the application of smoothing filters. Some of these approaches are global and/or recursive whereas other approaches are applied locally. Each approach has various natural advantages and disadvantages. A number of approaches were implimented in \emph{Python} or imported from the scientific computing package \emph{SciPy}[ref] and compared for a test set of trajectory data; these methods include convolution with the derivative of a Gaussian kernel, Wiener filtering, smoothing splines, Butterworth low-pass filtering, total-variance regularization, and Savitsky-Golay filtering. Qualitatively comparing these smoothing methods we find that we loose too many data points in the smoothing process, the variance remains large (especially in higher derivatives), large amplitudes are overly smoothed by repeated filtering passes, or there are significant end effects for most of these methods. A comparison of these smoothing approaches on a representative trajectory data set are shown in Figure \ref{fig:filters}. The power spectra for the same data are compared for these methods in Figure \ref{fig:power_spectra}.

\begin{figure}
%  \centerline{\includegraphics[height=7cm,width=13cm]{modes.eps}}
  \centerline{\includegraphics[height=7cm,width=7cm]{e88_1_thumb.jpg}}
  \caption{Filtered or fitted droplet trajectories compared to raw data.}
\label{fig:filters}
\end{figure}

\begin{figure}
%  \centerline{\includegraphics[height=7cm,width=13cm]{modes.eps}}
  \centerline{\includegraphics[height=7cm,width=7cm]{e88_1_thumb.jpg}}
  \caption{Power spectra of the filter methods compared.}
\label{fig:power_spectra}
\end{figure}

Savitsky-Golay filtering seems to produce the smoothest derivatives without overfitting of otherwise misrepresenting the underlying signal. The Savitsky-Golay algorithm

\end{document}

### 2017-07-30 doc/manuscript/ef_notes.tex
added data for bounces

--- 2017-06-13 ef_notes.tex
@@
 \usepackage{listings}
+\usepackage{verbatim}
 \lstset{
@@
 \section{The Electric Field}
+\begin{comment}
 Being thus armed with the assumption of a purely electrostatic problem (the electric field is conservative, that is $\nabla \times \mathbf{E} = 0$, where $\mathbf{E}$ is the electric field) we can describe the electric field by the Laplace equation for the electric potential.
@@
 
+The in lieu to an analytical solution to Laplace's equation on a dielectric half-space domain by separation of variables or other methods we might try modeling the static charge distribution by a series of Dirac delta funtions after the fasion of a Green's function.
+In the 2D case we have,
+\begin{equation}
+\varphi(x,z) = \frac{z}{\pi}\int^\infty_{-\infty} \frac{\rho(x^\prime)}{(x-x^\prime)^2 + z^2}dx^\prime
+\end{equation}
+\end{comment}
+We are faced with the need to compute the total electric field arising from the presence of free charge on the surface of a polarizable dielectric. In the electrostatic case we have
+\begin{eqnarray}
+\nabla \times \mathbf{E(r)}&=&0 \\
+\nabla \cdot \mathbf{D(r)}&=&\rho(\mathbf{r}).
+\end{eqnarray}
+If the dielectric is linear and isotropic then the displacement field is 
+\begin{equation}\label{displacement}
+\mathbf{D(r)} = \epsilon(\mathbf{r})\mathbf{E}(\mathbf{r}).
+\end{equation}
+Given that the electric field is defined as the gradient of the scalar potential, $\mathbf{E}=-\nabla \varphi $, we can write equation \ref{displacement} as 
+\begin{equation}
+\nabla \cdot \left[\epsilon(\mathbf{r})\nabla \varphi (\mathbf{r}) \right] = -\rho (\mathbf{r}).
+\end{equation}
+This is a form of \emph{Poisson's equation}.
+Our general method for finding the electric field, will solve $\varphi (\mathbf{r})$ on a half-space domain with permittivities $\epsilon_1$, $\epsilon_2$ for a point source using the free-space \emph{Green's function}.
+We can then find the total electric field by superposition of the individual Green's functions by direct integration.
+
+The non-homogoneous part of the Poisson's equation for the electrostatic potential is a Green's function, denoted by $\mathbf{G}(\mathbf{r} | \mathbf{r^\prime})$, where $\mathbf{G}$ satisfies Poisson's equation at $\mathbf{r}$ when the point source is located at $\mathbf{r^\prime}$ such that
+\begin{equation}
+\nabla^2 \mathbf{G}(\mathbf{r} | \mathbf{r^\prime}) = -\delta( \mathbf{r} - \mathbf{r^\prime}).
+\end{equation}
+Using the identity for the position vector $\nabla
+
 \section{A Simple Dynamical Model}
@@
 \section{Stability}
-\section{Future Directions}
 \section{Conclusions}

### 2017-10-19 doc/manuscript/outline.tex
made pretty plots

\documentclass[a4paper, 12pt]{article}
\usepackage{changepage}
\usepackage{color,soul}
\usepackage{listings}
\usepackage{verbatim}
\lstset{
basicstyle=\small\ttfamily,
columns=flexible,
breaklines=true
}
\title{\textsf{\textbf{Droplet Electro-Bouncing in Low-Gravity}}}
\vspace{-25mm}
\author{Erin S. Schmidt, Mark M. Weislogel}
\date{}

\usepackage{abstract}
\renewcommand{\abstractnamefont}{\normalfont\bfseries}
\renewcommand{\abstracttextfont}{\normalfont\small\itshape}

\begin{document}
\maketitle

\begin{abstract}
\noindent
Notes on electric fields `n stuff.
\end{abstract}

\section{Overview}
In design of fluidic systems for the environment of space we are often forced to deal with the inadequacy of our terrestrial born expectations about the behaviors of the physics of fluids.

\begin{itemize}
\item In the absence of gravity the influence of usually negligible electrostatic forces can suprise the unready. We have observed electrostatic accelerations 0.5 $mL$ water droplets on the order of 10's of $cm/s^2$ in proximity to charged surfaces. It's quite easy to (accidentally) charge dielectric surfaces as well. Simply washing fluorinated surfaces with water can induce large surface potentials (hundreds of volts).

\item We can harness these forces for useful applications in a low-gravity environment. This ties into the dreaded ``phase-separation'' problem of low-gravity which arises in the absence of a body force like gravity. Some decades of research has focused on the various manifestations of this problem (tank venting, propellant settling, gas ingestion during tank draining or PMD rewetting, mixing, etc.) and their means of resolution, usually by artifice of a susbstitute body force (such as electric forces). Applications for means of manipulating large droplets in microgravity include electrostatic precipitators, condensing heat exchanges, droplet radiators, droplet column reactors, and container-less processing.

\item Mainly we are concerned about what parameters are important in electrostatic transport of relatively large (e.g. millimetric) droplets in low-gravity, and what the values of the respective dimensionless groups might be. This raises an interesting challenge; determination of net droplet electric charge beyond ideal cases we system capacitance is easily determined (such as between parallel plane electrodes).

\end{itemize}
\section{Methods}
To find typical vales of these parameters we employed spontaneous droplet jumps on charged dielectric super-hydrophobic surfaces under low-gravity conditions in a 2.1 $s$ drop tower. Using high-speed video and image analysis software we captured the trajectories of the droplets. Then we solved the inverse problem to find the key parameters by minimizing the $\chi^2$ goodness-of-fit statistic between an observed trajectory and the trajectory predicted by a dynamical model given that certain set parameters. The best fit parameters obtained by direct-search are those corresponding to the maximum likelihood experimental values of the parameters subject to the validity of the assumptions encoded in the model, and the constraints set by the measurement precision of measured independent variables.

\subsection{Experimental}
\begin{itemize}
\item A very low-tech superhydrophobic electret was produced, with surface potentials 0.7-4.0 $kV$ and contact angles $\sim 150^{\circ}$ with approximately $20^{\circ}$ contact angle hysteresis when uncharged. The dielectrics are a lamina of 3-4 corona charged 0.4 $mm$ PMMA sheets. The electric field scales with the number of dielectric lamina. The final, superhydropobic layer, is produced by laser etching PMMA, and depositing a thin layer of PTFE on the resulting roughness topology to increase the Young's angle. The surface charge density can be modulated during the experiment by means of a 0-2 $kV$ DC-DC converter, which can re-polarize the dielectric substrate by means of an embedded electrode, and the resulting bound charge partially or fully neutralizes the electric field due to the surface ions deposited by corona charging of the electret.
\end{itemize}

\subsection{Parameter Estimation}
\begin{itemize}
\item The solution of the inverse problem  was achieved by direct search, using the \emph{Nelder-Mead} simplex algorithm. \emph{Nelder-Mead} is not robust to noise in the objective function so the experimental data and its approximate derivatives were interpolated by \emph{Savitsky-Golay} smoothing splines.
\end{itemize}

\section{Results}
\begin{itemize}
\item We found the distribution of mostly likely experimental net charges for a population of the droplets jumped in low-gravity. We found the charge to be a function of droplet volume and surface potential of the dielectric substrate. A two-ways T-test with a charge distribution determined by a corollary experiment suggests that the droplet charge is induced by the electric field (rather than through contact charging on the PTFE layer).

\item The bounce dynamics are controlled by a dimensionless ratio of electrostatic force to inertia. The dielectrophoretic force plays a very small role when droplets have net charge in a DC field.

\item Using the unique capabilities of the low-gravity environment we obtained data on dimensionless contact time and coefficients of restitution at very low Ohnesorge numbers for a range of electric Bond numbers. Despite strong electric fields (20-30 $kV/cm$) we found little evidence for wetting transitions due to excession of a critical pressure (the ``Fakir impalement''). There is no obvious trend in dimensionless contact time or coefficient of restitution with electric Bond number.

\item Jump velocities are more strongly damped for relatively small droplet volumes in the presence of the electric fields than was shown by Attari \emph{et. al.}. This may be evidence for electrowetting paradoxically enhancing the effect of contact angle hysteresis pinning on sharp corners. (How does this tie into the coefficients of restitution problem?)

\item We can extrapolate a simple rule if thumb in droplet ``escape velocity'' of impacts and time scales for returns.

\end{itemize} 
\end{document}

### 2017-10-25 doc/figures/asgsr_scratch.tex
updated the last few figs

\documentclass[10pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\author{Erin Schmidt}
\begin{document}
\[ m y'' + q \mathbf{E}_0 = 0 \hspace{2 mm} \mbox{subject to } \hspace{2 mm} y(0) = 0, \hspace{2 mm} y'(0) = U_0 \] 
\[ t_0 \sim \frac{m U_0}{q E_0}, \hspace{2 mm} y_0 \sim \frac{m U_0^2}{q E_0}\]
\[\frac{y_0}{L} \sim \frac{m U_0^2}{q E_0 L} \equiv {\mathbb{E}\mbox{u}}_e \equiv \frac{\mbox{inertia}}{\mbox{electrostatic force}}\]

\newpage
\begin{equation*}
\mbox{min} \hspace{2 mm} \chi^2 = \sum^n_{i=1} \frac{\left({yO(x)}_i - yX(x)_i \right)^2}{yX(x)_i}
\end{equation*}
\[\mbox{where} \hspace{2 mm} yX(x) \hspace{2 mm} \mbox{is a solution of} \hspace{2 mm} m y'' = \frac{1}{2} \rho C_D A_d^2 {y'}^2 + \rho_f \mathbf{E}(y) + \frac{1}{2} \left| \mathbf{E}(y) \right|^2 \nabla \epsilon\]
\begin{eqnarray*} \mbox{given} \hspace{2 mm} \begin{split}x = \left\{ \begin{array}{ll}      & V_d\\
          & \sigma 
          \end{array} \right. 
          \end{split} \hspace{2 mm} \mbox{subject to} \hspace{2 mm} \begin{split}
          g = \left\{ \begin{array}{ll}
          & V_d \pm u_{exp}\\
      	  & \sigma \pm u_{exp}\\
      	  & y_0 \pm u_{exp}\\
      	  & t_0 \pm u_{exp}\\
          \end{array} \right. 
          \end{split}
\end{eqnarray*}
\end{document}

### 2017-10-25 doc/figures/asgsr_scratch.tex
added to scratch

@@
 \begin{document}
+\subsection*{Playing with Scales}
+In the inertial limit, and with $y \ll L$,
 \[ m y'' + q \mathbf{E}_0 = 0 \hspace{2 mm} \mbox{subject to } \hspace{2 mm} y(0) = 0, \hspace{2 mm} y'(0) = U_0 \] 
@@
 \newpage
+\subsection*{Parameter Estimation}
+We find the parameters $\mathbf{x}$ that solve the inverse problem $G(\mathbf{x}) = D$, using a direct search method (\emph{Nelder-Mead}). 
 \begin{equation*}
-\mbox{min} \hspace{2 mm} \chi^2 = \sum^n_{i=1} \frac{\left({yO(x)}_i - yX(x)_i \right)^2}{yX(x)_i}
+\mbox{min} \hspace{2 mm} \chi^2 = \sum^n_{i=1} \frac{\left({yD(\mathbf{x})}_i - yG(\mathbf{x})_i \right)^2}{yG(\mathbf{x})_i}
 \end{equation*}
-\[\mbox{where} \hspace{2 mm} yX(x) \hspace{2 mm} \mbox{is a solution of} \hspace{2 mm} m y'' = \frac{1}{2} \rho C_D A_d^2 {y'}^2 + \rho_f \mathbf{E}(y) + \frac{1}{2} \left| \mathbf{E}(y) \right|^2 \nabla \epsilon\]
-\begin{eqnarray*} \mbox{given} \hspace{2 mm} \begin{split}x = \left\{ \begin{array}{ll}      & V_d\\
+\[\mbox{where} \hspace{2 mm} yG(\mathbf{x}) \hspace{2 mm} \mbox{is a solution of} \hspace{2 mm} m y'' = \frac{1}{2} \rho C_D A_d^2 {y'}^2 + q \mathbf{E}(y) + \frac{1}{2} \left| E(y) \right|^2 \nabla \epsilon\]
+\begin{eqnarray*} \mbox{} \hspace{2 mm} \begin{split} \mathbf{x} = \left\{ \begin{array}{ll}      & q\\
+		  &	V_d\\
           & \sigma 

### 2017-11-08 doc/figures/asgsr_scratch.tex
changes to figures

@@
 \begin{equation*}
-\mbox{min} \hspace{2 mm} \chi^2 = \sum^n_{i=1} \frac{\left({yD(\mathbf{x})}_i - yG(\mathbf{x})_i \right)^2}{yG(\mathbf{x})_i}
+\mbox{min} \hspace{2 mm} \chi^2 = \mbox{min} \hspace{2 mm} \sum^n_{i=1} \frac{\left({yD(\mathbf{x})}_i - yG(\mathbf{x})_i \right)^2}{yG(\mathbf{x})_i}
 \end{equation*}
-\[\mbox{where} \hspace{2 mm} yG(\mathbf{x}) \hspace{2 mm} \mbox{is a solution of} \hspace{2 mm} m y'' = \frac{1}{2} \rho C_D A_d^2 {y'}^2 + q \mathbf{E}(y) + \frac{1}{2} \left| E(y) \right|^2 \nabla \epsilon\]
+\[\mbox{where} \hspace{2 mm} yG(\mathbf{x}) \hspace{2 mm} \mbox{is a solution of} \hspace{2 mm} m y'' = \frac{1}{2} \rho C_D A_d {y'}^2 + q E(y) + \frac{1}{4} \frac{K q^2}{y^2} + \frac{1}{2} {E(y)}^2 \nabla \epsilon\]
 \begin{eqnarray*} \mbox{} \hspace{2 mm} \begin{split} \mathbf{x} = \left\{ \begin{array}{ll}      & q\\
@@
           g = \left\{ \begin{array}{ll}
-          & V_d \pm u_{exp}\\
-      	  & \sigma \pm u_{exp}\\
-      	  & y_0 \pm u_{exp}\\
-      	  & t_0 \pm u_{exp}\\
+           V_d &\pm \hspace{2 mm} u_{exp}\\
+      	   \sigma &\pm  \hspace{2 mm} u_{exp}\\
+      	   y_0 &\pm \hspace{2 mm} u_{exp}\\
+      	   t_0 &\pm \hspace{2 mm} u_{exp}\\
           \end{array} \right. 

### 2017-11-08 doc/manuscript/outline.tex
changes to figures

@@
 \noindent
-Notes on electric fields `n stuff.
+It's an abstract.
 \end{abstract}
+
+\section{Introduction}
 
@@
 \begin{itemize}
-\item In the absence of gravity the influence of usually negligible electrostatic forces can suprise the unready.
+\item In the absence of gravity the influence of usually negligible electrostatic forces can surprise the unready.
 We have observed electrostatic accelerations 0.5 $mL$ water droplets on the order of 10's of $cm/s^2$ in proximity to charged surfaces.
@@
 
-\item We can extrapolate a simple rule if thumb in droplet ``escape velocity'' of impacts and time scales for returns.
+\item By scale arguments and perturbation of solutions to the equations of motion we find several simple rules of thumb in droplet ``escape velocity'' of impacts, length scales and time scales for returns.
 

### 2018-01-04 doc/manuscript/parameter_esimation.tex
added notes on parameter estimation

\documentclass[10pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{color,soul}
\usepackage{listings}
\author{Erin Schmidt}
\begin{document}
\section{Parameter Estimation}
A non-dimensional number: $ {\mathbb{E}\mbox{u}}_e$.

We find the parameters $\mathbf{x}$ that solve the inverse problem $G(\mathbf{x}) = \mathbf{d}$, using a direct search method (\emph{Nelder-Mead}). 
\[
\mbox{min} \hspace{2 mm} \chi^2 = \mbox{min} \hspace{2 mm} \sum^n_{i=1} \frac{\left({y_d(\mathbf{x})}_i - y_G(\mathbf{x})_i \right)^2}{y_G(\mathbf{x})_i}
\]
\begin{eqnarray*} \mbox{} \hspace{2 mm} \begin{split} \mathbf{x} = \left\{ \begin{array}{ll}      & q\\
		  &	V_d\\
          & \sigma 
          \end{array} \right. 
          \end{split} \hspace{2 mm} \mbox{subject to constraints} \hspace{2 mm} \begin{split}
          g = \left\{ \begin{array}{ll}
           V_d &\pm \hspace{2 mm} u_{exp}\\
      	   \sigma &\pm  \hspace{2 mm} u_{exp}\\
      	   y_0 &\pm \hspace{2 mm} u_{exp}\\
      	   t_0 &\pm \hspace{2 mm} u_{exp}\\
          \end{array} \right. 
          \end{split}
\end{eqnarray*}
where $y_G(\mathbf{x})$ is a numerical solution of the equation of motion
\[
m y'' = \frac{1}{2} \rho C_D A_d {y'}^2 + q E(y) + \frac{1}{4} \frac{K q^2}{y^2} + \frac{1}{2} {E(y)}^2 \nabla \epsilon\]

In particular, it is impractical to directly measure the droplet net charge $q$, during a bounce experiement. Our workflow to identify these parameters is as follows:
\begin{enumerate}
\item Experimentally vary $V_d$, $\sigma$ and capture droplet trajectories using a high-speed camera.
\item Digitize droplet trajectories by using automatic tracking of ellipse-fitted centroids on the thresholded video.
\item Slice droplet trajectories by their bounce minima, and apply a smoothing filter.
\item Maximize the goodness of fit between the experimental trajectories and solutions of the equation of motion, by varying the design vector (which encodes the unkown parameters in the equation of motion) using a direct search optimizer. 
\end{enumerate}
\subsection*{Inverse Problems}
\begin{itemize}
\item We have a dynamical model describing the droplet electro-bounce; we wish to find typical values of the key parameter, droplet net charge $q$. In general it is not always possible nor practicle to measure model parameters experimentally. They may be hard, expensive, time consuming or perhaps even impossible to measure. 
\item A mathematical model designed to fit experiemental data so as to explicitly quantify physical parameters of interest.
\item Values of model parameters are obtained using parameter estimation techniques aimed at providing a ``best fit'' to the data.
\item Generally involves an interative process to minimize the average difference between the model and the data.
\item Evaluating the quality of an inverse model involves a combination of established mathematical techniques as well as intuition and creative insight.
\item A good inverse model has: good fit, model parameters are unique, and parameter values consistent with physical inuition or prior knowledge.
\item The steps in the process are: 1. Select an appropriate mathematical model from theory. 2. Define a ``figure of merit'' function which measures agreement between the data and model for a given set of parameters. 3. Adjust model parameters to get a ``best fit''. 4. Evaluate ``goodness of fit'' to data, which tends never to be perfect due to experimental noise. 5. Estimate accuracy fo the best-fit parameter values (provide confidence intervals and determine uniqueness). 6. Determine whether a much better fit is possible (which is difficult of ruggest respose surfaces; F-test can be used for comparing models of different complexity).

\item Maximum likelihood estimation: not ``what is the probability that my set of model parameters is correct?'' but rather ``given my set of model parameters, what is the probability that this data set occurred (what is the likelihood of the parameters given the data)?''

\item \hl{[notes on $\chi^2$ goodness-of-fit]}

\item Model parameter estimation is the process of indirect determination of unknown model parameters  from measurements of experiemental data.
\item This is mathemetically challenging \hl{[ref]}. There are practical challenges as well, as experimental data tends to be noisey and sparse.
\item In the most familliar sense determining model parameters is done using derivative based methods, essentially by estimating derivatives by finite differences (Euler's method) and fitting paramters using linear regression. However there are approaches to fitting any arbitrary function.
\item Suppose we have a model $G(\mathbf{m})$, with a vector of parameters $\mathbf{m}$, and set of perfect noiseless observations $\mathbf{d}$, we expect there to exist a relationship 
\[G(\mathbf{m}) = \mathbf{d} \]
where the operator $G$ might be an ODE.
\item Suppose we have a model given by the ODE
\[ \frac{dy}{dt} = f(t, \mathbf{y}; \mathbf{p}), \mathbf{y} \in \mathbb{R}^n, \mathbf{f} \in \mathbb{R}^n ,\]
where $\mathbf{p} \in \mathbb{R}^m$ is the vector of parameters, and a collection of measurements of experiemental data
\[ \left( t_1, \mathbf{y_1} \right), 
\left( t_2, \mathbf{y_2} \right), ... ,
\left( t_k, \mathbf{y_k} \right).\]
We wish to minimize an objection function which is the mean square error (or any goodness of fit figure of merit in general) between the model output and experimental data:
\[ \mbox{obj}(\mathbf{p}) = \sum_{j=1}^k \left|\mathbf{y}(t_j; \mathbf{p}) - \mathbf{y_j} \right|^2,\]
where $| . |$ is the Euclidian norm. Therefore the parameter estimation problem is a variety of optimization problem.
\item The process of fitting a function, defined by a collection of parameters, to a data set is called the discrete inverse, or parameter estimation problem (as opposed to the \emph{forward problem} to find $\mathbf{d}$ given $\mathbf{m}$ and $G(\mathbf{m})$).
\end{itemize}

\subsection*{Optimization}
Most generally the we state the constrained problem as 
\[
\begin{array}{lll}
\mbox{minimize:} & \hspace{2 mm} F\left(\mathbf{x}\right) & \mbox{objective function}\\
\mbox{subject to:} & & \\
& \centering g_j \left( \mathbf{x} \right) \leq 0 & \mbox{inequality constraints}\\
& \centering h_k \left(\mathbf{x} \right) = 0 & \mbox{equality constraints}
\end{array}
 \]

\[ 
\begin{array}{ll}
\mbox{where} \hspace{2 mm} \mathbf{x} = \left\{ \begin{array}{ll}

x_1 & \\
x_2 & \\
\vdots &\\
x_n &
\end{array} \right. & \mbox{design variables}
\end{array}
\]

Our specific optimization problem is non-convex, mixed discrete-continuously black-box (noisy), which is essentially the worst the worst case scenario. While in principle a gradient-based optimizer (such as ...) could be used by using finite-differences to obtain approximate gradients of the $\chi^2$ objective funtion, in practice doing so is problematic becasue the signal-to-noise ratio of the objective function scales like $\mathcal{O}(f)$ for $\frac{df}{dt}$ and $\mathcal{O}(f^2)$ for $\frac{d^2f}{ft^2}$ which will cause problems with our Hessians and Javobians respectively \hl{[Refs 5, 14, 49, 95.]}. As a further practical matter, given the relatively expensive function-calls (which requires solving a stiff, non-linear ODE) gradient-free approaches tend to offer better performence regardless.

\hl{[notes on gradient free optimization, Nelder-mead, sci-py ref]}
\begin{itemize}
\item We use the \emph{Nelder-Mead} algorithem to minimize the $\chi^2$ goodness-of-fit. \emph{Nelder-Mead}, sometimes called simplex-search or downhill-simplex, is a derivative-free direct search, LP method.
\item \emph{Nelder-Mead} is well-established.
\item A hueristic search method, with no guarantee of optimal solutions.
\item Is based on the concept of a simplex, which is a special polytrop of $N + 1$ vertices in $N$ diemsions.
\item Is derivative-free: does not use numerical or analytic gradients.
\item Is implimented in the \emph{Scipy} package for Scientific computing in Python.
\item \emph{Nelder-Mead} is very fast, but generally suitable for low-dimensional problems. Additionally convergence of the alogrithem is highly sensitive to the initial guess design vector $x_0$.
\end{itemize}

We do not have \emph{a priori} information regarding existence of true globality for our objective function. Perhaps more importantly, given the degrees-of-freedom in the parameter space there may be a multiplicity of local extrema of the $\chi^2$ hyper-response surface. \emph{Nelder-Mead} is not a global optimizer, though there are varients which use sequential local searches with probablistic restarts to achieve globality. However global optimization usually comes at a tremendous computational cost.

That we are capabible of fitting any arbitrary model to a dataset given sufficient degrees of freedom in our parameters is admittedly a disconcerting issue, and is manifested in the locality of the extrema of the $\chi^2$ response surface. However, some of the inverse model parameters are constrained by our experimental observations of them and their associated measurement uncertainties. This, we hope, makes the spectre of an overfitted model less frightening, but does convert our uncontrained optimization problem to an constrained one which raises special difficulties of its own.

The \emph{Nelder-Mead} direct search method cannot be used with explicity constrained problems. However, there are various implicit approaches to (approximately) solving general constrained problems using uncontrained algorithems. Generally, this is achieved by domain transformations or the use of penalty functions.  By the addition of a penalty function which depends in some way on the values of the constraints to the objective function, we minimize a pseudo-objective function where the infeasibility of the constraints is minimized simultaneously to the objective function.

There are various penalty function schemes. We use an Exterior Penalty Function as a simple way of converting converting the constrained problem into an unconstrained one. These are are especially useful in cases where the constraints are not ``hard'' in the sense that they need to be satisfied precisely. General penalty functions, which are sequential unconstrained minimization techniques, reformulate the general constrained problem as the pseudo-objective function given by

\[ \phi(\mathbf{x}, r_p ) = F(\mathbf{x}) + r_p P(\mathbf{x}) \]
where $P \left( \mathbf{x} \right)$ the penalty function, is given by
\begin{equation} \label{exterior}
 P( \mathbf{x} ) = \sum_{j = 1}^m \left\lbrace \mbox{max} \left[ 0, g_j(\mathbf{x} ) \right] \right\rbrace^2 + 
\sum_{k = 1}^l \left[ h_k( \mathbf{x}) \right]^2 .
\end{equation}
We see from Equation \ref{exterior} that there is no penalty if the constraints $g_j(\mathbf{x})$, and $h_k(\mathbf{x})$ are satisfied.

The Exterior Penalty Function specifically (and all Penalty Function approaches in general) do have several drawbacks. Namely these include the possibility of the objective function being undefined outside of the set of feasible solutions. Additionaly, by naively ``encouraging'' feasibility of the solution using large values of the penalty parameter, $r_p$, we will tend to ill-condition the unconstrained formulation of the problem.
\hl{[notes on choice of optimizer parameters, initial guesses, convergence, error estimates]}. Using penalty function methods tend to exascerbate the sensitivity of \emph{Nelder-Mead} solutions to the choice of intial guess vector \hl{[ref]}.

\subsection*{Smoothing}
In trying to recover the kinematic variables from the droplet trajectories we encounter a difficulty in the noise of the position data:

Error sources include misalignment of the camera, perspective due to objects (subject or reference scale) being out of the photographic plane, precision limits in digitization. Some of these errors are systematic in origin and introduce consistent biases into the data (e.g. coherent spectral sources, rather than truly stochastic noise). These systematic sources of error include inaccurate scales among others. Data smoothing tends not to help with the systematic errors in that they are usually of lower frequency than the signal (and here we are trying specifically to filter high frequency noise). Random errors, by contrast, are assumed to have a Gaussian distribution (by the central limit theorem), and are independent of the signal (which inherently results from a deterministic process).

In lieu of global polynomial fits we can attempt at finite differencing the data after the application of smoothing filters. Some of these approaches are global and/or recursive whereas other approaches are applied locally. Each approach has various natural advantages and disadvantages. A number of approaches were implimented in \emph{Python} or imported from the scientific computing package \emph{SciPy}[ref] and compared for a test set of trajectory data; these methods include convolution with the derivative of a Gaussian kernel, Wiener filtering, smoothing splines, Butterworth low-pass filtering, total-variance regularization, and Savitsky-Golay filtering. Qualitatively comparing these smoothing methods we find that we loose too many data points in the smoothing process, the variance remains large (especially in higher derivatives), large amplitudes are overly smoothed by repeated filtering passes, or there are significant end effects for most of these methods. A comparison of these smoothing approaches on a representative trajectory data set are shown in Figure \ref{fig:filters}. The power spectra for the same data are compared for these methods in Figure \ref{fig:power_spectra}.

\begin{figure}
%  \centerline{\includegraphics[height=7cm,width=13cm]{modes.eps}}
  \centerline{\includegraphics[height=7cm,width=7cm]{../figures/placeholder.png}}
  \caption{Filtered or fitted droplet trajectories compared to raw data.}
\label{fig:filters}
\end{figure}

\begin{figure}
%  \centerline{\includegraphics[height=7cm,width=13cm]{modes.eps}}
  \centerline{\includegraphics[height=7cm,width=7cm]{../figures/placeholder.png}}
  \caption{Power spectra of the filter methods compared.}
\label{fig:power_spectra}
\end{figure}

Savitsky-Golay filtering seems to produce the smoothest derivatives without overfitting of otherwise misrepresenting the underlying signal.

\subsection*{Numerical Solution to the Equation of Motion}
The equation of motion behaves stiffly due to the large disparity in Coulombic, image charge, and dielectrophoretic lenghtscales. We integrate it numerically using the \verb|odeint| \emph{Scipy} module. This is a shake-and-bake Python wrapper for the vernerable 1982 \emph{netlib ODEPACK} library double-precision \verb|lsoda| (Livermore Solver for Ordinary Differential equations with Automatic method switching for stiff and nonstiff problems) integrator \hl{[ref]}. The function switches between Adams (nonstiff) and Backwards Differentiation Formulas (BDF, stiff) according to the dyanmic value of a set of stiffness eigenvalues.

\end{document}

### 2018-01-06 doc/manuscript/electrets.tex
added some figures

--- 2017-06-12 ef_notes.tex
@@
-\documentclass[a4paper, 12pt]{article}
-\usepackage{changepage}
+\documentclass[10pt,a4paper]{article}
+\usepackage[utf8]{inputenc}
+\usepackage[english]{babel}
+\usepackage{amsmath}
+\usepackage{amsfonts}
+\usepackage{amssymb}
+\usepackage{graphicx}
 \usepackage{color,soul}
 \usepackage{listings}
-\lstset{
-basicstyle=\small\ttfamily,
-columns=flexible,
-breaklines=true
-}
-\title{\textsf{\textbf{Droplet Electro-Bouncing in $\mu$-Gravity}}}
-\vspace{-25mm}
-\author{Erin S. Schmidt, Mark M. Weislogel}
-\date{}
-
-\usepackage{abstract}
-\renewcommand{\abstractnamefont}{\normalfont\bfseries}
-\renewcommand{\abstracttextfont}{\normalfont\small\itshape}
-
+\author{Erin Schmidt}
 \begin{document}
-\maketitle
-
-\begin{abstract}
-\noindent
-Notes on electric fields `n stuff.
-\end{abstract}
-
-\section{Introduction}
-\subsection{Spontaneous Droplet Jump}
-When a nonwetting, gravity dominated sessile drop or puddle initially at rest in the Cassie-Baxter state on a surface undergoes a large step reduction in Bond number, $\mathbf{Bo} = \rho g V_d^{2/3}/\sigma$, where $\rho$ is the liquid density, $g$ is the acceleration of gravity, $V_d$ is the droplet volume, and $\sigma$ is the liquid surface tension, it will spontaneously jump away from the surface.
-This was first observed experimentally by Kirko \emph{et al.} in 1970 [ref] and later by Wollman \emph{et al.} in 2006 in a set of experiments conducted using a $\mu$-gravity drop tower \hl{[ref]}.
-The kinetic energy of the jump is supplied by the defect in free surface energy as the new minimum energy surface equilibrium has approximately constant curvature \hl{[ref]}.
-If the viscous energy losses by shear, and internal flows during roll up are neglected, as well as energy lost due to the hysteresis of the dynamic contact line, then the energy relation is given by
-\[KE = SE_2 -SE_1 = [(\sigma A)_{gl} + (\sigma A)_{sg}]_2 - [(\sigma A)_{ls} + (\sigma A)_{gl} + (\sigma A)_{sg}]_1. \]
-From this is derived a simple model for the droplet initial jump velocity, given by
-\[U_0 = \left(\frac{\sigma g}{\rho}\right)^{1/4}\left[1-\cos \theta + 2 \left(\frac{\pi H^3}{V_d} \right)^{1/2} - 6^{2/3} \left( \frac{\pi H^3}{V_d} \right)^{1/3} \right]^{1/2}, \]
-where \hl{[etc, etc, etc...]}.
-
-%\begin{figure}
-%  \centerline{\includegraphics[height=7cm,width=7cm]%{e88_1_thumb.jpg}}
-%  \caption{Droplet jump velocities, effect of hysteresis for small droplet size}
-%\label{fig:jump_velocities}
-%\end{figure}
-
-The droplet `rolls up' as it jumps away from the surface due to radial motion of capillary wave away from the contact line.
-The characteristic time scale of the rolling up scales as $t_j \sim R_p/U ~(\rho H R^2_p/\sigma)^{1/2}$ [ref], which resembles the contact time, $\tau \approx 2.6(\rho R^3_d/\sigma)^{1/2}$ reported by Richard \emph{et al.} in 2002 for the related problem of droplets impacting hydrophobic surfaces in 1-g \hl{[ref]}.
-For droplets with radial symmetry and sufficiently high initial $\mathbf{Bo}$ these waves coalesce as a shock leading to geyersing and creation of satellite drops by the Rayleigh-Plateau breakup of the geyser.
-In the case of smaller jumping droplets, the capillary waves do not lead to geyersing, and are viscously damped to varying degrees during the brief freefall period of the drop tower.
-
-The spontaneous droplet jump phenomenon provides a useful window though which to study the dynamics of large-lengthscale capillary dominated droplets.
-The governing physics of such massive droplets (far beyond the 1-g sub-millimetric capillary lengthscale) utterly defy terrestrial expectations about the ways in which liquid droplets `should' behave, and also are of critical importance in a space exploration setting where the design of practical $\mu$-gravity  multiphase fluidic systems will no doubt be needed as humankind gradually extends her domain into our solar system.
-\section{Bouncing}
-For the sake of bevity we will henceforth use the slightly confusing term `drop' as shorthand to refer to a single $\mu$-gravity drop tower experiment.
-\section{Experimental Methods}
-Superhydrophobic substrates were placed on a drop tower rig platform.
-The rig is released by a solenoid chucked pin at the same moment the exterior drag shield is allowed to fall.
-This decouples drag acceleration felt by the drag shield from the experiment which experiences approximately $1 \cdot 10^{-6}$g of high quality freefall for the 2.1s required for the rig/drag shield assembly to reach the bottom of drop tower 6 floors below.
-
-The superhydrophobic surface was treated with PTFE spray for the first experiment of the day, and approximately every $3^{\mbox{rd}}$ drop following.
-The general properties and details of the fabrication of these superhydrophobic surfaces are discussed in Section \ref{sec.suphydro}.
-Shortly before each drop the surfaces were briefly rinsed with distilled water, and then dried under a fume hood for about 10 minutes.
-The drop rigs were balanced to prevent unintentional torques from contaminating the kinematics data (as angular velocity of the camera-fixed inertial reference with respect to the droplets during freefall would appear as a linear acceleration of the droplet).
-Surface charge density was measured on the superhydrophobic surface using a \emph{Simco-Ion} FMX-004 electrostatic fieldmeter.
-This measurement was done with the superhydrophobic surfaces connected by a conductive ground plane by conductive tape, far away from the presence of other conductors.
-Some additional notes on idiosyncrasies of determining surface voltages (and thence surface charge densities) on insulative dielectric surfaces are provided in Appendix \ref{sec.surface_charge}.
-
-Droplets of distilled water, in a range of volumes ($0 \leq R_d \leq 1$mL), were very carefully deposited on the superhydrophobic surface in the final 1-5 minutes prior to the drop using an ungrounded glass syringe with $\pm 1\mu$L accuracy.
-Red tracer dye was added to improve trajectory digitization.
-During the drop, droplet trajectories were observed using a \emph{Panasonic} HC-WX970 Camera, shooting in high-speed mode at 120 fps and and 1/3000s shutter speed.
-In a few cases where higher frame rates were needed a \emph{Nikon} 1 J1 camera with a 30mm telephoto lens was used, shooting at 400 fps.
-The experimental test cell was illuminated with a 12V 6000K \emph{SEALIGHT} Chip-On-Board LED strip with a thin semi-opaque plastic film covering to make the light diffuse.
-The effect of static charges on spontaneously jumped droplet trajectories was studied in terms of the parameters droplet volume $V_d$, surface charge density $\sigma$, and a dependent variable, initial droplet jump velocity $U_0$.
-Since $q$ cannot be directly measured insitu during a drop (as high-input resistance electrometers, being notoriously fickle instruments, are not well suited to sudden 15-g decelerations), it was inferred from the statistical distribution determined in corollary experiments.
-The droplet charge determination is discussed in slightly more detail in Appendix \ref{sec.drop_charge}.
-
-\subsection{Superhydrophobic surfaces} \label{sec.suphydro}
-Wetting hysteresis.
-Methods of fabrication, comparison of wetting properties.
-Comparison of jump velocities between surfaces.
-Methods for determination of properties, roll-off angle, contact angle using \emph{SE-FIT}.
-Cassie-wenzel transition.
-Damping.
-Droplets are dyed red to improve the quality of image thresholding when digitizing the droplet trajectories during data reduction.
-
-%\begin{figure}
-%  \centerline{\includegraphics[height=7cm,width=13cm]{modes.eps}}
- % \centerline{\includegraphics[height=7cm,width=7cm]{e88_1_thumb.jpg}}
-%  \caption{SEM images for sandpaper and laser etched acrylic surfaces}
-%\label{fig:SEM}
-%\end{figure}
-
-\subsection{Data Reduction}
-Digitization of droplet trajectories requires several steps of post-processing.
-Video is first decomposed into a sequence of still images.
-Trajectories are captured using the particle tracking module in \emph{Fiji}\hl{[ref]}, a derivative of the popular \emph{ImageJ}\hl{[ref]} package for scientific image analysis.
-The series of still images is cropped, and the background (that is, the low-entropy pixels) of the series are removed using a builtin ``rolling ball'' algorithm.
-Each still is then split into its constituent RGB maps.
-In this case the green channel images contained the most information, so these were then globally thresholded using the Triangle algorithm to recover a map of the pixels corresponding to the droplet's approximate position in the original still.
-Finally ellipses are fitted to the pixel map stepping through the time series to determine the positions of the centroid, and the semi-major and minor axes of the droplets during the drop.
-The results of the particle capture in \emph{Fiji} are shown in Figure \ref{fig:fiji}.
-Droplet positional data was smoothed ex post facto using a Savitsky-Golay filter.
-Additional details regarding the data smoothing methodology are presented in Appendix \ref{sec.smoothing}.
-
-\section{EHD Forces}
-As previously speculated the the force acting on the droplets as a surrogate for gravity are likely electrohydrodynamical in origin.
-In the hopes of unraveling the underlying mechanism for the electro-bouncing we turn to the electrodynamical approximation of fluids under the influence of electric fields.
-To that effect, what follows is a condensed overview of mathematical description of basic electrohydrodynamic flows.
-We first assume a DC electric field, such that $Re \langle \epsilon \rangle \approx  \mbox{constant}$, where $\epsilon$ is the dielectric permittivity of the respective media.
-We also assume that currents are small such that the effects of magnetic fields can be neglected.
-For the validity of this assumption to hold the characteristic time scale for electrical phenomena $\tau_e = \epsilon \epsilon_0/\sigma_e \ll 1$, where we note that $\tau$ is the ratio of absolute dielectric permittivity $\kappa = \epsilon \epsilon_0$, to conductivity $\sigma_e$, of the medium [ref].
-Given the respective conductivity, and permittivity of air ($\sigma_e = 2.5 \cdot 10^{-16}$ $\Omega^{-1} cm^{-1}$), we estimate $\tau_e \approx 400$s.
-This assumption also allows us to assume that the net charge present in the medium surrounding the droplets remains approximately constant during the typical time interval of a $\mu$-gravity experiment, and no transfers of charge occur after the droplet leaves the surface.
-\hl{[lol, check these numbers...]}
-
-\subsection{Maxwell Stress}
-If we suppose that electrical forces acting on free charges and dipoles in a fluid are transferred directly to the fluid itself, then this overall electrical body force will be the the divergence of the Maxwell stress tensor $\tau_m $, by
-
-\[ \mathbf{F}_e = \nabla \cdot \tau_m = \nabla \cdot \left( \epsilon \epsilon_0 \mathbf{E} \mathbf{E} - \frac{1}{2} \epsilon \epsilon_0 \mathbf{E} \cdot \mathbf{E} \delta \right) ,\]
-where $\mathbf{F}_e$ is the electric body force per unit volume, \hl{$\rho_f$ is the free charge density}, and $\delta$ is the delta function.
-The product of the electric field vectors is the dyadic product.
-
-The classical Korteweg-Helmholtz force density formulation of the Maxwell stress tensor is usually expressed as 
-\begin{equation}
-\mathbf{F}_e = \rho_f \mathbf{E} + \frac{1}{2} \left| \mathbf{E} \right|^2 \nabla \epsilon - \nabla \left( \frac{1}{2} \rho \left( \frac{\partial \epsilon}{\partial \rho} \right)_T \left| \mathbf{E} \right|^2 \right) ,
-\end{equation}
-and $\rho$ is the density of the dielectric fluid[ref].
-
-The first term in this expression, equivalently written as $q\mathbf{E}$, is the well known Coulombic force or electrophoretic force, which arises from the presence of free charge in an external electric field.
-The second term is the force arising from polarization stresses due to a nonuniform field acting across a gradient in permittivity.
-This force is widely termed the dielectrophoretic force (DEP).
-The third term describes forces due to electrostriction, however in our case $\left( \frac{\partial \epsilon}{\partial \rho} \right)_T = 0$ due to the  incompressibility of the fluid[ref].
-While it is a relatively rigorous approach, and a useful conceptual model, evaluating the force density in this fashion can be somewhat onerous.
-
-\subsection{Dielectrophoresis}
-An alternative approximation for the polarization stress is to idealize the droplet as a simple dipole using the effective dipole moment method first suggested by Pohl and Jones\hl{[ref][ref]}.
-This approach can be related back to the force density by means of a Taylor series expansion of $\mathbf{E}$ in the limit of a small gradient \hl{[ref]}.
-The DEP force is distinct from the Coulombic force in that net charge is not required, and that the force vector goes in the direction of steepest descent of the field, $\nabla \left| \mathbf{E} \right|^2$, rather than in the direction of $\mathbf{E}$.
-The DEP force is related to the dipole moment (induced or polarized) of polarizable media which has a tendency to align the dipole with the electric field.
-If there is a gradient in the field then for a finite separation of charge one end of the dipole will feel a stronger electric field than the other, resulting in a net force.
-Whether the force is positive or negative in the direction of the electric field gradient depends on the difference of dielectric permittivites between the fluids, rather than on the polarity of $\mathbf{E}$.
-It bears repeating that droplets will polarize in a uniform field, but since there is no gradient in the field the forces felt by the dipoles are symmetric and there is no net force.
-The dipole moment of a spherical dielectric particle immersed in a dielectric medium is given by
-\begin{equation} \label{dipole_m_1}
-\mu = V_d \mathbf{P} = \frac{4}{3} \pi R_d^3 \mathbf{P},
-\end{equation} 
-where $\mathbf{P} = \left(\kappa_1 - 1 \right) \epsilon_0 \mathbf{E}_{iz}$ is the polarization moment, and $R_d$ is the particle radius, \hl{($\kappa_1$ being the relative dielectric constant of the medium}, and $\mathbf{E}_{iz}$ is the $z$-coordinate component of the electric field internal to the sphere, assuming the external electric field to be oriented parallel to the $z$-axis).
-The excess polarization $\mathbf{P}_e$, in the sphere is given by
-\begin{equation} \label{polarization}
-\mathbf{P}_e = \left( \kappa_2 - \kappa_1 \right) \epsilon_0 \mathbf{E}_{iz} = \frac{3 \kappa_1}{\kappa_2 +2\kappa_1}\mathbf{E}_{iz},
-\end{equation}
-where $\kappa_2$ is the dielectric constant of the particle. Taking together equations \ref{dipole_m_1}, and \ref{polarization} we find that the effective dipole moment of the particle is given by 
-\begin{equation}\label{dipole_m_2}
-\mu = 4 \pi R_d^3 \left( \frac{\kappa_2 - \kappa_1}{\kappa_2 + 2 \kappa_1} \right) \kappa_1 \epsilon_0 \mathbf{E},
-\end{equation}
-and the force felt by the dipole is 
-\begin{eqnarray} \label{dep_force}
-\mathbf{F}_{dep} &=& \left( \mathbf{P}_e \cdot \nabla \right) \mathbf{E}\\
-&=& 2 \pi R_d^3 \kappa_1 \epsilon_0 \left( \frac{\kappa_2 - \kappa_1}{\kappa_2 + 2 \kappa_1} \right) \nabla E^2,
-\end{eqnarray}
-where it is a useful shorthand to refer to the permittivity ratio by $K = \frac{\kappa_2 - \kappa_1}{\kappa_2 + 2 \kappa_1}$, which is also known as the Clausius-Mossotti factor.
-In cases where $K < 0$, or $K>0$ the particle will be repelled or attracted to regions of strong field respectively.
-In our experiment, taking the relative dielectric constants to be $\kappa_1 \approx 1$ and $\kappa_2 \approx 80$, we have $K \approx 0.96$.
-One limitation of the effective dipole moment approximation of the DEP force is that it requires an assumption of small physical scale of the particle relative to the lengthscale of nonuniformity of the field, which in this case we take to be the length of the charged superhydrophobic surface ($L,H =25$mm $\gg a \approx 2.5$mm).
-Though the effective dipole moment is a successful model due in large part to its simplicity, it can be readily extended to include higher-order multipole effects, and non-spherical particles (oblate and prolate spheroids).
-An excellent summary of DEP theory in terms of the effective dipole moment is given in \hl{[ref]}.
-\hl{[Some notes on scaling ...]}
-
-\subsection{Forces due to Image Charges in the Dielectric}
-
-\section{The Electric Field}
-Being thus armed with the assumption of a purely electrostatic problem (the electric field is conservative, that is $\nabla \times \mathbf{E} = 0$, where $\mathbf{E}$ is the electric field) we can describe the electric field by the Laplace equation for the electric potential.
-In the case of the volume charge density of the bulk medium to being zero, the divergence of the electric field is zero and we have
-
-\begin{eqnarray}
-\mathbf{E} &=& -\nabla \varphi \\
-\nabla \cdot \mathbf{E} &=& 0\\
-\nabla \cdot \mathbf{E} &=& - \nabla \cdot \nabla \varphi = \nabla^2 \varphi = 0,
-\end{eqnarray}
-it being convenient to solve the field in terms to $\varphi$ due to the form of the \emph{boundary conditions} usually given by
-\begin{enumerate}
-\item For finite charge distributions, the potential $\varphi$ goes to zero at infinity, is constant throughout a conductors, and is continuous across physical boundaries.
-\item The normal component of the displacement vector $\mathbf{D}$, differs on two sides of a boundary by the free charge density $\rho_f$ residing on the boundary.
-\item The tangential component of the field intensity $\mathbf{E}$ is continuous across a boundary.
-\end{enumerate}
-
-\section{A Simple Dynamical Model}
-\subsection{Trajectory Equation}
-\subsection{Numerical Methods}
-\section{Comparisons}
-\section{Stability}
-\section{Future Directions}
-\section{Conclusions}
-\appendix
-\section{\\Data Smoothing} \label{sec.smoothing}
-In trying to recover the kinematic variables from the droplet trajectories we encounter a difficulty in the noise of the position data:
-
+\section{Electrets}
 \begin{itemize}
-\item Notes from Wood, ``Data smoothing and Differentiation procedures in Biomechanics''
-
-\item Signal-to-noise ratio is $\mathcal{O}(f)$ for $\frac{df}{dt}$ and $\mathcal{O}(f^2)$ for $\frac{d^2f}{ft^2}$. Refs 5, 14, 49, 95.
-
-\item Error sources include misalignment of the camera, perspective due to objects (subject or reference scale) being out of the photographic plane, precision limits in digitization.
-Some of these errors are systematic in origin and introduce consistent biases into the data (e.g.
-coherent spectral sources, rather than truly stochastic noise).
-These systematic sources of error include inaccurate scales among others.
-Data smoothing tends not to help with the systematic errors in that they are usually of lower frequency than the signal (and here we are trying specifically to filter high frequency noise).
-
-\item Random errors are assumed to have a Gaussian distribution (by the central limit theorem), and are independent of the signal (which inherently results from a deterministic process).
-
-\item Central differences are usually a better approximation of the instantaneous value of the true derivative of the signal, as compared to forward differences.
-The finite differences are mathematically equivalent to passing a quadratic interpolating polynomial through the three points of the central difference (assuming the window size of the central difference is $N=3$, larger windows are possible).
-To obtain an approximation for the $m^{th}$ derivative of $f(x)$ at least an $m^{th}$ order polynomial is required.
-
-\item One straightforward approach to getting the position derivatives is to fit a least squares polynomial to the global position data, and analytically differentiate.
-This is a simple to apply, and therefore quite popular approach.
-The order of the polynomial is picked from theory, by ANOVA, or comparison of the residuals to determine goodness of fit for $m+1$.
-It should be stress that there are significant drawbacks with this approach: firstly is that when derived values depend on both accuracy of segmented displacement-time data and body segmental parameters (segmental masses and center of mass locations), then the errors are confounded and it is difficult to evaluate the accuracy of the derivative.
-Secondly, statistics used to asses agreement between curves are either in-appropriate because they aim to represent fundamentally deterministic processes in probabilistic ways (as would be the case using a product-moment correlation), or there is no test of significance (as is the case with a mean-errors correlation).
-Finally High order effects are easily lost by a global polynomial fit for time series containing multiple length scales or frequencies, as is the case here [ref].
+\item The method for determination of the evolution of the surface charge density for low conductivity polymers is described in \hl{[Davies, 1967]}.
+Surface charge in injected into the surface of the dielectric mounted on top of an grounded electrode.
+The charge decay is measured with a calibrated probe at periodic intervals.
+\item Additive stacking of electrets has been used in electret based vibrational energy harvesters \hl{[Stacking Electrets for Electrostatic Vibration Energy Harvesters, Wada et al.
+2012]} and in water desalinization \hl{[ref Application of electret technology to low cost desalination, R.C.
+Amme, 2002]}
+\item There are several charge decay mechanisms: internal ones, such as Ohmic resistence, and external ones such as compensation by envonmental ionic species.
+The relative magnitudes of these charge transport mechanisms, and therfore the stability of the electret varies drastically depending on its initial surface potential, material properties, environment, and charging method.
+In the case of unshielded electrets compensation by atmospheric ions is significant \hl{[E.W.
+Anderson et al, 1973]}.
+Because envornmental convection will tend to  maintain a gradient of these ions, sealing an electret in a container from the atmosphere will effectively halt this decay mechanism.
+Atmospheric humidity and water droplet condensation also significantly increase charge decay (presumably by reducing the surface resistence) \hl{[Haenen, 1975]}.
+\item According to \hl{[Sessler 1987]} an electret is a dielectric material with ``quasi-permanent'' electric charge in the sense that the characteristic decay period of the electret is much greater than a given period of interest.
+\item Electret charge may be `true' charge in the form of surface or space charges, or polarization charges (such as bound charges).
+If the electret is not screened by a conductor then it produces an external electric field if the polarization and real charges do not uniformly compates each other throughout the volume of the electret.
+For this reason electrets are though of as electrostatic analouges to permanent magnets (and the name \emph{electret} itself is a portmantau to the effect conjured by Heaviside in 1892 \hl{[ref O.
+Heaviside, 1982]}).
+Typical commerical electrets are Teflon type polytetraflouroethylene (PTFE) polymer films on the order of 10-50 $\mu$m thick with the charge being primarily real surface charge.
+Electrets have a plethora of applications, but most germanely they have been used in Electro-Wetting On Dielectric (EWOD) devices for low-voltage manipulation of small droplets \hl{[Wu, 2010]}.
+\item Real charge electrets can be produced by contact electrification, injection or deposition) of charge carriers by discharge or electron beam, ionizing radiation, or by frictional triboelectrification.
+Dipolar electrets by contrast are produced by a combination of polarization at elevated temperatures in a strong external electric field, followed by an annealing process.
+\item Effective surface charge densities are limited to the material dielectric strengths due to internal dielectric breakdown phenomenon (this typically occurs before external breakdown or Paschen breakdown).
+\item We use an isothermal electret formation process using a variation of the widely applied corona-charging technique.
+The typical corona-charging technique uses strong inhomogenous DC electric fields to produce discharge in air at ambient conditions; the dielectric substrate is atop a grounded electrode, and there is a screening potential electrode intermediately positioned to control (the the surface potential of the dielectric will tend to saturate at this grid potential if the material is not space-charge current limited).
+The corona field is usually produced by pin-shaped electrode.
+In air the most common charge carriers thus produced are $\mbox{CO}_3^-$ ions.
+This approach is known to generally produce samples with fairly uniform surface charge densities.
+\item Some work \hl{[ref J.
+van Turnhout, 1975]} showed using a Thermally Stimulated Current (TCS) measurements that in 4.8 mm thick polymethyl methacrylate (PMMA) polarization of the dielectric is non-uniform, due to real space-charge mostly ($\sim$90\%) residing in a thin (0.1-0.2 mm) layer near the free-surface of the sample.
+\item \hl{Notes on our version of the corona-discharge process, figure, plot of charge decay}.
+\item We plainly see a cross-over effect in the decay of the surface potential in our electret samples, whereby the samples charged to higher initial surface potentials decayed faster and reached the lower overall final potentials.
+This is a well known effect in polyethylenes charged by corona \hl{[Ferreira et al.
+1992]}
 \end{itemize}
-
-In lieu of global polynomial fits we can attempt at finite differencing the data after the application of smoothing filters.
-Some of these approaches are global and/or recursive whereas other approaches are applied locally.
-Each approach has various natural advantages and disadvantages.
-A number of approaches were implimented in \emph{Python} or imported from the scientific computing package \emph{SciPy}[ref] and compared for a test set of trajectory data; these methods include convolution with the derivative of a Gaussian kernel, Wiener filtering, smoothing splines, Butterworth low-pass filtering, total-variance regularization, and Savitsky-Golay filtering.
-Qualitatively comparing these smoothing methods we find that we loose too many data points in the smoothing process, the variance remains large (especially in higher derivatives), large amplitudes are overly smoothed by repeated filtering passes, or there are significant end effects for most of these methods.
-A comparison of these smoothing approaches on a representative trajectory data set are shown in Figure \ref{fig:filters}.
-The power spectra for the same data are compared for these methods in Figure \ref{fig:power_spectra}.
-
-%\begin{figure}
-%  \centerline{\includegraphics[height=7cm,width=13cm]{modes.eps}}
- % \centerline{\includegraphics[height=7cm,width=7cm]{e88_1_thumb.jpg}}
-  %\caption{Filtered or fitted droplet trajectories compared to raw data.}
-%\label{fig:filters}
-%\end{figure}
-
-%\begin{figure}
-%  \centerline{\includegraphics[height=7cm,width=13cm]{modes.eps}}
- % \centerline{\includegraphics[height=7cm,width=7cm]{e88_1_thumb.jpg}}
-  %\caption{Power spectra of the filter methods compared.}
-%\label{fig:power_spectra}
-%\end{figure}
-
-Savitsky-Golay filtering seems to produce the smoothest derivatives without overfitting of otherwise misrepresenting the underlying signal. The Savitsky-Golay algorithm
-
-\section{\\Surface charge density}\label{sec.surface_charge}
-Since the laser-etched acrylic, and sandpaper superhydrophobic surfaces are both dielectric materials there are some additional considerations for determining the surface charge density.
+\section{Surface charge density}
+Since the laser-etched PMMA superhydrophobic surface is a dielectric material there are some additional considerations for determining the surface charge density.
 Firstly, for an insulated conductor $A$ with charge $q$, the charge distribution in equilibrium will be such that the field on the interior of the conductor is zero, with field lines being normal to the surface and the integral of the field strength $\mathbf{E}$ from any point $P$ in or on the conductor to a ground point $G$ is a constant given by
@@
 
-%\begin{figure}
-%  \centerline{\includegraphics[height=7cm,width=13cm]{modes.eps}}
- % \centerline{\includegraphics[height=7cm,width=7cm]{e88_1_thumb.jpg}}
-  %\caption{Measured surface voltage versus position.}
-%\label{fig:surface_voltage}
-%\end{figure}
-
 A further consideration is the possibility of the change in total charge during a typical experimental timescale.
@@
 For an example case of a surface with an initial surface charge density $\sigma = 2.4 \cdot (10^{-6})$ $C/m^2$, relative permittivity $\epsilon = 3.5$ and bulk resistivity $\rho = 1.6 \cdot (10^{16})$ $\Omega/cm$ such as with the case of 1/4'' continuous cast acrylic sheet, then the time constant $\tau = \epsilon \rho$ is approximately 5000 s, which is a great deal longer than the typical time period for of a drop tower experiment.
-
-\section{\\Droplet Charge} \label{sec.drop_charge}
-\subsection*{Parallel Plate Method}
-Since, by the earlier scaling, we presuppose the source of the droplet bouncing behavior to be primarily Coulombic in origin (as opposed to dielectrophoretic), the droplet must have some net charge in addition to the charge induced by the electric field.
-To measure this charge concurrent methodologies were used.
-The first method of determining the droplet net charge is observation of the deflection of the droplets in the region of a known uniform field in a fashion inspired by Millikan's famous experiment to determine the fundamental charge of the electron [ref].
-
-Droplets were jumped in freefall from a sandpaper superhydrophobic surface placed between the plates of a parallel plate capacitor of known uniform electric field.
-The surface was first deionized using a balanced \emph{Ptec} IN5120 DC air-ionizer to remove the effect of surface charge of the superhydrophobic surface from perturbing the otherwise uniform field set up between the parallel plates.
-A schematic of the parallel plate drop apparatus is shown in Figure \ref{fig:millikan}.
-Since the droplet initial velocity $U_0$ is parallel to the electric field, the droplets are inertial in the direction of the electric force, and neglecting the effect of image charges mirrored across the conductors, we can determine the magnitude of the droplet charge by a balance of Coulombic force and inertia given by the equation of motion
-
-\[ \frac{d^2y}{dt^2} = q\mathbf{E}. \]
-
-Since the drag is negligible in the inertial limit we can find the charge $q$ by fitting a second-order least squares polynomial to the measured droplet positions, equating the $t^2$ term to the constant acceleration, and dividing by the known, constant magnitude of the electric field.
-From a survey of literature we suppose the droplet charge, if they are indeed charged by contact with PTFE, to be some function of the droplet volume and the residence time on the superhydrophobic surface.
-However, sweeping though droplet volumes over a series of drop tower experiments we find little correlation between droplet volume  and net droplet charge.
-This is shown in figure \ref{fig:drop_charge}.
-
-A 200-880 VAC source with a full wave bridge rectifier circuit was prototyped on perf-board for initial experiments to measure droplet charge.
-The circuit was analyzed on an laboratory oscilloscope to verify that the AC component of the signal was appropriately small (13 mV at 35 kHz).
-Current was determined to be a relatively low 80 $\mu$A.
-The high-voltage source terminals were led to two parallel polished 150x150 mm aluminum plate electrodes.
-The electrodes were mounted on an insulated 80/20 extruded aluminum rail for ease of adjustment.
-All droplet charge experiments were conducted with an electrode spacing of 28.30 mm.
-With this spacing the calibrated electric field between the plates was $\mathbf{E} \approx 35$kV/m.
-The electrodes were electrically isolated from the drop rig by two alternating layers of 4 mm thick laser cut acrylic sheet and Kapton tape.
-Potential across the plates was measured periodically with a load-impedance corrected multimeter to account for battery depletion.
-The typical capacitor rise time of the plates was measured to be 1.4 s, thus to make the most economical use of the brief window a micro-gravity a weighted switch was set by hand prior to the drop to close the high-voltage circuit, but which passively safed the system at the resumption of 1-g conditions in the tower.
-The drop apparatus is shown in Fig.
-
-%\begin{figure}
-%  \centerline{\includegraphics[height=7cm,width=13cm]{modes.eps}}
- % \centerline{\includegraphics[height=7cm,width=7cm]{e88_1_thumb.jpg}}
-  %\caption{Parallel plate experimental apparatus.}
-%\label{fig:millikan}
-%\end{figure}
-
-%\begin{figure}
-%  \centerline{\includegraphics[height=7cm,width=13cm]{modes.eps}}
- % \centerline{\includegraphics[height=7cm,width=7cm]{e88_1_thumb.jpg}}
-  %\caption{Parallel plates: Droplet net charge vs volume.}
-%\label{fig:drop_charge}
-%\end{figure}
-
-A brief screening experiment was conducted which alternated the polarity of the field by switching the positive and negative terminal leads between plates.
-Qualitative observations of droplet electrode preference seem to indicate that the assumption of small polarization stress was well founded.
-Following this a orthogonal array $3^2$ factorial design experiment with two replicates was conducted to test the effect of varying droplet volume and surface stay time on net charge at the time of jumping.
-It was hypothesized in accordance with previous studies \cite{Choi:2013dg}, that net charge would increase for levels of both factors.
-The results of the factorial experiment are presented in Fig.
-\ref{fig:chart1}.
-ANOVA analysis in \emph{R} of the linear multiple regression model for the data set indicates that neither droplet volume ($p=0.105$), nor surface stay time ($p=0.358$) is significant at the 95\% confidence level.
-The overall model F-statistics (2.177 in 2 and 13 degrees of freedom), and coefficients of determination ($r^2 = 0.2509$) indicate that the linear model neither fits the data particularly well, nor does it offer an improvement over the mean model.
-The mean charge was determined to be positive $2.3 \cdot 10^{-11}$ C, with a standard deviation of $1.8 \cdot 10^{-11}$ C.
-
-The failure of the model to describe the data raises interesting questions about the validity of our initial assumptions.
-Typical Reynolds numbers ($R_e=280$ average) indicate the general validity of the assumed quadratic drag model.
-The drag scale quantity given by Eqn.
-\ref{eqn:drag} was much less than 1 for all test runs, with mean value of $1.0\cdot 10^{-2}$ and a standard deviation of $2.0\cdot 10^{-3}$, which adds credence to a force balance of pure inertia and electrostatic force.
-
-One obvious issue, in retrospect, is that while we know the characteristic charging time for the droplets to be some function of droplet volume, \hl{[it has been shown to have a time constant dramatically smaller than that of a typical experimental timescale]} so we might have looked only for the charge as a function of volume, both on physical grounds and due to the conflation of the variables.
-
-Also of concern is that droplets in three of eighteen runs exhibited accelerations opposite to the expected direction.
-There is no pattern to the distribution of anomalous droplet accelerations, as they all occurred at unique level combinations.
-There are only four obvious ways of explaining this anomaly.
-The first is that the electric field is in fact non-uniform and polarization stress is non-negligible in this geometry.
-This option seems unlikely owing to the fundamental design of the experimental apparatus; \hl{[see figure from Agros2D FEM solution]}.
-A second possibility is that the few contrarian droplets actually accumulated net negative charge, instead of the net positive charge to be expected on the basis of evidence from some of the aforementioned studies.
-This is not impossible, and would also go some length to explain the variance in the measured charge generally.
-A third possibility is that another force neglected in this analysis, with some component in the direction opposite of the electric field, has an $\sim \mathcal{O}(1)$ magnitude.
-In principle this could for instance include the image charges which will subject the droplets to a force $\mathbf{F} = q^2/4 \pi \epsilon_0 d$ when ``close'' to one of the conductive plates (that is, when the plate can be treated as an infinite grounded conductor).
-However, this formulation of the image charge effect clearly does not describe the force close to the centerline where the Green's function needs to add additional sets of images to satisfy the boundary conditions of $\nabla^2 \varphi = 0$ in this geometry.
-To the knowledge of the author there is not a convergent series solution in the parallel plates geometry as yet.
-
-The droplet positive net charge developed by contact with a PTFE surface corresponds to findings elsewhere in literature \cite{Choi:2013dg} \cite{Miljkovic:2013dg} \cite{Moreno-Villa:1998dg}.
-The smallest droplet size treated in the present work is several times larger than the largest in any of comparable study.
-The most relevant comparison found droplet static charge of 2.5e-10 C for 10 $\mu$L droplets charged by pipetting from a PTFE tipped needle \cite{Choi:2013dg}.
-The present results mean charge level of 2.3e-11 C is, within error, roughly six times smaller than the cited study.
-
-\subsection*{Direct Measurement}
-A second approach to determining the net droplet charge is by direct measurement in a shielded Faraday cup using an extremely high input resistance electrometer, specifically a \emph{Keithly} 616 digital electrometer.
-\hl{[note on operational philosophy, data collection].
-Correlation of net charge to droplet volume is shown again for in figure} \ref{fig:electrometer}.
-
-%\begin{figure}
-%  \centerline{\includegraphics[height=7cm,width=13cm]{modes.eps}}
-%  \centerline{\includegraphics[height=7cm,width=7cm]{e88_1_thumb.jpg}}
- % \caption{Electrometer: charge vs. volume.}
-%\label{fig:electrometer}
-%\end{figure}
-
-[Discussion on discrepancy between the two approaches.]
-
+\hl{Add specific notes on charge measurement procedure}.
 \end{document}

### 2018-01-06 doc/manuscript/parameter_estimation.tex
added some figures

--- 2018-01-04 doc/manuscript/parameter_esimation.tex
@@
 \usepackage[utf8]{inputenc}
+%\usepackage{fontspec} % This line only for XeLaTeX and LuaLaTeX
+\usepackage{pgfplots}
+\usepackage{pgf}
 \usepackage[english]{babel}
@@
 \usepackage{listings}
+\usepackage{setspace}
 \author{Erin Schmidt}
+
+\newlength\figureheight
+\newlength\figurewidth
+\setlength\figureheight{7cm}
+\setlength\figurewidth{10cm}
+
 \begin{document}
+\onehalfspacing
 \section{Parameter Estimation}
@@
 
-In lieu of global polynomial fits we can attempt at finite differencing the data after the application of smoothing filters.
-Some of these approaches are global and/or recursive whereas other approaches are applied locally.
-Each approach has various natural advantages and disadvantages.
-A number of approaches were implimented in \emph{Python} or imported from the scientific computing package \emph{SciPy}[ref] and compared for a test set of trajectory data; these methods include convolution with the derivative of a Gaussian kernel, Wiener filtering, smoothing splines, Butterworth low-pass filtering, total-variance regularization, and Savitsky-Golay filtering.
-Qualitatively comparing these smoothing methods we find that we loose too many data points in the smoothing process, the variance remains large (especially in higher derivatives), large amplitudes are overly smoothed by repeated filtering passes, or there are significant end effects for most of these methods.
+We experimented with a variety of filters implimented in the \verb|scipy.signal| \emph{SciPy}[ref] module using a represenative set of trajectory data; these methods include 1D Gaussian convolution, Wiener, Butterworth, and Savitsky-Golay filters.
+Qualitatively comparing these smoothing methods (by handtuning filter orders and window sizes) we find that we loose too many data points in the smoothing process, large amplitudes are overly smoothed by repeated filtering passes, or there are significant end effects for most of these methods.
 A comparison of these smoothing approaches on a representative trajectory data set are shown in Figure \ref{fig:filters}.
@@
 
+%\begin{figure}[htb]
+%\centering
+%\resizebox{10cm}{!}{\input{../figures/y_filtered.tex}}
+%\caption{Power spectra of the filter methods compared.}\label{fig:myfigure}
+%\end{figure}
+
+%\begin{figure}[htb]
+%\centering
+%\resizebox{10cm}{!}{\input{../figures/dy_filtered.tex}}
+%\caption{Power spectra of the filter methods compared.}\label{fig:myfigure}
+%\end{figure}
+
+%\begin{figure}[htb]
+%\centering
+%\resizebox{10cm}{!}{\input{../figures/power_spectra.tex}}
+%\caption{Power spectra of the filter methods compared.}\label{fig:myfigure}
+%\end{figure}
+
 \begin{figure}
-%  \centerline{\includegraphics[height=7cm,width=13cm]{modes.eps}}
-  \centerline{\includegraphics[height=7cm,width=7cm]{../figures/placeholder.png}}
-  \caption{Filtered or fitted droplet trajectories compared to raw data.}
-\label{fig:filters}
+    \centering
+    \input{../figures/power_spectra.pgf}
+    \caption{A simple EMA plot.\label{fig:ema1}}
 \end{figure}
@@
 \begin{figure}
-%  \centerline{\includegraphics[height=7cm,width=13cm]{modes.eps}}
-  \centerline{\includegraphics[height=7cm,width=7cm]{../figures/placeholder.png}}
-  \caption{Power spectra of the filter methods compared.}
-\label{fig:power_spectra}
+    \centering
+    \input{../figures/y_filtered.pgf}
+       \caption{A simple EMA plot.\label{fig:ema2}}
 \end{figure}
 
-Savitsky-Golay filtering seems to produce the smoothest derivatives without overfitting of otherwise misrepresenting the underlying signal.
+\begin{figure}
+    \centering
+    \input{../figures/dy_filtered.pgf}
+       \caption{A simple EMA plot.\label{fig:ema3}}
+\end{figure}
+
+Qualitively speaking, the 4th-order Savitsky-Golay, and Butterworth filters both produce the smooth derivatives we desire for for the optimization algorithem; but the small window-size needed for Butterworth filter tends to also prduce a noticible end effect.
+The Savitsky-Golay filter essentially uses a moving-window based on local least-squares polynomial approximations.
+It was shown that fitting a polynomial to a set of input samples and then evaluating the resulting polynomial at a single point within the approximation interval is equivalent to discrete convolution with a fixed impulse response \hl{[Savitsky, 1964]}.
+One property of this kind of low-pass filter is their tendency to respect waveform aplitudes, and so they are attractive in applications with having noisey signals with shaply pointed waveforms such as ultrsound or synthetic aperature radar \hl{[Schafer, 2011]}, however these filters tend to suffer from end-effects.
+Because Savitsky-Golay is a Finite Impulse Response (FIR) filter it requires datapoints to be equally spaced; to accomedate this we interpolate points between the small gaps which sometime occur in the tracking results from image analysis \hl{[ref]}.
+\hl{[Notes on window length, polynomial order]}.
 

### 2018-01-07 doc/manuscript/ef_notes.tex
changes to figures
added some figures
added convergence plots, condition estimates, charge decay, and additional notes

@@
 \usepackage{verbatim}
+\usepackage{pgf}
 \lstset{
@@
 
+\usepackage{setspace}
 \begin{document}
@@
 \end{abstract}
-
+\doublespacing
 \section{Introduction}
@@
 \end{equation}
-Using the identity for the position vector $\nabla
+Using the identity for the position vector $\nabla$
+
+\begin{figure}[htb]
+    \centering
+    \input{../figures/E0.pgf}
+    \caption{A simple EMA plot.\label{fig:E0}}
+\end{figure}
 
@@
 \subsection{Numerical Methods}
+
 \section{Comparisons}
@@
 \appendix
-\section{\\Data Smoothing} \label{sec.smoothing}
-In trying to recover the kinematic variables from the droplet trajectories we encounter a difficulty in the noise of the position data:
-
-\begin{itemize}
-\item Notes from Wood, ``Data smoothing and Differentiation procedures in Biomechanics''
-
-\item Signal-to-noise ratio is $\mathcal{O}(f)$ for $\frac{df}{dt}$ and $\mathcal{O}(f^2)$ for $\frac{d^2f}{ft^2}$. Refs 5, 14, 49, 95.
-
-\item Error sources include misalignment of the camera, perspective due to objects (subject or reference scale) being out of the photographic plane, precision limits in digitization.
-Some of these errors are systematic in origin and introduce consistent biases into the data (e.g.
-coherent spectral sources, rather than truly stochastic noise).
-These systematic sources of error include inaccurate scales among others.
-Data smoothing tends not to help with the systematic errors in that they are usually of lower frequency than the signal (and here we are trying specifically to filter high frequency noise).
-
-\item Random errors are assumed to have a Gaussian distribution (by the central limit theorem), and are independent of the signal (which inherently results from a deterministic process).
-
-\item Central differences are usually a better approximation of the instantaneous value of the true derivative of the signal, as compared to forward differences.
-The finite differences are mathematically equivalent to passing a quadratic interpolating polynomial through the three points of the central difference (assuming the window size of the central difference is $N=3$, larger windows are possible).
-To obtain an approximation for the $m^{th}$ derivative of $f(x)$ at least an $m^{th}$ order polynomial is required.
-
-\item One straightforward approach to getting the position derivatives is to fit a least squares polynomial to the global position data, and analytically differentiate.
-This is a simple to apply, and therefore quite popular approach.
-The order of the polynomial is picked from theory, by ANOVA, or comparison of the residuals to determine goodness of fit for $m+1$.
-It should be stress that there are significant drawbacks with this approach: firstly is that when derived values depend on both accuracy of segmented displacement-time data and body segmental parameters (segmental masses and center of mass locations), then the errors are confounded and it is difficult to evaluate the accuracy of the derivative.
-Secondly, statistics used to asses agreement between curves are either in-appropriate because they aim to represent fundamentally deterministic processes in probabilistic ways (as would be the case using a product-moment correlation), or there is no test of significance (as is the case with a mean-errors correlation).
-Finally High order effects are easily lost by a global polynomial fit for time series containing multiple length scales or frequencies, as is the case here [ref].
-\end{itemize}
-
-In lieu of global polynomial fits we can attempt at finite differencing the data after the application of smoothing filters.
-Some of these approaches are global and/or recursive whereas other approaches are applied locally.
-Each approach has various natural advantages and disadvantages.
-A number of approaches were implimented in \emph{Python} or imported from the scientific computing package \emph{SciPy}[ref] and compared for a test set of trajectory data; these methods include convolution with the derivative of a Gaussian kernel, Wiener filtering, smoothing splines, Butterworth low-pass filtering, total-variance regularization, and Savitsky-Golay filtering.
-Qualitatively comparing these smoothing methods we find that we loose too many data points in the smoothing process, the variance remains large (especially in higher derivatives), large amplitudes are overly smoothed by repeated filtering passes, or there are significant end effects for most of these methods.
-A comparison of these smoothing approaches on a representative trajectory data set are shown in Figure \ref{fig:filters}.
-The power spectra for the same data are compared for these methods in Figure \ref{fig:power_spectra}.
-
-%\begin{figure}
-%  \centerline{\includegraphics[height=7cm,width=13cm]{modes.eps}}
- % \centerline{\includegraphics[height=7cm,width=7cm]{e88_1_thumb.jpg}}
-  %\caption{Filtered or fitted droplet trajectories compared to raw data.}
-%\label{fig:filters}
-%\end{figure}
-
-%\begin{figure}
-%  \centerline{\includegraphics[height=7cm,width=13cm]{modes.eps}}
- % \centerline{\includegraphics[height=7cm,width=7cm]{e88_1_thumb.jpg}}
-  %\caption{Power spectra of the filter methods compared.}
-%\label{fig:power_spectra}
-%\end{figure}
-
-Savitsky-Golay filtering seems to produce the smoothest derivatives without overfitting of otherwise misrepresenting the underlying signal. The Savitsky-Golay algorithm
-
-\section{\\Surface charge density}\label{sec.surface_charge}
-Since the laser-etched acrylic, and sandpaper superhydrophobic surfaces are both dielectric materials there are some additional considerations for determining the surface charge density.
-Firstly, for an insulated conductor $A$ with charge $q$, the charge distribution in equilibrium will be such that the field on the interior of the conductor is zero, with field lines being normal to the surface and the integral of the field strength $\mathbf{E}$ from any point $P$ in or on the conductor to a ground point $G$ is a constant given by
-\[ V = \int^G_P \mathbf{E} \cdot da, \]
-where $V$ is the voltage or potential of the conductor (or alternatively, the surface voltage potential). The voltage $V$ and the charge $q$ are proportional and $q$ is usually given by
-\[q = CV, \]
-where $C$ is the capacitance of the insulated conductor and is determined by the conductor's size and shape, and its placement relative to the conductors and ground.
-However, the case of a charged insulator departs significantly from that of the insulated conductor.
-Here we have the possibility of the density and net polarity of the charge varying as a function of position about the surface.
-The field of the interior may not be zero, and the field lines are not necessarily normal to the the surface.
-The integral of the field strength from a point on or in the insulator to ground is usually different from point to point.
-In general the surface voltages will vary from point to point on an insulator (including point on the interior of the insulator.
-Therefore it is not possible to uniquely define the voltage of a charged insulator, except in certain contrived cases (notably the the potential of a uniformly charged sphere positioned infinitely far away from any conductors).
-It follows that there is no definition for the capacitance of an insulator as well.
-Though insulative sheets may store charge and discharge in the manner of capacitors, this discharge is never particularly complete.
-
-There are two cases where we can make meaningful quantitative measurements of state variables for charged insulators: we can measure the electric field arising from the charge, and possible the total charge for uniformly charged free insulative sheets, and uniformly charged insulative sheets backed by a grounded conductor.
-To do this we can use field meters and non-contacting voltmeters.
-If the field strength indicated on the meter is $\mathbf{E}$, the charge density $\sigma$ on the part of the insulator in the front should be $\sigma = \epsilon_0 \mathbf{E}$.
-If a non-contacting voltmeter is placed a at a distance $d$ from the sheet, then the surface voltage $V_s$ indicated on the meter is given by
-\[V_s = d \mathbf{E} = d \frac{\sigma}{\epsilon_0}. \]
-
-An ideal approach to determining surface charge on a dielectric surface is to screen perturbing effects of external electric fields.
-This is partly accomplished by grounding the fieldmeter, and by placing the dielectric sample on a grounded conductive plate backing.
-In this case the surface charge density is determined from
-
-\[ \sigma = \frac{V_s \epsilon}{l}, \]
-
-where $l$ and $\epsilon$ are the absolute permittivity and thickness of the dielectric surface respectively.
-The measured surface voltage is a function of position away from the charged dielectric.
-In most cases this function is relatively constant at a distance about 1-2 cm away from the surface (there is some measurement error in surface voltage due to small mispositioning of the electrostatic fieldmeter, say by $\pm$1 mm) and add it to the precision error of measurement in $V_s$.
-The measured surface voltage can also be compared to the analytically derived surface voltage determined from the analytical expression for the electric field from above, and to those determined from finite element solutions to poisson's equation on the domain in question.
-[Notes about \emph{Agros2D}] The surface voltage is shown schematically as a function of the measurement distance in Figure \ref{fig:surface_voltage} for a sample charge density $\sigma = $.
-
-%\begin{figure}
-%  \centerline{\includegraphics[height=7cm,width=13cm]{modes.eps}}
- % \centerline{\includegraphics[height=7cm,width=7cm]{e88_1_thumb.jpg}}
-  %\caption{Measured surface voltage versus position.}
-%\label{fig:surface_voltage}
-%\end{figure}
-
-A further consideration is the possibility of the change in total charge during a typical experimental timescale.
-If we consider the drop rig to be a ground (which seems reasonable given that the rig is isolated from true ground, but is at some reference voltage with respect to the surface charges on the dielectric, it also has an abundance of free charge carriers, that it, it is conductive), then there will be both bulk and surface decay of the charge on the dielectric.
-The evolution of the charge can be approximated by
-\[ \sigma = \sigma_0 e^{\frac{-t}{\epsilon \rho}}, \]
-where $\sigma_0$ is the initial surface charge density, and $\rho$ is the bulk resistivity (which can also be reframed in terms of conductivity by $\rho = 1/\gamma$, where $\gamma$ is the conductivity).
-For an example case of a surface with an initial surface charge density $\sigma = 2.4 \cdot (10^{-6})$ $C/m^2$, relative permittivity $\epsilon = 3.5$ and bulk resistivity $\rho = 1.6 \cdot (10^{16})$ $\Omega/cm$ such as with the case of 1/4'' continuous cast acrylic sheet, then the time constant $\tau = \epsilon \rho$ is approximately 5000 s, which is a great deal longer than the typical time period for of a drop tower experiment.
 

### 2018-01-07 doc/manuscript/parameter_estimation.tex
added convergence plots, condition estimates, charge decay, and additional notes

@@
 \begin{document}
-\onehalfspacing
+\doublespacing
 \section{Parameter Estimation}
@@
 \end{enumerate}
-\subsection*{Inverse Problems}
+\subsection{Inverse Problems}
 \begin{itemize}
@@
 
-\subsection*{Optimization}
+\begin{figure}[htb]
+    \centering
+    \resizebox{14cm}{!}{\input{../figures/jump_matrix.pgf}}
+    \caption{A simple EMA plot.\label{fig:trajectories}}
+\end{figure}
+
+\begin{figure}[htb]
+    \centering
+    \resizebox{14cm}{!}{\input{../figures/inverse_problem.pgf}}
+    \caption{A simple EMA plot.\label{fig:inverse_problem}}
+\end{figure}
+
+\begin{figure}[htb]
+    \centering
+    \resizebox{14cm}{!}{\input{../figures/convergence.pgf}}
+    \caption{A simple EMA plot.\label{fig:convergence}}
+\end{figure}
+
+\subsection{Optimization}
 Most generally the we state the constrained problem as 
@@
 
-\hl{[notes on gradient free optimization, Nelder-mead, sci-py ref]}
-\begin{itemize}
-\item We use the \emph{Nelder-Mead} algorithem to minimize the $\chi^2$ goodness-of-fit.
-\emph{Nelder-Mead}, sometimes called simplex-search or downhill-simplex, is a derivative-free direct search, LP method.
-\item \emph{Nelder-Mead} is well-established.
-\item A hueristic search method, with no guarantee of optimal solutions.
-\item Is based on the concept of a simplex, which is a special polytrop of $N + 1$ vertices in $N$ diemsions.
-\item Is derivative-free: does not use numerical or analytic gradients.
-\item Is implimented in the \emph{Scipy} package for Scientific computing in Python.
-\item \emph{Nelder-Mead} is very fast, but generally suitable for low-dimensional problems. Additionally convergence of the alogrithem is highly sensitive to the initial guess design vector $x_0$.
-\end{itemize}
+Mathematical optimization is the problem of finding minima of a function $f$.
+In this context the function in question is referred to as a cost, or objective function.
+The field of mathematical optimization is as old as calculus itself, and the number of particular optimization techniques is correspondingly myriad; particular techniques lend themselves well to particular types of optimization problems.
+The minima of the objective function $f$ is sought on a domain $A$ specified by the constraints of the problem, this is usually called the feasible region.
+Minima of objective function $f: A \rightarrow \mathbb{R}^n$ on $A$ are usually called feasible solutions.
+If the function $f$ is convex the feasible solution is the global minimum, otherwise additional local minima exist.
+The scale of the optimization problem is set ultimately by dimensionality of the objective function.
+Functions may not always be smooth in the sense of having continuous derivatives, this is problematic in that optimization methods fundimentally rely on gradients of the objective function.
+Problems with anisotropic objective functions in the sense that the gradient vector tends to differ significantly from the Newton direction ($-\mathbf{H}^{-1} f' ( \mathbf{x} )^T$, where $\mathbf{H}$ is the Hessian matrix) are considered ill-conditoned.
+In ill-conditioned problems gradient based deterministic search may be extremely slow.
+Numerical optimization may deal with black box functions (where we do not have an explicit mathematical expression of the function we are optimizing).
+Black box problems are challenging because we do not have access to analytic gradients of the objective function, and approximating them by finite-differences is slow and noisey.
+In general, noisey, black box, non-linear, non-quadratic, non-convex, constrained, ill-conditioned, high-dimensional objective functions are problematic to optimize.
+This is the practical essense of the parameter estimation problem.
+In particular there are few methods that work well with noisey, ill-conditioned problems.
+
+We use a gradient-free, direct-search approach: Nelder-Mead \hl{[Nelder, 1965]} implimented in \verb|scipy.optimize| \hl{[Jones et al.
+2001 --]}.
+Nelder-Mead is robust to noise (relatively speaking), and is relatively thrifty with our extremely expensive function-calls.
+\emph{Nelder-Mead}, sometimes called simplex-search or downhill-simplex, is a hueristic search method, with no guarantee of optimal solutions, but is well-established and widely used despite that.
+\emph{Nelder-Mead} is based on the concept of a $N$-simplex, which generalizes a triangle into higher dimensions as a polytrope of $N + 1$ vertices in $N$ dimensions.
+It uses only-function calls and expands or contracts the simplex according to the function values at its vertices in a way visually reminiscent (in $\mathbb{R}^2$) of the oscillations of the jumping droplets themselves (in fact \emph{Nelder-Mead} is sometimes also called the ``ameoba method'').
+
+Preconditioning, scaling the constraints in the penalty function.
 
@@
 
-\subsection*{Smoothing}
+\subsection{Smoothing}
 In trying to recover the kinematic variables from the droplet trajectories we encounter a difficulty in the noise of the position data:
@@
 
-\subsection*{Numerical Solution to the Equation of Motion}
+\subsection{Numerical Solution to the Equation of Motion}
 The equation of motion behaves stiffly due to the large disparity in Coulombic, image charge, and dielectrophoretic lenghtscales.

### 2018-01-08 doc/manuscript/parameter_estimation.tex
covariance and condition MLE estimates

@@
 \end{figure}
+
+\begin{itemize}
+\item We seek to maximize the likelyhood $L = k - \frac{\chi^2}{2}$, which is equivalent to maximizing $\chi^2$.
+\item Typically, each iteration evaluates the goal function only once or twice, which is why the Nelder-Mead algorithm is comparatively fast if goal function evaluation is the computational bottleneck (Singer and Mead, 2009).
+\end{itemize}
 

### 2018-01-10 doc/manuscript/parameter_estimation.tex
modifcation of PE parameters, some notes on Hessian matrix

@@
 \section{Parameter Estimation}
-A non-dimensional number: $ {\mathbb{E}\mbox{u}}_e$.
-
 We find the parameters $\mathbf{x}$ that solve the inverse problem $G(\mathbf{x}) = \mathbf{d}$, using a direct search method (\emph{Nelder-Mead}). 
@@
 
-\item \hl{[notes on $\chi^2$ goodness-of-fit]}
-
 \item Model parameter estimation is the process of indirect determination of unknown model parameters  from measurements of experiemental data.
@@
 \item The process of fitting a function, defined by a collection of parameters, to a data set is called the discrete inverse, or parameter estimation problem (as opposed to the \emph{forward problem} to find $\mathbf{d}$ given $\mathbf{m}$ and $G(\mathbf{m})$).
+
+\item By Bayes' Theorem
+\[\mbox{prob}(X|D, I) = \frac{\mbox{prob}(D|X,I) \times \mbox{prob}(X|I)}{\mbox{prob}(D|I)}\]
+where $\mbox{prob}(X|D, I)$ is the posterior probability density function that we want to estimate, $\mbox{prob}(D|X,I)$ is the likelihood function, $\mbox{prob}(X|I)$ is the prior probability density function that reflects our knowledge of the system, and $\mbox{prob}(D|I)$ is our evidence (the likelihood of the data based on our knowledge).
+\item The Maximum Likelyhood Estimate (MLE) for the the model prarameters $\mathbf{x_0}$, is given by the maximum of the posterior PDF, hwich is equivalent to the solution that produces the highest probability of the observed data.
+(The optimal parameter set is the one with the highest probability of
+observing the data and can be determined by maximizing the likelihood $\mathcal{L}$ of the data $y$ with respect to the parameter set $\mathbf{x}$).
+\item The log-likelihood is given by
+\[\mathcal{L} = \ln(\mbox{prob}(X|D, I)) = \mbox{const} - \frac{\chi^2}{2}\]
+so the maximum of the posterior will occur when $\chi^2$ is smallest, and the corresponding optimal solution $\mathbf{x_0}$ is then called the least-squares estimate.
+\item We precondition the problem by minimizing $\ln(\chi^2)$, and scaling our constraints by their initial guesses.Scaling can help solve convergence problems and improve numerical stability.
+Here is goal is to make the problem qually senstive to steps in any direction.
+We use a naieve scaling (scaling variables such that their magnitudes $\sim 1$).
+\item Open questions: given the structure of a model is it possible to uniquely estimate it's unknown parameters?
+What experimental data are required to achieve unique parameter identification?
+These questions are called the problem of identifiability.
+Global identifiability is a challenging problem, and even in cases where is the problem is shown to be structurally identifiable, the problem may yet be practically unidentifiable.
+Our general approach to satisfying the uniqueness of our estimates is instead based on sensitivy analysis.
+\item the Hessian matrix must be negative definite for $\mathcal{L}$ to have a maximum at $\mathbf{x_0}$.
+\item We can use the condition number
+\[ \mbox{cond} (A) = \frac{\mbox{max}[\mbox{eig}(A)]}{\mbox{min}[\mbox{eig}(A)]} \]
+as a means to evaluate to stability of our problem. We find typical conditon numbers $\sim \mathcal{O}(10^{27})$ which indicate the problem is strongly ill-conditoned near the mimima $\mathbf{x_0}$.
+\item We're intested in the variance and co-variance as a means to determine the quality if the parameter estimate.
+\item The $\left( i, j \right)$-th element of the matrix $\sigma (\mathbf{x}, \mathbf{y})$ is equal to the covariance $\mbox{cov}(X_i, Y_j)$ between the $i$-th scalar component of $\mathbf{x}$ and the $j$-th scalar component of $\mathbf{Y}$.
+\item Here the concept of error bars in linear correllation associated with a covariance matrix are not suitable.
+We might try to generalize the idea of confidence intervals to a multidimensional space, but usually it will be hard to describe the surface of the (smallest) hypervolume containing 90\% of the probability in just a few numbers.
+The situation is worse if the probability density function has several maxima.
+However we notice that
+\[ \left[\sigma^2 \right]_{ij} = -\left[ \left( \nabla \nabla \mathcal{L}\right)^{-1}\right]_{ij} = 2 \left[ \nabla \nabla \left( \chi^2\right)\right]_{ij}^{-1} = -\left[H^{-1} \right]_{ij}\]
+where $H$ refers to the Hessian matrix and $\left[\sigma^2 \right]_{ij}$ is the covariance matrix $C$.
+The likelhood function (and thus the postierior probability density function) are defined completely by the optimal solution $\mathbf{x}$ and the second derivative of $\mathcal{L}$ at the maximum, which corresponds to the covariance matrix $C$.
+\item The standard errors are the square roots of the diagonal of the covariance matrix.
+Our relative errors thus produced are extremely small ($> 1 \%$).
+Verification of the results is crucial, yet it has not be done yet.
+\hl{[Ref]} suggests verification by generation of Monte Carlo data sets.
+Does the estimation code recover the target parameters?
 \end{itemize}
@@
 \begin{itemize}
-\item We seek to maximize the likelyhood $L = k - \frac{\chi^2}{2}$, which is equivalent to maximizing $\chi^2$.
+\item We seek to maximize the likelyhood $\mathcal{L} = k - \frac{\chi^2}{2}$, which is equivalent to maximizing $\chi^2$.
 \item Typically, each iteration evaluates the goal function only once or twice, which is why the Nelder-Mead algorithm is comparatively fast if goal function evaluation is the computational bottleneck (Singer and Mead, 2009).
@@
 It uses only-function calls and expands or contracts the simplex according to the function values at its vertices in a way visually reminiscent (in $\mathbb{R}^2$) of the oscillations of the jumping droplets themselves (in fact \emph{Nelder-Mead} is sometimes also called the ``ameoba method'').
-
-Preconditioning, scaling the constraints in the penalty function.
+Very little is known about the convergence properties of the \emph{Nelder-Mead} algorithem in its classical form for non smooth objective functions (\hl{[Price and Coope, 2003]}), except that in general it doesnt satisfy the properties required for convergence by other direct search algorithems: that the simplex remains uniformly non-degenerate, and that some form of ``sufficient'' descent conditon for function values at the vertices is required at each iteration
 
@@
 Namely these include the possibility of the objective function being undefined outside of the set of feasible solutions.
-Additionaly, by naively ``encouraging'' feasibility of the solution using large values of the penalty parameter, $r_p$, we will tend to ill-condition the unconstrained formulation of the problem.
+Additionaly, by naively ``encouraging'' feasibility of the solution using large values of the penalty parameter, $r_p$, we will tend to ill-condition the unconstrained formulation of the problem (thoug in our implimentation the preconditoning tends to make the psuedo-objectibve function less and less sentive to the constraints as the likelihood is approaches a maximum).
 \hl{[notes on choice of optimizer parameters, initial guesses, convergence, error estimates]}.
 Using penalty function methods tend to exascerbate the sensitivity of \emph{Nelder-Mead} solutions to the choice of intial guess vector \hl{[ref]}.
+
+Despite their wide use in parameter estimation, there is very little known about convergence properties of \emph{Nelder-Mead}.The iterative procedure may thus converge very slowly near the optimum, unless the Hessian is "well-conditioned", i.e., the condition number is near one.
+However, if parameter estimates are highly correlated among themselves, the Fisher information matrix is near-singular and its inversion is either impossible or involves significant numerical error.
 

### 2018-01-18 doc/manuscript/introduction.tex
added asymptotic estimates

 \documentclass[10pt,a4paper]{article}
\usepackage[utf8]{inputenc}
%\usepackage{fontspec} % This line only for XeLaTeX and LuaLaTeX
\usepackage{pgfplots}
\usepackage{pgf}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{color,soul}
\usepackage{listings}
\usepackage{setspace}
\author{Erin Schmidt}

\newlength\figureheight
\newlength\figurewidth
\setlength\figureheight{7cm}
\setlength\figurewidth{10cm}

\begin{document}
\doublespacing
\section{Introduction}
When asked to name one of the biggest challenges to living in
space, Astronaut Suni Williams replied that it is removing and
dealing with bubbles in fluids systems.

\begin{quote}
``... multiphase systems and thermal transport processes are enabling for proposed human exploration by NASA.''
- 2011 Decadal Survey
\end{quote}

\begin{quote}
``When the influence of gravity on fluid behavior is diminished or removed, other forces, otherwise of small significance, can assume paramount roles.''
- NRC Report to NASA, 2003
\end{quote}

Un-terrestrially large droplets are produces by a huge array of mechanisms in a low-gravity environemnt.

Comprehensive list? of electrostatic applications particular to low-gravity:
\begin{itemize}
\item Spacecraft charging due to space environment. Surface charging largely due to low energy electrons (3-50 keV) which do not penetrate the surface of the spacecraft external stureture. This deposited charge accumulate  and can lead to significant potential differences between different parts of a spacecraft. Deep dielectric charging occurs when higher energy charged particles penetrate the surface of a dielectric material, which can also lead to large potential differences if the dielectric leakage is lower than the external charging rate. The ultimate sources of these charges are trapped charged particles of the van Allen radiation belts, galactic cosmic rays, and the solar wind. \hl{Which space environemts have higher charging risks, propellant deopt locations}. Venting, droplets.

\item Active (but solid-state) phase seperation for ECLSS multiphase flows, espcially high void-fraction flows (dish washing, laundry, waste solids drying, food processing, Sabatier CO$_2$ reaction, possibly in vapor-compression cycle condensers). Phase separation is critical to high reliability and low power gas-liquid systems for used in thermal control and life support. Phase seperation for other disperse droplet flows include electrostatic droplet seperators for high-efficiency Rankine cycle turbines. Removal of satellite droplets produced during pippetting during wet-lab research outside of a glovebox environemnt aboard ISS.

\item Electrostatic levitators for containerless processing, droplet combustion experiements. Containerless creatio, and collection of monodisperse spheres (dielectrics or conductor; the chargeing mechanism will vary).

\item Electrospray-based fire suppression systems.

\item EHD (dielectrophoretic) augmentation of convection (electroconvection, an analog of natural convection due to a dielectric permititivy gradient, which is a function of fluid temperature, int he presence of a body force field analog, in this case an electric field) and condensation heat transfer. Boiling heat transfer by promotion of bubble detachment and prevention of dryout (e.g. as a substitute for bouyancy).

\item EHD heat pipes, which substitude an electrode structre for the capillary wicking structure of a conventional thermocapillary heat pipe can evade the wicking limit. Problematically restricted to the use of insulating dielectric liquids (which usually have relatively low thermal conductivity), but offer advantages in highly-reliable priming, bubble rejection, flow control, and low viscous losses.

\item Dielectrophoretic settling of cryogenic propellants (in both total and partial communication configurations), slosh baffling, vent screening, mitigation of vapor pulltrough (and concomittent minimization of propellant residuals at burnout). Reduction in heat transfer by collecting propellants away from tank walls, reducing boiloff losses.

\item High temperature liquid droplet radiators with electrostatic collection.
\end{itemize}

\end{document}

### 2018-01-18 doc/manuscript/parameter_estimation.tex
added asymptotic estimates

--- 2018-01-07 doc/manuscript/parameter_estimation.tex
@@
 \section{Parameter Estimation}
-A non-dimensional number: $ {\mathbb{E}\mbox{u}}_e$.
-
 We find the parameters $\mathbf{x}$ that solve the inverse problem $G(\mathbf{x}) = \mathbf{d}$, using a direct search method (\emph{Nelder-Mead}). 
 \[
-\mbox{min} \hspace{2 mm} \chi^2 = \mbox{min} \hspace{2 mm} \sum^n_{i=1} \frac{\left({y_d(\mathbf{x})}_i - y_G(\mathbf{x})_i \right)^2}{y_G(\mathbf{x})_i}
+\mbox{min} \hspace{2 mm} \chi^2 = \mbox{min} \hspace{2 mm} \sum^n_{i=1} \frac{\left({y_d(t)}_i - y_G(t, \mathbf{x})_i \right)^2}{y_G(t, \mathbf{x})_i}
 \]
@@
 \end{eqnarray*}
-where $y_G(\mathbf{x})$ is a numerical solution of the equation of motion
+where $y_G(t, \mathbf{x})$ is a numerical solution of the equation of motion
 \[
@@
 
-In particular, it is impractical to directly measure the droplet net charge $q$, during a bounce experiement. Our workflow to identify these parameters is as follows:
+In particular, it is impractical to directly measure the droplet net charge $q$, during a bounce experiment. Our work flow to identify this parameters is as follows:
 \begin{enumerate}
@@
 \item Slice droplet trajectories by their bounce minima, and apply a smoothing filter.
-\item Maximize the goodness of fit between the experimental trajectories and solutions of the equation of motion, by varying the design vector (which encodes the unkown parameters in the equation of motion) using a direct search optimizer.
+\item Extract the droplet charge (and other experimental parameters) by maximizing the log-likelihood of the data given the dynamical model and parameters, by varying the parameter vector using a direct search optimization.
 \end{enumerate}
+
 \subsection{Inverse Problems}
-\begin{itemize}
-\item We have a dynamical model describing the droplet electro-bounce; we wish to find typical values of the key parameter, droplet net charge $q$.
-In general it is not always possible nor practicle to measure model parameters experimentally.
-They may be hard, expensive, time consuming or perhaps even impossible to measure.
-\item A mathematical model designed to fit experiemental data so as to explicitly quantify physical parameters of interest.
-\item Values of model parameters are obtained using parameter estimation techniques aimed at providing a ``best fit'' to the data.
-\item Generally involves an interative process to minimize the average difference between the model and the data.
-\item Evaluating the quality of an inverse model involves a combination of established mathematical techniques as well as intuition and creative insight.
-\item A good inverse model has: good fit, model parameters are unique, and parameter values consistent with physical inuition or prior knowledge.
-\item The steps in the process are: 1.
-Select an appropriate mathematical model from theory.
-2.
-Define a ``figure of merit'' function which measures agreement between the data and model for a given set of parameters.
-3.
-Adjust model parameters to get a ``best fit''.
-4.
-Evaluate ``goodness of fit'' to data, which tends never to be perfect due to experimental noise.
-5.
-Estimate accuracy fo the best-fit parameter values (provide confidence intervals and determine uniqueness).
-6.
-Determine whether a much better fit is possible (which is difficult of ruggest respose surfaces; F-test can be used for comparing models of different complexity).
+We have a simple model for 1D projectile motion of charged droplets within Coulomb potential wells in low-g.
+Using various scaling arguments we have gleaned from this model a series of non-dimensional numbers characteristic of droplet bounce apoapses and times of flight, but these dimensionless groups depend on a set of physical parameters.
+Unfortunately not all of these parameters are physically practical to accurately measure by experiment.
+Droplet net charge $q$, in particular, could in principle be directly measured by collecting the charged drops in a faraday cup under low-g and measuring the change in capacitence of the cup using a very high input-resistence electrometer, but this is a problematic experiment to set up in a drop tower from a practical standpoint.
+The other state variables we can directly measure by experiement with varying levels of accuracy.
+To measure the charge, $q$, we instead turn to parameter estimation techniques.
 
-\item Maximum likelihood estimation: not ``what is the probability that my set of model parameters is correct?'' but rather ``given my set of model parameters, what is the probability that this data set occurred (what is the likelihood of the parameters given the data)?''
-
-\item \hl{[notes on $\chi^2$ goodness-of-fit]}
-
-\item Model parameter estimation is the process of indirect determination of unknown model parameters  from measurements of experiemental data.
-\item This is mathemetically challenging \hl{[ref]}. There are practical challenges as well, as experimental data tends to be noisey and sparse.
-\item In the most familliar sense determining model parameters is done using derivative based methods, essentially by estimating derivatives by finite differences (Euler's method) and fitting paramters using linear regression.
-However there are approaches to fitting any arbitrary function.
-\item Suppose we have a model $G(\mathbf{m})$, with a vector of parameters $\mathbf{m}$, and set of perfect noiseless observations $\mathbf{d}$, we expect there to exist a relationship 
-\[G(\mathbf{m}) = \mathbf{d} \]
-where the operator $G$ might be an ODE.
-\item Suppose we have a model given by the ODE
-\[ \frac{dy}{dt} = f(t, \mathbf{y}; \mathbf{p}), \mathbf{y} \in \mathbb{R}^n, \mathbf{f} \in \mathbb{R}^n ,\]
-where $\mathbf{p} \in \mathbb{R}^m$ is the vector of parameters, and a collection of measurements of experiemental data
-\[ \left( t_1, \mathbf{y_1} \right), 
+Suppose we have a model $G(\mathbf{x})$, with a vector of parameters $\mathbf{x}$, and set of (noiseless) observations $\mathbf{d}$, the we naturally expect there to exist a relationship 
+\[G(\mathbf{x}) = \mathbf{d} ,\]
+where the operator $G$ might be an ODE. Suppose the model $G(\mathbf{x})$ is the ODE
+\[ \frac{dy}{dt} = f(t, \mathbf{y}; \mathbf{x}), \hspace{1 mm}  \mathbf{y} \in \mathbb{R}^n, \]
+and a collection of $n$ measurements of experimental data
+\[ \mathbf{d} = \left( t_1, \mathbf{y_1} \right), 
 \left( t_2, \mathbf{y_2} \right), ... ,
 \left( t_k, \mathbf{y_k} \right).\]
-We wish to minimize an objection function which is the mean square error (or any goodness of fit figure of merit in general) between the model output and experimental data:
-\[ \mbox{obj}(\mathbf{p}) = \sum_{j=1}^k \left|\mathbf{y}(t_j; \mathbf{p}) - \mathbf{y_j} \right|^2,\]
-where $| . |$ is the Euclidian norm. Therefore the parameter estimation problem is a variety of optimization problem.
-\item The process of fitting a function, defined by a collection of parameters, to a data set is called the discrete inverse, or parameter estimation problem (as opposed to the \emph{forward problem} to find $\mathbf{d}$ given $\mathbf{m}$ and $G(\mathbf{m})$).
-\end{itemize}
+The process of fitting a function, defined by a collection of parameters, to a data set is called the discrete inverse, or parameter estimation problem (as opposed to the \emph{forward problem} to find $\mathbf{d}$ given $\mathbf{x}$ and $G(\mathbf{x})$).
+This is a familiar procedure when the determination of model parameters is done using linear or polynomial regression.
+However there are approaches even to fitting an arbitrary function to a noisy and sparse dataset.
+In this work we use the conventional Maximum Likelihood Estimate (MLE) method to identify the model parameters.
 
-\begin{figure}[htb]
-    \centering
-    \resizebox{14cm}{!}{\input{../figures/jump_matrix.pgf}}
-    \caption{A simple EMA plot.\label{fig:trajectories}}
-\end{figure}
-
-\begin{figure}[htb]
-    \centering
-    \resizebox{14cm}{!}{\input{../figures/inverse_problem.pgf}}
-    \caption{A simple EMA plot.\label{fig:inverse_problem}}
-\end{figure}
-
-\begin{figure}[htb]
-    \centering
-    \resizebox{14cm}{!}{\input{../figures/convergence.pgf}}
-    \caption{A simple EMA plot.\label{fig:convergence}}
-\end{figure}
+Using MLE we don't ask the question: ``what is the probability that my set of model parameters is correct?''(because the probability is very nearly zero!), but rather ``given my set of model parameters, what is the probability that this data set occurred (what is the likelihood of the parameters given the data)?''.
+Bayes' Theorem holds that
+\[\mbox{prob}(X|D, I) = \frac{\mbox{prob}(D|X,I) \times \mbox{prob}(X|I)}{\mbox{prob}(D|I)}\]
+where $D$ are our observations (dataset), $X$ is our vector of parameters, and $I$ is general background information about the problem including our mathematical model (for instance the ODE above), and
+\[\begin{array}{lll}
+& \centering \mbox{prob}(X|D, I) & \mbox{posterior probability density function},\\
+& \centering \mbox{prob}(D|X, I) & \mbox{likelihood function},\\
+& \centering \mbox{prob}(X|I) &  \mbox{prior probability density function},\\
+& \centering \mbox{prob}(D|I) &  \mbox{evidence}.
+\end{array}
+\]
+The posterior probability density function (PDF) $\mbox{prob}(X|D, I)$, is ultimately what we want to estimate, the prior PDF $\mbox{prob}(X|I)$, reflects our knowledge of the system, and the evidence $\mbox{prob}(D|I)$, is the likelihood of the data based on our knowledge.
+We also note that since it only makes sense to compare the conditional PDF's for the same data, we can ignore the denominator (that is, the evidence).
+We further note that the prior $\mbox{prob}(X|I)$, is fixed before our observations and so can be
+treated as invariant to our problem.
+We can therefore infer that $\mbox{prob}(X|D, I) \propto \mbox{prob}(D|X, I)$.
+The MLE for the the model parameters $\mathbf{x_0}$, then is given by the maximum of the posterior PDF, which is equivalent to the solution of the ODE given the the parameters $\mathbf{x}$, that produces the highest probability of the observed data.
+Since the likelihood $\mathcal{L}(\mathbf{x}) = \prod_i^n \mathcal{P}_i$, and the probability $\mathcal{P}$, of any single observation is less than one, then the total likelihood which is the product of a large number of probabilities tends to be vanishingly small.
+The more well behaved log-likelihood is given by
+\[\mathcal{M} = \ln(\mathcal{L}) = \ln(\mbox{prob}(D|X, I)) = \mbox{const} - \frac{\chi^2}{2}\]
+where 
+\[
+\chi^2 = \sum^n_{i=1} \frac{\left({y_d}_i - {y_G}_i \right)^2}{{\sigma_d}_i^2}
+\]
+is the $\chi^2$ goodness-of-fit, $y_d = y_d(t)$ is a observation of droplet position at a point in time, and $y_G =  y_G(t, \mathbf{x})$ is the droplet position predicted by the solution to the equation of motion at time $t$, and $\sigma$ is the standard error of the position measurement.
+If the number of data points $n$, is small was can use the Poisson error $\sigma_d^2 = {y_G}$.
+The optimal parameter set is the one with the highest probability of observing the data (the maximum of the posterior PDF) and can be determined by maximizing the log-likelihood $\mathcal{M}$ (or minimizing $\chi^2$) of the data $\mathbf{d}$ with respect to the parameter set $\mathbf{x}$.
+Thus parameter estimation is a variety of optimization problem.
 
 \subsection{Optimization}
-Most generally the we state the constrained problem as 
+Most generally a constrained optimization problem is stated as 
 \[
 \begin{array}{lll}
-\mbox{minimize:} & \hspace{2 mm} F\left(\mathbf{x}\right) & \mbox{objective function}\\
+\mbox{minimize:} & \hspace{2 mm} f\left(\mathbf{x}\right) & \mbox{objective function}\\
 \mbox{subject to:} & & \\
@@
 
-Our specific optimization problem is non-convex, mixed discrete-continuously black-box (noisy), which is essentially the worst the worst case scenario.
-While in principle a gradient-based optimizer (such as ...) could be used by using finite-differences to obtain approximate gradients of the $\chi^2$ objective funtion, in practice doing so is problematic becasue the signal-to-noise ratio of the objective function scales like $\mathcal{O}(f)$ for $\frac{df}{dt}$ and $\mathcal{O}(f^2)$ for $\frac{d^2f}{ft^2}$ which will cause problems with our Hessians and Javobians respectively \hl{[Refs 5, 14, 49, 95.]}.
-As a further practical matter, given the relatively expensive function-calls (which requires solving a stiff, non-linear ODE) gradient-free approaches tend to offer better performence regardless.
-
 Mathematical optimization is the problem of finding minima of a function $f$.
-In this context the function in question is referred to as a cost, or objective function.
+In this context the function is called the cost, or objective function.
 The field of mathematical optimization is as old as calculus itself, and the number of particular optimization techniques is correspondingly myriad; particular techniques lend themselves well to particular types of optimization problems.
-The minima of the objective function $f$ is sought on a domain $A$ specified by the constraints of the problem, this is usually called the feasible region.
-Minima of objective function $f: A \rightarrow \mathbb{R}^n$ on $A$ are usually called feasible solutions.
+The minima of the objective function $f$ is sought on a domain $A$ specified by the constraints of the problem; this domain is usually called the feasible region.
+Minima of objective function $f: A \rightarrow \mathbb{R}^m$ are called feasible solutions.
 If the function $f$ is convex the feasible solution is the global minimum, otherwise additional local minima exist.
 The scale of the optimization problem is set ultimately by dimensionality of the objective function.
-Functions may not always be smooth in the sense of having continuous derivatives, this is problematic in that optimization methods fundimentally rely on gradients of the objective function.
-Problems with anisotropic objective functions in the sense that the gradient vector tends to differ significantly from the Newton direction ($-\mathbf{H}^{-1} f' ( \mathbf{x} )^T$, where $\mathbf{H}$ is the Hessian matrix) are considered ill-conditoned.
-In ill-conditioned problems gradient based deterministic search may be extremely slow.
+Functions may not always be smooth in the sense of having continuous derivatives, and this is problematic in that optimization methods fundamentally rely on gradients of the objective function.
+Problems with anisotropic objective functions where there is strong covariance between the parameters, and the gradient vector generally to differ significantly from the Newton direction ($-\mathbf{H}^{-1} f' ( \mathbf{x} )^T$, where $\mathbf{H}$ is the Hessian matrix) are considered ill-conditioned.
+Ill-conditioned problems gradient based deterministic search tend to converge slowly as they take a zigzagging path determined by the local value of the gradient rather than following the Newton-direction vector which towards the minimum.
 Numerical optimization may deal with black box functions (where we do not have an explicit mathematical expression of the function we are optimizing).
-Black box problems are challenging because we do not have access to analytic gradients of the objective function, and approximating them by finite-differences is slow and noisey.
-In general, noisey, black box, non-linear, non-quadratic, non-convex, constrained, ill-conditioned, high-dimensional objective functions are problematic to optimize.
-This is the practical essense of the parameter estimation problem.
-In particular there are few methods that work well with noisey, ill-conditioned problems.
+Black box problems are challenging because we do not have access to analytic gradients of the objective function, and approximating them by finite-differences is slow and noisy.
+In general, noisy, black box, non-linear, non-quadratic, non-convex, constrained, ill-conditioned, high-dimensional objective functions are problematic to optimize.
+Unfortunately, problems of this type are the essence of the parameter estimation, which often leads to its characterization as an `art' rather than a precise science (though we submit that it is a dark art).
 
-We use a gradient-free, direct-search approach: Nelder-Mead \hl{[Nelder, 1965]} implimented in \verb|scipy.optimize| \hl{[Jones et al.
+The equation of motion behaves stiffly due to the large disparity in Coulombic, image charge, and dielectrophoretic length scales.
+We integrate it numerically using the \verb|odeint| \emph{Scipy} module.
+This is a shake-and-bake Python wrapper for the venerable 1982 \emph{netlib ODEPACK} library double-precision \verb|lsoda| (Livermore Solver for Ordinary Differential equations with Automatic method switching for stiff and nonstiff problems) integrator \hl{[ref]}.
+The function switches between Adams (nonstiff) and Backwards Differentiation Formulas (BDF, stiff) according to the dynamic value of a set of stiffness eigenvalues.
+
+Our specific optimization problem is non-convex, mixed discrete-continuous black-box (noisy), and highly ill-conditioned which is essentially the worst the worst case scenario for an optimization problem.
+The ill-conditioning arises due to the strong covariance between several of the model parameters (particularly $q=q(V_d, E_0)$).
+The non-convexity of the problem implies that there are many local minima of the objective function.
+While in principle a gradient-based optimizer (for instance using the quasi-Newton method of Broyden, Fletcher, Goldfarb, and Shanno (BFGS) \hl{[Nocedal, J, and S J Wright.
+2006]}) could be used by using finite-differences to obtain approximate gradients of the $\chi^2$ objective function, in practice doing so is extremely problematic because the noise-to-signal ratio of the objective function scales like $\mathcal{O}(f)$ for $\frac{df}{dt}$ and $\mathcal{O}(f^2)$ for $\frac{d^2f}{ft^2}$ which will tend to cause convergence to a local minima with is an artifact of the likelihood response surface \hl{[Wood, 1982: Refs 5, 14, 49, 95.]}.
+As a further practical matter, given the relatively expensive function-calls (which requires solving a stiff, non-linear ODE) gradient-free approaches tend to offer better performance regardless\hl{[Singer and Mead, 2009]}.
+
+We use a gradient-free, direct-search approach: Nelder-Mead \hl{[Nelder, 1965]} implemented in \verb|scipy.optimize| \hl{[Jones et al.
 2001 --]}.
 Nelder-Mead is robust to noise (relatively speaking), and is relatively thrifty with our extremely expensive function-calls.
-\emph{Nelder-Mead}, sometimes called simplex-search or downhill-simplex, is a hueristic search method, with no guarantee of optimal solutions, but is well-established and widely used despite that.
+\emph{Nelder-Mead}, sometimes called simplex-search or downhill-simplex, is a heuristic search method, with no guarantee of optimal solutions, but is well-established and widely used despite that.
 \emph{Nelder-Mead} is based on the concept of a $N$-simplex, which generalizes a triangle into higher dimensions as a polytrope of $N + 1$ vertices in $N$ dimensions.
-It uses only-function calls and expands or contracts the simplex according to the function values at its vertices in a way visually reminiscent (in $\mathbb{R}^2$) of the oscillations of the jumping droplets themselves (in fact \emph{Nelder-Mead} is sometimes also called the ``ameoba method'').
+It uses only-function calls and expands or contracts the simplex according to the function values at its vertices in a way visually reminiscent (in $\mathbb{R}^2$) of the oscillations of the jumping droplets themselves (in fact \emph{Nelder-Mead} is sometimes also called the ``amoeba method'').
+Very little is known about the convergence properties of the \emph{Nelder-Mead} algorithm in its classical form for non smooth objective functions (\hl{[Price and Coope, 2003]}), except that in general it doesn't satisfy the properties required for convergence by other direct search algorithms: that the simplex remains uniformly non-degenerate, and that some form of ``sufficient'' descent condition for function values at the vertices is required at each iteration.
+Scaling can help solve convergence problems and improve numerical stability.
+We precondition the optimization problem by minimizing $\ln(\chi^2)$, and using a naive scaling (scaling variables such that their magnitudes $\sim 1$) of our constraints by their initial guesses.
+Here is goal is to make the problem equally sensitive to steps in any direction.
+\emph{Nelder-Mead} is not a global optimizer, though there are variants which use sequential local searches with probabilistic restarts to achieve globality.
+However global optimization usually comes at a tremendous computational cost.
+However, \emph{Nelder-Mead} behaves less locally than many gradient-based approaches.
+The convergence history of the parameter MLE using \emph{Nelder-Mead} for a single drop jump experiment is shown in Figure \ref{fig:convergence}.
 
-Preconditioning, scaling the constraints in the penalty function.
+\begin{figure}[htb]
+    \centering
+    \input{../figures/convergence.pgf}
+    \caption{As is typical with \emph{Nelder-Mead} much of the improvment in $\chi^2$ is realized in the first few iterations.
+Overall the rate of convergence is sub-linear, which is to be expected for non-liner constrained problems using an hueristic algorithem.\label{fig:convergence}}
+\end{figure}
 
-We do not have \emph{a priori} information regarding existence of true globality for our objective function.
-Perhaps more importantly, given the degrees-of-freedom in the parameter space there may be a multiplicity of local extrema of the $\chi^2$ hyper-response surface.
-\emph{Nelder-Mead} is not a global optimizer, though there are varients which use sequential local searches with probablistic restarts to achieve globality.
-However global optimization usually comes at a tremendous computational cost.
+\subsection{Smoothing}
+All optimization methods, including \emph{Nelder-Mead}, whether explicit or implicitly follow gradients towards an optimum.
+In a parameter estimation problem, if we approximate these gradients by finite differences, then the noise manifests itself as amplification of the roughness in the hyper-response surface.
+Gradient based optimizers do poorly in these situations because they tend to converge to local minima.
+While so called gradient free algorithms offer an improvement in this regard, speed of convergence and the quality of the MLE is improved by smoothing the objective function.
+This is equivalent to smoothing the underlying dataset.
 
-That we are capabible of fitting any arbitrary model to a dataset given sufficient degrees of freedom in our parameters is admittedly a disconcerting issue, and is manifested in the locality of the extrema of the $\chi^2$ response surface.
+Our choice of smoothing approach depends principally on the nature of the errors in the dataset.
+The sources of error include misalignment of the camera, error in the fiduciary length scale, perspective due to objects (subject or reference scale) being out of the photographic plane, and various errors arising in the digitization process (including the difference between the thresholded ellipse fitted centroid and the true centroid of the non-ellipse drop centroid).
+Some of these errors are systematic in origin and introduce consistent biases into the data (e.g.
+coherent spectral sources, rather than truly stochastic noise).
+Data smoothing does little to help systematic errors in that they are usually of lower frequency than the signal.
+Random errors, by contrast, are assumed to have a Gaussian distribution (by the central limit theorem), and are independent of the signal (which inherently results from a deterministic process).
+
+We experimented with a variety of filters implemented in the \verb|scipy.signal| \emph{SciPy} module on a representative set of trajectory data; these methods include 1D Gaussian convolution, Wiener, Butterworth, and Savitsky-Golay filters.
+Qualitatively comparing these smoothing methods (by hand tuning filter orders and window sizes) we find that we loose too many data points in the smoothing process, large amplitudes are overly smoothed by repeated filtering passes, or there are significant end effects for most of these methods.
+A comparison of these smoothing approaches on a representative trajectory data set are shown in Figure \ref{fig:y_filtered}.
+
+\begin{figure}
+    \centering
+    \input{../figures/y_filtered.pgf}
+       \caption{The underlying signal is `noisy', due partially to deterministic errors in determining the centroid position.
+These deterministic errors are largely due to droplet oscillations, especially the rapidly damped higher harmonics which do not have azimuthal symmetry.
+There is also Gaussian error in the ellipse fitting due to thresholding and noise in the video itself.
+We see that 1D Gaussian convolution and Wiener filters suffer from significant end effects.
+At this scale Butterworth and Savistsky-Golay filters are nearly indistinguishable.}
+      \label{fig:y_filtered}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \input{../figures/dy_filtered.pgf}
+    \caption{Comparing the first derivatives of the Butterworth and Savitsky-Golay filters we see that the Butterworth filter also suffers from a slight end effect.
+This implies that the optimization will find a different optima of the likelyhood depending on which type of filter is used.\label{fig:dy_filtered}}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \input{../figures/power_spectra.pgf}
+    \caption{The power spectra has a peak at 1 Hz, which is the droplet trajectory parabola itself, and smaller peaks in the kHz range corresponding to various noise frequencies.
+The Savitsky-Golay and Butturworth filters seem to have the least distortion of the power spectra of the true signal.
+Both also do a good job of attenuating the noise at the 2 kHz peak.
+\label{fig:power}}
+\end{figure}
+
+The Savitsky-Golay, and Butterworth filters both produce fairly smooth derivatives as can be seen in Figure \ref{fig:dy_filtered}; but the small window-size needed for Butterworth filter tends to also produce a noticeable end effect.
+The Savitsky-Golay filter essentially uses a moving-window based on local least-squares polynomial approximations.
+It was shown that fitting a polynomial to a set of input samples and then evaluating the resulting polynomial at a single point within the approximation interval is equivalent to discrete convolution with a fixed impulse response \hl{[Savitsky, 1964]}.
+A beneficial property of this kind of low-pass filter is their tendency to maintain waveform amplitudes, and so they are attractive in applications having noisy signals with sharply pointed waveforms such as ultrasound or synthetic aperture radar \hl{[Schafer, 2011]}.
+Because Savitsky-Golay is a Finite Impulse Response (FIR) filter it requires data points to be equally spaced; to accommodated this we interpolate points between the small gaps which sometime occur in the tracking results from image analysis.
+We use a moving window size slightly smaller than the length of the current bounce in a drop jump data set.
+The windows are piecewise defined by partitioning the data set into a series of individual bounces (the dataset is sliced at minima identified after an initial rough smoothing pass, using the \verb|scipy.signal.argrelextrema()| function).
+The Savitsky-Golay polynomial order is 4.
+To understand how these filters differ it is useful to look at their frequency response.
+In Fourier space, convolution becomes a multiplication, and we can understand what a filter does by looking at which frequencies it lets pass through.
+We can do this using a Discrete Fourier Transform (though it is worth noting that our signal is not truly periodic).
+The power spectra for these same data are shown in Figure \ref{fig:power}.
+
+\subsection{Identifiability}
+That we are capable of fitting any arbitrary model to a dataset given sufficient degrees of freedom in our parameters is admittedly a disconcerting issue, begging the question ``given the structure of the model is it possible to uniquely estimate the unknown parameters?'' This question is called the problem of identifiability.
 However, some of the inverse model parameters are constrained by our experimental observations of them and their associated measurement uncertainties.
-This, we hope, makes the spectre of an overfitted model less frightening, but does convert our uncontrained optimization problem to an constrained one which raises special difficulties of its own.
+This, we hope, makes the specter of an over fitted model less frightening, but does convert our unconstrained optimization problem to an constrained one which raises special difficulties of its own, which we discuss below.
 
-The \emph{Nelder-Mead} direct search method cannot be used with explicity constrained problems.
-However, there are various implicit approaches to (approximately) solving general constrained problems using uncontrained algorithems.
+We're interested in the variance and co-variance as a means to determine the quality if the parameter estimate.
+The $\left( i, j \right)$-th element of the matrix $\sigma (\mathbf{x}, \mathbf{y})$ is equal to the covariance $\mbox{cov}(X_i, Y_j)$ between the $i$-th scalar component of $\mathbf{x}$ and the $j$-th scalar component of $\mathbf{Y}$.
+Here the concept of error bars in linear correlation associated with a covariance matrix are not suitable.
+We might try to generalize the idea of confidence intervals to a multidimensional space, but usually it will be hard to describe the surface of the (smallest) hyper-volume containing 90\% of the probability in just a few numbers.
+The situation is worse if the probability density function has several maxima.
+However we notice that
+\[ \left[\sigma^2 \right]_{ij} = -\left[ \left( \nabla \nabla \mathcal{L}\right)^{-1}\right]_{ij} = 2 \left[ \nabla \nabla \left( \chi^2\right)\right]_{ij}^{-1} = -\left[H^{-1} \right]_{ij}\]
+where $H$ refers to the Hessian matrix and $\left[\sigma^2 \right]_{ij}$ is the covariance matrix $C$.
+The issue of identifiability is especially fraught for non-linear, black box type problems were it is difficult to explicitly evaluate the Hessian.
+The likelihood function (and thus the posterior probability density function) are defined completely by the optimal solution $\mathbf{x}$ and the second derivative of $\mathcal{L}$ at the maximum, which corresponds to the covariance matrix $C$.
+The standard errors (marginal variances) are the square roots of the diagonal of the covariance matrix.
+Our relative errors thus produced are extremely small ($> 1 \%$).
+The Hessian matrix must be negative definite for $\mathcal{L}$ to have a maximum at $\mathbf{x_0}$.
+We can use the condition number
+\[ \mbox{cond} (A) = \frac{\mbox{max}[\mbox{eig}(A)]}{\mbox{min}[\mbox{eig}(A)]} \]
+as a means to evaluate to stability of our problem. We find typical condition numbers $\sim \mathcal{O}(10^{27})$ which indicate the problem is strongly ill-conditioned near the mimima $\mathbf{x_0}$.
+
+The \emph{Nelder-Mead} direct search method cannot be used with explicitly constrained problems.
+However, there are various implicit approaches to (approximately) solving general constrained problems using unconstrained algorithms.
 Generally, this is achieved by domain transformations or the use of penalty functions.
-By the addition of a penalty function which depends in some way on the values of the constraints to the objective function, we minimize a pseudo-objective function where the infeasibility of the constraints is minimized simultaneously to the objective function.
+By the addition of a penalty function which depends in some way on the values of the constraints to the objective function, we minimize a pseudo-objective function where the in feasibility of the constraints is minimized simultaneously to the objective function.
 
@@
 Namely these include the possibility of the objective function being undefined outside of the set of feasible solutions.
-Additionaly, by naively ``encouraging'' feasibility of the solution using large values of the penalty parameter, $r_p$, we will tend to ill-condition the unconstrained formulation of the problem.
-\hl{[notes on choice of optimizer parameters, initial guesses, convergence, error estimates]}.
-Using penalty function methods tend to exascerbate the sensitivity of \emph{Nelder-Mead} solutions to the choice of intial guess vector \hl{[ref]}.
+Additionally, by naively ``encouraging'' feasibility of the solution using large values of the penalty parameter, $r_p$, we will tend to ill-condition the unconstrained formulation of the problem (though in our implementation the preconditioning tends to make the pseudo-objective function less and less sensitive to the constraints as the likelihood is approaches a maximum).
+We use the the measured values of $u_0$, $V_d$, and $E_0$, and the informed guess $q \approx k V_d^{2/3} E_0$ where k is a constant $k \approx 1 \time 10^{-11}$ as an initial guess for the parameter vector $\mathbf{x}$.
+We stop the optimization after 300 iterations rather than waiting for convergence.
 
-\subsection{Smoothing}
-In trying to recover the kinematic variables from the droplet trajectories we encounter a difficulty in the noise of the position data:
+Despite their wide use in parameter estimation, there is very little known about convergence properties of \emph{Nelder-Mead}.
+The iterative procedure may thus converge very slowly near the optimum, unless the Hessian is "well-conditioned", i.e., the condition number is near one.
+However, if parameter estimates are highly correlated among themselves, the Hessian matrix is near-singular and its inversion is either impossible or involves significant numerical error.
+Posteriori verification of the results is crucial to bound the identifiability of the parameter estimation problem, yet it has not be done yet.
+\hl{[Ref]} suggests verification by generation of Monte Carlo data sets.
 
-Error sources include misalignment of the camera, perspective due to objects (subject or reference scale) being out of the photographic plane, precision limits in digitization.
-Some of these errors are systematic in origin and introduce consistent biases into the data (e.g.
-coherent spectral sources, rather than truly stochastic noise).
-These systematic sources of error include inaccurate scales among others.
-Data smoothing tends not to help with the systematic errors in that they are usually of lower frequency than the signal (and here we are trying specifically to filter high frequency noise).
-Random errors, by contrast, are assumed to have a Gaussian distribution (by the central limit theorem), and are independent of the signal (which inherently results from a deterministic process).
-
-We experimented with a variety of filters implimented in the \verb|scipy.signal| \emph{SciPy}[ref] module using a represenative set of trajectory data; these methods include 1D Gaussian convolution, Wiener, Butterworth, and Savitsky-Golay filters.
-Qualitatively comparing these smoothing methods (by handtuning filter orders and window sizes) we find that we loose too many data points in the smoothing process, large amplitudes are overly smoothed by repeated filtering passes, or there are significant end effects for most of these methods.
-A comparison of these smoothing approaches on a representative trajectory data set are shown in Figure \ref{fig:filters}.
-The power spectra for the same data are compared for these methods in Figure \ref{fig:power_spectra}.
-
-%\begin{figure}[htb]
-%\centering
-%\resizebox{10cm}{!}{\input{../figures/y_filtered.tex}}
-%\caption{Power spectra of the filter methods compared.}\label{fig:myfigure}
-%\end{figure}
-
-%\begin{figure}[htb]
-%\centering
-%\resizebox{10cm}{!}{\input{../figures/dy_filtered.tex}}
-%\caption{Power spectra of the filter methods compared.}\label{fig:myfigure}
-%\end{figure}
-
-%\begin{figure}[htb]
-%\centering
-%\resizebox{10cm}{!}{\input{../figures/power_spectra.tex}}
-%\caption{Power spectra of the filter methods compared.}\label{fig:myfigure}
-%\end{figure}
-
-\begin{figure}
+\begin{figure}[h]
     \centering
-    \input{../figures/power_spectra.pgf}
-    \caption{A simple EMA plot.\label{fig:ema1}}
+    \resizebox{\textwidth}{!}{\input{../figures/jump_matrix.pgf}}
+    \caption{A series of filtered droplet trajectories arranged by increasing apoapse.
+The blue dots represent either the beginning and end of the experiment, or points at which the droplet is either coming into, or leaving contact with the surface.}
+    \label{fig:trajectories}
 \end{figure}
 
-\begin{figure}
+\begin{figure}[h]
     \centering
-    \input{../figures/y_filtered.pgf}
-       \caption{A simple EMA plot.\label{fig:ema2}}
+    \resizebox{\textwidth}{!}{\input{../figures/inverse_problem.pgf}}
+    \caption{A series of droplet trajectories showing the results of the parameter estimation.
+The trajectories are shown only up to the apoapse of the first bounce.
+The red lines show the ODE solution with given the MLE parameter vector.
+$\chi^2$ goodness-of-fit varies between $1 \times 10^{-5}$ and $1 \times 10^{-8}$ with the better fit occurring typically for the droplets with the lowest apoapses.}
+    \label{fig:inverse_problem}
 \end{figure}
 
-\begin{figure}
-    \centering
-    \input{../figures/dy_filtered.pgf}
-       \caption{A simple EMA plot.\label{fig:ema3}}
-\end{figure}
-
-Qualitively speaking, the 4th-order Savitsky-Golay, and Butterworth filters both produce the smooth derivatives we desire for for the optimization algorithem; but the small window-size needed for Butterworth filter tends to also prduce a noticible end effect.
-The Savitsky-Golay filter essentially uses a moving-window based on local least-squares polynomial approximations.
-It was shown that fitting a polynomial to a set of input samples and then evaluating the resulting polynomial at a single point within the approximation interval is equivalent to discrete convolution with a fixed impulse response \hl{[Savitsky, 1964]}.
-One property of this kind of low-pass filter is their tendency to respect waveform aplitudes, and so they are attractive in applications with having noisey signals with shaply pointed waveforms such as ultrsound or synthetic aperature radar \hl{[Schafer, 2011]}, however these filters tend to suffer from end-effects.
-Because Savitsky-Golay is a Finite Impulse Response (FIR) filter it requires datapoints to be equally spaced; to accomedate this we interpolate points between the small gaps which sometime occur in the tracking results from image analysis \hl{[ref]}.
-\hl{[Notes on window length, polynomial order]}.
-
-\subsection{Numerical Solution to the Equation of Motion}
-The equation of motion behaves stiffly due to the large disparity in Coulombic, image charge, and dielectrophoretic lenghtscales.
-We integrate it numerically using the \verb|odeint| \emph{Scipy} module.
-This is a shake-and-bake Python wrapper for the vernerable 1982 \emph{netlib ODEPACK} library double-precision \verb|lsoda| (Livermore Solver for Ordinary Differential equations with Automatic method switching for stiff and nonstiff problems) integrator \hl{[ref]}.
-The function switches between Adams (nonstiff) and Backwards Differentiation Formulas (BDF, stiff) according to the dyanmic value of a set of stiffness eigenvalues.
-
 \end{document}

### 2018-01-18 doc/manuscript/theory.tex
small update to theory

--- 2018-01-07 doc/manuscript/ef_notes.tex
@@
 \begin{document}
-\maketitle
+%\maketitle
 
-\begin{abstract}
-\noindent
-Notes on electric fields `n stuff.
-\end{abstract}
 \doublespacing
-\section{Introduction}
-\subsection{Spontaneous Droplet Jump}
-When a nonwetting, gravity dominated sessile drop or puddle initially at rest in the Cassie-Baxter state on a surface undergoes a large step reduction in Bond number, $\mathbf{Bo} = \rho g V_d^{2/3}/\sigma$, where $\rho$ is the liquid density, $g$ is the acceleration of gravity, $V_d$ is the droplet volume, and $\sigma$ is the liquid surface tension, it will spontaneously jump away from the surface.
-This was first observed experimentally by Kirko \emph{et al.} in 1970 [ref] and later by Wollman \emph{et al.} in 2006 in a set of experiments conducted using a $\mu$-gravity drop tower \hl{[ref]}.
-The kinetic energy of the jump is supplied by the defect in free surface energy as the new minimum energy surface equilibrium has approximately constant curvature \hl{[ref]}.
-If the viscous energy losses by shear, and internal flows during roll up are neglected, as well as energy lost due to the hysteresis of the dynamic contact line, then the energy relation is given by
-\[KE = SE_2 -SE_1 = [(\sigma A)_{gl} + (\sigma A)_{sg}]_2 - [(\sigma A)_{ls} + (\sigma A)_{gl} + (\sigma A)_{sg}]_1. \]
-From this is derived a simple model for the droplet initial jump velocity, given by
-\[U_0 = \left(\frac{\sigma g}{\rho}\right)^{1/4}\left[1-\cos \theta + 2 \left(\frac{\pi H^3}{V_d} \right)^{1/2} - 6^{2/3} \left( \frac{\pi H^3}{V_d} \right)^{1/3} \right]^{1/2}, \]
-where \hl{[etc, etc, etc...]}.
 
-%\begin{figure}
-%  \centerline{\includegraphics[height=7cm,width=7cm]%{e88_1_thumb.jpg}}
-%  \caption{Droplet jump velocities, effect of hysteresis for small droplet size}
-%\label{fig:jump_velocities}
-%\end{figure}
-
-The droplet `rolls up' as it jumps away from the surface due to radial motion of capillary wave away from the contact line.
-The characteristic time scale of the rolling up scales as $t_j \sim R_p/U ~(\rho H R^2_p/\sigma)^{1/2}$ [ref], which resembles the contact time, $\tau \approx 2.6(\rho R^3_d/\sigma)^{1/2}$ reported by Richard \emph{et al.} in 2002 for the related problem of droplets impacting hydrophobic surfaces in 1-g \hl{[ref]}.
-For droplets with radial symmetry and sufficiently high initial $\mathbf{Bo}$ these waves coalesce as a shock leading to geyersing and creation of satellite drops by the Rayleigh-Plateau breakup of the geyser.
-In the case of smaller jumping droplets, the capillary waves do not lead to geyersing, and are viscously damped to varying degrees during the brief freefall period of the drop tower.
-
-The spontaneous droplet jump phenomenon provides a useful window though which to study the dynamics of large-lengthscale capillary dominated droplets.
-The governing physics of such massive droplets (far beyond the 1-g sub-millimetric capillary lengthscale) utterly defy terrestrial expectations about the ways in which liquid droplets `should' behave, and also are of critical importance in a space exploration setting where the design of practical $\mu$-gravity  multiphase fluidic systems will no doubt be needed as humankind gradually extends her domain into our solar system.
-\section{Bouncing}
-For the sake of brevity we will henceforth use the slightly confusing term `drop' as shorthand to refer to a single $\mu$-gravity drop tower experiment.
-\section{Experimental Methods}
-Superhydrophobic substrates were placed on a drop tower rig platform.
-The rig is released by a solenoid chucked pin at the same moment the exterior drag shield is allowed to fall.
-This decouples drag acceleration felt by the drag shield from the experiment which experiences approximately $1 \cdot 10^{-6}$g of high quality freefall for the 2.1s required for the rig/drag shield assembly to reach the bottom of drop tower 6 floors below.
-
-The superhydrophobic surface was treated with PTFE spray for the first experiment of the day, and approximately every $3^{\mbox{rd}}$ drop following.
-The general properties and details of the fabrication of these superhydrophobic surfaces are discussed in Section \ref{sec.suphydro}.
-Shortly before each drop the surfaces were briefly rinsed with distilled water, and then dried under a fume hood for about 10 minutes.
-The drop rigs were balanced to prevent unintentional torques from contaminating the kinematics data (as angular velocity of the camera-fixed inertial reference with respect to the droplets during freefall would appear as a linear acceleration of the droplet).
-Surface charge density was measured on the superhydrophobic surface using a \emph{Simco-Ion} FMX-004 electrostatic fieldmeter.
-This measurement was done with the superhydrophobic surfaces connected by a conductive ground plane by conductive tape, far away from the presence of other conductors.
-Some additional notes on idiosyncrasies of determining surface voltages (and thence surface charge densities) on insulative dielectric surfaces are provided in Appendix \ref{sec.surface_charge}.
-
-Droplets of distilled water, in a range of volumes ($0 \leq R_d \leq 1$mL), were very carefully deposited on the superhydrophobic surface in the final 1-5 minutes prior to the drop using an ungrounded glass syringe with $\pm 1\mu$L accuracy.
-Red tracer dye was added to improve trajectory digitization.
-During the drop, droplet trajectories were observed using a \emph{Panasonic} HC-WX970 Camera, shooting in high-speed mode at 120 fps and and 1/3000s shutter speed.
-In a few cases where higher frame rates were needed a \emph{Nikon} 1 J1 camera with a 30mm telephoto lens was used, shooting at 400 fps.
-The experimental test cell was illuminated with a 12V 6000K \emph{SEALIGHT} Chip-On-Board LED strip with a thin semi-opaque plastic film covering to make the light diffuse.
-The effect of static charges on spontaneously jumped droplet trajectories was studied in terms of the parameters droplet volume $V_d$, surface charge density $\sigma$, and a dependent variable, initial droplet jump velocity $U_0$.
-Since $q$ cannot be directly measured insitu during a drop (as high-input resistance electrometers, being notoriously fickle instruments, are not well suited to sudden 15-g decelerations), it was inferred from the statistical distribution determined in corollary experiments.
-The droplet charge determination is discussed in slightly more detail in Appendix \ref{sec.drop_charge}.
-
-\subsection{Superhydrophobic surfaces} \label{sec.suphydro}
-Wetting hysteresis.
-Methods of fabrication, comparison of wetting properties.
-Comparison of jump velocities between surfaces.
-Methods for determination of properties, roll-off angle, contact angle using \emph{SE-FIT}.
-Cassie-wenzel transition.
-Damping.
-Droplets are dyed red to improve the quality of image thresholding when digitizing the droplet trajectories during data reduction.
-
-%\begin{figure}
-%  \centerline{\includegraphics[height=7cm,width=13cm]{modes.eps}}
- % \centerline{\includegraphics[height=7cm,width=7cm]{e88_1_thumb.jpg}}
-%  \caption{SEM images for sandpaper and laser etched acrylic surfaces}
-%\label{fig:SEM}
-%\end{figure}
-
-\subsection{Data Reduction}
-Digitization of droplet trajectories requires several steps of post-processing.
-Video is first decomposed into a sequence of still images.
-Trajectories are captured using the particle tracking module in \emph{Fiji}\hl{[ref]}, a derivative of the popular \emph{ImageJ}\hl{[ref]} package for scientific image analysis.
-The series is stabilized to remove the effect of drop transients from the kinetmatic data[ref].
-The series of still images is cropped, and the background (that is, the low-entropy pixels) of the series is removed using a builtin ``rolling ball'' algorithm.
-Each still is then split into its constituent RGB maps.
-In this case the green channel images contained the most information, so these were then globally thresholded using the Triangle algorithm to recover a map of the pixels corresponding to the droplet's approximate position in the original still.
-Finally ellipses are fitted to the pixel map stepping through the time series to determine the positions of the centroid, and the semi-major and minor axes of the droplets during the drop.
-The results of the particle capture in \emph{Fiji} are shown in Figure \ref{fig:fiji}.
-Out of plane motion for `weakly 3D' trajectories is inferred from the change in tracked area of the droplet.
-Droplet positional data was smoothed ex post facto using a Savitsky-Golay filter.
-Additional details regarding the data smoothing methodology are presented in Appendix \ref{sec.smoothing}.
-
-\section{EHD Forces}
+\section{Trajectory Model}
 As previously speculated the the force acting on the droplets as a surrogate for gravity are likely electrohydrodynamical in origin.
@@
 
-\section{A Simple Dynamical Model}
-\subsection{Trajectory Equation}
-\subsection{Numerical Methods}
-
-\section{Comparisons}
-\section{Stability}
-\section{Conclusions}
-\appendix
-
-\section{\\Droplet Charge} \label{sec.drop_charge}
-\subsection*{Parallel Plate Method}
-Since, by the earlier scaling, we presuppose the source of the droplet bouncing behavior to be primarily Coulombic in origin (as opposed to dielectrophoretic), the droplet must have some net charge in addition to the charge induced by the electric field.
-To measure this charge concurrent methodologies were used.
-The first method of determining the droplet net charge is observation of the deflection of the droplets in the region of a known uniform field in a fashion inspired by Millikan's famous experiment to determine the fundamental charge of the electron [ref].
-
-Droplets were jumped in freefall from a sandpaper superhydrophobic surface placed between the plates of a parallel plate capacitor of known uniform electric field.
-The surface was first deionized using a balanced \emph{Ptec} IN5120 DC air-ionizer to remove the effect of surface charge of the superhydrophobic surface from perturbing the otherwise uniform field set up between the parallel plates.
-A schematic of the parallel plate drop apparatus is shown in Figure \ref{fig:millikan}.
-Since the droplet initial velocity $U_0$ is parallel to the electric field, the droplets are inertial in the direction of the electric force, and neglecting the effect of image charges mirrored across the conductors, we can determine the magnitude of the droplet charge by a balance of Coulombic force and inertia given by the equation of motion
-
-\[ \frac{d^2y}{dt^2} = q\mathbf{E}. \]
-
-Since the drag is negligible in the inertial limit we can find the charge $q$ by fitting a second-order least squares polynomial to the measured droplet positions, equating the $t^2$ term to the constant acceleration, and dividing by the known, constant magnitude of the electric field.
-From a survey of literature we suppose the droplet charge, if they are indeed charged by contact with PTFE, to be some function of the droplet volume and the residence time on the superhydrophobic surface.
-However, sweeping though droplet volumes over a series of drop tower experiments we find little correlation between droplet volume  and net droplet charge.
-This is shown in figure \ref{fig:drop_charge}.
-
-A 200-880 VAC source with a full wave bridge rectifier circuit was prototyped on perf-board for initial experiments to measure droplet charge.
-The circuit was analyzed on an laboratory oscilloscope to verify that the AC component of the signal was appropriately small (13 mV at 35 kHz).
-Current was determined to be a relatively low 80 $\mu$A.
-The high-voltage source terminals were led to two parallel polished 150x150 mm aluminum plate electrodes.
-The electrodes were mounted on an insulated 80/20 extruded aluminum rail for ease of adjustment.
-All droplet charge experiments were conducted with an electrode spacing of 28.30 mm.
-With this spacing the calibrated electric field between the plates was $\mathbf{E} \approx 35$kV/m.
-The electrodes were electrically isolated from the drop rig by two alternating layers of 4 mm thick laser cut acrylic sheet and Kapton tape.
-Potential across the plates was measured periodically with a load-impedance corrected multimeter to account for battery depletion.
-The typical capacitor rise time of the plates was measured to be 1.4 s, thus to make the most economical use of the brief window a micro-gravity a weighted switch was set by hand prior to the drop to close the high-voltage circuit, but which passively safed the system at the resumption of 1-g conditions in the tower.
-The drop apparatus is shown in Fig.
-
-%\begin{figure}
-%  \centerline{\includegraphics[height=7cm,width=13cm]{modes.eps}}
- % \centerline{\includegraphics[height=7cm,width=7cm]{e88_1_thumb.jpg}}
-  %\caption{Parallel plate experimental apparatus.}
-%\label{fig:millikan}
-%\end{figure}
-
-%\begin{figure}
-%  \centerline{\includegraphics[height=7cm,width=13cm]{modes.eps}}
- % \centerline{\includegraphics[height=7cm,width=7cm]{e88_1_thumb.jpg}}
-  %\caption{Parallel plates: Droplet net charge vs volume.}
-%\label{fig:drop_charge}
-%\end{figure}
-
-A brief screening experiment was conducted which alternated the polarity of the field by switching the positive and negative terminal leads between plates.
-Qualitative observations of droplet electrode preference seem to indicate that the assumption of small polarization stress was well founded.
-Following this a orthogonal array $3^2$ factorial design experiment with two replicates was conducted to test the effect of varying droplet volume and surface stay time on net charge at the time of jumping.
-It was hypothesized in accordance with previous studies \cite{Choi:2013dg}, that net charge would increase for levels of both factors.
-The results of the factorial experiment are presented in Fig.
-\ref{fig:chart1}.
-ANOVA analysis in \emph{R} of the linear multiple regression model for the data set indicates that neither droplet volume ($p=0.105$), nor surface stay time ($p=0.358$) is significant at the 95\% confidence level.
-The overall model F-statistics (2.177 in 2 and 13 degrees of freedom), and coefficients of determination ($r^2 = 0.2509$) indicate that the linear model neither fits the data particularly well, nor does it offer an improvement over the mean model.
-The mean charge was determined to be positive $2.3 \cdot 10^{-11}$ C, with a standard deviation of $1.8 \cdot 10^{-11}$ C.
-
-The failure of the model to describe the data raises interesting questions about the validity of our initial assumptions.
-Typical Reynolds numbers ($R_e=280$ average) indicate the general validity of the assumed quadratic drag model.
-The drag scale quantity given by Eqn.
-\ref{eqn:drag} was much less than 1 for all test runs, with mean value of $1.0\cdot 10^{-2}$ and a standard deviation of $2.0\cdot 10^{-3}$, which adds credence to a force balance of pure inertia and electrostatic force.
-
-One obvious issue, in retrospect, is that while we know the characteristic charging time for the droplets to be some function of droplet volume, \hl{[it has been shown to have a time constant dramatically smaller than that of a typical experimental timescale]} so we might have looked only for the charge as a function of volume, both on physical grounds and due to the conflation of the variables.
-
-Also of concern is that droplets in three of eighteen runs exhibited accelerations opposite to the expected direction.
-There is no pattern to the distribution of anomalous droplet accelerations, as they all occurred at unique level combinations.
-There are only four obvious ways of explaining this anomaly.
-The first is that the electric field is in fact non-uniform and polarization stress is non-negligible in this geometry.
-This option seems unlikely owing to the fundamental design of the experimental apparatus; \hl{[see figure from Agros2D FEM solution]}.
-A second possibility is that the few contrarian droplets actually accumulated net negative charge, instead of the net positive charge to be expected on the basis of evidence from some of the aforementioned studies.
-This is not impossible, and would also go some length to explain the variance in the measured charge generally.
-A third possibility is that another force neglected in this analysis, with some component in the direction opposite of the electric field, has an $\sim \mathcal{O}(1)$ magnitude.
-In principle this could for instance include the image charges which will subject the droplets to a force $\mathbf{F} = q^2/4 \pi \epsilon_0 d$ when ``close'' to one of the conductive plates (that is, when the plate can be treated as an infinite grounded conductor).
-However, this formulation of the image charge effect clearly does not describe the force close to the centerline where the Green's function needs to add additional sets of images to satisfy the boundary conditions of $\nabla^2 \varphi = 0$ in this geometry.
-To the knowledge of the author there is not a convergent series solution in the parallel plates geometry as yet.
-
-The droplet positive net charge developed by contact with a PTFE surface corresponds to findings elsewhere in literature \cite{Choi:2013dg} \cite{Miljkovic:2013dg} \cite{Moreno-Villa:1998dg}.
-The smallest droplet size treated in the present work is several times larger than the largest in any of comparable study.
-The most relevant comparison found droplet static charge of 2.5e-10 C for 10 $\mu$L droplets charged by pipetting from a PTFE tipped needle \cite{Choi:2013dg}.
-The present results mean charge level of 2.3e-11 C is, within error, roughly six times smaller than the cited study.
-
-\subsection*{Direct Measurement}
-A second approach to determining the net droplet charge is by direct measurement in a shielded Faraday cup using an extremely high input resistance electrometer, specifically a \emph{Keithly} 616 digital electrometer.
-\hl{[note on operational philosophy, data collection].
-Correlation of net charge to droplet volume is shown again for in figure} \ref{fig:electrometer}.
-
-%\begin{figure}
-%  \centerline{\includegraphics[height=7cm,width=13cm]{modes.eps}}
-%  \centerline{\includegraphics[height=7cm,width=7cm]{e88_1_thumb.jpg}}
- % \caption{Electrometer: charge vs. volume.}
-%\label{fig:electrometer}
-%\end{figure}
-
-[Discussion on discrepancy between the two approaches.]
-
 \end{document}

### 2018-01-20 doc/manuscript/abstract.tex
added additional figures, and theory

\documentclass[10pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\author{Erin Schmidt}
\title{Abstract}
\begin{document}
Our terrestrially born intuition about how liquids flow is easily confounded in a low-gravity environment. This should come as little surprise, as we are creatures evolved at the bottom of a steep gravity well; gravity is natural to us. However when the magnitude of the gravity body-force becomes small, other forces come into play in fluid dynamics which are otherwise negligible, relatively speaking, under normal circumstances in 1-g. This 1-g cognitive bias leads to a plethora of problems which are both trivially easy to solve in 1-g, and which despite decades of study continue to elude solutions in a low-gravity context. One example of these problems is the so-called "phase separation" problem of separating a gas phase from a multi-phase flow (or the reverse case) without the aid of gravitational buoyancy. Sans buoyancy otherwise mundane activities such as venting a gas or settling a liquid in a tank become problematic. Trapped bubbles can vapor lock ECLSS (Environmental Control and Life Support), power, or propulsion systems. Issues of phase separation have so bedeviled human endeavors in space that an entire Apollo Saturn 1B mission (AS-203) was earmarked to study them. This problem has for some time motivated a quest for substitute body forces, and the present work follows in that august tradition.

We investigate the dynamics of spontaneous jumps of water droplets from electrically charged superhydrophobic dielectric surfaces during a sudden step reduction in gravity level. In the brief free-fall environment of a drop tower, with a non-homogeneous external electric field (with strengths ~0.39-2.36 kV/cm) arising due to dielectric surface charges, body forces acting on the jumped droplets are primarily supplied by polarization stress and Coulombic attraction instead of gravity. This electric body force leads to a droplet bouncing behavior similar to well-known phenomena in 1-g, though occurring for much larger droplets (~0.5 mL). We show a simple model for the phenomenon, its scaling, and asymptotic estimates for droplet time of flight. The droplet net charge, estimated to be on the order of 1E-9 C, is field induced rather than by contact charging at the (PTFE coated) hydrophobic interface. In 1-g, for Weber numbers > 0.4, impact recoil behavior on a super-hydrophobic surface is normally dominated by damping from contact line hysteresis. However, at the low Bond and Ohnesorge numbers occurring in free-fall, the droplet impact dynamics additionally include electrohydrodynamic surface wettability effects. This is qualitatively discussed in terms of trends in coefficients of restitution and dimensionless contact time. 
\end{document}

### 2018-01-20 doc/manuscript/introduction.tex
added additional figures, and theory

@@
 \usepackage{setspace}
-\author{Erin Schmidt}
+\title{\textsf{\textbf{Droplet Electro-Bouncing in Low-Gravity}}}
+\vspace{-25mm}
+\author{Erin S. Schmidt, Mark M. Weislogel}
+\date{}
 
+\usepackage{abstract}
+\renewcommand{\abstractnamefont}{\normalfont\bfseries}
+\renewcommand{\abstracttextfont}{\normalfont\small\itshape}
+
+\usepackage{setspace}
 \newlength\figureheight
@@
 \begin{document}
+\maketitle
 \doublespacing
+
+\begin{abstract}
+\noindent
+We investigate the dynamics of spontaneous jumps of water droplets from electrically charged superhydrophobic dielectric surfaces during a sudden step reduction in gravity level.
+In the brief free-fall environment of a drop tower, with a non-homogeneous external electric field (with strengths ~0.39-2.36 kV/cm) arising due to dielectric surface charges, body forces acting on the jumped droplets are primarily supplied by polarization stress and Coulombic attraction instead of gravity.
+This electric body force leads to a droplet bouncing behavior similar to well-known phenomena in 1-g, though occurring for much larger droplets ($\sim$ 0.5 mL).
+We show a simple model for the phenomenon, its scaling, and asymptotic estimates for droplet time of flight.
+The droplet net charge, estimated to be on the order of 1E-9 C, is field induced rather than by contact charging at the (PTFE coated) hydrophobic interface.
+In 1-g, for Weber numbers $>$ 0.4, impact recoil behavior on a super-hydrophobic surface is normally dominated by damping from contact line hysteresis.
+However, at the low Bond and Ohnesorge numbers occurring in free-fall, the droplet impact dynamics additionally include electrohydrodynamic surface wettability effects.
+This is qualitatively discussed in terms of trends in coefficients of restitution and dimensionless contact time.
+\end{abstract}
+
 \section{Introduction}
+Our terrestrially born intuition about how liquids flow is easily confounded in a low-gravity environment.
+This should come as little surprise, as we are creatures evolved at the bottom of a steep gravity well; gravity is natural to us.
+However when the magnitude of the gravity body-force becomes small, other forces come into play in fluid dynamics which are otherwise negligible, relatively speaking, under normal circumstances in 1-g.
+This 1-g cognitive bias leads to a plethora of problems which are both trivially easy to solve in 1-g, and which despite decades of study continue to elude solutions in a low-gravity context.
+One example of these problems is the so-called "phase separation" problem of separating a gas phase from a multi-phase flow (or the reverse case) without the aid of gravitational buoyancy.
+Sans buoyancy otherwise mundane activities such as venting a gas or settling a liquid in a tank become problematic.
+Trapped bubbles can vapor lock ECLSS (Environmental Control and Life Support), power, or propulsion systems.
+Issues of phase separation have so bedeviled human endeavors in space that an entire Apollo Saturn 1B mission (AS-203) was earmarked to study them.
+This problem has for some time motivated a quest for substitute body forces, and the present work follows in that august tradition.
+
 When asked to name one of the biggest challenges to living in

### 2018-01-20 doc/manuscript/theory.tex
added additional figures, and theory

@@
 \usepackage{verbatim}
+\usepackage{pgfplots}
 \usepackage{pgf}
+\usepackage[english]{babel}
+\usepackage{amsmath}
+\usepackage{amsfonts}
+\usepackage{amssymb}
+\usepackage{graphicx}
+\usepackage{setspace}
 \lstset{
@@
 \section{Trajectory Model}
-As previously speculated the the force acting on the droplets as a surrogate for gravity are likely electrohydrodynamical in origin.
-In the hopes of unraveling the underlying mechanism for the electro-bouncing we turn to the electrodynamical approximation of fluids under the influence of electric fields.
-To that effect, what follows is a condensed overview of mathematical description of basic electrohydrodynamic flows.
+\subsection{Forces and the Equation of Motion}
+Treating a droplet as a particle, with radius $R_d$, the  equation of motion for a charged droplet translating vertically along the central axis of a finite square charged dielectric sheet is given by
+\begin{equation}
+m y'' = - \mathbf{F}_D - \mathbf{F}_E, \hspace{5 mm} y(0) = R_d, \hspace{5 mm} y'(0) = U_0,
+\label{gov_eqn}
+\end{equation}
+where $m$ is the droplet mass, $y'' = \frac{d^2 y}{d t^2}$ is the droplet acceleration, $\mathbf{F}_D$ is the drag force, and $\mathbf{F}_E$ is the electrostatic force.
+The initial conditions are such that the droplet leaves its resting position $R_d$ at $t=0$, with initial velocity $U_0$.
+The signs of the forces on the right side of Equation \ref{gov_eqn} indicate that they act in the opposite direction of the droplet motion.
+In this section we aim specifiy models for the various forces in this equation.
+
+If we assume an intermediate range of Reynolds numbers $\mathbb{R}\mbox{e} \equiv \frac{2UR_d}{\nu}$, $1 <\mathbb{R}\mbox{e} < 1000 $ then the drag is quadratic,
+\begin{equation*}\label{drag_force}
+\mathbf{F}_D = \frac{1}{2}C_D \rho A {y'}^2,
+\end{equation*}
+where $C_D$ is the drag coefficient, $\rho$ is the density of the sorrounding fluid medium (air, in this case), and $A$ is the frontal area of the droplet.
+For this range of Reynolds numbers we may also approximate the drag coefficient by the well known Abraham correlation \hl{ref.}
+\[C_D = \frac{24}{9.06^2} \left( 1 + \frac{9.06}{\sqrt{\mathbb{R}\mbox{e}}} \right)^2\]
+
+Modeling the electrostatic force is somehwhat more involved, but we will adopt the standard electrohydrodynamic (EHD) approximation model because of the dramatic simplifications it offers \hl{ref}.
 We first assume a DC electric field, such that $Re \langle \epsilon \rangle \approx  \mbox{constant}$, where $\epsilon$ is the dielectric permittivity of the respective media.
 We also assume that currents are small such that the effects of magnetic fields can be neglected.
-For the validity of this assumption to hold the characteristic time scale for electrical phenomena $\tau_e = \epsilon \epsilon_0/\sigma_e \ll 1$, where we note that $\tau$ is the ratio of absolute dielectric permittivity $\kappa = \epsilon \epsilon_0$, to conductivity $\sigma_e$, of the medium [ref].
-Given the respective conductivity, and permittivity of air ($\sigma_e = 2.5 \cdot 10^{-16}$ $\Omega^{-1} cm^{-1}$), we estimate $\tau_e \approx 400$s.
-This assumption also allows us to assume that the net charge present in the medium surrounding the droplets remains approximately constant during the typical time interval of a $\mu$-gravity experiment, and no transfers of charge occur after the droplet leaves the surface.
-\hl{[lol, check these numbers...]}
+For the validity of this assumption to hold the characteristic time scale for electrical phenomena $\tau_e = \epsilon \epsilon_0/\sigma_e \ll 1$, where $\tau$ is the ratio of absolute dielectric permittivity $\kappa = \epsilon \epsilon_0$, to conductivity $\sigma_e$, of the medium [ref].
+\hl{Given the respective conductivity, and permittivity of water ($\sigma_e = 2.5 \cdot 10^{-4}$ $\Omega^{-1} \mbox{cm}^{-1}$), we estimate $\tau_e \approx 7 \times 10^{-8}$ s}.
+This assumption also allows us to assume that the net charge present in the medium surrounding the droplets remains approximately constant during the typical time interval of a low-gravity experiment, and no transfers of charge occur after the droplet leaves the surface.
 
-\subsection{Maxwell Stress}
 If we suppose that electrical forces acting on free charges and dipoles in a fluid are transferred directly to the fluid itself, then this overall electrical body force will be the the divergence of the Maxwell stress tensor $\tau_m $, by
 
-\[ \mathbf{F}_e = \nabla \cdot \tau_m = \nabla \cdot \left( \epsilon \epsilon_0 \mathbf{E} \mathbf{E} - \frac{1}{2} \epsilon \epsilon_0 \mathbf{E} \cdot \mathbf{E} \delta \right) ,\]
-where $\mathbf{F}_e$ is the electric body force per unit volume, \hl{$\rho_f$ is the free charge density}, and $\delta$ is the delta function.
-The product of the electric field vectors is the dyadic product.
+\[ \mathbf{F}_E = \nabla \cdot \tau_m = \nabla \cdot \left( \epsilon \epsilon_0 \mathbf{E} \mathbf{E} - \frac{1}{2} \epsilon \epsilon_0 \mathbf{E} \cdot \mathbf{E} \delta \right) ,\]
+where $\mathbf{F}_E$ is the electric body force per unit volume, and $\delta$ is the delta function. The product of the electric field vectors is the dyadic product.
 
-The classical Korteweg-Helmholtz force density formulation of the Maxwell stress tensor is usually expressed as 
-\begin{equation}
-\mathbf{F}_e = \rho_f \mathbf{E} + \frac{1}{2} \left| \mathbf{E} \right|^2 \nabla \epsilon - \nabla \left( \frac{1}{2} \rho \left( \frac{\partial \epsilon}{\partial \rho} \right)_T \left| \mathbf{E} \right|^2 \right) ,
+The classical Korteweg-Helmholtz force density formulation of the Maxwell stress tensor is usually expressed as \hl{[ref]}
+\begin{equation}\label{force_density}
+\mathbf{F}_E = \rho_f \mathbf{E} + \frac{1}{2} \left| \mathbf{E} \right|^2 \nabla \epsilon - \nabla \left( \frac{1}{2} \rho \left( \frac{\partial \epsilon}{\partial \rho} \right)_T \left| \mathbf{E} \right|^2 \right) .
 \end{equation}
-and $\rho$ is the density of the dielectric fluid[ref].
 
@@
 This force is widely termed the dielectrophoretic force (DEP).
-The third term describes forces due to electrostriction, however in our case $\left( \frac{\partial \epsilon}{\partial \rho} \right)_T = 0$ due to the  incompressibility of the fluid[ref].
-While it is a relatively rigorous approach, and a useful conceptual model, evaluating the force density in this fashion can be somewhat onerous.
+The third term describes forces due to electrostriction.
+It has been noted by Melcher and Hurwitz that the electrostriction term is the gradient of a scalar and can thus be cannononically lumped togeather with the hydrostatic pressure for incompressible fluids)\hl{[ref]}; we neglect it in our analysis.
 
-\subsection{Dielectrophoresis}
-An alternative approximation for the polarization stress is to idealize the droplet as a simple dipole using the effective dipole moment method first suggested by Pohl and Jones\hl{[ref][ref]}.
+It is common to approximate the polarization stress by idealizing the droplet as a simple dipole using the effective dipole moment method first suggested by Pohl and Jones\hl{[ref][ref]}.
 This approach can be related back to the force density by means of a Taylor series expansion of $\mathbf{E}$ in the limit of a small gradient \hl{[ref]}.
-The DEP force is distinct from the Coulombic force in that net charge is not required, and that the force vector goes in the direction of steepest descent of the field, $\nabla \left| \mathbf{E} \right|^2$, rather than in the direction of $\mathbf{E}$.
-The DEP force is related to the dipole moment (induced or polarized) of polarizable media which has a tendency to align the dipole with the electric field.
+The DEP force is distinct from the Coulombic force in that net charge is not required, and that the force vector goes in the direction of the gradient of the field, $\nabla \left| \mathbf{E} \right|^2$, rather than in the direction of $\mathbf{E}$.
+The DEP force is related to the dipole moment (induced or permanent) of polarizable media which has a tendency to align the dipole with the electric field.
 If there is a gradient in the field then for a finite separation of charge one end of the dipole will feel a stronger electric field than the other, resulting in a net force.
-Whether the force is positive or negative in the direction of the electric field gradient depends on the difference of dielectric permittivites between the fluids, rather than on the polarity of $\mathbf{E}$.
+Whether the force is positive or negative in the direction of the electric field gradient depends on the difference of dielectric permittivites between the fluids, rather than on the polarity of $\mathbf{E}$ itself.
 It bears repeating that droplets will polarize in a uniform field, but since there is no gradient in the field the forces felt by the dipoles are symmetric and there is no net force.
-The dipole moment of a spherical dielectric particle immersed in a dielectric medium is given by
+The dipole moment of a spherical linear-dielectric particle immersed in a dielectric medium is given by
 \begin{equation} \label{dipole_m_1}
@@
 \end{equation} 
-where $\mathbf{P} = \left(\kappa_1 - 1 \right) \epsilon_0 \mathbf{E}_{iz}$ is the polarization moment, and $R_d$ is the particle radius, \hl{($\kappa_1$ being the relative dielectric constant of the medium}, and $\mathbf{E}_{iz}$ is the $z$-coordinate component of the electric field internal to the sphere, assuming the external electric field to be oriented parallel to the $z$-axis).
+where $\mathbf{P} = \left(\kappa_1 - 1 \right) \epsilon_0 \mathbf{E}_{iz} = \chi_e \epsilon_0 \mathbf{E}_{iz}$ is the polarization moment, and $R_d$ is the particle radius, \hl{$\kappa_1 = \frac{\epsilon}{\epsilon_0}$ being the relative dielectric constant of the medium (air in this case)}, $\chi_e = \kappa_1 - 1$ being the electric susceptibility of the dielectric medium, and $\mathbf{E}_{iz}$ is the $z$-coordinate component of the electric field internal to the sphere, assuming the external electric field to be oriented parallel to the $z$-axis.
 The excess polarization $\mathbf{P}_e$, in the sphere is given by
@@
 \end{equation}
-where $\kappa_2$ is the dielectric constant of the particle. Taking together equations \ref{dipole_m_1}, and \ref{polarization} we find that the effective dipole moment of the particle is given by 
+where $\kappa_2$ is the relative dielectric constant of the spherical particle.
+Taking together equations \ref{dipole_m_1}, and \ref{polarization} we find that the effective dipole moment of the particle is given by
 \begin{equation}\label{dipole_m_2}
@@
 \begin{eqnarray} \label{dep_force}
-\mathbf{F}_{dep} &=& \left( \mathbf{P}_e \cdot \nabla \right) \mathbf{E}\\
-&=& 2 \pi R_d^3 \kappa_1 \epsilon_0 \left( \frac{\kappa_2 - \kappa_1}{\kappa_2 + 2 \kappa_1} \right) \nabla E^2,
+\mathbf{F}_{DEP} &=& \left( \mathbf{P}_e \cdot \nabla \right) \mathbf{E} \nonumber \\
+&=& 2 \pi R_d^3 \kappa_1 \epsilon_0 K \nabla E^2,
 \end{eqnarray}
-where it is a useful shorthand to refer to the permittivity ratio by $K = \frac{\kappa_2 - \kappa_1}{\kappa_2 + 2 \kappa_1}$, which is also known as the Clausius-Mossotti factor.
-In cases where $K < 0$, or $K>0$ the particle will be repelled or attracted to regions of strong field respectively.
-In our experiment, taking the relative dielectric constants to be $\kappa_1 \approx 1$ and $\kappa_2 \approx 80$, we have $K \approx 0.96$.
-One limitation of the effective dipole moment approximation of the DEP force is that it requires an assumption of small physical scale of the particle relative to the lengthscale of nonuniformity of the field, which in this case we take to be the length of the charged superhydrophobic surface ($L,H =25$mm $\gg a \approx 2.5$mm).
-Though the effective dipole moment is a successful model due in large part to its simplicity, it can be readily extended to include higher-order multipole effects, and non-spherical particles (oblate and prolate spheroids).
-An excellent summary of DEP theory in terms of the effective dipole moment is given in \hl{[ref]}.
-\hl{[Some notes on scaling ...]}
+where it is an asthetically pleasing shorthand to refer to the permittivity ratio by $K = \frac{\kappa_2 - \kappa_1}{\kappa_2 + 2 \kappa_1}$, which is also known as the Clausius-Mossotti factor.
+In cases where $K <$ 0, or $K>$ 0 the particle will be repelled or attracted to regions of strong field respectively.
+In our experiment, taking the relative dielectric constants to be $\kappa_1 \approx$ 1 and $\kappa_2 \approx$ 80, we have $K \approx$ 0.96.
+We also note that the equivalent dipole approximation requires an assumption of small physical scale of the particle relative to the lengthscale of nonuniformity of the field, which in this case we take to be the length of the charged superhydrophobic surface ($L =$ 25 mm $\gg a \approx$ 2.5 mm).
 
-\subsection{Forces due to Image Charges in the Dielectric}
+When the droplet is close to the dielectric surface, the net charge on the droplet will tend to polarize the dielectric, perturbing the electric field.
+The polarization bound charge in the dielectric will be of the opposite sign of the net droplet charge and thus there will be a force of attraction.
+This so-called image force is a correction to the Colomb force due to the external electric field only, and can be found by the method of images \hl{ref}.
+The image force $\mathbf{F}_I$, is given by
 
-\section{The Electric Field}
-\begin{comment}
-Being thus armed with the assumption of a purely electrostatic problem (the electric field is conservative, that is $\nabla \times \mathbf{E} = 0$, where $\mathbf{E}$ is the electric field) we can describe the electric field by the Laplace equation for the electric potential.
-In the case of the volume charge density of the bulk medium to being zero, the divergence of the electric field is zero and we have
+\begin{equation}
+\mathbf{F}_I = \frac{k q^2}{16 \pi \epsilon_0} y^{-2} \hat{\mathbf{j}},
+\label{image_force}
+\end{equation}
+where the factor $k$ is a function of the dielectric surface susceptibility $k = \frac{\chi_e}{\chi_e + 2}$, and $\hat{\mathbf{j}}$ is a unit vector normal to the dielectric surface.
 
+By substituting Equations \ref{dep_force}, \ref{image_force} into Equation \ref{force_density} we have
+\begin{eqnarray*}
+ \mathbf{F}_E &=& q \mathbf{E} + \mathbf{F}_{DEP} + \mathbf{F}_I \\
+ &=& q \mathbf{E} + \frac{k q^2}{16 \pi \epsilon_0 } y^{-2} \hat{\mathbf{j}} + 2 \pi R_d^3 \kappa_1 \epsilon_0 K \nabla E^2, 
+\end{eqnarray*}
+
+and the 1-D governing equation becomes
+\begin{eqnarray} \label{gov_eqn_subs}
+&m y'' = - \frac{1}{2} C_D \rho A {y'}^2 - q E - \frac{k q^2}{16 \pi \epsilon_0} y^{-2}- 2 \pi R_d^3 \kappa_1 \epsilon_0 K \nabla E^2,& \nonumber \\
+&y(0) = R, \hspace{1 mm} y'(0) = U_0 .&
+\end{eqnarray}
+
+By comparing DEP and Coulombic terms in Equation \ref{gov_eqn_subs}, we note that a condition to neglect the DEP term is
 \begin{eqnarray}
-\mathbf{E} &=& -\nabla \varphi \\
-\nabla \cdot \mathbf{E} &=& 0\\
-\nabla \cdot \mathbf{E} &=& - \nabla \cdot \nabla \varphi = \nabla^2 \varphi = 0,
+1 &\gg& \frac{R_d^2 \kappa_2 \epsilon_0 K E_0}{q} \nonumber
 \end{eqnarray}
-it being convenient to solve the field in terms to $\varphi$ due to the form of the \emph{boundary conditions} usually given by
-\begin{enumerate}
-\item For finite charge distributions, the potential $\varphi$ goes to zero at infinity, is constant throughout a conductors, and is continuous across physical boundaries.
-\item The normal component of the displacement vector $\mathbf{D}$, differs on two sides of a boundary by the free charge density $\rho_f$ residing on the boundary.
-\item The tangential component of the field intensity $\mathbf{E}$ is continuous across a boundary.
-\end{enumerate}
+As this condition holds in all cases under study we herefore neglect the DEP force in our analysis.
 
-The in lieu to an analytical solution to Laplace's equation on a dielectric half-space domain by separation of variables or other methods we might try modeling the static charge distribution by a series of Dirac delta funtions after the fasion of a Green's function.
-In the 2D case we have,
+\subsection{The Electric Field}
+If we consider the charged dielectric surface of our experiments to be a square sheet of charge lying in the $xz$-plane with width $L$, the symmetry of the problem happily lets us obtain the $y$-component of the electric field $\mathbf{E}_y$ by direct integration \hl{ref}.
+In particular it is easy to constuct the electric field due to a finite plane of charge by supoerposition of the electric fields of a series of line charges.
+By symmetry the electric field points along the y-axis; for a point along the $y$-axis the position vector is $\mathbf{r} = \left( x^2 + y^2 + z^2 \right)^{1/2} \hat{\mathbf{r}}$.
+The $y$-component of $\mathbf{E}$ is given by $\mathbf{E}_y \cos \theta = \mathbf{E}_y y/ \mathbf{r}$.
+Then if the charge in an element of area, $dx dz$ is $\sigma dx dz$ the electric field $\mathbf{E}_y$ is
+\[ \mathbf{E}_y = \frac{\sigma y}{4 \pi \epsilon_0} \int^{L/2}_{L/2} \int^{L/2}_{L/2} \left( x^2 + y^2 + z^2 \right)^{3/2} dx dz \hspace{1mm}\hat{\mathbf{r}} 
+,\]
+where $\sigma$ is the surface charge density. This can be easily integrated to obtain an expression for the electric field in terms of $y$, 
 \begin{equation}
-\varphi(x,z) = \frac{z}{\pi}\int^\infty_{-\infty} \frac{\rho(x^\prime)}{(x-x^\prime)^2 + z^2}dx^\prime
-\end{equation}
-\end{comment}
-We are faced with the need to compute the total electric field arising from the presence of free charge on the surface of a polarizable dielectric. In the electrostatic case we have
-\begin{eqnarray}
-\nabla \times \mathbf{E(r)}&=&0 \\
-\nabla \cdot \mathbf{D(r)}&=&\rho(\mathbf{r}).
-\end{eqnarray}
-If the dielectric is linear and isotropic then the displacement field is 
-\begin{equation}\label{displacement}
-\mathbf{D(r)} = \epsilon(\mathbf{r})\mathbf{E}(\mathbf{r}).
-\end{equation}
-Given that the electric field is defined as the gradient of the scalar potential, $\mathbf{E}=-\nabla \varphi $, we can write equation \ref{displacement} as 
+\mathbf{E}_y = \frac{\sigma y}{ \pi \epsilon_0} \tan^{-1} \left( \frac{L^2}{y \sqrt{2L^2 + y^2}}\right)
+.\end{equation}
+
+By taking Taylor series expansions in large and small limits we can intuit a bit about the behavior of this field.
+In the limit $L \rightarrow \infty, \hspace{1mm} y \ll L$ the argument of the function tends towards infinity and
+\[ \lim_{x\to\infty} \tan^{-1}(x) = \frac{\pi}{2}
+,\]
+and thus
 \begin{equation}
-\nabla \cdot \left[\epsilon(\mathbf{r})\nabla \varphi (\mathbf{r}) \right] = -\rho (\mathbf{r}).
-\end{equation}
-This is a form of \emph{Poisson's equation}.
-Our general method for finding the electric field, will solve $\varphi (\mathbf{r})$ on a half-space domain with permittivities $\epsilon_1$, $\epsilon_2$ for a point source using the free-space \emph{Green's function}.
-We can then find the total electric field by superposition of the individual Green's functions by direct integration.
-
-The non-homogoneous part of the Poisson's equation for the electrostatic potential is a Green's function, denoted by $\mathbf{G}(\mathbf{r} | \mathbf{r^\prime})$, where $\mathbf{G}$ satisfies Poisson's equation at $\mathbf{r}$ when the point source is located at $\mathbf{r^\prime}$ such that
+\mathbf{E}_y \approx \frac{\sigma}{4 \pi \epsilon_0} \hat{\mathbf{j}} \hspace{10mm} y \ll L
+,\end{equation}
+which is constant, and equivalent to the electric field due to an infinite plane of charge. In the limit of $y \gg L$, the argument of the arctangent function can be approximated by
+\[ \frac{L^2}{2 y \left( 2 L^2 + 4 y^2\right)^{1/2}} = \frac{L^2}{4 y^2 \left( 1 + L^2/2y^2 \right)^{1/2}} \approx \frac{L^2}{4 y^2}
+.\]
+For small $x$, $\tan^{-1}(x) \sim x$ and we thus find the familiar electric field due to a point charge
 \begin{equation}
-\nabla^2 \mathbf{G}(\mathbf{r} | \mathbf{r^\prime}) = -\delta( \mathbf{r} - \mathbf{r^\prime}).
-\end{equation}
-Using the identity for the position vector $\nabla$
-
+\mathbf{E}_y \approx \frac{\sigma L^2}{4 \pi \epsilon_0} y^{-2} \hat{\mathbf{j}} \hspace{10mm} y \gg L
+.\end{equation}
+With the characteristic electric field given by $E_0 = \frac{\sigma}{4 \pi \epsilon_0}$, both these regiemes can be clearly seen in the plot of $\mathbf{E}_y$ shown in Figure \ref{fig:E0}.
 \begin{figure}[htb]
@@
     \input{../figures/E0.pgf}
-    \caption{A simple EMA plot.\label{fig:E0}}
+    \caption{A log-log plot of the magnitude of the non-dimensional electric field, $\mathbf{E}_y$.\label{fig:E0}}
 \end{figure}
 
+\subsection{Scaling}
+Introducing scaled variables
+\[ \bar{t} = \frac{t}{t_c}, \hspace{10 mm} \bar{y} = \frac{y}{y_c}, \]
+where $y_c$ and $t_c$ are characteristic length and time scales respectively, and using the cooridnate transformation $y(0) - R = 0$, the governing equation becomes
+\begin{eqnarray}
+& \bar{y}'' = - \frac{1}{2} \frac{C_D \rho A y_c}{m} \bar{y}'^2
+- \frac{q E_0 t_c^2}{m y_c} \bar{E} 
+- \frac{k q^2 t_c^2}{16 \pi \epsilon_0 R^2 m y_c} \frac{1}{\left( \frac{y_c}{R} \bar{y} + 1 \right)^2}, & \nonumber \\
+& \bar{y}(0) = 0, \hspace{1 mm} \bar{y}'(0) = \frac{U_0 t_c}{y_c} .&
+\end{eqnarray}
+We note several dimensionless groups
+\[ \mathbf{\Pi}_1 = \frac{C_D \rho A y_c}{2 m}, \hspace{5 mm}
+\mathbf{\Pi}_2 = \frac{q E_0 t_c^2}{m y_c}, \hspace{5 mm}
+\mathbf{\Pi}_3 = \frac{k q^2 t_c^2}{16 \pi \epsilon_0 R^2 m y_c}, \hspace{5 mm}
+\mathbf{\Pi}_4 = \frac{y_c}{R}.\]
+
+\subsubsection{Inertial Electro-Image Limit}
+In the limit of small $y, \hspace{1mm} t$ we expect intertia to scale as Coulombic and image force. With $y_c \sim U_0 t_c$ and picking $t_c$ such that Coulombic force is $\mathcal{O}(1)$
+\[ t_c \sim \frac{m U_0}{q E_0}, \hspace{5 mm}
+y_c \sim \frac{m U_0^2}{q E_0} .
+\]
+With these scales the governing equation then becomes
+\begin{eqnarray}
+& \bar{y}'' = -1 - \mathbb{I}\mbox{m} \frac{1}{\left( \mathbb{E}\mbox{u}\bar{y} + 1 \right)^2} ,& \nonumber \\
+& \bar{y}(0) = 0, \hspace{1 mm} \bar{y}'(0) = 1 .&
+\end{eqnarray} 
+with 
+\[ \mathbb{I}\mbox{m} \equiv \frac{k q}{16 \pi \epsilon_0 R_d^2 E_0} = \mathbf{\Pi}_3, \hspace{5 mm}
+\mathbb{E}\mbox{u} \equiv \frac{m U_0^2}{q E_0} = \mathbf{\Pi}_4 ,
+\]
+where $\mathbb{I}\mbox{m}$ is the Image number, and denotes the ratio of image forces to the Coulombic force of the unperturbed field, and where where $\mathbb{E}\mbox{u}$ is the electrostatic Euler number, and is a ratio of inertia to electrostatic force.
+
+\subsubsection{Inertial Electro-Viscous Limit}
+In the limit of large $y, \hspace{1mm} t$ we expect droplet inertia to scale as Coulombic force and drag. In this case there are several obvious choices of scales:
+\begin{enumerate}
+\item $y_c \sim U_0 t_c$ and make Coulomb force $\mathcal{O}(1)$.
+\item $y_c \sim R_d$ or $L$, $t_c \sim \frac{L}{U_0}$ but this makes the governing equation singular.
+\item $y_c \sim R_d$ or $L$, $t_c \sim \left( \frac{L m}{q E_0} \right)^{1/2}$.
+\item $y_c \sim R_d$ or $L$, and making Coulomb force $\mathcal{O}(1)$.
+\end{enumerate}
+
+In Case 3, the characterisitc time is $t_c \sim \left( \frac{4 \pi R_d^2}{q E_0 L} \right)^2 $ and the non-dimensional governing equation is given by
+\begin{eqnarray}
+&\bar{y}'' = - \frac{C_D \rho A L}{2 m} \bar{y}'^2 - \frac{1}{\left( \frac{L}{R} \bar{y} + 1\right)^2} ,& \nonumber \\
+& \bar{y}(0) = \frac{R}{L}, \hspace{5 mm} \bar{y}'(0) = \left( \frac{4 \pi U_0^2 R_d^2}{q E_0 L^3}\right)^{1/2} = \frac{R}{L} \sqrt{\mathbb{E}\mbox{u}_+}.& \nonumber
+\end{eqnarray}
+where $\mathbb{E}\mbox{u}_+ = \frac{4 \pi m U_0^2}{q E_0 L}$ is a long time scaled electrostatic Euler number.
+We prefer the approach with the greatest physical simplicity, fewest Pi terms, and has homogoenous initial conditions.
+
+In Case 1, the characteristic dimensions are
+\[ t_c \sim \frac{R^2}{L^2} \frac{4 \pi m U_0}{q E_0}, \hspace{5mm} y_c \sim \frac{R^2}{L^2} \frac{4 \pi m U_0^2}{q E_0}.
+\]
+With this scaling the non-dimensional governing equation is 
+\begin{eqnarray}
+&\bar{y}'' = - \mathbb{D}\mbox{g} \mathbb{E}\mbox{u}_+ \bar{y}'^2 - \frac{1}{\left( \mathbb{E}\mbox{u}_+ \bar{y} + 1 \right)^2}, & \nonumber \\
+& \bar{y}(0) = 0, \hspace{1 mm} \bar{y}'(0) = 1 & 
+\end{eqnarray}
+where $\mathbb{D}\mbox{g} = \frac{C_D \rho_a}{\rho_l}$. This is the preferred scaling.
+
+\subsection{Asymptotic Estimates}
+
+\subsubsection{Inertial Electro-Image Limit}
+With $\epsilon = \mathbb{E}\mbox{u}$, where $\epsilon$ is a small parameter, and $\alpha = \mathbb{I}\mbox{m}$,
+\begin{eqnarray*}
+&\bar{y}(\bar{t}) = \bar{t} + \frac{\bar{t}^{2}}{2} \left(-1 - \alpha\right) + \epsilon \left(\frac{\alpha \bar{t}^{3}}{3} + \frac{\alpha \bar{t}^{4}}{12} \left(-1 - \alpha\right)\right)& \\
+&+ \epsilon^{2} \left(- \frac{\alpha \bar{t}^{4}}{4} + \frac{\alpha \bar{t}^{5}}{60} \left(9 + 11 \alpha\right) + \frac{\alpha \bar{t}^{6}}{360} \left(-9 - 20 \alpha - 11 \alpha^{2}\right)\right) + \mathcal{O}(\epsilon^3)&
+\end{eqnarray*}
+
+\newpage
+\begin{figure}[htb]
+    \centering
+    \resizebox{1\textwidth}{!}{\input{../figures/short_times.pgf}}
+    \caption{Text.}
+    \label{fig:short_times}
+\end{figure}
+
+\subsubsection{Inertial Electro-Viscous Limit}
+Asymptotic estimate of the trajectory. With $\epsilon = {\mathbb{E}\mbox{u}}_+$, where $\epsilon$ is a small parameter, and $\beta = \mathbb{D}\mbox{g}$,
+\begin{eqnarray*}
+&\bar{y}(\bar{t}) = \bar{t} - \frac{\bar{t}^{2}}{2} + \epsilon \left(\frac{\bar{t}^{3}}{3} \left(1 + \beta\right) + \frac{\bar{t}^{4}}{12} \left(-1 - \beta\right) - \frac{\beta \bar{t}^{2}}{2}\right)&  \\
+&+ \epsilon^{2} \left(\frac{\bar{t}^{4}}{12} \left(-3 - 3 \beta - 4 \beta^{2}\right) + \frac{\bar{t}^{5}}{60} \left(11 + 10 \beta + 8 \beta^{2}\right)+ \frac{\bar{t}^{6}}{360} \left(-11 - 10 \beta - 8 \beta^{2}\right) + \frac{\beta^{2} \bar{t}^{3}}{3}\right)& \\
+ &+ \mathcal{O}(\epsilon^3)&
+\end{eqnarray*}
+
+\newpage
+\begin{figure}[htb]
+    \centering
+    \input{../figures/long_times.pgf}
+    \caption{Text.}
+     \label{fig:long_times}
+\end{figure}
+
+Times for returns
+\[t_c = 2 + \epsilon \left(\frac{4}{3} - \frac{2 \beta}{3}\right) + \epsilon^{2} \left(\frac{4}{5} - \frac{4 \beta}{3} + \frac{2 \beta^{2}}{5}\right)
+\]
+\begin{figure}[htb]
+    \centering
+    \input{../figures/drag.pgf}
+    \caption{Text.}
+    \label{fig:drag}
+\end{figure}
 \end{document}

### 2018-01-21 doc/manuscript/theory.tex
added references, more theory, updated figures

@@
 }
-\title{\textsf{\textbf{Droplet Electro-Bouncing in $\mu$-Gravity}}}
+\title{\textsf{\textbf{Droplet Electro-Bouncing in Low-Gravity}}}
 \vspace{-25mm}
@@
 \usepackage{setspace}
+\usepackage[
+backend=biber,
+style=phys,
+sorting=none
+]{biblatex}
+\addbibresource{thesis.bib}
+
 \begin{document}
@@
 \subsection{Forces and the Equation of Motion}
-Treating a droplet as a particle, with radius $R_d$, the  equation of motion for a charged droplet translating vertically along the central axis of a finite square charged dielectric sheet is given by
+This section will develop a simple, 1-dimensional model of the dynamics of droplets dominated by electrostatic forces.
+Treating a droplet as a particle, with radius $R_d$, the  equation of motion of charged droplets center of mass as it translates vertically along the central axis of a finite square charged dielectric sheet is given by
 \begin{equation}
@@
 where $m$ is the droplet mass, $y'' = \frac{d^2 y}{d t^2}$ is the droplet acceleration, $\mathbf{F}_D$ is the drag force, and $\mathbf{F}_E$ is the electrostatic force.
-The initial conditions are such that the droplet leaves its resting position $R_d$ at $t=0$, with initial velocity $U_0$.
+The initial conditions are such that, when the $\mathbb{B}\mbox{o}$ is suddenly reduced at the start of the drop tower experiment, the droplet jumps with initial velocity $U_0$ from its 1-g resting position $R_d$ at $t=0$.
 The signs of the forces on the right side of Equation \ref{gov_eqn} indicate that they act in the opposite direction of the droplet motion.
-In this section we aim specifiy models for the various forces in this equation.
+We need to specify models for the various forces in this equation to begin our analysis of the droplet dynamics.
 
-If we assume an intermediate range of Reynolds numbers $\mathbb{R}\mbox{e} \equiv \frac{2UR_d}{\nu}$, $1 <\mathbb{R}\mbox{e} < 1000 $ then the drag is quadratic,
+With the assumption of an intermediate range of Reynolds numbers $\mathbb{R}\mbox{e} \equiv \frac{2UR_d}{\nu}$, $1 \leq \mathbb{R}\mbox{e} \leq 5000 $ then the force drag drag acting on the droplet will be quadratic,
 \begin{equation*}\label{drag_force}
@@
 where $C_D$ is the drag coefficient, $\rho$ is the density of the sorrounding fluid medium (air, in this case), and $A$ is the frontal area of the droplet.
-For this range of Reynolds numbers we may also approximate the drag coefficient by the well known Abraham correlation \hl{ref.}
-\[C_D = \frac{24}{9.06^2} \left( 1 + \frac{9.06}{\sqrt{\mathbb{R}\mbox{e}}} \right)^2\]
+For this range of Reynolds numbers it is appropriate to approximate the drag coefficient by the well known Abraham correlation \cite{abraham_functional_1970}
+\[C_D = \frac{24}{9.06^2} \left( 1 + \frac{9.06}{\sqrt{\mathbb{R}\mbox{e}}} \right)^2 .\]
 
-Modeling the electrostatic force is somehwhat more involved, but we will adopt the standard electrohydrodynamic (EHD) approximation model because of the dramatic simplifications it offers \hl{ref}.
-We first assume a DC electric field, such that $Re \langle \epsilon \rangle \approx  \mbox{constant}$, where $\epsilon$ is the dielectric permittivity of the respective media.
-We also assume that currents are small such that the effects of magnetic fields can be neglected.
-For the validity of this assumption to hold the characteristic time scale for electrical phenomena $\tau_e = \epsilon \epsilon_0/\sigma_e \ll 1$, where $\tau$ is the ratio of absolute dielectric permittivity $\kappa = \epsilon \epsilon_0$, to conductivity $\sigma_e$, of the medium [ref].
-\hl{Given the respective conductivity, and permittivity of water ($\sigma_e = 2.5 \cdot 10^{-4}$ $\Omega^{-1} \mbox{cm}^{-1}$), we estimate $\tau_e \approx 7 \times 10^{-8}$ s}.
-This assumption also allows us to assume that the net charge present in the medium surrounding the droplets remains approximately constant during the typical time interval of a low-gravity experiment, and no transfers of charge occur after the droplet leaves the surface.
+Modeling the electrostatic force is somehwhat more involved, but we will start with the standard electrohydrodynamic (EHD) approximation \cite{saville_electrohydrodynamics:taylor-melcher_1997} as our model, and further simplify where possible.
+Under a DC electric field, we assume that the real part of the dielectric permitivity $\epsilon$, $Re \langle \epsilon \rangle \approx  \mbox{constant}$.
+We also assume that electric currents are small enough that the effects of magnetic fields can be neglected.
+The validity of this assumption rests on the size of the characteristic time scale for electrical phenomena $\tau_e = \epsilon \epsilon_0/\sigma_e \ll 1$, where $\tau_e$ is the ratio of absolute dielectric permittivity $\kappa = \epsilon \epsilon_0$, to conductivity $\sigma_e$, of the medium.
+The time characteristic time $\tau_e$ is also known as the relaxation time, and is a measure of how quickly the polarization of a dielectric responds to a change in electric field.
+Given the respective conductivity, and permittivity of extremely-pure water ($ \kappa \sim 80$, $\sigma_e = 18.2 \times 10^{6}$ $\Omega\mbox{cm}$) \cite{yatsuzuka_electrification_1994}, we estimate $\tau_e \approx 4 \times 10^{-6}$ s.
+The relaxation for the common distilled water that is actually used in the droplet experiments is undobtedly even smaller (due to the presence of solvated ions).
+Neglecting the effects of a electric double layer on hydration of ions (in the water or the ambient atmosphere), then the assumption of small relaxation time further implies that the net charge present in the droplets will remain approximately constant during the typical time interval of a low-gravity experiment.
 
-If we suppose that electrical forces acting on free charges and dipoles in a fluid are transferred directly to the fluid itself, then this overall electrical body force will be the the divergence of the Maxwell stress tensor $\tau_m $, by
+Supposing that electrical forces acting on free charges and dipoles in a fluid are transferred directly to the fluid itself, then this overall electrical body force will be the the divergence of the Maxwell stress tensor $\tau_m $, by
 
@@
 
-The classical Korteweg-Helmholtz force density formulation of the Maxwell stress tensor is usually expressed as \hl{[ref]}
+The classical Korteweg-Helmholtz force density formulation of the Maxwell stress tensor is usually expressed as \cite{melcher_continuum_????}
 \begin{equation}\label{force_density}
-\mathbf{F}_E = \rho_f \mathbf{E} + \frac{1}{2} \left| \mathbf{E} \right|^2 \nabla \epsilon - \nabla \left( \frac{1}{2} \rho \left( \frac{\partial \epsilon}{\partial \rho} \right)_T \left| \mathbf{E} \right|^2 \right) .
+\mathbf{F}_E = \rho_f \mathbf{E} + \frac{1}{2} \left| E \right|^2 \nabla \epsilon - \nabla \left( \frac{1}{2} \rho \left( \frac{\partial \epsilon}{\partial \rho} \right)_T \left| E \right|^2 \right) .
 \end{equation}
@@
 The first term in this expression, equivalently written as $q\mathbf{E}$, is the well known Coulombic force or electrophoretic force, which arises from the presence of free charge in an external electric field.
+We expect this term to dominate the electric force in a DC field.
 The second term is the force arising from polarization stresses due to a nonuniform field acting across a gradient in permittivity.
@@
 The third term describes forces due to electrostriction.
-It has been noted by Melcher and Hurwitz that the electrostriction term is the gradient of a scalar and can thus be cannononically lumped togeather with the hydrostatic pressure for incompressible fluids)\hl{[ref]}; we neglect it in our analysis.
+It has been noted by Melcher and Hurwitz that the electrostriction term is the gradient of a scalar and can thus be cannononically lumped togeather with the hydrostatic pressure for incompressible fluids) \cite{hurwitz_electrohydrodynamic_1966}; we neglect it in our analysis.
 
-It is common to approximate the polarization stress by idealizing the droplet as a simple dipole using the effective dipole moment method first suggested by Pohl and Jones\hl{[ref][ref]}.
-This approach can be related back to the force density by means of a Taylor series expansion of $\mathbf{E}$ in the limit of a small gradient \hl{[ref]}.
-The DEP force is distinct from the Coulombic force in that net charge is not required, and that the force vector goes in the direction of the gradient of the field, $\nabla \left| \mathbf{E} \right|^2$, rather than in the direction of $\mathbf{E}$.
+It is common to approximate the polarization stress by idealizing the droplet as a simple dipole using the effective dipole moment method first suggested by Pohl in 1958 \cite{pohl_effects_1958}.
+This approach has been related back to the force density by the volumetric integration of the force density the substitution of a Taylor series expansion of $\mathbf{E}$ in the limit of a small radial gradient of the field within the dielectric sphere \cite{wang_general_1997}.
 The DEP force is related to the dipole moment (induced or permanent) of polarizable media which has a tendency to align the dipole with the electric field.
@@
 Whether the force is positive or negative in the direction of the electric field gradient depends on the difference of dielectric permittivites between the fluids, rather than on the polarity of $\mathbf{E}$ itself.
-It bears repeating that droplets will polarize in a uniform field, but since there is no gradient in the field the forces felt by the dipoles are symmetric and there is no net force.
+In principle an external electric field will tend to induce a dipole in a dielectric material, but if the field is spatially uniform there is no gradient in the field the forces felt by the dipoles are symmetric and thus no net force.
 The dipole moment of a spherical linear-dielectric particle immersed in a dielectric medium is given by
@@
 \end{equation} 
-where $\mathbf{P} = \left(\kappa_1 - 1 \right) \epsilon_0 \mathbf{E}_{iz} = \chi_e \epsilon_0 \mathbf{E}_{iz}$ is the polarization moment, and $R_d$ is the particle radius, \hl{$\kappa_1 = \frac{\epsilon}{\epsilon_0}$ being the relative dielectric constant of the medium (air in this case)}, $\chi_e = \kappa_1 - 1$ being the electric susceptibility of the dielectric medium, and $\mathbf{E}_{iz}$ is the $z$-coordinate component of the electric field internal to the sphere, assuming the external electric field to be oriented parallel to the $z$-axis.
+where $\mathbf{P} = \left(\kappa_1 - 1 \right) \epsilon_0 \mathbf{E} = \chi_e \epsilon_0 \mathbf{E}$ is the polarization moment, and $R_d$ is the particle radius, $\kappa_1 = \frac{\epsilon}{\epsilon_0}$ being the relative dielectric constant of the external medium (air in this case), $\chi_e = \kappa_1 - 1$ being the electric susceptibility of the dielectric medium.
 The excess polarization $\mathbf{P}_e$, in the sphere is given by
 \begin{equation} \label{polarization}
-\mathbf{P}_e = \left( \kappa_2 - \kappa_1 \right) \epsilon_0 \mathbf{E}_{iz} = \frac{3 \kappa_1}{\kappa_2 +2\kappa_1}\mathbf{E}_{iz},
+\mathbf{P}_e = \left( \kappa_2 - \kappa_1 \right) \epsilon_0 \mathbf{E} = \frac{3 \kappa_1}{\kappa_2 +2\kappa_1}\mathbf{E},
 \end{equation}
 where $\kappa_2$ is the relative dielectric constant of the spherical particle.
-Taking together equations \ref{dipole_m_1}, and \ref{polarization} we find that the effective dipole moment of the particle is given by
+Taking together Equations \ref{dipole_m_1}, and \ref{polarization} the effective dipole moment of the particle is given by
 \begin{equation}\label{dipole_m_2}
@@
 \end{eqnarray}
-where it is an asthetically pleasing shorthand to refer to the permittivity ratio by $K = \frac{\kappa_2 - \kappa_1}{\kappa_2 + 2 \kappa_1}$, which is also known as the Clausius-Mossotti factor.
+where it is nice to use the simplifying shorthand $K = \frac{\kappa_2 - \kappa_1}{\kappa_2 + 2 \kappa_1}$, which is also known as the Clausius-Mossotti factor.
 In cases where $K <$ 0, or $K>$ 0 the particle will be repelled or attracted to regions of strong field respectively.
-In our experiment, taking the relative dielectric constants to be $\kappa_1 \approx$ 1 and $\kappa_2 \approx$ 80, we have $K \approx$ 0.96.
-We also note that the equivalent dipole approximation requires an assumption of small physical scale of the particle relative to the lengthscale of nonuniformity of the field, which in this case we take to be the length of the charged superhydrophobic surface ($L =$ 25 mm $\gg a \approx$ 2.5 mm).
+In our experiment, taking the relative dielectric constants to be $\kappa_1 \approx$ 1 and $\kappa_2 \approx$ 80, the Clausius-Mossotti factor $K \approx$ 0.96.
+It is important to note that the equivalent dipole approximation critically requires an assumption of small physical scale of the particle relative to the lengthscale of nonuniformity of the field, which in this case we take to be the length of the charged superhydrophobic surface ($L =$ 25 mm $\gg a \approx$ 2.5 mm).
 
-When the droplet is close to the dielectric surface, the net charge on the droplet will tend to polarize the dielectric, perturbing the electric field.
+When the droplet is close to the dielectric surface, the net charge on the droplet will tend to induce polarization of the dielectric, perturbing the electric field.
 The polarization bound charge in the dielectric will be of the opposite sign of the net droplet charge and thus there will be a force of attraction.
-This so-called image force is a correction to the Colomb force due to the external electric field only, and can be found by the method of images \hl{ref}.
+This so-called image force is a correction to the Colomb force due to the external electric field only, and can be found by the method of images \cite{david_j._griffiths_introduction_1999}.
 The image force $\mathbf{F}_I$, is given by
@@
 \end{eqnarray}
-As this condition holds in all cases under study we herefore neglect the DEP force in our analysis.
+As this condition likely holds in our experiments we henceforth neglect the DEP force in our analysis.
+There is some physical intuition to support this conclusion as well.
+The dielectric displacement, $\mathbf{D} = \kappa \epsilon_0 \mathbf{E}$ of a water droplet in air is very high due to its large relative dielectric constant.
+This implies that the field strength within the droplet is about 2 orders of magnitude smaller than in the surrounding medium (which is essentially the same as a vacuum from a dielectric standpoint), thus it is not particularly inaccurate to model the dielectric volume of a droplet as a conductive shell (an equipotential), with zero field in its interior.
 
 \subsection{The Electric Field}
-If we consider the charged dielectric surface of our experiments to be a square sheet of charge lying in the $xz$-plane with width $L$, the symmetry of the problem happily lets us obtain the $y$-component of the electric field $\mathbf{E}_y$ by direct integration \hl{ref}.
+If we consider the charged dielectric surface of our experiments to be a square sheet of charge lying in the $xz$-plane with width $L$, the symmetry of the problem happily lets us obtain the $y$-component of the electric field $\mathbf{E}$ by direct integration.
 In particular it is easy to constuct the electric field due to a finite plane of charge by supoerposition of the electric fields of a series of line charges.
-By symmetry the electric field points along the y-axis; for a point along the $y$-axis the position vector is $\mathbf{r} = \left( x^2 + y^2 + z^2 \right)^{1/2} \hat{\mathbf{r}}$.
-The $y$-component of $\mathbf{E}$ is given by $\mathbf{E}_y \cos \theta = \mathbf{E}_y y/ \mathbf{r}$.
-Then if the charge in an element of area, $dx dz$ is $\sigma dx dz$ the electric field $\mathbf{E}_y$ is
-\[ \mathbf{E}_y = \frac{\sigma y}{4 \pi \epsilon_0} \int^{L/2}_{L/2} \int^{L/2}_{L/2} \left( x^2 + y^2 + z^2 \right)^{3/2} dx dz \hspace{1mm}\hat{\mathbf{r}} 
-,\]
-where $\sigma$ is the surface charge density. This can be easily integrated to obtain an expression for the electric field in terms of $y$, 
+By symmetry the electric field points along the $y$-axis; for a point along the $y$-axis the position vector is $\mathbf{r} = \left( x^2 + y^2 \right)^{1/2} \hat{\mathbf{r}}$ to the center of a line charge in the $xz$-plane.
+The $y$-component of $d\mathbf{E}$ is found by $d E_r = d E_y \cos \theta = d E_y y/ r$, where $\theta$ is the angle made between the $y$-axis and the positon vector $\mathbf{r}$.
+If the charge in a line element, $dx$ is $\sigma L dx$, where $\sigma$ is the surface charge density, the electric field of a line charge is given by \cite{david_j._griffiths_introduction_1999}
+\[d E_r = \frac{k \sigma L dx}{4 \pi \epsilon_0 r \sqrt{r^2 + L^2/4}}.
+\]
+The $y$-component of the electric field $E_y$, is then
+\[ E_y = \frac{\sigma L y }{4 \pi \epsilon_0} \int^{L/2}_{-L/2} \frac{1}{(y^2 + x^2) \sqrt{y^2 + x^2 + L^2/4}} dx 
+.\]
+With some substitutions this can be integrated to obtain an expression for the electric field in terms of $y$, 
 \begin{equation}
-\mathbf{E}_y = \frac{\sigma y}{ \pi \epsilon_0} \tan^{-1} \left( \frac{L^2}{y \sqrt{2L^2 + y^2}}\right)
+E_y = \frac{\sigma}{ \pi \epsilon_0} \tan^{-1} \left( \frac{L^2}{y \sqrt{2L^2 + y^2}}\right)
 .\end{equation}
@@
 \begin{equation}
-\mathbf{E}_y \approx \frac{\sigma}{4 \pi \epsilon_0} \hat{\mathbf{j}} \hspace{10mm} y \ll L
+E_y \approx \frac{\sigma}{4 \pi \epsilon_0} = E_0 \hspace{10mm} y \ll L
 ,\end{equation}
-which is constant, and equivalent to the electric field due to an infinite plane of charge. In the limit of $y \gg L$, the argument of the arctangent function can be approximated by
+where $E_0$ is the characteristic electric field given by $E_0 = \frac{\sigma}{4 \pi \epsilon_0}$.
+This field is constant, and equivalent to the electric field due to an infinite plane of charge.
+In the limit of $y \gg L$, the argument of the arctangent function can be approximated by
 \[ \frac{L^2}{2 y \left( 2 L^2 + 4 y^2\right)^{1/2}} = \frac{L^2}{4 y^2 \left( 1 + L^2/2y^2 \right)^{1/2}} \approx \frac{L^2}{4 y^2}
@@
 \begin{equation}
-\mathbf{E}_y \approx \frac{\sigma L^2}{4 \pi \epsilon_0} y^{-2} \hat{\mathbf{j}} \hspace{10mm} y \gg L
+E_y \approx L^2 E_0 y^{-2}  \hspace{10mm} y \gg L
 .\end{equation}
-With the characteristic electric field given by $E_0 = \frac{\sigma}{4 \pi \epsilon_0}$, both these regiemes can be clearly seen in the plot of $\mathbf{E}_y$ shown in Figure \ref{fig:E0}.
+Both these regimes can be clearly seen in the plot of $E_y$ shown in Figure \ref{fig:E0}.
 \begin{figure}[htb]
@@
     \input{../figures/E0.pgf}
-    \caption{A log-log plot of the magnitude of the non-dimensional electric field, $\mathbf{E}_y$.\label{fig:E0}}
+    \caption{A log-log plot of the magnitude of the non-dimensional electric field, $E_y$.\label{fig:E0}}
 \end{figure}
@@
 Introducing scaled variables
-\[ \bar{t} = \frac{t}{t_c}, \hspace{10 mm} \bar{y} = \frac{y}{y_c}, \]
+\begin{equation}
+ \bar{t} = \frac{t}{t_c}, \hspace{10 mm} \bar{y} = \frac{y}{y_c}, \end{equation}
 where $y_c$ and $t_c$ are characteristic length and time scales respectively, and using the cooridnate transformation $y(0) - R = 0$, the governing equation becomes
@@
 - \frac{q E_0 t_c^2}{m y_c} \bar{E} 
-- \frac{k q^2 t_c^2}{16 \pi \epsilon_0 R^2 m y_c} \frac{1}{\left( \frac{y_c}{R} \bar{y} + 1 \right)^2}, & \nonumber \\
+- \frac{k q^2 t_c^2}{16 \pi \epsilon_0 R^2 m y_c} \left( \frac{y_c}{R} \bar{y} + 1 \right)^{-2}, & \nonumber \\
 & \bar{y}(0) = 0, \hspace{1 mm} \bar{y}'(0) = \frac{U_0 t_c}{y_c} .&
@@
 \begin{eqnarray}
-& \bar{y}'' = -1 - \mathbb{I}\mbox{m} \frac{1}{\left( \mathbb{E}\mbox{u}\bar{y} + 1 \right)^2} ,& \nonumber \\
-& \bar{y}(0) = 0, \hspace{1 mm} \bar{y}'(0) = 1 .&
+& \bar{y}'' = -1 - \mathbb{I}\mbox{m} \left( \mathbb{E}\mbox{u}\bar{y} + 1 \right)^{-2} ,& \nonumber \\
+& \bar{y}(0) = 0, \hspace{1 mm} \bar{y}'(0) = 1 .& \label{img_limit}
 \end{eqnarray} 
@@
 \[ \mathbb{I}\mbox{m} \equiv \frac{k q}{16 \pi \epsilon_0 R_d^2 E_0} = \mathbf{\Pi}_3, \hspace{5 mm}
-\mathbb{E}\mbox{u} \equiv \frac{m U_0^2}{q E_0} = \mathbf{\Pi}_4 ,
+\mathbb{E}\mbox{u} \equiv \frac{m U_0^2}{q E_0 R_d} = \mathbf{\Pi}_4 ,
 \]
@@
 \begin{eqnarray}
-&\bar{y}'' = - \frac{C_D \rho A L}{2 m} \bar{y}'^2 - \frac{1}{\left( \frac{L}{R} \bar{y} + 1\right)^2} ,& \nonumber \\
-& \bar{y}(0) = \frac{R}{L}, \hspace{5 mm} \bar{y}'(0) = \left( \frac{4 \pi U_0^2 R_d^2}{q E_0 L^3}\right)^{1/2} = \frac{R}{L} \sqrt{\mathbb{E}\mbox{u}_+}.& \nonumber
+&\bar{y}'' = - \frac{C_D \rho A L}{2 m} \bar{y}'^2 - \left( \frac{L}{R_d} \bar{y} + 1\right)^{-2} ,& \nonumber \\
+& \bar{y}(0) = \frac{R_d}{L}, \hspace{5 mm} \bar{y}'(0) = \left( \frac{4 \pi U_0^2 R_d^2}{q E_0 L^3}\right)^{1/2} = \frac{R_d}{L} \sqrt{\mathbb{E}\mbox{u}_+}.& \nonumber
 \end{eqnarray}
@@
 In Case 1, the characteristic dimensions are
-\[ t_c \sim \frac{R^2}{L^2} \frac{4 \pi m U_0}{q E_0}, \hspace{5mm} y_c \sim \frac{R^2}{L^2} \frac{4 \pi m U_0^2}{q E_0}.
+\[ t_c \sim \frac{R_d^2}{L^2} \frac{4 \pi m U_0}{q E_0}, \hspace{5mm} y_c \sim \frac{R_d^2}{L^2} \frac{4 \pi m U_0^2}{q E_0}.
 \]
@@
 \begin{eqnarray}
-&\bar{y}'' = - \mathbb{D}\mbox{g} \mathbb{E}\mbox{u}_+ \bar{y}'^2 - \frac{1}{\left( \mathbb{E}\mbox{u}_+ \bar{y} + 1 \right)^2}, & \nonumber \\
-& \bar{y}(0) = 0, \hspace{1 mm} \bar{y}'(0) = 1 & 
+&\bar{y}'' = - \mathbb{D}\mbox{g} \mathbb{E}\mbox{u}_+ \bar{y}'^2 - \left( \mathbb{E}\mbox{u}_+ \bar{y} + 1 \right)^{-2}, & \nonumber \\
+& \bar{y}(0) = 0, \hspace{1 mm} \bar{y}'(0) = 1 & \label{drag_limit}
 \end{eqnarray}
-where $\mathbb{D}\mbox{g} = \frac{C_D \rho_a}{\rho_l}$. This is the preferred scaling.
+where $\mathbb{D}\mbox{g} \equiv \frac{C_D \rho_a}{\rho_l}$ and $\mathbb{E}\mbox{u}_+ = 4 \pi \frac{R_d^2}{L^2} \mathbb{E}\mbox{u}$. This is the preferred scaling.
 
 \subsection{Asymptotic Estimates}
+\subsubsection{Inertial Electro-Image Limit}
+The alternate scalings of the equation of motion given by Equations \ref{drag_limit}, \ref{img_limit} are weakly non-linear differential equations in the sense that they reduce to linear equations as the parameter $\mathbb{E}\mbox{u} \rightarrow 0$.
+If we take $\mathbb{E}\mbox{u}$ to be a small parameter $\epsilon$, we can find an asymptotic approximation to the solution of the non-linear equation by means of a regular perturbation.
+In this case we use the naive expansion
+\[ \bar{y}(\bar{t}) \sim \bar{y}_0(\bar{t}) + \epsilon \bar{y}_1(\bar{t}) + \epsilon^2 \bar{y}_2(\bar{t}) \ldots \epsilon^n\bar{y}_n(\bar{t})  
+.\]
+By substitution of the expansion (and its derivatives) into the differential equation, and equating terms by order, and using the notation $\alpha = \mathbb{I}\mbox{m}$ (this being the equation scaled in the small-times limit), we first find the $\mathcal{O}(1)$, unperturbed, solution to the equation of motion to be
+\[{\bar{y}_{0}}{\left (\bar{t} \right )} = \bar{t} + \frac{\bar{t}^{2}}{2} \left(-1 - \alpha\right). \]
+Looking at this solution it is evident that if we let $\alpha=0$, the solution is the classical kinematic equation for projectile motion without drag under constant gravity, $g_0$.
+Continuing on with this procedure we find, (after some tedious computations, documented in Appendix \hl{ref}) the higher order composite solutions to be
 
-\subsubsection{Inertial Electro-Image Limit}
-With $\epsilon = \mathbb{E}\mbox{u}$, where $\epsilon$ is a small parameter, and $\alpha = \mathbb{I}\mbox{m}$,
 \begin{eqnarray*}
 &\bar{y}(\bar{t}) = \bar{t} + \frac{\bar{t}^{2}}{2} \left(-1 - \alpha\right) + \epsilon \left(\frac{\alpha \bar{t}^{3}}{3} + \frac{\alpha \bar{t}^{4}}{12} \left(-1 - \alpha\right)\right)& \\
-&+ \epsilon^{2} \left(- \frac{\alpha \bar{t}^{4}}{4} + \frac{\alpha \bar{t}^{5}}{60} \left(9 + 11 \alpha\right) + \frac{\alpha \bar{t}^{6}}{360} \left(-9 - 20 \alpha - 11 \alpha^{2}\right)\right) + \mathcal{O}(\epsilon^3)&
+&+ \epsilon^{2} \left(- \frac{\alpha \bar{t}^{4}}{4} + \frac{\alpha \bar{t}^{5}}{60} \left(9 + 11 \alpha\right) + \frac{\alpha \bar{t}^{6}}{360} \left(-9 - 20 \alpha - 11 \alpha^{2}\right)\right) + \mathcal{O}(\epsilon^3)&.
 \end{eqnarray*}
 
-\newpage
+In fact we, for somewhat arbitrary reasons, computed an $\mathcal{O}(\epsilon^5)$ accurate solution, but it is far to ugly to reprint here in its entirety.
+However, we plot these approximate short-time scaled solutions with varying values of the Image number, $\mathbb{I}\mbox{m} = \alpha$ in Figure \ref{fig:short_times}.
+%\newpage
 \begin{figure}[htb]
@@
     \resizebox{1\textwidth}{!}{\input{../figures/short_times.pgf}}
-    \caption{Text.}
+    \caption{Non-dimensional droplet trajectories for various values of $\mathbb{E}\mbox{u}=\epsilon$, $\mathbb{I}\mbox{m}=\alpha$.
+The trajectory reduces to the classical $\mathcal{O}(1)$ solution for small values of $\alpha$.
+It should be noted that depsite what is implied by these plots $\alpha$ is not neccisarily completely independent of $\epsilon$, as they share $q$, and $E_0$ as common factors, $U_0 \sim R_d^2$, and $m \sim R_d^3$.}
     \label{fig:short_times}
 \end{figure}
+These plots show a trend of decreasing time-of-flight (the time for the droplet to return to the origin, or complete a single ``bounce''), and height at apoapse with increasing values of the Image number $\alpha$.
+When $\alpha = 1$ the time of flight is exactly half of characteristic time scale in this regime.
+In the limit of small $\epsilon$ the trajectories collapse to the $\mathcal{O}(1)$ solution regardless of the Image number.
+In principle there is some coupling between $\mathbb{E}\mbox{u}$ and $\mathbb{I}\mbox{m}$, notably this relationship does not depend on the electric field $E_0$ but on a charge to mass ratio.
+The effect of contact line hysteresis on the initial jump velocity $U_0$ will also tend to independently decohere the natural covariance between these parameters.
 
 \subsubsection{Inertial Electro-Viscous Limit}
-Asymptotic estimate of the trajectory. With $\epsilon = {\mathbb{E}\mbox{u}}_+$, where $\epsilon$ is a small parameter, and $\beta = \mathbb{D}\mbox{g}$,
+By similar arguments we find an asymptotic estimate of the trajectory in the long-times scaled regime.
+With $\epsilon = {\mathbb{E}\mbox{u}}_+$, where $\epsilon$ again is a small parameter, and $\beta = \mathbb{D}\mbox{g}$, the approximate solution is
 \begin{eqnarray*}
@@
 &+ \epsilon^{2} \left(\frac{\bar{t}^{4}}{12} \left(-3 - 3 \beta - 4 \beta^{2}\right) + \frac{\bar{t}^{5}}{60} \left(11 + 10 \beta + 8 \beta^{2}\right)+ \frac{\bar{t}^{6}}{360} \left(-11 - 10 \beta - 8 \beta^{2}\right) + \frac{\beta^{2} \bar{t}^{3}}{3}\right)& \\
- &+ \mathcal{O}(\epsilon^3)&
+ &+ \mathcal{O}(\epsilon^3)&.
 \end{eqnarray*}
-
-\newpage
+This trajectory given by this solution is shown in Figure \ref{fig:long_times}.
+If we assume a constant scale for the drag coefficient, $C_d \approx 0.5$, then  the Drag number $\beta = \mathbb{D}\mbox{g}$ is approximately a constant $\beta \approx 6 \times 10^{-4}$ in all of our experiments.
 \begin{figure}[htb]
@@
     \input{../figures/long_times.pgf}
-    \caption{Text.}
+    \caption{Non-dimensional droplet trajectories for various values of $\mathbb{E}\mbox{u}=\epsilon$.}
      \label{fig:long_times}
@@
 
-Times for returns
-\[t_c = 2 + \epsilon \left(\frac{4}{3} - \frac{2 \beta}{3}\right) + \epsilon^{2} \left(\frac{4}{5} - \frac{4 \beta}{3} + \frac{2 \beta^{2}}{5}\right)
-\]
+Again, the trajectory seemingly reduces to the classical $\mathcal{O}(1)$ solution for small values of of $\epsilon$.
+We also note that the effect of drag is very slight, despite the fact that it appears explicity in the $\mathcal{O}(1)$ solution; the apoapse is very nearly equal to half the characteristic length scale.
+In practical terms this linearizing effect of small $\beta$ may dissapear if the fluid density is much less than that of water, as in our experiements.
+
+By again appying a regular perturbation to the asymptotic solution with the expansion
+
+\[ \bar{t} \sim \bar{t}_0 + \epsilon \bar{t}_1 + \epsilon^2 \bar{t}_2 \ldots \epsilon^n\bar{t}_n  
+,\]
+
+and solving for the roots (that is, the times when $\bar{y} = 0$), we find an asymptotic estimate for the time-of-flight, $t_f$.
+The $\mathcal{O}(\epsilon^2)$ accurate time-of-flight estimate is given by
+
+\[t_f = 2 + \epsilon \left(\frac{4}{3} - \frac{2 \beta}{3}\right) + \epsilon^{2} \left(\frac{4}{5} - \frac{4 \beta}{3} + \frac{2 \beta^{2}}{5}\right).\]
+
+Substituting the experiemental value of $\beta$ we find the time-of-flight estimate for water droplets in air to be
+
+\[ t_f = 2 + 1.333 \epsilon + 0.799 \epsilon^{2} \]
+
+In Figure \ref{fig:drag} we look at the effect of increasing values of ${\mathbb{E}\mbox{u}}_+$ on time-of-flight.
 \begin{figure}[htb]
@@
     \input{../figures/drag.pgf}
-    \caption{Text.}
+    \caption{Droplet time of flight as a function of $\epsilon = {\mathbb{E}\mbox{u}}_+$.}
     \label{fig:drag}
 \end{figure}
+
+We see that as $\epsilon$ grows to be no longer small, the time-of-flight grows rapidly, but this behaviour appears to have an asymptote at a certain critical velocity as $\mathcal{O}({\mathbb{E}\mbox{u}}_+) \rightarrow \mathcal{O}(1)$; this is an electrostatic escape velocity, $U_e$.
+
+We can find the escape velocity by solving a modified version of the equation of motion,
+\[ m u' = - \frac{q E_0}{y^2}, \]
+where $u = \frac{d y}{d t}$ is the droplet velocity. Integrating between the respective limits,
+\[m \int^{u(y)}_{U_0} u du = -q E_0 \int^y_{R_d} \frac{dy}{y^2} ,\]
+which has the solution
+\[ u(y) = \pm U_0 \left[1 + \frac{2q E_0}{m U_0^2} \left( \frac{1}{y} - \frac{1}{R_d} \right) \right]^{1/2}.
+\]
+This equation has an asymptotic velocity, $U_{\infty}$ at $y = \infty$ which is real if 
+\[ U_0 \geq  U_e = \sqrt{\frac{2 q E_0}{m R_d}},
+\]
+where $U_e$ is the escape velocity and $U_{\infty} = \sqrt{U_0^2 - U_e^2}$. The condition for the droplets to escape the electric field is then given by
+\[
+8 \pi {\mathbb{E}\mbox{u}}_+ > 1.
+\]
+
+If the droplet escapes the electric field it will have a residual velocity $U_{\infty}$, and will be in a regime of pure inertia $\sim$ drag. The velocity will then decay as
+\[
+\bar{u}(\bar{t}) = \frac{1}{\bar{t} + 1},
+\]
+with a characteristic time $t_c \sim \frac{2 m}{C_D \rho A U_{\infty}}$ which is the halving time of the velocity.
+
+\printbibliography
 \end{document}

### 2018-01-23 doc/manuscript/ef_notes.tex
added complete, intro, theory, and methods sections

@@
 \doublespacing
-\section{Introduction}
-\subsection{Spontaneous Droplet Jump}
-When a nonwetting, gravity dominated sessile drop or puddle initially at rest in the Cassie-Baxter state on a surface undergoes a large step reduction in Bond number, $\mathbf{Bo} = \rho g V_d^{2/3}/\sigma$, where $\rho$ is the liquid density, $g$ is the acceleration of gravity, $V_d$ is the droplet volume, and $\sigma$ is the liquid surface tension, it will spontaneously jump away from the surface.
-This was first observed experimentally by Kirko \emph{et al.} in 1970 [ref] and later by Wollman \emph{et al.} in 2006 in a set of experiments conducted using a $\mu$-gravity drop tower \hl{[ref]}.
-The kinetic energy of the jump is supplied by the defect in free surface energy as the new minimum energy surface equilibrium has approximately constant curvature \hl{[ref]}.
-If the viscous energy losses by shear, and internal flows during roll up are neglected, as well as energy lost due to the hysteresis of the dynamic contact line, then the energy relation is given by
-\[KE = SE_2 -SE_1 = [(\sigma A)_{gl} + (\sigma A)_{sg}]_2 - [(\sigma A)_{ls} + (\sigma A)_{gl} + (\sigma A)_{sg}]_1. \]
-From this is derived a simple model for the droplet initial jump velocity, given by
-\[U_0 = \left(\frac{\sigma g}{\rho}\right)^{1/4}\left[1-\cos \theta + 2 \left(\frac{\pi H^3}{V_d} \right)^{1/2} - 6^{2/3} \left( \frac{\pi H^3}{V_d} \right)^{1/3} \right]^{1/2}, \]
-where \hl{[etc, etc, etc...]}.
-
-%\begin{figure}
-%  \centerline{\includegraphics[height=7cm,width=7cm]%{e88_1_thumb.jpg}}
-%  \caption{Droplet jump velocities, effect of hysteresis for small droplet size}
-%\label{fig:jump_velocities}
-%\end{figure}
-
-The droplet `rolls up' as it jumps away from the surface due to radial motion of capillary wave away from the contact line.
-The characteristic time scale of the rolling up scales as $t_j \sim R_p/U ~(\rho H R^2_p/\sigma)^{1/2}$ [ref], which resembles the contact time, $\tau \approx 2.6(\rho R^3_d/\sigma)^{1/2}$ reported by Richard \emph{et al.} in 2002 for the related problem of droplets impacting hydrophobic surfaces in 1-g \hl{[ref]}.
-For droplets with radial symmetry and sufficiently high initial $\mathbf{Bo}$ these waves coalesce as a shock leading to geyersing and creation of satellite drops by the Rayleigh-Plateau breakup of the geyser.
-In the case of smaller jumping droplets, the capillary waves do not lead to geyersing, and are viscously damped to varying degrees during the brief freefall period of the drop tower.
-
-The spontaneous droplet jump phenomenon provides a useful window though which to study the dynamics of large-lengthscale capillary dominated droplets.
-The governing physics of such massive droplets (far beyond the 1-g sub-millimetric capillary lengthscale) utterly defy terrestrial expectations about the ways in which liquid droplets `should' behave, and also are of critical importance in a space exploration setting where the design of practical $\mu$-gravity  multiphase fluidic systems will no doubt be needed as humankind gradually extends her domain into our solar system.
-\section{Bouncing}
-For the sake of brevity we will henceforth use the slightly confusing term `drop' as shorthand to refer to a single $\mu$-gravity drop tower experiment.
-\section{Experimental Methods}
-Superhydrophobic substrates were placed on a drop tower rig platform.
-The rig is released by a solenoid chucked pin at the same moment the exterior drag shield is allowed to fall.
-This decouples drag acceleration felt by the drag shield from the experiment which experiences approximately $1 \cdot 10^{-6}$g of high quality freefall for the 2.1s required for the rig/drag shield assembly to reach the bottom of drop tower 6 floors below.
-
-The superhydrophobic surface was treated with PTFE spray for the first experiment of the day, and approximately every $3^{\mbox{rd}}$ drop following.
-The general properties and details of the fabrication of these superhydrophobic surfaces are discussed in Section \ref{sec.suphydro}.
-Shortly before each drop the surfaces were briefly rinsed with distilled water, and then dried under a fume hood for about 10 minutes.
-The drop rigs were balanced to prevent unintentional torques from contaminating the kinematics data (as angular velocity of the camera-fixed inertial reference with respect to the droplets during freefall would appear as a linear acceleration of the droplet).
-Surface charge density was measured on the superhydrophobic surface using a \emph{Simco-Ion} FMX-004 electrostatic fieldmeter.
-This measurement was done with the superhydrophobic surfaces connected by a conductive ground plane by conductive tape, far away from the presence of other conductors.
-Some additional notes on idiosyncrasies of determining surface voltages (and thence surface charge densities) on insulative dielectric surfaces are provided in Appendix \ref{sec.surface_charge}.
-
-Droplets of distilled water, in a range of volumes ($0 \leq R_d \leq 1$mL), were very carefully deposited on the superhydrophobic surface in the final 1-5 minutes prior to the drop using an ungrounded glass syringe with $\pm 1\mu$L accuracy.
-Red tracer dye was added to improve trajectory digitization.
-During the drop, droplet trajectories were observed using a \emph{Panasonic} HC-WX970 Camera, shooting in high-speed mode at 120 fps and and 1/3000s shutter speed.
-In a few cases where higher frame rates were needed a \emph{Nikon} 1 J1 camera with a 30mm telephoto lens was used, shooting at 400 fps.
-The experimental test cell was illuminated with a 12V 6000K \emph{SEALIGHT} Chip-On-Board LED strip with a thin semi-opaque plastic film covering to make the light diffuse.
-The effect of static charges on spontaneously jumped droplet trajectories was studied in terms of the parameters droplet volume $V_d$, surface charge density $\sigma$, and a dependent variable, initial droplet jump velocity $U_0$.
-Since $q$ cannot be directly measured insitu during a drop (as high-input resistance electrometers, being notoriously fickle instruments, are not well suited to sudden 15-g decelerations), it was inferred from the statistical distribution determined in corollary experiments.
-The droplet charge determination is discussed in slightly more detail in Appendix \ref{sec.drop_charge}.
-
-\subsection{Superhydrophobic surfaces} \label{sec.suphydro}
-Wetting hysteresis.
-Methods of fabrication, comparison of wetting properties.
-Comparison of jump velocities between surfaces.
-Methods for determination of properties, roll-off angle, contact angle using \emph{SE-FIT}.
-Cassie-wenzel transition.
-Damping.
-Droplets are dyed red to improve the quality of image thresholding when digitizing the droplet trajectories during data reduction.
-
-%\begin{figure}
-%  \centerline{\includegraphics[height=7cm,width=13cm]{modes.eps}}
- % \centerline{\includegraphics[height=7cm,width=7cm]{e88_1_thumb.jpg}}
-%  \caption{SEM images for sandpaper and laser etched acrylic surfaces}
-%\label{fig:SEM}
-%\end{figure}
-
-\subsection{Data Reduction}
-Digitization of droplet trajectories requires several steps of post-processing.
-Video is first decomposed into a sequence of still images.
-Trajectories are captured using the particle tracking module in \emph{Fiji}\hl{[ref]}, a derivative of the popular \emph{ImageJ}\hl{[ref]} package for scientific image analysis.
-The series is stabilized to remove the effect of drop transients from the kinetmatic data[ref].
-The series of still images is cropped, and the background (that is, the low-entropy pixels) of the series is removed using a builtin ``rolling ball'' algorithm.
-Each still is then split into its constituent RGB maps.
-In this case the green channel images contained the most information, so these were then globally thresholded using the Triangle algorithm to recover a map of the pixels corresponding to the droplet's approximate position in the original still.
-Finally ellipses are fitted to the pixel map stepping through the time series to determine the positions of the centroid, and the semi-major and minor axes of the droplets during the drop.
-The results of the particle capture in \emph{Fiji} are shown in Figure \ref{fig:fiji}.
-Out of plane motion for `weakly 3D' trajectories is inferred from the change in tracked area of the droplet.
-Droplet positional data was smoothed ex post facto using a Savitsky-Golay filter.
-Additional details regarding the data smoothing methodology are presented in Appendix \ref{sec.smoothing}.
-
-\section{EHD Forces}
-As previously speculated the the force acting on the droplets as a surrogate for gravity are likely electrohydrodynamical in origin.
-In the hopes of unraveling the underlying mechanism for the electro-bouncing we turn to the electrodynamical approximation of fluids under the influence of electric fields.
-To that effect, what follows is a condensed overview of mathematical description of basic electrohydrodynamic flows.
-We first assume a DC electric field, such that $Re \langle \epsilon \rangle \approx  \mbox{constant}$, where $\epsilon$ is the dielectric permittivity of the respective media.
-We also assume that currents are small such that the effects of magnetic fields can be neglected.
-For the validity of this assumption to hold the characteristic time scale for electrical phenomena $\tau_e = \epsilon \epsilon_0/\sigma_e \ll 1$, where we note that $\tau$ is the ratio of absolute dielectric permittivity $\kappa = \epsilon \epsilon_0$, to conductivity $\sigma_e$, of the medium [ref].
-Given the respective conductivity, and permittivity of air ($\sigma_e = 2.5 \cdot 10^{-16}$ $\Omega^{-1} cm^{-1}$), we estimate $\tau_e \approx 400$s.
-This assumption also allows us to assume that the net charge present in the medium surrounding the droplets remains approximately constant during the typical time interval of a $\mu$-gravity experiment, and no transfers of charge occur after the droplet leaves the surface.
-\hl{[lol, check these numbers...]}
-
-\subsection{Maxwell Stress}
-If we suppose that electrical forces acting on free charges and dipoles in a fluid are transferred directly to the fluid itself, then this overall electrical body force will be the the divergence of the Maxwell stress tensor $\tau_m $, by
-
-\[ \mathbf{F}_e = \nabla \cdot \tau_m = \nabla \cdot \left( \epsilon \epsilon_0 \mathbf{E} \mathbf{E} - \frac{1}{2} \epsilon \epsilon_0 \mathbf{E} \cdot \mathbf{E} \delta \right) ,\]
-where $\mathbf{F}_e$ is the electric body force per unit volume, \hl{$\rho_f$ is the free charge density}, and $\delta$ is the delta function.
-The product of the electric field vectors is the dyadic product.
-
-The classical Korteweg-Helmholtz force density formulation of the Maxwell stress tensor is usually expressed as 
-\begin{equation}
-\mathbf{F}_e = \rho_f \mathbf{E} + \frac{1}{2} \left| \mathbf{E} \right|^2 \nabla \epsilon - \nabla \left( \frac{1}{2} \rho \left( \frac{\partial \epsilon}{\partial \rho} \right)_T \left| \mathbf{E} \right|^2 \right) ,
-\end{equation}
-and $\rho$ is the density of the dielectric fluid[ref].
-
-The first term in this expression, equivalently written as $q\mathbf{E}$, is the well known Coulombic force or electrophoretic force, which arises from the presence of free charge in an external electric field.
-The second term is the force arising from polarization stresses due to a nonuniform field acting across a gradient in permittivity.
-This force is widely termed the dielectrophoretic force (DEP).
-The third term describes forces due to electrostriction, however in our case $\left( \frac{\partial \epsilon}{\partial \rho} \right)_T = 0$ due to the  incompressibility of the fluid[ref].
-While it is a relatively rigorous approach, and a useful conceptual model, evaluating the force density in this fashion can be somewhat onerous.
-
-\subsection{Dielectrophoresis}
-An alternative approximation for the polarization stress is to idealize the droplet as a simple dipole using the effective dipole moment method first suggested by Pohl and Jones\hl{[ref][ref]}.
-This approach can be related back to the force density by means of a Taylor series expansion of $\mathbf{E}$ in the limit of a small gradient \hl{[ref]}.
-The DEP force is distinct from the Coulombic force in that net charge is not required, and that the force vector goes in the direction of steepest descent of the field, $\nabla \left| \mathbf{E} \right|^2$, rather than in the direction of $\mathbf{E}$.
-The DEP force is related to the dipole moment (induced or polarized) of polarizable media which has a tendency to align the dipole with the electric field.
-If there is a gradient in the field then for a finite separation of charge one end of the dipole will feel a stronger electric field than the other, resulting in a net force.
-Whether the force is positive or negative in the direction of the electric field gradient depends on the difference of dielectric permittivites between the fluids, rather than on the polarity of $\mathbf{E}$.
-It bears repeating that droplets will polarize in a uniform field, but since there is no gradient in the field the forces felt by the dipoles are symmetric and there is no net force.
-The dipole moment of a spherical dielectric particle immersed in a dielectric medium is given by
-\begin{equation} \label{dipole_m_1}
-\mu = V_d \mathbf{P} = \frac{4}{3} \pi R_d^3 \mathbf{P},
-\end{equation} 
-where $\mathbf{P} = \left(\kappa_1 - 1 \right) \epsilon_0 \mathbf{E}_{iz}$ is the polarization moment, and $R_d$ is the particle radius, \hl{($\kappa_1$ being the relative dielectric constant of the medium}, and $\mathbf{E}_{iz}$ is the $z$-coordinate component of the electric field internal to the sphere, assuming the external electric field to be oriented parallel to the $z$-axis).
-The excess polarization $\mathbf{P}_e$, in the sphere is given by
-\begin{equation} \label{polarization}
-\mathbf{P}_e = \left( \kappa_2 - \kappa_1 \right) \epsilon_0 \mathbf{E}_{iz} = \frac{3 \kappa_1}{\kappa_2 +2\kappa_1}\mathbf{E}_{iz},
-\end{equation}
-where $\kappa_2$ is the dielectric constant of the particle. Taking together equations \ref{dipole_m_1}, and \ref{polarization} we find that the effective dipole moment of the particle is given by 
-\begin{equation}\label{dipole_m_2}
-\mu = 4 \pi R_d^3 \left( \frac{\kappa_2 - \kappa_1}{\kappa_2 + 2 \kappa_1} \right) \kappa_1 \epsilon_0 \mathbf{E},
-\end{equation}
-and the force felt by the dipole is 
-\begin{eqnarray} \label{dep_force}
-\mathbf{F}_{dep} &=& \left( \mathbf{P}_e \cdot \nabla \right) \mathbf{E}\\
-&=& 2 \pi R_d^3 \kappa_1 \epsilon_0 \left( \frac{\kappa_2 - \kappa_1}{\kappa_2 + 2 \kappa_1} \right) \nabla E^2,
-\end{eqnarray}
-where it is a useful shorthand to refer to the permittivity ratio by $K = \frac{\kappa_2 - \kappa_1}{\kappa_2 + 2 \kappa_1}$, which is also known as the Clausius-Mossotti factor.
-In cases where $K < 0$, or $K>0$ the particle will be repelled or attracted to regions of strong field respectively.
-In our experiment, taking the relative dielectric constants to be $\kappa_1 \approx 1$ and $\kappa_2 \approx 80$, we have $K \approx 0.96$.
-One limitation of the effective dipole moment approximation of the DEP force is that it requires an assumption of small physical scale of the particle relative to the lengthscale of nonuniformity of the field, which in this case we take to be the length of the charged superhydrophobic surface ($L,H =25$mm $\gg a \approx 2.5$mm).
-Though the effective dipole moment is a successful model due in large part to its simplicity, it can be readily extended to include higher-order multipole effects, and non-spherical particles (oblate and prolate spheroids).
-An excellent summary of DEP theory in terms of the effective dipole moment is given in \hl{[ref]}.
-\hl{[Some notes on scaling ...]}
-
-\subsection{Forces due to Image Charges in the Dielectric}
-
 \section{The Electric Field}
@@
 
-\begin{figure}[htb]
-    \centering
-    \input{../figures/E0.pgf}
-    \caption{A simple EMA plot.\label{fig:E0}}
-\end{figure}
-
-\section{A Simple Dynamical Model}
-\subsection{Trajectory Equation}
-\subsection{Numerical Methods}
-
-\section{Comparisons}
-\section{Stability}
-\section{Conclusions}
-\appendix
-
-\section{\\Droplet Charge} \label{sec.drop_charge}
-\subsection*{Parallel Plate Method}
-Since, by the earlier scaling, we presuppose the source of the droplet bouncing behavior to be primarily Coulombic in origin (as opposed to dielectrophoretic), the droplet must have some net charge in addition to the charge induced by the electric field.
-To measure this charge concurrent methodologies were used.
-The first method of determining the droplet net charge is observation of the deflection of the droplets in the region of a known uniform field in a fashion inspired by Millikan's famous experiment to determine the fundamental charge of the electron [ref].
-
-Droplets were jumped in freefall from a sandpaper superhydrophobic surface placed between the plates of a parallel plate capacitor of known uniform electric field.
-The surface was first deionized using a balanced \emph{Ptec} IN5120 DC air-ionizer to remove the effect of surface charge of the superhydrophobic surface from perturbing the otherwise uniform field set up between the parallel plates.
-A schematic of the parallel plate drop apparatus is shown in Figure \ref{fig:millikan}.
-Since the droplet initial velocity $U_0$ is parallel to the electric field, the droplets are inertial in the direction of the electric force, and neglecting the effect of image charges mirrored across the conductors, we can determine the magnitude of the droplet charge by a balance of Coulombic force and inertia given by the equation of motion
-
-\[ \frac{d^2y}{dt^2} = q\mathbf{E}. \]
-
-Since the drag is negligible in the inertial limit we can find the charge $q$ by fitting a second-order least squares polynomial to the measured droplet positions, equating the $t^2$ term to the constant acceleration, and dividing by the known, constant magnitude of the electric field.
-From a survey of literature we suppose the droplet charge, if they are indeed charged by contact with PTFE, to be some function of the droplet volume and the residence time on the superhydrophobic surface.
-However, sweeping though droplet volumes over a series of drop tower experiments we find little correlation between droplet volume  and net droplet charge.
-This is shown in figure \ref{fig:drop_charge}.
-
-A 200-880 VAC source with a full wave bridge rectifier circuit was prototyped on perf-board for initial experiments to measure droplet charge.
-The circuit was analyzed on an laboratory oscilloscope to verify that the AC component of the signal was appropriately small (13 mV at 35 kHz).
-Current was determined to be a relatively low 80 $\mu$A.
-The high-voltage source terminals were led to two parallel polished 150x150 mm aluminum plate electrodes.
-The electrodes were mounted on an insulated 80/20 extruded aluminum rail for ease of adjustment.
-All droplet charge experiments were conducted with an electrode spacing of 28.30 mm.
-With this spacing the calibrated electric field between the plates was $\mathbf{E} \approx 35$kV/m.
-The electrodes were electrically isolated from the drop rig by two alternating layers of 4 mm thick laser cut acrylic sheet and Kapton tape.
-Potential across the plates was measured periodically with a load-impedance corrected multimeter to account for battery depletion.
-The typical capacitor rise time of the plates was measured to be 1.4 s, thus to make the most economical use of the brief window a micro-gravity a weighted switch was set by hand prior to the drop to close the high-voltage circuit, but which passively safed the system at the resumption of 1-g conditions in the tower.
-The drop apparatus is shown in Fig.
-
-%\begin{figure}
-%  \centerline{\includegraphics[height=7cm,width=13cm]{modes.eps}}
- % \centerline{\includegraphics[height=7cm,width=7cm]{e88_1_thumb.jpg}}
-  %\caption{Parallel plate experimental apparatus.}
-%\label{fig:millikan}
-%\end{figure}
-
-%\begin{figure}
-%  \centerline{\includegraphics[height=7cm,width=13cm]{modes.eps}}
- % \centerline{\includegraphics[height=7cm,width=7cm]{e88_1_thumb.jpg}}
-  %\caption{Parallel plates: Droplet net charge vs volume.}
-%\label{fig:drop_charge}
-%\end{figure}
-
-A brief screening experiment was conducted which alternated the polarity of the field by switching the positive and negative terminal leads between plates.
-Qualitative observations of droplet electrode preference seem to indicate that the assumption of small polarization stress was well founded.
-Following this a orthogonal array $3^2$ factorial design experiment with two replicates was conducted to test the effect of varying droplet volume and surface stay time on net charge at the time of jumping.
-It was hypothesized in accordance with previous studies \cite{Choi:2013dg}, that net charge would increase for levels of both factors.
-The results of the factorial experiment are presented in Fig.
-\ref{fig:chart1}.
-ANOVA analysis in \emph{R} of the linear multiple regression model for the data set indicates that neither droplet volume ($p=0.105$), nor surface stay time ($p=0.358$) is significant at the 95\% confidence level.
-The overall model F-statistics (2.177 in 2 and 13 degrees of freedom), and coefficients of determination ($r^2 = 0.2509$) indicate that the linear model neither fits the data particularly well, nor does it offer an improvement over the mean model.
-The mean charge was determined to be positive $2.3 \cdot 10^{-11}$ C, with a standard deviation of $1.8 \cdot 10^{-11}$ C.
-
-The failure of the model to describe the data raises interesting questions about the validity of our initial assumptions.
-Typical Reynolds numbers ($R_e=280$ average) indicate the general validity of the assumed quadratic drag model.
-The drag scale quantity given by Eqn.
-\ref{eqn:drag} was much less than 1 for all test runs, with mean value of $1.0\cdot 10^{-2}$ and a standard deviation of $2.0\cdot 10^{-3}$, which adds credence to a force balance of pure inertia and electrostatic force.
-
-One obvious issue, in retrospect, is that while we know the characteristic charging time for the droplets to be some function of droplet volume, \hl{[it has been shown to have a time constant dramatically smaller than that of a typical experimental timescale]} so we might have looked only for the charge as a function of volume, both on physical grounds and due to the conflation of the variables.
-
-Also of concern is that droplets in three of eighteen runs exhibited accelerations opposite to the expected direction.
-There is no pattern to the distribution of anomalous droplet accelerations, as they all occurred at unique level combinations.
-There are only four obvious ways of explaining this anomaly.
-The first is that the electric field is in fact non-uniform and polarization stress is non-negligible in this geometry.
-This option seems unlikely owing to the fundamental design of the experimental apparatus; \hl{[see figure from Agros2D FEM solution]}.
-A second possibility is that the few contrarian droplets actually accumulated net negative charge, instead of the net positive charge to be expected on the basis of evidence from some of the aforementioned studies.
-This is not impossible, and would also go some length to explain the variance in the measured charge generally.
-A third possibility is that another force neglected in this analysis, with some component in the direction opposite of the electric field, has an $\sim \mathcal{O}(1)$ magnitude.
-In principle this could for instance include the image charges which will subject the droplets to a force $\mathbf{F} = q^2/4 \pi \epsilon_0 d$ when ``close'' to one of the conductive plates (that is, when the plate can be treated as an infinite grounded conductor).
-However, this formulation of the image charge effect clearly does not describe the force close to the centerline where the Green's function needs to add additional sets of images to satisfy the boundary conditions of $\nabla^2 \varphi = 0$ in this geometry.
-To the knowledge of the author there is not a convergent series solution in the parallel plates geometry as yet.
-
-The droplet positive net charge developed by contact with a PTFE surface corresponds to findings elsewhere in literature \cite{Choi:2013dg} \cite{Miljkovic:2013dg} \cite{Moreno-Villa:1998dg}.
-The smallest droplet size treated in the present work is several times larger than the largest in any of comparable study.
-The most relevant comparison found droplet static charge of 2.5e-10 C for 10 $\mu$L droplets charged by pipetting from a PTFE tipped needle \cite{Choi:2013dg}.
-The present results mean charge level of 2.3e-11 C is, within error, roughly six times smaller than the cited study.
-
-\subsection*{Direct Measurement}
-A second approach to determining the net droplet charge is by direct measurement in a shielded Faraday cup using an extremely high input resistance electrometer, specifically a \emph{Keithly} 616 digital electrometer.
-\hl{[note on operational philosophy, data collection].
-Correlation of net charge to droplet volume is shown again for in figure} \ref{fig:electrometer}.
-
-%\begin{figure}
-%  \centerline{\includegraphics[height=7cm,width=13cm]{modes.eps}}
-%  \centerline{\includegraphics[height=7cm,width=7cm]{e88_1_thumb.jpg}}
- % \caption{Electrometer: charge vs. volume.}
-%\label{fig:electrometer}
-%\end{figure}
-
-[Discussion on discrepancy between the two approaches.]
-
 \end{document}

### 2018-01-23 doc/manuscript/introduction.tex
added complete, intro, theory, and methods sections

@@
 \usepackage{graphicx}
+\graphicspath{ {../figures/} }
+%\usepackage{svg}
 \usepackage{color,soul}
@@
 
+\usepackage[
+backend=biber,
+style=phys,
+sorting=none
+]{biblatex}
+\addbibresource{thesis.bib}
+
 \begin{document}
@@
 
+\newpage
 \section{Introduction}
+\begin{quote}
+``When the influence of gravity on fluid behavior is diminished or removed, other forces, otherwise of small significance, can assume paramount roles.''
+- NRC Report to NASA, 2003  \cite{motil_priorities_2012}
+\end{quote}
+
 Our terrestrially born intuition about how liquids flow is easily confounded in a low-gravity environment.
@@
 This 1-g cognitive bias leads to a plethora of problems which are both trivially easy to solve in 1-g, and which despite decades of study continue to elude solutions in a low-gravity context.
-One example of these problems is the so-called "phase separation" problem of separating a gas phase from a multi-phase flow (or the reverse case) without the aid of gravitational buoyancy.
-Sans buoyancy otherwise mundane activities such as venting a gas or settling a liquid in a tank become problematic.
-Trapped bubbles can vapor lock ECLSS (Environmental Control and Life Support), power, or propulsion systems.
-Issues of phase separation have so bedeviled human endeavors in space that an entire Apollo Saturn 1B mission (AS-203) was earmarked to study them.
+One example of these problems is the so-called ``phase separation'' problem of separating a gas phase from a multi-phase flow (or the reverse case) without the aid of gravitational buoyancy.
+Sans buoyancy otherwise mundane activities such as venting a gas or settling a liquid in a tank become problematic \cite{petrash_controlling_1964}.
+Trapped bubbles can vapor lock ECLSS (Environmental Control and Life Support), power, or propulsion systems \cite{jenson_passive_2014}.
+Issues of phase separation have so bedeviled human endeavors in space that an entire Apollo Saturn 1B mission (AS-203) was earmarked to study them \cite{hastings_[saturn_1965}.
 This problem has for some time motivated a quest for substitute body forces, and the present work follows in that august tradition.
 
-When asked to name one of the biggest challenges to living in
-space, Astronaut Suni Williams replied that it is removing and
-dealing with bubbles in fluids systems.
+Considering the scope of this problem of poor low-gravity intuition, we would profit by identifying a scale to quantify how wrong our intuition is.
+First, let's clear up a common misnomer about the state of ``zero-gravity''.
+The theory of general relativity is based on the fundimental equivalence of gravity and acceleration.
+There is no known way to determine whether one is in gravity-free space or free-falling in a gravitational field (or conversely whether or not we are uniformly accelerating, or standing at rest in a gravitational field).
+This is sometimes called the equivalence principle of general relativity (e.g.
+the equivilence of gravitational and inertial mass).
+In theoretical terms a zero-g experiment performed in a drop tower on the surface of the Earth is equivalent to the same experiment performed in the nearly gravity-free deep space between galaxies, despite the fact that the drop tower itself is in a 1-g gravity field.
+At the orbital altitude of the Internation Space Station (ISS) the gravity level is still nearly 90\% of its value at sea-level on Earth, but the astronauts aboard ISS feel weightlessness because they are free-falling.
+In a practical sense there is never true zero-g, even in the aforemention dark space between galaxies, as there are always small, but nonetheless, measureable forces to accelerate any body.
+For instance in low-Earth orbit, accelerations due to drag in the tenuous outer atmosphere are on the order of $1 \times 10^{-6}$ g, hence the term ``microgravity''.
+This small acceleration provides an ersatz gravity, but there are also other forces present.
+Foremost of these are capillary forces.
 
-\begin{quote}
-``... multiphase systems and thermal transport processes are enabling for proposed human exploration by NASA.''
-- 2011 Decadal Survey
-\end{quote}
+Capillary forces are due to the cummulative effect of a large number of very short range molecular interations and in a 1-g context are usually quite weak, relatively speaking.
+However, in a low-gravity environment these are nearly the only forces present, and are therefore strong in a relative sense.
+In comparing the relative magnitudes of gravity and the unusually strong capillary force we arrive at a useful figure of merit for assesing how wrong our fluid mechanical intuition is likely to be in a low-gravity context.
+This figure of merit is the Bond number dimensionless group
+\[ \mathbb{B}\mbox{o} \equiv \frac{g R^2 \Delta \rho}{\gamma} 
+\]
+where $g$ is the acceleration, $R$ is the interfacial radius of curvature, $\Delta \rho$ is the difference in densities across the interface (which simplifies to $\rho$, for large $\Delta \rho$, as in the case of a air-water interface), and where $\gamma$ is the surface tension.
+In cases where $\mathbb{B}\mbox{o}$ is small, a liquid is effectivly in low-gravity regardless of the nominal local gravity level.
+Very small droplets ($R < 1$ mm), for instance, are in low-gravity for all intents and purposes and have nearly spherical shapes.
+Contrarily, in a space environment in cases where $R$ becomes large, such as with the case of large diameter spacecraft propellant tanks then $ \mathbb{B}\mbox{o} \gg 1$ even though the acceleration is small.
+As a corrallary to this discussion we note that on the basis of dimensional similarity, we can accurately simulate the low-gravity fluid mechanics of large propellant tanks even in small drop towers simply by scaling dimensonless groups like the Bond number.
 
-\begin{quote}
-``When the influence of gravity on fluid behavior is diminished or removed, other forces, otherwise of small significance, can assume paramount roles.''
-- NRC Report to NASA, 2003
-\end{quote}
+As with surface tension, electrostatic forces also have useful applications as substitutes for gravity.
+Electrohydrodynamic (EHD) body forces have been suggested to combat thermal stratification of propellants under low-g conditions where bouyancy induced natural convection is very small \cite{blackmon_collection_1965}.
+In this case electro-convection is an analog of natural convection due to a dielectric permitivity gradient (as opposed to a fluid density gradient), which is a function of fluid temperature, in the presence of a body force field (in this case an electric field).
+The study also suggested applications in cryogenic tank vent screening, and in reducing heat transfer to cryogenic propellants (and thus boiloff losses) by dielectrophoretically positioning ullage vapors around the tank walls as a thermal barrier.
+EHD forces have been studied for enhancing boiling heat transfer by promotion of bubble detachment and prevention of dryout (again as an ersatz bouyancy) \cite{snyder_dielectrophoresis_2001} \cite{di_marco_influence_2003} \cite{marco_use_2012}.
+EHD heat pipes, which substitute an electrode structure for the capillary wicking structure of a conventional thermocapillary heat pipe can evade the wicking limit \cite{jones_electrohydrodynamic_1973}.
+These are restricted to the use of insulating dielectric liquids (which usually have relatively low thermal conductivity), but are highly robust against dryout, support active flow control, and have low viscous losses.
+Dielectrophoretic settling of cryogenic propellants (in both total and partial communication configurations), has been studied analytically in both static \cite{hurwitz_electrohydrodynamic_1966} and dynamic cases \cite{koval_dynamics_1967}, and in drop tower experiments \cite{fax_dielectrophoretic_1969}.
+EHD forces have also beeen suggested for low-g slosh baffling \cite{boretz_orbital_1970} \cite{petrash_use_1968} \cite{hurwitz_dielectrophoretic_1968}, and studied extensively for the mitigation of vapor pullthrough during tank emptying (and concomittent minimization of propellant residuals at burnout) in a series of experiments at the NASA Lewis (now Glenn) Research Center 2.2 s drop tower facillity \cite{berenyi_dielectrophoretic_1970}.
 
-Un-terrestrially large droplets are produces by a huge array of mechanisms in a low-gravity environemnt.
+\subsection{Spontaneous Droplet Jump}
+Low-gravity droplet dynamics, and the dynamics and applications of the so-called spontaneous droplet jump, is an active area of study at the Portland State University Dryen Drop Tower labratory (DDT).
+When a nonwetting, gravity dominated sessile droplet (e.g.
+a puddle), initially at rest in the Cassie-Baxter state undergoes a large step reduction in $\mathbb{B}\mbox{o}$ it will spontaneously jump away from the surface.
+The Cassie-Baxter state is a metastable non-wetting state on a textured surface, sometimes also known as the Fakir state.
+This was first observed experimentally by Kirko \emph{et al.} \cite{kirko_phenomenon_1970} in 1970 and later by Wollman \emph{et al.} in 2006 in a set of experiments conducted using a low-gravity drop tower \cite{wollman_more_2016}.
+The kinetic energy of the jump is supplied by the defect in free surface energy as the new minimum energy surface equilibrium has approximately constant curvature.
+If the viscous energy losses by shear, and internal flows during roll up are neglected, as well as energy lost due to the hysteresis of the dynamic contact line, then the available kinetic energy is given by
+\[KE = SE_2 -SE_1 = [(\sigma A)_{gl} + (\sigma A)_{sg}]_2 - [(\sigma A)_{ls} + (\sigma A)_{gl} + (\sigma A)_{sg}]_1. \]
 
-Comprehensive list? of electrostatic applications particular to low-gravity:
+The droplet `rolls up' as it jumps away from the surface due to radial motion of a capillary wave away from the contact line.
+The characteristic time scale of the rolling up scales as $t_j \sim R_p/U ~(\rho H R^2_p/\sigma)^{1/2}$ \cite{attari_puddle_2016}, which resembles the contact time, $\tau \approx 2.6(\rho R^3_d/\sigma)^{1/2}$ reported by Richard \emph{et al.} in 2002 for the related problem of droplets impacting hydrophobic surfaces in 1-g \cite{richard_surface_2002}.
+For droplets with radial symmetry and sufficiently high initial $\mathbb{B}\mbox{o}$ these waves coalesce as a shock leading to geysering and creation of satellite drops by the Rayleigh-Plateau breakup of the geyser.
+In the case of smaller jumping droplets, the capillary waves do not lead to geysering, and are viscously damped to varying degrees during the brief free-fall period of the drop tower.
+
+The spontaneous droplet jump phenomenon provides a useful window though which to study the dynamics of large-length scale capillary dominated droplets.
+The physics of such massive droplets (far beyond the 1-g millimetric capillary length scale) utterly defy terrestrial expectations about the ways in which liquid droplets `should' behave, and also are of critical practical importance in a space systems setting where large capillary length scale multiphase flows are common.
+
+\subsection{Droplet Electro-bounce}
+During `rolling-up' under ideal conditions, the droplet jump phenomenon is governed by a balance of inertia and surface tension forces, and once aloft the droplet motion is nominally in a regime of pure drag, however other forces can again come into play.
+
+\emph{Occasionally we observe jumped droplets to decelerate and return to the superhydrophobic surface, rebounding multiple times after fashion of a rigid body bouncing on a surface under 1-g.
+The forces at work in this phenomenon are presumably electrostatic in origin.} This was unintended, but the phenomenon is interesting.
+Admittedly, there is a certain irony that this typical failure of low-gravity intuition come as any surprise to experienced low-gravity researchers.
+A time-lapsed composite image showing an example of the phenomenon is shown in Figure \ref{fig:bounce}.
+
+\newpage
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.75\textwidth]{bounce}
+\caption{The trajectory of a $0.5$ mL droplet is captured in a composite image over a single bounce period ($\sim 1.25$ s).
+The surface potential of the superhydrophobic dielectric is $1.25 \pm 0.41$ kV.
+\label{fig:bounce}}
+\end{figure}
+
+This ``electro-bounce'' phenomenon is the subject of this thesis. We begin with some preliminary observations of the phenomenon:
 \begin{itemize}
-\item Spacecraft charging due to space environment.
-Surface charging largely due to low energy electrons (3-50 keV) which do not penetrate the surface of the spacecraft external stureture.
-This deposited charge accumulate  and can lead to significant potential differences between different parts of a spacecraft.
+\item We have observed droplet accelerations on the order of 10's of cm/s$^2$ in proximity to charged surfaces.
+\item Droplets appear to be attracted to regions of high electric field.
+The horizontal (surface plane parallel) components of the droplet trajectory usually oscillate about their initial position during drops (except in cases of nearly pure 1-D vertical translation).
+For especially small drops close to the spontaneous droplet jump limit ($V_d \sim 0.01$ mL) the droplets do not jump, but translate across the surface in a hovering regime until either they reach a local maximum of the electric field, or until their motion is sufficiently damped by contact line hysteresis that pinning arrests their motion.
+\item Droplets appear to have net free charge. In cases of multiple simultaneous droplet jumps the droplets repel each other as they bounce or hover in orbital motion around regions of strong field.
+\item The magnitude of the droplet trajectory maxima (apoapses) appear to be related to the droplet volume (which affects their mass, and initial jump velocity, and thence their inertia), and to the electric field strength.
+\end{itemize}
+
+There are several potential origins of the electric charge responsible for this phenonenon.
+It is well known that water acquires free charge (usually positive) when in contact with certain polymers, especially polytetrafluoroethylene (PTFE) \cite{langmuir_surface_1938}, through a process called contact charging.
+The superhydrophobic surfaces used in the spontanous droplet jump experiments have thin PTFE coatings, and we observe that it is extremely easy to produce significant surface potentials ($\sim 100-500$ V) by simply running streams of filtered water over them.
+A study of this water on PTFE contact charging phenomenon was done by Yatsuzuka \emph{et al.} \cite{yatsuzuka_electrification_1994}, who suggest this process results from formation of an electrical double layer formed by selective adsoption of ions at the polymer surface.
+They also found that the specific charge on the droplets in contact with the surface depends on their surface velocity and conductivity.
+New developments suggest that adsoption of $OH^-$ ions are the source of the double layer \cite{beattie_intrinsic_2006} \cite{strazdaite_water_2015}.
+This is the most likely accidental source of charge on the suphydrophobic surface.
+Given the large roughness (in the sense of the ratio projected to actual surface area), of the superhydrophobic surfaces used in the experiment, and given that the droplets are initially in a Cassie-Baxter state, an electrically insulating air layer is maintained that prevents grounding of the droplets despite the large potential difference between them and and the surface charges.
+Ultimately it is this potential, in the energetic sense, that is responsible for the droplet bouncing motion we observe.
+
+The source of the net free charge on the droplets is another issue.
+The droplet charge could also be due to this contact charging mechanism.
+For instance, in a 1996 paper, NASA flight engineer Don Pettit discusses the problem of flow induced charging of liquids in a low-gravity context, resulting ultimately from contact charging phenomenon \cite{pettit_donald_flow_????}.
+Another mechanism for the droplet charge is field induced charging.
+Field induced charging occurs due to physical breakup of a conductor having a field induced dipole.
+In our case this occurs when the droplet is deposit on the charged surface by a syringe.
+The metal syringe needle tip, and the liquid in the syrigne itself are essentially a ground connection which is broken when the syringe is removed.
+Field induced charging is at work in the famous Kevin thunderstorm, and is applied in inkjet, and electrospay technologies (where in each case the breakup is by the Rayleigh-Plateau instability).
+Notably, in Pettit's discussion of contact charging of liquids in low-g, he remarks on accidental electrostatic ``hula-ing'' of sillicon oil droplets when ejected from a syringe in the vicinity of a highly-charged polymer surface during an experiment conducted aboard STS-5 by mission specialist Joseph Allen.
+Depending on the (highly-variable) electrical conductivity of the sillicon oil, and the material of the syringe used in the experiment, the charge could as easily be field induced as due to contact charging.
+Relatedly, in a series of informal, and somewhat whimsical experiments Pettit electrostatically orbited small water droplets around a triboelectrically charged PTFE knitting needle while aboard ISS during expedition 30/31 \cite{stevenson_electrostatic_2015}.
+Again, in this case, the droplet charge is very likely field induced.
+
+\subsection{Applications}
+Study of the droplet electro-bounce phenomenon may have results which can be extended to useful applications in a space environment.
+
+External surfaces of spacecraft tend to become charged with time due to the space environment itself.
+Surface charging largely occurs due to low energy electrons (3-50 keV) which do not penetrate the surface of the spacecraft external stucture \cite{czepiela_charging_1997}.
+This deposited charge accumulates and can lead to significant potential differences between different parts of a spacecraft, sometime leading to breakdown and discharge, called Paschen discharge.
 Deep dielectric charging occurs when higher energy charged particles penetrate the surface of a dielectric material, which can also lead to large potential differences if the dielectric leakage is lower than the external charging rate.
 The ultimate sources of these charges are trapped charged particles of the van Allen radiation belts, galactic cosmic rays, and the solar wind.
-\hl{Which space environemts have higher charging risks, propellant deopt locations}.
-Venting, droplets.
+In a fluid mechanical context, this accumulated charge could be problematic during any multiphase venting process, as might be expected to occur during autonomous satellite servicing refueling operations, or during boil-off venting of cryogens stored over long periods in a space environment (as in crewed Mars missions, or in propellant depot operations).
+Such venting, if uncontrolled, can lead to contamination of spacecraft surfaces by the propellant.
 
-\item Active (but solid-state) phase seperation for ECLSS multiphase flows, espcially high void-fraction flows (dish washing, laundry, waste solids drying, food processing, Sabatier CO$_2$ reaction, possibly in vapor-compression cycle condensers).
-Phase separation is critical to high reliability and low power gas-liquid systems for used in thermal control and life support.
-Phase seperation for other disperse droplet flows include electrostatic droplet seperators for high-efficiency Rankine cycle turbines.
-Removal of satellite droplets produced during pippetting during wet-lab research outside of a glovebox environemnt aboard ISS.
+As previously noted, robust phase separation is critical to high reliability multiphase systems used in thermal control and life support.
+Active (but solid-state) phase seperation for ECLSS multiphase flows, espcially high void-fraction flows is a possible application of this work.
+Such flows pertain to dish washing, laundry, waste solids drying, food processing, the Sabatier CO$_2$ reaction, and possibly in vapor-compression cycle condensers.
+Phase seperation for other disperse droplet flows include electrostatic droplet seperators for high-efficiency Rankine-cycle turbines (which require a droplet-free vapor phase entering the turbine, but where convertional superheat approaches comes with severe mass penalties) \cite{unterberg_zero_1962}, or more speculatively, in high temperature liquid droplet radiators with electrostatic collection \cite{white_liquid_1987}.
+Removal of satellite droplets produced during pippetting in wet-lab research outside of a glovebox environment aboard ISS has also been recently suggested as a application of the work \hl{[ref, personal discussion with NASA MSFC folk at ASGSR17 conference]}.
+Droplets can become spontaneously charged by contact with standard micropipette tips \cite{choi_spontaneous_2013}, and this free charge can possibly be leveraged for the purposes of phase separation in low-gravity.
 
-\item Electrostatic levitators for containerless processing, droplet combustion experiements.
-Containerless creatio, and collection of monodisperse spheres (dielectrics or conductor; the chargeing mechanism will vary).
+\subsection{Overview of this Thesis}
+This work primarily concerns itself with development of a simple model to aid in design of future electrostatic disperse droplet phase separators. To that end this work encompasses:
+\begin{enumerate}
+\item A simple mathematical model of droplet electro-bounce, its scale analysis, and asymptotic estimates for droplet peak apoapses and times-of-flight.
+\item The results of a controlled experiment, where the effect of key independent variables droplet volume $V_d$, and dielectric surface charge density $\sigma$, on droplet trajectories is tested.
+\item Science of opportunity comprising experimental data on droplet impacts at very low Weber and Ohnesorge numbers, for varying levels of electrostatic Bond number. 
+\end{enumerate}
 
-\item Electrospray-based fire suppression systems.
-
-\item EHD (dielectrophoretic) augmentation of convection (electroconvection, an analog of natural convection due to a dielectric permititivy gradient, which is a function of fluid temperature, int he presence of a body force field analog, in this case an electric field) and condensation heat transfer.
-Boiling heat transfer by promotion of bubble detachment and prevention of dryout (e.g.
-as a substitute for bouyancy).
-
-\item EHD heat pipes, which substitude an electrode structre for the capillary wicking structure of a conventional thermocapillary heat pipe can evade the wicking limit.
-Problematically restricted to the use of insulating dielectric liquids (which usually have relatively low thermal conductivity), but offer advantages in highly-reliable priming, bubble rejection, flow control, and low viscous losses.
-
-\item Dielectrophoretic settling of cryogenic propellants (in both total and partial communication configurations), slosh baffling, vent screening, mitigation of vapor pulltrough (and concomittent minimization of propellant residuals at burnout).
-Reduction in heat transfer by collecting propellants away from tank walls, reducing boiloff losses.
-
-\item High temperature liquid droplet radiators with electrostatic collection.
-\end{itemize}
-
+\printbibliography
 \end{document}

### 2018-01-23 doc/manuscript/methods.tex
added complete, intro, theory, and methods sections

--- 2018-01-18 doc/manuscript/parameter_estimation.tex
@@
 \usepackage{graphicx}
+\graphicspath{ {../figures/} }
+%\usepackage{svg}
+\usepackage{verbatim}
 \usepackage{color,soul}
@@
 \begin{document}
+
 \doublespacing
+\section{Overview}
+Mainly we are concerned about what parameters are important in electrostatic transport of relatively large (e.g.
+millimetric) droplets in low-gravity, and what the values of the respective dimensionless groups, namely $\mathbb{I}\mbox{m}$, $\mathbb{E}\mbox{u}$ and ${\mathbb{E}\mbox{u}}_+$ might be.
+
+To find typical vales of these parameters we used the following approach:
+\begin{enumerate}
+\item We observed spontaneous droplet jumps on charged dielectric super-hydrophobic surfaces under low-gravity conditions in a $2.14$ s drop tower, while varying the independent variables $V_d$, $\sigma$.
+However, this raises an interesting challenge; it is impractical to directly measure all of the key physical quantities that appear in the dimensionless groups at once in a drop tower experiment.
+In particular, determination of net droplet free electric charge $q$, is difficult.
+\item Using high-speed video and image analysis software we captured the trajectories of the droplets. 
+\item We solved the inverse problem to find the key parameters by maximizing a statisitical likelihood function between an observed trajectory and the trajectory predicted by a dynamical model given that certain set parameters.
+The best fit parameters obtained by direct-search optimization are those corresponding to the maximum likelihood experimental values.
+The optimization is constrained by the measurement precision of directly measured independent, and dependent variables.
+\end{enumerate}
+
+\begin{figure}[ht]
+ \centering
+ \includegraphics[width=0.75\textwidth]{../figures/apparatus0.pdf}
+ \caption{Caption.\label{fig:apparatus0}}
+\end{figure}
+
+\begin{figure}[ht]
+ \centering
+ \includegraphics[width=0.75\textwidth]{../figures/SEM.pdf}
+ \caption{Caption.\label{fig:SEM}}
+\end{figure}
+
+\begin{figure}[ht]
+ \centering
+ \includegraphics[width=0.75\textwidth]{../figures/schematic.pdf}
+ \caption{Caption.\label{fig:schematic}}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \def\svgwidth{\columnwidth}
+    \input{../figures/rig.pdf_tex}
+    \caption{Caption.\label{fig:rig}}
+\end{figure}
+
+\section{Experimental Methods}
+\begin{itemize}
+\item A very low-tech superhydrophobic electret was produced, with surface potentials 0.7-4.0 $kV$ and contact angles $\sim 150^{\circ}$ with approximately $20^{\circ}$ contact angle hysteresis when uncharged.
+The dielectrics are a lamina of 3-4 corona charged 0.4 $mm$ PMMA sheets.
+The electric field scales with the number of dielectric lamina.
+The final, superhydropobic layer, is produced by laser etching PMMA, and depositing a thin layer of PTFE on the resulting roughness topology to increase the Young's angle.
+The surface charge density can be modulated during the experiment by means of a 0-2 $kV$ DC-DC converter, which can re-polarize the dielectric substrate by means of an embedded electrode, and the resulting bound charge partially or fully neutralizes the electric field due to the surface ions deposited by corona charging of the electret.
+\end{itemize}
+
+Superhydrophobic substrates were placed on a drop tower rig platform.
+The rig is released by a solenoid chucked pin at the same moment the exterior drag shield is allowed to fall.
+This decouples drag acceleration felt by the drag shield from the experiment which experiences approximately $1 \cdot 10^{-6}$g of high quality freefall for the 2.1s required for the rig/drag shield assembly to reach the bottom of drop tower 6 floors below.
+
+The superhydrophobic surface was treated with PTFE spray for the first experiment of the day, and approximately every $3^{\mbox{rd}}$ drop following.
+The general properties and details of the fabrication of these superhydrophobic surfaces are discussed in Section [ref].
+Shortly before each drop the surfaces were briefly rinsed with distilled water, and then dried under a fume hood for about 10 minutes.
+The drop rigs were balanced to prevent unintentional torques from contaminating the kinematics data (as angular velocity of the camera-fixed inertial reference with respect to the droplets during freefall would appear as a linear acceleration of the droplet).
+Surface charge density was measured on the superhydrophobic surface using a \emph{Simco-Ion} FMX-004 electrostatic fieldmeter.
+This measurement was done with the superhydrophobic surfaces connected by a conductive ground plane by conductive tape, far away from the presence of other conductors.
+Some additional notes on idiosyncrasies of determining surface voltages (and thence surface charge densities) on insulative dielectric surfaces are provided in Appendix [ref].
+
+Droplets of distilled water, in a range of volumes ($0 \leq R_d \leq 1$mL), were very carefully deposited on the superhydrophobic surface in the final 1-5 minutes prior to the drop using an ungrounded glass syringe with $\pm 1\mu$L accuracy.
+Red tracer dye was added to improve trajectory digitization.
+During the drop, droplet trajectories were observed using a \emph{Panasonic} HC-WX970 Camera, shooting in high-speed mode at 120 fps and and 1/3000s shutter speed.
+In a few cases where higher frame rates were needed a \emph{Nikon} 1 J1 camera with a 30mm telephoto lens was used, shooting at 400 fps.
+The experimental test cell was illuminated with a 12V 6000K \emph{SEALIGHT} Chip-On-Board LED strip with a thin semi-opaque plastic film covering to make the light diffuse.
+The effect of static charges on spontaneously jumped droplet trajectories was studied in terms of the parameters droplet volume $V_d$, surface charge density $\sigma$, and a dependent variable, initial droplet jump velocity $U_0$.
+Since $q$ cannot be directly measured insitu during a drop (as high-input resistance electrometers, being notoriously fickle instruments, are not well suited to sudden 15-g decelerations), it was inferred from the statistical distribution determined in corollary experiments.
+The droplet charge determination is discussed in slightly more detail in Appendix  [ref].
+
+\subsection{Electrets}
+
+\begin{figure}
+    \centering
+    \input{../figures/hysteresis.pgf}
+       \caption{Charge decay.\label{fig:hysteresis}}
+\end{figure}
+
+\begin{itemize}
+\item The method for determination of the evolution of the surface charge density for low conductivity polymers is described in \hl{[Davies, 1967]}.
+Surface charge in injected into the surface of the dielectric mounted on top of an grounded electrode.
+The charge decay is measured with a calibrated probe at periodic intervals.
+\item Additive stacking of electrets has been used in electret based vibrational energy harvesters \hl{[Stacking Electrets for Electrostatic Vibration Energy Harvesters, Wada et al.
+2012]} and in water desalinization \hl{[ref Application of electret technology to low cost desalination, R.C.
+Amme, 2002]}
+\item There are several charge decay mechanisms: internal ones, such as Ohmic resistence, and external ones such as compensation by envonmental ionic species.
+The relative magnitudes of these charge transport mechanisms, and therfore the stability of the electret varies drastically depending on its initial surface potential, material properties, environment, and charging method.
+In the case of unshielded electrets compensation by atmospheric ions is significant \hl{[E.W.
+Anderson et al, 1973]}.
+Because envornmental convection will tend to  maintain a gradient of these ions, sealing an electret in a container from the atmosphere will effectively halt this decay mechanism.
+Atmospheric humidity and water droplet condensation also significantly increase charge decay (presumably by reducing the surface resistence) \hl{[Haenen, 1975]}.
+\item According to \hl{[Sessler 1987]} an electret is a dielectric material with ``quasi-permanent'' electric charge in the sense that the characteristic decay period of the electret is much greater than a given period of interest.
+\item Electret charge may be `true' charge in the form of surface or space charges, or polarization charges (such as bound charges).
+If the electret is not screened by a conductor then it produces an external electric field if the polarization and real charges do not uniformly compates each other throughout the volume of the electret.
+For this reason electrets are though of as electrostatic analouges to permanent magnets (and the name \emph{electret} itself is a portmantau to the effect conjured by Heaviside in 1892 \hl{[ref O.
+Heaviside, 1982]}).
+Typical commerical electrets are Teflon type polytetraflouroethylene (PTFE) polymer films on the order of 10-50 $\mu$m thick with the charge being primarily real surface charge.
+Electrets have a plethora of applications, but most germanely they have been used in Electro-Wetting On Dielectric (EWOD) devices for low-voltage manipulation of small droplets \hl{[Wu, 2010]}.
+\item Real charge electrets can be produced by contact electrification, injection or deposition) of charge carriers by discharge or electron beam, ionizing radiation, or by frictional triboelectrification.
+Dipolar electrets by contrast are produced by a combination of polarization at elevated temperatures in a strong external electric field, followed by an annealing process.
+\item Effective surface charge densities are limited to the material dielectric strengths due to internal dielectric breakdown phenomenon (this typically occurs before external breakdown or Paschen breakdown).
+\item We use an isothermal electret formation process using a variation of the widely applied corona-charging technique.
+The typical corona-charging technique uses strong inhomogenous DC electric fields to produce discharge in air at ambient conditions; the dielectric substrate is atop a grounded electrode, and there is a screening potential electrode intermediately positioned to control (the the surface potential of the dielectric will tend to saturate at this grid potential if the material is not space-charge current limited).
+The corona field is usually produced by pin-shaped electrode.
+In air the most common charge carriers thus produced are $\mbox{CO}_3^-$ ions.
+This approach is known to generally produce samples with fairly uniform surface charge densities.
+\item Some work \hl{[ref J.
+van Turnhout, 1975]} showed using a Thermally Stimulated Current (TCS) measurements that in 4.8 mm thick polymethyl methacrylate (PMMA) polarization of the dielectric is non-uniform, due to real space-charge mostly ($\sim$90\%) residing in a thin (0.1-0.2 mm) layer near the free-surface of the sample.
+\item \hl{Notes on our version of the corona-discharge process, figure, plot of charge decay}.
+\item We plainly see a cross-over effect in the decay of the surface potential in our electret samples, whereby the samples charged to higher initial surface potentials decayed faster and reached the lower overall final potentials.
+This is a well known effect in polyethylenes charged by corona \hl{[Ferreira et al.
+1992]}
+\end{itemize}
+
+\subsubsection{Surface charge density}
+Since the laser-etched PMMA superhydrophobic surface is a dielectric material there are some additional considerations for determining the surface charge density.
+Firstly, for an insulated conductor $A$ with charge $q$, the charge distribution in equilibrium will be such that the field on the interior of the conductor is zero, with field lines being normal to the surface and the integral of the field strength $\mathbf{E}$ from any point $P$ in or on the conductor to a ground point $G$ is a constant given by
+\[ V = \int^G_P \mathbf{E} \cdot da, \]
+where $V$ is the voltage or potential of the conductor (or alternatively, the surface voltage potential). The voltage $V$ and the charge $q$ are proportional and $q$ is usually given by
+\[q = CV, \]
+where $C$ is the capacitance of the insulated conductor and is determined by the conductor's size and shape, and its placement relative to the conductors and ground.
+However, the case of a charged insulator departs significantly from that of the insulated conductor.
+Here we have the possibility of the density and net polarity of the charge varying as a function of position about the surface.
+The field of the interior may not be zero, and the field lines are not necessarily normal to the the surface.
+The integral of the field strength from a point on or in the insulator to ground is usually different from point to point.
+In general the surface voltages will vary from point to point on an insulator (including point on the interior of the insulator.
+Therefore it is not possible to uniquely define the voltage of a charged insulator, except in certain contrived cases (notably the the potential of a uniformly charged sphere positioned infinitely far away from any conductors).
+It follows that there is no definition for the capacitance of an insulator as well.
+Though insulative sheets may store charge and discharge in the manner of capacitors, this discharge is never particularly complete.
+
+There are two cases where we can make meaningful quantitative measurements of state variables for charged insulators: we can measure the electric field arising from the charge, and possible the total charge for uniformly charged free insulative sheets, and uniformly charged insulative sheets backed by a grounded conductor.
+To do this we can use field meters and non-contacting voltmeters.
+If the field strength indicated on the meter is $\mathbf{E}$, the charge density $\sigma$ on the part of the insulator in the front should be $\sigma = \epsilon_0 \mathbf{E}$.
+If a non-contacting voltmeter is placed a at a distance $d$ from the sheet, then the surface voltage $V_s$ indicated on the meter is given by
+\[V_s = d \mathbf{E} = d \frac{\sigma}{\epsilon_0}. \]
+
+An ideal approach to determining surface charge on a dielectric surface is to screen perturbing effects of external electric fields.
+This is partly accomplished by grounding the fieldmeter, and by placing the dielectric sample on a grounded conductive plate backing.
+In this case the surface charge density is determined from
+
+\[ \sigma = \frac{V_s \epsilon}{l}, \]
+
+where $l$ and $\epsilon$ are the absolute permittivity and thickness of the dielectric surface respectively.
+The measured surface voltage is a function of position away from the charged dielectric.
+In most cases this function is relatively constant at a distance about 1-2 cm away from the surface (there is some measurement error in surface voltage due to small mispositioning of the electrostatic fieldmeter, say by $\pm$1 mm) and add it to the precision error of measurement in $V_s$.
+
+A further consideration is the possibility of the change in total charge during a typical experimental timescale.
+If we consider the drop rig to be a ground (which seems reasonable given that the rig is isolated from true ground, but is at some reference voltage with respect to the surface charges on the dielectric, it also has an abundance of free charge carriers, that it, it is conductive), then there will be both bulk and surface decay of the charge on the dielectric.
+The evolution of the charge can be approximated by
+\[ \sigma = \sigma_0 e^{\frac{-t}{\epsilon \rho}}, \]
+where $\sigma_0$ is the initial surface charge density, and $\rho$ is the bulk resistivity (which can also be reframed in terms of conductivity by $\rho = 1/\gamma$, where $\gamma$ is the conductivity).
+For an example case of a surface with an initial surface charge density $\sigma = 2.4 \cdot (10^{-6})$ $C/m^2$, relative permittivity $\epsilon = 3.5$ and bulk resistivity $\rho = 1.6 \cdot (10^{16})$ $\Omega/cm$ such as with the case of 1/4'' continuous cast acrylic sheet, then the time constant $\tau = \epsilon \rho$ is approximately 5000 s, which is a great deal longer than the typical time period for of a drop tower experiment.
+\hl{Add specific notes on charge measurement procedure}.
+
+\begin{figure}
+    \centering
+    \input{../figures/charge_decay.pgf}
+       \caption{Charge decay.\label{fig:charge_decay}}
+\end{figure}
+
+\newpage
+\section{Data Munging}
+Digitization of droplet trajectories requires several steps of post-processing.
+Video is first decomposed into a sequence of still images.
+Trajectories are captured using the particle tracking module in \emph{Fiji}\hl{[ref]}, a derivative of the popular \emph{ImageJ}\hl{[ref]} package for scientific image analysis.
+The series is stabilized to remove the effect of drop transients from the kinetmatic data[ref].
+The series of still images is cropped, and the background (that is, the low-entropy pixels) of the series is removed using a builtin ``rolling ball'' algorithm.
+Each still is then split into its constituent RGB maps.
+In this case the green channel images contained the most information, so these were then globally thresholded using the Triangle algorithm to recover a map of the pixels corresponding to the droplet's approximate position in the original still.
+Finally ellipses are fitted to the pixel map stepping through the time series to determine the positions of the centroid, and the semi-major and minor axes of the droplets during the drop.
+The results of the particle capture in \emph{Fiji} are shown in Figure [ref].
+Out of plane motion for `weakly 3D' trajectories is inferred from the change in tracked area of the droplet.
+Droplet positional data was smoothed ex post facto using a Savitsky-Golay filter.
+Additional details regarding the data smoothing methodology are presented in Appendix [ref].
+
 \section{Parameter Estimation}
@@
 
-In particular, it is impractical to directly measure the droplet net charge $q$, during a bounce experiment. Our work flow to identify this parameters is as follows:
+In particular, it is impractical to directly measure the droplet free charge $q$, during a bounce experiment. Our work flow to identify this parameters is as follows:
 \begin{enumerate}
@@
 Unfortunately not all of these parameters are physically practical to accurately measure by experiment.
-Droplet net charge $q$, in particular, could in principle be directly measured by collecting the charged drops in a faraday cup under low-g and measuring the change in capacitence of the cup using a very high input-resistence electrometer, but this is a problematic experiment to set up in a drop tower from a practical standpoint.
+Droplet free charge $q$, in particular, could in principle be directly measured by collecting the charged drops in a faraday cup under low-g and measuring the change in capacitence of the cup using a very high input-resistence electrometer, but this is a problematic experiment to set up in a drop tower from a practical standpoint.
 The other state variables we can directly measure by experiement with varying levels of accuracy.
@@
 Thus parameter estimation is a variety of optimization problem.
+
+\subsection{Smoothing}
+All optimization methods, explicitly or implicitly follow gradients towards an optimum.
+In a parameter estimation problem, if we approximate these gradients by finite differences, then the noise manifests itself as amplification of the roughness in the hyper-response surface.
+Gradient based optimizers do poorly in these situations because they tend to converge to local minima.
+While so called gradient free algorithms offer an improvement in this regard, speed of convergence and the quality of the MLE is improved by smoothing the objective function.
+This is equivalent to smoothing the underlying dataset.
+
+Our choice of smoothing approach depends principally on the nature of the errors in the dataset.
+The sources of error include misalignment of the camera, error in the fiduciary length scale, perspective due to objects (subject or reference scale) being out of the photographic plane, and various errors arising in the digitization process (including the difference between the thresholded ellipse fitted centroid and the true centroid of the non-ellipse drop centroid).
+Some of these errors are systematic in origin and introduce consistent biases into the data (e.g.
+coherent spectral sources, rather than truly stochastic noise).
+Data smoothing does little to help systematic errors in that they are usually of lower frequency than the signal.
+Random errors, by contrast, are assumed to have a Gaussian distribution (by the central limit theorem), and are independent of the signal (which inherently results from a deterministic process).
+
+We experimented with a variety of filters implemented in the \verb|scipy.signal| \emph{SciPy} module on a representative set of trajectory data; these methods include 1D Gaussian convolution, Wiener, Butterworth, and Savitsky-Golay filters.
+Qualitatively comparing these smoothing methods (by hand tuning filter orders and window sizes) we find that we loose too many data points in the smoothing process, large amplitudes are overly smoothed by repeated filtering passes, or there are significant end effects for most of these methods.
+A comparison of these smoothing approaches on a representative trajectory data set are shown in Figure \ref{fig:y_filtered}.
+
+\begin{figure}
+    \centering
+    \input{../figures/y_filtered.pgf}
+       \caption{The underlying signal is `noisy', due partially to deterministic errors in determining the centroid position.
+These deterministic errors are largely due to droplet oscillations, especially the rapidly damped higher harmonics which do not have azimuthal symmetry.
+There is also Gaussian error in the ellipse fitting due to thresholding and noise in the video itself.
+We see that 1D Gaussian convolution and Wiener filters suffer from significant end effects.
+At this scale Butterworth and Savistsky-Golay filters are nearly indistinguishable.}
+      \label{fig:y_filtered}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \input{../figures/dy_filtered.pgf}
+    \caption{Comparing the first derivatives of the Butterworth and Savitsky-Golay filters we see that the Butterworth filter also suffers from a slight end effect.
+This implies that the optimization will find a different optima of the likelyhood depending on which type of filter is used.\label{fig:dy_filtered}}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \input{../figures/power_spectra.pgf}
+    \caption{The power spectra has a peak at 1 Hz, which is the droplet trajectory parabola itself, and smaller peaks in the kHz range corresponding to various noise frequencies.
+The Savitsky-Golay and Butturworth filters seem to have the least distortion of the power spectra of the true signal.
+Both also do a good job of attenuating the noise at the 2 kHz peak.
+\label{fig:power}}
+\end{figure}
+
+The Savitsky-Golay, and Butterworth filters both produce fairly smooth derivatives as can be seen in Figure \ref{fig:dy_filtered}; but the small window-size needed for Butterworth filter tends to also produce a noticeable end effect.
+The Savitsky-Golay filter essentially uses a moving-window based on local least-squares polynomial approximations.
+It was shown that fitting a polynomial to a set of input samples and then evaluating the resulting polynomial at a single point within the approximation interval is equivalent to discrete convolution with a fixed impulse response \hl{[Savitsky, 1964]}.
+A beneficial property of this kind of low-pass filter is their tendency to maintain waveform amplitudes, and so they are attractive in applications having noisy signals with sharply pointed waveforms such as ultrasound or synthetic aperture radar \hl{[Schafer, 2011]}.
+Because Savitsky-Golay is a Finite Impulse Response (FIR) filter it requires data points to be equally spaced; to accommodated this we interpolate points between the small gaps which sometime occur in the tracking results from image analysis.
+We use a moving window size slightly smaller than the length of the current bounce in a drop jump data set.
+The windows are piecewise defined by partitioning the data set into a series of individual bounces (the dataset is sliced at minima identified after an initial rough smoothing pass, using the \verb|scipy.signal.argrelextrema()| function).
+The Savitsky-Golay polynomial order is 4.
+To understand how these filters differ it is useful to look at their frequency response.
+In Fourier space, convolution becomes a multiplication, and we can understand what a filter does by looking at which frequencies it lets pass through.
+We can do this using a Discrete Fourier Transform (though it is worth noting that our signal is not truly periodic).
+The power spectra for these same data are shown in Figure \ref{fig:power}.
 
@@
 
-\begin{figure}[htb]
+\begin{figure}[h]
     \centering
@@
 \end{figure}
-
-\subsection{Smoothing}
-All optimization methods, including \emph{Nelder-Mead}, whether explicit or implicitly follow gradients towards an optimum.
-In a parameter estimation problem, if we approximate these gradients by finite differences, then the noise manifests itself as amplification of the roughness in the hyper-response surface.
-Gradient based optimizers do poorly in these situations because they tend to converge to local minima.
-While so called gradient free algorithms offer an improvement in this regard, speed of convergence and the quality of the MLE is improved by smoothing the objective function.
-This is equivalent to smoothing the underlying dataset.
-
-Our choice of smoothing approach depends principally on the nature of the errors in the dataset.
-The sources of error include misalignment of the camera, error in the fiduciary length scale, perspective due to objects (subject or reference scale) being out of the photographic plane, and various errors arising in the digitization process (including the difference between the thresholded ellipse fitted centroid and the true centroid of the non-ellipse drop centroid).
-Some of these errors are systematic in origin and introduce consistent biases into the data (e.g.
-coherent spectral sources, rather than truly stochastic noise).
-Data smoothing does little to help systematic errors in that they are usually of lower frequency than the signal.
-Random errors, by contrast, are assumed to have a Gaussian distribution (by the central limit theorem), and are independent of the signal (which inherently results from a deterministic process).
-
-We experimented with a variety of filters implemented in the \verb|scipy.signal| \emph{SciPy} module on a representative set of trajectory data; these methods include 1D Gaussian convolution, Wiener, Butterworth, and Savitsky-Golay filters.
-Qualitatively comparing these smoothing methods (by hand tuning filter orders and window sizes) we find that we loose too many data points in the smoothing process, large amplitudes are overly smoothed by repeated filtering passes, or there are significant end effects for most of these methods.
-A comparison of these smoothing approaches on a representative trajectory data set are shown in Figure \ref{fig:y_filtered}.
-
-\begin{figure}
-    \centering
-    \input{../figures/y_filtered.pgf}
-       \caption{The underlying signal is `noisy', due partially to deterministic errors in determining the centroid position.
-These deterministic errors are largely due to droplet oscillations, especially the rapidly damped higher harmonics which do not have azimuthal symmetry.
-There is also Gaussian error in the ellipse fitting due to thresholding and noise in the video itself.
-We see that 1D Gaussian convolution and Wiener filters suffer from significant end effects.
-At this scale Butterworth and Savistsky-Golay filters are nearly indistinguishable.}
-      \label{fig:y_filtered}
-\end{figure}
-
-\begin{figure}
-    \centering
-    \input{../figures/dy_filtered.pgf}
-    \caption{Comparing the first derivatives of the Butterworth and Savitsky-Golay filters we see that the Butterworth filter also suffers from a slight end effect.
-This implies that the optimization will find a different optima of the likelyhood depending on which type of filter is used.\label{fig:dy_filtered}}
-\end{figure}
-
-\begin{figure}
-    \centering
-    \input{../figures/power_spectra.pgf}
-    \caption{The power spectra has a peak at 1 Hz, which is the droplet trajectory parabola itself, and smaller peaks in the kHz range corresponding to various noise frequencies.
-The Savitsky-Golay and Butturworth filters seem to have the least distortion of the power spectra of the true signal.
-Both also do a good job of attenuating the noise at the 2 kHz peak.
-\label{fig:power}}
-\end{figure}
-
-The Savitsky-Golay, and Butterworth filters both produce fairly smooth derivatives as can be seen in Figure \ref{fig:dy_filtered}; but the small window-size needed for Butterworth filter tends to also produce a noticeable end effect.
-The Savitsky-Golay filter essentially uses a moving-window based on local least-squares polynomial approximations.
-It was shown that fitting a polynomial to a set of input samples and then evaluating the resulting polynomial at a single point within the approximation interval is equivalent to discrete convolution with a fixed impulse response \hl{[Savitsky, 1964]}.
-A beneficial property of this kind of low-pass filter is their tendency to maintain waveform amplitudes, and so they are attractive in applications having noisy signals with sharply pointed waveforms such as ultrasound or synthetic aperture radar \hl{[Schafer, 2011]}.
-Because Savitsky-Golay is a Finite Impulse Response (FIR) filter it requires data points to be equally spaced; to accommodated this we interpolate points between the small gaps which sometime occur in the tracking results from image analysis.
-We use a moving window size slightly smaller than the length of the current bounce in a drop jump data set.
-The windows are piecewise defined by partitioning the data set into a series of individual bounces (the dataset is sliced at minima identified after an initial rough smoothing pass, using the \verb|scipy.signal.argrelextrema()| function).
-The Savitsky-Golay polynomial order is 4.
-To understand how these filters differ it is useful to look at their frequency response.
-In Fourier space, convolution becomes a multiplication, and we can understand what a filter does by looking at which frequencies it lets pass through.
-We can do this using a Discrete Fourier Transform (though it is worth noting that our signal is not truly periodic).
-The power spectra for these same data are shown in Figure \ref{fig:power}.
 
@@
 \end{figure}
-
+\newpage
 \begin{figure}[h]

### 2018-01-23 doc/manuscript/results.tex
added complete, intro, theory, and methods sections

--- 2017-06-12 ef_notes.tex
@@
-\documentclass[a4paper, 12pt]{article}
-\usepackage{changepage}
+\documentclass[10pt,a4paper]{article}
+\usepackage[utf8]{inputenc}
+%\usepackage{fontspec} % This line only for XeLaTeX and LuaLaTeX
+\usepackage{pgfplots}
+\usepackage{pgf}
+\usepackage[english]{babel}
+\usepackage{amsmath}
+\usepackage{amsfonts}
+\usepackage{amssymb}
+\usepackage{graphicx}
+\graphicspath{ {../figures/} }
+%\usepackage{svg}
+\usepackage{verbatim}
 \usepackage{color,soul}
 \usepackage{listings}
-\lstset{
-basicstyle=\small\ttfamily,
-columns=flexible,
-breaklines=true
-}
-\title{\textsf{\textbf{Droplet Electro-Bouncing in $\mu$-Gravity}}}
-\vspace{-25mm}
-\author{Erin S. Schmidt, Mark M. Weislogel}
-\date{}
+\usepackage{setspace}
+\author{Erin Schmidt}
 
-\usepackage{abstract}
-\renewcommand{\abstractnamefont}{\normalfont\bfseries}
-\renewcommand{\abstracttextfont}{\normalfont\small\itshape}
+\newlength\figureheight
+\newlength\figurewidth
+\setlength\figureheight{7cm}
+\setlength\figurewidth{10cm}
 
 \begin{document}
-\maketitle
 
-\begin{abstract}
-\noindent
-Notes on electric fields `n stuff.
-\end{abstract}
+\doublespacing
+\section{Overview}
+\begin{itemize}
+\item We found the distribution of mostly likely experimental net charges for a population of the droplets jumped in low-gravity.
+We found the charge to be a function of droplet volume and surface potential of the dielectric substrate.
+A two-ways T-test with a charge distribution determined by a corollary experiment suggests that the droplet charge is induced by the electric field (rather than through contact charging on the PTFE layer).
 
-\section{Introduction}
-\subsection{Spontaneous Droplet Jump}
-When a nonwetting, gravity dominated sessile drop or puddle initially at rest in the Cassie-Baxter state on a surface undergoes a large step reduction in Bond number, $\mathbf{Bo} = \rho g V_d^{2/3}/\sigma$, where $\rho$ is the liquid density, $g$ is the acceleration of gravity, $V_d$ is the droplet volume, and $\sigma$ is the liquid surface tension, it will spontaneously jump away from the surface.
-This was first observed experimentally by Kirko \emph{et al.} in 1970 [ref] and later by Wollman \emph{et al.} in 2006 in a set of experiments conducted using a $\mu$-gravity drop tower \hl{[ref]}.
-The kinetic energy of the jump is supplied by the defect in free surface energy as the new minimum energy surface equilibrium has approximately constant curvature \hl{[ref]}.
-If the viscous energy losses by shear, and internal flows during roll up are neglected, as well as energy lost due to the hysteresis of the dynamic contact line, then the energy relation is given by
-\[KE = SE_2 -SE_1 = [(\sigma A)_{gl} + (\sigma A)_{sg}]_2 - [(\sigma A)_{ls} + (\sigma A)_{gl} + (\sigma A)_{sg}]_1. \]
-From this is derived a simple model for the droplet initial jump velocity, given by
-\[U_0 = \left(\frac{\sigma g}{\rho}\right)^{1/4}\left[1-\cos \theta + 2 \left(\frac{\pi H^3}{V_d} \right)^{1/2} - 6^{2/3} \left( \frac{\pi H^3}{V_d} \right)^{1/3} \right]^{1/2}, \]
-where \hl{[etc, etc, etc...]}.
+\item The bounce dynamics are controlled by a dimensionless ratio of electrostatic force to inertia. The dielectrophoretic force plays a very small role when droplets have net charge in a DC field.
 
-%\begin{figure}
-%  \centerline{\includegraphics[height=7cm,width=7cm]%{e88_1_thumb.jpg}}
-%  \caption{Droplet jump velocities, effect of hysteresis for small droplet size}
-%\label{fig:jump_velocities}
-%\end{figure}
+\item Using the unique capabilities of the low-gravity environment we obtained data on dimensionless contact time and coefficients of restitution at very low Ohnesorge numbers for a range of electric Bond numbers.
+Despite strong electric fields (20-30 $kV/cm$) we found little evidence for wetting transitions due to excession of a critical pressure (the ``Fakir impalement'').
+There is no obvious trend in dimensionless contact time or coefficient of restitution with electric Bond number.
 
-The droplet `rolls up' as it jumps away from the surface due to radial motion of capillary wave away from the contact line.
-The characteristic time scale of the rolling up scales as $t_j \sim R_p/U ~(\rho H R^2_p/\sigma)^{1/2}$ [ref], which resembles the contact time, $\tau \approx 2.6(\rho R^3_d/\sigma)^{1/2}$ reported by Richard \emph{et al.} in 2002 for the related problem of droplets impacting hydrophobic surfaces in 1-g \hl{[ref]}.
-For droplets with radial symmetry and sufficiently high initial $\mathbf{Bo}$ these waves coalesce as a shock leading to geyersing and creation of satellite drops by the Rayleigh-Plateau breakup of the geyser.
-In the case of smaller jumping droplets, the capillary waves do not lead to geyersing, and are viscously damped to varying degrees during the brief freefall period of the drop tower.
+\item Jump velocities are more strongly damped for relatively small droplet volumes in the presence of the electric fields than was shown by Attari \emph{et.
+al.}.
+This may be evidence for electrowetting paradoxically enhancing the effect of contact angle hysteresis pinning on sharp corners.
+(How does this tie into the coefficients of restitution problem?)
 
-The spontaneous droplet jump phenomenon provides a useful window though which to study the dynamics of large-lengthscale capillary dominated droplets.
-The governing physics of such massive droplets (far beyond the 1-g sub-millimetric capillary lengthscale) utterly defy terrestrial expectations about the ways in which liquid droplets `should' behave, and also are of critical importance in a space exploration setting where the design of practical $\mu$-gravity  multiphase fluidic systems will no doubt be needed as humankind gradually extends her domain into our solar system.
-\section{Bouncing}
-For the sake of bevity we will henceforth use the slightly confusing term `drop' as shorthand to refer to a single $\mu$-gravity drop tower experiment.
-\section{Experimental Methods}
-Superhydrophobic substrates were placed on a drop tower rig platform.
-The rig is released by a solenoid chucked pin at the same moment the exterior drag shield is allowed to fall.
-This decouples drag acceleration felt by the drag shield from the experiment which experiences approximately $1 \cdot 10^{-6}$g of high quality freefall for the 2.1s required for the rig/drag shield assembly to reach the bottom of drop tower 6 floors below.
-
-The superhydrophobic surface was treated with PTFE spray for the first experiment of the day, and approximately every $3^{\mbox{rd}}$ drop following.
-The general properties and details of the fabrication of these superhydrophobic surfaces are discussed in Section \ref{sec.suphydro}.
-Shortly before each drop the surfaces were briefly rinsed with distilled water, and then dried under a fume hood for about 10 minutes.
-The drop rigs were balanced to prevent unintentional torques from contaminating the kinematics data (as angular velocity of the camera-fixed inertial reference with respect to the droplets during freefall would appear as a linear acceleration of the droplet).
-Surface charge density was measured on the superhydrophobic surface using a \emph{Simco-Ion} FMX-004 electrostatic fieldmeter.
-This measurement was done with the superhydrophobic surfaces connected by a conductive ground plane by conductive tape, far away from the presence of other conductors.
-Some additional notes on idiosyncrasies of determining surface voltages (and thence surface charge densities) on insulative dielectric surfaces are provided in Appendix \ref{sec.surface_charge}.
-
-Droplets of distilled water, in a range of volumes ($0 \leq R_d \leq 1$mL), were very carefully deposited on the superhydrophobic surface in the final 1-5 minutes prior to the drop using an ungrounded glass syringe with $\pm 1\mu$L accuracy.
-Red tracer dye was added to improve trajectory digitization.
-During the drop, droplet trajectories were observed using a \emph{Panasonic} HC-WX970 Camera, shooting in high-speed mode at 120 fps and and 1/3000s shutter speed.
-In a few cases where higher frame rates were needed a \emph{Nikon} 1 J1 camera with a 30mm telephoto lens was used, shooting at 400 fps.
-The experimental test cell was illuminated with a 12V 6000K \emph{SEALIGHT} Chip-On-Board LED strip with a thin semi-opaque plastic film covering to make the light diffuse.
-The effect of static charges on spontaneously jumped droplet trajectories was studied in terms of the parameters droplet volume $V_d$, surface charge density $\sigma$, and a dependent variable, initial droplet jump velocity $U_0$.
-Since $q$ cannot be directly measured insitu during a drop (as high-input resistance electrometers, being notoriously fickle instruments, are not well suited to sudden 15-g decelerations), it was inferred from the statistical distribution determined in corollary experiments.
-The droplet charge determination is discussed in slightly more detail in Appendix \ref{sec.drop_charge}.
-
-\subsection{Superhydrophobic surfaces} \label{sec.suphydro}
-Wetting hysteresis.
-Methods of fabrication, comparison of wetting properties.
-Comparison of jump velocities between surfaces.
-Methods for determination of properties, roll-off angle, contact angle using \emph{SE-FIT}.
-Cassie-wenzel transition.
-Damping.
-Droplets are dyed red to improve the quality of image thresholding when digitizing the droplet trajectories during data reduction.
-
-%\begin{figure}
-%  \centerline{\includegraphics[height=7cm,width=13cm]{modes.eps}}
- % \centerline{\includegraphics[height=7cm,width=7cm]{e88_1_thumb.jpg}}
-%  \caption{SEM images for sandpaper and laser etched acrylic surfaces}
-%\label{fig:SEM}
-%\end{figure}
-
-\subsection{Data Reduction}
-Digitization of droplet trajectories requires several steps of post-processing.
-Video is first decomposed into a sequence of still images.
-Trajectories are captured using the particle tracking module in \emph{Fiji}\hl{[ref]}, a derivative of the popular \emph{ImageJ}\hl{[ref]} package for scientific image analysis.
-The series of still images is cropped, and the background (that is, the low-entropy pixels) of the series are removed using a builtin ``rolling ball'' algorithm.
-Each still is then split into its constituent RGB maps.
-In this case the green channel images contained the most information, so these were then globally thresholded using the Triangle algorithm to recover a map of the pixels corresponding to the droplet's approximate position in the original still.
-Finally ellipses are fitted to the pixel map stepping through the time series to determine the positions of the centroid, and the semi-major and minor axes of the droplets during the drop.
-The results of the particle capture in \emph{Fiji} are shown in Figure \ref{fig:fiji}.
-Droplet positional data was smoothed ex post facto using a Savitsky-Golay filter.
-Additional details regarding the data smoothing methodology are presented in Appendix \ref{sec.smoothing}.
-
-\section{EHD Forces}
-As previously speculated the the force acting on the droplets as a surrogate for gravity are likely electrohydrodynamical in origin.
-In the hopes of unraveling the underlying mechanism for the electro-bouncing we turn to the electrodynamical approximation of fluids under the influence of electric fields.
-To that effect, what follows is a condensed overview of mathematical description of basic electrohydrodynamic flows.
-We first assume a DC electric field, such that $Re \langle \epsilon \rangle \approx  \mbox{constant}$, where $\epsilon$ is the dielectric permittivity of the respective media.
-We also assume that currents are small such that the effects of magnetic fields can be neglected.
-For the validity of this assumption to hold the characteristic time scale for electrical phenomena $\tau_e = \epsilon \epsilon_0/\sigma_e \ll 1$, where we note that $\tau$ is the ratio of absolute dielectric permittivity $\kappa = \epsilon \epsilon_0$, to conductivity $\sigma_e$, of the medium [ref].
-Given the respective conductivity, and permittivity of air ($\sigma_e = 2.5 \cdot 10^{-16}$ $\Omega^{-1} cm^{-1}$), we estimate $\tau_e \approx 400$s.
-This assumption also allows us to assume that the net charge present in the medium surrounding the droplets remains approximately constant during the typical time interval of a $\mu$-gravity experiment, and no transfers of charge occur after the droplet leaves the surface.
-\hl{[lol, check these numbers...]}
-
-\subsection{Maxwell Stress}
-If we suppose that electrical forces acting on free charges and dipoles in a fluid are transferred directly to the fluid itself, then this overall electrical body force will be the the divergence of the Maxwell stress tensor $\tau_m $, by
-
-\[ \mathbf{F}_e = \nabla \cdot \tau_m = \nabla \cdot \left( \epsilon \epsilon_0 \mathbf{E} \mathbf{E} - \frac{1}{2} \epsilon \epsilon_0 \mathbf{E} \cdot \mathbf{E} \delta \right) ,\]
-where $\mathbf{F}_e$ is the electric body force per unit volume, \hl{$\rho_f$ is the free charge density}, and $\delta$ is the delta function.
-The product of the electric field vectors is the dyadic product.
-
-The classical Korteweg-Helmholtz force density formulation of the Maxwell stress tensor is usually expressed as 
-\begin{equation}
-\mathbf{F}_e = \rho_f \mathbf{E} + \frac{1}{2} \left| \mathbf{E} \right|^2 \nabla \epsilon - \nabla \left( \frac{1}{2} \rho \left( \frac{\partial \epsilon}{\partial \rho} \right)_T \left| \mathbf{E} \right|^2 \right) ,
-\end{equation}
-and $\rho$ is the density of the dielectric fluid[ref].
-
-The first term in this expression, equivalently written as $q\mathbf{E}$, is the well known Coulombic force or electrophoretic force, which arises from the presence of free charge in an external electric field.
-The second term is the force arising from polarization stresses due to a nonuniform field acting across a gradient in permittivity.
-This force is widely termed the dielectrophoretic force (DEP).
-The third term describes forces due to electrostriction, however in our case $\left( \frac{\partial \epsilon}{\partial \rho} \right)_T = 0$ due to the  incompressibility of the fluid[ref].
-While it is a relatively rigorous approach, and a useful conceptual model, evaluating the force density in this fashion can be somewhat onerous.
-
-\subsection{Dielectrophoresis}
-An alternative approximation for the polarization stress is to idealize the droplet as a simple dipole using the effective dipole moment method first suggested by Pohl and Jones\hl{[ref][ref]}.
-This approach can be related back to the force density by means of a Taylor series expansion of $\mathbf{E}$ in the limit of a small gradient \hl{[ref]}.
-The DEP force is distinct from the Coulombic force in that net charge is not required, and that the force vector goes in the direction of steepest descent of the field, $\nabla \left| \mathbf{E} \right|^2$, rather than in the direction of $\mathbf{E}$.
-The DEP force is related to the dipole moment (induced or polarized) of polarizable media which has a tendency to align the dipole with the electric field.
-If there is a gradient in the field then for a finite separation of charge one end of the dipole will feel a stronger electric field than the other, resulting in a net force.
-Whether the force is positive or negative in the direction of the electric field gradient depends on the difference of dielectric permittivites between the fluids, rather than on the polarity of $\mathbf{E}$.
-It bears repeating that droplets will polarize in a uniform field, but since there is no gradient in the field the forces felt by the dipoles are symmetric and there is no net force.
-The dipole moment of a spherical dielectric particle immersed in a dielectric medium is given by
-\begin{equation} \label{dipole_m_1}
-\mu = V_d \mathbf{P} = \frac{4}{3} \pi R_d^3 \mathbf{P},
-\end{equation} 
-where $\mathbf{P} = \left(\kappa_1 - 1 \right) \epsilon_0 \mathbf{E}_{iz}$ is the polarization moment, and $R_d$ is the particle radius, \hl{($\kappa_1$ being the relative dielectric constant of the medium}, and $\mathbf{E}_{iz}$ is the $z$-coordinate component of the electric field internal to the sphere, assuming the external electric field to be oriented parallel to the $z$-axis).
-The excess polarization $\mathbf{P}_e$, in the sphere is given by
-\begin{equation} \label{polarization}
-\mathbf{P}_e = \left( \kappa_2 - \kappa_1 \right) \epsilon_0 \mathbf{E}_{iz} = \frac{3 \kappa_1}{\kappa_2 +2\kappa_1}\mathbf{E}_{iz},
-\end{equation}
-where $\kappa_2$ is the dielectric constant of the particle. Taking together equations \ref{dipole_m_1}, and \ref{polarization} we find that the effective dipole moment of the particle is given by 
-\begin{equation}\label{dipole_m_2}
-\mu = 4 \pi R_d^3 \left( \frac{\kappa_2 - \kappa_1}{\kappa_2 + 2 \kappa_1} \right) \kappa_1 \epsilon_0 \mathbf{E},
-\end{equation}
-and the force felt by the dipole is 
-\begin{eqnarray} \label{dep_force}
-\mathbf{F}_{dep} &=& \left( \mathbf{P}_e \cdot \nabla \right) \mathbf{E}\\
-&=& 2 \pi R_d^3 \kappa_1 \epsilon_0 \left( \frac{\kappa_2 - \kappa_1}{\kappa_2 + 2 \kappa_1} \right) \nabla E^2,
-\end{eqnarray}
-where it is a useful shorthand to refer to the permittivity ratio by $K = \frac{\kappa_2 - \kappa_1}{\kappa_2 + 2 \kappa_1}$, which is also known as the Clausius-Mossotti factor.
-In cases where $K < 0$, or $K>0$ the particle will be repelled or attracted to regions of strong field respectively.
-In our experiment, taking the relative dielectric constants to be $\kappa_1 \approx 1$ and $\kappa_2 \approx 80$, we have $K \approx 0.96$.
-One limitation of the effective dipole moment approximation of the DEP force is that it requires an assumption of small physical scale of the particle relative to the lengthscale of nonuniformity of the field, which in this case we take to be the length of the charged superhydrophobic surface ($L,H =25$mm $\gg a \approx 2.5$mm).
-Though the effective dipole moment is a successful model due in large part to its simplicity, it can be readily extended to include higher-order multipole effects, and non-spherical particles (oblate and prolate spheroids).
-An excellent summary of DEP theory in terms of the effective dipole moment is given in \hl{[ref]}.
-\hl{[Some notes on scaling ...]}
-
-\subsection{Forces due to Image Charges in the Dielectric}
-
-\section{The Electric Field}
-Being thus armed with the assumption of a purely electrostatic problem (the electric field is conservative, that is $\nabla \times \mathbf{E} = 0$, where $\mathbf{E}$ is the electric field) we can describe the electric field by the Laplace equation for the electric potential.
-In the case of the volume charge density of the bulk medium to being zero, the divergence of the electric field is zero and we have
-
-\begin{eqnarray}
-\mathbf{E} &=& -\nabla \varphi \\
-\nabla \cdot \mathbf{E} &=& 0\\
-\nabla \cdot \mathbf{E} &=& - \nabla \cdot \nabla \varphi = \nabla^2 \varphi = 0,
-\end{eqnarray}
-it being convenient to solve the field in terms to $\varphi$ due to the form of the \emph{boundary conditions} usually given by
-\begin{enumerate}
-\item For finite charge distributions, the potential $\varphi$ goes to zero at infinity, is constant throughout a conductors, and is continuous across physical boundaries.
-\item The normal component of the displacement vector $\mathbf{D}$, differs on two sides of a boundary by the free charge density $\rho_f$ residing on the boundary.
-\item The tangential component of the field intensity $\mathbf{E}$ is continuous across a boundary.
-\end{enumerate}
-
-\section{A Simple Dynamical Model}
-\subsection{Trajectory Equation}
-\subsection{Numerical Methods}
-\section{Comparisons}
-\section{Stability}
-\section{Future Directions}
-\section{Conclusions}
-\appendix
-\section{\\Data Smoothing} \label{sec.smoothing}
-In trying to recover the kinematic variables from the droplet trajectories we encounter a difficulty in the noise of the position data:
-
-\begin{itemize}
-\item Notes from Wood, ``Data smoothing and Differentiation procedures in Biomechanics''
-
-\item Signal-to-noise ratio is $\mathcal{O}(f)$ for $\frac{df}{dt}$ and $\mathcal{O}(f^2)$ for $\frac{d^2f}{ft^2}$. Refs 5, 14, 49, 95.
-
-\item Error sources include misalignment of the camera, perspective due to objects (subject or reference scale) being out of the photographic plane, precision limits in digitization.
-Some of these errors are systematic in origin and introduce consistent biases into the data (e.g.
-coherent spectral sources, rather than truly stochastic noise).
-These systematic sources of error include inaccurate scales among others.
-Data smoothing tends not to help with the systematic errors in that they are usually of lower frequency than the signal (and here we are trying specifically to filter high frequency noise).
-
-\item Random errors are assumed to have a Gaussian distribution (by the central limit theorem), and are independent of the signal (which inherently results from a deterministic process).
-
-\item Central differences are usually a better approximation of the instantaneous value of the true derivative of the signal, as compared to forward differences.
-The finite differences are mathematically equivalent to passing a quadratic interpolating polynomial through the three points of the central difference (assuming the window size of the central difference is $N=3$, larger windows are possible).
-To obtain an approximation for the $m^{th}$ derivative of $f(x)$ at least an $m^{th}$ order polynomial is required.
-
-\item One straightforward approach to getting the position derivatives is to fit a least squares polynomial to the global position data, and analytically differentiate.
-This is a simple to apply, and therefore quite popular approach.
-The order of the polynomial is picked from theory, by ANOVA, or comparison of the residuals to determine goodness of fit for $m+1$.
-It should be stress that there are significant drawbacks with this approach: firstly is that when derived values depend on both accuracy of segmented displacement-time data and body segmental parameters (segmental masses and center of mass locations), then the errors are confounded and it is difficult to evaluate the accuracy of the derivative.
-Secondly, statistics used to asses agreement between curves are either in-appropriate because they aim to represent fundamentally deterministic processes in probabilistic ways (as would be the case using a product-moment correlation), or there is no test of significance (as is the case with a mean-errors correlation).
-Finally High order effects are easily lost by a global polynomial fit for time series containing multiple length scales or frequencies, as is the case here [ref].
+\item By scale arguments and perturbation of solutions to the equations of motion we find several simple rules of thumb in droplet ``escape velocity'' of impacts, length scales and time scales for returns.
 \end{itemize}
 
-In lieu of global polynomial fits we can attempt at finite differencing the data after the application of smoothing filters.
-Some of these approaches are global and/or recursive whereas other approaches are applied locally.
-Each approach has various natural advantages and disadvantages.
-A number of approaches were implimented in \emph{Python} or imported from the scientific computing package \emph{SciPy}[ref] and compared for a test set of trajectory data; these methods include convolution with the derivative of a Gaussian kernel, Wiener filtering, smoothing splines, Butterworth low-pass filtering, total-variance regularization, and Savitsky-Golay filtering.
-Qualitatively comparing these smoothing methods we find that we loose too many data points in the smoothing process, the variance remains large (especially in higher derivatives), large amplitudes are overly smoothed by repeated filtering passes, or there are significant end effects for most of these methods.
-A comparison of these smoothing approaches on a representative trajectory data set are shown in Figure \ref{fig:filters}.
-The power spectra for the same data are compared for these methods in Figure \ref{fig:power_spectra}.
+\begin{figure}[htb]
+    \centering
+    \input{../figures/charge.pgf}
+    \caption{A simple EMA plot.\label{fig:charge}}
+\end{figure}
 
-%\begin{figure}
-%  \centerline{\includegraphics[height=7cm,width=13cm]{modes.eps}}
- % \centerline{\includegraphics[height=7cm,width=7cm]{e88_1_thumb.jpg}}
-  %\caption{Filtered or fitted droplet trajectories compared to raw data.}
-%\label{fig:filters}
-%\end{figure}
+\begin{figure}[htb]
+    \centering
+    \input{../figures/series.pgf}
+    \caption{A simple EMA plot.\label{fig:series}}
+\end{figure}
 
-%\begin{figure}
-%  \centerline{\includegraphics[height=7cm,width=13cm]{modes.eps}}
- % \centerline{\includegraphics[height=7cm,width=7cm]{e88_1_thumb.jpg}}
-  %\caption{Power spectra of the filter methods compared.}
-%\label{fig:power_spectra}
-%\end{figure}
+\begin{figure}[htb]
+    \centering
+    \resizebox{14cm}{!}{\input{../figures/forces.pgf}}
+    \caption{A simple EMA plot.\label{fig:forces}}
+\end{figure}
 
-Savitsky-Golay filtering seems to produce the smoothest derivatives without overfitting of otherwise misrepresenting the underlying signal. The Savitsky-Golay algorithm
+\begin{figure}[htb]
+    \centering
+    \input{../figures/contact.pgf}
+    \caption{A simple EMA plot.\label{fig:contact}}
+\end{figure}
 
-\section{\\Surface charge density}\label{sec.surface_charge}
-Since the laser-etched acrylic, and sandpaper superhydrophobic surfaces are both dielectric materials there are some additional considerations for determining the surface charge density.
-Firstly, for an insulated conductor $A$ with charge $q$, the charge distribution in equilibrium will be such that the field on the interior of the conductor is zero, with field lines being normal to the surface and the integral of the field strength $\mathbf{E}$ from any point $P$ in or on the conductor to a ground point $G$ is a constant given by
-\[ V = \int^G_P \mathbf{E} \cdot da, \]
-where $V$ is the voltage or potential of the conductor (or alternatively, the surface voltage potential). The voltage $V$ and the charge $q$ are proportional and $q$ is usually given by
-\[q = CV, \]
-where $C$ is the capacitance of the insulated conductor and is determined by the conductor's size and shape, and its placement relative to the conductors and ground.
-However, the case of a charged insulator departs significantly from that of the insulated conductor.
-Here we have the possibility of the density and net polarity of the charge varying as a function of position about the surface.
-The field of the interior may not be zero, and the field lines are not necessarily normal to the the surface.
-The integral of the field strength from a point on or in the insulator to ground is usually different from point to point.
-In general the surface voltages will vary from point to point on an insulator (including point on the interior of the insulator.
-Therefore it is not possible to uniquely define the voltage of a charged insulator, except in certain contrived cases (notably the the potential of a uniformly charged sphere positioned infinitely far away from any conductors).
-It follows that there is no definition for the capacitance of an insulator as well.
-Though insulative sheets may store charge and discharge in the manner of capacitors, this discharge is never particularly complete.
+\begin{figure}[htb]
+    \centering
+    \input{../figures/restitution.pgf}
+    \caption{A simple EMA plot.\label{fig:restitution}}
+\end{figure}
 
-There are two cases where we can make meaningful quantitative measurements of state variables for charged insulators: we can measure the electric field arising from the charge, and possible the total charge for uniformly charged free insulative sheets, and uniformly charged insulative sheets backed by a grounded conductor.
-To do this we can use field meters and non-contacting voltmeters.
-If the field strength indicated on the meter is $\mathbf{E}$, the charge density $\sigma$ on the part of the insulator in the front should be $\sigma = \epsilon_0 \mathbf{E}$.
-If a non-contacting voltmeter is placed a at a distance $d$ from the sheet, then the surface voltage $V_s$ indicated on the meter is given by
-\[V_s = d \mathbf{E} = d \frac{\sigma}{\epsilon_0}. \]
-
-An ideal approach to determining surface charge on a dielectric surface is to screen perturbing effects of external electric fields.
-This is partly accomplished by grounding the fieldmeter, and by placing the dielectric sample on a grounded conductive plate backing.
-In this case the surface charge density is determined from
-
-\[ \sigma = \frac{V_s \epsilon}{l}, \]
-
-where $l$ and $\epsilon$ are the absolute permittivity and thickness of the dielectric surface respectively.
-The measured surface voltage is a function of position away from the charged dielectric.
-In most cases this function is relatively constant at a distance about 1-2 cm away from the surface (there is some measurement error in surface voltage due to small mispositioning of the electrostatic fieldmeter, say by $\pm$1 mm) and add it to the precision error of measurement in $V_s$.
-The measured surface voltage can also be compared to the analytically derived surface voltage determined from the analytical expression for the electric field from above, and to those determined from finite element solutions to poisson's equation on the domain in question.
-[Notes about \emph{Agros2D}] The surface voltage is shown schematically as a function of the measurement distance in Figure \ref{fig:surface_voltage} for a sample charge density $\sigma = $.
-
-%\begin{figure}
-%  \centerline{\includegraphics[height=7cm,width=13cm]{modes.eps}}
- % \centerline{\includegraphics[height=7cm,width=7cm]{e88_1_thumb.jpg}}
-  %\caption{Measured surface voltage versus position.}
-%\label{fig:surface_voltage}
-%\end{figure}
-
-A further consideration is the possibility of the change in total charge during a typical experimental timescale.
-If we consider the drop rig to be a ground (which seems reasonable given that the rig is isolated from true ground, but is at some reference voltage with respect to the surface charges on the dielectric, it also has an abundance of free charge carriers, that it, it is conductive), then there will be both bulk and surface decay of the charge on the dielectric.
-The evolution of the charge can be approximated by
-\[ \sigma = \sigma_0 e^{\frac{-t}{\epsilon \rho}}, \]
-where $\sigma_0$ is the initial surface charge density, and $\rho$ is the bulk resistivity (which can also be reframed in terms of conductivity by $\rho = 1/\gamma$, where $\gamma$ is the conductivity).
-For an example case of a surface with an initial surface charge density $\sigma = 2.4 \cdot (10^{-6})$ $C/m^2$, relative permittivity $\epsilon = 3.5$ and bulk resistivity $\rho = 1.6 \cdot (10^{16})$ $\Omega/cm$ such as with the case of 1/4'' continuous cast acrylic sheet, then the time constant $\tau = \epsilon \rho$ is approximately 5000 s, which is a great deal longer than the typical time period for of a drop tower experiment.
+\newpage
+\appendix
 
@@
 \subsection*{Parallel Plate Method}
-Since, by the earlier scaling, we presuppose the source of the droplet bouncing behavior to be primarily Coulombic in origin (as opposed to dielectrophoretic), the droplet must have some net charge in addition to the charge induced by the electric field.
+Since, by the earlier scaling, we presuppose the source of the droplet bouncing behavior to be primarily Coulombic in origin (as opposed to dielectrophoretic), the droplet must have some free charge in addition to the charge induced by the electric field.
 To measure this charge concurrent methodologies were used.
-The first method of determining the droplet net charge is observation of the deflection of the droplets in the region of a known uniform field in a fashion inspired by Millikan's famous experiment to determine the fundamental charge of the electron [ref].
+The first method of determining the droplet free charge is observation of the deflection of the droplets in the region of a known uniform field in a fashion inspired by Millikan's famous experiment to determine the fundamental charge of the electron [ref].
 
@@
 From a survey of literature we suppose the droplet charge, if they are indeed charged by contact with PTFE, to be some function of the droplet volume and the residence time on the superhydrophobic surface.
-However, sweeping though droplet volumes over a series of drop tower experiments we find little correlation between droplet volume  and net droplet charge.
+However, sweeping though droplet volumes over a series of drop tower experiments we find little correlation between droplet volume  and free droplet charge.
 This is shown in figure \ref{fig:drop_charge}.
@@
  % \centerline{\includegraphics[height=7cm,width=7cm]{e88_1_thumb.jpg}}
-  %\caption{Parallel plates: Droplet net charge vs volume.}
+  %\caption{Parallel plates: Droplet free charge vs volume.}
 %\label{fig:drop_charge}
@@
 Qualitative observations of droplet electrode preference seem to indicate that the assumption of small polarization stress was well founded.
-Following this a orthogonal array $3^2$ factorial design experiment with two replicates was conducted to test the effect of varying droplet volume and surface stay time on net charge at the time of jumping.
-It was hypothesized in accordance with previous studies \cite{Choi:2013dg}, that net charge would increase for levels of both factors.
+Following this a orthogonal array $3^2$ factorial design experiment with two replicates was conducted to test the effect of varying droplet volume and surface stay time on free charge at the time of jumping.
+It was hypothesized in accordance with previous studies \cite{Choi:2013dg}, that free charge would increase for levels of both factors.
 The results of the factorial experiment are presented in Fig.
@@
 
-The failure of the model to describe the data raises interesting questions about the validity of our initial assumptions.
-Typical Reynolds numbers ($R_e=280$ average) indicate the general validity of the assumed quadratic drag model.
-The drag scale quantity given by Eqn.
-\ref{eqn:drag} was much less than 1 for all test runs, with mean value of $1.0\cdot 10^{-2}$ and a standard deviation of $2.0\cdot 10^{-3}$, which adds credence to a force balance of pure inertia and electrostatic force.
-
-One obvious issue, in retrospect, is that while we know the characteristic charging time for the droplets to be some function of droplet volume, \hl{[it has been shown to have a time constant dramatically smaller than that of a typical experimental timescale]} so we might have looked only for the charge as a function of volume, both on physical grounds and due to the conflation of the variables.
-
-Also of concern is that droplets in three of eighteen runs exhibited accelerations opposite to the expected direction.
-There is no pattern to the distribution of anomalous droplet accelerations, as they all occurred at unique level combinations.
-There are only four obvious ways of explaining this anomaly.
-The first is that the electric field is in fact non-uniform and polarization stress is non-negligible in this geometry.
-This option seems unlikely owing to the fundamental design of the experimental apparatus; \hl{[see figure from Agros2D FEM solution]}.
-A second possibility is that the few contrarian droplets actually accumulated net negative charge, instead of the net positive charge to be expected on the basis of evidence from some of the aforementioned studies.
-This is not impossible, and would also go some length to explain the variance in the measured charge generally.
-A third possibility is that another force neglected in this analysis, with some component in the direction opposite of the electric field, has an $\sim \mathcal{O}(1)$ magnitude.
-In principle this could for instance include the image charges which will subject the droplets to a force $\mathbf{F} = q^2/4 \pi \epsilon_0 d$ when ``close'' to one of the conductive plates (that is, when the plate can be treated as an infinite grounded conductor).
-However, this formulation of the image charge effect clearly does not describe the force close to the centerline where the Green's function needs to add additional sets of images to satisfy the boundary conditions of $\nabla^2 \varphi = 0$ in this geometry.
-To the knowledge of the author there is not a convergent series solution in the parallel plates geometry as yet.
-
-The droplet positive net charge developed by contact with a PTFE surface corresponds to findings elsewhere in literature \cite{Choi:2013dg} \cite{Miljkovic:2013dg} \cite{Moreno-Villa:1998dg}.
-The smallest droplet size treated in the present work is several times larger than the largest in any of comparable study.
-The most relevant comparison found droplet static charge of 2.5e-10 C for 10 $\mu$L droplets charged by pipetting from a PTFE tipped needle \cite{Choi:2013dg}.
-The present results mean charge level of 2.3e-11 C is, within error, roughly six times smaller than the cited study.
-
-\subsection*{Direct Measurement}
-A second approach to determining the net droplet charge is by direct measurement in a shielded Faraday cup using an extremely high input resistance electrometer, specifically a \emph{Keithly} 616 digital electrometer.
-\hl{[note on operational philosophy, data collection].
-Correlation of net charge to droplet volume is shown again for in figure} \ref{fig:electrometer}.
-
-%\begin{figure}
-%  \centerline{\includegraphics[height=7cm,width=13cm]{modes.eps}}
-%  \centerline{\includegraphics[height=7cm,width=7cm]{e88_1_thumb.jpg}}
- % \caption{Electrometer: charge vs. volume.}
-%\label{fig:electrometer}
-%\end{figure}
-
-[Discussion on discrepancy between the two approaches.]
-
 \end{document}

### 2018-01-23 doc/manuscript/theory.tex
added complete, intro, theory, and methods sections

@@
 
-With the assumption of an intermediate range of Reynolds numbers $\mathbb{R}\mbox{e} \equiv \frac{2UR_d}{\nu}$, $1 \leq \mathbb{R}\mbox{e} \leq 5000 $ then the force drag drag acting on the droplet will be quadratic,
+With the assumption of an intermediate range of Reynolds numbers $\mathbb{R}\mbox{e} \equiv \frac{2UR_d}{\nu}$, $1 \leq \mathbb{R}\mbox{e} \leq 5000 $ then the force of drag acting on the droplet will be quadratic,
 \begin{equation*}\label{drag_force}
@@
 The validity of this assumption rests on the size of the characteristic time scale for electrical phenomena $\tau_e = \epsilon \epsilon_0/\sigma_e \ll 1$, where $\tau_e$ is the ratio of absolute dielectric permittivity $\kappa = \epsilon \epsilon_0$, to conductivity $\sigma_e$, of the medium.
-The time characteristic time $\tau_e$ is also known as the relaxation time, and is a measure of how quickly the polarization of a dielectric responds to a change in electric field.
+This characteristic time $\tau_e$ is also known as the relaxation time, and is a measure of how quickly the polarization of a dielectric responds to a change in electric field.
 Given the respective conductivity, and permittivity of extremely-pure water ($ \kappa \sim 80$, $\sigma_e = 18.2 \times 10^{6}$ $\Omega\mbox{cm}$) \cite{yatsuzuka_electrification_1994}, we estimate $\tau_e \approx 4 \times 10^{-6}$ s.
-The relaxation for the common distilled water that is actually used in the droplet experiments is undobtedly even smaller (due to the presence of solvated ions).
-Neglecting the effects of a electric double layer on hydration of ions (in the water or the ambient atmosphere), then the assumption of small relaxation time further implies that the net charge present in the droplets will remain approximately constant during the typical time interval of a low-gravity experiment.
+The relaxation time for the common distilled water that is actually used in the droplet experiments is undoubtedly even shorted (due to the presence of solvated ions).
+Neglecting the effects of a electric double layer on hydration of ions (in the water or the ambient atmosphere) due to the reletively massive size of the droplets studied, then the assumption of small relaxation time further implies that the free charge present in the droplets will remain approximately constant during the typical time interval of a low-gravity experiment.
 
 Supposing that electrical forces acting on free charges and dipoles in a fluid are transferred directly to the fluid itself, then this overall electrical body force will be the the divergence of the Maxwell stress tensor $\tau_m $, by
-
 \[ \mathbf{F}_E = \nabla \cdot \tau_m = \nabla \cdot \left( \epsilon \epsilon_0 \mathbf{E} \mathbf{E} - \frac{1}{2} \epsilon \epsilon_0 \mathbf{E} \cdot \mathbf{E} \delta \right) ,\]
@@
 \end{equation}
-
 The first term in this expression, equivalently written as $q\mathbf{E}$, is the well known Coulombic force or electrophoretic force, which arises from the presence of free charge in an external electric field.
@@
 It is common to approximate the polarization stress by idealizing the droplet as a simple dipole using the effective dipole moment method first suggested by Pohl in 1958 \cite{pohl_effects_1958}.
-This approach has been related back to the force density by the volumetric integration of the force density the substitution of a Taylor series expansion of $\mathbf{E}$ in the limit of a small radial gradient of the field within the dielectric sphere \cite{wang_general_1997}.
+This approach has been related back to the force density by the volumetric integration of the force density with the substitution of a Taylor series expansion of $\mathbf{E}$ in the limit of a small radial gradient of the field within the dielectric sphere \cite{wang_general_1997}.
 The DEP force is related to the dipole moment (induced or permanent) of polarizable media which has a tendency to align the dipole with the electric field.
@@
 Whether the force is positive or negative in the direction of the electric field gradient depends on the difference of dielectric permittivites between the fluids, rather than on the polarity of $\mathbf{E}$ itself.
-In principle an external electric field will tend to induce a dipole in a dielectric material, but if the field is spatially uniform there is no gradient in the field the forces felt by the dipoles are symmetric and thus no net force.
+In principle an external electric field will tend to induce a dipole in a dielectric material, but if the field is spatially uniform there is no gradient in the field and the forces felt by the dipoles are symmetric and thus there is no net force.
 The dipole moment of a spherical linear-dielectric particle immersed in a dielectric medium is given by
@@
 
-When the droplet is close to the dielectric surface, the net charge on the droplet will tend to induce polarization of the dielectric, perturbing the electric field.
-The polarization bound charge in the dielectric will be of the opposite sign of the net droplet charge and thus there will be a force of attraction.
+When the droplet is close to the dielectric surface, the free charge on the droplet will tend to induce polarization of the dielectric, perturbing the electric field.
+The polarization bound charge in the dielectric will be of the opposite sign of the free droplet charge and thus there will be a force of attraction.
 This so-called image force is a correction to the Colomb force due to the external electric field only, and can be found by the method of images \cite{david_j._griffiths_introduction_1999}.
 The image force $\mathbf{F}_I$, is given by
-
 \begin{equation}
@@
 \end{eqnarray*}
-
 and the 1-D governing equation becomes
@@
 \begin{eqnarray}
-1 &\gg& \frac{R_d^2 \kappa_2 \epsilon_0 K E_0}{q} \nonumber
+\frac{q}{ \kappa_2 \epsilon_0 K R_d^2 E_0} \gg 1 \nonumber
 \end{eqnarray}
@@
 This implies that the field strength within the droplet is about 2 orders of magnitude smaller than in the surrounding medium (which is essentially the same as a vacuum from a dielectric standpoint), thus it is not particularly inaccurate to model the dielectric volume of a droplet as a conductive shell (an equipotential), with zero field in its interior.
+As an aside, in treating the droplet as an ideal conductor we note that in our specific case the electrostatic force is not a body force \emph{per se} as the electric field is acting on charges on the surface of the conductor.
 
 \subsection{The Electric Field}
+
 If we consider the charged dielectric surface of our experiments to be a square sheet of charge lying in the $xz$-plane with width $L$, the symmetry of the problem happily lets us obtain the $y$-component of the electric field $\mathbf{E}$ by direct integration.
@@
 By symmetry the electric field points along the $y$-axis; for a point along the $y$-axis the position vector is $\mathbf{r} = \left( x^2 + y^2 \right)^{1/2} \hat{\mathbf{r}}$ to the center of a line charge in the $xz$-plane.
-The $y$-component of $d\mathbf{E}$ is found by $d E_r = d E_y \cos \theta = d E_y y/ r$, where $\theta$ is the angle made between the $y$-axis and the positon vector $\mathbf{r}$.
-If the charge in a line element, $dx$ is $\sigma L dx$, where $\sigma$ is the surface charge density, the electric field of a line charge is given by \cite{david_j._griffiths_introduction_1999}
+The $y$-component of $d\mathbf{E}$ is found by $d E_r = d E_y \cos \theta = d E_y y/ r$, where $\theta$ is the angle made between the $y$-axis and the position vector $\mathbf{r}$.
+If the charge in a line element, $dx$ is $\sigma L dx$, where $\sigma$ is the average surface charge density, the electric field of a line charge is given by \cite{david_j._griffiths_introduction_1999}
 \[d E_r = \frac{k \sigma L dx}{4 \pi \epsilon_0 r \sqrt{r^2 + L^2/4}}.
@@
 .\end{equation}
+We note that this model of the electric field will be poor except in cases where $y \ll L, \hspace{1 mm} R_d \ll L$, which will be true for cases of large drops very close to the dielectric surface.
+For accurate models of the field in this case we likely would need to solve Laplace's equation for the electric potential $\varphi$
+\[ - \nabla^2 \varphi = 0,\]
+numerically using finite element methods.
 
@@
 .\end{equation}
-Both these regimes can be clearly seen in the plot of $E_y$ shown in Figure \ref{fig:E0}.
+Both of these regimes can be clearly seen in the plot of $E_y$ shown in Figure \ref{fig:E0}.
 \begin{figure}[htb]
@@
 \subsection{Scaling}
-Introducing scaled variables
+
+The equation of motion is non-linear, non-homogenous and is best solved numerically, but nevertheless we are curious if we can obtain approximate solutions to the equation analytically using perturbation methods.
+This is aided by non-dimensionalizing the governing equations, and seeing if any dimensionless groups exist, and whether any are particualy small or large, and whether any fortuitous opportunities for simplifcation appear.
+Introducing the scaled variables
 \begin{equation}
@@
 - \frac{k q^2 t_c^2}{16 \pi \epsilon_0 R^2 m y_c} \left( \frac{y_c}{R} \bar{y} + 1 \right)^{-2}, & \nonumber \\
-& \bar{y}(0) = 0, \hspace{1 mm} \bar{y}'(0) = \frac{U_0 t_c}{y_c} .&
+& \bar{y}(0) = 0, \hspace{1 mm} \bar{y}'(0) = \frac{U_0 t_c}{y_c} .& \label{scaled_eqn}
 \end{eqnarray}
-We note several dimensionless groups
+We note the existence of several dimensionless groups
 \[ \mathbf{\Pi}_1 = \frac{C_D \rho A y_c}{2 m}, \hspace{5 mm}
@@
 \mathbf{\Pi}_3 = \frac{k q^2 t_c^2}{16 \pi \epsilon_0 R^2 m y_c}, \hspace{5 mm}
-\mathbf{\Pi}_4 = \frac{y_c}{R}.\]
+\mathbf{\Pi}_4 = \frac{y_c}{R}, \hspace{5 mm}
+\mathbf{\Pi}_5 = \frac{U_0 t_c}{y_c}.\]
 
 \subsubsection{Inertial Electro-Image Limit}
-In the limit of small $y, \hspace{1mm} t$ we expect intertia to scale as Coulombic and image force. With $y_c \sim U_0 t_c$ and picking $t_c$ such that Coulombic force is $\mathcal{O}(1)$
+
+In the limit of small $y$ and $t$ we expect intertia to scale as Coulombic and image force.
+In this limit we can approximate the electric field as the constant, $E_0$.
+One possible characteristic lengthscale is $y_c \sim R_d$, however this ultimately is a poor choice.
+With $y_c \sim U_0 t_c$ and picking $t_c$ such that Coulombic force is $\mathcal{O}(1)$, the intrinsic scales become
 \[ t_c \sim \frac{m U_0}{q E_0}, \hspace{5 mm}
@@
 \]
-where $\mathbb{I}\mbox{m}$ is the Image number, and denotes the ratio of image forces to the Coulombic force of the unperturbed field, and where where $\mathbb{E}\mbox{u}$ is the electrostatic Euler number, and is a ratio of inertia to electrostatic force.
+where $\mathbb{I}\mbox{m}$ is the Image number, and denotes the ratio of image forces to the Coulombic force of the unperturbed field, and where $\mathbb{E}\mbox{u}$ is the electrostatic Euler number, and is a ratio of inertia to electrostatic force.
 
 \subsubsection{Inertial Electro-Viscous Limit}
-In the limit of large $y, \hspace{1mm} t$ we expect droplet inertia to scale as Coulombic force and drag. In this case there are several obvious choices of scales:
+
+In the limit of large $y$ and $t$ we expect droplet inertia to scale as Coulombic force and drag.
+In this limit we approximate the electric field as $E \approx y_c^2 E_0 y^{-2}$.
+In this case there are several (obvious) possible choices of scales:
 \begin{enumerate}
-\item $y_c \sim U_0 t_c$ and make Coulomb force $\mathcal{O}(1)$.
-\item $y_c \sim R_d$ or $L$, $t_c \sim \frac{L}{U_0}$ but this makes the governing equation singular.
-\item $y_c \sim R_d$ or $L$, $t_c \sim \left( \frac{L m}{q E_0} \right)^{1/2}$.
-\item $y_c \sim R_d$ or $L$, and making Coulomb force $\mathcal{O}(1)$.
+\item $y_c \sim U_0 t_c$, and make Coulomb force $\mathcal{O}(1)$.
+\item $y_c \sim L$, $t_c \sim \frac{L}{U_0}$ (however, this makes Equation \ref{scaled_eqn} singular).
+\item $y_c \sim L$, $t_c \sim \left( \frac{L m}{q E_0} \right)^{1/2}$.
+\item $y_c \sim L$, and make Coulomb force $\mathcal{O}(1)$.
 \end{enumerate}
+%In Case 4, the characterisitc time is $t_c \sim \left( \frac{4 \pi R_d^2}{q E_0 L} \right)^2 $ and the non-dimensional governing equation is given by
+%\begin{eqnarray}
+%&\bar{y}'' = - \frac{C_D \rho A L}{2 m} \bar{y}'^2 - \left( \frac{L}{R_d} \bar{y} + 1\right)^{-2} ,& \nonumber \\
+%& \bar{y}(0) = \frac{R_d}{L}, \hspace{5 mm} \bar{y}'(0) = \left( \frac{4 \pi U_0^2 R_d^2}{q E_0 L^3}\right)^{1/2} = \frac{R_d}{L} \sqrt{\mathbb{E}\mbox{u}_+}.& \nonumber
+%\end{eqnarray}
+%where $\mathbb{E}\mbox{u}_+ = \frac{4 \pi m U_0^2}{q E_0 L}$ is a long time scaled electrostatic Euler number.
 
-In Case 3, the characterisitc time is $t_c \sim \left( \frac{4 \pi R_d^2}{q E_0 L} \right)^2 $ and the non-dimensional governing equation is given by
-\begin{eqnarray}
-&\bar{y}'' = - \frac{C_D \rho A L}{2 m} \bar{y}'^2 - \left( \frac{L}{R_d} \bar{y} + 1\right)^{-2} ,& \nonumber \\
-& \bar{y}(0) = \frac{R_d}{L}, \hspace{5 mm} \bar{y}'(0) = \left( \frac{4 \pi U_0^2 R_d^2}{q E_0 L^3}\right)^{1/2} = \frac{R_d}{L} \sqrt{\mathbb{E}\mbox{u}_+}.& \nonumber
-\end{eqnarray}
-where $\mathbb{E}\mbox{u}_+ = \frac{4 \pi m U_0^2}{q E_0 L}$ is a long time scaled electrostatic Euler number.
-We prefer the approach with the greatest physical simplicity, fewest Pi terms, and has homogoenous initial conditions.
-
-In Case 1, the characteristic dimensions are
+We prefer the approach with the greatest physical simplicity, fewest Pi terms, and that has homogenous initial conditions. We choose Case 1, where the intrinsic scales are given by
 \[ t_c \sim \frac{R_d^2}{L^2} \frac{4 \pi m U_0}{q E_0}, \hspace{5mm} y_c \sim \frac{R_d^2}{L^2} \frac{4 \pi m U_0^2}{q E_0}.
@@
 \end{eqnarray}
-where $\mathbb{D}\mbox{g} \equiv \frac{C_D \rho_a}{\rho_l}$ and $\mathbb{E}\mbox{u}_+ = 4 \pi \frac{R_d^2}{L^2} \mathbb{E}\mbox{u}$. This is the preferred scaling.
+where we call $\mathbb{D}\mbox{g}$ the drag number, $\mathbb{D}\mbox{g} \equiv \frac{C_D \rho_a}{\rho_l}$ and $\mathbb{E}\mbox{u}_+ = 4 \pi \frac{R_d^2}{L^2} \mathbb{E}\mbox{u}$.
 
@@
 \subsubsection{Inertial Electro-Image Limit}
-The alternate scalings of the equation of motion given by Equations \ref{drag_limit}, \ref{img_limit} are weakly non-linear differential equations in the sense that they reduce to linear equations as the parameter $\mathbb{E}\mbox{u} \rightarrow 0$.
+
+The alternate scalings of the equation of motion given by Equations \ref{img_limit}, and \ref{drag_limit} are weakly non-linear differential equations in the sense that they reduce to linear equations as the parameter $\mathbb{E}\mbox{u} \rightarrow 0$.
 If we take $\mathbb{E}\mbox{u}$ to be a small parameter $\epsilon$, we can find an asymptotic approximation to the solution of the non-linear equation by means of a regular perturbation.
@@
 .\]
+
 By substitution of the expansion (and its derivatives) into the differential equation, and equating terms by order, and using the notation $\alpha = \mathbb{I}\mbox{m}$ (this being the equation scaled in the small-times limit), we first find the $\mathcal{O}(1)$, unperturbed, solution to the equation of motion to be
 \[{\bar{y}_{0}}{\left (\bar{t} \right )} = \bar{t} + \frac{\bar{t}^{2}}{2} \left(-1 - \alpha\right). \]
+
 Looking at this solution it is evident that if we let $\alpha=0$, the solution is the classical kinematic equation for projectile motion without drag under constant gravity, $g_0$.
 Continuing on with this procedure we find, (after some tedious computations, documented in Appendix \hl{ref}) the higher order composite solutions to be
-
 \begin{eqnarray*}
@@
 The trajectory reduces to the classical $\mathcal{O}(1)$ solution for small values of $\alpha$.
-It should be noted that depsite what is implied by these plots $\alpha$ is not neccisarily completely independent of $\epsilon$, as they share $q$, and $E_0$ as common factors, $U_0 \sim R_d^2$, and $m \sim R_d^3$.}
+It should be noted that despite what is implied by these plots $\alpha$ is not neccisarily completely independent of $\epsilon$, as they share $q$, and $E_0$ as common factors, $U_0 \sim R_d^2$, and $m \sim R_d^3$.}
     \label{fig:short_times}
@@
 In the limit of small $\epsilon$ the trajectories collapse to the $\mathcal{O}(1)$ solution regardless of the Image number.
-In principle there is some coupling between $\mathbb{E}\mbox{u}$ and $\mathbb{I}\mbox{m}$, notably this relationship does not depend on the electric field $E_0$ but on a charge to mass ratio.
+In principle there is some coupling between $\mathbb{E}\mbox{u}$ and $\mathbb{I}\mbox{m}$; notably this relationship does not depend on the electric field $E_0$ but on a charge to mass ratio.
 The effect of contact line hysteresis on the initial jump velocity $U_0$ will also tend to independently decohere the natural covariance between these parameters.
@@
 \subsubsection{Inertial Electro-Viscous Limit}
+
 By similar arguments we find an asymptotic estimate of the trajectory in the long-times scaled regime.
@@
 \end{figure}
-
 Again, the trajectory seemingly reduces to the classical $\mathcal{O}(1)$ solution for small values of of $\epsilon$.
@@
 By again appying a regular perturbation to the asymptotic solution with the expansion
-
 \[ \bar{t} \sim \bar{t}_0 + \epsilon \bar{t}_1 + \epsilon^2 \bar{t}_2 \ldots \epsilon^n\bar{t}_n  
 ,\]
-
 and solving for the roots (that is, the times when $\bar{y} = 0$), we find an asymptotic estimate for the time-of-flight, $t_f$.
 The $\mathcal{O}(\epsilon^2)$ accurate time-of-flight estimate is given by
-
-\[t_f = 2 + \epsilon \left(\frac{4}{3} - \frac{2 \beta}{3}\right) + \epsilon^{2} \left(\frac{4}{5} - \frac{4 \beta}{3} + \frac{2 \beta^{2}}{5}\right).\]
-
-Substituting the experiemental value of $\beta$ we find the time-of-flight estimate for water droplets in air to be
-
-\[ t_f = 2 + 1.333 \epsilon + 0.799 \epsilon^{2} \]
-
+\[t_f = 2 + \epsilon \left(\frac{4}{3} - \frac{2 \beta}{3}\right) + \epsilon^{2} \left(\frac{4}{5} - \frac{4 \beta}{3} + \frac{2 \beta^{2}}{5}\right) + \mathcal{O}(\epsilon^3).\]
+Substituting the experimental value of $\beta$ we find the time-of-flight estimate for water droplets in air to be
+\begin{equation} \label{time_of_flight}
+t_f = 2 + 1.333 \epsilon + 0.799 \epsilon^{2} + \mathcal{O}(\epsilon^3) 
+\end{equation} 
 In Figure \ref{fig:drag} we look at the effect of increasing values of ${\mathbb{E}\mbox{u}}_+$ on time-of-flight.
@@
     \input{../figures/drag.pgf}
-    \caption{Droplet time of flight as a function of $\epsilon = {\mathbb{E}\mbox{u}}_+$.}
+    \caption{Droplet time-of-flight as a function of $\epsilon = {\mathbb{E}\mbox{u}}_+$.}
     \label{fig:drag}
@@
 We see that as $\epsilon$ grows to be no longer small, the time-of-flight grows rapidly, but this behaviour appears to have an asymptote at a certain critical velocity as $\mathcal{O}({\mathbb{E}\mbox{u}}_+) \rightarrow \mathcal{O}(1)$; this is an electrostatic escape velocity, $U_e$.
-
 We can find the escape velocity by solving a modified version of the equation of motion,
@@
 where $U_e$ is the escape velocity and $U_{\infty} = \sqrt{U_0^2 - U_e^2}$. The condition for the droplets to escape the electric field is then given by
-\[
-8 \pi {\mathbb{E}\mbox{u}}_+ > 1.
-\]
+\begin{equation}\label{escape}
+{\mathbb{E}\mbox{u}}_+ > 1/8 \pi.
+\end{equation}
 
@@
 \]
-with a characteristic time $t_c \sim \frac{2 m}{C_D \rho A U_{\infty}}$ which is the halving time of the velocity.
+with a characteristic time $t_c \sim \frac{2 m}{C_D \rho A U_{\infty}}$, which is the halving time of the velocity.
 

### 2018-01-25 doc/manuscript/introduction.tex
draft

@@
 
-\newpage
 \section{Introduction}
@@
 \begin{itemize}
-\item We have observed droplet accelerations on the order of 10's of cm/s$^2$ in proximity to charged surfaces.
+\item We have observed droplet accelerations on the order of 10's of cm/s$^2$ in proximity to charged surfaces for a range of droplet volumes $V_d \approx 0.01- 0.5$ mL.
 \item Droplets appear to be attracted to regions of high electric field.
@@
 The superhydrophobic surfaces used in the spontanous droplet jump experiments have thin PTFE coatings, and we observe that it is extremely easy to produce significant surface potentials ($\sim 100-500$ V) by simply running streams of filtered water over them.
-A study of this water on PTFE contact charging phenomenon was done by Yatsuzuka \emph{et al.} \cite{yatsuzuka_electrification_1994}, who suggest this process results from formation of an electrical double layer formed by selective adsoption of ions at the polymer surface.
+A study of this water on PTFE contact charging phenomenon was done by Yatsuzuka \emph{et al.} \cite{yatsuzuka_electrification_1994}, who suggest this process results from formation of an electrical double layer formed by selective adsorption of ions at the polymer surface.
 They also found that the specific charge on the droplets in contact with the surface depends on their surface velocity and conductivity.
-New developments suggest that adsoption of $OH^-$ ions are the source of the double layer \cite{beattie_intrinsic_2006} \cite{strazdaite_water_2015}.
+New developments suggest that adsorption of $\mbox{OH}^-$ ions are the source of the double layer \cite{beattie_intrinsic_2006} \cite{strazdaite_water_2015}.
 This is the most likely accidental source of charge on the suphydrophobic surface.
-Given the large roughness (in the sense of the ratio projected to actual surface area), of the superhydrophobic surfaces used in the experiment, and given that the droplets are initially in a Cassie-Baxter state, an electrically insulating air layer is maintained that prevents grounding of the droplets despite the large potential difference between them and and the surface charges.
+Given the large roughness (in the sense of the ratio of projected to actual surface area), of the superhydrophobic surfaces used in the experiment, and given that the droplets are initially in a Cassie-Baxter state, an electrically insulating air layer is maintained that prevents grounding of the droplets despite the large potential difference between them and and the surface charges.
 Ultimately it is this potential, in the energetic sense, that is responsible for the droplet bouncing motion we observe.
@@
 Field induced charging occurs due to physical breakup of a conductor having a field induced dipole.
-In our case this occurs when the droplet is deposit on the charged surface by a syringe.
+In our case this occurs when the droplet is deposited on the charged surface by a syringe.
 The metal syringe needle tip, and the liquid in the syrigne itself are essentially a ground connection which is broken when the syringe is removed.
@@
 Surface charging largely occurs due to low energy electrons (3-50 keV) which do not penetrate the surface of the spacecraft external stucture \cite{czepiela_charging_1997}.
+The ultimate sources of these charges are trapped charged particles of the van Allen radiation belts, galactic cosmic rays, and the solar wind.
 This deposited charge accumulates and can lead to significant potential differences between different parts of a spacecraft, sometime leading to breakdown and discharge, called Paschen discharge.
 Deep dielectric charging occurs when higher energy charged particles penetrate the surface of a dielectric material, which can also lead to large potential differences if the dielectric leakage is lower than the external charging rate.
-The ultimate sources of these charges are trapped charged particles of the van Allen radiation belts, galactic cosmic rays, and the solar wind.
-In a fluid mechanical context, this accumulated charge could be problematic during any multiphase venting process, as might be expected to occur during autonomous satellite servicing refueling operations, or during boil-off venting of cryogens stored over long periods in a space environment (as in crewed Mars missions, or in propellant depot operations).
+In a fluid mechanical context, this accumulated charge could be problematic during any multiphase venting process, as might be expected to occur during autonomous satellite servicing refueling operations, or during boil-off venting of cryogens stored over long periods in a space environment (as in many crewed Mars mission scenarios, or in cryogenic propellant depot operations).
 Such venting, if uncontrolled, can lead to contamination of spacecraft surfaces by the propellant.

### 2018-01-25 doc/manuscript/manuscript.tex
draft

\documentclass[12pt,a4paper,oneside]{book}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
%\usepackage{fontspec} % This line only for XeLaTeX and LuaLaTeX
\usepackage{pgfplots}
\usepackage{pgf}
\graphicspath{ {../figures/} }
%\usepackage{svg}
\usepackage{verbatim}
\usepackage{color,soul}
\usepackage{listings}
\usepackage{setspace}
\newlength\figureheight
\newlength\figurewidth
\setlength\figureheight{7cm}
\setlength\figurewidth{10cm}
\usepackage[
backend=biber,
style=phys,
sorting=none
]{biblatex}
\addbibresource{thesis.bib}
\usepackage{import}
\let\pgfimageWithoutPath\pgfimage 
\renewcommand{\pgfimage}[2][]{\pgfimageWithoutPath[#1]{../figures/#2}}
\usepackage{array} 
\usepackage{appendix}
\usepackage{makeidx}
\makeindex

\title{\textsf{\textbf{Droplet Electro-Bouncing in Low-Gravity}}}
\vspace{-25mm}
\author{Erin S. Schmidt, Mark M. Weislogel}
\date{}

%\usepackage{abstract}
%\renewcommand{\abstractnamefont}{\normalfont\bfseries}
%\renewcommand{\abstracttextfont}{\normalfont\small\itshape}

\raggedbottom
\usepackage{setspace}
\usepackage{afterpage}
\newcommand\blankpage{%
    \null
    \thispagestyle{empty}%
    \addtocounter{page}{-1}%
    \newpage}

\begin{document}
%\frontmatter
%\maketitle
%\afterpage{\blankpage}
\begin{titlepage}
\doublespacing

\centering %\vspace*{-10ex}
{\large \textsf{\textbf{Droplet Electro-Bouncing in Low-Gravity}}}

\vspace{15ex}
by\\
Erin Stivers Schmidt

\vspace{15ex}
\singlespacing
A thesis submitted in partial fulfillment of the\\
requirements for the degree of

\vspace{11ex}
Master of Science\\
in\\
Mechanical Engineering

\vspace{12ex}
Thesis Committee:\\
Mark Weislogel, Chair\\
Ra\'ul Bayo\'an Cal\\
Gerry Recktenwald\\

\vfill
\vspace{2ex}
Portland State University\\%[8pt]
{\number\year}
\end{titlepage}

\doublespacing
\clearpage

\frontmatter

\doublespacing
\section*{Abstract}
\addcontentsline{toc}{chapter}{\numberline{Abstract}}
\noindent
We investigate the dynamics of spontaneous jumps of water droplets from electrically charged superhydrophobic dielectric surfaces during a sudden step reduction in gravity level. In the brief free-fall environment of a drop tower, with a non-homogeneous external electric field (with strengths ~0.39-2.36 kV/cm) arising due to dielectric surface charges, body forces acting on the jumped droplets are primarily supplied by polarization stress and Coulombic attraction instead of gravity. This electric body force leads to a droplet bouncing behavior similar to well-known phenomena in 1-g, though occurring for much larger droplets ($\sim$ 0.5 mL). We show a simple model for the phenomenon, its scaling, and asymptotic estimates for droplet time of flight. The droplet net charge, estimated to be on the order of $1 \times 10^{-9}$ C, is field induced rather than by contact charging at the (PTFE coated) hydrophobic interface. In 1-g, for Weber numbers $>$ 0.4, impact recoil behavior on a super-hydrophobic surface is normally dominated by damping from contact line hysteresis. However, at the low Bond and Ohnesorge numbers occurring in free-fall, the droplet impact dynamics additionally include electrohydrodynamic surface wettability effects. This is qualitatively discussed in terms of trends in coefficients of restitution and dimensionless contact time.

\clearpage
% ========================================

%\vspace*{8ex}
\vspace*{\fill}
%\section*{Dedication}
%\addcontentsline{toc}{chapter}{\numberline{Dedication}}

\emph{To Mom, Laura, and the DDT team.}\\
\vspace*{\fill}

\clearpage

% ========================================

%\vspace*{8ex}
\vspace*{\fill}
\section*{Acknowledgements}
\addcontentsline{toc}{chapter}{\numberline{Acknowledgements}}

This work was supported primarily by NASA Cooperative Agreement NNX12A047A. I am also greatly indebted to Andrew Greenberg for his frequent and sage technical advice, and to Joe Shields for his assistance with drop tower experiments. \\ 
\vspace*{\fill}
\clearpage

\tableofcontents
\afterpage{\blankpage}
\listoffigures
\afterpage{\blankpage}

\mainmatter
\chapter{Introduction}
\begin{quote}
``When the influence of gravity on fluid behavior is diminished or removed, other forces, otherwise of small significance, can assume paramount roles.''
- NRC Report to NASA, 2003  \cite{motil_priorities_2012}
\end{quote}

Our terrestrially born intuition about how liquids flow is easily confounded in a low-gravity environment. This should come as little surprise, as we are creatures evolved at the bottom of a steep gravity well; gravity is natural to us. However when the magnitude of the gravity body-force becomes small, other forces come into play in fluid dynamics which are otherwise negligible, relatively speaking, under normal circumstances in 1-g. This 1-g cognitive bias leads to a plethora of problems which are both trivially easy to solve in 1-g, and which despite decades of study continue to elude solutions in a low-gravity context. One example of these problems is the so-called ``phase separation'' problem of separating a gas phase from a multi-phase flow (or the reverse case), without the aid of gravitational buoyancy. Sans buoyancy otherwise mundane activities such as venting a gas or settling a liquid in a tank become problematic \cite{petrash_controlling_1964}. Trapped bubbles can vapor lock ECLSS (Environmental Control and Life Support), power, or propulsion systems \cite{jenson_passive_2014}. Issues of phase separation have so bedeviled human endeavors in space that an entire Apollo Saturn 1B mission (AS-203) was earmarked to study them \cite{hastings_[saturn_1965}. This problem has for some time motivated a quest for substitute body forces, and the present work follows in that august tradition.

Considering the scope of this problem of poor low-gravity intuition, we would profit by identifying a scale to quantify how wrong our intuition is. First, let's clear up a common misnomer about the state of ``zero-gravity''. The theory of general relativity is based on the fundamental equivalence of gravity and acceleration. There is no known way to determine whether one is in gravity-free space or free-falling in a gravitational field (or conversely whether or not we are uniformly accelerating, or standing at rest in a gravitational field). This is sometimes called the equivalence principle of general relativity (e.g. the equivilence of gravitational and inertial mass). In theoretical terms a zero-g experiment performed in a drop tower on the surface of the Earth is equivalent to the same experiment performed in the nearly gravity-free deep space between galaxies, despite the fact that the drop tower itself is in a 1-g gravity field. At the orbital altitude of the International Space Station (ISS) the gravity level is still nearly 90\% of its value at sea-level on Earth, but the astronauts aboard ISS feel weightlessness because they are free-falling. In a practical sense there is never true zero-g, even in the aforementioned dark space between galaxies, as there are always small, but nonetheless, measurable forces to accelerate any body. For instance in low-Earth orbit, accelerations due to drag in the tenuous outer atmosphere are on the order of $1 \times 10^{-6}$ g, hence the term ``microgravity''. This small acceleration provides an ersatz gravity, but there are also other forces present. Foremost of these are capillary forces.

Capillary forces are due to the cumulative effect of a large number of very short range molecular interactions and in a 1-g context are usually quite weak, relatively speaking. However, in a low-gravity environment these are nearly the only forces present, and are therefore strong in a relative sense. In comparing the relative magnitudes of gravity and the unusually strong capillary force we arrive at a useful figure of merit for assessing how wrong our fluid mechanical intuition is likely to be in a low-gravity context. This figure of merit is the Bond number dimensionless group
\[ \mathbb{B}\mbox{o} \equiv \frac{g R^2 \Delta \rho}{\gamma} 
\]
where $g$ is the acceleration, $R$ is the interfacial radius of curvature, $\Delta \rho$ is the difference in densities across the interface (which simplifies to $\rho$, for large $\Delta \rho$, as in the case of a air-water interface), and where $\gamma$ is the surface tension. In cases where $\mathbb{B}\mbox{o}$ is small, a liquid is effectively in low-gravity regardless of the nominal local gravity level. Very small droplets ($R < 1$ mm), for instance, are in low-gravity for all intents and purposes and have nearly spherical shapes. Contrarily, in a space environment in cases where $R$ becomes large, such as with the case of large diameter spacecraft propellant tanks then $ \mathbb{B}\mbox{o} \gg 1$ even though the acceleration is small. As a corollary to this discussion we note that on the basis of dimensional similarity, we can accurately simulate the low-gravity fluid mechanics of large propellant tanks even in small drop towers simply by scaling dimensionless groups like the Bond number.

As with surface tension, electrostatic forces also have useful applications as substitutes for gravity. Electrohydrodynamic (EHD) body forces have been suggested to combat thermal stratification of propellants under low-g conditions where bouyancy induced natural convection is very small \cite{blackmon_collection_1965}. In this case electro-convection is an analog of natural convection due to a dielectric permitivity gradient (as opposed to a fluid density gradient), which is a function of fluid temperature, in the presence of a body force field (in this case an electric field). The study also suggested applications in cryogenic tank vent screening, and in reducing heat transfer to cryogenic propellants (and thus boiloff losses) by dielectrophoretically positioning ullage vapors around the tank walls as a thermal barrier. EHD forces have been studied for enhancing boiling heat transfer by promotion of bubble detachment and prevention of dryout (again as an ersatz bouyancy) \cite{snyder_dielectrophoresis_2001} \cite{di_marco_influence_2003} \cite{marco_use_2012}. EHD heat pipes, which substitute an electrode structure for the capillary wicking structure of a conventional thermocapillary heat pipe can evade the wicking limit \cite{jones_electrohydrodynamic_1973}. These are restricted to the use of insulating dielectric liquids (which usually have relatively low thermal conductivity), but are highly robust against dryout, support active flow control, and have low viscous losses. Dielectrophoretic settling of cryogenic propellants (in both total and partial communication configurations), has been studied analytically in both static \cite{hurwitz_electrohydrodynamic_1966} and dynamic cases \cite{koval_dynamics_1967}, and in drop tower experiments \cite{fax_dielectrophoretic_1969}. EHD forces have also beeen suggested for low-g slosh baffling \cite{boretz_orbital_1970} \cite{petrash_use_1968} \cite{hurwitz_dielectrophoretic_1968}, and studied extensively for the mitigation of vapor pullthrough during tank emptying (and concomittent minimization of propellant residuals at burnout) in a series of experiments at the NASA Lewis (now Glenn) Research Center 2.2 s drop tower facillity \cite{berenyi_dielectrophoretic_1970}.

\section{Spontaneous Droplet Jump}
Low-gravity droplet dynamics, and the dynamics and applications of the so-called spontaneous droplet jump, is an active area of study at the Portland State University Dryen Drop Tower labratory (DDT). When a nonwetting, gravity dominated sessile droplet (e.g. a puddle), initially at rest in the Cassie-Baxter state undergoes a large step reduction in $\mathbb{B}\mbox{o}$ it will spontaneously jump away from the surface. The Cassie-Baxter state is a metastable non-wetting state on a textured surface, sometimes also known as the Fakir state. This was first observed experimentally by Kirko \emph{et al.} \cite{kirko_phenomenon_1970} in 1970 and later by Wollman \emph{et al.} in 2016 in a set of experiments conducted using a low-gravity drop tower \cite{wollman_more_2016}. The kinetic energy of the jump is supplied by the defect in free surface energy as the new minimum energy surface equilibrium has approximately constant curvature. If the viscous energy losses by shear, and internal flows during roll up are neglected, as well as energy lost due to the hysteresis of the dynamic contact line, then the available kinetic energy is given by
\[KE = SE_2 -SE_1 = [(\sigma A)_{gl} + (\sigma A)_{sg}]_2 - [(\sigma A)_{ls} + (\sigma A)_{gl} + (\sigma A)_{sg}]_1. \]

The droplet `rolls up' as it jumps away from the surface due to radial motion of a capillary wave away from the contact line. The characteristic time scale of the rolling up scales as $t_j \sim R_p/U ~(\rho H R^2_p/\sigma)^{1/2}$ \cite{attari_puddle_2016}, which resembles the contact time, $\tau \approx 2.6(\rho R^3_d/\sigma)^{1/2}$ reported by Richard \emph{et al.} in 2002 for the related problem of droplets impacting hydrophobic surfaces in 1-g \cite{richard_surface_2002}. For droplets with radial symmetry and sufficiently high initial $\mathbb{B}\mbox{o}$ these waves coalesce as a shock leading to geysering and creation of satellite drops by the Rayleigh-Plateau breakup of the geyser. In the case of smaller jumping droplets, the capillary waves do not lead to geysering, and are viscously damped to varying degrees during the brief free-fall period of the drop tower.

The spontaneous droplet jump phenomenon provides a useful window though which to study the dynamics of large-length scale capillary dominated droplets. The physics of such massive droplets (far beyond the 1-g millimetric capillary length scale) utterly defy terrestrial expectations about the ways in which liquid droplets `should' behave, and also are of critical practical importance in a space systems setting where large capillary length scale multiphase flows are common.

\section{Droplet Electro-Bounce}
During `rolling-up' under ideal conditions, the droplet jump phenomenon is governed by a balance of inertia and surface tension forces, and once aloft the droplet motion is nominally in a regime of pure drag, however other forces can again come into play.

\emph{Occasionally we observe jumped droplets to decelerate and return to the superhydrophobic surface, rebounding multiple times after fashion of a rigid body bouncing on a surface under 1-g. The forces at work in this phenomenon are presumably electrostatic in origin.} This was unintended, but the phenomenon is interesting. Admittedly, there is a certain irony that this typical failure of low-gravity intuition come as any surprise to experienced low-gravity researchers. A time-lapsed composite image showing an example of the phenomenon is shown in Figure \ref{fig:bounce}.
\begin{figure}[htb]
\centering
\includegraphics[width=0.75\textwidth]{bounce}
\caption{The trajectory of a 0.5 mL droplet is captured in a composite image over a single bounce period ($\sim 1.25$ s). The surface potential of the superhydrophobic dielectric is $\varphi_s = 1.25 \pm 0.41$ kV. \label{fig:bounce}}
\end{figure}

This ``electro-bounce'' phenomenon is the subject of this thesis. We begin with some preliminary observations of the phenomenon:
\begin{itemize}
\item We have observed droplet accelerations on the order of 10's of cm/s$^2$ in proximity to charged surfaces for a range of droplet volumes $V_d \approx$ 0.01- 0.5 mL.
\item Droplets appear to be attracted to regions of high electric field. The horizontal (surface plane parallel) components of the droplet trajectory usually oscillate about their initial position during drops (except in cases of nearly pure 1-D vertical translation). For especially small drops close to the spontaneous droplet jump limit ($V_d \sim$ 0.01 mL) the droplets do not jump, but translate across the surface in a hovering regime until either they reach a local maximum of the electric field, or until their motion is sufficiently damped by contact line hysteresis that pinning arrests their motion.
\item Droplets appear to have net free charge. In cases of multiple simultaneous droplet jumps the droplets repel each other as they bounce or hover in orbital motion around regions of strong field.
\item The magnitude of the droplet trajectory maxima (apoapses) appear to be related to the droplet volume (which affects their mass, and initial jump velocity, and thence their inertia), and to the electric field strength.
\end{itemize}

There are several potential origins of the electric charge responsible for this phenonenon. It is well known that water acquires free charge (usually positive) when in contact with certain polymers, especially polytetrafluoroethylene (PTFE) \cite{langmuir_surface_1938}, through a process called contact charging. The superhydrophobic surfaces used in the spontanous droplet jump experiments have thin PTFE coatings, and we observe that it is extremely easy to produce significant surface potentials ($\varphi_s \sim$ 100-500 V) by simply running streams of distilled water over them. A study of this water on PTFE contact charging phenomenon was done by Yatsuzuka \emph{et al.} \cite{yatsuzuka_electrification_1994}, who suggest this process results from formation of an electrical double layer formed by selective adsorption of ions at the polymer surface. They also found that the specific charge on the droplets in contact with the surface depends on their surface velocity and conductivity. New developments suggest that adsorption of $\mbox{OH}^-$ ions are the source of the double layer \cite{beattie_intrinsic_2006} \cite{strazdaite_water_2015}. This is the most likely accidental source of charge on the suphydrophobic surface. Given the large roughness (in the sense of the ratio of projected to actual surface area), of the superhydrophobic surfaces used in the experiment, and given that the droplets are initially in a Cassie-Baxter state, an electrically insulating air layer is maintained that prevents grounding of the droplets despite the large potential difference between them and and the surface charges. Ultimately it is this potential, in the energetic sense, that is responsible for the droplet bouncing motion we observe.

The source of the net free charge on the droplets is another issue. The droplet charge could also be due to this contact charging mechanism. For instance, in a 1996 paper, NASA flight engineer Don Pettit discusses the problem of flow induced charging of liquids in a low-gravity context, resulting ultimately from contact charging phenomenon \cite{pettit_donald_flow_????}. Another mechanism for the droplet charge is field induced charging. Field induced charging occurs due to physical breakup of a conductor having a field induced dipole. In our case this occurs when the droplet is deposited on the charged surface by a syringe. The metal syringe needle tip, and the liquid in the syrigne itself are essentially a ground connection which is broken when the syringe is removed. Field induced charging is at work in the famous Kevin thunderstorm, and is applied in inkjet, and electrospay technologies (where in each case the breakup is by the Rayleigh-Plateau instability). Notably, in Pettit's discussion of contact charging of liquids in low-g, he remarks on accidental electrostatic ``hula-ing'' of sillicon oil droplets when ejected from a syringe in the vicinity of a highly-charged polymer surface during an experiment conducted aboard STS-5 by mission specialist Joseph Allen. Depending on the (highly-variable) electrical conductivity of the sillicon oil, and the material of the syringe used in the experiment, the charge could as easily be field induced as due to contact charging. Relatedly, in a series of informal, and somewhat whimsical experiments Pettit electrostatically orbited small water droplets around a triboelectrically charged PTFE knitting needle while aboard ISS during expedition 30/31 \cite{stevenson_electrostatic_2015}. Again, in this case, the droplet charge is very likely field induced.

\section{Applications}
Study of the droplet electro-bounce phenomenon may have results which can be extended to useful applications in a space environment.

External surfaces of spacecraft tend to become charged with time due to the space environment itself. Surface charging largely occurs due to low energy electrons (3-50 keV) which do not penetrate the surface of the spacecraft external stucture \cite{czepiela_charging_1997}. The ultimate sources of these charges are trapped charged particles of the van Allen radiation belts, galactic cosmic rays, and the solar wind. This deposited charge accumulates and can lead to significant potential differences between different parts of a spacecraft, sometime leading to breakdown and discharge, called Paschen discharge. Deep dielectric charging occurs when higher energy charged particles penetrate the surface of a dielectric material, which can also lead to large potential differences if the dielectric leakage is lower than the external charging rate. In a fluid mechanical context, this accumulated charge could be problematic during any multiphase venting process, as might be expected to occur during autonomous satellite servicing refueling operations, or during boil-off venting of cryogens stored over long periods in a space environment (as in many crewed Mars mission scenarios, or in cryogenic propellant depot operations). Such venting, if occurring in a region of strong field, will also tend to produce a stream of charged droplets, which can then return and lead to contamination of the spacecraft surfaces.

As previously noted, robust phase separation is critical to high reliability multiphase systems used in thermal control and life support. Active (but solid-state) phase seperation for ECLSS multiphase flows, espcially high void-fraction flows is a possible application of this work. Such flows pertain to dish washing, laundry, waste solids drying, food processing, the Sabatier CO$_2$ reaction, and possibly in vapor-compression cycle condensers. Phase seperation for other disperse droplet flows include electrostatic droplet seperators for high-efficiency Rankine-cycle turbines (which require a droplet-free vapor phase entering the turbine, but where convertional superheat approaches comes with severe mass penalties) \cite{unterberg_zero_1962}, or more speculatively, in high temperature liquid droplet radiators with electrostatic collection \cite{white_liquid_1987}. Removal of satellite droplets produced during pippetting in wet-lab research outside of a glovebox environment aboard ISS has also been recently suggested as a application of the work \hl{[ref, personal discussion with NASA MSFC folk at ASGSR17 conference]}. Droplets can become spontaneously charged by contact with standard micropipette tips \cite{choi_spontaneous_2013}, and this free charge can possibly be leveraged for the purposes of phase separation in low-gravity.

\section{Overview of this Thesis}
This work primarily concerns itself with development of a simple model to aid in design of future electrostatic disperse droplet phase separators. To that end this work encompasses:
\begin{enumerate}
\item A simple mathematical model of droplet electro-bounce, its scale analysis, and asymptotic estimates for droplet apoapses and times-of-flight.
\item The results of a controlled experiment, where the effect of key independent variables droplet volume $V_d$, and dielectric surface charge density $\sigma$, on droplet trajectories is tested.
\item Science of opportunity comprising experimental data on droplet impacts at very low Weber and Ohnesorge numbers, for varying levels of electrostatic Bond number. 
\end{enumerate}

\chapter{Theory}
\section{Forces and the Equation of Motion}
This section will develop a simple, 1-dimensional model of the dynamics of droplets dominated by electrostatic forces. Treating a droplet as a particle, with radius $R_d$, the  equation of motion of charged droplets center of mass as it translates vertically along the central axis of a finite square charged dielectric sheet is given by
\begin{equation}
m y'' = - \mathbf{F}_D - \mathbf{F}_E, \hspace{5 mm} y(0) = R_d, \hspace{5 mm} y'(0) = U_0,
\label{gov_eqn}
\end{equation}
where $m$ is the droplet mass, $y'' = \frac{d^2 y}{d t^2}$ is the droplet acceleration, $\mathbf{F}_D$ is the drag force, and $\mathbf{F}_E$ is the electrostatic force. The initial conditions are such that, when the $\mathbb{B}\mbox{o}$ is suddenly reduced at the start of the drop tower experiment, the droplet jumps with initial velocity $U_0$ from its 1-g resting position $R_d$ at $t=0$. The signs of the forces on the right side of Equation \ref{gov_eqn} indicate that they act in the opposite direction of the droplet motion. We need to specify models for the various forces in this equation to begin our analysis of the droplet dynamics.

With the assumption of an intermediate range of Reynolds numbers $\mathbb{R}\mbox{e} \equiv \frac{2UR_d}{\nu}$, $1 \leq \mathbb{R}\mbox{e} \leq 5000 $ then the force of drag acting on the droplet will be quadratic,
\begin{equation*}\label{drag_force}
\mathbf{F}_D = \frac{1}{2}C_D \rho A {y'}^2,
\end{equation*}
where $C_D$ is the drag coefficient, $\rho$ is the density of the sorrounding fluid medium (air, in this case), and $A$ is the frontal area of the droplet. For this range of Reynolds numbers it is appropriate to approximate the drag coefficient by the well known Abraham correlation \cite{abraham_functional_1970}
\[C_D = \frac{24}{9.06^2} \left( 1 + \frac{9.06}{\sqrt{\mathbb{R}\mbox{e}}} \right)^2 .\]

Modeling the electrostatic force is somehwhat more involved, but we will start with the standard electrohydrodynamic (EHD) approximation \cite{saville_electrohydrodynamics:taylor-melcher_1997} as our model, and further simplify where possible. Under a DC electric field, we assume that the real part of the dielectric permitivity $\epsilon$, $Re \langle \epsilon \rangle \approx  \mbox{constant}$. We also assume that electric currents are small enough that the effects of magnetic fields can be neglected. The validity of this assumption rests on the size of the characteristic time scale for electrical phenomena $\tau_e = \epsilon \epsilon_0/\sigma_e \ll 1$, where $\tau_e$ is the ratio of absolute dielectric permittivity $\kappa = \epsilon \epsilon_0$, to conductivity $\sigma_e$, of the medium. This characteristic time $\tau_e$ is also known as the relaxation time, and is a measure of how quickly the polarization of a dielectric responds to a change in electric field. Given the respective conductivity, and permittivity of extremely-pure water ($ \kappa \sim 80$, $\sigma_e = 18.2 \times 10^{6}$ $\Omega\mbox{cm}$) \cite{yatsuzuka_electrification_1994}, we estimate $\tau_e \approx 4 \times 10^{-6}$ s. The relaxation time for the common distilled water that is actually used in the droplet experiments is undoubtedly even shorted (due to the presence of solvated ions). Neglecting the effects of a electric double layer on hydration of ions (in the water or the ambient atmosphere) due to the reletively massive size of the droplets studied, then the assumption of small relaxation time further implies that the free charge present in the droplets will remain approximately constant during the typical time interval of a low-gravity experiment.

Supposing that electrical forces acting on free charges and dipoles in a fluid are transferred directly to the fluid itself, then this overall electrical body force will be the the divergence of the Maxwell stress tensor $\tau_m $, by
\[ \mathbf{F}_E = \nabla \cdot \tau_m = \nabla \cdot \left( \epsilon \epsilon_0 \mathbf{E} \mathbf{E} - \frac{1}{2} \epsilon \epsilon_0 \mathbf{E} \cdot \mathbf{E} \delta \right) ,\]
where $\mathbf{F}_E$ is the electric body force per unit volume, and $\delta$ is the delta function. The product of the electric field vectors is the dyadic product.

The classical Korteweg-Helmholtz force density formulation of the Maxwell stress tensor is usually expressed as \cite{melcher_continuum_????}
\begin{equation}\label{force_density}
\mathbf{F}_E = \rho_f \mathbf{E} + \frac{1}{2} \left| E \right|^2 \nabla \epsilon - \nabla \left( \frac{1}{2} \rho \left( \frac{\partial \epsilon}{\partial \rho} \right)_T \left| E \right|^2 \right) .
\end{equation}
The first term in this expression, equivalently written as $q\mathbf{E}$, is the well known Coulombic force or electrophoretic force, which arises from the presence of free charge in an external electric field. We expect this term to dominate the electric force in a DC field. The second term is the force arising from polarization stresses due to a nonuniform field acting across a gradient in permittivity. This force is widely termed the dielectrophoretic force (DEP). The third term describes forces due to electrostriction. It has been noted by Melcher and Hurwitz that the electrostriction term is the gradient of a scalar and can thus be cannononically lumped togeather with the hydrostatic pressure for incompressible fluids \cite{hurwitz_electrohydrodynamic_1966}; we neglect it in our analysis.

It is common to approximate the polarization stress by idealizing the droplet as a simple dipole using the effective dipole moment method first suggested by Pohl in 1958 \cite{pohl_effects_1958}. This approach has been related back to the force density by the volumetric integration of the force density with the substitution of a Taylor series expansion of $\mathbf{E}$ in the limit of a small radial gradient of the field within the dielectric sphere \cite{wang_general_1997}. The DEP force is related to the dipole moment (induced or permanent) of polarizable media which has a tendency to align the dipole with the electric field. If there is a gradient in the field then for a finite separation of charge one end of the dipole will feel a stronger electric field than the other, resulting in a net force. Whether the force is positive or negative in the direction of the electric field gradient depends on the difference of dielectric permittivites between the fluids, rather than on the polarity of $\mathbf{E}$ itself. In principle an external electric field will tend to induce a dipole in a dielectric material, but if the field is spatially uniform there is no gradient in the field and the forces felt by the dipoles are symmetric and thus there is no net force. The dipole moment of a spherical linear-dielectric particle immersed in a dielectric medium is given by
\begin{equation} \label{dipole_m_1}
\mu = V_d \mathbf{P} = \frac{4}{3} \pi R_d^3 \mathbf{P},
\end{equation} 
where $\mathbf{P} = \left(\kappa_1 - 1 \right) \epsilon_0 \mathbf{E} = \chi_e \epsilon_0 \mathbf{E}$ is the polarization moment, and $R_d$ is the particle radius, $\kappa_1 = \frac{\epsilon}{\epsilon_0}$ being the relative dielectric constant of the external medium (air in this case), $\chi_e = \kappa_1 - 1$ being the electric susceptibility of the dielectric medium. The excess polarization $\mathbf{P}_e$, in the sphere is given by
\begin{equation} \label{polarization}
\mathbf{P}_e = \left( \kappa_2 - \kappa_1 \right) \epsilon_0 \mathbf{E} = \frac{3 \kappa_1}{\kappa_2 +2\kappa_1}\mathbf{E},
\end{equation}
where $\kappa_2$ is the relative dielectric constant of the spherical particle. Taking together Equations \ref{dipole_m_1}, and \ref{polarization} the effective dipole moment of the particle is given by 
\begin{equation}\label{dipole_m_2}
\mu = 4 \pi R_d^3 \left( \frac{\kappa_2 - \kappa_1}{\kappa_2 + 2 \kappa_1} \right) \kappa_1 \epsilon_0 \mathbf{E},
\end{equation}
and the force felt by the dipole is 
\begin{eqnarray} \label{dep_force}
\mathbf{F}_{DEP} &=& \left( \mathbf{P}_e \cdot \nabla \right) \mathbf{E} \nonumber \\
&=& 2 \pi R_d^3 \kappa_1 \epsilon_0 K \nabla E^2,
\end{eqnarray}
where it is nice to use the simplifying shorthand $K = \frac{\kappa_2 - \kappa_1}{\kappa_2 + 2 \kappa_1}$, which is also known as the Clausius-Mossotti factor. In cases where $K <$ 0, or $K>$ 0 the particle will be repelled or attracted to regions of strong field respectively. In our experiment, taking the relative dielectric constants to be $\kappa_1 \approx$ 1 and $\kappa_2 \approx$ 80, the Clausius-Mossotti factor $K \approx$ 0.96. It is important to note that the equivalent dipole approximation critically requires an assumption of small physical scale of the particle relative to the lengthscale of nonuniformity of the field, which in this case we take to be the length of the charged superhydrophobic surface ($L =$ 25 mm $\gg a \approx$ 2.5 mm).

When the droplet is close to the dielectric surface, the free charge on the droplet will tend to induce polarization of the dielectric, perturbing the electric field. The polarization bound charge in the dielectric will be of the opposite sign of the free droplet charge and thus there will be a force of attraction. This so-called image force is a correction to the Colomb force due to the external electric field only, and can be found by the method of images \cite{david_j._griffiths_introduction_1999}. The image force $\mathbf{F}_I$, is given by
\begin{equation}
\mathbf{F}_I = \frac{k q^2}{16 \pi \epsilon_0} y^{-2} \hat{\mathbf{j}},
\label{image_force}
\end{equation}
where the factor $k$ is a function of the dielectric surface susceptibility $k = \frac{\chi_e}{\chi_e + 2}$, and $\hat{\mathbf{j}}$ is a unit vector normal to the dielectric surface.

By substituting Equations \ref{dep_force}, \ref{image_force} into Equation \ref{force_density} we have
\begin{eqnarray*}
 \mathbf{F}_E &=& q \mathbf{E} + \mathbf{F}_{DEP} + \mathbf{F}_I \\
 &=& q \mathbf{E} + \frac{k q^2}{16 \pi \epsilon_0 } y^{-2} \hat{\mathbf{j}} + 2 \pi R_d^3 \kappa_1 \epsilon_0 K \nabla E^2, 
\end{eqnarray*}
and the 1-D governing equation becomes
\begin{eqnarray} \label{gov_eqn_subs}
&m y'' = - \frac{1}{2} C_D \rho A {y'}^2 - q E - \frac{k q^2}{16 \pi \epsilon_0} y^{-2}- 2 \pi R_d^3 \kappa_1 \epsilon_0 K \nabla E^2,& \nonumber \\
&y(0) = R, \hspace{1 mm} y'(0) = U_0 .&
\end{eqnarray}

By comparing DEP and Coulombic terms in Equation \ref{gov_eqn_subs}, we note that a condition to neglect the DEP term is
\begin{eqnarray}
\frac{q}{ \kappa_2 \epsilon_0 K R_d^2 E_0} \gg 1 \nonumber
\end{eqnarray}
As this condition likely holds in our experiments we henceforth neglect the DEP force in our analysis. There is some physical intuition to support this conclusion as well. The dielectric displacement, $\mathbf{D} = \kappa \epsilon_0 \mathbf{E}$ of a water droplet in air is very high due to its large relative dielectric constant. This implies that the field strength within the droplet is about 2 orders of magnitude smaller than in the surrounding medium (which is essentially the same as a vacuum from a dielectric standpoint), thus it is not particularly inaccurate to model the dielectric volume of a droplet as a conductive shell (an equipotential), with zero field in its interior. As an aside, in treating the droplet as an ideal conductor we note that in our specific case the electrostatic force is not a body force \emph{per se} as the electric field is acting on charges on the surface of the conductor.

\section{The Electric Field}
If we consider the charged dielectric surface of our experiments to be a square sheet of charge lying in the $xz$-plane with width $L$, the symmetry of the problem happily lets us obtain the $y$-component of the electric field $\mathbf{E}$ by direct integration. In particular it is easy to constuct the electric field due to a finite plane of charge by superposition of the electric fields of a series of line charges. By symmetry the electric field points along the $y$-axis; for a point along the $y$-axis the position vector is $\mathbf{r} = \left( x^2 + y^2 \right)^{1/2} \hat{\mathbf{r}}$ to the center of a line charge in the $xz$-plane. The $y$-component of $d\mathbf{E}$ is found by $d E_r = d E_y \cos \theta = d E_y y/ r$, where $\theta$ is the angle made between the $y$-axis and the position vector $\mathbf{r}$. If the charge in a line element, $dx$ is $\sigma L dx$, where $\sigma$ is the average surface charge density, the electric field of a line charge is given by \cite{david_j._griffiths_introduction_1999}
\[d E_r = \frac{k \sigma L dx}{4 \pi \epsilon_0 r \sqrt{r^2 + L^2/4}}.
\]
The $y$-component of the electric field $E_y$, is then
\[ E_y = \frac{\sigma L y }{4 \pi \epsilon_0} \int^{L/2}_{-L/2} \frac{1}{(y^2 + x^2) \sqrt{y^2 + x^2 + L^2/4}} dx 
.\]
With some substitutions this can be integrated to obtain an expression for the electric field in terms of $y$, 
\begin{equation}
E_y = \frac{\sigma}{ \pi \epsilon_0} \tan^{-1} \left( \frac{L^2}{y \sqrt{2L^2 + 4y^2}}\right)
.\end{equation}
We note that this model of the electric field will be poor except in cases where $y \ll L, \hspace{1 mm} R_d \ll L$, which will be true for cases of large drops very close to the dielectric surface. For accurate models of the field in this case we likely would need to solve Laplace's equation for the electric potential $\varphi$
\[ - \nabla^2 \varphi = 0,\]
numerically using finite element methods.

By taking Taylor series expansions in large and small limits we can intuit a bit about the behavior of this field. In the limit $L \rightarrow \infty, \hspace{1mm} y \ll L$ the argument of the function tends towards infinity and
\[ \lim_{x\to\infty} \tan^{-1}(x) = \frac{\pi}{2}
,\]
and thus
\begin{equation}
E_y \approx \frac{\sigma}{4 \pi \epsilon_0} = E_0 \hspace{10mm} y \ll L
,\end{equation}
where $E_0$ is the characteristic electric field given by $E_0 = \frac{\sigma}{4 \pi \epsilon_0}$. This field is constant, and equivalent to the electric field due to an infinite plane of charge. In the limit of $y \gg L$, the argument of the arctangent function can be approximated by
\[ \frac{L^2}{2 y \left( 2 L^2 + 4 y^2\right)^{1/2}} = \frac{L^2}{4 y^2 \left( 1 + L^2/2y^2 \right)^{1/2}} \approx \frac{L^2}{4 y^2}
.\]
For small $x$, $\tan^{-1}(x) \sim x$ and we thus find the familiar electric field due to a point charge
\begin{equation}
E_y \approx L^2 E_0 y^{-2}  \hspace{10mm} y \gg L
.\end{equation}
Both of these regimes can be clearly seen in the plot of $E_y$ shown in Figure \ref{fig:E0}.
\begin{figure}[htb]
    \centering
    \input{../figures/E0.pgf}
    \caption{A log-log plot of the magnitude of the non-dimensional electric field, $E_y$.\label{fig:E0}}
\end{figure}
\newpage

\section{Scaling}
The equation of motion is non-linear, non-homogeneous and is best solved numerically, but nevertheless we are curious if we can obtain approximate solutions to the equation analytically using perturbation methods. This is aided by non-dimensionalizing the governing equations, and seeing if any dimensionless groups exist, and whether any are particularly small or large, and whether any fortuitous opportunities for simplification appear. Introducing the scaled variables
\begin{equation}
 \bar{t} = \frac{t}{t_c}, \hspace{10 mm} \bar{y} = \frac{y}{y_c}, \end{equation}
where $y_c$ and $t_c$ are characteristic length and time scales respectively, and using the coordinate transformation $y(0) - R = 0$, the governing equation becomes
\begin{eqnarray}
& \bar{y}'' = - \frac{1}{2} \frac{C_D \rho A y_c}{m} \bar{y}'^2
- \frac{q E_0 t_c^2}{m y_c} \bar{E} ( \bar{y} ) 
- \frac{k q^2 t_c^2}{16 \pi \epsilon_0 R^2 m y_c} \left( \frac{y_c}{R} \bar{y} + 1 \right)^{-2}, & \nonumber \\
& \bar{y}(0) = 0, \hspace{1 mm} \bar{y}'(0) = \frac{U_0 t_c}{y_c} .& \label{scaled_eqn}
\end{eqnarray}
We note the existence of several dimensionless groups
\[ \mathbf{\Pi}_1 = \frac{C_D \rho A y_c}{2 m}, \hspace{5 mm}
\mathbf{\Pi}_2 = \frac{q E_0 t_c^2}{m y_c}, \hspace{5 mm}
\mathbf{\Pi}_3 = \frac{k q^2 t_c^2}{16 \pi \epsilon_0 R^2 m y_c}, \hspace{5 mm}
\mathbf{\Pi}_4 = \frac{y_c}{R}, \hspace{5 mm}
\mathbf{\Pi}_5 = \frac{U_0 t_c}{y_c}.\]

\subsection{Inertial Electro-Image Limit}
In the limit of small $y$ and $t$ we expect inertia to scale as Coulombic and image force. In this limit we can approximate the electric field as the constant, $E_0$. One possible characteristic length scale is $y_c \sim R_d$, however this ultimately is a poor choice. With $y_c \sim U_0 t_c$ and picking $t_c$ such that Coulombic force is $\mathcal{O}(1)$, the intrinsic scales become
\[ t_c \sim \frac{m U_0}{q E_0}, \hspace{5 mm}
y_c \sim \frac{m U_0^2}{q E_0} .
\]
With these scales the governing equation then becomes
\begin{eqnarray}
& \bar{y}'' = -1 - \mathbb{I}\mbox{m} \left( \mathbb{E}\mbox{u}\bar{y} + 1 \right)^{-2} ,& \nonumber \\
& \bar{y}(0) = 0, \hspace{1 mm} \bar{y}'(0) = 1 .& \label{img_limit}
\end{eqnarray} 
with 
\[ \mathbb{I}\mbox{m} \equiv \frac{k q}{16 \pi \epsilon_0 R_d^2 E_0} = \mathbf{\Pi}_3, \hspace{5 mm}
\mathbb{E}\mbox{u} \equiv \frac{m U_0^2}{q E_0 R_d} = \mathbf{\Pi}_4 ,
\]
where $\mathbb{I}\mbox{m}$ is the Image number, and denotes the ratio of image forces to the Coulombic force of the unperturbed field, and where $\mathbb{E}\mbox{u}$ is the electrostatic Euler number, and is a ratio of inertia to electrostatic force. With these dimensionless groups the intrinsic scales become
\[ t_c = \mathbb{E}\mbox{u} \frac{R_d}{U_0}, \hspace{5 mm}
y_c = \mathbb{E}\mbox{u} R_d.
\]

\subsection{Inertial Electro-Viscous Limit}
In the limit of large $y$ and $t$ we expect droplet inertia to scale as Coulombic force and drag. In this limit we approximate the electric field as $E \approx y_c^2 E_0 y^{-2}$. In this case there are several (obvious) possible choices of scales:
\begin{enumerate}
\item $y_c \sim U_0 t_c$, and make Coulomb force $\mathcal{O}(1)$.
\item $y_c \sim L$, $t_c \sim \frac{L}{U_0}$ (however, this makes Equation \ref{scaled_eqn} singular).
\item $y_c \sim L$, $t_c \sim \left( \frac{L m}{q E_0} \right)^{1/2}$.
\item $y_c \sim L$, and make Coulomb force $\mathcal{O}(1)$.
\end{enumerate}
%In Case 4, the characterisitc time is $t_c \sim \left( \frac{4 \pi R_d^2}{q E_0 L} \right)^2 $ and the non-dimensional governing equation is given by
%\begin{eqnarray}
%&\bar{y}'' = - \frac{C_D \rho A L}{2 m} \bar{y}'^2 - \left( \frac{L}{R_d} \bar{y} + 1\right)^{-2} ,& \nonumber \\
%& \bar{y}(0) = \frac{R_d}{L}, \hspace{5 mm} \bar{y}'(0) = \left( \frac{4 \pi U_0^2 R_d^2}{q E_0 L^3}\right)^{1/2} = \frac{R_d}{L} \sqrt{\mathbb{E}\mbox{u}_+}.& \nonumber
%\end{eqnarray}
%where $\mathbb{E}\mbox{u}_+ = \frac{4 \pi m U_0^2}{q E_0 L}$ is a long time scaled electrostatic Euler number.

We prefer the approach with the greatest physical simplicity, fewest Pi terms, and that has homogeneous initial conditions. We choose Case 1, where the intrinsic scales are given by
\[ t_c \sim \frac{R_d^2}{L^2} \frac{4 \pi m U_0}{q E_0}, \hspace{5mm} y_c \sim \frac{R_d^2}{L^2} \frac{4 \pi m U_0^2}{q E_0}.
\]
With this scaling the non-dimensional governing equation is 
\begin{eqnarray}
&\bar{y}'' = - \mathbb{D}\mbox{g} \mathbb{E}\mbox{u}_+ \bar{y}'^2 - \left( \mathbb{E}\mbox{u}_+ \bar{y} + 1 \right)^{-2}, & \nonumber \\
& \bar{y}(0) = 0, \hspace{1 mm} \bar{y}'(0) = 1 & \label{drag_limit}
\end{eqnarray}
where we call $\mathbb{D}\mbox{g}$ the drag number, $\mathbb{D}\mbox{g} \equiv \frac{C_D \rho_a}{\rho_l} = \mathbf{\Pi}_1 {\mathbb{E}\mbox{u}}_+^{-1}$ and $\mathbb{E}\mbox{u}_+ = 4 \pi \frac{R_d^2}{L^2} \mathbb{E}\mbox{u}$.

\section{Asymptotic Estimates}
\subsection{Inertial Electro-Image Limit}
The alternate scalings of the equation of motion given by Equations \ref{img_limit}, and \ref{drag_limit} are weakly non-linear differential equations in the sense that they reduce to linear equations as the parameter $\mathbb{E}\mbox{u} \rightarrow 0$. If we take $\mathbb{E}\mbox{u}$ to be a small parameter $\epsilon$, we can find an asymptotic approximation to the solution of the non-linear equation by means of a regular perturbation. In this case we use the naive expansion
\[ \bar{y}(\bar{t}) \sim \bar{y}_0(\bar{t}) + \epsilon \bar{y}_1(\bar{t}) + \epsilon^2 \bar{y}_2(\bar{t}) \ldots \epsilon^n\bar{y}_n(\bar{t})  
.\]

By substitution of the expansion (and its derivatives) into the differential equation, and equating terms by order, and using the notation $\alpha = \mathbb{I}\mbox{m}$ (this being the equation scaled in the small-times limit), we first find the $\mathcal{O}(1)$, unperturbed, solution to the equation of motion to be
\[{\bar{y}_{0}}{\left (\bar{t} \right )} = \bar{t} + \frac{\bar{t}^{2}}{2} \left(-1 - \alpha\right). \]

Looking at this solution it is evident that if we let $\alpha=0$, the solution is the classical kinematic equation for projectile motion without drag under constant gravity, $g_0$. Continuing on with this procedure we find, (after some tedious computations, documented in in the project repository for this thesis \cite{schmidt_droplet_electro-bounce:_2017}) the higher order composite solutions to be
\begin{eqnarray*}
&\bar{y}(\bar{t}) = \bar{t} + \frac{\bar{t}^{2}}{2} \left(-1 - \alpha\right) + \epsilon \left(\frac{\alpha \bar{t}^{3}}{3} + \frac{\alpha \bar{t}^{4}}{12} \left(-1 - \alpha\right)\right)& \\
&+ \epsilon^{2} \left(- \frac{\alpha \bar{t}^{4}}{4} + \frac{\alpha \bar{t}^{5}}{60} \left(9 + 11 \alpha\right) + \frac{\alpha \bar{t}^{6}}{360} \left(-9 - 20 \alpha - 11 \alpha^{2}\right)\right) + \mathcal{O}(\epsilon^3)&.
\end{eqnarray*}

In fact we, for somewhat arbitrary reasons, computed an $\mathcal{O}(\epsilon^5)$ accurate solution, but it is far to ugly to reprint here in its entirety. However, we plot these approximate short-time scaled solutions with varying values of the Image number, $\mathbb{I}\mbox{m} = \alpha$ in Figure \ref{fig:short_times}.
%\newpage
\begin{figure}[htb]
    \centering
    \resizebox{1\textwidth}{!}{\input{../figures/short_times.pgf}}
    \caption{Non-dimensional droplet trajectories for various values of $\mathbb{E}\mbox{u}=\epsilon$, $\mathbb{I}\mbox{m}=\alpha$. The trajectory reduces to the classical $\mathcal{O}(1)$ solution for small values of $\alpha$. It should be noted that despite what is implied by these plots $\alpha$ is not necessarily completely independent of $\epsilon$, as they share $q$, and $E_0$ as common factors, $U_0 \sim R_d^2$, and $m \sim R_d^3$.}
    \label{fig:short_times}
\end{figure}
These plots show a trend of decreasing time-of-flight (the time for the droplet to return to the origin, or complete a single ``bounce''), and height at apoapse with increasing values of the Image number $\alpha$. When $\alpha = 1$ the time of flight is exactly half of characteristic time scale in this regime. In the limit of small $\epsilon$ the trajectories collapse to the $\mathcal{O}(1)$ solution regardless of the Image number. In principle there is some coupling between $\mathbb{E}\mbox{u}$ and $\mathbb{I}\mbox{m}$; notably this relationship does not depend on the electric field $E_0$ but on a charge to mass ratio. The effect of contact line hysteresis on the initial jump velocity $U_0$ will also tend to independently decohere the natural covariance between these parameters.

\subsection{Inertial Electro-Viscous Limit}
By similar arguments we find an asymptotic estimate of the trajectory in the long-times scaled regime. With $\epsilon = {\mathbb{E}\mbox{u}}_+$, where $\epsilon$ again is a small parameter, and $\beta = \mathbb{D}\mbox{g}$, the approximate solution is 
\begin{eqnarray*}
&\bar{y}(\bar{t}) = \bar{t} - \frac{\bar{t}^{2}}{2} + \epsilon \left(\frac{\bar{t}^{3}}{3} \left(1 + \beta\right) + \frac{\bar{t}^{4}}{12} \left(-1 - \beta\right) - \frac{\beta \bar{t}^{2}}{2}\right)&  \\
&+ \epsilon^{2} \left(\frac{\bar{t}^{4}}{12} \left(-3 - 3 \beta - 4 \beta^{2}\right) + \frac{\bar{t}^{5}}{60} \left(11 + 10 \beta + 8 \beta^{2}\right)+ \frac{\bar{t}^{6}}{360} \left(-11 - 10 \beta - 8 \beta^{2}\right) + \frac{\beta^{2} \bar{t}^{3}}{3}\right)& \\
 &+ \mathcal{O}(\epsilon^3)&.
\end{eqnarray*}
This trajectory given by this solution is shown in Figure \ref{fig:long_times}. If we assume a constant scale for the drag coefficient, $C_d \approx 0.5$, then  the Drag number $\beta = \mathbb{D}\mbox{g}$ is approximately a constant $\beta \approx 6 \times 10^{-4}$ in all of our experiments.
\begin{figure}[htb]
    \centering
    \input{../figures/long_times.pgf}
    \caption{Non-dimensional droplet trajectories for various values of $\mathbb{E}\mbox{u}=\epsilon$.}
     \label{fig:long_times}
\end{figure}
Again, the trajectory seemingly reduces to the classical $\mathcal{O}(1)$ solution for small values of of $\epsilon$. We also note that the effect of drag is very slight, appearing only as a slight correction to the higher order terms; the apoapse is very nearly equal to half the characteristic length scale. In practical terms this linearizing effect of small $\beta$ may disappear if the fluid density is much less than that of water, as in our experiments.

By again applying a regular perturbation to the asymptotic solution with the expansion
\[ \bar{t} \sim \bar{t}_0 + \epsilon \bar{t}_1 + \epsilon^2 \bar{t}_2 \ldots \epsilon^n\bar{t}_n  
,\]
and solving for the roots (that is, the times when $\bar{y} = 0$), we find an asymptotic estimate for the time-of-flight, $t_f$. The $\mathcal{O}(\epsilon^2)$ accurate time-of-flight estimate is given by
\[t_f = 2 + \epsilon \left(\frac{4}{3} - \frac{2 \beta}{3}\right) + \epsilon^{2} \left(\frac{4}{5} - \frac{4 \beta}{3} + \frac{2 \beta^{2}}{5}\right) + \mathcal{O}(\epsilon^3).\]
Substituting the experimental value of $\beta$ we find the time-of-flight estimate for water droplets in air to be
\begin{equation} \label{time_of_flight}
t_f = 2 + 1.333 \epsilon + 0.799 \epsilon^{2} + \mathcal{O}(\epsilon^3) 
\end{equation} 
In Figure \ref{fig:drag} we look at the effect of increasing values of ${\mathbb{E}\mbox{u}}_+$ on time-of-flight.
\begin{figure}[htb]
    \centering
    \input{../figures/drag.pgf}
    \caption{$\mathcal{O}(\epsilon^3)$ asymptotic estimate of droplet time-of-flight as a function of $\epsilon = {\mathbb{E}\mbox{u}}_+$.}
    \label{fig:drag}
\end{figure}
We see that as $\epsilon$ grows to be no longer small, the time-of-flight grows rapidly, but this behavior appears to have an asymptote at a certain critical velocity as $\mathcal{O}({\mathbb{E}\mbox{u}}_+) \rightarrow \mathcal{O}(1)$; this is an electrostatic escape velocity, $U_e$. We can find the escape velocity by solving a modified version of the equation of motion,
\[ m u' = - \frac{q E_0}{y^2}, \]
where $u = \frac{d y}{d t}$ is the droplet velocity. Integrating between the respective limits,
\[m \int^{u(y)}_{U_0} u du = -q E_0 \int^y_{R_d} \frac{dy}{y^2} ,\]
which has the solution
\[ u(y) = \pm U_0 \left[1 + \frac{2q E_0}{m U_0^2} \left( \frac{1}{y} - \frac{1}{R_d} \right) \right]^{1/2}.
\]
This equation has an asymptotic velocity, $U_{\infty}$ at $y = \infty$ which is real if 
\[ U_0 \geq  U_e = \sqrt{\frac{2 q E_0}{m R_d}},
\]
where $U_e$ is the escape velocity and $U_{\infty} = \sqrt{U_0^2 - U_e^2}$. The condition for the droplets to escape the electric field is then given by
\begin{equation}\label{escape}
{\mathbb{E}\mbox{u}}_+ > 1/8 \pi.
\end{equation}
Referring again to Figure \ref{fig:drag}, we suspect that there is perhaps a better choice of scaling available, as the time-of-flight estimate is not asymptotic at ${\mathbb{E}\mbox{u}}_+ = 1/8 \pi$.

If the droplet escapes the electric field it will have a residual velocity $U_{\infty}$, and will be in a regime of pure inertia $\sim$ drag. The velocity will then decay as
\[
\bar{u}(\bar{t}) = \frac{1}{\bar{t} + 1},
\]
with a characteristic time $t_c \sim \frac{2 m}{C_D \rho A U_{\infty}}$, which is the halving time of the velocity.

\chapter{Methodology}
\section{Overview}
Mainly we are concerned about what parameters are important in electrostatic transport of relatively large (e.g. millimetric) droplets in low-gravity, and what the values of the respective dimensionless groups, namely $\mathbb{I}\mbox{m}$, $\mathbb{E}\mbox{u}$ and ${\mathbb{E}\mbox{u}}_+$ might be. To find typical vales of these parameters we used the following approach:
\begin{enumerate}
\item We observed spontaneous droplet jumps on charged dielectric super-hydrophobic surfaces under low-gravity conditions in a $2.1$ s drop tower, while varying the independent variables $V_d$, $\sigma$. However, this raises an interesting challenge; it is impractical to directly measure all of the key physical quantities that appear in the dimensionless groups at once in a drop tower experiment. In particular, determination of net droplet free electric charge $q$, is difficult (as high-input resistance electrometers, being notoriously fickle instruments, are not well suited to sudden 15-g decelerations). Schematic representations of the droplet jump, and of the droplet in the Cassie-Baxter 1-g initial state is shown in Figures \ref{fig:apparatus0} and \ref{fig:schematic}.
\item Using high-speed video and image analysis software we captured the trajectories of the droplets. 
\item We solved the inverse problem to find the key parameters by maximizing a statistical likelihood function between an observed trajectory and the trajectory predicted by a dynamical model given that certain set parameters. The best fit parameters obtained by direct-search optimization are those corresponding to the maximum likelihood experimental values. The optimization is constrained by the measurement precision of directly measured independent, and dependent variables.
\end{enumerate}
\begin{figure}[ht]
 \centering
 \includegraphics[width=0.75\textwidth]{../figures/schematic.pdf}
 \caption{A schematic representation of the droplet initial condition, resting on the superhydrophobic surface in the Cassie-Baxter state just prior to the drop tower experiment. The variables $q$, $\sigma$, and $V_d$ are the droplet net free charge, dielectric surface charge density, and droplet volume respectively.\label{fig:schematic}}
\end{figure}
\begin{figure}[ht]
 \centering
 \includegraphics[width=0.75\textwidth]{../figures/apparatus0.pdf}
 \caption{A schematic representation of a droplet electro-bounce experiment with labeled characteristic time and length scales, \hl{$t_c$, $y_c$} shown. Also shown are the dimensions of the superhydrophobic electret substrate.\label{fig:apparatus0}}
\end{figure}

\section{Experimental Methods}
The DDT uses a dual capsule design, inspired by the 2.2 s facility at NASA Glenn Research Center, which decouples drag acceleration felt by the external drag shield from the experiment. The experiment then experiences approximately $1 \times 10^{-6}$g of high quality free-fall for the 2.1s required for the rig/drag shield assembly to plummet to the bottom of drop tower 6 floors below. Single droplets of distilled water, in a range of volumes ($0.01 \leq R_d \leq 0.5$ mL), were very carefully deposited on the charged superhydrophobic surface using an grounded glass syringe with $\pm $1 $\mu$L accuracy, and then dropped in the drop tower. Red dye was added to improve thresholding accuracy in trajectory digitization. Droplet trajectories were recorded using a \emph{Panasonic} HC-WX970 Camera, at 120 fps and and 1/3000s shutter speed. In a few cases where higher frame rates were needed a \emph{Nikon} 1 J1 camera with a 30mm telephoto lens was used, shooting at 400 fps. The experimental test cell was illuminated with a 6000K LED strip, with a thin semi-opaque plastic film covering to make the light diffuse.

Rather than haphazardly contact charge the surfaces with streams of water, as likely happened by accident in the experiments which inspired this inquiry, we strive for a more controlled, uniform surface charge distribution. Following from this desire, superhydrophobic electrets were prepared, with surface potentials $\varphi_s = 0.7$-$4.0$ kV. According to a review by Sessler \cite{_electrets_????}, an electret is a dielectric material with ``quasi-permanent'' electric charge in the sense that the characteristic decay period of the electret is much greater than a practical experiment time scale. Electret charge may be `true' charge in the form of surface or space charges, or polarization charges (such as bound charges). If the electret is not screened by a conductor then it produces an external electric field if the polarization and real charges do not uniformly compate each other throughout the volume of the electret. For this reason electrets are thought of as electrostatic analogs to permanent magnets (and the name \emph{electret} itself is a portmantau to that effect conjured by Heaviside in 1892 \cite{heaviside_electrical_2011}). Typical commerical electrets are Teflon type (PTFE) polymer films on the order of 10-50 $\mu$m thick with the charge being primarily real surface charge. Electrets have a plethora of applications, but most germanely they have been used in Electro-Wetting On Dielectric (EWOD) devices for low-voltage manipulation of small droplets \cite{wu_low-voltage_2010}. Real charge electrets can be produced by contact electrification, injection or deposition) of charge carriers by discharge or electron beam, ionizing radiation, or by frictional triboelectrification. Dipolar electrets by contrast are produced by a combination of polarization at elevated temperatures in a strong external electric field, followed by an annealing process. Effective surface charge densities are limited to the material dielectric strengths due to internal dielectric breakdown phenomenon (this typically occurs before external breakdown or Paschen breakdown).

We use an isothermal electret formation process using a variation of the widely applied corona-charging technique. The typical corona-charging technique uses strong inhomogenous DC electric fields to produce discharge in air at ambient conditions; the dielectric substrate is atop a grounded electrode, and there is a screening potential electrode intermediately positioned to control the surface potential (the the surface potential of the dielectric will tend to saturate at this grid potential if the material is not space-charge current limited). The corona field is usually produced by pin-shaped electrode. In air the most common charge carriers thus produced are $\mbox{CO}_3^-$ ions. This approach is known to generally produce samples with fairly uniform surface charge densities. Some work by van Turnhout in 1975 showed, using Thermally Stimulated Current (TCS) measurements, that in 4.8 mm thick polymethyl methacrylate (PMMA) polarization of the dielectric is non-uniform, due to real space-charge mostly ($\sim$90\%) residing in a thin (0.1-0.2 mm) layer near the free-surface of the sample \cite{van_turnhout_thermally_1975}. In this work we use a balanced AC corona ion source (Ptec IN5120), to direct a net neutral stream of ions towards the dielectric target, which we polarize by an electrode with a $2$ kV$+$ (absolute reference) DC-DC converter. The ion stream compensates the surface and space bound charges arising due to the polarization of the dielectric. When the DC-DC converter is switched to ground, the deposited negative ions remain on the surface.

The electret is lamina of 3-4 0.4 mm thick corona charged PMMA sheets. The electric field strength scales with the number of dielectric lamina as has also been shown in work on electret based vibrational energy harvesters \cite{wada_stacking_2012} and in water desalinization \cite{ni_desalination_2005}.

The final, superhydropobic layer, is produced by laser etching PMMA, and depositing a thin layer of PTFE on the resulting roughness topology to increase the Young's angle. The surface charge density can be modulated during the experiment using the high-voltage DC-DC converter, which can re-polarize the dielectric substrate by means of an embedded electrode, and the resulting bound charge partially or fully neutralizes the electric field due to the surface ions deposited by corona charging of the electret. The high-voltage system is armed manually before the drop and is automatically safed by a high-voltage power switching relay, which switches the load across a 100 k$\Omega$ resistor when triggered by the resumption of 1-g conditions. The safing is set by an accelerometer pin-interrupt triggered microcontroller command. The rig with a mounted experiment is shown in Figure \ref{fig:rig}. 
\begin{figure}
    \centering
    \def\svgwidth{\columnwidth}
    \input{../figures/rig.pdf_tex}
    \caption{The droplet electro-bounce experiment hardware mounted on a drop tower rig.\label{fig:rig}}
\end{figure}

Contact angles of distilled water on the electret $\sim 150^{\circ}$. The hysteresis of the contact angle (the difference between the advancing and receding contact angles) is estimated from the roll-off angle using the method of Furmidge, 1962 \cite{furmidge_studies_1962}, and is found to be approximately $20^{\circ}$ when the surface is uncharged. The innate Young's angle hydrophobicity of the PTFE layer is enhanced by the underlying roughness length scales of the surface. We use a laser-etched pillared geometry with pillar heights $\sim 775$ $\mu$m, widths $\sim 70$ $\mu$m and pitch $\sim 100$ $\mu$m. An SEM image of the pillar geometry is shown in Figure \ref{fig:SEM}.
\begin{figure}
    \centering
    \input{../figures/hysteresis.pgf}
       \caption{Hysteresis of the contact line plotted as a function of static contact angle and roll-off angle for $1$ mL droplets.\label{fig:hysteresis}}
\end{figure}

\begin{figure}[ht]
 \centering
 \includegraphics[width=0.75\textwidth]{../figures/SEM.pdf}
 \caption{SEM image of the superhydrophobic surface.\label{fig:SEM}}
\end{figure}

Surface potentials $\varphi_s$, were measured on the superhydrophobic surface using a \emph{Simco-Ion} FMX-004 electrostatic fieldmeter and the method for determination of surface charge density for low conductivity polymers described in Davies, 1967 \cite{davies_examination_1967}. This measurement was done with the superhydrophobic surfaces connected by a conductive ground plane by conductive tape, far away from the presence of other conductors. An ideal approach to determining surface charge on a dielectric surface is to screen perturbing effects of external electric fields. This is partly accomplished by grounding the fieldmeter, and by placing the dielectric sample on a grounded conductive plate backing. In this case the surface charge density is determined from
\[ \sigma = \frac{\varphi_s \kappa}{l}, \]
where $l$ and $\kappa$ are the thickness of the dielectric surface, and the absolute permitivity respectively. The measured surface voltage is a function of position away from the charged dielectric. In most cases this function is relatively constant at a distance about 1-2 cm away from the surface (there is some measurement error in surface voltage due to small mispositioning of the electrostatic fieldmeter, say by $\pm$1 mm). The relative dielectric constant of the PMMA sheet was measured by using a 65$\times$65 mm polished aluminum parallel plate capacitor with $C = \epsilon \epsilon_0 \frac{A}{l}$ where $C$ is the capacitance, and $A$ is the sheet area. Measuring the capacitance with 3 sample thicknesses using a GenRad 1657 RLC Digibridge, we found the relative permitivity to be $\epsilon = 3.5 \pm 0.4$.

A further consideration is the possibility of the change in total charge during a typical experimental timescale. If we consider the drop rig to be a ground (which seems reasonable given that the rig is isolated from true ground, but is at some reference voltage with respect to the surface charges on the dielectric, it also has an abundance of free charge carriers, that is, if it is conductive), then there will be both bulk and surface decay of the charge on the dielectric. The evolution of the charge can in some cases be approximated by
\[ \sigma = \sigma_0 e^{\frac{-t}{\epsilon \rho}}, \]
where $\sigma_0$ is the initial surface charge density, and $\rho$ is the bulk resistivity (which can also be reframed in terms of conductivity by $\rho = 1/\gamma$, where $\gamma$ is the conductivity). For an example case of a surface with an initial surface charge density $\sigma = 2.4 \times (10^{-6})$ $C/m^2$, relative permittivity $\epsilon = 3.5$ and bulk resistivity $\rho = 1.6 \times (10^{16})$ $\Omega$cm such as with the case of 2.8 mm PMMA sheet, then the time constant $\tau = \kappa \rho$ is approximately 5000 s, which is a great deal longer than the typical time period for of a drop tower experiment. We measured the charge decay with a calibrated probe at periodic intervals. There are several charge decay mechanisms: internal ones, such as Ohmic resistence, and external ones such as compensation by envonmental ionic species. The relative magnitudes of these charge transport mechanisms, and therfore the stability of the electret varies drastically depending on its initial surface potential, material properties, environment, and charging method. In the case of unshielded electrets compensation by atmospheric ions is significant \cite{perlman_electrets_1973}. Because environmental convection will tend to  maintain a gradient of these ions, sealing an electret in a container from the atmosphere will effectively halt this decay mechanism. Atmospheric humidity and water droplet condensation also significantly increase charge decay (presumably by reducing the surface resistence) \cite{haenen_characteristic_1975}. Examples of this decay can be seen in Figure \ref{fig:charge_decay} for differing numbers of dielectric lamina used in this experiment. In looking at the trends in charge decay for our electrets we notice firstly, that the decay does not appear to be exponential, as in the model described above. Secondly, we plainly see a cross-over effect in the decay of the surface potential in our electret samples, whereby the samples charged to higher initial surface potentials decayed faster and reached the lower overall final potentials. This is a well known effect in polyethylenes charged by corona \cite{ferreira_corona_1992}.
\begin{figure}[htb!]
    \centering
    {\input{../figures/charge_decay.pgf}}
       \caption{Charge decay in the dielectric laminates for differing numbers of layers.\label{fig:charge_decay}}
\end{figure}
\newpage

\section{Data Munging}
Digitization of droplet trajectories requires several steps of post-processing. Video is first decomposed into a sequence of still images. Trajectories are captured using the particle tracking module in \emph{Fiji} \cite{schindelin_fiji:_2012}, a derivative of the popular \emph{ImageJ} \cite{schneider_nih_2012} package for scientific image analysis. The series is stabilized to remove the effect of drop transients from the kinetmatic data \cite{li_image_2008}. The series of still images is cropped, and the background (that is, the low-entropy pixels) of the series is removed using a built-in ``rolling ball'' algorithm. Each still is then split into its constituent RGB maps. In this case the green channel images contained the most information, so these were then globally thresholded using the Triangle algorithm to recover a map of the pixels corresponding to the droplet's approximate position in the original still. Ellipses are fitted to the pixel map stepping through the time series to determine the positions of the center of mass, and the semi-major and minor axes of the droplets during the drop. Finally, a perspective correction is applied to the center-of-mass positions.

The code used in this work, as well as the raw data, and the make files for this thesis are archived on the open-source project portal Github \cite{schmidt_droplet_electro-bounce:_2017}.

\section{Parameter Estimation}
Using various scaling arguments we have gleaned from our simple model a series of non-dimensional numbers characteristic of droplet bounce apoapses and times of flight, but these dimensionless groups depend on a set of physical parameters. Unfortunately not all of these parameters are physically practical to accurately measure by experiment. Droplet free charge $q$, in particular, could in principle be directly measured by collecting the charged drops in a faraday cup under low-g and measuring the change in capacitance of the cup using a very high input-resistance electrometer, but this is a problematic experiment to set up in a drop tower from a practical standpoint. The other state variables we can directly measure by experiment with varying levels of accuracy. To measure the charge, $q$, we instead turn to parameter estimation techniques. Our work flow to identify this parameter is as follows:
\begin{enumerate}
\item Experimentally vary $V_d$, $\sigma$ and capture droplet trajectories using a high-speed camera.
\item Digitize droplet trajectories by using automatic tracking of ellipse-fitted centers of mass on the thresholded video.
\item Slice droplet trajectories by their bounce minima, and apply a smoothing filter.
\item Extract the droplet charge (and other experimental parameters) by maximizing the log-likelihood of the data given the dynamical model and parameters, by varying the parameter vector using a direct search optimization. 
\end{enumerate}

Mathematically we state that we find the parameters $\mathbf{x}$ that solve the inverse problem $G(\mathbf{x}) = \mathbf{d}$, using a direct search method (\emph{Nelder-Mead}). 
\[
\mbox{min} \hspace{2 mm} \chi^2 = \mbox{min} \hspace{2 mm} \sum^n_{i=1} \frac{\left({y_d(t)}_i - y_G(t, \mathbf{x})_i \right)^2}{y_G(t, \mathbf{x})_i}
\]
\begin{eqnarray*} \mbox{} \hspace{2 mm} \begin{split} \mathbf{x} = \left\{ \begin{array}{ll}      & q\\
		  &	V_d\\
          & \sigma 
          \end{array} \right. 
          \end{split} \hspace{2 mm} \mbox{subject to constraints} \hspace{2 mm} \begin{split}
          g = \left\{ \begin{array}{ll}
           V_d &\pm \hspace{2 mm} u_{exp}\\
      	   \sigma &\pm  \hspace{2 mm} u_{exp}\\
      	   y_0 &\pm \hspace{2 mm} u_{exp}\\
      	   t_0 &\pm \hspace{2 mm} u_{exp}\\
          \end{array} \right. 
          \end{split}
\end{eqnarray*}
where $y_G(t, \mathbf{x})$ is a numerical solution of the equation of motion
\[
m y'' = \frac{1}{2} \rho C_D A_d {y'}^2 + q E(y) + K q^2 y^{-2} \]

\subsection{Inverse Problems}
Suppose we have a model $G(\mathbf{x})$, with a vector of parameters $\mathbf{x}$, and set of (noiseless) observations $\mathbf{d}$, then we naturally expect there to exist a relationship 
\[G(\mathbf{x}) = \mathbf{d} ,\]
where the operator $G$ might be an ODE. Suppose the model $G(\mathbf{x})$ is the ODE
\[ y'(t) = f(t, \mathbf{y}; \mathbf{x}), \hspace{1 mm}  \mathbf{y} \in \mathbb{R}^n, \]
and a collection of $n$ measurements of experimental data
\[ \mathbf{d} = \left( t_1, \mathbf{y_1} \right), 
\left( t_2, \mathbf{y_2} \right), ... ,
\left( t_k, \mathbf{y_k} \right).\]
The process of fitting a function, defined by a collection of parameters, to a data set is called the discrete inverse, or parameter estimation problem (as opposed to the \emph{forward problem} to find $\mathbf{d}$ given $\mathbf{x}$ and $G(\mathbf{x})$). This is a familiar procedure when the determination of model parameters is done using linear or polynomial regression. However there are approaches even to fitting an arbitrary function to a noisy and sparse dataset. In this work we use the conventional Maximum Likelihood Estimate (MLE) method to identify the model parameters.

Using MLE we don't ask the question: ``what is the probability that my set of model parameters is correct?''(because the probability is very nearly zero!), but rather ``given my set of model parameters, what is the probability that this data set occurred (what is the likelihood of the parameters given the data)?''. Bayes' Theorem holds that
\[\mbox{prob}(X|D, I) = \frac{\mbox{prob}(D|X,I) \times \mbox{prob}(X|I)}{\mbox{prob}(D|I)}\]
where $D$ are our observations (dataset), $X$ is our vector of parameters, and $I$ is general background information about the problem including our mathematical model (for instance the ODE above), and 
\[\begin{array}{lll}
& \centering \mbox{prob}(X|D, I) & \mbox{posterior probability density function},\\
& \centering \mbox{prob}(D|X, I) & \mbox{likelihood function},\\
& \centering \mbox{prob}(X|I) &  \mbox{prior probability density function},\\
& \centering \mbox{prob}(D|I) &  \mbox{evidence}.
\end{array}
\]
The posterior probability density function (PDF) $\mbox{prob}(X|D, I)$, is ultimately what we want to estimate, the prior PDF $\mbox{prob}(X|I)$, reflects our knowledge of the system, and the evidence $\mbox{prob}(D|I)$, is the likelihood of the data based on our knowledge. We also note that since it only makes sense to compare the conditional PDF's for the same data, we can ignore the denominator (that is, the evidence). We further note that the prior $\mbox{prob}(X|I)$, is fixed before our observations and so can be
treated as invariant to our problem. We can therefore infer that $\mbox{prob}(X|D, I) \propto \mbox{prob}(D|X, I)$. The MLE for the the model parameters $\mathbf{x_0}$, then is given by the maximum of the posterior PDF, which is equivalent to the solution of the ODE given the the parameters $\mathbf{x}$, that produces the highest probability of the observed data. Since the likelihood $\mathcal{L}(\mathbf{x}) = \prod_i^n \mathcal{P}_i$, and the probability $\mathcal{P}$, of any single observation is less than one, then the total likelihood which is the product of a large number of probabilities tends to be vanishingly small. The more well behaved log-likelihood is given by
\[\mathcal{M} = \ln(\mathcal{L}) = \ln(\mbox{prob}(D|X, I)) = \mbox{const} - \frac{\chi^2}{2}\]
where 
\[
\chi^2 = \sum^n_{i=1} \frac{\left({y_d}_i - {y_G}_i \right)^2}{{\sigma_d}_i^2}
\]
is the $\chi^2$ goodness-of-fit, $y_d = y_d(t)$ is a observation of droplet position at a point in time, and $y_G =  y_G(t, \mathbf{x})$ is the droplet position predicted by the solution to the equation of motion at time $t$, and $\sigma$ is the standard error of the position measurement. If the number of data points $n$, is small was can use the Poisson error $\sigma_d^2 = {y_G}$. The optimal parameter set is the one with the highest probability of observing the data (the maximum of the posterior PDF) and can be determined by maximizing the log-likelihood $\mathcal{M}$ (or minimizing $\chi^2$) of the data $\mathbf{d}$ with respect to the parameter set $\mathbf{x}$. Thus parameter estimation is a variety of optimization problem.

\subsection{Smoothing}
All optimization methods, whether explicitly or implicitly, follow gradients towards an optimum. In a parameter estimation problem, if we approximate these gradients by finite differences, then the noise manifests itself as amplification of the roughness in the hyper-response surface. Gradient based optimizers do poorly in these situations because they tend to converge to local minima. While so called gradient free algorithms offer an improvement in this regard, speed of convergence and the quality of the MLE is improved by smoothing the objective function. This is equivalent to smoothing the underlying dataset.

Our choice of smoothing approach depends principally on the nature of the errors in the dataset. The sources of error include misalignment of the camera, error in the fiduciary length scale, perspective due to objects (subject or reference scale) being out of the photographic plane, and various errors arising in the digitization process (including the difference between the thresholded ellipse fitted centroid and the true centroid of the non-ellipse drop centroid). Some of these errors are systematic in origin and introduce consistent biases into the data (e.g. coherent spectral sources, rather than truly stochastic noise). Data smoothing does little to help systematic errors in that they are usually of lower frequency than the signal. Random errors, by contrast, are assumed to have a Gaussian distribution (by the central limit theorem), and are independent of the signal (which inherently results from a deterministic process).

We experimented with a variety of filters implemented in the \verb|scipy.signal| Python \emph{SciPy} \cite{oliphant_python_2007} module on a representative set of trajectory data; these methods include 1D Gaussian convolution, Wiener, Butterworth, and Savitsky-Golay filters. Qualitatively comparing these smoothing methods (by hand tuning filter orders and window sizes) we find that we loose too many data points in the smoothing process, large amplitudes are overly smoothed by repeated filtering passes, or there are significant end effects for most of these methods. A comparison of these smoothing approaches on a representative trajectory data set is shown in Figure \ref{fig:y_filtered}.
\begin{figure}
    \centering
    \input{../figures/y_filtered.pgf}
       \caption{The underlying signal is `noisy', due partially to deterministic errors in determining the center of mass position. These deterministic errors are largely due to droplet oscillations, especially the rapidly damped higher harmonics which do not have azimuthal symmetry. There is also Gaussian error in the ellipse fitting due to thresholding and noise in the video itself. We see that 1D Gaussian convolution and Wiener filters suffer from significant end effects. At this scale Butterworth and Savistsky-Golay filters are nearly indistinguishable.}
      \label{fig:y_filtered}
\end{figure}

\begin{figure}
    \centering
    \input{../figures/dy_filtered.pgf}
    \caption{Comparing the first derivatives of the Butterworth and Savitsky-Golay filters we see that the Butterworth filter also suffers from a slight end effect. This implies that the optimization will find a different optima of the likelyhood depending on which type of filter is used.\label{fig:dy_filtered}}
\end{figure}

\begin{figure}
    \centering
    \input{../figures/power_spectra.pgf}
    \caption{The power spectra has a peak at 1 Hz, which is the droplet trajectory parabola itself, and smaller peaks in the kHz range corresponding to various noise frequencies. The Savitsky-Golay and Butterworth filters seem to have the least distortion of the power spectra of the true signal. Both also do a good job of attenuating the noise at the 2 kHz peak. \label{fig:power}}
\end{figure}
The Savitsky-Golay, and Butterworth filters both produce fairly smooth derivatives as can be seen in Figure \ref{fig:dy_filtered}; but the small window-size needed for Butterworth filter tends to also produce a noticeable end effect. The Savitsky-Golay filter essentially uses a moving-window based on local least-squares polynomial approximations. It was shown that fitting a polynomial to a set of input samples and then evaluating the resulting polynomial at a single point within the approximation interval is equivalent to discrete convolution with a fixed impulse response \cite{savitzky_smoothing_1964}. A beneficial property of this kind of low-pass filter is their tendency to maintain waveform amplitudes, and so they are attractive in applications having noisy signals with sharply pointed waveforms such as ultrasound or synthetic aperture radar \cite{schafer_what_2011}. Because Savitsky-Golay is a Finite Impulse Response (FIR) filter it requires data points to be equally spaced; to accommodate this requirement we interpolate points between the small gaps which sometime occur in the tracking results from image analysis. We use a moving window size slightly smaller than the length of the current bounce in a single drop jump data set. The windows are piecewise defined by partitioning the data set into a series of individual bounces (the dataset is sliced at minima identified after an initial rough smoothing pass, using the \verb|scipy.signal.argrelextrema()| function). The Savitsky-Golay polynomial order is 4.

To understand how these filters differ it is useful to look at their frequency response. In Fourier space, convolution becomes a multiplication, and we can understand what a filter does by looking at which frequencies it lets pass through. We can do this using a Discrete Fourier Transform (though it is worth noting that our signal is not truly periodic). The power spectra for these same data are shown in Figure \ref{fig:power}.

\subsection{Optimization}
Most generally a constrained optimization problem is stated as 
\[
\begin{array}{lll}
\mbox{minimize:} & \hspace{2 mm} f\left(\mathbf{x}\right) & \mbox{objective function}\\
\mbox{subject to:} & & \\
& \centering g_j \left( \mathbf{x} \right) \leq 0 & \mbox{inequality constraints}\\
& \centering h_k \left(\mathbf{x} \right) = 0 & \mbox{equality constraints}
\end{array}
 \]
\[ 
\begin{array}{ll}
\mbox{where} \hspace{2 mm} \mathbf{x} = \left\{ \begin{array}{ll}
x_1 & \\
x_2 & \\
\vdots &\\
x_n &
\end{array} \right. & \mbox{design variables}
\end{array}
\]

Mathematical optimization is the problem of finding minima of a function $f$. In this context the function is called the cost, or objective function. The field of mathematical optimization is as old as calculus itself, and the number of particular optimization techniques is correspondingly myriad; particular techniques lend themselves well to particular types of optimization problems. The minima of the objective function $f$ is sought on a domain $A$ specified by the constraints of the problem; this domain is usually called the feasible region. Minima of objective function $f: A \rightarrow \mathbb{R}^m$ are called feasible solutions. If the function $f$ is convex the feasible solution is the global minimum, otherwise additional local minima exist. The scale of the optimization problem is set ultimately by dimensionality of the objective function. Functions may not always be smooth in the sense of having continuous derivatives, and this is problematic in that optimization methods fundamentally rely on gradients of the objective function. Problems with anisotropic objective functions where there is strong covariance between the parameters, and the gradient vector generally to differ significantly from the Newton direction ($-\mathbf{H}^{-1} f' ( \mathbf{x} )^T$, where $\mathbf{H}$ is the Hessian matrix) are considered ill-conditioned. Ill-conditioned problems gradient based deterministic search tend to converge slowly as they take a zigzagging path determined by the local value of the gradient rather than following the Newton-direction vector which towards the minimum. Numerical optimization may deal with black box functions (where we do not have an explicit mathematical expression of the function we are optimizing). Black box problems are challenging because we do not have access to analytic gradients of the objective function, and approximating them by finite-differences is slow and noisy. In general, noisy, black box, non-linear, non-quadratic, non-convex, constrained, ill-conditioned, high-dimensional objective functions are problematic to optimize. Unfortunately, problems of this type are the essence of the parameter estimation, which often leads to its characterization as an `art' rather than a precise science (though we submit that it is a dark art).

The equation of motion behaves stiffly due to the large disparity in Coulombic, image charge length scales. We integrate it numerically using the \verb|odeint| \emph{Scipy} module. This is a shake-and-bake Python wrapper for the venerable 1982 \emph{netlib ODEPACK} library double-precision \verb|lsoda| (Livermore Solver for Ordinary Differential equations with Automatic method switching for stiff and nonstiff problems) integrator \cite{hindmarsh_odepack_1983}. The function switches between Adams (nonstiff) and Backwards Differentiation Formulas (BDF, stiff) according to the dynamic value of a set of stiffness eigenvalues.

Our specific optimization problem is non-convex, mixed discrete-continuous black-box (noisy), and highly ill-conditioned which is essentially the worst case scenario for an optimization problem. The ill-conditioning arises due to the strong covariance between several of the model parameters (particularly $q=q(V_d, E_0)$). The non-convexity of the problem implies that there are many local minima of the objective function. While in principle a gradient-based optimizer (for instance using the quasi-Newton method of Broyden, Fletcher, Goldfarb, and Shanno (BFGS) \cite{_numerical_????}) could be used by using finite-differences to obtain approximate gradients of the $\chi^2$ objective function, in practice doing so is extremely problematic because the noise-to-signal ratio of the objective function scales like $\mathcal{O}(f)$ for $\frac{df}{dt}$ and $\mathcal{O}(f^2)$ for $\frac{d^2f}{ft^2}$ which will tend to cause convergence to a local minima which is only an artifact of the likelihood response surface \cite{wood_data_1982}. As a further practical matter, given the relatively expensive function-calls (which requires solving a stiff, non-linear ODE) gradient-free approaches tend to offer better performance regardless \cite{kolda_optimization_2003}.

We use a gradient-free, direct-search approach: Nelder-Mead \cite{nelder_simplex_1965} implemented in \verb|scipy.optimize|. Nelder-Mead is robust to noise (relatively speaking), and is thrifty with our extremely expensive function-calls.  \emph{Nelder-Mead}, sometimes called simplex-search or downhill-simplex, is a heuristic search method, with no guarantee of optimal solutions, but is well-established and widely used despite that. \emph{Nelder-Mead} is based on the concept of a $N$-simplex, which generalizes a triangle into higher dimensions as a polytrope of $N + 1$ vertices in $N$ dimensions. It uses only-function calls and expands or contracts the simplex according to the function values at its vertices in a way visually reminiscent (in $\mathbb{R}^3$) of the oscillations of the jumping droplets themselves (in fact \emph{Nelder-Mead} is sometimes also called the ``amoeba method''). Very little is known about the convergence properties of the \emph{Nelder-Mead} algorithm in its classical form for non-smooth objective functions \cite{price_convergent_2002}, except that in general it doesn't satisfy the properties required for convergence by other direct search algorithms: that the simplex remains uniformly non-degenerate, and that some form of ``sufficient'' descent condition for function values at the vertices is required at each iteration. Scaling can help solve convergence problems and improve numerical stability. We precondition the optimization problem by minimizing $\ln(\chi^2)$, and using a naive scaling (scaling variables such that their magnitudes $\sim \mathcal{O}(1)$) of our constraints by their initial guesses. Here is goal is to make the problem equally sensitive to steps in any direction. \emph{Nelder-Mead} is not a global optimizer, though there are variants which use sequential local searches with probabilistic restarts to achieve globality. However global optimization usually comes at a tremendous computational cost. However, \emph{Nelder-Mead} behaves less locally than many gradient-based approaches. The convergence history of the parameter MLE using \emph{Nelder-Mead} for a single drop jump experiment is shown in Figure \ref{fig:convergence}. Results of the parameter estimation are shown in Figures \ref{fig:trajectories}, \ref{fig:inverse_problem}.

\begin{figure}[h]
    \centering
    \input{../figures/convergence.pgf}
    \caption{As is typical with \emph{Nelder-Mead} much of the improvment in $\chi^2$ is realized in the first few iterations. Overall the rate of convergence is sub-linear, which is to be expected for non-linear constrained problems using an hueristic algorithem.\label{fig:convergence}}
\end{figure}

%\newpage
\begin{figure}[h]
    \centering
    \resizebox{\textwidth}{!}{\input{../figures/jump_matrix.pgf}}
    \caption{A series of filtered droplet trajectories arranged by increasing apoapse. The blue dots represent either the beginning and end of the experiment, or points at which the droplet is either coming into, or leaving contact with the surface.}
    \label{fig:trajectories}
\end{figure}
%\newpage
\begin{figure}[h]
    \centering
    \resizebox{\textwidth}{!}{\input{../figures/inverse_problem.pgf}}
    \caption{A series of droplet trajectories showing the results of the parameter estimation. The trajectories are shown only up to the apoapse of the first bounce. The red lines show the ODE solution with given the MLE parameter vector. $\chi^2$ goodness-of-fit varies between $1 \times 10^{-5}$ and $1 \times 10^{-8}$ with the better fit occurring typically for the droplets with the lowest apoapses.}
    \label{fig:inverse_problem}
\end{figure}
%\newpage

\subsection{Identifiability}
That we are capable of fitting any arbitrary model to a dataset given sufficient degrees of freedom in our parameters is admittedly a disconcerting issue, begging the question ``given the structure of the model is it possible to uniquely estimate the unknown parameters?'' This question is called the problem of identifiability. However, some of the inverse model parameters are constrained by our experimental observations of them and their associated measurement uncertainties. This, we hope, makes the specter of an over fit model less frightening, but does convert our unconstrained optimization problem to an constrained one which raises special difficulties of its own, which we discuss below.

The \emph{Nelder-Mead} direct search method cannot be used with explicitly constrained problems. However, there are various implicit approaches to (approximately) solving general constrained problems using unconstrained algorithms. Generally, this is achieved by domain transformations or the use of penalty functions.  By the addition of a penalty function which depends in some way on the values of the constraints to the objective function, we minimize a pseudo-objective function where the in feasibility of the constraints is minimized simultaneously to the objective function.

There are various penalty function schemes. We use an Exterior Penalty Function as a simple way of converting converting the constrained problem into an unconstrained one. These are are especially useful in cases where the constraints are not ``hard'' in the sense that they need to be satisfied precisely. General penalty functions, which are sequential unconstrained minimization techniques, reformulate the general constrained problem as the pseudo-objective function given by

\[ \phi(\mathbf{x}, r_p ) = F(\mathbf{x}) + r_p P(\mathbf{x}) \]
where $P \left( \mathbf{x} \right)$ the penalty function, is given by
\begin{equation} \label{exterior}
 P( \mathbf{x} ) = \sum_{j = 1}^m \left\lbrace \mbox{max} \left[ 0, g_j(\mathbf{x} ) \right] \right\rbrace^2 + 
\sum_{k = 1}^l \left[ h_k( \mathbf{x}) \right]^2 .
\end{equation}
We see from Equation \ref{exterior} that there is no penalty if the constraints $g_j(\mathbf{x})$, and $h_k(\mathbf{x})$ are satisfied.

The Exterior Penalty Function specifically (and all Penalty Function approaches in general) do have several drawbacks. Namely these include the possibility of the objective function being undefined outside of the set of feasible solutions. Additionally, by naively ``encouraging'' feasibility of the solution using large values of the penalty parameter, $r_p$, we will tend to ill-condition the unconstrained formulation of the problem (though in our implementation the preconditioning tends to make the pseudo-objective function less and less sensitive to the constraints as the likelihood is approaches a maximum). We use the the measured values of $u_0$, $V_d$, and $E_0$, and the informed guess $q \approx k V_d^{2/3} E_0$ where k is a constant $k \approx 1 \time 10^{-11}$ as an initial guess for the parameter vector $\mathbf{x}$. We stop the optimization after 300 iterations rather than waiting for convergence.

We're interested in the variance and co-variance as a means to determine the quality if the parameter estimate. The $\left( i, j \right)$-th element of the matrix $\sigma (\mathbf{x}, \mathbf{y})$ is equal to the covariance $\mbox{cov}(X_i, Y_j)$ between the $i$-th scalar component of $\mathbf{x}$ and the $j$-th scalar component of $\mathbf{y}$. Here the concept of error bars in linear correlation associated with a covariance matrix are not suitable. We might try to generalize the idea of confidence intervals to a multidimensional space, but it is likely difficult to describe the surface of the (smallest) hyper-volume containing 90\% of the probability with just a few numbers. The situation becomes worse if the probability density function has several maxima. However, there is another approach to find the covariance matrix [ref] 
\[ \left[\sigma^2 \right]_{ij} = -\left[ \left( \nabla^2 \mathcal{L}\right)^{-1}\right]_{ij} = 2 \left[ \nabla^2 \left( \chi^2\right)\right]_{ij}^{-1} = -\left[H^{-1} \right]_{ij}\]
where $H$ refers to the Hessian matrix and $\left[\sigma^2 \right]_{ij}$ is the covariance matrix $C$. The issue of identifiability is especially fraught for non-linear, black box type problems were it is difficult to explicitly evaluate the Hessian. 
The likelihood function (and thus the posterior probability density function) are defined completely by the optimal solution $\mathbf{x}$ and the second derivative of $\mathcal{L}$ at the maximum, which corresponds to the covariance matrix $C$. The standard errors (marginal variances) are the square roots of the diagonal of the covariance matrix. The Hessian matrix must be negative definite for $\mathcal{L}$ to have a maximum at $\mathbf{x_0}$. We obtain an approximate Hessian using the approach suggested in Nelder's original paper, by fitting quadratics to the simplex vertices and midpoints \cite{nelder_simplex_1965}\cite{spendley_sequential_1962}. We can use the condition number
\[ \mbox{cond} (H) = \frac{\mbox{max}[\mbox{eig}(H)]}{\mbox{min}[\mbox{eig}(H)]} \]
to make a qualitative assesment of the stability of the problem. We find typical condition numbers $\sim \mathcal{O}(10^{27})$. In fact, in many cases our Hessian is not negative definite, or invertible at the minmia $\mathbf{x}_0$, which implies negative values of the variances (which is impossible). These issues indicate the problem is extremely ill-conditioned near the minima $\mathbf{x_0}$. Given that the parameter estimates are highly colinear, it is unsuprising that the Hessian matrix is near-singular and its inversion is either impossible or involves significant numerical error. Posteriori verification of the results is crucial to bound the identifiability of the parameter estimation problem, but it remains as future work. Several sources suggest senstivity analysis of the parameter estimates by generation of synthetic Monte Carlo data sets as a means of establishing identifiability \cite{bevington_data_1969}\cite{jaqaman_linking_2006}.

\chapter{Results}
\section{Charge Estimates}
We found the distribution of mostly likely experimental net charges for a population of the droplets jumped in low-gravity. A covariance plot of the model variables is shown in Figure \ref{fig:scatter}. The multicollinear dependence of charge on droplet surface area, $A$, and the characteristic electric field, $E_0$, is evident. Assuming the main effect is the interaction between charge and electric field, a Robust Least Squares model fit $q \sim kAE_0$ (using the Python \verb|statsmodels.formula.api.RLM| function), with the non-linear transformation $A = V_d^{2/3}$, found that $k=5.01 \times 10^{-11} \pm  2.85 \times 10^{-11}$ with $R^2 = 0.946$. This model uses Huber's T norm, median absolute scaling, and H1 covariance estimation. A contour plot showing the estimated droplet free charge as a function of $V_d$ and $\varphi_s$ is shown in Figure \ref{fig:charge}.
\begin{figure}[htb]
    \centering
    \resizebox{12cm}{!}{\input{../figures/scatter.pgf}}
    \caption{A simple EMA plot.\label{fig:scatter}}
\end{figure}
\begin{figure}[htb]
    \centering
    \input{../figures/charge.pgf}
    \caption{A simple EMA plot.\label{fig:charge}}
\end{figure}

A two-ways T-test comparison of charge distributions between the droplet bounce experiment and a corollary experiment with zero electric field at the time of droplet deposition on the superhydrophobic surface suggests that the droplet charge is induced by the electric field, rather than through contact charging on the PTFE layer ($t = 5.11, p = 0.0002$). The T-test informs us that the charge distribution  are about 5 times more different from each other as they are within each other, and there is a 0.02$\%$ probability that this result happened by chance. This corollary experiment is documented in Appendix \ref{sec.drop_charge}.

The model $q \sim kAE_0$ is incidentally very similar to the classical solution for the surface charge density of a half-spherical conductor with a field induced dipole \cite{david_j._griffiths_introduction_1999}
\begin{eqnarray*}
q &=& 3 \epsilon_0 E_0 \int_A \cos \theta dA \\
&=& 3 \pi^{1/3} 6 \left(6 V_d \right)^{2/3} \epsilon_0 E_0 \int^{4 \pi/2}_{\pi / 2} \cos \theta d\theta \\
&=& k E_0 V_d^{2/3}
\end{eqnarray*}
with $k \approx 1.3 \times 10^{-10}$. This is also of a similar form to the charge found by Takamatsu and coauthors for droplets falling from a grounded nozzle in an external electric field \cite{takamatsu_theoretical_1981}
\[q = 4 \pi \epsilon_0 \beta E_0 R_d^2 \]
with $\beta \approx 2.63$.

\section{Scale Quantities}
The dielectrophoretic force plays a very small role when droplets have net charge in a DC field; the condition to neglect the DEP force was satisfied for all experiments in the dataset. Dimensional droplet apoapses scale closely with $\mathbb{E}\mbox{u}$ as seen in Figure \ref{fig:series_s_eu}. The relative magnitudes of the simulated forces felt by the droplets is shown in Figure \ref{fig:forces}. Forces acting on the drops vary in magnitude between $\mathcal{O}(10^{-6})-\mathcal{O}(10^{-4})$ N. We see that, of the drops in the experimental dataset only the two with the largest $\mathbb{E}\mbox{u}$, $\mathbb{E}\mbox{u} \sim \mathcal{O}(1)$ could appropriately be said to be in the inertial electro-viscous regime. In all other cases image forces are much stronger than drag. For these drops $\mathbb{E}\mbox{u} \gg 1/8 \pi$, and are likely on escape trajectories. The image forces themselves rapidly become small compared to Coulomb forces for drops with apoapses $\mbox{max}\left( y\right) \gtrapprox L$, thus it is reasonable to claim that for intermediate drops Coulomb force scales as inertia, and we can neglect the effects of drag and image forces.

\begin{figure}[htb]
    \centering
    \input{../figures/series_s_eu.pgf}
    \caption{Droplet trajectories as a function of $\mathbb{E}\mbox{u}$.\label{fig:series_s_eu}}
\end{figure}
\begin{figure}[htb]
    \centering
    \resizebox{14cm}{!}{\input{../figures/forces.pgf}}
    \caption{Simulated forces acting on the droplet. Experiments are shown by order of increasing apoapse.\label{fig:forces}}
\end{figure}

In the non-dimensional trajectories with short-time scaling shown in Figure \ref{fig:series_s_ds}, we see that the trajectory apoapses are consistently $\mathcal{O}(1)$, but most trajectories overshoot their characteristic time scale (which predicts returns at $\bar{t}  =2$ to the first order). We also observe that that $\mathbb{E}\mbox{u}$ is not typically a small number in this regime, imperiling our use of asymptotic estimates in this regime. We can perhaps gain some insight by comparing the asymptotic estimate for return times to the scaled experiemental return times. We see in Figure \ref{fig:times} that the long-time scaled non-dimensional time of first bounce in the experiment $t_b / t_c$, compares poorly to the asymptotic estimate for returns $t_f$ as $\mathbb{E}\mbox{u}_+$ becomes large. This is very much as we'd expect, but it is also unfortunate; for small $\mathbb{E}\mbox{u}$ the asymptotic length scale could be used to improve the characteristic length scale by $t_a = t_c t_f$. We also notice a two-tailed effect in the data; for the small $\mathbb{E}\mbox{u}$ droplets, the long-time scaling distorts the return times considerably.   
\begin{figure}[htb]
    \centering
    \input{../figures/series_s_ds.pgf}
    \caption{Non-dimensional trajectories with the short-time scaling.\label{fig:series_s_ds}}
\end{figure}

\begin{figure}[htb]
    \centering
    \input{../figures/times.pgf}
    \caption{.\label{fig:times}}
\end{figure}

The covariance of $\mathbb{I}\mbox{m}$ with $\mathbb{E}\mbox{u}$ is shown in Figure \ref{fig:dnumbs}. Predictably, there is quite strong correlation between the dimensionless groups. We also see that $\mathbb{I}\mbox{m} < 1$ for all drops. Using an OLS regression, we find the model $\mathbb{I}\mbox{m} \sim (0.012 \pm 0.003) \mathbb{E}\mbox{u} + (0.212 \pm 0.036) $ with $R^2 =0.59$.
\begin{figure}[htb]
    \centering
    \input{../figures/dnumbs.pgf}
    \caption{.\label{fig:dnumbs}}
\end{figure}

Finally we show several trajectories in the long-time scaled regime in Figure \ref{fig:series_l_ds}.
\begin{figure}[htb]
    \centering
    \input{../figures/series_l_ds.pgf}
    \caption{Non-dimensional trajectories with the long-time scaling as a function of ${\mathbb{E}\mbox{u}}_+$.\label{fig:series_l_ds}}
\end{figure}
We should note that there are several kinds of systematic error that influence our data. We assume that droplet translate purely along the central axis of the electric field, but in practice, despite the improvement in surface charge density uniformity produced by corona charging, there are still local areas of especially high charge density. In principle, this kind of error should become small for droplets which are far enough away from the charge distribution, that the geometry of the charge distribution disappears, and the electric field looks like that due to a point charge. Another form of error is in the initial velocity as it appears in $\mathbb{E}\mbox{u}$. Because we usually lose the first few frames of video due to camera shake transients at the start of the low-gravity experiment, we will consistently underestimate $U_0$ because the droplet will already have decelerated significantly during that period of time. The primary sources of random error are the effect of contact line hysteresis on the droplet initial velocity, and of the variance in the MLE parameter estimates.
\newpage

\section{Impact Dynamics \hl{[placeholder section]}}
Using the unique capabilities of the low-gravity environment we obtained data on dimensionless contact time and coefficients of restitution at very low Ohnesorge numbers for a range of electric Bond numbers. Despite strong electric fields (0.5-1.5 $kV/cm$) we found little evidence for wetting transitions due to excession of a critical pressure (the ``Fakir impalement''). There is no obvious trend in dimensionless contact time or coefficient of restitution with electric Bond number.

Jump velocities are more strongly damped for relatively small droplet volumes in the presence of the electric fields than was shown by Attari \emph{et. al.}. This may be evidence for electrowetting paradoxically enhancing the effect of contact angle hysteresis pinning on sharp corners. (How does this tie into the coefficients of restitution problem?)

\begin{figure}[htb]
    \centering
    \input{../figures/contact.pgf}
    \caption{.\label{fig:contact}}
\end{figure}

\begin{figure}[htb]
    \centering
    \input{../figures/restitution.pgf}
    \caption{.\label{fig:restitution}}
\end{figure}

\newpage

\appendix
\appendixpage
\noappendicestocpagenum
\addappheadtotoc

\chapter{Parallel Plate Method}
\label{sec.drop_charge}
Since, by the earlier scaling, we presuppose the source of the droplet bouncing behavior to be primarily Coulombic in origin (as opposed to dielectrophoretic), the droplet must have some free charge in addition to the charge induced by the electric field. Whether this free charge arises due to contact charge or field induction To measure this charge concurrent methodologies were used. We determined the droplet free charge by observation of the deflection of the droplets in the region of a known uniform field in a fashion inspired by Millikan's famous experiment to determine the fundamental charge of the electron.

Droplets were jumped in free-fall from a superhydrophobic surface placed between the plates of a parallel plate capacitor of known uniform electric field. The surface was charge neutralized. Since the droplet initial velocity $U_0$ is parallel to the electric field, the droplets are inertial in the direction of the electric force, and neglecting the effect of image charges mirrored across the conductors, we can determine the magnitude of the droplet charge by a balance of Coulombic force and inertia given by the equation of motion

\[ y'(t) = q\mathbf{E}. \]

Since the drag is negligible in the inertial limit we can find the charge $q$ by fitting a second-order least squares polynomial to the measured droplet positions, equating the $t^2$ term to the constant acceleration, and dividing by the known, constant magnitude of the electric field.

A 200-880 VAC source with a full wave bridge rectifier circuit was prototyped on perf-board for initial experiments to measure droplet charge. The circuit was analyzed on an laboratory oscilloscope to verify that the AC component of the signal was appropriately small (13 mV at 35 kHz). Current was determined to be a relatively low 80 $\mu$A. The high-voltage source terminals were led to two parallel polished 150x150 mm aluminum plate electrodes. The electrodes were mounted on an insulated 80/20 extruded aluminum rail for ease of adjustment. All droplet charge experiments were conducted with an electrode spacing of 28.30 mm. With this spacing the calibrated electric field between the plates was $\mathbf{E} \approx 35$kV/m. The electrodes were electrically isolated from the drop rig by two alternating layers of 4 mm thick PMMA sheet and Kapton tape. Potential across the plates was measured periodically with a load-impedance corrected multimeter to account for battery depletion. The typical capacitor rise time of the plates was measured to be 1.4 s, thus to make the most economical use of the brief window a low-gravity a weighted switch was set by hand prior to the drop to close the high-voltage circuit, but which passively safed the system at the resumption of 1-g conditions in the tower. From a survey of literature we suppose the droplet charge, if they are indeed charged by contact with PTFE, to be some function of the droplet volume and the residence time on the superhydrophobic surface. However, sweeping though droplet volumes over a series of drop tower experiments we find little correlation between droplet volume  and free droplet charge.

A brief screening experiment was conducted which alternated the polarity of the field by switching the positive and negative terminal leads between plates. Qualitative observations of droplet electrode preference seem to indicate that the assumption of small polarization stress was well founded. Following this a orthogonal array $3^2$ factorial design experiment with two replicates was conducted to test the effect of varying droplet volume and surface stay time on free charge at the time of jumping. It was hypothesized in accordance with previous studies [ref], that free charge would increase for levels of both factors. ANOVA analysis in \emph{R} of the linear multiple regression model for the data set indicates that neither droplet volume ($p=0.105$), nor surface stay time ($p=0.358$) is significant at the 95\% confidence level. The overall model F-statistics (2.177 in 2 and 13 degrees of freedom), and coefficients of determination ($r^2 = 0.2509$) indicate that the linear model neither fits the data particularly well, nor does it offer an improvement over the mean model. The mean charge was determined to be positive $2.3 \cdot 10^{-11}$ C, with a standard deviation of $1.8 \cdot 10^{-11}$ C.

\backmatter
\printbibliography
\end{document}

### 2018-01-25 doc/manuscript/methods.tex
draft

--- 2018-01-18 doc/manuscript/parameter_estimation.tex
@@
 \usepackage{setspace}
-\author{Erin Schmidt}
+%\author{Erin Schmidt}
+\date{}
+\title{Methods}
 
+\usepackage{setspace}
 \newlength\figureheight
@@
 \setlength\figurewidth{10cm}
+\usepackage[
+backend=biber,
+style=phys,
+sorting=none
+]{biblatex}
+\addbibresource{thesis.bib}
 
 \begin{document}
+\maketitle
 \doublespacing
+\section{Overview}
+Mainly we are concerned about what parameters are important in electrostatic transport of relatively large (e.g.
+millimetric) droplets in low-gravity, and what the values of the respective dimensionless groups, namely $\mathbb{I}\mbox{m}$, $\mathbb{E}\mbox{u}$ and ${\mathbb{E}\mbox{u}}_+$ might be.
+
+To find typical vales of these parameters we used the following approach:
+\begin{enumerate}
+\item We observed spontaneous droplet jumps on charged dielectric super-hydrophobic surfaces under low-gravity conditions in a $2.1$ s drop tower, while varying the independent variables $V_d$, $\sigma$.
+However, this raises an interesting challenge; it is impractical to directly measure all of the key physical quantities that appear in the dimensionless groups at once in a drop tower experiment.
+In particular, determination of net droplet free electric charge $q$, is difficult (as high-input resistance electrometers, being notoriously fickle instruments, are not well suited to sudden 15-g decelerations).
+Schematic representations of the droplet jump, and of the droplet in the Cassie-Baxter 1-g initial state is shown in Figures \ref{fig:apparatus0} and \ref{fig:schematic}.
+\item Using high-speed video and image analysis software we captured the trajectories of the droplets. 
+\item We solved the inverse problem to find the key parameters by maximizing a statistical likelihood function between an observed trajectory and the trajectory predicted by a dynamical model given that certain set parameters.
+The best fit parameters obtained by direct-search optimization are those corresponding to the maximum likelihood experimental values.
+The optimization is constrained by the measurement precision of directly measured independent, and dependent variables.
+\end{enumerate}
+
+\begin{figure}[ht]
+ \centering
+ \includegraphics[width=0.75\textwidth]{../figures/schematic.pdf}
+ \caption{A schematic representation of the droplet initial condition, prior to the drop.\label{fig:schematic}}
+\end{figure}
+
+\begin{figure}[ht]
+ \centering
+ \includegraphics[width=0.75\textwidth]{../figures/apparatus0.pdf}
+ \caption{The experimental concept with characteristic time and length scales, \hl{$t_c$, $y_c$} shown.\label{fig:apparatus0}}
+\end{figure}
+
+\section{Experimental Methods}
+
+Droplets of distilled water, in a range of volumes ($0 \leq R_d \leq 1$mL), were very carefully deposited on the charged superhydrophobic surface using an grounded glass syringe with $\pm 1\mu$L accuracy, and then dropped in the drop tower.
+The DDT uses a dual capsule design, inspired by the 2.2 s facility at NASA Glenn Research Center, which decouples drag acceleration felt by the external drag shield from the experiment.
+The experiment then experiences approximately $1 \times 10^{-6}$g of high quality free-fall for the 2.1s required for the rig/drag shield assembly to plummet to the bottom of drop tower 6 floors below.
+Red dye was added to improve trajectory digitization.
+Droplet trajectories were recorded using a \emph{Panasonic} HC-WX970 Camera, at 120 fps and and 1/3000s shutter speed.
+In a few cases where higher frame rates were needed a \emph{Nikon} 1 J1 camera with a 30mm telephoto lens was used, shooting at 400 fps.
+The experimental test cell was illuminated with a 6000K LED strip, with a thin semi-opaque plastic film covering to make the light diffuse.
+
+Rather than haphazardly contact charge the surfaces with streams of water, as likely happened by accident in the experiments which inspired this inquiry, we strive for a more controlled, uniform surface charge distribution.
+Following from this desire, superhydrophobic electrets were prepared, with surface potentials 0.7-4.0 $kV$.
+According to a review by Sessler \cite{_electrets_????}, an electret is a dielectric material with ``quasi-permanent'' electric charge in the sense that the characteristic decay period of the electret is much greater than a practical experiment time scale.
+Electret charge may be `true' charge in the form of surface or space charges, or polarization charges (such as bound charges).
+If the electret is not screened by a conductor then it produces an external electric field if the polarization and real charges do not uniformly compates each other throughout the volume of the electret.
+For this reason electrets are though of as electrostatic analouges to permanent magnets (and the name \emph{electret} itself is a portmantau to that effect conjured by Heaviside in 1892 \cite{heaviside_electrical_2011}).
+Typical commerical electrets are Teflon type (PTFE) polymer films on the order of 10-50 $\mu$m thick with the charge being primarily real surface charge.
+Electrets have a plethora of applications, but most germanely they have been used in Electro-Wetting On Dielectric (EWOD) devices for low-voltage manipulation of small droplets \cite{wu_low-voltage_2010}.
+Real charge electrets can be produced by contact electrification, injection or deposition) of charge carriers by discharge or electron beam, ionizing radiation, or by frictional triboelectrification.
+Dipolar electrets by contrast are produced by a combination of polarization at elevated temperatures in a strong external electric field, followed by an annealing process.
+Effective surface charge densities are limited to the material dielectric strengths due to internal dielectric breakdown phenomenon (this typically occurs before external breakdown or Paschen breakdown).
+We use an isothermal electret formation process using a variation of the widely applied corona-charging technique.
+The typical corona-charging technique uses strong inhomogenous DC electric fields to produce discharge in air at ambient conditions; the dielectric substrate is atop a grounded electrode, and there is a screening potential electrode intermediately positioned to control the surface potential (the the surface potential of the dielectric will tend to saturate at this grid potential if the material is not space-charge current limited).
+The corona field is usually produced by pin-shaped electrode.
+In air the most common charge carriers thus produced are $\mbox{CO}_3^-$ ions.
+This approach is known to generally produce samples with fairly uniform surface charge densities.
+Some work by van Turnhout in 1975 showed, using Thermally Stimulated Current (TCS) measurements, that in 4.8 mm thick polymethyl methacrylate (PMMA) polarization of the dielectric is non-uniform, due to real space-charge mostly ($\sim$90\%) residing in a thin (0.1-0.2 mm) layer near the free-surface of the sample \cite{van_turnhout_thermally_1975}.
+In this work we use a balanced AC corona ion source (Ptec IN5120), to direct a net neutral stream of ions towards the dielectric target, which we polarize by an electrode with a $2$ kV$+$ (absolute reference) DC-DC converter.
+The ion stream compensates the surface, and space bound charges arising due to the polarization of the dielectric.
+When the DC-DC converter is switched to ground, the deposited negative ions remain on the surface.
+
+The electret is lamina of 3-4 0.4 mm corona charged PMMA sheets.
+The electric field strength scales with the number of dielectric lamina as has also been shown in work on electret based vibrational energy harvesters \cite{wada_stacking_2012} and in water desalinization \cite{ni_desalination_2005}.
+
+The final, superhydropobic layer, is produced by laser etching PMMA, and depositing a thin layer of PTFE on the resulting roughness topology to increase the Young's angle.
+The surface charge density can be modulated during the experiment using the high-voltage DC-DC converter, which can re-polarize the dielectric substrate by means of an embedded electrode, and the resulting bound charge partially or fully neutralizes the electric field due to the surface ions deposited by corona charging of the electret.
+The high-voltage system is armed manually before the drop and is automatically safed by a high-voltage power switching relay, which switches the load across a 100 k$\Omega$ resistor when triggered by the resumption of 1-g conditions.
+The safing is set by an accelerometer pin-interrupt triggered microcontroller command.
+The rig with a mounted experiment is shown in Figure \ref{fig:rig}.
+\begin{figure}
+    \centering
+    \def\svgwidth{\columnwidth}
+    \input{../figures/rig.pdf_tex}
+    \caption{The droplet electro-bounce experiment hardware mounted on a drop tower rig.\label{fig:rig}}
+\end{figure}
+
+Contact angles of distilled water on the electret $\sim 150^{\circ}$.
+The hysteresis of the contact angle (the difference between the advancing and receding contact angles) is estimated from the roll-off angle using the method of Furmidge, 1962 \cite{furmidge_studies_1962}, and is found to be approximately $20^{\circ}$ when the surface is uncharged.
+The innate Young's angle hydrophobicity of the PTFE layer is enhanced by the underlying roughness length scales of the surface.
+We use a laser-etched pillared geometry with pillar heights $\sim 680$ $\mu$m, widths $\sim 70$ $\mu$m and pitch $\sim 100$ $\mu$m.
+An SEM image of the pillar geometry is shown in Figure \ref{fig:SEM}.
+\begin{figure}
+    \centering
+    \input{../figures/hysteresis.pgf}
+       \caption{Hysteresis of the contact line plotted as a function of static contact angle and roll-off angle for $1$ mL droplets.\label{fig:hysteresis}}
+\end{figure}
+
+\begin{figure}[ht]
+ \centering
+ \includegraphics[width=0.75\textwidth]{../figures/SEM.pdf}
+ \caption{SEM image of the superhydrophobic surface.\label{fig:SEM}}
+\end{figure}
+
+Surface potentials were measured on the superhydrophobic surface using a \emph{Simco-Ion} FMX-004 electrostatic fieldmeter and the method for determination of surface charge density for low conductivity polymers described in Davies, 1967 \cite{davies_examination_1967}.
+This measurement was done with the superhydrophobic surfaces connected by a conductive ground plane by conductive tape, far away from the presence of other conductors.
+An ideal approach to determining surface charge on a dielectric surface is to screen perturbing effects of external electric fields.
+This is partly accomplished by grounding the fieldmeter, and by placing the dielectric sample on a grounded conductive plate backing.
+In this case the surface charge density is determined from
+\[ \sigma = \frac{\varphi_s \kappa}{l}, \]
+where $\varphi_s$ is the surface potential read by the fieldmeter, and where $l$ and $\kappa$ are the thickness of the dielectric surface, and the absolute permitivity respectively.
+The measured surface voltage is a function of position away from the charged dielectric.
+In most cases this function is relatively constant at a distance about 1-2 cm away from the surface (there is some measurement error in surface voltage due to small mispositioning of the electrostatic fieldmeter, say by $\pm$1 mm).
+The relative dielectric constant of the PMMA sheet was measured by using a 65 mm $\square$ polished aluminum parallel plate capacitor with $C = \epsilon \epsilon_0 \frac{A}{l}$ where $C$ is the capacitance, and $A$ is the sheet area.
+Measuring the capacitance with 3 sample thicknesses using a GenRad 1657 RLC Digibridge, we found the relative permitivity to be $\epsilon = 3.5 \pm 0.4$.
+
+A further consideration is the possibility of the change in total charge during a typical experimental timescale.
+If we consider the drop rig to be a ground (which seems reasonable given that the rig is isolated from true ground, but is at some reference voltage with respect to the surface charges on the dielectric, it also has an abundance of free charge carriers, that is, if it is conductive), then there will be both bulk and surface decay of the charge on the dielectric.
+The evolution of the charge can in some cases be approximated by
+\[ \sigma = \sigma_0 e^{\frac{-t}{\epsilon \rho}}, \]
+where $\sigma_0$ is the initial surface charge density, and $\rho$ is the bulk resistivity (which can also be reframed in terms of conductivity by $\rho = 1/\gamma$, where $\gamma$ is the conductivity).
+For an example case of a surface with an initial surface charge density $\sigma = 2.4 \times (10^{-6})$ $C/m^2$, relative permittivity $\epsilon = 3.5$ and bulk resistivity $\rho = 1.6 \times (10^{16})$ $\Omega$cm such as with the case of 2.8 mm PMMA sheet, then the time constant $\tau = \kappa \rho$ is approximately 5000 s, which is a great deal longer than the typical time period for of a drop tower experiment.
+We measured the charge decay with a calibrated probe at periodic intervals.
+There are several charge decay mechanisms: internal ones, such as Ohmic resistence, and external ones such as compensation by envonmental ionic species.
+The relative magnitudes of these charge transport mechanisms, and therfore the stability of the electret varies drastically depending on its initial surface potential, material properties, environment, and charging method.
+In the case of unshielded electrets compensation by atmospheric ions is significant \cite{perlman_electrets_1973}.
+Because environmental convection will tend to  maintain a gradient of these ions, sealing an electret in a container from the atmosphere will effectively halt this decay mechanism.
+Atmospheric humidity and water droplet condensation also significantly increase charge decay (presumably by reducing the surface resistence) \cite{haenen_characteristic_1975}.
+Examples of this decay can be seen in Figure \ref{fig:charge_decay} for differing numers of dielectric lamina used in this experiment.
+In looking at the trends in charge decay for our electrets we notice firstly, that the decay does not appear to be exponential, as in the model described above.
+Secondly, we plainly see a cross-over effect in the decay of the surface potential in our electret samples, whereby the samples charged to higher initial surface potentials decayed faster and reached the lower overall final potentials.
+This is a well known effect in polyethylenes charged by corona \cite{ferreira_corona_1992}.
+\begin{figure}[htb!]
+    \centering
+    {\input{../figures/charge_decay.pgf}}
+       \caption{Charge decay in the dielectric laminates for differing numbers of layers.\label{fig:charge_decay}}
+\end{figure}
+\newpage
+
+%Because the PMMA is a dielectric material there are some additional considerations for determining the surface charge density.
+Firstly, for an insulated conductor $A$ with charge $q$, the charge distribution in equilibrium will be such that the field on the interior of the conductor is zero, with field lines being normal to the surface and the integral of the field strength $\mathbf{E}$ from any point $P$ in or on the conductor to a ground point $G$ is a constant given by
+%\[ V = \int^G_P \mathbf{E} \cdot da, \]
+%where $V$ is the voltage or potential of the conductor (or alternatively, the surface voltage potential). The voltage $V$ and the charge $q$ are proportional and $q$ is usually given by
+%\[q = CV, \]
+%where $C$ is the capacitance of the insulated conductor and is determined by the conductor's size and shape, and its placement relative to the conductors and ground.
+However, the case of a charged insulator departs significantly from that of the insulated conductor.
+Here we have the possibility of the density and net polarity of the charge varying as a function of position about the surface.
+The field of the interior may not be zero, and the field lines are not necessarily normal to the the surface.
+The integral of the field strength from a point on or in the insulator to ground is usually different from point to point.
+In general the surface voltages will vary from point to point on an insulator (including point on the interior of the insulator.
+Therefore it is not possible to uniquely define the voltage of a charged insulator, except in certain contrived cases (notably the the potential of a uniformly charged sphere positioned infinitely far away from any conductors).
+It follows that there is no definition for the capacitance of an insulator as well.
+Though insulative sheets may store charge and discharge in the manner of capacitors, this discharge is never particularly complete.
+
+%There are two cases where we can make meaningful quantitative measurements of state variables for charged insulators: we can measure the electric field arising from the charge, and possible the total charge for uniformly charged free insulative sheets, and uniformly charged insulative sheets backed by a grounded conductor.
+To do this we can use field meters and non-contacting voltmeters.
+If the field strength indicated on the meter is $\mathbf{E}$, the charge density $\sigma$ on the part of the insulator in the front should be $\sigma = \epsilon_0 \mathbf{E}$.
+If a non-contacting voltmeter is placed a at a distance $d$ from the sheet, then the surface voltage $V_s$ indicated on the meter is given by
+%\[V_s = d \mathbf{E} = d \frac{\sigma}{\epsilon_0}. \]
+
+\newpage
+\section{Data Munging}
+Digitization of droplet trajectories requires several steps of post-processing.
+Video is first decomposed into a sequence of still images.
+Trajectories are captured using the particle tracking module in \emph{Fiji} \cite{schindelin_fiji:_2012}, a derivative of the popular \emph{ImageJ} \cite{schneider_nih_2012} package for scientific image analysis.
+The series is stabilized to remove the effect of drop transients from the kinetmatic data \cite{li_image_2008}.
+The series of still images is cropped, and the background (that is, the low-entropy pixels) of the series is removed using a builtin ``rolling ball'' algorithm.
+Each still is then split into its constituent RGB maps.
+In this case the green channel images contained the most information, so these were then globally thresholded using the Triangle algorithm to recover a map of the pixels corresponding to the droplet's approximate position in the original still.
+Ellipses are fitted to the pixel map stepping through the time series to determine the positions of the center of mass, and the semi-major and minor axes of the droplets during the drop.
+Finally, a perspective correction is applied to the center-of-mass positions.
+A Python data class was made to object orient experimental metadata, as opposed to using HDF5 data format or some form of structured array.
+The code used in this work, as well as the raw data, and the make files for this thesis are archived on the open-source project portal Github \cite{schmidt_droplet_electro-bounce:_2017}.
+
 \section{Parameter Estimation}
-We find the parameters $\mathbf{x}$ that solve the inverse problem $G(\mathbf{x}) = \mathbf{d}$, using a direct search method (\emph{Nelder-Mead}). 
+
+Using various scaling arguments we have gleaned from our simple model a series of non-dimensional numbers characteristic of droplet bounce apoapses and times of flight, but these dimensionless groups depend on a set of physical parameters.
+Unfortunately not all of these parameters are physically practical to accurately measure by experiment.
+Droplet free charge $q$, in particular, could in principle be directly measured by collecting the charged drops in a faraday cup under low-g and measuring the change in capacitance of the cup using a very high input-resistance electrometer, but this is a problematic experiment to set up in a drop tower from a practical standpoint.
+The other state variables we can directly measure by experiment with varying levels of accuracy.
+To measure the charge, $q$, we instead turn to parameter estimation techniques.
+Our work flow to identify this parameter is as follows:
+\begin{enumerate}
+\item Experimentally vary $V_d$, $\sigma$ and capture droplet trajectories using a high-speed camera.
+\item Digitize droplet trajectories by using automatic tracking of ellipse-fitted centroids on the thresholded video.
+\item Slice droplet trajectories by their bounce minima, and apply a smoothing filter.
+\item Extract the droplet charge (and other experimental parameters) by maximizing the log-likelihood of the data given the dynamical model and parameters, by varying the parameter vector using a direct search optimization.
+\end{enumerate}
+
+Mathematically we state that we find the parameters $\mathbf{x}$ that solve the inverse problem $G(\mathbf{x}) = \mathbf{d}$, using a direct search method (\emph{Nelder-Mead}). 
 \[
@@
 \[
-m y'' = \frac{1}{2} \rho C_D A_d {y'}^2 + q E(y) + \frac{1}{4} \frac{K q^2}{y^2} + \frac{1}{2} {E(y)}^2 \nabla \epsilon\]
-
-In particular, it is impractical to directly measure the droplet net charge $q$, during a bounce experiment. Our work flow to identify this parameters is as follows:
-\begin{enumerate}
-\item Experimentally vary $V_d$, $\sigma$ and capture droplet trajectories using a high-speed camera.
-\item Digitize droplet trajectories by using automatic tracking of ellipse-fitted centroids on the thresholded video.
-\item Slice droplet trajectories by their bounce minima, and apply a smoothing filter.
-\item Extract the droplet charge (and other experimental parameters) by maximizing the log-likelihood of the data given the dynamical model and parameters, by varying the parameter vector using a direct search optimization.
-\end{enumerate}
+m y'' = \frac{1}{2} \rho C_D A_d {y'}^2 + q E(y) + K q^2 y^{-2} \]
 
 \subsection{Inverse Problems}
-We have a simple model for 1D projectile motion of charged droplets within Coulomb potential wells in low-g.
-Using various scaling arguments we have gleaned from this model a series of non-dimensional numbers characteristic of droplet bounce apoapses and times of flight, but these dimensionless groups depend on a set of physical parameters.
-Unfortunately not all of these parameters are physically practical to accurately measure by experiment.
-Droplet net charge $q$, in particular, could in principle be directly measured by collecting the charged drops in a faraday cup under low-g and measuring the change in capacitence of the cup using a very high input-resistence electrometer, but this is a problematic experiment to set up in a drop tower from a practical standpoint.
-The other state variables we can directly measure by experiement with varying levels of accuracy.
-To measure the charge, $q$, we instead turn to parameter estimation techniques.
 
@@
 where the operator $G$ might be an ODE. Suppose the model $G(\mathbf{x})$ is the ODE
-\[ \frac{dy}{dt} = f(t, \mathbf{y}; \mathbf{x}), \hspace{1 mm}  \mathbf{y} \in \mathbb{R}^n, \]
+\[ y'(t) = f(t, \mathbf{y}; \mathbf{x}), \hspace{1 mm}  \mathbf{y} \in \mathbb{R}^n, \]
 and a collection of $n$ measurements of experimental data
@@
 Thus parameter estimation is a variety of optimization problem.
+
+\subsection{Smoothing}
+All optimization methods, whether explicitly or implicitly, follow gradients towards an optimum.
+In a parameter estimation problem, if we approximate these gradients by finite differences, then the noise manifests itself as amplification of the roughness in the hyper-response surface.
+Gradient based optimizers do poorly in these situations because they tend to converge to local minima.
+While so called gradient free algorithms offer an improvement in this regard, speed of convergence and the quality of the MLE is improved by smoothing the objective function.
+This is equivalent to smoothing the underlying dataset.
+
+Our choice of smoothing approach depends principally on the nature of the errors in the dataset.
+The sources of error include misalignment of the camera, error in the fiduciary length scale, perspective due to objects (subject or reference scale) being out of the photographic plane, and various errors arising in the digitization process (including the difference between the thresholded ellipse fitted centroid and the true centroid of the non-ellipse drop centroid).
+Some of these errors are systematic in origin and introduce consistent biases into the data (e.g.
+coherent spectral sources, rather than truly stochastic noise).
+Data smoothing does little to help systematic errors in that they are usually of lower frequency than the signal.
+Random errors, by contrast, are assumed to have a Gaussian distribution (by the central limit theorem), and are independent of the signal (which inherently results from a deterministic process).
+
+We experimented with a variety of filters implemented in the \verb|scipy.signal| Python \emph{SciPy} \cite{oliphant_python_2007} module on a representative set of trajectory data; these methods include 1D Gaussian convolution, Wiener, Butterworth, and Savitsky-Golay filters.
+Qualitatively comparing these smoothing methods (by hand tuning filter orders and window sizes) we find that we loose too many data points in the smoothing process, large amplitudes are overly smoothed by repeated filtering passes, or there are significant end effects for most of these methods.
+A comparison of these smoothing approaches on a representative trajectory data set is shown in Figure \ref{fig:y_filtered}.
+
+\begin{figure}
+    \centering
+    \input{../figures/y_filtered.pgf}
+       \caption{The underlying signal is `noisy', due partially to deterministic errors in determining the center of mass position.
+These deterministic errors are largely due to droplet oscillations, especially the rapidly damped higher harmonics which do not have azimuthal symmetry.
+There is also Gaussian error in the ellipse fitting due to thresholding and noise in the video itself.
+We see that 1D Gaussian convolution and Wiener filters suffer from significant end effects.
+At this scale Butterworth and Savistsky-Golay filters are nearly indistinguishable.}
+      \label{fig:y_filtered}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \input{../figures/dy_filtered.pgf}
+    \caption{Comparing the first derivatives of the Butterworth and Savitsky-Golay filters we see that the Butterworth filter also suffers from a slight end effect.
+This implies that the optimization will find a different optima of the likelyhood depending on which type of filter is used.\label{fig:dy_filtered}}
+\end{figure}
+
+\begin{figure}
+    \centering
+    \input{../figures/power_spectra.pgf}
+    \caption{The power spectra has a peak at 1 Hz, which is the droplet trajectory parabola itself, and smaller peaks in the kHz range corresponding to various noise frequencies.
+The Savitsky-Golay and Butturworth filters seem to have the least distortion of the power spectra of the true signal.
+Both also do a good job of attenuating the noise at the 2 kHz peak.
+\label{fig:power}}
+\end{figure}
+
+The Savitsky-Golay, and Butterworth filters both produce fairly smooth derivatives as can be seen in Figure \ref{fig:dy_filtered}; but the small window-size needed for Butterworth filter tends to also produce a noticeable end effect.
+The Savitsky-Golay filter essentially uses a moving-window based on local least-squares polynomial approximations.
+It was shown that fitting a polynomial to a set of input samples and then evaluating the resulting polynomial at a single point within the approximation interval is equivalent to discrete convolution with a fixed impulse response \cite{savitzky_smoothing_1964}.
+A beneficial property of this kind of low-pass filter is their tendency to maintain waveform amplitudes, and so they are attractive in applications having noisy signals with sharply pointed waveforms such as ultrasound or synthetic aperture radar \cite{schafer_what_2011}.
+Because Savitsky-Golay is a Finite Impulse Response (FIR) filter it requires data points to be equally spaced; to accommodate this requirement we interpolate points between the small gaps which sometime occur in the tracking results from image analysis.
+We use a moving window size slightly smaller than the length of the current bounce in a single drop jump data set.
+The windows are piecewise defined by partitioning the data set into a series of individual bounces (the dataset is sliced at minima identified after an initial rough smoothing pass, using the \verb|scipy.signal.argrelextrema()| function).
+The Savitsky-Golay polynomial order is 4.
+To understand how these filters differ it is useful to look at their frequency response.
+In Fourier space, convolution becomes a multiplication, and we can understand what a filter does by looking at which frequencies it lets pass through.
+We can do this using a Discrete Fourier Transform (though it is worth noting that our signal is not truly periodic).
+The power spectra for these same data are shown in Figure \ref{fig:power}.
 
@@
 
-The equation of motion behaves stiffly due to the large disparity in Coulombic, image charge, and dielectrophoretic length scales.
+The equation of motion behaves stiffly due to the large disparity in Coulombic, image charge length scales.
 We integrate it numerically using the \verb|odeint| \emph{Scipy} module.
-This is a shake-and-bake Python wrapper for the venerable 1982 \emph{netlib ODEPACK} library double-precision \verb|lsoda| (Livermore Solver for Ordinary Differential equations with Automatic method switching for stiff and nonstiff problems) integrator \hl{[ref]}.
+This is a shake-and-bake Python wrapper for the venerable 1982 \emph{netlib ODEPACK} library double-precision \verb|lsoda| (Livermore Solver for Ordinary Differential equations with Automatic method switching for stiff and nonstiff problems) integrator \cite{hindmarsh_odepack_1983}.
 The function switches between Adams (nonstiff) and Backwards Differentiation Formulas (BDF, stiff) according to the dynamic value of a set of stiffness eigenvalues.
 
-Our specific optimization problem is non-convex, mixed discrete-continuous black-box (noisy), and highly ill-conditioned which is essentially the worst the worst case scenario for an optimization problem.
+Our specific optimization problem is non-convex, mixed discrete-continuous black-box (noisy), and highly ill-conditioned which is essentially the worst case scenario for an optimization problem.
 The ill-conditioning arises due to the strong covariance between several of the model parameters (particularly $q=q(V_d, E_0)$).
 The non-convexity of the problem implies that there are many local minima of the objective function.
-While in principle a gradient-based optimizer (for instance using the quasi-Newton method of Broyden, Fletcher, Goldfarb, and Shanno (BFGS) \hl{[Nocedal, J, and S J Wright.
-2006]}) could be used by using finite-differences to obtain approximate gradients of the $\chi^2$ objective function, in practice doing so is extremely problematic because the noise-to-signal ratio of the objective function scales like $\mathcal{O}(f)$ for $\frac{df}{dt}$ and $\mathcal{O}(f^2)$ for $\frac{d^2f}{ft^2}$ which will tend to cause convergence to a local minima with is an artifact of the likelihood response surface \hl{[Wood, 1982: Refs 5, 14, 49, 95.]}.
-As a further practical matter, given the relatively expensive function-calls (which requires solving a stiff, non-linear ODE) gradient-free approaches tend to offer better performance regardless\hl{[Singer and Mead, 2009]}.
+While in principle a gradient-based optimizer (for instance using the quasi-Newton method of Broyden, Fletcher, Goldfarb, and Shanno (BFGS) \cite{_numerical_????}) could be used by using finite-differences to obtain approximate gradients of the $\chi^2$ objective function, in practice doing so is extremely problematic because the noise-to-signal ratio of the objective function scales like $\mathcal{O}(f)$ for $\frac{df}{dt}$ and $\mathcal{O}(f^2)$ for $\frac{d^2f}{ft^2}$ which will tend to cause convergence to a local minima which is only an artifact of the likelihood response surface \cite{wood_data_1982}.
+As a further practical matter, given the relatively expensive function-calls (which requires solving a stiff, non-linear ODE) gradient-free approaches tend to offer better performance regardless \cite{kolda_optimization_2003}.
 
-We use a gradient-free, direct-search approach: Nelder-Mead \hl{[Nelder, 1965]} implemented in \verb|scipy.optimize| \hl{[Jones et al.
-2001 --]}.
-Nelder-Mead is robust to noise (relatively speaking), and is relatively thrifty with our extremely expensive function-calls.
+We use a gradient-free, direct-search approach: Nelder-Mead \cite{nelder_simplex_1965} implemented in \verb|scipy.optimize|.
+Nelder-Mead is robust to noise (relatively speaking), and is thrifty with our extremely expensive function-calls.
 \emph{Nelder-Mead}, sometimes called simplex-search or downhill-simplex, is a heuristic search method, with no guarantee of optimal solutions, but is well-established and widely used despite that.
 \emph{Nelder-Mead} is based on the concept of a $N$-simplex, which generalizes a triangle into higher dimensions as a polytrope of $N + 1$ vertices in $N$ dimensions.
-It uses only-function calls and expands or contracts the simplex according to the function values at its vertices in a way visually reminiscent (in $\mathbb{R}^2$) of the oscillations of the jumping droplets themselves (in fact \emph{Nelder-Mead} is sometimes also called the ``amoeba method'').
-Very little is known about the convergence properties of the \emph{Nelder-Mead} algorithm in its classical form for non smooth objective functions (\hl{[Price and Coope, 2003]}), except that in general it doesn't satisfy the properties required for convergence by other direct search algorithms: that the simplex remains uniformly non-degenerate, and that some form of ``sufficient'' descent condition for function values at the vertices is required at each iteration.
+It uses only-function calls and expands or contracts the simplex according to the function values at its vertices in a way visually reminiscent (in $\mathbb{R}^3$) of the oscillations of the jumping droplets themselves (in fact \emph{Nelder-Mead} is sometimes also called the ``amoeba method'').
+Very little is known about the convergence properties of the \emph{Nelder-Mead} algorithm in its classical form for non-smooth objective functions \cite{price_convergent_2002}, except that in general it doesn't satisfy the properties required for convergence by other direct search algorithms: that the simplex remains uniformly non-degenerate, and that some form of ``sufficient'' descent condition for function values at the vertices is required at each iteration.
 Scaling can help solve convergence problems and improve numerical stability.
-We precondition the optimization problem by minimizing $\ln(\chi^2)$, and using a naive scaling (scaling variables such that their magnitudes $\sim 1$) of our constraints by their initial guesses.
+We precondition the optimization problem by minimizing $\ln(\chi^2)$, and using a naive scaling (scaling variables such that their magnitudes $\sim \mathcal{O}(1)$) of our constraints by their initial guesses.
 Here is goal is to make the problem equally sensitive to steps in any direction.
@@
 The convergence history of the parameter MLE using \emph{Nelder-Mead} for a single drop jump experiment is shown in Figure \ref{fig:convergence}.
+Results of the parameter estimation are shown in Figures \ref{fig:trajectories}, \ref{fig:inverse_problem}.
 
-\begin{figure}[htb]
+\begin{figure}[h]
     \centering
@@
 
-\subsection{Smoothing}
-All optimization methods, including \emph{Nelder-Mead}, whether explicit or implicitly follow gradients towards an optimum.
-In a parameter estimation problem, if we approximate these gradients by finite differences, then the noise manifests itself as amplification of the roughness in the hyper-response surface.
-Gradient based optimizers do poorly in these situations because they tend to converge to local minima.
-While so called gradient free algorithms offer an improvement in this regard, speed of convergence and the quality of the MLE is improved by smoothing the objective function.
-This is equivalent to smoothing the underlying dataset.
-
-Our choice of smoothing approach depends principally on the nature of the errors in the dataset.
-The sources of error include misalignment of the camera, error in the fiduciary length scale, perspective due to objects (subject or reference scale) being out of the photographic plane, and various errors arising in the digitization process (including the difference between the thresholded ellipse fitted centroid and the true centroid of the non-ellipse drop centroid).
-Some of these errors are systematic in origin and introduce consistent biases into the data (e.g.
-coherent spectral sources, rather than truly stochastic noise).
-Data smoothing does little to help systematic errors in that they are usually of lower frequency than the signal.
-Random errors, by contrast, are assumed to have a Gaussian distribution (by the central limit theorem), and are independent of the signal (which inherently results from a deterministic process).
-
-We experimented with a variety of filters implemented in the \verb|scipy.signal| \emph{SciPy} module on a representative set of trajectory data; these methods include 1D Gaussian convolution, Wiener, Butterworth, and Savitsky-Golay filters.
-Qualitatively comparing these smoothing methods (by hand tuning filter orders and window sizes) we find that we loose too many data points in the smoothing process, large amplitudes are overly smoothed by repeated filtering passes, or there are significant end effects for most of these methods.
-A comparison of these smoothing approaches on a representative trajectory data set are shown in Figure \ref{fig:y_filtered}.
-
-\begin{figure}
+\newpage
+\begin{figure}[h]
     \centering
-    \input{../figures/y_filtered.pgf}
-       \caption{The underlying signal is `noisy', due partially to deterministic errors in determining the centroid position.
-These deterministic errors are largely due to droplet oscillations, especially the rapidly damped higher harmonics which do not have azimuthal symmetry.
-There is also Gaussian error in the ellipse fitting due to thresholding and noise in the video itself.
-We see that 1D Gaussian convolution and Wiener filters suffer from significant end effects.
-At this scale Butterworth and Savistsky-Golay filters are nearly indistinguishable.}
-      \label{fig:y_filtered}
+    \resizebox{\textwidth}{!}{\input{../figures/jump_matrix.pgf}}
+    \caption{A series of filtered droplet trajectories arranged by increasing apoapse.
+The blue dots represent either the beginning and end of the experiment, or points at which the droplet is either coming into, or leaving contact with the surface.}
+    \label{fig:trajectories}
 \end{figure}
-
-\begin{figure}
+\newpage
+\begin{figure}[h]
     \centering
-    \input{../figures/dy_filtered.pgf}
-    \caption{Comparing the first derivatives of the Butterworth and Savitsky-Golay filters we see that the Butterworth filter also suffers from a slight end effect.
-This implies that the optimization will find a different optima of the likelyhood depending on which type of filter is used.\label{fig:dy_filtered}}
+    \resizebox{\textwidth}{!}{\input{../figures/inverse_problem.pgf}}
+    \caption{A series of droplet trajectories showing the results of the parameter estimation.
+The trajectories are shown only up to the apoapse of the first bounce.
+The red lines show the ODE solution with given the MLE parameter vector.
+$\chi^2$ goodness-of-fit varies between $1 \times 10^{-5}$ and $1 \times 10^{-8}$ with the better fit occurring typically for the droplets with the lowest apoapses.}
+    \label{fig:inverse_problem}
 \end{figure}
-
-\begin{figure}
-    \centering
-    \input{../figures/power_spectra.pgf}
-    \caption{The power spectra has a peak at 1 Hz, which is the droplet trajectory parabola itself, and smaller peaks in the kHz range corresponding to various noise frequencies.
-The Savitsky-Golay and Butturworth filters seem to have the least distortion of the power spectra of the true signal.
-Both also do a good job of attenuating the noise at the 2 kHz peak.
-\label{fig:power}}
-\end{figure}
-
-The Savitsky-Golay, and Butterworth filters both produce fairly smooth derivatives as can be seen in Figure \ref{fig:dy_filtered}; but the small window-size needed for Butterworth filter tends to also produce a noticeable end effect.
-The Savitsky-Golay filter essentially uses a moving-window based on local least-squares polynomial approximations.
-It was shown that fitting a polynomial to a set of input samples and then evaluating the resulting polynomial at a single point within the approximation interval is equivalent to discrete convolution with a fixed impulse response \hl{[Savitsky, 1964]}.
-A beneficial property of this kind of low-pass filter is their tendency to maintain waveform amplitudes, and so they are attractive in applications having noisy signals with sharply pointed waveforms such as ultrasound or synthetic aperture radar \hl{[Schafer, 2011]}.
-Because Savitsky-Golay is a Finite Impulse Response (FIR) filter it requires data points to be equally spaced; to accommodated this we interpolate points between the small gaps which sometime occur in the tracking results from image analysis.
-We use a moving window size slightly smaller than the length of the current bounce in a drop jump data set.
-The windows are piecewise defined by partitioning the data set into a series of individual bounces (the dataset is sliced at minima identified after an initial rough smoothing pass, using the \verb|scipy.signal.argrelextrema()| function).
-The Savitsky-Golay polynomial order is 4.
-To understand how these filters differ it is useful to look at their frequency response.
-In Fourier space, convolution becomes a multiplication, and we can understand what a filter does by looking at which frequencies it lets pass through.
-We can do this using a Discrete Fourier Transform (though it is worth noting that our signal is not truly periodic).
-The power spectra for these same data are shown in Figure \ref{fig:power}.
+\newpage
 
@@
 This, we hope, makes the specter of an over fitted model less frightening, but does convert our unconstrained optimization problem to an constrained one which raises special difficulties of its own, which we discuss below.
-
-We're interested in the variance and co-variance as a means to determine the quality if the parameter estimate.
-The $\left( i, j \right)$-th element of the matrix $\sigma (\mathbf{x}, \mathbf{y})$ is equal to the covariance $\mbox{cov}(X_i, Y_j)$ between the $i$-th scalar component of $\mathbf{x}$ and the $j$-th scalar component of $\mathbf{Y}$.
-Here the concept of error bars in linear correlation associated with a covariance matrix are not suitable.
-We might try to generalize the idea of confidence intervals to a multidimensional space, but usually it will be hard to describe the surface of the (smallest) hyper-volume containing 90\% of the probability in just a few numbers.
-The situation is worse if the probability density function has several maxima.
-However we notice that
-\[ \left[\sigma^2 \right]_{ij} = -\left[ \left( \nabla \nabla \mathcal{L}\right)^{-1}\right]_{ij} = 2 \left[ \nabla \nabla \left( \chi^2\right)\right]_{ij}^{-1} = -\left[H^{-1} \right]_{ij}\]
-where $H$ refers to the Hessian matrix and $\left[\sigma^2 \right]_{ij}$ is the covariance matrix $C$.
-The issue of identifiability is especially fraught for non-linear, black box type problems were it is difficult to explicitly evaluate the Hessian.
-The likelihood function (and thus the posterior probability density function) are defined completely by the optimal solution $\mathbf{x}$ and the second derivative of $\mathcal{L}$ at the maximum, which corresponds to the covariance matrix $C$.
-The standard errors (marginal variances) are the square roots of the diagonal of the covariance matrix.
-Our relative errors thus produced are extremely small ($> 1 \%$).
-The Hessian matrix must be negative definite for $\mathcal{L}$ to have a maximum at $\mathbf{x_0}$.
-We can use the condition number
-\[ \mbox{cond} (A) = \frac{\mbox{max}[\mbox{eig}(A)]}{\mbox{min}[\mbox{eig}(A)]} \]
-as a means to evaluate to stability of our problem. We find typical condition numbers $\sim \mathcal{O}(10^{27})$ which indicate the problem is strongly ill-conditioned near the mimima $\mathbf{x_0}$.
 
@@
 
-Despite their wide use in parameter estimation, there is very little known about convergence properties of \emph{Nelder-Mead}.
-The iterative procedure may thus converge very slowly near the optimum, unless the Hessian is "well-conditioned", i.e., the condition number is near one.
-However, if parameter estimates are highly correlated among themselves, the Hessian matrix is near-singular and its inversion is either impossible or involves significant numerical error.
-Posteriori verification of the results is crucial to bound the identifiability of the parameter estimation problem, yet it has not be done yet.
-\hl{[Ref]} suggests verification by generation of Monte Carlo data sets.
+We're interested in the variance and co-variance as a means to determine the quality if the parameter estimate.
+The $\left( i, j \right)$-th element of the matrix $\sigma (\mathbf{x}, \mathbf{y})$ is equal to the covariance $\mbox{cov}(X_i, Y_j)$ between the $i$-th scalar component of $\mathbf{x}$ and the $j$-th scalar component of $\mathbf{y}$.
+Here the concept of error bars in linear correlation associated with a covariance matrix are not suitable.
+We might try to generalize the idea of confidence intervals to a multidimensional space, but it is likely difficult to describe the surface of the (smallest) hyper-volume containing 90\% of the probability with just a few numbers.
+The situation becomes worse if the probability density function has several maxima.
+However, there is another approach to find the covariance matrix [ref]
+\[ \left[\sigma^2 \right]_{ij} = -\left[ \left( \nabla^2 \mathcal{L}\right)^{-1}\right]_{ij} = 2 \left[ \nabla^2 \left( \chi^2\right)\right]_{ij}^{-1} = -\left[H^{-1} \right]_{ij}\]
+where $H$ refers to the Hessian matrix and $\left[\sigma^2 \right]_{ij}$ is the covariance matrix $C$.
+The issue of identifiability is especially fraught for non-linear, black box type problems were it is difficult to explicitly evaluate the Hessian.
+The likelihood function (and thus the posterior probability density function) are defined completely by the optimal solution $\mathbf{x}$ and the second derivative of $\mathcal{L}$ at the maximum, which corresponds to the covariance matrix $C$.
+The standard errors (marginal variances) are the square roots of the diagonal of the covariance matrix.
+The Hessian matrix must be negative definite for $\mathcal{L}$ to have a maximum at $\mathbf{x_0}$.
+We obtain an approximate Hessian using the approach suggested in Nelder's original paper, by fitting quadratics to the simplex vertices and midpoints \cite{nelder_simplex_1965}\cite{spendley_sequential_1962}.
+We can use the condition number
+\[ \mbox{cond} (H) = \frac{\mbox{max}[\mbox{eig}(H)]}{\mbox{min}[\mbox{eig}(H)]} \]
+to make a qualitative assesment of the stability of the problem.
+We find typical condition numbers $\sim \mathcal{O}(10^{27})$.
+In fact, in many cases our Hessian is not negative definite, or invertible at the minmia $\mathbf{x}_0$, which implies negative values of the variances (which is impossible).
+These issues indicate the problem is extremely ill-conditioned near the mimima $\mathbf{x_0}$.
+Given that the parameter estimates are highly colinear, it is unsuprising that the Hessian matrix is near-singular and its inversion is either impossible or involves significant numerical error.
+Posteriori verification of the results is crucial to bound the identifiability of the parameter estimation problem, but it remains as future work.
+Several sources suggest senstivity analysis of the parameter estimates by generation of synthetic Monte Carlo data sets as a means of establishing identifiability \cite{bevington_data_1969}\cite{jaqaman_linking_2006}.
 
-\begin{figure}[h]
-    \centering
-    \resizebox{\textwidth}{!}{\input{../figures/jump_matrix.pgf}}
-    \caption{A series of filtered droplet trajectories arranged by increasing apoapse.
-The blue dots represent either the beginning and end of the experiment, or points at which the droplet is either coming into, or leaving contact with the surface.}
-    \label{fig:trajectories}
-\end{figure}
-
-\begin{figure}[h]
-    \centering
-    \resizebox{\textwidth}{!}{\input{../figures/inverse_problem.pgf}}
-    \caption{A series of droplet trajectories showing the results of the parameter estimation.
-The trajectories are shown only up to the apoapse of the first bounce.
-The red lines show the ODE solution with given the MLE parameter vector.
-$\chi^2$ goodness-of-fit varies between $1 \times 10^{-5}$ and $1 \times 10^{-8}$ with the better fit occurring typically for the droplets with the lowest apoapses.}
-    \label{fig:inverse_problem}
-\end{figure}
-
+\printbibliography
 \end{document}

### 2018-01-25 doc/manuscript/results.tex
draft

@@
 
+\let\pgfimageWithoutPath\pgfimage 
+\renewcommand{\pgfimage}[2][]{\pgfimageWithoutPath[#1]{../figures/#2}}
+
+\usepackage[
+backend=biber,
+style=phys,
+sorting=none
+]{biblatex}
+\addbibresource{thesis.bib}
+
 \begin{document}
@@
 \doublespacing
-\section{Overview}
-\begin{itemize}
-\item We found the distribution of mostly likely experimental net charges for a population of the droplets jumped in low-gravity.
-We found the charge to be a function of droplet volume and surface potential of the dielectric substrate.
-A two-ways T-test with a charge distribution determined by a corollary experiment suggests that the droplet charge is induced by the electric field (rather than through contact charging on the PTFE layer).
-
-\item The bounce dynamics are controlled by a dimensionless ratio of electrostatic force to inertia. The dielectrophoretic force plays a very small role when droplets have net charge in a DC field.
-
-\item Using the unique capabilities of the low-gravity environment we obtained data on dimensionless contact time and coefficients of restitution at very low Ohnesorge numbers for a range of electric Bond numbers.
-Despite strong electric fields (20-30 $kV/cm$) we found little evidence for wetting transitions due to excession of a critical pressure (the ``Fakir impalement'').
-There is no obvious trend in dimensionless contact time or coefficient of restitution with electric Bond number.
-
-\item Jump velocities are more strongly damped for relatively small droplet volumes in the presence of the electric fields than was shown by Attari \emph{et.
-al.}.
-This may be evidence for electrowetting paradoxically enhancing the effect of contact angle hysteresis pinning on sharp corners.
-(How does this tie into the coefficients of restitution problem?)
-
-\item By scale arguments and perturbation of solutions to the equations of motion we find several simple rules of thumb in droplet ``escape velocity'' of impacts, length scales and time scales for returns.
-\end{itemize}
-
+\section{Charge Estimates}
+We found the distribution of mostly likely experimental net charges for a population of the droplets jumped in low-gravity.
+A covariance plot of the model variables is shown in Figure \ref{fig:scatter}.
+The multicollinear dependence of charge on droplet surface area, $A$, and the characteristic electric field, $E_0$, is evident.
+Assuming the main effect is the interaction between charge and electric field, a Robust Least Squares model fit $q \sim kAE_0$ (using the Python \verb|statsmodels.formula.api.RLM| function), with the non-linear transformation $A = V_d^{2/3}$, found that $k=5.01 \times 10^{-11} \pm  2.85 \times 10^{-11}$ with $R^2 = 0.946$.
+This model uses Huber's T norm, median absolute scaling, and H1 covariance estimation.
+A contour plot showing the estimated droplet free charge as a function of $V_d$ and $\varphi_s$ is shown in Figure \ref{fig:charge}.
+\begin{figure}[htb]
+    \centering
+    \resizebox{12cm}{!}{\input{../figures/scatter.pgf}}
+    \caption{A simple EMA plot.\label{fig:scatter}}
+\end{figure}
 \begin{figure}[htb]
@@
 
+A two-ways T-test comparison of charge distributions between the droplet bounce experiment and a corollary experiment with zero electric field at the time of droplet deposition on the superhydrophobic surface suggests that the droplet charge is induced by the electric field, rather than through contact charging on the PTFE layer ($t = 5.11, p = 0.0002$).
+The T-test informs us that the charge distribution  are about 5 times more different from each other as they are within each other, and there is a 0.02$\%$ probability that this result happened by chance.
+This corollary experiment is documented in Appendix \ref{sec.drop_charge}.
+
+The model $q \sim kAE_0$ is incidentally very similar to the classical solution for the surface charge density of a half-spherical conductor with a field induced dipole \cite{david_j._griffiths_introduction_1999}
+\begin{eqnarray*}
+q &=& 3 \epsilon_0 E_0 \int_A \cos \theta dA \\
+&=& 3 \pi^{1/3} 6 \left(6 V_d \right)^{2/3} \epsilon_0 E_0 \int^{4 \pi/2}_{\pi / 2} \cos \theta d\theta \\
+&=& k E_0 V_d^{2/3}
+\end{eqnarray*}
+with $k \approx 1.3 \times 10^{-10}$.
+This is also of a similar form to the charge found by Takamatsu and coauthors for droplets falling from a grounded nozzle in an external electric field \cite{takamatsu_theoretical_1981}
+\[q = 4 \pi \epsilon_0 \beta E_0 R_d^2 \]
+with $\beta \approx 2.63$.
+
+\section{Scale Quantities}
+The dielectrophoretic force plays a very small role when droplets have net charge in a DC field; the condition to neglect the DEP force was satisfied for all experiments in the dataset.
+Dimensional droplet apoapses scale closely with $\mathbb{E}\mbox{u}$ as seen in Figure \ref{fig:series_s_eu}.
+The relative magnitudes of the simulated forces felt by the droplets is shown in Figure \ref{fig:forces}.
+Forces acting on the drops vary in magnitude between $\mathcal{O}(10^{-6})-\mathcal{O}(10^{-4})$ N.
+We see that, of the drops in the experimental dataset only the two with the largest $\mathbb{E}\mbox{u}$, $\mathbb{E}\mbox{u} \sim \mathcal{O}(1)$ could appropriately be said to be in the inertial electro-viscous regime.
+In all other cases image forces are much stronger than drag.
+For these drops $\mathbb{E}\mbox{u} \gg 1/8 \pi$, and are likely on escape trajectories.
+The image forces themselves rapidly become small compared to Coulomb forces for drops with apoapses $\mbox{max}\left( y\right) \gtrapprox L$, thus it is reasonable to claim that for intermediate drops Coulomb force scales as inertia, and we can neglect the effects of drag and image forces.
+
 \begin{figure}[htb]
     \centering
-    \input{../figures/series.pgf}
-    \caption{A simple EMA plot.\label{fig:series}}
+    \input{../figures/series_s_eu.pgf}
+    \caption{Droplet trajectories as a function of $\mathbb{E}\mbox{u}$.\label{fig:series_s_eu}}
+\end{figure}
+\begin{figure}[htb]
+    \centering
+    \resizebox{14cm}{!}{\input{../figures/forces.pgf}}
+    \caption{Simulated forces acting on the droplet. Experiments are shown by order of increasing apoapse.\label{fig:forces}}
+\end{figure}
+
+In the non-dimensional trajectories with short-time scaling shown in Figure \ref{fig:series_s_ds}, we see that the trajectory apoapses are consistently $\mathcal{O}(1)$, but most trajectories overshoot their characteristic time scale (which predicts returns at $\bar{t}  =2$ to the first order).
+We also observe that that $\mathbb{E}\mbox{u}$ is not typically a small number in this regime, imperiling our use of asymptotic estimates in this regime.
+We can perhaps gain some insight by comparing the asymptotic estimate for return times to the scaled experiemental return times.
+We see in Figure \ref{fig:times} that the long-time scaled non-dimensional time of first bounce in the experiment $t_b / t_c$, compares poorly to the asymptotic estimate for returns $t_f$ as $\mathbb{E}\mbox{u}_+$ becomes large.
+This is very much as we'd expect, but it is also unfortunate; for small $\mathbb{E}\mbox{u}$ the asymptotic length scale could be used to improve the characteristic length scale by $t_a = t_c t_f$.
+We also notice a two-tailed effect in the data; for the small $\mathbb{E}\mbox{u}$ droplets, the long-time scaling distorts the return times considerably.
+\begin{figure}[htb]
+    \centering
+    \input{../figures/series_s_ds.pgf}
+    \caption{Non-dimensional trajectories with the short-time scaling.\label{fig:series_s_ds}}
 \end{figure}
@@
     \centering
-    \resizebox{14cm}{!}{\input{../figures/forces.pgf}}
-    \caption{A simple EMA plot.\label{fig:forces}}
+    \input{../figures/times.pgf}
+    \caption{.\label{fig:times}}
 \end{figure}
+
+The covariance of $\mathbb{I}\mbox{m}$ with $\mathbb{E}\mbox{u}$ is shown in Figure \ref{fig:dnumbs}.
+Predictably, there is quite strong correlation between the dimensionless groups.
+We also see that $\mathbb{I}\mbox{m} < 1$ for all drops.
+Using an OLS regression, we find the model $\mathbb{I}\mbox{m} \sim (0.012 \pm 0.003) \mathbb{E}\mbox{u} + (0.212 \pm 0.036) $ with $R^2 =0.59$.
+\begin{figure}[htb]
+    \centering
+    \input{../figures/dnumbs.pgf}
+    \caption{.\label{fig:dnumbs}}
+\end{figure}
+
+Finally we show several trajectories in the long-time scaled regime in Figure \ref{fig:series_l_ds}.
+\begin{figure}[htb]
+    \centering
+    \input{../figures/series_l_ds.pgf}
+    \caption{Non-dimensional trajectories with the long-time scaling as a function of ${\mathbb{E}\mbox{u}}_+$.\label{fig:series_l_ds}}
+\end{figure}
+We should note that there are several kinds of systematic error that influence our data.
+We assume that droplet translate purely along the central axis of the electric field, but in practice, despite the improvement in surface charge density uniformity produced by corona charging, there are still local areas of especially high charge density.
+In principle, this kind of error should become small for droplets which are far enough away from the charge distribution, that the geometry of the charge distribution disappears, and the electric field looks like that due to a point charge.
+Another form of error is in the initial velocity as it appears in $\mathbb{E}\mbox{u}$.
+Because we usually lose the first few frames of video due to camera shake transients at the start of the low-gravity experiment, we will consistently underestimate $U_0$ because the droplet will already have decelerated significantly during that period of time.
+The primary sources of random error are the effect of contact line hysteresis on the droplet initial velocity, and of the variance in the MLE parameter estimates.
+\newpage
+
+\section{Impact Dynamics \hl{[placeholder section]}}
+Using the unique capabilities of the low-gravity environment we obtained data on dimensionless contact time and coefficients of restitution at very low Ohnesorge numbers for a range of electric Bond numbers.
+Despite strong electric fields (20-30 $kV/cm$) we found little evidence for wetting transitions due to excession of a critical pressure (the ``Fakir impalement'').
+There is no obvious trend in dimensionless contact time or coefficient of restitution with electric Bond number.
+
+Jump velocities are more strongly damped for relatively small droplet volumes in the presence of the electric fields than was shown by Attari \emph{et.
+al.}.
+This may be evidence for electrowetting paradoxically enhancing the effect of contact angle hysteresis pinning on sharp corners.
+(How does this tie into the coefficients of restitution problem?)
 
@@
     \input{../figures/contact.pgf}
-    \caption{A simple EMA plot.\label{fig:contact}}
+    \caption{.\label{fig:contact}}
 \end{figure}
@@
     \input{../figures/restitution.pgf}
-    \caption{A simple EMA plot.\label{fig:restitution}}
+    \caption{.\label{fig:restitution}}
 \end{figure}
@@
 \appendix
-
 \section{\\Droplet Charge} \label{sec.drop_charge}
@@
 
+\printbibliography
 \end{document}

### 2018-01-25 doc/manuscript/theory.tex
draft

@@
 If we consider the charged dielectric surface of our experiments to be a square sheet of charge lying in the $xz$-plane with width $L$, the symmetry of the problem happily lets us obtain the $y$-component of the electric field $\mathbf{E}$ by direct integration.
-In particular it is easy to constuct the electric field due to a finite plane of charge by supoerposition of the electric fields of a series of line charges.
+In particular it is easy to constuct the electric field due to a finite plane of charge by superposition of the electric fields of a series of line charges.
 By symmetry the electric field points along the $y$-axis; for a point along the $y$-axis the position vector is $\mathbf{r} = \left( x^2 + y^2 \right)^{1/2} \hat{\mathbf{r}}$ to the center of a line charge in the $xz$-plane.
@@
 
-The equation of motion is non-linear, non-homogenous and is best solved numerically, but nevertheless we are curious if we can obtain approximate solutions to the equation analytically using perturbation methods.
-This is aided by non-dimensionalizing the governing equations, and seeing if any dimensionless groups exist, and whether any are particualy small or large, and whether any fortuitous opportunities for simplifcation appear.
+The equation of motion is non-linear, non-homogeneous and is best solved numerically, but nevertheless we are curious if we can obtain approximate solutions to the equation analytically using perturbation methods.
+This is aided by non-dimensionalizing the governing equations, and seeing if any dimensionless groups exist, and whether any are particularly small or large, and whether any fortuitous opportunities for simplification appear.
 Introducing the scaled variables
@@
  \bar{t} = \frac{t}{t_c}, \hspace{10 mm} \bar{y} = \frac{y}{y_c}, \end{equation}
-where $y_c$ and $t_c$ are characteristic length and time scales respectively, and using the cooridnate transformation $y(0) - R = 0$, the governing equation becomes
+where $y_c$ and $t_c$ are characteristic length and time scales respectively, and using the coordinate transformation $y(0) - R = 0$, the governing equation becomes
 \begin{eqnarray}
 & \bar{y}'' = - \frac{1}{2} \frac{C_D \rho A y_c}{m} \bar{y}'^2
-- \frac{q E_0 t_c^2}{m y_c} \bar{E} 
+- \frac{q E_0 t_c^2}{m y_c} \bar{E} ( \bar{y} ) 
 - \frac{k q^2 t_c^2}{16 \pi \epsilon_0 R^2 m y_c} \left( \frac{y_c}{R} \bar{y} + 1 \right)^{-2}, & \nonumber \\
@@
 
-In the limit of small $y$ and $t$ we expect intertia to scale as Coulombic and image force.
+In the limit of small $y$ and $t$ we expect inertia to scale as Coulombic and image force.
 In this limit we can approximate the electric field as the constant, $E_0$.
-One possible characteristic lengthscale is $y_c \sim R_d$, however this ultimately is a poor choice.
+One possible characteristic length scale is $y_c \sim R_d$, however this ultimately is a poor choice.
 With $y_c \sim U_0 t_c$ and picking $t_c$ such that Coulombic force is $\mathcal{O}(1)$, the intrinsic scales become
@@
 
-We prefer the approach with the greatest physical simplicity, fewest Pi terms, and that has homogenous initial conditions. We choose Case 1, where the intrinsic scales are given by
+We prefer the approach with the greatest physical simplicity, fewest Pi terms, and that has homogeneous initial conditions. We choose Case 1, where the intrinsic scales are given by
 \[ t_c \sim \frac{R_d^2}{L^2} \frac{4 \pi m U_0}{q E_0}, \hspace{5mm} y_c \sim \frac{R_d^2}{L^2} \frac{4 \pi m U_0^2}{q E_0}.
@@
 \end{eqnarray}
-where we call $\mathbb{D}\mbox{g}$ the drag number, $\mathbb{D}\mbox{g} \equiv \frac{C_D \rho_a}{\rho_l}$ and $\mathbb{E}\mbox{u}_+ = 4 \pi \frac{R_d^2}{L^2} \mathbb{E}\mbox{u}$.
+where we call $\mathbb{D}\mbox{g}$ the drag number, $\mathbb{D}\mbox{g} \equiv \frac{C_D \rho_a}{\rho_l} = \mathbf{\Pi}_1 {\mathbb{E}\mbox{u}}_+^{-1}$ and $\mathbb{E}\mbox{u}_+ = 4 \pi \frac{R_d^2}{L^2} \mathbb{E}\mbox{u}$.
 
@@
 The trajectory reduces to the classical $\mathcal{O}(1)$ solution for small values of $\alpha$.
-It should be noted that despite what is implied by these plots $\alpha$ is not neccisarily completely independent of $\epsilon$, as they share $q$, and $E_0$ as common factors, $U_0 \sim R_d^2$, and $m \sim R_d^3$.}
+It should be noted that despite what is implied by these plots $\alpha$ is not necessarily completely independent of $\epsilon$, as they share $q$, and $E_0$ as common factors, $U_0 \sim R_d^2$, and $m \sim R_d^3$.}
     \label{fig:short_times}
@@
 Again, the trajectory seemingly reduces to the classical $\mathcal{O}(1)$ solution for small values of of $\epsilon$.
-We also note that the effect of drag is very slight, despite the fact that it appears explicity in the $\mathcal{O}(1)$ solution; the apoapse is very nearly equal to half the characteristic length scale.
-In practical terms this linearizing effect of small $\beta$ may dissapear if the fluid density is much less than that of water, as in our experiements.
+We also note that the effect of drag is very slight, \hl{despite the fact that it appears explicitly in the $\mathcal{O}(1)$ solution [it does not]}; the apoapse is very nearly equal to half the characteristic length scale.
+In practical terms this linearizing effect of small $\beta$ may disappear if the fluid density is much less than that of water, as in our experiments.
 
-By again appying a regular perturbation to the asymptotic solution with the expansion
+By again applying a regular perturbation to the asymptotic solution with the expansion
 \[ \bar{t} \sim \bar{t}_0 + \epsilon \bar{t}_1 + \epsilon^2 \bar{t}_2 \ldots \epsilon^n\bar{t}_n  
@@
 \end{figure}
-
-We see that as $\epsilon$ grows to be no longer small, the time-of-flight grows rapidly, but this behaviour appears to have an asymptote at a certain critical velocity as $\mathcal{O}({\mathbb{E}\mbox{u}}_+) \rightarrow \mathcal{O}(1)$; this is an electrostatic escape velocity, $U_e$.
+We see that as $\epsilon$ grows to be no longer small, the time-of-flight grows rapidly, but this behavior appears to have an asymptote at a certain critical velocity as $\mathcal{O}({\mathbb{E}\mbox{u}}_+) \rightarrow \mathcal{O}(1)$; this is an electrostatic escape velocity, $U_e$.
 We can find the escape velocity by solving a modified version of the equation of motion,

### 2018-01-25 doc/manuscript/manuscript.tex
paper edits

@@
 \centering %\vspace*{-10ex}
-{\large \textsf{\textbf{Droplet Electro-Bouncing in Low-Gravity}}}
+{\large \textsf{\textbf{Drop Electro-Bouncing in Low-Gravity}}}
 
@@
 \noindent
-We investigate the dynamics of spontaneous jumps of water droplets from electrically charged superhydrophobic dielectric surfaces during a sudden step reduction in gravity level.
+We investigate the dynamics of spontaneous jumps of water droplets from electrically charged superhydrophobic dielectric substrates during a sudden step reduction in gravity level.
 In the brief free-fall environment of a drop tower, with a non-homogeneous external electric field (with strengths ~0.39-2.36 kV/cm) arising due to dielectric surface charges, body forces acting on the jumped droplets are primarily supplied by polarization stress and Coulombic attraction instead of gravity.
@@
 We show a simple model for the phenomenon, its scaling, and asymptotic estimates for droplet time of flight.
-The droplet net charge, estimated to be on the order of $1 \times 10^{-9}$ C, is field induced rather than by contact charging at the (PTFE coated) hydrophobic interface.
+The droplet trajectories are controlled primarily by the dimensionless electrostatic Euler number $\mathbb{E}\mbox{u}$, which is a ratio of inertial to electrostatic forces.
+For ${\mathbb{E}\mbox{u}}_+ \gg 1/8 \pi$ droplets escape the electric field.
+The droplet net charge, estimated to be on the order of $1 \times 10^{-9}$ C, is field-induced rather than by contact charging at the (PTFE coated) hydrophobic interface.
 In 1-g, for Weber numbers $>$ 0.4, impact recoil behavior on a super-hydrophobic surface is normally dominated by damping from contact line hysteresis.
-However, at the low Bond and Ohnesorge numbers occurring in free-fall, the droplet impact dynamics additionally include electrohydrodynamic surface wettability effects.
+However, for the low Bond and Ohnesorge numbers occurring in free-fall, the droplet impact dynamics additionally include electrohydrodynamic surface wettability effects.
 This is qualitatively discussed in terms of trends in coefficients of restitution and dimensionless contact time.
@@
 
-\emph{To Mom, Laura, and the DDT team.}\\
+\emph{To Mom, Laura, and the DDT team}\\
 \vspace*{\fill}
@@
 
-This work was supported primarily by NASA Cooperative Agreement NNX12A047A.
+This work was supported by NASA Cooperative Agreement NNX12A047A.
 I am also greatly indebted to Andrew Greenberg for his frequent and sage technical advice, and to Joe Shields for his assistance with drop tower experiments.
@@
 Our terrestrially born intuition about how liquids flow is easily confounded in a low-gravity environment.
-This should come as little surprise, as we are creatures evolved at the bottom of a steep gravity well; gravity is natural to us.
-However when the magnitude of the gravity body-force becomes small, other forces come into play in fluid dynamics which are otherwise negligible, relatively speaking, under normal circumstances in 1-g.
-This 1-g cognitive bias leads to a plethora of problems which are both trivially easy to solve in 1-g, and which despite decades of study continue to elude solutions in a low-gravity context.
-One example of these problems is the so-called ``phase separation'' problem of separating a gas phase from a multi-phase flow (or the reverse case), without the aid of gravitational buoyancy.
-Sans buoyancy otherwise mundane activities such as venting a gas or settling a liquid in a tank become problematic \cite{petrash_controlling_1964}.
-Trapped bubbles can vapor lock ECLSS (Environmental Control and Life Support), power, or propulsion systems \cite{jenson_passive_2014}.
+This should come as little surprise, as we are creatures evolved at the bottom of a gravity well; gravity is natural to us.
+However when the magnitude of gravitational body forces become small, other forces come into play in fluid dynamical problems which are otherwise negligible under normal circumstances in 1-g.
+Our 1-g cognitive bias then leads to a plethora of problems which are both simultaneously trivially easy to solve in 1-g, and which despite decades of study continue to elude solutions in a low-gravity context.
+One example of these problems is the so-called ``phase separation'' problem of separating a gas phase from a multi-phase flow (or the reverse case), without the aid of buoyancy due to gravity.
+Sans buoyancy, otherwise mundane activities such as venting a gas or settling a liquid in a tank become problematic \cite{petrash_controlling_1964}.
+Trapped bubbles can vapor lock life support, power, or propulsion systems \cite{jenson_passive_2014}.
 Issues of phase separation have so bedeviled human endeavors in space that an entire Apollo Saturn 1B mission (AS-203) was earmarked to study them \cite{hastings_[saturn_1965}.
-This problem has for some time motivated a quest for substitute body forces, and the present work follows in that august tradition.
-
-Considering the scope of this problem of poor low-gravity intuition, we would profit by identifying a scale to quantify how wrong our intuition is.
+This problem has for some time motivated a quest for substitute body forces, and the present work follows in that well-worn tradition.
+
+A solid beginning to rectifying our problem of poor low-gravity intuition, would be to quantify how wrong our intuition is.
 First, let's clear up a common misnomer about the state of ``zero-gravity''.
-The theory of general relativity is based on the fundamental equivalence of gravity and acceleration.
-There is no known way to determine whether one is in gravity-free space or free-falling in a gravitational field (or conversely whether or not we are uniformly accelerating, or standing at rest in a gravitational field).
+The theory of general relativity is based on a fundamental equivalence of gravity and acceleration.
+By measuring acceleration alone, one cannot determine whether one is in gravity-free space or free-falling in a gravitational field (or conversely whether or not one is uniformly accelerating, or standing at rest in a gravitational field).
 This is sometimes called the equivalence principle of general relativity (e.g.
-the equivilence of gravitational and inertial mass).
-In theoretical terms a zero-g experiment performed in a drop tower on the surface of the Earth is equivalent to the same experiment performed in the nearly gravity-free deep space between galaxies, despite the fact that the drop tower itself is in a 1-g gravity field.
-At the orbital altitude of the International Space Station (ISS) the gravity level is still nearly 90\% of its value at sea-level on Earth, but the astronauts aboard ISS feel weightlessness because they are free-falling.
-In a practical sense there is never true zero-g, even in the aforementioned dark space between galaxies, as there are always small, but nonetheless, measurable forces to accelerate any body.
-For instance in low-Earth orbit, accelerations due to drag in the tenuous outer atmosphere are on the order of $1 \times 10^{-6}$ g, hence the term ``microgravity''.
-This small acceleration provides an ersatz gravity, but there are also other forces present.
+the equivalence of gravitational and inertial mass).
+In theoretical terms, a zero-g experiment performed in a drop tower on the surface of the Earth is equivalent to the same experiment performed in the nearly gravity-free deep space between galaxies, despite the fact that the drop tower itself is enveloped in a 1-g gravity field.
+At the orbital altitude of the International Space Station (ISS) the gravity level is still nearly 90\% of its value at sea-level on Earth, but the astronauts aboard ISS feel weightlessness because they are in free-fall.
+In a practical sense true zero-g does not exit anywhere in the universe as there are always small, but nonetheless, measurable forces which can accelerate any massive body.
+For instance in low-Earth orbit, accelerations due to aerodynamic resistance in the tenuous outer atmosphere are on the order of $1 \times 10^{-6}$ g (from hence comes the term ``microgravity'').
+This small drag acceleration provides some ersatz gravity, but there are also other forces present.
 Foremost of these are capillary forces.
 
-Capillary forces are due to the cumulative effect of a large number of very short range molecular interactions and in a 1-g context are usually quite weak, relatively speaking.
-However, in a low-gravity environment these are nearly the only forces present, and are therefore strong in a relative sense.
-In comparing the relative magnitudes of gravity and the unusually strong capillary force we arrive at a useful figure of merit for assessing how wrong our fluid mechanical intuition is likely to be in a low-gravity context.
+Capillary forces are due to the cumulative effects of a large number of very short range molecular interactions and in a 1-g context are usually quite weak, relatively speaking.
+However, in a low-gravity environment other forces are so weak that the capillary forces becomes extraordinarily strong in a relative sense.
+In comparing the relative magnitudes of gravity and the capillary force we arrive at our figure of merit for assessing how wrong our fluid mechanical intuition is likely to be in a low-gravity context.
 This figure of merit is the Bond number dimensionless group
-\[ \mathbb{B}\mbox{o} \equiv \frac{g R^2 \Delta \rho}{\gamma} 
-\]
-where $g$ is the acceleration, $R$ is the interfacial radius of curvature, $\Delta \rho$ is the difference in densities across the interface (which simplifies to $\rho$, for large $\Delta \rho$, as in the case of a air-water interface), and where $\gamma$ is the surface tension.
+\[ \mathbb{B}\mbox{o} \equiv \frac{g R^2 \Delta \rho}{\gamma}, 
+\]
+where $g$ is the acceleration, $R$ is the characteristic interfacial length scale, $\Delta \rho$ is the difference in densities across the interface (which simplifies to $\rho$, for large $\Delta \rho$, as in the case of a air-water interface), and where $\gamma$ is the surface tension.
 In cases where $\mathbb{B}\mbox{o}$ is small, a liquid is effectively in low-gravity regardless of the nominal local gravity level.
 Very small droplets ($R < 1$ mm), for instance, are in low-gravity for all intents and purposes and have nearly spherical shapes.
-Contrarily, in a space environment in cases where $R$ becomes large, such as with the case of large diameter spacecraft propellant tanks then $ \mathbb{B}\mbox{o} \gg 1$ even though the acceleration is small.
-As a corollary to this discussion we note that on the basis of dimensional similarity, we can accurately simulate the low-gravity fluid mechanics of large propellant tanks even in small drop towers simply by scaling dimensionless groups like the Bond number.
-
-As with surface tension, electrostatic forces also have useful applications as substitutes for gravity.
+Contrarily, for cases of large $R$ in a space environment, such as with large diameter spacecraft propellant tanks then $ \mathbb{B}\mbox{o} \gg 1$ even though the acceleration remains small.
+This is actually a quite useful result, for on the basis of dimensional similarity, it is possible to accurately simulate low-gravity fluid mechanics (say of large propellant tanks), even in small drop towers simply by scaling dimensionless groups like the Bond number.
+
+As with capillary forces, electrostatic forces have a multitude of applications as substitutes for gravity.
 Electrohydrodynamic (EHD) body forces have been suggested to combat thermal stratification of propellants under low-g conditions where bouyancy induced natural convection is very small \cite{blackmon_collection_1965}.
-In this case electro-convection is an analog of natural convection due to a dielectric permitivity gradient (as opposed to a fluid density gradient), which is a function of fluid temperature, in the presence of a body force field (in this case an electric field).
+In this case electro-convection is an analog of natural convection due to a fluid temperature dependent dielectric permitivity gradient (as opposed to a fluid density gradient), in the presence of a body force field: the electric field.
 The study also suggested applications in cryogenic tank vent screening, and in reducing heat transfer to cryogenic propellants (and thus boiloff losses) by dielectrophoretically positioning ullage vapors around the tank walls as a thermal barrier.
-EHD forces have been studied for enhancing boiling heat transfer by promotion of bubble detachment and prevention of dryout (again as an ersatz bouyancy) \cite{snyder_dielectrophoresis_2001} \cite{di_marco_influence_2003} \cite{marco_use_2012}.
+EHD forces have been studied for enhancing boiling heat transfer by promotion of bubble detachment and prevention of dryout, again as an ersatz bouyancy \cite{snyder_dielectrophoresis_2001} \cite{di_marco_influence_2003} \cite{marco_use_2012}.
 EHD heat pipes, which substitute an electrode structure for the capillary wicking structure of a conventional thermocapillary heat pipe can evade the wicking limit \cite{jones_electrohydrodynamic_1973}.
-These are restricted to the use of insulating dielectric liquids (which usually have relatively low thermal conductivity), but are highly robust against dryout, support active flow control, and have low viscous losses.
-Dielectrophoretic settling of cryogenic propellants (in both total and partial communication configurations), has been studied analytically in both static \cite{hurwitz_electrohydrodynamic_1966} and dynamic cases \cite{koval_dynamics_1967}, and in drop tower experiments \cite{fax_dielectrophoretic_1969}.
-EHD forces have also beeen suggested for low-g slosh baffling \cite{boretz_orbital_1970} \cite{petrash_use_1968} \cite{hurwitz_dielectrophoretic_1968}, and studied extensively for the mitigation of vapor pullthrough during tank emptying (and concomittent minimization of propellant residuals at burnout) in a series of experiments at the NASA Lewis (now Glenn) Research Center 2.2 s drop tower facillity \cite{berenyi_dielectrophoretic_1970}.
+These are restricted to the use of insulating dielectric liquids, which usually have relatively low thermal conductivity, but are highly robust against dryout, support active flow control, and have low viscous losses.
+Dielectrophoretic settling of cryogenic propellants, in both total and partial communication PMD configurations, has been studied analytically in both static \cite{hurwitz_electrohydrodynamic_1966} and dynamic cases 1967}, and in drop tower experiments \cite{fax_dielectrophoretic_1969}.
+EHD forces have also beeen applied to the low-g slosh baffling problem \cite{boretz_orbital_1970} \cite{petrash_use_1968} \cite{hurwitz_dielectrophoretic_1968}, and studied extensively for the mitigation of vapor pullthrough during tank draining, and concomittent minimization of propellant residuals at burnout, in a series of experiments at the NASA Lewis (now Glenn) Research Center 2.2 s drop tower facillity \cite{berenyi_dielectrophoretic_1970}.
 
 \section{Spontaneous Droplet Jump}
-Low-gravity droplet dynamics, and the dynamics and applications of the so-called spontaneous droplet jump, is an active area of study at the Portland State University Dryen Drop Tower labratory (DDT).
+Low-gravity phase separation, droplet dynamics, and the dynamics and applications of the so-called spontaneous droplet jump, is an active area of study at the Portland State University Dryen Drop Tower labratory (DDT).
 When a nonwetting, gravity dominated sessile droplet (e.g.
-a puddle), initially at rest in the Cassie-Baxter state undergoes a large step reduction in $\mathbb{B}\mbox{o}$ it will spontaneously jump away from the surface.
-The Cassie-Baxter state is a metastable non-wetting state on a textured surface, sometimes also known as the Fakir state.
-This was first observed experimentally by Kirko \emph{et al.} \cite{kirko_phenomenon_1970} in 1970 and later by Wollman \emph{et al.} in 2016 in a set of experiments conducted using a low-gravity drop tower \cite{wollman_more_2016}.
+a puddle), which is initially at rest on a surface in the Cassie-Baxter state suddenly undergoes a large step reduction in $\mathbb{B}\mbox{o}$ it will spontaneously jump away from the surface.
+The Cassie-Baxter state, sometimes also known as the Fakir state, is a metastable heterogenously non-wetting state on a textured surface characterized by the existance of a vapor-layer which seperates roughness features of the surface from the bottom of the droplet.
+The spontaneous droplet jump was first observed experimentally in the Soviet Union by Kirko \emph{et al.} \cite{kirko_phenomenon_1970} in 1970, and later by Wollman \emph{et al.} in 2016 in a set of experiments conducted using a low-gravity drop tower \cite{wollman_more_2016}.
 The kinetic energy of the jump is supplied by the defect in free surface energy as the new minimum energy surface equilibrium has approximately constant curvature.
 If the viscous energy losses by shear, and internal flows during roll up are neglected, as well as energy lost due to the hysteresis of the dynamic contact line, then the available kinetic energy is given by
-\[KE = SE_2 -SE_1 = [(\sigma A)_{gl} + (\sigma A)_{sg}]_2 - [(\sigma A)_{ls} + (\sigma A)_{gl} + (\sigma A)_{sg}]_1. \]
-
+\[KE = SE_2 -SE_1 = [(\sigma A)_{gl} + (\sigma A)_{sg}]_2 - [(\sigma A)_{ls} + (\sigma A)_{gl} + (\sigma A)_{sg}]_1, \]
+
+where the subscripts $_1$ and $_2$ denote the intial 1-g, and low-g surface energies.
+The motive force is due to the inertia of internal flows which occur as the interface deflects under the suddenely lessened $\mathbb{B}\mbox{o}$.
 The droplet `rolls up' as it jumps away from the surface due to radial motion of a capillary wave away from the contact line.
-The characteristic time scale of the rolling up scales as $t_j \sim R_p/U ~(\rho H R^2_p/\sigma)^{1/2}$ \cite{attari_puddle_2016}, which resembles the contact time, $\tau \approx 2.6(\rho R^3_d/\sigma)^{1/2}$ reported by Richard \emph{et al.} in 2002 for the related problem of droplets impacting hydrophobic surfaces in 1-g \cite{richard_surface_2002}.
-For droplets with radial symmetry and sufficiently high initial $\mathbb{B}\mbox{o}$ these waves coalesce as a shock leading to geysering and creation of satellite drops by the Rayleigh-Plateau breakup of the geyser.
-In the case of smaller jumping droplets, the capillary waves do not lead to geysering, and are viscously damped to varying degrees during the brief free-fall period of the drop tower.
-
-The spontaneous droplet jump phenomenon provides a useful window though which to study the dynamics of large-length scale capillary dominated droplets.
-The physics of such massive droplets (far beyond the 1-g millimetric capillary length scale) utterly defy terrestrial expectations about the ways in which liquid droplets `should' behave, and also are of critical practical importance in a space systems setting where large capillary length scale multiphase flows are common.
+The characteristic time scale of the rolling up scales as $t_j \sim R_p/U ~(\rho H R^2_p/\sigma)^{1/2}$ \cite{attari_puddle_2016}, which resembles the contact time, $\tau \approx 2.6(\rho R^3_d/\sigma)^{1/2}$ presented by Richard \emph{et al.} in 2002 for the related problem of droplets impacting hydrophobic surfaces in 1-g \cite{richard_surface_2002}.
+For droplets with radial symmetry and sufficiently high initial $\mathbb{B}\mbox{o}$ these waves coalesce as a shock, leading to geysering and creation of satellite drops by the Rayleigh-Plateau breakup of the geyser.
+In the case of smaller jumping droplets the capillary waves are gradually damped viscously.
+
+The physics of these relatively massive droplets (far beyond the 1-g millimetric capillary length scale) at once utterly defy terrestrial expectations about the ways in which liquid `should' behave, and also are of critical practical importance to space systems design where examples of such large capillary length scale multiphase flows are commonplace.
 
 \section{Droplet Electro-Bounce}
-During `rolling-up' under ideal conditions, the droplet jump phenomenon is governed by a balance of inertia and surface tension forces, and once aloft the droplet motion is nominally in a regime of pure drag, however other forces can again come into play.
-
-\emph{Occasionally we observe jumped droplets to decelerate and return to the superhydrophobic surface, rebounding multiple times after fashion of a rigid body bouncing on a surface under 1-g.
-The forces at work in this phenomenon are presumably electrostatic in origin.} This was unintended, but the phenomenon is interesting.
-Admittedly, there is a certain irony that this typical failure of low-gravity intuition come as any surprise to experienced low-gravity researchers.
+During the `rolling-up' of droplets under ideal conditions, the spontaneous jump phenomenon is governed by a balance of inertia and surface tension forces, and once aloft the droplet motion is nominally in a regime of pure drag, however other forces can again come into play.
+
+\emph{We have observed jumped droplets to occasionally decelerate and return to the superhydrophobic surface, rebounding multiple times after fashion of rigid body bouncing ounder 1-g.
+The forces at work in this phenomenon are presumably electrostatic in origin.} Though this was an unintended effect in our work on spontaneous droplet jump, but the phenomenon is interesting itself.
+There is a certain irony to this typical failure of low-gravity intuition (the effect of relatively tiny electrostatic forces becoming suddenly large in the absence of gravity), being as we are experienced low-gravity researchers who perhaps should know better.
 A time-lapsed composite image showing an example of the phenomenon is shown in Figure \ref{fig:bounce}.
@@
 \caption{The trajectory of a 0.5 mL droplet is captured in a composite image over a single bounce period ($\sim 1.25$ s).
-The surface potential of the superhydrophobic dielectric is $\varphi_s = 1.25 \pm 0.41$ kV.
+The surface potential of the superhydrophobic dielectric in this example is $\varphi_s = 1.25 \pm 0.41$ kV.
 \label{fig:bounce}}
@@
 \begin{itemize}
-\item We have observed droplet accelerations on the order of 10's of cm/s$^2$ in proximity to charged surfaces for a range of droplet volumes $V_d \approx$ 0.01- 0.5 mL.
-\item Droplets appear to be attracted to regions of high electric field.
-The horizontal (surface plane parallel) components of the droplet trajectory usually oscillate about their initial position during drops (except in cases of nearly pure 1-D vertical translation).
+\item Observed droplet (de-)accelerations are on the order of 10's of cm/s$^2$ for a range of droplet volumes $V_d \approx$ 0.03-0.5 mL.
+\item The droplets are attracted to regions of high electric field.
+The horizontal (surface plane parallel) components of the droplet trajectory usually oscillate about their initial position during the experiment (except in cases of nearly pure 1-D vertical translation).
 For especially small drops close to the spontaneous droplet jump limit ($V_d \sim$ 0.01 mL) the droplets do not jump, but translate across the surface in a hovering regime until either they reach a local maximum of the electric field, or until their motion is sufficiently damped by contact line hysteresis that pinning arrests their motion.
-\item Droplets appear to have net free charge. In cases of multiple simultaneous droplet jumps the droplets repel each other as they bounce or hover in orbital motion around regions of strong field.
+\item The droplets appear to have net free charge. In cases of multiple simultaneous droplet jumps the droplets repel each other as they bounce or hover in orbital motion around regions of high field.
 \item The magnitude of the droplet trajectory maxima (apoapses) appear to be related to the droplet volume (which affects their mass, and initial jump velocity, and thence their inertia), and to the electric field strength.
@@
 
-There are several potential origins of the electric charge responsible for this phenonenon.
+There are several possible origins of the electric charge which are ultimately responsible for this phenonenon.
 It is well known that water acquires free charge (usually positive) when in contact with certain polymers, especially polytetrafluoroethylene (PTFE) \cite{langmuir_surface_1938}, through a process called contact charging.
-The superhydrophobic surfaces used in the spontanous droplet jump experiments have thin PTFE coatings, and we observe that it is extremely easy to produce significant surface potentials ($\varphi_s \sim$ 100-500 V) by simply running streams of distilled water over them.
-A study of this water on PTFE contact charging phenomenon was done by Yatsuzuka \emph{et al.} \cite{yatsuzuka_electrification_1994}, who suggest this process results from formation of an electrical double layer formed by selective adsorption of ions at the polymer surface.
-They also found that the specific charge on the droplets in contact with the surface depends on their surface velocity and conductivity.
-New developments suggest that adsorption of $\mbox{OH}^-$ ions are the source of the double layer \cite{beattie_intrinsic_2006} \cite{strazdaite_water_2015}.
-This is the most likely accidental source of charge on the suphydrophobic surface.
-Given the large roughness (in the sense of the ratio of projected to actual surface area), of the superhydrophobic surfaces used in the experiment, and given that the droplets are initially in a Cassie-Baxter state, an electrically insulating air layer is maintained that prevents grounding of the droplets despite the large potential difference between them and and the surface charges.
-Ultimately it is this potential, in the energetic sense, that is responsible for the droplet bouncing motion we observe.
+PTFE, on the other hand, tends to readily acquire negative chage by contact with water.
+The superhydrophobic surfaces used in the spontanous droplet jump experiments have thin (nanometric) PTFE coatings, and we observe that it is extremely easy to produce significant surface potentials ($\varphi_s \sim$ 100-500 V) by simply flowing streams of distilled water over them.
+A study of this water on PTFE contact charging phenomenon was done by Yatsuzuka \emph{et al.} \cite{yatsuzuka_electrification_1994}, who suggest that this process results from formation of an electrical double layer driven by selective adsorption of ($\mbox{OH}^-$) ions at the polymer surface; other recent work strongly supports this hypothesis \cite{beattie_intrinsic_2006} \cite{strazdaite_water_2015}.
+Yatsuzuka \emph{et al.} also found that the specific charge on the droplets in contact with the surface depends on their both surface velocity and conductivity.
+This contact charge is the most likely accidental source of charge on the suphydrophobic surface.
+Given the large roughness, or the ratio of projected to actual surface area, of the superhydrophobic surfaces used in the experiment, and given that the droplets are initially in a Cassie-Baxter state, an electrically insulating air layer is maintained that prevents grounding of the droplets despite the large potential difference between them and and the surface charges.
+If this electrostatic potential is greater than the release of surface energy under the sudden change in $\mathbb{B}\mbox{o}$ (in the form of the droplet kinetic energy), we expect that the droplet will return to an equilibrium state on the charged surface (minimizing the potential).
 
 The source of the net free charge on the droplets is another issue.
-The droplet charge could also be due to this contact charging mechanism.
-For instance, in a 1996 paper, NASA flight engineer Don Pettit discusses the problem of flow induced charging of liquids in a low-gravity context, resulting ultimately from contact charging phenomenon \cite{pettit_donald_flow_????}.
+The droplet charge could of course also be due to the contact charging mechanism mentioned previously.
+For instance, in a 1996 paper, NASA flight engineer Don Pettit discusses the problem of low-gravity flow induced charging of liquids, resulting ultimately from contact charging phenomenon \cite{pettit_donald_flow_????}.
 Another mechanism for the droplet charge is field induced charging.
-Field induced charging occurs due to physical breakup of a conductor having a field induced dipole.
+Field induced charging occurs due to physical breakup of a conductor having a field induced dipole (e.g a physical seperation of charge).
 In our case this occurs when the droplet is deposited on the charged surface by a syringe.
@@
 Depending on the (highly-variable) electrical conductivity of the sillicon oil, and the material of the syringe used in the experiment, the charge could as easily be field induced as due to contact charging.
-Relatedly, in a series of informal, and somewhat whimsical experiments Pettit electrostatically orbited small water droplets around a triboelectrically charged PTFE knitting needle while aboard ISS during expedition 30/31 \cite{stevenson_electrostatic_2015}.
+Relatedly, in a series of informal, and somewhat whimsical experiments Pettit himself electrostatically orbited small water droplets around a triboelectrically charged PTFE knitting needle while aboard ISS during expedition 30/31 \cite{stevenson_electrostatic_2015}.
 Again, in this case, the droplet charge is very likely field induced.
@@
 \section{Applications}
-Study of the droplet electro-bounce phenomenon may have results which can be extended to useful applications in a space environment.
+This study of the droplet electro-bounce phenomenon may have results which can be extended to useful applications in a space environment.
 
@@
 \section{Overview of this Thesis}
-This work primarily concerns itself with development of a simple model to aid in design of future electrostatic disperse droplet phase separators. To that end this work encompasses:
+In this thesis we develop, and partly validate a simple model to aid in design of future electrostatic disperse droplet phase separators. To that end this work encompasses:
 \begin{enumerate}
-\item A simple mathematical model of droplet electro-bounce, its scale analysis, and asymptotic estimates for droplet apoapses and times-of-flight.
+\item A mathematical model of the droplet electro-bounce, its scale analysis, asymptotic estimates for droplet apoapses and times-of-flight.
 \item The results of a controlled experiment, where the effect of key independent variables droplet volume $V_d$, and dielectric surface charge density $\sigma$, on droplet trajectories is tested.
@@
 This section will develop a simple, 1-dimensional model of the dynamics of droplets dominated by electrostatic forces.
-Treating a droplet as a particle, with radius $R_d$, the  equation of motion of charged droplets center of mass as it translates vertically along the central axis of a finite square charged dielectric sheet is given by
+We treat a droplet as a particle, with radius $R_d$, which translates vertically along the central axis of a finite square charged dielectric sheet with initial velocity $U_0$.
+The equation of motion for this system is given by,
 \begin{equation}
@@
 The initial conditions are such that, when the $\mathbb{B}\mbox{o}$ is suddenly reduced at the start of the drop tower experiment, the droplet jumps with initial velocity $U_0$ from its 1-g resting position $R_d$ at $t=0$.
-The signs of the forces on the right side of Equation \ref{gov_eqn} indicate that they act in the opposite direction of the droplet motion.
-We need to specify models for the various forces in this equation to begin our analysis of the droplet dynamics.
-
-With the assumption of an intermediate range of Reynolds numbers $\mathbb{R}\mbox{e} \equiv \frac{2UR_d}{\nu}$, $1 \leq \mathbb{R}\mbox{e} \leq 5000 $ then the force of drag acting on the droplet will be quadratic,
+The signs of the forces on the right side of Equation \ref{gov_eqn} indicate that they act in opposition direction of the droplet motion.
+To stat to describe the droplet electro-bounce we must define models for each of the forces in this equation.
+
+At intermediate range of Reynolds numbers $\mathbb{R}\mbox{e} \equiv \frac{2UR_d}{\nu}$, $1 \leq \mathbb{R}\mbox{e} \leq 5000 $ the force of drag acting on the droplet will be quadratic such that,
 \begin{equation*}\label{drag_force}
@@
 where $C_D$ is the drag coefficient, $\rho$ is the density of the sorrounding fluid medium (air, in this case), and $A$ is the frontal area of the droplet.
-For this range of Reynolds numbers it is appropriate to approximate the drag coefficient by the well known Abraham correlation \cite{abraham_functional_1970}
+For this range of Reynolds numbers it is appropriate to approximate the drag coefficient by the well known Abraham correlation \cite{abraham_functional_1970},
 \[C_D = \frac{24}{9.06^2} \left( 1 + \frac{9.06}{\sqrt{\mathbb{R}\mbox{e}}} \right)^2 .\]
@@
 This characteristic time $\tau_e$ is also known as the relaxation time, and is a measure of how quickly the polarization of a dielectric responds to a change in electric field.
-Given the respective conductivity, and permittivity of extremely-pure water ($ \kappa \sim 80$, $\sigma_e = 18.2 \times 10^{6}$ $\Omega\mbox{cm}$) \cite{yatsuzuka_electrification_1994}, we estimate $\tau_e \approx 4 \times 10^{-6}$ s.
+Given the respective conductivity, and permittivity in the limiting case of extremely-pure water ($ \kappa \sim 80$, $\sigma_e = 18.2 \times 10^{6}$ $\Omega\mbox{cm}$) \cite{yatsuzuka_electrification_1994}, we estimate $\tau_e \approx 4 \times 10^{-6}$ s.
 The relaxation time for the common distilled water that is actually used in the droplet experiments is undoubtedly even shorted (due to the presence of solvated ions).
-Neglecting the effects of a electric double layer on hydration of ions (in the water or the ambient atmosphere) due to the reletively massive size of the droplets studied, then the assumption of small relaxation time further implies that the free charge present in the droplets will remain approximately constant during the typical time interval of a low-gravity experiment.
-
-Supposing that electrical forces acting on free charges and dipoles in a fluid are transferred directly to the fluid itself, then this overall electrical body force will be the the divergence of the Maxwell stress tensor $\tau_m $, by
+Neglecting the effects of a electric double layer on hydration of ions (in the water or the ambient atmosphere) due to the relatively massive size of the droplets studied, then the assumption of small relaxation time further implies that the free charge present in the droplets will remain approximately constant during the typical time interval of a low-gravity experiment.
+
+Supposing that electrical forces acting on free charges and dipoles in a fluid are transferred directly to the fluid itself, then this overall electrical body force will be the the divergence of the Maxwell stress tensor $\tau_m $,
 \[ \mathbf{F}_E = \nabla \cdot \tau_m = \nabla \cdot \left( \epsilon \epsilon_0 \mathbf{E} \mathbf{E} - \frac{1}{2} \epsilon \epsilon_0 \mathbf{E} \cdot \mathbf{E} \delta \right) ,\]
@@
 
-The classical Korteweg-Helmholtz force density formulation of the Maxwell stress tensor is usually expressed as \cite{melcher_continuum_????}
+The classical Korteweg-Helmholtz volumetric force density formulation of the Maxwell stress tensor is usually expressed as \cite{melcher_continuum_????}
 \begin{equation}\label{force_density}
@@
 \end{equation}
-The first term in this expression, equivalently written as $q\mathbf{E}$, is the well known Coulombic force or electrophoretic force, which arises from the presence of free charge in an external electric field.
+The first term in this expression, is the well known Coulombic force or electrophoretic force, which arises from the presence of free charge in an external electric field.
 We expect this term to dominate the electric force in a DC field.
@@
 
-It is common to approximate the polarization stress by idealizing the droplet as a simple dipole using the effective dipole moment method first suggested by Pohl in 1958 \cite{pohl_effects_1958}.
-This approach has been related back to the force density by the volumetric integration of the force density with the substitution of a Taylor series expansion of $\mathbf{E}$ in the limit of a small radial gradient of the field within the dielectric sphere \cite{wang_general_1997}.
+It is common to approximate the polarization stress by idealizing the droplet as a simple dipole using the effective dipole moment method first described by Pohl in 1958 \cite{pohl_effects_1958}.
+This approach has since been related back to the force density by the volumetric integration of the force density with the substitution of a Taylor series expansion of $\mathbf{E}$ in the limit of a small radial gradient of the field within the dielectric sphere \cite{wang_general_1997}.
 The DEP force is related to the dipole moment (induced or permanent) of polarizable media which has a tendency to align the dipole with the electric field.
 If there is a gradient in the field then for a finite separation of charge one end of the dipole will feel a stronger electric field than the other, resulting in a net force.
-Whether the force is positive or negative in the direction of the electric field gradient depends on the difference of dielectric permittivites between the fluids, rather than on the polarity of $\mathbf{E}$ itself.
+Whether the force is positive or negative in the direction of the electric field gradient depends on the difference of dielectric permittivites between the fluids, rather than on the polarity of $\mathbf{E}$.
 In principle an external electric field will tend to induce a dipole in a dielectric material, but if the field is spatially uniform there is no gradient in the field and the forces felt by the dipoles are symmetric and thus there is no net force.

### 2018-01-25 doc/manuscript/manuscript.tex
edits

@@
 
-\title{\textsf{\textbf{Droplet Electro-Bouncing in Low-Gravity}}}
+\title{\textsf{\textbf{Drop Electro-Bouncing in Low-Gravity}}}
 \vspace{-25mm}
@@
 In the brief free-fall environment of a drop tower, with a non-homogeneous external electric field (with strengths ~0.39-2.36 kV/cm) arising due to dielectric surface charges, body forces acting on the jumped droplets are primarily supplied by polarization stress and Coulombic attraction instead of gravity.
-This electric body force leads to a droplet bouncing behavior similar to well-known phenomena in 1-g, though occurring for much larger droplets ($\sim$ 0.5 mL).
+This electric body force leads to a droplet bouncing behavior similar to well-known phenomena in 1-$g_0$, though occurring for much larger droplets ($\sim$ 0.5 mL).
 We show a simple model for the phenomenon, its scaling, and asymptotic estimates for droplet time of flight.
@@
 The droplet net charge, estimated to be on the order of $1 \times 10^{-9}$ C, is field-induced rather than by contact charging at the (PTFE coated) hydrophobic interface.
-In 1-g, for Weber numbers $>$ 0.4, impact recoil behavior on a super-hydrophobic surface is normally dominated by damping from contact line hysteresis.
+In 1-$g_0$, for Weber numbers $>$ 0.4, impact recoil behavior on a super-hydrophobic surface is normally dominated by damping from contact line hysteresis.
 However, for the low Bond and Ohnesorge numbers occurring in free-fall, the droplet impact dynamics additionally include electrohydrodynamic surface wettability effects.
@@
 This should come as little surprise, as we are creatures evolved at the bottom of a gravity well; gravity is natural to us.
-However when the magnitude of gravitational body forces become small, other forces come into play in fluid dynamical problems which are otherwise negligible under normal circumstances in 1-g.
-Our 1-g cognitive bias then leads to a plethora of problems which are both simultaneously trivially easy to solve in 1-g, and which despite decades of study continue to elude solutions in a low-gravity context.
+However when the magnitude of gravitational body forces become small, other forces come into play in fluid dynamical problems which are otherwise negligible under normal circumstances in 1-$g_0$.
+Our 1-$g_0$ cognitive bias then leads to a plethora of problems which are both simultaneously trivially easy to solve in 1-$g_0$, and which despite decades of study continue to elude solutions in a low-gravity context.
 One example of these problems is the so-called ``phase separation'' problem of separating a gas phase from a multi-phase flow (or the reverse case), without the aid of buoyancy due to gravity.
@@
 the equivalence of gravitational and inertial mass).
-In theoretical terms, a zero-g experiment performed in a drop tower on the surface of the Earth is equivalent to the same experiment performed in the nearly gravity-free deep space between galaxies, despite the fact that the drop tower itself is enveloped in a 1-g gravity field.
+In theoretical terms, a zero-g experiment performed in a drop tower on the surface of the Earth is equivalent to the same experiment performed in the nearly gravity-free deep space between galaxies, despite the fact that the drop tower itself is enveloped in a 1-$g_0$ gravity field.
 At the orbital altitude of the International Space Station (ISS) the gravity level is still nearly 90\% of its value at sea-level on Earth, but the astronauts aboard ISS feel weightlessness because they are in free-fall.
@@
 
-Capillary forces are due to the cumulative effects of a large number of very short range molecular interactions and in a 1-g context are usually quite weak, relatively speaking.
+Capillary forces are due to the cumulative effects of a large number of very short range molecular interactions and in a 1-$g_0$ context are usually quite weak, relatively speaking.
 However, in a low-gravity environment other forces are so weak that the capillary forces becomes extraordinarily strong in a relative sense.
@@
 In cases where $\mathbb{B}\mbox{o}$ is small, a liquid is effectively in low-gravity regardless of the nominal local gravity level.
-Very small droplets ($R < 1$ mm), for instance, are in low-gravity for all intents and purposes and have nearly spherical shapes.
+Very small drops ($R < 1$ mm), for instance, are in low-gravity for all intents and purposes and have nearly spherical shapes.
 Contrarily, for cases of large $R$ in a space environment, such as with large diameter spacecraft propellant tanks then $ \mathbb{B}\mbox{o} \gg 1$ even though the acceleration remains small.
@@
 These are restricted to the use of insulating dielectric liquids, which usually have relatively low thermal conductivity, but are highly robust against dryout, support active flow control, and have low viscous losses.
-Dielectrophoretic settling of cryogenic propellants, in both total and partial communication PMD configurations, has been studied analytically in both static \cite{hurwitz_electrohydrodynamic_1966} and dynamic cases 1967}, and in drop tower experiments \cite{fax_dielectrophoretic_1969}.
+Dielectrophoretic settling of cryogenic propellants, in both total and partial communication PMD configurations, has been studied analytically in both static \cite{hurwitz_electrohydrodynamic_1966} and dynamic cases \cite{koval_dynamics_1967}, and in drop tower experiments \cite{fax_dielectrophoretic_1969}.
 EHD forces have also beeen applied to the low-g slosh baffling problem \cite{boretz_orbital_1970} \cite{petrash_use_1968} \cite{hurwitz_dielectrophoretic_1968}, and studied extensively for the mitigation of vapor pullthrough during tank draining, and concomittent minimization of propellant residuals at burnout, in a series of experiments at the NASA Lewis (now Glenn) Research Center 2.2 s drop tower facillity \cite{berenyi_dielectrophoretic_1970}.
 
-\section{Spontaneous Droplet Jump}
+\section{Spontaneous Drop Jump}
 Low-gravity phase separation, droplet dynamics, and the dynamics and applications of the so-called spontaneous droplet jump, is an active area of study at the Portland State University Dryen Drop Tower labratory (DDT).
@@
 The Cassie-Baxter state, sometimes also known as the Fakir state, is a metastable heterogenously non-wetting state on a textured surface characterized by the existance of a vapor-layer which seperates roughness features of the surface from the bottom of the droplet.
-The spontaneous droplet jump was first observed experimentally in the Soviet Union by Kirko \emph{et al.} \cite{kirko_phenomenon_1970} in 1970, and later by Wollman \emph{et al.} in 2016 in a set of experiments conducted using a low-gravity drop tower \cite{wollman_more_2016}.
+The spontaneous drop jump was first observed experimentally in the Soviet Union by Kirko \emph{et al.} \cite{kirko_phenomenon_1970} in 1970 for drops of mercury in HCl, and later by Wollman \emph{et al.} in 2016 for water drops in a set of experiments conducted using a low-gravity drop tower \cite{wollman_more_2016}.
 The kinetic energy of the jump is supplied by the defect in free surface energy as the new minimum energy surface equilibrium has approximately constant curvature.
-If the viscous energy losses by shear, and internal flows during roll up are neglected, as well as energy lost due to the hysteresis of the dynamic contact line, then the available kinetic energy is given by
-\[KE = SE_2 -SE_1 = [(\sigma A)_{gl} + (\sigma A)_{sg}]_2 - [(\sigma A)_{ls} + (\sigma A)_{gl} + (\sigma A)_{sg}]_1, \]
-
-where the subscripts $_1$ and $_2$ denote the intial 1-g, and low-g surface energies.
+If the energy losses by viscous and contact line dynamics are neglected, the available kinetic energy is given by
+\[KE_2 = SE_1 - SE_2= [(\sigma A)_{ls} + (\sigma A)_{gl} + (\sigma A)_{sg}]_1 - [(\sigma A)_{gl} + (\sigma A)_{sg}]_2, \]
+
+where the subscripts $_1$ and $_2$ denote the intial 1-$g_0$, and low-g surface energies.
 The motive force is due to the inertia of internal flows which occur as the interface deflects under the suddenely lessened $\mathbb{B}\mbox{o}$.
-The droplet `rolls up' as it jumps away from the surface due to radial motion of a capillary wave away from the contact line.
-The characteristic time scale of the rolling up scales as $t_j \sim R_p/U ~(\rho H R^2_p/\sigma)^{1/2}$ \cite{attari_puddle_2016}, which resembles the contact time, $\tau \approx 2.6(\rho R^3_d/\sigma)^{1/2}$ presented by Richard \emph{et al.} in 2002 for the related problem of droplets impacting hydrophobic surfaces in 1-g \cite{richard_surface_2002}.
-For droplets with radial symmetry and sufficiently high initial $\mathbb{B}\mbox{o}$ these waves coalesce as a shock, leading to geysering and creation of satellite drops by the Rayleigh-Plateau breakup of the geyser.
-In the case of smaller jumping droplets the capillary waves are gradually damped viscously.
-
-The physics of these relatively massive droplets (far beyond the 1-g millimetric capillary length scale) at once utterly defy terrestrial expectations about the ways in which liquid `should' behave, and also are of critical practical importance to space systems design where examples of such large capillary length scale multiphase flows are commonplace.
-
-\section{Droplet Electro-Bounce}
-During the `rolling-up' of droplets under ideal conditions, the spontaneous jump phenomenon is governed by a balance of inertia and surface tension forces, and once aloft the droplet motion is nominally in a regime of pure drag, however other forces can again come into play.
-
-\emph{We have observed jumped droplets to occasionally decelerate and return to the superhydrophobic surface, rebounding multiple times after fashion of rigid body bouncing ounder 1-g.
-The forces at work in this phenomenon are presumably electrostatic in origin.} Though this was an unintended effect in our work on spontaneous droplet jump, but the phenomenon is interesting itself.
+\hl{The characteristic time scale of the rolling up scales as} $t_j \sim R_p/U ~(\rho H R^2_p/\sigma)^{1/2}$ \cite{attari_puddle_2016}, which resembles the contact time, $\tau \approx 2.6(\rho R^3_d/\sigma)^{1/2}$ presented by Richard \emph{et al.} in 2002 for the related problem of drops impacting hydrophobic surfaces in 1-$g_0$ \cite{richard_surface_2002}.
+For drops with radial symmetry and sufficiently high initial $\mathbb{B}\mbox{o}$ inward radial capillary waves coalesce at the axis, leading to geysering and creation of satellite droplets by the Rayleigh-Plateau breakup of the geyser.
+In the case of smaller jumping drops the capillary waves are gradually damped by viscous forces.
+A time-lapsed composite photograph of spontaneous drop jump can be seen in Figure \ref{fig:nobounce}
+\begin{figure}[htb]
+\centering
+\includegraphics[width=0.75\textwidth]{drop_jump}
+\caption{The trajectory of a 0.2 mL drop is captured in a composite image over a period $\sim 0.67$ s at 120 fps. \label{fig:nobounce}}
+\end{figure}
+
+The physics of these relatively massive drops (far beyond the 1-$g_0$ millimetric capillary length scale) at once utterly defy terrestrial expectations about the ways in which liquid `should' behave, and also are of critical practical importance to space systems design where examples of such large capillary length scale multiphase flows are commonplace.
+
+\section{Drop Electro-Bounce}
+During the `rolling-up' of drops under ideal conditions, the spontaneous jump phenomenon is governed by a balance of inertia and surface tension forces, and once aloft the drop motion is nominally in a regime of pure drag, however other forces can again come into play.
+
+We have observed jumped drops to occasionally decelerate and return to the superhydrophobic surface, rebounding multiple times in the fashion of rigid bodies bouncing under 1-$g_0$.
+The forces at work in such situations are presumably electrostatic in origin.
+Though this was an unintended effect in our work on spontaneous drop jump, but the phenomenon is interesting itself.
 There is a certain irony to this typical failure of low-gravity intuition (the effect of relatively tiny electrostatic forces becoming suddenly large in the absence of gravity), being as we are experienced low-gravity researchers who perhaps should know better.
@@
 \includegraphics[width=0.75\textwidth]{bounce}
-\caption{The trajectory of a 0.5 mL droplet is captured in a composite image over a single bounce period ($\sim 1.25$ s).
+\caption{The trajectory of a 0.5 mL drop is captured in a composite image over a single bounce period ($\sim 1.25$ s).
 The surface potential of the superhydrophobic dielectric in this example is $\varphi_s = 1.25 \pm 0.41$ kV.
@@
 \begin{itemize}
-\item Observed droplet (de-)accelerations are on the order of 10's of cm/s$^2$ for a range of droplet volumes $V_d \approx$ 0.03-0.5 mL.
-\item The droplets are attracted to regions of high electric field.
-The horizontal (surface plane parallel) components of the droplet trajectory usually oscillate about their initial position during the experiment (except in cases of nearly pure 1-D vertical translation).
-For especially small drops close to the spontaneous droplet jump limit ($V_d \sim$ 0.01 mL) the droplets do not jump, but translate across the surface in a hovering regime until either they reach a local maximum of the electric field, or until their motion is sufficiently damped by contact line hysteresis that pinning arrests their motion.
-\item The droplets appear to have net free charge. In cases of multiple simultaneous droplet jumps the droplets repel each other as they bounce or hover in orbital motion around regions of high field.
-\item The magnitude of the droplet trajectory maxima (apoapses) appear to be related to the droplet volume (which affects their mass, and initial jump velocity, and thence their inertia), and to the electric field strength.
+\item Observed maximum drop (de-)accelerations are on the order of $\sim$30 cm/s$^2$ for a range of drop volumes $0.03 \lessapprox V_d \lessapprox 0.5$ mL.
+\item The drops are attracted to regions of high electric field.
+The horizontal (surface plane parallel) components of the drop trajectory usually oscillate about their initial position during the experiment (except in cases of nearly pure 1-D vertical translation).
+For especially small drops close to the spontaneous drop jump limit ($V_d \sim$ 0.01 mL) the drops do not jump, but translate across the surface in a rolling regime until either they reach a local maximum of the electric field, or until their motion is sufficiently damped by contact line hysteresis that pinning arrests their motion.
+\item The drops appear to have net free charge. In cases of multiple simultaneous drop jumps the drops repel each other as they bounce or roll in orbital motion around regions of high field.
+\item The magnitude of the drop trajectory maxima (apoapses) appear to be related to the drop volume, which affects their mass, and initial jump velocity, and thence their inertia, and to the electric field strength.
 \end{itemize}
@@
 There are several possible origins of the electric charge which are ultimately responsible for this phenonenon.
-It is well known that water acquires free charge (usually positive) when in contact with certain polymers, especially polytetrafluoroethylene (PTFE) \cite{langmuir_surface_1938}, through a process called contact charging.
+It is well known that water acquires positive free charge when in contact with certain polymers, especially polytetrafluoroethylene (PTFE) \cite{langmuir_surface_1938}, through a process called contact charging.
 PTFE, on the other hand, tends to readily acquire negative chage by contact with water.
-The superhydrophobic surfaces used in the spontanous droplet jump experiments have thin (nanometric) PTFE coatings, and we observe that it is extremely easy to produce significant surface potentials ($\varphi_s \sim$ 100-500 V) by simply flowing streams of distilled water over them.
-A study of this water on PTFE contact charging phenomenon was done by Yatsuzuka \emph{et al.} \cite{yatsuzuka_electrification_1994}, who suggest that this process results from formation of an electrical double layer driven by selective adsorption of ($\mbox{OH}^-$) ions at the polymer surface; other recent work strongly supports this hypothesis \cite{beattie_intrinsic_2006} \cite{strazdaite_water_2015}.
-Yatsuzuka \emph{et al.} also found that the specific charge on the droplets in contact with the surface depends on their both surface velocity and conductivity.
-This contact charge is the most likely accidental source of charge on the suphydrophobic surface.
-Given the large roughness, or the ratio of projected to actual surface area, of the superhydrophobic surfaces used in the experiment, and given that the droplets are initially in a Cassie-Baxter state, an electrically insulating air layer is maintained that prevents grounding of the droplets despite the large potential difference between them and and the surface charges.
-If this electrostatic potential is greater than the release of surface energy under the sudden change in $\mathbb{B}\mbox{o}$ (in the form of the droplet kinetic energy), we expect that the droplet will return to an equilibrium state on the charged surface (minimizing the potential).
-
-The source of the net free charge on the droplets is another issue.
-The droplet charge could of course also be due to the contact charging mechanism mentioned previously.
+The superhydrophobic surfaces used in the spontanous drop jump experiments have thin (nanometric) PTFE coatings, and we observe that it is extremely easy to produce significant surface potentials ($\varphi_s \sim$ 100-500 V) by simply flowing streams of distilled water over them.
+A study of this water on PTFE contact charging phenomenon was conducted by Yatsuzuka \emph{et al.} \cite{yatsuzuka_electrification_1994}, who suggest that this process results from formation of an electrical double layer driven by selective adsorption of ($\mbox{OH}^-$) ions at the polymer surface; other recent work strongly supports this hypothesis \cite{beattie_intrinsic_2006} \cite{strazdaite_water_2015}.
+Yatsuzuka \emph{et al.} also found that the specific charge on the drops in contact with the surface depends on their both surface velocity and conductivity.
+The contact charging mechanism is the most likely accidental source of charge on the suphydrophobic surfaces used in our work.
+Given the large roughness, or the ratio of projected to actual surface area, of the superhydrophobic surfaces used in the experiment, and given that the drops are initially in a Cassie-Baxter state, a somewhat electrically resistive air layer is maintained that reduces grounding of the drops despite the large potential difference between them and and the surface charges.
+If this electrostatic potential is greater than the release of surface energy under the sudden change in $\mathbb{B}\mbox{o}$ (in the form of the drop kinetic energy), we expect that the drop will return to an equilibrium state on the charged surface which minimizing the potential.
+
+The source of the net free charge on the drops is another issue.
+The drop charge could of course also be due to the contact charging mechanism mentioned previously.
 For instance, in a 1996 paper, NASA flight engineer Don Pettit discusses the problem of low-gravity flow induced charging of liquids, resulting ultimately from contact charging phenomenon \cite{pettit_donald_flow_????}.
-Another mechanism for the droplet charge is field induced charging.
-Field induced charging occurs due to physical breakup of a conductor having a field induced dipole (e.g a physical seperation of charge).
-In our case this occurs when the droplet is deposited on the charged surface by a syringe.
+Another mechanism for the drop charge is field-induced charging.
+Field-induced charging occurs due to physical breakup of a conductor having a field-induced dipole (e.g a physical seperation of charge).
+In our case this occurs when the drop is deposited on the charged surface by a syringe.
 The metal syringe needle tip, and the liquid in the syrigne itself are essentially a ground connection which is broken when the syringe is removed.
-Field induced charging is at work in the famous Kevin thunderstorm, and is applied in inkjet, and electrospay technologies (where in each case the breakup is by the Rayleigh-Plateau instability).
-Notably, in Pettit's discussion of contact charging of liquids in low-g, he remarks on accidental electrostatic ``hula-ing'' of sillicon oil droplets when ejected from a syringe in the vicinity of a highly-charged polymer surface during an experiment conducted aboard STS-5 by mission specialist Joseph Allen.
-Depending on the (highly-variable) electrical conductivity of the sillicon oil, and the material of the syringe used in the experiment, the charge could as easily be field induced as due to contact charging.
-Relatedly, in a series of informal, and somewhat whimsical experiments Pettit himself electrostatically orbited small water droplets around a triboelectrically charged PTFE knitting needle while aboard ISS during expedition 30/31 \cite{stevenson_electrostatic_2015}.
-Again, in this case, the droplet charge is very likely field induced.
+Field-induced charging is at work in the famous Kevin thunderstorm, and is applied in inkjet, and electrospay technologies, where in each case the breakup is by the Rayleigh-Plateau instability.
+Notably, in Pettit's discussion of contact charging of liquids in low-g, he remarks on accidental electrostatic `hula-ing' of silicone oil drops when ejected from a syringe in the vicinity of a highly-charged polymer surface during an experiment conducted aboard STS-5 by mission specialist Joseph Allen \cite{pettit_donald_flow_????}.
+Depending on the (highly-variable) electrical conductivity of the silicone oil, and the material of the syringe used in the experiment, the charge could arise just as easily by field-induction as by contact charging.
+Relatedly, in a series of informal, and somewhat whimsical experiments, Pettit himself electrostatically orbited small water drops around a triboelectrically charged PTFE knitting needle while aboard ISS during expedition 30/31 \cite{stevenson_electrostatic_2015}.
+Again, in this case, the drop charge is likely field-induced.
 
 \section{Applications}
-This study of the droplet electro-bounce phenomenon may have results which can be extended to useful applications in a space environment.
-
+This study of the drop electro-bounce phenomenon may have results which can be extended to useful applications in a space environment.
 External surfaces of spacecraft tend to become charged with time due to the space environment itself.
@@
 As previously noted, robust phase separation is critical to high reliability multiphase systems used in thermal control and life support.
-Active (but solid-state) phase seperation for ECLSS multiphase flows, espcially high void-fraction flows is a possible application of this work.
+Active (but solid-state) phase seperation for life support multiphase flows, espcially high void-fraction flows is a possible application of this work.
 Such flows pertain to dish washing, laundry, waste solids drying, food processing, the Sabatier CO$_2$ reaction, and possibly in vapor-compression cycle condensers.
@@
 Removal of satellite droplets produced during pippetting in wet-lab research outside of a glovebox environment aboard ISS has also been recently suggested as a application of the work \hl{[ref, personal discussion with NASA MSFC folk at ASGSR17 conference]}.
-Droplets can become spontaneously charged by contact with standard micropipette tips \cite{choi_spontaneous_2013}, and this free charge can possibly be leveraged for the purposes of phase separation in low-gravity.
+Drops can become spontaneously charged by contact with standard micropipette tips \cite{choi_spontaneous_2013}, and this free charge can possibly be leveraged for the purposes of phase separation in low-gravity.
 
 \section{Overview of this Thesis}
-In this thesis we develop, and partly validate a simple model to aid in design of future electrostatic disperse droplet phase separators. To that end this work encompasses:
+In this thesis we develop, and partly validate a simple model to aid in design of future electrostatic disperse drop phase separators. To this end the work encompasses:
 \begin{enumerate}
-\item A mathematical model of the droplet electro-bounce, its scale analysis, asymptotic estimates for droplet apoapses and times-of-flight.
-\item The results of a controlled experiment, where the effect of key independent variables droplet volume $V_d$, and dielectric surface charge density $\sigma$, on droplet trajectories is tested.
-\item Science of opportunity comprising experimental data on droplet impacts at very low Weber and Ohnesorge numbers, for varying levels of electrostatic Bond number. 
+\item A mathematical model of the drop electro-bounce, its scale analysis, asymptotic estimates for drop apoapses and times-of-flight.
+\item The results of a controlled experiment, where the effect of key independent variables drop volume $V_d$, and dielectric surface charge density $\sigma$, on drop trajectories is tested.
+\item Science of opportunity comprising experimental data on drop impacts at very low Weber and Ohnesorge numbers, for varying levels of electrostatic Bond number. 
 \end{enumerate}
@@
 \section{Forces and the Equation of Motion}
-This section will develop a simple, 1-dimensional model of the dynamics of droplets dominated by electrostatic forces.
-We treat a droplet as a particle, with radius $R_d$, which translates vertically along the central axis of a finite square charged dielectric sheet with initial velocity $U_0$.
+This section will develop a simple, 1-dimensional model of the dynamics of drops dominated by electrostatic forces.
+We treat a drop as a particle, with radius $R_d$, which translates vertically along the central axis of a finite square charged dielectric sheet with initial velocity $U_0$.
 The equation of motion for this system is given by,
@@
 \end{equation}
-where $m$ is the droplet mass, $y'' = \frac{d^2 y}{d t^2}$ is the droplet acceleration, $\mathbf{F}_D$ is the drag force, and $\mathbf{F}_E$ is the electrostatic force.
-The initial conditions are such that, when the $\mathbb{B}\mbox{o}$ is suddenly reduced at the start of the drop tower experiment, the droplet jumps with initial velocity $U_0$ from its 1-g resting position $R_d$ at $t=0$.
-The signs of the forces on the right side of Equation \ref{gov_eqn} indicate that they act in opposition direction of the droplet motion.
-To stat to describe the droplet electro-bounce we must define models for each of the forces in this equation.
-
-At intermediate range of Reynolds numbers $\mathbb{R}\mbox{e} \equiv \frac{2UR_d}{\nu}$, $1 \leq \mathbb{R}\mbox{e} \leq 5000 $ the force of drag acting on the droplet will be quadratic such that,
+where $m$ is the drop mass, $y'' = \frac{d^2 y}{d t^2}$ is the drop acceleration, $\mathbf{F}_D$ is the drag force, and $\mathbf{F}_E$ is the electrostatic force.
+The initial conditions are such that, when the $\mathbb{B}\mbox{o}$ is suddenly reduced at the start of the drop tower experiment, the drop jumps with initial velocity $U_0$ from its 1-$g_0$ resting position $R_d$ at $t=0$.
+The signs of the forces on the right side of Equation \ref{gov_eqn} indicate that they act in opposition direction of the drop motion.
+To stat to describe the drop electro-bounce we must define models for each of the forces in this equation.
+
+At intermediate range of Reynolds numbers $\mathbb{R}\mbox{e} \equiv \frac{2UR_d}{\nu}$, $1 \leq \mathbb{R}\mbox{e} \leq 5000 $ the force of drag acting on the drop will be quadratic such that,
 \begin{equation*}\label{drag_force}
@@
 \end{equation*}
-where $C_D$ is the drag coefficient, $\rho$ is the density of the sorrounding fluid medium (air, in this case), and $A$ is the frontal area of the droplet.
+where $C_D$ is the drag coefficient, $\rho$ is the density of the sorrounding fluid medium (air, in this case), and $A$ is the frontal area of the drop.
 For this range of Reynolds numbers it is appropriate to approximate the drag coefficient by the well known Abraham correlation \cite{abraham_functional_1970},
@@
 Given the respective conductivity, and permittivity in the limiting case of extremely-pure water ($ \kappa \sim 80$, $\sigma_e = 18.2 \times 10^{6}$ $\Omega\mbox{cm}$) \cite{yatsuzuka_electrification_1994}, we estimate $\tau_e \approx 4 \times 10^{-6}$ s.
-The relaxation time for the common distilled water that is actually used in the droplet experiments is undoubtedly even shorted (due to the presence of solvated ions).
-Neglecting the effects of a electric double layer on hydration of ions (in the water or the ambient atmosphere) due to the relatively massive size of the droplets studied, then the assumption of small relaxation time further implies that the free charge present in the droplets will remain approximately constant during the typical time interval of a low-gravity experiment.
+The relaxation time for the common distilled water that is actually used in the drop experiments is undoubtedly even shorted (due to the presence of solvated ions).
+Neglecting the effects of a electric double layer on hydration of ions (in the water or the ambient atmosphere) due to the relatively massive size of the drops studied, then the assumption of small relaxation time further implies that the free charge present in the drops will remain approximately constant during the typical time interval of a low-gravity experiment.
 
@@
 
-It is common to approximate the polarization stress by idealizing the droplet as a simple dipole using the effective dipole moment method first described by Pohl in 1958 \cite{pohl_effects_1958}.
+It is common to approximate the polarization stress by idealizing the drop as a simple dipole using the effective dipole moment method first described by Pohl in 1958 \cite{pohl_effects_1958}.
 This approach has since been related back to the force density by the volumetric integration of the force density with the substitution of a Taylor series expansion of $\mathbf{E}$ in the limit of a small radial gradient of the field within the dielectric sphere \cite{wang_general_1997}.
@@
 
-When the droplet is close to the dielectric surface, the free charge on the droplet will tend to induce polarization of the dielectric, perturbing the electric field.
-The polarization bound charge in the dielectric will be of the opposite sign of the free droplet charge and thus there will be a force of attraction.
+When the drop is close to the dielectric surface, the free charge on the drop will tend to induce polarization of the dielectric, perturbing the electric field.
+The polarization bound charge in the dielectric will be of the opposite sign of the free drop charge and thus there will be a force of attraction.
 This so-called image force is a correction to the Colomb force due to the external electric field only, and can be found by the method of images \cite{david_j._griffiths_introduction_1999}.
@@
 There is some physical intuition to support this conclusion as well.
-The dielectric displacement, $\mathbf{D} = \kappa \epsilon_0 \mathbf{E}$ of a water droplet in air is very high due to its large relative dielectric constant.
-This implies that the field strength within the droplet is about 2 orders of magnitude smaller than in the surrounding medium (which is essentially the same as a vacuum from a dielectric standpoint), thus it is not particularly inaccurate to model the dielectric volume of a droplet as a conductive shell (an equipotential), with zero field in its interior.
-As an aside, in treating the droplet as an ideal conductor we note that in our specific case the electrostatic force is not a body force \emph{per se} as the electric field is acting on charges on the surface of the conductor.
+The dielectric displacement, $\mathbf{D} = \kappa \epsilon_0 \mathbf{E}$ of a water drop in air is very high due to its large relative dielectric constant.
+This implies that the field strength within the drop is about 2 orders of magnitude smaller than in the surrounding medium (which is essentially the same as a vacuum from a dielectric standpoint), thus it is not particularly inaccurate to model the dielectric volume of a drop as a conductive shell (an equipotential), with zero field in its interior.
+As an aside, in treating the drop as an ideal conductor we note that in our specific case the electrostatic force is not a body force \emph{per se} as the electric field is acting on charges on the surface of the conductor.
 
@@
 \subsection{Inertial Electro-Viscous Limit}
-In the limit of large $y$ and $t$ we expect droplet inertia to scale as Coulombic force and drag.
+In the limit of large $y$ and $t$ we expect drop inertia to scale as Coulombic force and drag.
 In this limit we approximate the electric field as $E \approx y_c^2 E_0 y^{-2}$.
@@
     \resizebox{1\textwidth}{!}{\input{../figures/short_times.pgf}}
-    \caption{Non-dimensional droplet trajectories for various values of $\mathbb{E}\mbox{u}=\epsilon$, $\mathbb{I}\mbox{m}=\alpha$.
+    \caption{Non-dimensional drop trajectories for various values of $\mathbb{E}\mbox{u}=\epsilon$, $\mathbb{I}\mbox{m}=\alpha$.
 The trajectory reduces to the classical $\mathcal{O}(1)$ solution for small values of $\alpha$.
@@
 \end{figure}
-These plots show a trend of decreasing time-of-flight (the time for the droplet to return to the origin, or complete a single ``bounce''), and height at apoapse with increasing values of the Image number $\alpha$.
+These plots show a trend of decreasing time-of-flight (the time for the drop to return to the origin, or complete a single ``bounce''), and height at apoapse with increasing values of the Image number $\alpha$.
 When $\alpha = 1$ the time of flight is exactly half of characteristic time scale in this regime.
@@
     \input{../figures/long_times.pgf}
-    \caption{Non-dimensional droplet trajectories for various values of $\mathbb{E}\mbox{u}=\epsilon$.}
+    \caption{Non-dimensional drop trajectories for various values of $\mathbb{E}\mbox{u}=\epsilon$.}
      \label{fig:long_times}
@@
 \[t_f = 2 + \epsilon \left(\frac{4}{3} - \frac{2 \beta}{3}\right) + \epsilon^{2} \left(\frac{4}{5} - \frac{4 \beta}{3} + \frac{2 \beta^{2}}{5}\right) + \mathcal{O}(\epsilon^3).\]
-Substituting the experimental value of $\beta$ we find the time-of-flight estimate for water droplets in air to be
+Substituting the experimental value of $\beta$ we find the time-of-flight estimate for water drops in air to be
 \begin{equation} \label{time_of_flight}
@@
     \input{../figures/drag.pgf}
-    \caption{$\mathcal{O}(\epsilon^3)$ asymptotic estimate of droplet time-of-flight as a function of $\epsilon = {\mathbb{E}\mbox{u}}_+$.}
+    \caption{$\mathcal{O}(\epsilon^3)$ asymptotic estimate of drop time-of-flight as a function of $\epsilon = {\mathbb{E}\mbox{u}}_+$.}
     \label{fig:drag}
@@
 We can find the escape velocity by solving a modified version of the equation of motion,
-\[ m u' = - \frac{q E_0}{y^2}, \]
-where $u = \frac{d y}{d t}$ is the droplet velocity. Integrating between the respective limits,
-\[m \int^{u(y)}_{U_0} u du = -q E_0 \int^y_{R_d} \frac{dy}{y^2} ,\]
+\[ m u' = - \frac{q E_0 y_c^2}{y^2}, \]
+where $u = \frac{d y}{d t}$ is the drop velocity. Integrating between the respective limits,
+\[m \int^{u(y)}_{U_0} u du = -q E_0 y_c^2 \int^y_{R_d} \frac{dy}{y^2} ,\]
 which has the solution
-\[ u(y) = \pm U_0 \left[1 + \frac{2q E_0}{m U_0^2} \left( \frac{1}{y} - \frac{1}{R_d} \right) \right]^{1/2}.
+\[ u(y) = \pm U_0 \left[1 + \frac{2q E_0 y_c^2}{m U_0^2} \left( \frac{1}{y} - \frac{1}{R_d} \right) \right]^{1/2}.
 \]
 This equation has an asymptotic velocity, $U_{\infty}$ at $y = \infty$ which is real if 
-\[ U_0 \geq  U_e = \sqrt{\frac{2 q E_0}{m R_d}},
-\]
-where $U_e$ is the escape velocity and $U_{\infty} = \sqrt{U_0^2 - U_e^2}$. The condition for the droplets to escape the electric field is then given by
+\[ U_0 \geq  U_e = y_c \sqrt{\frac{2 q E_0 }{m R_d}},
+\]
+where $U_e$ is the escape velocity and $U_{\infty} = \sqrt{U_0^2 - U_e^2}$. The condition for the drops to escape the electric field is then given by
 \begin{equation}\label{escape}
-{\mathbb{E}\mbox{u}}_+ > 1/8 \pi.
+{\mbox{B}^2 \mathbb{E}\mbox{u}}^3 > 1,
 \end{equation}
-Referring again to Figure \ref{fig:drag}, we suspect that there is perhaps a better choice of scaling available, as the time-of-flight estimate is not asymptotic at ${\mathbb{E}\mbox{u}}_+ = 1/8 \pi$.
-
-If the droplet escapes the electric field it will have a residual velocity $U_{\infty}$, and will be in a regime of pure inertia $\sim$ drag. The velocity will then decay as
+where $B^2= 8 \pi\frac{ R_d^2}{L^2}$ If the drop escapes the electric field it will have a residual velocity $U_{\infty}$, and will be in a regime of pure inertia $\sim$ drag.
+The velocity will then decay as
 \[
@@
 Mainly we are concerned about what parameters are important in electrostatic transport of relatively large (e.g.
-millimetric) droplets in low-gravity, and what the values of the respective dimensionless groups, namely $\mathbb{I}\mbox{m}$, $\mathbb{E}\mbox{u}$ and ${\mathbb{E}\mbox{u}}_+$ might be.
+millimetric) drops in low-gravity, and what the values of the respective dimensionless groups, namely $\mathbb{I}\mbox{m}$, $\mathbb{E}\mbox{u}$ and ${\mathbb{E}\mbox{u}}_+$ might be.
 To find typical vales of these parameters we used the following approach:
 \begin{enumerate}
-\item We observed spontaneous droplet jumps on charged dielectric super-hydrophobic surfaces under low-gravity conditions in a $2.1$ s drop tower, while varying the independent variables $V_d$, $\sigma$.
+\item We observed spontaneous drop jumps on charged dielectric super-hydrophobic surfaces under low-gravity conditions in a $2.1$ s drop tower, while varying the independent variables $V_d$, $\sigma$.
 However, this raises an interesting challenge; it is impractical to directly measure all of the key physical quantities that appear in the dimensionless groups at once in a drop tower experiment.
-In particular, determination of net droplet free electric charge $q$, is difficult (as high-input resistance electrometers, being notoriously fickle instruments, are not well suited to sudden 15-g decelerations).
-Schematic representations of the droplet jump, and of the droplet in the Cassie-Baxter 1-g initial state is shown in Figures \ref{fig:apparatus0} and \ref{fig:schematic}.
-\item Using high-speed video and image analysis software we captured the trajectories of the droplets. 
+In particular, determination of net drop free electric charge $q$, is difficult (as high-input resistance electrometers, being notoriously fickle instruments, are not well suited to sudden 15-g decelerations).
+Schematic representations of the drop jump, and of the drop in the Cassie-Baxter 1-$g_0$ initial state is shown in Figures \ref{fig:apparatus0} and \ref{fig:schematic}.
+\item Using high-speed video and image analysis software we captured the trajectories of the drops. 
 \item We solved the inverse problem to find the key parameters by maximizing a statistical likelihood function between an observed trajectory and the trajectory predicted by a dynamical model given that certain set parameters.
@@
  \includegraphics[width=0.75\textwidth]{../figures/schematic.pdf}
- \caption{A schematic representation of the droplet initial condition, resting on the superhydrophobic surface in the Cassie-Baxter state just prior to the drop tower experiment.
-The variables $q$, $\sigma$, and $V_d$ are the droplet net free charge, dielectric surface charge density, and droplet volume respectively.\label{fig:schematic}}
+ \caption{A schematic representation of the drop initial condition, resting on the superhydrophobic surface in the Cassie-Baxter state just prior to the drop tower experiment.
+The variables $q$, $\sigma$, and $V_d$ are the drop net free charge, dielectric surface charge density, and drop volume respectively.\label{fig:schematic}}
 \end{figure}
@@
  \includegraphics[width=0.75\textwidth]{../figures/apparatus0.pdf}
- \caption{A schematic representation of a droplet electro-bounce experiment with labeled characteristic time and length scales, \hl{$t_c$, $y_c$} shown.
+ \caption{A schematic representation of a drop electro-bounce experiment with labeled characteristic time and length scales, \hl{$t_c$, $y_c$} shown.
 Also shown are the dimensions of the superhydrophobic electret substrate.\label{fig:apparatus0}}
@@
 The experiment then experiences approximately $1 \times 10^{-6}$g of high quality free-fall for the 2.1s required for the rig/drag shield assembly to plummet to the bottom of drop tower 6 floors below.
-Single droplets of distilled water, in a range of volumes ($0.01 \leq R_d \leq 0.5$ mL), were very carefully deposited on the charged superhydrophobic surface using an grounded glass syringe with $\pm $1 $\mu$L accuracy, and then dropped in the drop tower.
+Single drops of distilled water, in a range of volumes ($0.01 \leq R_d \leq 0.5$ mL), were very carefully deposited on the charged superhydrophobic surface using an grounded glass syringe with $\pm $1 $\mu$L accuracy, and then dropped in the drop tower.
 Red dye was added to improve thresholding accuracy in trajectory digitization.
-Droplet trajectories were recorded using a \emph{Panasonic} HC-WX970 Camera, at 120 fps and and 1/3000s shutter speed.
+Drop trajectories were recorded using a \emph{Panasonic} HC-WX970 Camera, at 120 fps and and 1/3000s shutter speed.
 In a few cases where higher frame rates were needed a \emph{Nikon} 1 J1 camera with a 30mm telephoto lens was used, shooting at 400 fps.
@@
 Typical commerical electrets are Teflon type (PTFE) polymer films on the order of 10-50 $\mu$m thick with the charge being primarily real surface charge.
-Electrets have a plethora of applications, but most germanely they have been used in Electro-Wetting On Dielectric (EWOD) devices for low-voltage manipulation of small droplets \cite{wu_low-voltage_2010}.
+Electrets have a plethora of applications, but most germanely they have been used in Electro-Wetting On Dielectric (EWOD) devices for low-voltage manipulation of small drops \cite{wu_low-voltage_2010}.
 Real charge electrets can be produced by contact electrification, injection or deposition) of charge carriers by discharge or electron beam, ionizing radiation, or by frictional triboelectrification.
@@
 The surface charge density can be modulated during the experiment using the high-voltage DC-DC converter, which can re-polarize the dielectric substrate by means of an embedded electrode, and the resulting bound charge partially or fully neutralizes the electric field due to the surface ions deposited by corona charging of the electret.
-The high-voltage system is armed manually before the drop and is automatically safed by a high-voltage power switching relay, which switches the load across a 100 k$\Omega$ resistor when triggered by the resumption of 1-g conditions.
+The high-voltage system is armed manually before the drop and is automatically safed by a high-voltage power switching relay, which switches the load across a 100 k$\Omega$ resistor when triggered by the resumption of 1-$g_0$ conditions.
 The safing is set by an accelerometer pin-interrupt triggered microcontroller command.
@@
     \input{../figures/rig.pdf_tex}
-    \caption{The droplet electro-bounce experiment hardware mounted on a drop tower rig.\label{fig:rig}}
+    \caption{The drop electro-bounce experiment hardware mounted on a drop tower rig.\label{fig:rig}}
 \end{figure}
@@
     \input{../figures/hysteresis.pgf}
-       \caption{Hysteresis of the contact line plotted as a function of static contact angle and roll-off angle for $1$ mL droplets.\label{fig:hysteresis}}
+       \caption{Hysteresis of the contact line plotted as a function of static contact angle and roll-off angle for $1$ mL drops.\label{fig:hysteresis}}
 \end{figure}
@@
 Because environmental convection will tend to  maintain a gradient of these ions, sealing an electret in a container from the atmosphere will effectively halt this decay mechanism.
-Atmospheric humidity and water droplet condensation also significantly increase charge decay (presumably by reducing the surface resistence) \cite{haenen_characteristic_1975}.
+Atmospheric humidity and water drop condensation also significantly increase charge decay (presumably by reducing the surface resistence) \cite{haenen_characteristic_1975}.
 Examples of this decay can be seen in Figure \ref{fig:charge_decay} for differing numbers of dielectric lamina used in this experiment.
@@
 \section{Data Munging}
-Digitization of droplet trajectories requires several steps of post-processing.
+Digitization of drop trajectories requires several steps of post-processing.
 Video is first decomposed into a sequence of still images.
@@
 Each still is then split into its constituent RGB maps.
-In this case the green channel images contained the most information, so these were then globally thresholded using the Triangle algorithm to recover a map of the pixels corresponding to the droplet's approximate position in the original still.
-Ellipses are fitted to the pixel map stepping through the time series to determine the positions of the center of mass, and the semi-major and minor axes of the droplets during the drop.
+In this case the green channel images contained the most information, so these were then globally thresholded using the Triangle algorithm to recover a map of the pixels corresponding the approximate position of the drop in the original still.
+Ellipses are fitted to the pixel map stepping through the time series to determine the positions of the center of mass, and the semi-major and minor axes of the drops during the drop.
 Finally, a perspective correction is applied to the center-of-mass positions.
@@
 \section{Parameter Estimation}
-Using various scaling arguments we have gleaned from our simple model a series of non-dimensional numbers characteristic of droplet bounce apoapses and times of flight, but these dimensionless groups depend on a set of physical parameters.
+Using various scaling arguments we have gleaned from our simple model a series of non-dimensional numbers characteristic of drop bounce apoapses and times of flight, but these dimensionless groups depend on a set of physical parameters.
 Unfortunately not all of these parameters are physically practical to accurately measure by experiment.
-Droplet free charge $q$, in particular, could in principle be directly measured by collecting the charged drops in a faraday cup under low-g and measuring the change in capacitance of the cup using a very high input-resistance electrometer, but this is a problematic experiment to set up in a drop tower from a practical standpoint.
+Drop free charge $q$, in particular, could in principle be directly measured by collecting the charged drops in a faraday cup under low-g and measuring the change in capacitance of the cup using a very high input-resistance electrometer, but this is a problematic experiment to set up in a drop tower from a practical standpoint.
 The other state variables we can directly measure by experiment with varying levels of accuracy.
@@
 \begin{enumerate}
-\item Experimentally vary $V_d$, $\sigma$ and capture droplet trajectories using a high-speed camera.
-\item Digitize droplet trajectories by using automatic tracking of ellipse-fitted centers of mass on the thresholded video.
-\item Slice droplet trajectories by their bounce minima, and apply a smoothing filter.
-\item Extract the droplet charge (and other experimental parameters) by maximizing the log-likelihood of the data given the dynamical model and parameters, by varying the parameter vector using a direct search optimization.
+\item Experimentally vary $V_d$, $\sigma$ and capture drop trajectories using a high-speed camera.
+\item Digitize drop trajectories by using automatic tracking of ellipse-fitted centers of mass on the thresholded video.
+\item Slice drop trajectories by their bounce minima, and apply a smoothing filter.
+\item Extract the drop charge (and other experimental parameters) by maximizing the log-likelihood of the data given the dynamical model and parameters, by varying the parameter vector using a direct search optimization.
 \end{enumerate}
@@
 \]
-is the $\chi^2$ goodness-of-fit, $y_d = y_d(t)$ is a observation of droplet position at a point in time, and $y_G =  y_G(t, \mathbf{x})$ is the droplet position predicted by the solution to the equation of motion at time $t$, and $\sigma$ is the standard error of the position measurement.
+is the $\chi^2$ goodness-of-fit, $y_d = y_d(t)$ is a observation of drop position at a point in time, and $y_G =  y_G(t, \mathbf{x})$ is the drop position predicted by the solution to the equation of motion at time $t$, and $\sigma$ is the standard error of the position measurement.
 If the number of data points $n$, is small was can use the Poisson error $\sigma_d^2 = {y_G}$.
@@
        \caption{The underlying signal is `noisy', due partially to deterministic errors in determining the center of mass position.
-These deterministic errors are largely due to droplet oscillations, especially the rapidly damped higher harmonics which do not have azimuthal symmetry.
+These deterministic errors are largely due to drop oscillations, especially the rapidly damped higher harmonics which do not have azimuthal symmetry.
 There is also Gaussian error in the ellipse fitting due to thresholding and noise in the video itself.
@@
     \input{../figures/power_spectra.pgf}
-    \caption{The power spectra has a peak at 1 Hz, which is the droplet trajectory parabola itself, and smaller peaks in the kHz range corresponding to various noise frequencies.
+    \caption{The power spectra has a peak at 1 Hz, which is the drop trajectory parabola itself, and smaller peaks in the kHz range corresponding to various noise frequencies.
 The Savitsky-Golay and Butterworth filters seem to have the least distortion of the power spectra of the true signal.
@@
 \emph{Nelder-Mead} is based on the concept of a $N$-simplex, which generalizes a triangle into higher dimensions as a polytrope of $N + 1$ vertices in $N$ dimensions.
-It uses only-function calls and expands or contracts the simplex according to the function values at its vertices in a way visually reminiscent (in $\mathbb{R}^3$) of the oscillations of the jumping droplets themselves (in fact \emph{Nelder-Mead} is sometimes also called the ``amoeba method'').
+It uses only-function calls and expands or contracts the simplex according to the function values at its vertices in a way visually reminiscent (in $\mathbb{R}^3$) of the oscillations of the jumping drops themselves (in fact \emph{Nelder-Mead} is sometimes also called the ``amoeba method'').
 Very little is known about the convergence properties of the \emph{Nelder-Mead} algorithm in its classical form for non-smooth objective functions \cite{price_convergent_2002}, except that in general it doesn't satisfy the properties required for convergence by other direct search algorithms: that the simplex remains uniformly non-degenerate, and that some form of ``sufficient'' descent condition for function values at the vertices is required at each iteration.
@@
     \resizebox{\textwidth}{!}{\input{../figures/jump_matrix.pgf}}
-    \caption{A series of filtered droplet trajectories arranged by increasing apoapse.
-The blue dots represent either the beginning and end of the experiment, or points at which the droplet is either coming into, or leaving contact with the surface.}
+    \caption{A series of filtered drop trajectories arranged by increasing apoapse.
+The blue dots represent either the beginning and end of the experiment, or points at which the drop is either coming into, or leaving contact with the surface.}
     \label{fig:trajectories}
@@
     \resizebox{\textwidth}{!}{\input{../figures/inverse_problem.pgf}}
-    \caption{A series of droplet trajectories showing the results of the parameter estimation.
+    \caption{A series of drop trajectories showing the results of the parameter estimation.
 The trajectories are shown only up to the apoapse of the first bounce.
 The red lines show the ODE solution with given the MLE parameter vector.
-$\chi^2$ goodness-of-fit varies between $1 \times 10^{-5}$ and $1 \times 10^{-8}$ with the better fit occurring typically for the droplets with the lowest apoapses.}
+$\chi^2$ goodness-of-fit varies between $1 \times 10^{-5}$ and $1 \times 10^{-8}$ with the better fit occurring typically for the drops with the lowest apoapses.}
     \label{fig:inverse_problem}
@@
 \section{Charge Estimates}
-We found the distribution of mostly likely experimental net charges for a population of the droplets jumped in low-gravity.
+We found the distribution of mostly likely experimental net charges for a population of the drops jumped in low-gravity.
 A covariance plot of the model variables is shown in Figure \ref{fig:scatter}.
-The multicollinear dependence of charge on droplet surface area, $A$, and the characteristic electric field, $E_0$, is evident.
+The multicollinear dependence of charge on drop surface area, $A$, and the characteristic electric field, $E_0$, is evident.
 Assuming the main effect is the interaction between charge and electric field, a Robust Least Squares model fit $q \sim kAE_0$ (using the Python \verb|statsmodels.formula.api.RLM| function), with the non-linear transformation $A = V_d^{2/3}$, found that $k=5.01 \times 10^{-11} \pm  2.85 \times 10^{-11}$ with $R^2 = 0.946$.
 This model uses Huber's T norm, median absolute scaling, and H1 covariance estimation.
-A contour plot showing the estimated droplet free charge as a function of $V_d$ and $\varphi_s$ is shown in Figure \ref{fig:charge}.
+A contour plot showing the estimated drop free charge as a function of $V_d$ and $\varphi_s$ is shown in Figure \ref{fig:charge}.
 \begin{figure}[htb]
@@
 
-A two-ways T-test comparison of charge distributions between the droplet bounce experiment and a corollary experiment with zero electric field at the time of droplet deposition on the superhydrophobic surface suggests that the droplet charge is induced by the electric field, rather than through contact charging on the PTFE layer ($t = 5.11, p = 0.0002$).
+A two-ways T-test comparison of charge distributions between the drop bounce experiment and a corollary experiment with zero electric field at the time of drop deposition on the superhydrophobic surface suggests that the drop charge is induced by the electric field, rather than through contact charging on the PTFE layer ($t = 5.11, p = 0.0002$).
 The T-test informs us that the charge distribution  are about 5 times more different from each other as they are within each other, and there is a 0.02$\%$ probability that this result happened by chance.
@@
 
-The model $q \sim kAE_0$ is incidentally very similar to the classical solution for the surface charge density of a half-spherical conductor with a field induced dipole \cite{david_j._griffiths_introduction_1999}
+The model $q \sim kAE_0$ is incidentally very similar to the classical solution for the surface charge density of a half-spherical conductor with a field-induced dipole \cite{david_j._griffiths_introduction_1999}
 \begin{eqnarray*}
@@
 with $k \approx 1.3 \times 10^{-10}$.
-This is also of a similar form to the charge found by Takamatsu and coauthors for droplets falling from a grounded nozzle in an external electric field \cite{takamatsu_theoretical_1981}
+This is also of a similar form to the charge found by Takamatsu and coauthors for drops falling from a grounded nozzle in an external electric field \cite{takamatsu_theoretical_1981}
 \[q = 4 \pi \epsilon_0 \beta E_0 R_d^2 \]
@@
 \section{Scale Quantities}
-The dielectrophoretic force plays a very small role when droplets have net charge in a DC field; the condition to neglect the DEP force was satisfied for all experiments in the dataset.
-Dimensional droplet apoapses scale closely with $\mathbb{E}\mbox{u}$ as seen in Figure \ref{fig:series_s_eu}.
-The relative magnitudes of the simulated forces felt by the droplets is shown in Figure \ref{fig:forces}.
+The dielectrophoretic force plays a very small role when drops have net charge in a DC field; the condition to neglect the DEP force was satisfied for all experiments in the dataset.
+Dimensional drop apoapses scale closely with $\mathbb{E}\mbox{u}$ as seen in Figure \ref{fig:series_s_eu}.
+The relative magnitudes of the simulated forces felt by the drops is shown in Figure \ref{fig:forces}.
 Forces acting on the drops vary in magnitude between $\mathcal{O}(10^{-6})-\mathcal{O}(10^{-4})$ N.
@@
     \input{../figures/series_s_eu.pgf}
-    \caption{Droplet trajectories as a function of $\mathbb{E}\mbox{u}$.\label{fig:series_s_eu}}
+    \caption{Drop trajectories as a function of $\mathbb{E}\mbox{u}$.\label{fig:series_s_eu}}
 \end{figure}
@@
     \resizebox{14cm}{!}{\input{../figures/forces.pgf}}
-    \caption{Simulated forces acting on the droplet. Experiments are shown by order of increasing apoapse.\label{fig:forces}}
+    \caption{Simulated forces acting on the drop. Experiments are shown by order of increasing apoapse.\label{fig:forces}}
 \end{figure}
@@
 We can perhaps gain some insight by comparing the asymptotic estimate for return times to the scaled experiemental return times.
-We see in Figure \ref{fig:times} that the long-time scaled non-dimensional time of first bounce in the experiment $t_b / t_c$, compares poorly to the asymptotic estimate for returns $t_f$ as $\mathbb{E}\mbox{u}_+$ becomes large.
-This is very much as we'd expect, but it is also unfortunate; for small $\mathbb{E}\mbox{u}$ the asymptotic length scale could be used to improve the characteristic length scale by $t_a = t_c t_f$.
-We also notice a two-tailed effect in the data; for the small $\mathbb{E}\mbox{u}$ droplets, the long-time scaling distorts the return times considerably.
+We see in Figure \ref{fig:times} that the long-time scaled non-dimensional time of first bounce in the experiment $t_b / t_c$, compares poorly to the asymptotic estimate for returns $t_f$ in the limit of small $\mathbb{E}\mbox{u}_+$, this is due to the use on long-time scaling for drops with $y/L \ll 1$.
 \begin{figure}[htb]
@@
     \input{../figures/times.pgf}
-    \caption{.\label{fig:times}}
+    \caption{Asymptotic $t_f$ estimates compared with dimensionless bounce times.\label{fig:times}}
 \end{figure}
@@
     \input{../figures/dnumbs.pgf}
-    \caption{.\label{fig:dnumbs}}
+    \caption{Experimental covariance between $\mathbb{E}\mbox{u}$ and $\mathbb{I}\mbox{m}$.\label{fig:dnumbs}}
 \end{figure}
@@
 We should note that there are several kinds of systematic error that influence our data.
-We assume that droplet translate purely along the central axis of the electric field, but in practice, despite the improvement in surface charge density uniformity produced by corona charging, there are still local areas of especially high charge density.
-In principle, this kind of error should become small for droplets which are far enough away from the charge distribution, that the geometry of the charge distribution disappears, and the electric field looks like that due to a point charge.
+We assume that drop translate purely along the central axis of the electric field, but in practice, despite the improvement in surface charge density uniformity produced by corona charging, there are still local areas of especially high charge density.
+In principle, this kind of error should become small for drops which are far enough away from the charge distribution, that the geometry of the charge distribution disappears, and the electric field looks like that due to a point charge.
 Another form of error is in the initial velocity as it appears in $\mathbb{E}\mbox{u}$.
-Because we usually lose the first few frames of video due to camera shake transients at the start of the low-gravity experiment, we will consistently underestimate $U_0$ because the droplet will already have decelerated significantly during that period of time.
-The primary sources of random error are the effect of contact line hysteresis on the droplet initial velocity, and of the variance in the MLE parameter estimates.
-\newpage
-
-\section{Impact Dynamics \hl{[placeholder section]}}
-Using the unique capabilities of the low-gravity environment we obtained data on dimensionless contact time and coefficients of restitution at very low Ohnesorge numbers for a range of electric Bond numbers.
-Despite strong electric fields (0.5-1.5 $kV/cm$) we found little evidence for wetting transitions due to excession of a critical pressure (the ``Fakir impalement'').
-There is no obvious trend in dimensionless contact time or coefficient of restitution with electric Bond number.
-
-Jump velocities are more strongly damped for relatively small droplet volumes in the presence of the electric fields than was shown by Attari \emph{et.
-al.}.
-This may be evidence for electrowetting paradoxically enhancing the effect of contact angle hysteresis pinning on sharp corners.
-(How does this tie into the coefficients of restitution problem?)
-
-\begin{figure}[htb]
-    \centering
-    \input{../figures/contact.pgf}
-    \caption{.\label{fig:contact}}
-\end{figure}
-
-\begin{figure}[htb]
-    \centering
-    \input{../figures/restitution.pgf}
-    \caption{.\label{fig:restitution}}
-\end{figure}
-
-\newpage
+Because we usually lose the first few frames of video due to camera shake transients at the start of the low-gravity experiment, we will consistently underestimate $U_0$ because the drop will already have decelerated significantly during that period of time.
+The primary sources of random error are the effect of contact line hysteresis on the drop initial velocity, and of the variance in the MLE parameter estimates.
+%\newpage
+
+%\section{Impact Dynamics \hl{[placeholder section]}}
+%\newpage
 
@@
 \label{sec.drop_charge}
-Since, by the earlier scaling, we presuppose the source of the droplet bouncing behavior to be primarily Coulombic in origin (as opposed to dielectrophoretic), the droplet must have some free charge in addition to the charge induced by the electric field.
-Whether this free charge arises due to contact charge or field induction To measure this charge concurrent methodologies were used.
-We determined the droplet free charge by observation of the deflection of the droplets in the region of a known uniform field in a fashion inspired by Millikan's famous experiment to determine the fundamental charge of the electron.
-
-Droplets were jumped in free-fall from a superhydrophobic surface placed between the plates of a parallel plate capacitor of known uniform electric field.
+Since, by the earlier scaling, we presuppose the source of the drop bouncing behavior to be primarily Coulombic in origin (as opposed to dielectrophoretic), the drop must have some free charge in addition to the charge induced by the electric field.
+Whether this free charge arises due to contact charge or field-induction To measure this charge concurrent methodologies were used.
+We determined the drop free charge by observation of the deflection of the drops in the region of a known uniform field in a fashion inspired by Millikan's famous experiment to determine the fundamental charge of the electron.
+
+Drops were jumped in free-fall from a superhydrophobic surface placed between the plates of a parallel plate capacitor of known uniform electric field.
 The surface was charge neutralized.
-Since the droplet initial velocity $U_0$ is parallel to the electric field, the droplets are inertial in the direction of the electric force, and neglecting the effect of image charges mirrored across the conductors, we can determine the magnitude of the droplet charge by a balance of Coulombic force and inertia given by the equation of motion
+Since the drop initial velocity $U_0$ is parallel to the electric field, the drops are inertial in the direction of the electric force, and neglecting the effect of image charges mirrored across the conductors, we can determine the magnitude of the drop charge by a balance of Coulombic force and inertia given by the equation of motion
 
@@
 
-Since the drag is negligible in the inertial limit we can find the charge $q$ by fitting a second-order least squares polynomial to the measured droplet positions, equating the $t^2$ term to the constant acceleration, and dividing by the known, constant magnitude of the electric field.
-
-A 200-880 VAC source with a full wave bridge rectifier circuit was prototyped on perf-board for initial experiments to measure droplet charge.
+Since the drag is negligible in the inertial limit we can find the charge $q$ by fitting a second-order least squares polynomial to the measured drop positions, equating the $t^2$ term to the constant acceleration, and dividing by the known, constant magnitude of the electric field.
+
+A 200-880 VAC source with a full wave bridge rectifier circuit was prototyped on perf-board for initial experiments to measure drop charge.
 The circuit was analyzed on an laboratory oscilloscope to verify that the AC component of the signal was appropriately small (13 mV at 35 kHz).
@@
 The electrodes were mounted on an insulated 80/20 extruded aluminum rail for ease of adjustment.
-All droplet charge experiments were conducted with an electrode spacing of 28.30 mm.
+All drop charge experiments were conducted with an electrode spacing of 28.30 mm.
 With this spacing the calibrated electric field between the plates was $\mathbf{E} \approx 35$kV/m.
@@
 Potential across the plates was measured periodically with a load-impedance corrected multimeter to account for battery depletion.
-The typical capacitor rise time of the plates was measured to be 1.4 s, thus to make the most economical use of the brief window a low-gravity a weighted switch was set by hand prior to the drop to close the high-voltage circuit, but which passively safed the system at the resumption of 1-g conditions in the tower.
-From a survey of literature we suppose the droplet charge, if they are indeed charged by contact with PTFE, to be some function of the droplet volume and the residence time on the superhydrophobic surface.
-However, sweeping though droplet volumes over a series of drop tower experiments we find little correlation between droplet volume  and free droplet charge.
+The typical capacitor rise time of the plates was measured to be 1.4 s, thus to make the most economical use of the brief window a low-gravity a weighted switch was set by hand prior to the drop to close the high-voltage circuit, but which passively safed the system at the resumption of 1-$g_0$ conditions in the tower.
+From a survey of literature we suppose the drop charge, if they are indeed charged by contact with PTFE, to be some function of the drop volume and the residence time on the superhydrophobic surface.
+However, sweeping though drop volumes over a series of drop tower experiments we find little correlation between drop volume  and free drop charge.
 
 A brief screening experiment was conducted which alternated the polarity of the field by switching the positive and negative terminal leads between plates.
-Qualitative observations of droplet electrode preference seem to indicate that the assumption of small polarization stress was well founded.
-Following this a orthogonal array $3^2$ factorial design experiment with two replicates was conducted to test the effect of varying droplet volume and surface stay time on free charge at the time of jumping.
+Qualitative observations of drop electrode preference seem to indicate that the assumption of small polarization stress was well founded.
+Following this a orthogonal array $3^2$ factorial design experiment with two replicates was conducted to test the effect of varying drop volume and surface stay time on free charge at the time of jumping.
 It was hypothesized in accordance with previous studies [ref], that free charge would increase for levels of both factors.
-ANOVA analysis in \emph{R} of the linear multiple regression model for the data set indicates that neither droplet volume ($p=0.105$), nor surface stay time ($p=0.358$) is significant at the 95\% confidence level.
+ANOVA analysis in \emph{R} of the linear multiple regression model for the data set indicates that neither drop volume ($p=0.105$), nor surface stay time ($p=0.358$) is significant at the 95\% confidence level.
 The overall model F-statistics (2.177 in 2 and 13 degrees of freedom), and coefficients of determination ($r^2 = 0.2509$) indicate that the linear model neither fits the data particularly well, nor does it offer an improvement over the mean model.

### 2018-01-25 doc/manuscript/results.tex
edits

@@
 \end{figure}
+
+\begin{figure}[htb]
+    \centering
+    \input{../figures/series_m_ds.pgf}
+    \caption{.\label{fig:dnumbs}}
+\end{figure}
+\begin{figure}[htb]
+    \centering
+    \input{../figures/series_m2_ds.pgf}
+    \caption{.\label{fig:dnumbs}}
+\end{figure}
 We should note that there are several kinds of systematic error that influence our data.
@@
 Since, by the earlier scaling, we presuppose the source of the droplet bouncing behavior to be primarily Coulombic in origin (as opposed to dielectrophoretic), the droplet must have some free charge in addition to the charge induced by the electric field.
-To measure this charge concurrent methodologies were used.
-The first method of determining the droplet free charge is observation of the deflection of the droplets in the region of a known uniform field in a fashion inspired by Millikan's famous experiment to determine the fundamental charge of the electron [ref].
+Whether this free charge arises due to contact charge or field induction To measure this charge concurrent methodologies were used.
+We determined the droplet free charge by observation of the deflection of the droplets in the region of a known uniform field in a fashion inspired by Millikan's famous experiment to determine the fundamental charge of the electron.
 
-Droplets were jumped in freefall from a sandpaper superhydrophobic surface placed between the plates of a parallel plate capacitor of known uniform electric field.
-The surface was first deionized using a balanced \emph{Ptec} IN5120 DC air-ionizer to remove the effect of surface charge of the superhydrophobic surface from perturbing the otherwise uniform field set up between the parallel plates.
-A schematic of the parallel plate drop apparatus is shown in Figure \ref{fig:millikan}.
+Droplets were jumped in free-fall from a superhydrophobic surface placed between the plates of a parallel plate capacitor of known uniform electric field.
+The surface was charge neutralized.
 Since the droplet initial velocity $U_0$ is parallel to the electric field, the droplets are inertial in the direction of the electric force, and neglecting the effect of image charges mirrored across the conductors, we can determine the magnitude of the droplet charge by a balance of Coulombic force and inertia given by the equation of motion
 
-\[ \frac{d^2y}{dt^2} = q\mathbf{E}. \]
+\[ y'(t) = q\mathbf{E}. \]
 
 Since the drag is negligible in the inertial limit we can find the charge $q$ by fitting a second-order least squares polynomial to the measured droplet positions, equating the $t^2$ term to the constant acceleration, and dividing by the known, constant magnitude of the electric field.
-From a survey of literature we suppose the droplet charge, if they are indeed charged by contact with PTFE, to be some function of the droplet volume and the residence time on the superhydrophobic surface.
-However, sweeping though droplet volumes over a series of drop tower experiments we find little correlation between droplet volume  and free droplet charge.
-This is shown in figure \ref{fig:drop_charge}.
 
@@
 With this spacing the calibrated electric field between the plates was $\mathbf{E} \approx 35$kV/m.
-The electrodes were electrically isolated from the drop rig by two alternating layers of 4 mm thick laser cut acrylic sheet and Kapton tape.
+The electrodes were electrically isolated from the drop rig by two alternating layers of 4 mm thick PMMA sheet and Kapton tape.
 Potential across the plates was measured periodically with a load-impedance corrected multimeter to account for battery depletion.
-The typical capacitor rise time of the plates was measured to be 1.4 s, thus to make the most economical use of the brief window a micro-gravity a weighted switch was set by hand prior to the drop to close the high-voltage circuit, but which passively safed the system at the resumption of 1-g conditions in the tower.
-The drop apparatus is shown in Fig.
-
-%\begin{figure}
-%  \centerline{\includegraphics[height=7cm,width=13cm]{modes.eps}}
- % \centerline{\includegraphics[height=7cm,width=7cm]{e88_1_thumb.jpg}}
-  %\caption{Parallel plate experimental apparatus.}
-%\label{fig:millikan}
-%\end{figure}
-
-%\begin{figure}
-%  \centerline{\includegraphics[height=7cm,width=13cm]{modes.eps}}
- % \centerline{\includegraphics[height=7cm,width=7cm]{e88_1_thumb.jpg}}
-  %\caption{Parallel plates: Droplet free charge vs volume.}
-%\label{fig:drop_charge}
-%\end{figure}
+The typical capacitor rise time of the plates was measured to be 1.4 s, thus to make the most economical use of the brief window a low-gravity a weighted switch was set by hand prior to the drop to close the high-voltage circuit, but which passively safed the system at the resumption of 1-g conditions in the tower.
+From a survey of literature we suppose the droplet charge, if they are indeed charged by contact with PTFE, to be some function of the droplet volume and the residence time on the superhydrophobic surface.
+However, sweeping though droplet volumes over a series of drop tower experiments we find little correlation between droplet volume  and free droplet charge.
 
@@
 Following this a orthogonal array $3^2$ factorial design experiment with two replicates was conducted to test the effect of varying droplet volume and surface stay time on free charge at the time of jumping.
-It was hypothesized in accordance with previous studies \cite{Choi:2013dg}, that free charge would increase for levels of both factors.
-The results of the factorial experiment are presented in Fig.
-\ref{fig:chart1}.
+It was hypothesized in accordance with previous studies [ref], that free charge would increase for levels of both factors.
 ANOVA analysis in \emph{R} of the linear multiple regression model for the data set indicates that neither droplet volume ($p=0.105$), nor surface stay time ($p=0.358$) is significant at the 95\% confidence level.

### 2018-01-26 doc/manuscript/manuscript.tex
presentation figures

@@
     \resizebox{12cm}{!}{\input{../figures/scatter.pgf}}
-    \caption{A simple EMA plot.\label{fig:scatter}}
+    \caption{Covariance plot of main parameters $E_0$, $U_0$, droplet area ($V_d^{2/3})$, and $q$.\label{fig:scatter}}
 \end{figure}
@@
     \input{../figures/charge.pgf}
-    \caption{A simple EMA plot.\label{fig:charge}}
+    \caption{Charge $q$, as a function of $V_d$, $\varphi_s$.\label{fig:charge}}
 \end{figure}
@@
 The relative magnitudes of the simulated forces felt by the drops is shown in Figure \ref{fig:forces}.
-Forces acting on the drops vary in magnitude between $\mathcal{O}(10^{-6})-\mathcal{O}(10^{-4})$ N.
+Forces acting on the drops vary in magnitude between $\mathcal{O}(10^{-6})$-$\mathcal{O}(10^{-4})$ N.
 We see that, of the drops in the experimental dataset only the two with the largest $\mathbb{E}\mbox{u}$, $\mathbb{E}\mbox{u} \sim \mathcal{O}(1)$ could appropriately be said to be in the inertial electro-viscous regime.

### 2018-02-19 doc/manuscript/results.tex
added improved figures, results discussion

@@
 \usepackage{setspace}
+\usepackage{float}
 \author{Erin Schmidt}
@@
 \section{Charge Estimates}
-We found the distribution of mostly likely experimental net charges for a population of the droplets jumped in low-gravity.
+We found the distribution of mostly likely experimental net charges for a population of the drops jumped in low-gravity.
 A covariance plot of the model variables is shown in Figure \ref{fig:scatter}.
-The multicollinear dependence of charge on droplet surface area, $A$, and the characteristic electric field, $E_0$, is evident.
+The multicollinear dependence of charge on drop surface area, $A$, and the characteristic electric field, $E_0$, is evident.
 Assuming the main effect is the interaction between charge and electric field, a Robust Least Squares model fit $q \sim kAE_0$ (using the Python \verb|statsmodels.formula.api.RLM| function), with the non-linear transformation $A = V_d^{2/3}$, found that $k=5.01 \times 10^{-11} \pm  2.85 \times 10^{-11}$ with $R^2 = 0.946$.
 This model uses Huber's T norm, median absolute scaling, and H1 covariance estimation.
-A contour plot showing the estimated droplet free charge as a function of $V_d$ and $\varphi_s$ is shown in Figure \ref{fig:charge}.
-\begin{figure}[htb]
+A contour plot showing the estimated drop free charge as a function of $V_d$ and $\varphi_s$ is shown in Figure \ref{fig:charge}.
+\begin{figure}[H]
     \centering
     \resizebox{12cm}{!}{\input{../figures/scatter.pgf}}
-    \caption{A simple EMA plot.\label{fig:scatter}}
+    \caption{Covariance plot of main parameters $E_0$, $U_0$, droplet area ($V_d^{2/3})$, and $q$.\label{fig:scatter}}
 \end{figure}
-\begin{figure}[htb]
+\begin{figure}[H]
     \centering
     \input{../figures/charge.pgf}
-    \caption{A simple EMA plot.\label{fig:charge}}
+    \caption{Charge $q$, as a function of $V_d$, $\varphi_s$.\label{fig:charge}}
 \end{figure}
 
-A two-ways T-test comparison of charge distributions between the droplet bounce experiment and a corollary experiment with zero electric field at the time of droplet deposition on the superhydrophobic surface suggests that the droplet charge is induced by the electric field, rather than through contact charging on the PTFE layer ($t = 5.11, p = 0.0002$).
+A two-ways T-test comparison of charge distributions between the drop bounce experiment and a corollary experiment with zero electric field at the time of drop deposition on the superhydrophobic surface suggests that the drop charge is induced by the electric field, rather than through contact charging on the PTFE layer ($t = 5.11, p = 0.0002$).
 The T-test informs us that the charge distribution  are about 5 times more different from each other as they are within each other, and there is a 0.02$\%$ probability that this result happened by chance.
@@
 \section{Scale Quantities}
-The dielectrophoretic force plays a very small role when droplets have net charge in a DC field; the condition to neglect the DEP force was satisfied for all experiments in the dataset.
-Dimensional droplet apoapses scale closely with $\mathbb{E}\mbox{u}$ as seen in Figure \ref{fig:series_s_eu}.
-The relative magnitudes of the simulated forces felt by the droplets is shown in Figure \ref{fig:forces}.
-Forces acting on the drops vary in magnitude between $\mathcal{O}(10^{-6})-\mathcal{O}(10^{-4})$ N.
+The dielectrophoretic force plays a very small role when drops have net charge in a DC field; the condition to neglect the DEP force was satisfied for all experiments in the dataset.
+Dimensional drop apoapses scale closely with $\mathbb{E}\mbox{u}$ as seen in Figure \ref{fig:series_s_eu}.
+The relative magnitudes of the simulated forces felt by the drops is shown in Figure \ref{fig:forces}.
+Forces acting on the drops vary in magnitude between $\mathcal{O}(10^{-6})$-$\mathcal{O}(10^{-4})$ N.
 We see that, of the drops in the experimental dataset only the two with the largest $\mathbb{E}\mbox{u}$, $\mathbb{E}\mbox{u} \sim \mathcal{O}(1)$ could appropriately be said to be in the inertial electro-viscous regime.
@@
 
-\begin{figure}[htb]
+\begin{figure}[!htb]
     \centering
     \input{../figures/series_s_eu.pgf}
-    \caption{Droplet trajectories as a function of $\mathbb{E}\mbox{u}$.\label{fig:series_s_eu}}
+    \caption{Drop trajectories as a function of $\mathbb{E}\mbox{u}$.\label{fig:series_s_eu}}
 \end{figure}
-\begin{figure}[htb]
+\begin{figure}[!htb]
     \centering
-    \resizebox{14cm}{!}{\input{../figures/forces.pgf}}
-    \caption{Simulated forces acting on the droplet. Experiments are shown by order of increasing apoapse.\label{fig:forces}}
+    \resizebox{14cm}{!}{\input{../figures/forces_all.pgf}}
+    \caption{Simulated forces acting on the drop. Experiments are shown by order of increasing apoapse.\label{fig:forces}}
 \end{figure}
@@
 We also observe that that $\mathbb{E}\mbox{u}$ is not typically a small number in this regime, imperiling our use of asymptotic estimates in this regime.
-We can perhaps gain some insight by comparing the asymptotic estimate for return times to the scaled experiemental return times.
-We see in Figure \ref{fig:times} that the long-time scaled non-dimensional time of first bounce in the experiment $t_b / t_c$, compares poorly to the asymptotic estimate for returns $t_f$ as $\mathbb{E}\mbox{u}_+$ becomes large.
-This is very much as we'd expect, but it is also unfortunate; for small $\mathbb{E}\mbox{u}$ the asymptotic length scale could be used to improve the characteristic length scale by $t_a = t_c t_f$.
-We also notice a two-tailed effect in the data; for the small $\mathbb{E}\mbox{u}$ droplets, the long-time scaling distorts the return times considerably.
-\begin{figure}[htb]
+We can perhaps gain some insight by comparing the asymptotic estimate for return times to the scaled experimental return times.
+We see in Figure \ref{fig:times} that the long-time scaled non-dimensional time of first bounce in the experiment $t_b / t_c$, compares poorly to the asymptotic estimate for returns $t_f$ in the limit of small $\mathbb{E}\mbox{u}_+$, this is due to the use on long-time scaling for drops with $y/L \ll 1$.
+\begin{figure}[H]
     \centering
@@
     \caption{Non-dimensional trajectories with the short-time scaling.\label{fig:series_s_ds}}
-\end{figure}
-
-\begin{figure}[htb]
-    \centering
-    \input{../figures/times.pgf}
-    \caption{.\label{fig:times}}
 \end{figure}
@@
 Using an OLS regression, we find the model $\mathbb{I}\mbox{m} \sim (0.012 \pm 0.003) \mathbb{E}\mbox{u} + (0.212 \pm 0.036) $ with $R^2 =0.59$.
-\begin{figure}[htb]
+\begin{figure}[H]
     \centering
     \input{../figures/dnumbs.pgf}
-    \caption{.\label{fig:dnumbs}}
+    \caption{Experimental covariance between $\mathbb{E}\mbox{u}$ and $\mathbb{I}\mbox{m}$.\label{fig:dnumbs}}
 \end{figure}
 
-Finally we show several trajectories in the long-time scaled regime in Figure \ref{fig:series_l_ds}.
-\begin{figure}[htb]
-    \centering
-    \input{../figures/series_l_ds.pgf}
-    \caption{Non-dimensional trajectories with the long-time scaling as a function of ${\mathbb{E}\mbox{u}}_+$.\label{fig:series_l_ds}}
-\end{figure}
+We should note that there are several kinds of systematic error that influence our data.
+We assume that drop translate purely along the central axis of the electric field, but in practice, despite the improvement in surface charge density uniformity produced by corona charging, there are still local areas of especially high charge density.
+In principle, this kind of error should become small for drops which are far enough away from the charge distribution, that the geometry of the charge distribution disappears, and the electric field looks like that due to a point charge.
+Another form of error is in the initial velocity as it appears in $\mathbb{E}\mbox{u}$.
+Because we usually lose the first few frames of video due to camera shake transients at the start of the low-gravity experiment, we will consistently underestimate $U_0$ because the drop will already have decelerated significantly during that period of time.
+The primary sources of random error are the effect of contact line hysteresis on the drop initial velocity, and of the variance in the MLE parameter estimates.
 
-\begin{figure}[htb]
-    \centering
-    \input{../figures/series_m_ds.pgf}
-    \caption{.\label{fig:dnumbs}}
-\end{figure}
-\begin{figure}[htb]
-    \centering
-    \input{../figures/series_m2_ds.pgf}
-    \caption{.\label{fig:dnumbs}}
-\end{figure}
-We should note that there are several kinds of systematic error that influence our data.
-We assume that droplet translate purely along the central axis of the electric field, but in practice, despite the improvement in surface charge density uniformity produced by corona charging, there are still local areas of especially high charge density.
-In principle, this kind of error should become small for droplets which are far enough away from the charge distribution, that the geometry of the charge distribution disappears, and the electric field looks like that due to a point charge.
-Another form of error is in the initial velocity as it appears in $\mathbb{E}\mbox{u}$.
-Because we usually lose the first few frames of video due to camera shake transients at the start of the low-gravity experiment, we will consistently underestimate $U_0$ because the droplet will already have decelerated significantly during that period of time.
-The primary sources of random error are the effect of contact line hysteresis on the droplet initial velocity, and of the variance in the MLE parameter estimates.
-\newpage
+\section{Impact Dynamics}
+\hl{Check the Oh numbers}.
+Very little work to date on drop impacts outside of two regimes: first, very low $\mathbb{R}\mbox{e}$ viscous drop spreading driven by capillary forces at the contact line, and second, impacts at ``high'' $\mathbb{W}\mbox{e}$.
+There has been some computational work with impacts at $\mathbb{R}\mbox{e}=1.4$ (Fukai \emph{et al.}), but the results are suspect as the model neglects uncompensated Young's force at the contact line (which is the dominant spreading force for low $\mathbb{R}\mbox{e}$ impacts).
+Of course models for dynamic contact lines in general remain controversial, even for ordinary spreading of liquids, despite decades of work in the area.
 
-\section{Impact Dynamics \hl{[placeholder section]}}
-Using the unique capabilities of the low-gravity environment we obtained data on dimensionless contact time and coefficients of restitution at very low Ohnesorge numbers for a range of electric Bond numbers.
-Despite strong electric fields (20-30 $kV/cm$) we found little evidence for wetting transitions due to excession of a critical pressure (the ``Fakir impalement'').
-There is no obvious trend in dimensionless contact time or coefficient of restitution with electric Bond number.
+Naivly neglecting dimensionless groups governing the dynamic contact line, the pertinent dimensionless groups for isothermal droplet impacts are the Weber number $\mathbb{W}\mbox{e} = \frac{\rho U^2 R_d}{\sigma}$, which is a ratio of droplet inertia to surface tension, the Ohnesorge number, $\mathbb{O}\mbox{h} = \frac{\mu}{\sqrt{\rho \sigma R_d}}$, which is a ratio of viscous to inertial and surface tension forces, and the Bond number, $\mathbb{B}\mbox{o}$, defined previously.
+The dynamics of spreading are characterized primarily by $\mathbb{W}\mbox{e}$ and $\mathbb{O}\mbox{h}$.
+Additionally the final stages of spreading depend strongly on $\theta_e$, which is the static contact angle.
+The Weber number scales the \emph{driving force} of the impact.
+In the more familiar case of high $\mathbb{W}\mbox{e}$ the drop liquid bulk is driven radially outward by the impact induced pressure gradient, whereas in the case of small $\mathbb{W}\mbox{e}$ the liquid is pulled outwards by capillary force (e.g.
+uncompensated Young's force) at the contact line.
+The Ohnesorge number, by contrast, scales the force that \emph{resists} spreading.
+For large $\mathbb{O}\mbox{h}$ the resistive force is viscous, whereas for low $\mathbb{O}\mbox{h}$ the force is inertia.
 
-Jump velocities are more strongly damped for relatively small droplet volumes in the presence of the electric fields than was shown by Attari \emph{et.
-al.}.
-This may be evidence for electrowetting paradoxically enhancing the effect of contact angle hysteresis pinning on sharp corners.
-(How does this tie into the coefficients of restitution problem?)
+We observe average drop impact $\mathbb{O}\mbox{h} \approx 2.18 \pm 0.36$, and  $\mathbb{W}\mbox{e} \approx 0.28 \pm 0.22$.
+Thus impact velocity plays little role in the spreading dynamics of the bounces, and viscous effects are important but do not dominate inertia.
+Notably we observe underdamped oscillations of drop interfaces during impact.
+according to (Schiaffino, 1997) viscous forces play a role in the final (which?
+describe) stage of spreading even for drop impact at very low $\mathbb{O}\mbox{h}$.
+In the regime of intermediate viscosity, following spreading the oscillations of the interface are damped with a characteristic time that is generally longer than the spreading time (again, given by $t_c \sim \left( \sigma / \rho R_d^3 \right)^{1/2}$).
+The celebrated Hoffman-Tanner-Voinov law, which relates the contact line velocity $U_c$ of an isothermal spreading process to the static contact angle $\theta_e$ to the dynamic advancing contact angle $\theta_a$ by
+\[
+\frac{\mu U_c}{\sigma} \approx \kappa \left( \theta_a^3 - \theta_e^3 \right),
+\]
+where $\kappa \approx 0.013$ is an empirical coefficient extracted from Hoffman's data.
+The Hoffman-Tanner-Voinov law implies that the transition between low $\mathbb{W}\mbox{e}$ inviscid and viscous regimes occurs at $\mathbb{O}\mbox{h} \sim \mathcal{O}(10^{-2})$ rather than $\mathbb{O}\mbox{h} \sim \mathcal{O}(1)$ given by a naive scaling.
 
-\begin{figure}[htb]
-    \centering
-    \input{../figures/contact.pgf}
-    \caption{.\label{fig:contact}}
-\end{figure}
+Some notes:
+\begin{itemize}
+\item{\textbf{Schiaffino, 1997}} 
+\end{itemize}
 
-\begin{figure}[htb]
-    \centering
-    \input{../figures/restitution.pgf}
-    \caption{.\label{fig:restitution}}
-\end{figure}
-
-\newpage
-\appendix
-\section{\\Droplet Charge} \label{sec.drop_charge}
-\subsection*{Parallel Plate Method}
-Since, by the earlier scaling, we presuppose the source of the droplet bouncing behavior to be primarily Coulombic in origin (as opposed to dielectrophoretic), the droplet must have some free charge in addition to the charge induced by the electric field.
-Whether this free charge arises due to contact charge or field induction To measure this charge concurrent methodologies were used.
-We determined the droplet free charge by observation of the deflection of the droplets in the region of a known uniform field in a fashion inspired by Millikan's famous experiment to determine the fundamental charge of the electron.
-
-Droplets were jumped in free-fall from a superhydrophobic surface placed between the plates of a parallel plate capacitor of known uniform electric field.
-The surface was charge neutralized.
-Since the droplet initial velocity $U_0$ is parallel to the electric field, the droplets are inertial in the direction of the electric force, and neglecting the effect of image charges mirrored across the conductors, we can determine the magnitude of the droplet charge by a balance of Coulombic force and inertia given by the equation of motion
-
-\[ y'(t) = q\mathbf{E}. \]
-
-Since the drag is negligible in the inertial limit we can find the charge $q$ by fitting a second-order least squares polynomial to the measured droplet positions, equating the $t^2$ term to the constant acceleration, and dividing by the known, constant magnitude of the electric field.
-
-A 200-880 VAC source with a full wave bridge rectifier circuit was prototyped on perf-board for initial experiments to measure droplet charge.
-The circuit was analyzed on an laboratory oscilloscope to verify that the AC component of the signal was appropriately small (13 mV at 35 kHz).
-Current was determined to be a relatively low 80 $\mu$A.
-The high-voltage source terminals were led to two parallel polished 150x150 mm aluminum plate electrodes.
-The electrodes were mounted on an insulated 80/20 extruded aluminum rail for ease of adjustment.
-All droplet charge experiments were conducted with an electrode spacing of 28.30 mm.
-With this spacing the calibrated electric field between the plates was $\mathbf{E} \approx 35$kV/m.
-The electrodes were electrically isolated from the drop rig by two alternating layers of 4 mm thick PMMA sheet and Kapton tape.
-Potential across the plates was measured periodically with a load-impedance corrected multimeter to account for battery depletion.
-The typical capacitor rise time of the plates was measured to be 1.4 s, thus to make the most economical use of the brief window a low-gravity a weighted switch was set by hand prior to the drop to close the high-voltage circuit, but which passively safed the system at the resumption of 1-g conditions in the tower.
-From a survey of literature we suppose the droplet charge, if they are indeed charged by contact with PTFE, to be some function of the droplet volume and the residence time on the superhydrophobic surface.
-However, sweeping though droplet volumes over a series of drop tower experiments we find little correlation between droplet volume  and free droplet charge.
-
-A brief screening experiment was conducted which alternated the polarity of the field by switching the positive and negative terminal leads between plates.
-Qualitative observations of droplet electrode preference seem to indicate that the assumption of small polarization stress was well founded.
-Following this a orthogonal array $3^2$ factorial design experiment with two replicates was conducted to test the effect of varying droplet volume and surface stay time on free charge at the time of jumping.
-It was hypothesized in accordance with previous studies [ref], that free charge would increase for levels of both factors.
-ANOVA analysis in \emph{R} of the linear multiple regression model for the data set indicates that neither droplet volume ($p=0.105$), nor surface stay time ($p=0.358$) is significant at the 95\% confidence level.
-The overall model F-statistics (2.177 in 2 and 13 degrees of freedom), and coefficients of determination ($r^2 = 0.2509$) indicate that the linear model neither fits the data particularly well, nor does it offer an improvement over the mean model.
-The mean charge was determined to be positive $2.3 \cdot 10^{-11}$ C, with a standard deviation of $1.8 \cdot 10^{-11}$ C.
-
-\printbibliography
+%\newpage
 \end{document}

### 2018-03-22 doc/manuscript/manuscript.tex
added presentation latex scratch pad
fotmatting changes, updated figures

@@
 \usepackage{pgf}
+\usepackage{bookmark}
+\usepackage{color}
+\usepackage{tikz}
 \graphicspath{ {../figures/} }
@@
 \usepackage{setspace}
+\usepackage[caption=false]{subfig}
 \newlength\figureheight
@@
 \begin{document}
+
+\newcommand{\redline}{\raisebox{2pt}{\tikz{\draw[-,red,solid,line width = 1.5pt](0,0) -- (5mm,0);}}}
 %\frontmatter
@@
 Ra\'ul Bayo\'an Cal\\
-Gerry Recktenwald\\
+Gerald Recktenwald\\
 
@@
 
-\doublespacing
+%\doublespacing
 \clearpage
@@
 
-\doublespacing
+%\doublespacing
 \section*{Abstract}
@@
 For ${\mathbb{E}\mbox{u}}_+ \gg 1/8 \pi$ droplets escape the electric field.
-The droplet net charge, estimated to be on the order of $1 \times 10^{-9}$ C, is field-induced rather than by contact charging at the (PTFE coated) hydrophobic interface.
+The droplet net charge, estimated to be on the order of $1 \times 10^{-9}$ C, is field-induced rather than occurring by contact charging at the (PTFE coated) hydrophobic interface.
 In 1-$g_0$, for Weber numbers $>$ 0.4, impact recoil behavior on a super-hydrophobic surface is normally dominated by damping from contact line hysteresis.
@@
 ``When the influence of gravity on fluid behavior is diminished or removed, other forces, otherwise of small significance, can assume paramount roles.''
-- NRC Report to NASA, 2003  \cite{motil_priorities_2012}
+- NRC Report to NASA, 2003\cite{motil_priorities_2012}
 \end{quote}
@@
 This should come as little surprise, as we are creatures evolved at the bottom of a gravity well; gravity is natural to us.
-However when the magnitude of gravitational body forces become small, other forces come into play in fluid dynamical problems which are otherwise negligible under normal circumstances in 1-$g_0$.
+However when the magnitude of gravitational body forces become small, other forces come into play in fluid dynamical problems, which are otherwise negligible under normal circumstances in 1-$g_0$.
 Our 1-$g_0$ cognitive bias then leads to a plethora of problems which are both simultaneously trivially easy to solve in 1-$g_0$, and which despite decades of study continue to elude solutions in a low-gravity context.
 One example of these problems is the so-called ``phase separation'' problem of separating a gas phase from a multi-phase flow (or the reverse case), without the aid of buoyancy due to gravity.
-Sans buoyancy, otherwise mundane activities such as venting a gas or settling a liquid in a tank become problematic \cite{petrash_controlling_1964}.
-Trapped bubbles can vapor lock life support, power, or propulsion systems \cite{jenson_passive_2014}.
-Issues of phase separation have so bedeviled human endeavors in space that an entire Apollo Saturn 1B mission (AS-203) was earmarked to study them \cite{hastings_[saturn_1965}.
+Sans buoyancy, otherwise mundane activities such as venting a gas or settling a liquid in a tank become problematic\cite{petrash_controlling_1964}.
+Trapped bubbles can vapor lock life-support, power, or propulsion systems\cite{jenson_passive_2014}.
+Issues of phase separation have so bedeviled human endeavors in space that an entire Apollo Saturn 1B mission (AS-203) was earmarked to study them\cite{hastings_saturn_1965}.
 This problem has for some time motivated a quest for substitute body forces, and the present work follows in that well-worn tradition.
@@
 A solid beginning to rectifying our problem of poor low-gravity intuition, would be to quantify how wrong our intuition is.
-First, let's clear up a common misnomer about the state of ``zero-gravity''.
+First, let us clear up a common misnomer about the state of ``zero-gravity''.
 The theory of general relativity is based on a fundamental equivalence of gravity and acceleration.
@@
 the equivalence of gravitational and inertial mass).
-In theoretical terms, a zero-g experiment performed in a drop tower on the surface of the Earth is equivalent to the same experiment performed in the nearly gravity-free deep space between galaxies, despite the fact that the drop tower itself is enveloped in a 1-$g_0$ gravity field.
-At the orbital altitude of the International Space Station (ISS) the gravity level is still nearly 90\% of its value at sea-level on Earth, but the astronauts aboard ISS feel weightlessness because they are in free-fall.
+In theoretical terms, a zero-g experiment performed in a drop tower on the surface of the Earth is equivalent to the same experiment performed in the nearly gravity-free deep space between galaxies, despite the fact that the drop tower itself is enveloped in a 1-$g_0$ gravity field, where $g_0=9.81$ m/s$^2$ is the standard gravitational acceleration at sea-level .
+At the orbital altitude of the International Space Station (ISS) the gravity level is still nearly 90\% of its value at sea-level on Earth, but the astronauts aboard ISS feel weightlessness because they are in a state of free-fall.
 In a practical sense true zero-g does not exit anywhere in the universe as there are always small, but nonetheless, measurable forces which can accelerate any massive body.
-For instance in low-Earth orbit, accelerations due to aerodynamic resistance in the tenuous outer atmosphere are on the order of $1 \times 10^{-6}$ g (from hence comes the term ``microgravity'').
+For instance in low-Earth orbit, accelerations due to aerodynamic resistance in the tenuous outer atmosphere are on the order of $1 \times 10^{-6}$ $g_0$ (from hence comes the term ``microgravity'').
 This small drag acceleration provides some ersatz gravity, but there are also other forces present.
@@
 As with capillary forces, electrostatic forces have a multitude of applications as substitutes for gravity.
-Electrohydrodynamic (EHD) body forces have been suggested to combat thermal stratification of propellants under low-g conditions where bouyancy induced natural convection is very small \cite{blackmon_collection_1965}.
+Electrohydrodynamic (EHD) body forces have been suggested to combat thermal stratification of propellants under low-g conditions where bouyancy induced natural convection is very small\cite{blackmon_collection_1965}.
 In this case electro-convection is an analog of natural convection due to a fluid temperature dependent dielectric permitivity gradient (as opposed to a fluid density gradient), in the presence of a body force field: the electric field.
 The study also suggested applications in cryogenic tank vent screening, and in reducing heat transfer to cryogenic propellants (and thus boiloff losses) by dielectrophoretically positioning ullage vapors around the tank walls as a thermal barrier.
-EHD forces have been studied for enhancing boiling heat transfer by promotion of bubble detachment and prevention of dryout, again as an ersatz bouyancy \cite{snyder_dielectrophoresis_2001} \cite{di_marco_influence_2003} \cite{marco_use_2012}.
-EHD heat pipes, which substitute an electrode structure for the capillary wicking structure of a conventional thermocapillary heat pipe can evade the wicking limit \cite{jones_electrohydrodynamic_1973}.
+EHD forces have been studied for enhancing boiling heat transfer by promotion of bubble detachment and prevention of dryout, again as an ersatz bouyancy\cite{snyder_dielectrophoresis_2001}\cite{di_marco_influence_2003}\cite{marco_use_2012}.
+EHD heat pipes, which substitute an electrode structure for the capillary wicking structure of a conventional thermocapillary heat pipe can evade the wicking limit\cite{jones_electrohydrodynamic_1973}.
 These are restricted to the use of insulating dielectric liquids, which usually have relatively low thermal conductivity, but are highly robust against dryout, support active flow control, and have low viscous losses.
-Dielectrophoretic settling of cryogenic propellants, in both total and partial communication PMD configurations, has been studied analytically in both static \cite{hurwitz_electrohydrodynamic_1966} and dynamic cases \cite{koval_dynamics_1967}, and in drop tower experiments \cite{fax_dielectrophoretic_1969}.
-EHD forces have also beeen applied to the low-g slosh baffling problem \cite{boretz_orbital_1970} \cite{petrash_use_1968} \cite{hurwitz_dielectrophoretic_1968}, and studied extensively for the mitigation of vapor pullthrough during tank draining, and concomittent minimization of propellant residuals at burnout, in a series of experiments at the NASA Lewis (now Glenn) Research Center 2.2 s drop tower facillity \cite{berenyi_dielectrophoretic_1970}.
+Dielectrophoretic settling of cryogenic propellants, in both total and partial communication Propellant Management Device (PMD) configurations, has been studied analytically in both static\cite{hurwitz_electrohydrodynamic_1966} and dynamic cases\cite{koval_dynamics_1967}, and in drop tower experiments\cite{fax_dielectrophoretic_1969}.
+EHD forces have also been applied to the low-g slosh baffling problem\cite{boretz_orbital_1970}\cite{petrash_use_1968}\cite{hurwitz_dielectrophoretic_1968}, and studied extensively for the mitigation of vapor pullthrough during tank draining, and concomittent minimization of propellant residuals at burnout, in a series of experiments at the NASA Lewis (now Glenn) Research Center 2.2 s drop tower facillity\cite{berenyi_dielectrophoretic_1970}.
 
 \section{Spontaneous Drop Jump}
-Low-gravity phase separation, droplet dynamics, and the dynamics and applications of the so-called spontaneous droplet jump, is an active area of study at the Portland State University Dryen Drop Tower labratory (DDT).
+Low-gravity phase separation, droplet dynamics, and the dynamics and applications of the so-called spontaneous droplet jump, is an active area of study at the Portland State University Dryden Drop Tower labratory (DDT).
 When a nonwetting, gravity dominated sessile droplet (e.g.
@@
 The Cassie-Baxter state, sometimes also known as the Fakir state, is a metastable heterogenously non-wetting state on a textured surface characterized by the existance of a vapor-layer which seperates roughness features of the surface from the bottom of the droplet.
-The spontaneous drop jump was first observed experimentally in the Soviet Union by Kirko \emph{et al.} \cite{kirko_phenomenon_1970} in 1970 for drops of mercury in HCl, and later by Wollman \emph{et al.} in 2016 for water drops in a set of experiments conducted using a low-gravity drop tower \cite{wollman_more_2016}.
+The spontaneous drop jump was first observed experimentally in the Soviet Union by Kirko \emph{et al.}\cite{kirko_phenomenon_1970} in 1970 for drops of mercury in hydrochloric acid, and later by Wollman \emph{et al.} in 2016 for water drops in a set of experiments conducted using drop towers\cite{wollman_more_2016}.
 The kinetic energy of the jump is supplied by the defect in free surface energy as the new minimum energy surface equilibrium has approximately constant curvature.
-If the energy losses by viscous and contact line dynamics are neglected, the available kinetic energy is given by
-\[KE_2 = SE_1 - SE_2= [(\sigma A)_{ls} + (\sigma A)_{gl} + (\sigma A)_{sg}]_1 - [(\sigma A)_{gl} + (\sigma A)_{sg}]_2, \]
-
-where the subscripts $_1$ and $_2$ denote the intial 1-$g_0$, and low-g surface energies.
+If the energy losses by viscous and contact line dynamics are neglected, the available kinetic energy is approximated by
+\[KE_2 = SE_2 - SE_1 = [(\gamma A)_{gl} + (\gamma A)_{sg}]_2 - [(\gamma A)_{ls} + (\gamma A)_{gl} + (\gamma A)_{sg}]_1, \]
+
+where $KE$ and $SE$ are the kinetic and surface energies, $A$ is the surface area, the subscripts $_1$ and $_2$ denote the intial 1-$g_0$, and low-g states, and the subscripts ${gl}$, ${sg}$, and ${ls}$ denote the gas-liquid, solid-gas and liquid-solid interfaces repectively.
 The motive force is due to the inertia of internal flows which occur as the interface deflects under the suddenely lessened $\mathbb{B}\mbox{o}$.
-\hl{The characteristic time scale of the rolling up scales as} $t_j \sim R_p/U ~(\rho H R^2_p/\sigma)^{1/2}$ \cite{attari_puddle_2016}, which resembles the contact time, $\tau \approx 2.6(\rho R^3_d/\sigma)^{1/2}$ presented by Richard \emph{et al.} in 2002 for the related problem of drops impacting hydrophobic surfaces in 1-$g_0$ \cite{richard_surface_2002}.
-For drops with radial symmetry and sufficiently high initial $\mathbb{B}\mbox{o}$ inward radial capillary waves coalesce at the axis, leading to geysering and creation of satellite droplets by the Rayleigh-Plateau breakup of the geyser.
+The characteristic time scale of the rolling up scales as $t_j \sim (\rho V_d/\sigma)^{1/2}$\cite{attari_puddle_2016}, which resembles the contact time, $\tau \approx 2.6(\rho R^3_d/\sigma)^{1/2}$ presented by Richard \emph{et al.} in 2002 for the related problem of drops impacting hydrophobic surfaces in 1-$g_0$\cite{richard_surface_2002}.
+For drops with radial symmetry and sufficiently high initial $\mathbb{B}\mbox{o}$, inward radial capillary waves coalesce at the axis, leading to geysering and creation of satellite droplets by the Rayleigh-Plateau breakup of the geyser.
 In the case of smaller jumping drops the capillary waves are gradually damped by viscous forces.
-A time-lapsed composite photograph of spontaneous drop jump can be seen in Figure \ref{fig:nobounce}
+A time-lapsed composite photograph of spontaneous drop jump can be seen in Figure \ref{fig:nobounce}.
 \begin{figure}[htb]
@@
 \includegraphics[width=0.75\textwidth]{drop_jump}
-\caption{The trajectory of a 0.2 mL drop is captured in a composite image over a period $\sim 0.67$ s at 120 fps. \label{fig:nobounce}}
+\caption{The trajectory of a 0.2 mL spontaneous drop jump is captured in a composite image over a period $\sim 0.67$ s at 120 fps. \label{fig:nobounce}}
 \end{figure}
@@
 \section{Drop Electro-Bounce}
-During the `rolling-up' of drops under ideal conditions, the spontaneous jump phenomenon is governed by a balance of inertia and surface tension forces, and once aloft the drop motion is nominally in a regime of pure drag, however other forces can again come into play.
+During the `rolling-up' of drops under ideal conditions, the spontaneous jump phenomenon is governed by a balance of inertia and surface tension forces, and once aloft the drop motion is nominally in a regime of pure drag.
+However, other forces can again come into play.
 
@@
 The forces at work in such situations are presumably electrostatic in origin.
-Though this was an unintended effect in our work on spontaneous drop jump, but the phenomenon is interesting itself.
-There is a certain irony to this typical failure of low-gravity intuition (the effect of relatively tiny electrostatic forces becoming suddenly large in the absence of gravity), being as we are experienced low-gravity researchers who perhaps should know better.
+Though this was an unintended effect during our work on spontaneous drop jump, the phenomenon is interesting itself.
+There is a certain irony to this typical failure of low-gravity intuition, where relatively tiny electrostatic forces have become suddenly large in the absence of gravity leading to unintentional experimental results, being as we are experienced low-gravity researchers who perhaps should know better.
 A time-lapsed composite image showing an example of the phenomenon is shown in Figure \ref{fig:bounce}.
@@
 There are several possible origins of the electric charge which are ultimately responsible for this phenonenon.
-It is well known that water acquires positive free charge when in contact with certain polymers, especially polytetrafluoroethylene (PTFE) \cite{langmuir_surface_1938}, through a process called contact charging.
-PTFE, on the other hand, tends to readily acquire negative chage by contact with water.
-The superhydrophobic surfaces used in the spontanous drop jump experiments have thin (nanometric) PTFE coatings, and we observe that it is extremely easy to produce significant surface potentials ($\varphi_s \sim$ 100-500 V) by simply flowing streams of distilled water over them.
-A study of this water on PTFE contact charging phenomenon was conducted by Yatsuzuka \emph{et al.} \cite{yatsuzuka_electrification_1994}, who suggest that this process results from formation of an electrical double layer driven by selective adsorption of ($\mbox{OH}^-$) ions at the polymer surface; other recent work strongly supports this hypothesis \cite{beattie_intrinsic_2006} \cite{strazdaite_water_2015}.
+It is well known that water acquires positive free charge when in contact with certain polymers, especially polytetrafluoroethylene (PTFE)\cite{langmuir_surface_1938}, through a process called contact charging.
+PTFE, on the other hand, tends to readily acquire negative charge by contact with water.
+The superhydrophobic surfaces used in the spontanous drop jump experiments have thin (nanometric) PTFE coatings, and we observe that it is extremely easy to produce significant surface potentials, $\varphi_s \sim$ 100-500 V, by simply flowing streams of distilled water over them.
+A study of this water on PTFE contact charging phenomenon was conducted by Yatsuzuka \emph{et al.}\cite{yatsuzuka_electrification_1994}, who suggest that this process results from formation of an electrical double layer driven by selective adsorption of ($\mbox{OH}^-$) ions at the polymer surface; other recent work strongly supports this hypothesis\cite{beattie_intrinsic_2006}\cite{strazdaite_water_2015}.
 Yatsuzuka \emph{et al.} also found that the specific charge on the drops in contact with the surface depends on their both surface velocity and conductivity.
@@
 Given the large roughness, or the ratio of projected to actual surface area, of the superhydrophobic surfaces used in the experiment, and given that the drops are initially in a Cassie-Baxter state, a somewhat electrically resistive air layer is maintained that reduces grounding of the drops despite the large potential difference between them and and the surface charges.
-If this electrostatic potential is greater than the release of surface energy under the sudden change in $\mathbb{B}\mbox{o}$ (in the form of the drop kinetic energy), we expect that the drop will return to an equilibrium state on the charged surface which minimizing the potential.
+If this electrostatic potential is greater than the release of surface energy under the sudden change in $\mathbb{B}\mbox{o}$, in the form of the drop kinetic energy, we expect that the drop will return to an equilibrium state on the charged surface which minimizes the potential.
 
@@
 The drop charge could of course also be due to the contact charging mechanism mentioned previously.
-For instance, in a 1996 paper, NASA flight engineer Don Pettit discusses the problem of low-gravity flow induced charging of liquids, resulting ultimately from contact charging phenomenon \cite{pettit_donald_flow_????}.
+For instance, in a 1996 paper, NASA flight engineer Don Pettit discusses the problem of low-gravity flow induced charging of liquids, resulting ultimately from contact charging phenomenon\cite{pettit_donald_flow_????}.
 Another mechanism for the drop charge is field-induced charging.
 Field-induced charging occurs due to physical breakup of a conductor having a field-induced dipole (e.g a physical seperation of charge).
-In our case this occurs when the drop is deposited on the charged surface by a syringe.
-The metal syringe needle tip, and the liquid in the syrigne itself are essentially a ground connection which is broken when the syringe is removed.
-Field-induced charging is at work in the famous Kevin thunderstorm, and is applied in inkjet, and electrospay technologies, where in each case the breakup is by the Rayleigh-Plateau instability.
-Notably, in Pettit's discussion of contact charging of liquids in low-g, he remarks on accidental electrostatic `hula-ing' of silicone oil drops when ejected from a syringe in the vicinity of a highly-charged polymer surface during an experiment conducted aboard STS-5 by mission specialist Joseph Allen \cite{pettit_donald_flow_????}.
+In our work this might occur when a drop is deposited on the charged surface by a grounded syringe.
+The metal syringe needle tip, and the liquid in the syringe itself are essentially a ground connection which is broken when the syringe is suddenly removed in the presence of an external electric field.
+Field-induced charging is at work in the famous Kelvin thunderstorm, and is applied in inkjet, and electrospay technologies, where in each case the breakup is by the Rayleigh-Plateau instability.
+Notably, in Pettit's aforementioned discussion of contact charging of liquids in low-g, he remarks on accidental electrostatic `hula-ing' of silicone oil drops when ejected from a syringe in the vicinity of a highly-charged polymer surface during an experiment conducted aboard STS-5 by mission specialist Joseph Allen\cite{pettit_donald_flow_????}.
 Depending on the (highly-variable) electrical conductivity of the silicone oil, and the material of the syringe used in the experiment, the charge could arise just as easily by field-induction as by contact charging.
-Relatedly, in a series of informal, and somewhat whimsical experiments, Pettit himself electrostatically orbited small water drops around a triboelectrically charged PTFE knitting needle while aboard ISS during expedition 30/31 \cite{stevenson_electrostatic_2015}.
+Relatedly, in a series of informal, and somewhat whimsical experiments, Pettit himself electrostatically orbited small water drops around a triboelectrically charged PTFE knitting needle while aboard ISS during expedition 30/31\cite{stevenson_electrostatic_2015}.
 Again, in this case, the drop charge is likely field-induced.
@@
 External surfaces of spacecraft tend to become charged with time due to the space environment itself.
-Surface charging largely occurs due to low energy electrons (3-50 keV) which do not penetrate the surface of the spacecraft external stucture \cite{czepiela_charging_1997}.
+Surface charging largely occurs due to low energy electrons (3-50 keV) which do not penetrate the surface of the spacecraft external stucture\cite{czepiela_charging_1997}.
 The ultimate sources of these charges are trapped charged particles of the van Allen radiation belts, galactic cosmic rays, and the solar wind.
@@
 In a fluid mechanical context, this accumulated charge could be problematic during any multiphase venting process, as might be expected to occur during autonomous satellite servicing refueling operations, or during boil-off venting of cryogens stored over long periods in a space environment (as in many crewed Mars mission scenarios, or in cryogenic propellant depot operations).
-Such venting, if occurring in a region of strong field, will also tend to produce a stream of charged droplets, which can then return and lead to contamination of the spacecraft surfaces.
+Such venting, if occurring in a region of strong field, will also tend to produce a stream of charged drops, which will be decelerated by the field, causing their eventual return, impacting and potentially contaminating the spacecraft surfaces.
 
 As previously noted, robust phase separation is critical to high reliability multiphase systems used in thermal control and life support.
-Active (but solid-state) phase seperation for life support multiphase flows, espcially high void-fraction flows is a possible application of this work.
-Such flows pertain to dish washing, laundry, waste solids drying, food processing, the Sabatier CO$_2$ reaction, and possibly in vapor-compression cycle condensers.
-Phase seperation for other disperse droplet flows include electrostatic droplet seperators for high-efficiency Rankine-cycle turbines (which require a droplet-free vapor phase entering the turbine, but where convertional superheat approaches comes with severe mass penalties) \cite{unterberg_zero_1962}, or more speculatively, in high temperature liquid droplet radiators with electrostatic collection \cite{white_liquid_1987}.
-Removal of satellite droplets produced during pippetting in wet-lab research outside of a glovebox environment aboard ISS has also been recently suggested as a application of the work \hl{[ref, personal discussion with NASA MSFC folk at ASGSR17 conference]}.
-Drops can become spontaneously charged by contact with standard micropipette tips \cite{choi_spontaneous_2013}, and this free charge can possibly be leveraged for the purposes of phase separation in low-gravity.
+Active (but solid-state) phase seperation for life support multiphase flows, espcially high void-fraction droplet-disperse flows is a possible application of this work.
+Such flows are encountered in dish washing, laundry, waste solids drying, food processing, the Sabatier CO$_2$ reaction, and possibly in vapor-compression cycle condensers.
+Phase seperation for other disperse droplet flows include electrostatic droplet seperators for high-efficiency Rankine-cycle turbines, which require a droplet-free vapor phase entering the turbine, but where conventional superheat approaches comes with severe mass penalties\cite{unterberg_zero_1962}, or more speculatively, in high temperature liquid droplet radiators with electrostatic collection\cite{white_liquid_1987}.
+Removal of satellite droplets produced during pippetting in wet-lab research outside of a glovebox environment aboard ISS has also been recently suggested as a application of the work [private communication, NASA JSC, E.
+Unger, 2017].
+Drops can become spontaneously charged by contact with standard micropipette tips\cite{choi_spontaneous_2013}, and this free charge can possibly be leveraged for the purposes of phase separation in low-gravity.
 
@@
 \item A mathematical model of the drop electro-bounce, its scale analysis, asymptotic estimates for drop apoapses and times-of-flight.
-\item The results of a controlled experiment, where the effect of key independent variables drop volume $V_d$, and dielectric surface charge density $\sigma$, on drop trajectories is tested.
-\item Science of opportunity comprising experimental data on drop impacts at very low Weber and Ohnesorge numbers, for varying levels of electrostatic Bond number. 
+\item The results of controlled experiments, where the effect of key independent variables drop volume $V_d$, and dielectric surface charge density $\sigma$, on drop trajectories is tested. 
 \end{enumerate}
@@
 \section{Forces and the Equation of Motion}
-This section will develop a simple, 1-dimensional model of the dynamics of drops dominated by electrostatic forces.
-We treat a drop as a particle, with radius $R_d$, which translates vertically along the central axis of a finite square charged dielectric sheet with initial velocity $U_0$.
+In this section we develop a simple, 1-dimensional model of the dynamics of drops dominated by electrostatic forces.
+We treat a drop as a particle with radius $R_d$, which translates vertically along the central axis of a charged dielectric square sheet substrate with initial velocity $U_0$.
 The equation of motion for this system is given by,
 \begin{equation}
-m y'' = - \mathbf{F}_D - \mathbf{F}_E, \hspace{5 mm} y(0) = R_d, \hspace{5 mm} y'(0) = U_0,
+m y'' = - \mathbf{F}_D - \mathbf{F}_E,
 \label{gov_eqn}
 \end{equation}
-where $m$ is the drop mass, $y'' = \frac{d^2 y}{d t^2}$ is the drop acceleration, $\mathbf{F}_D$ is the drag force, and $\mathbf{F}_E$ is the electrostatic force.
-The initial conditions are such that, when the $\mathbb{B}\mbox{o}$ is suddenly reduced at the start of the drop tower experiment, the drop jumps with initial velocity $U_0$ from its 1-$g_0$ resting position $R_d$ at $t=0$.
-The signs of the forces on the right side of Equation \ref{gov_eqn} indicate that they act in opposition direction of the drop motion.
-To stat to describe the drop electro-bounce we must define models for each of the forces in this equation.
-
-At intermediate range of Reynolds numbers $\mathbb{R}\mbox{e} \equiv \frac{2UR_d}{\nu}$, $1 \leq \mathbb{R}\mbox{e} \leq 5000 $ the force of drag acting on the drop will be quadratic such that,
+subject to
+\begin{equation}
+y(0) = R_d, \hspace{5 mm} \mbox{and} \hspace{5 mm} y'(0) = U_0,
+\end{equation}
+where $m$ is the drop mass, $y'' = \frac{d^2 y}{d t^2}$ is the drop acceleration, $\mathbf{F}_D$ is the drag force which always opposes motion, and $\mathbf{F}_E$ is the electrostatic force.
+The assumed initial conditions are such that, when $\mathbb{B}\mbox{o}$ is suddenly reduced at the start of the drop tower free-fall period, the drop jumps with instantaneous initial velocity $U_0$ from its 1-$g_0$ resting position with fixed radius $R_d$ at $t=0$.
+We now define models for each of the forces in this equation.
+
+For the intermediate range of Reynolds numbers $1 \leq \mathbb{R}\mbox{e} \equiv \frac{2UR_d}{\nu} \leq 5000 $ observed in our experiments the force of drag acting on the drop may be quadratic such that,
 \begin{equation*}\label{drag_force}
@@
 \end{equation*}
-where $C_D$ is the drag coefficient, $\rho$ is the density of the sorrounding fluid medium (air, in this case), and $A$ is the frontal area of the drop.
-For this range of Reynolds numbers it is appropriate to approximate the drag coefficient by the well known Abraham correlation \cite{abraham_functional_1970},
+where $C_D$ is the drag coefficient, $\rho$ is the density of the air host fluid, and $A$ is the frontal projected area of the drop.
+For this range of Reynolds numbers the drag coefficient may be approximated by the well known Abraham correlation\cite{abraham_functional_1970},
 \[C_D = \frac{24}{9.06^2} \left( 1 + \frac{9.06}{\sqrt{\mathbb{R}\mbox{e}}} \right)^2 .\]
 
-Modeling the electrostatic force is somehwhat more involved, but we will start with the standard electrohydrodynamic (EHD) approximation \cite{saville_electrohydrodynamics:taylor-melcher_1997} as our model, and further simplify where possible.
-Under a DC electric field, we assume that the real part of the dielectric permitivity $\epsilon$, $Re \langle \epsilon \rangle \approx  \mbox{constant}$.
+Modeling the electrostatic force is more involved, but we begin with the standard electrohydrodynamic (EHD) approximation\cite{saville_electrohydrodynamics:_1997}.
+Under a DC electric field, we assume that the real part of the dielectric permitivity $\epsilon$, $\mbox{Re} \langle \epsilon \rangle \approx  \mbox{constant}$.
 We also assume that electric currents are small enough that the effects of magnetic fields can be neglected.
-The validity of this assumption rests on the size of the characteristic time scale for electrical phenomena $\tau_e = \epsilon \epsilon_0/\sigma_e \ll 1$, where $\tau_e$ is the ratio of absolute dielectric permittivity $\kappa = \epsilon \epsilon_0$, to conductivity $\sigma_e$, of the medium.
+The validity of this assumption rests on the characteristic time scale for electrical phenomena $\tau_e = \epsilon /\sigma_e \ll 1$, where $\tau_e$ is the ratio of absolute dielectric permittivity $\epsilon = \kappa \epsilon_0$, to conductivity $\sigma_e$, of the medium, $\kappa$ is the relative dielectric permittivity, and $\epsilon_0$ is the vacuum permitivity.
 This characteristic time $\tau_e$ is also known as the relaxation time, and is a measure of how quickly the polarization of a dielectric responds to a change in electric field.
-Given the respective conductivity, and permittivity in the limiting case of extremely-pure water ($ \kappa \sim 80$, $\sigma_e = 18.2 \times 10^{6}$ $\Omega\mbox{cm}$) \cite{yatsuzuka_electrification_1994}, we estimate $\tau_e \approx 4 \times 10^{-6}$ s.
-The relaxation time for the common distilled water that is actually used in the drop experiments is undoubtedly even shorted (due to the presence of solvated ions).
-Neglecting the effects of a electric double layer on hydration of ions (in the water or the ambient atmosphere) due to the relatively massive size of the drops studied, then the assumption of small relaxation time further implies that the free charge present in the drops will remain approximately constant during the typical time interval of a low-gravity experiment.
-
-Supposing that electrical forces acting on free charges and dipoles in a fluid are transferred directly to the fluid itself, then this overall electrical body force will be the the divergence of the Maxwell stress tensor $\tau_m $,
-\[ \mathbf{F}_E = \nabla \cdot \tau_m = \nabla \cdot \left( \epsilon \epsilon_0 \mathbf{E} \mathbf{E} - \frac{1}{2} \epsilon \epsilon_0 \mathbf{E} \cdot \mathbf{E} \delta \right) ,\]
-where $\mathbf{F}_E$ is the electric body force per unit volume, and $\delta$ is the delta function. The product of the electric field vectors is the dyadic product.
-
-The classical Korteweg-Helmholtz volumetric force density formulation of the Maxwell stress tensor is usually expressed as \cite{melcher_continuum_????}
+Given the conductivity, and permittivity in the limiting case of extremely-pure water ($ \epsilon \sim 80$, $\sigma_e = 18.2 \times 10^{6}$ $\Omega\mbox{cm}$)\cite{yatsuzuka_electrification_1994}, we estimate $\tau_e \approx 4 \times 10^{-6}$ s.
+The relaxation time for the common distilled water that is actually used in the drop experiments is undoubtedly shorter due to the presence of solvated ions.
+Neglecting the effects of an electric double layer on hydration of ions in the water or the ambient atmosphere due to the relatively massive size of the drops studied, then the assumption of small relaxation time further implies that the free charge present in the drops will remain approximately constant during the typical time interval of a low-gravity experiment.
+
+Supposing that electrical forces acting on free charges and dipoles in a fluid are transferred directly to the fluid itself, the overall electrical body force will be the divergence of the Maxwell stress tensor $\tau_m $,
+\[ \mathbf{F}_E = \nabla \cdot \tau_m = \nabla \cdot \left( \epsilon \mathbf{E} \mathbf{E} - \frac{1}{2} \epsilon \mathbf{E} \cdot \mathbf{E} \delta \right) ,\]
+where $\mathbf{F}_E$ is the electric body force per unit volume, and $\delta$ is the Dirac delta function. The product of the electric field vectors is the dyadic product.
+
+The Korteweg-Helmholtz volumetric force density formulation of the Maxwell stress tensor is usually expressed as\cite{melcher_continuum_????}
 \begin{equation}\label{force_density}
@@
 \end{equation}
-The first term in this expression, is the well known Coulombic force or electrophoretic force, which arises from the presence of free charge in an external electric field.
+The first term on the right hand side this expression, is the well known Coulombic force or electrophoretic force, which arises from the presence of free charge in an external electric field.
 We expect this term to dominate the electric force in a DC field.
 The second term is the force arising from polarization stresses due to a nonuniform field acting across a gradient in permittivity.
-This force is widely termed the dielectrophoretic force (DEP).
+This force is widely termed the dielectrophoretic (DEP) force.
 The third term describes forces due to electrostriction.
-It has been noted by Melcher and Hurwitz that the electrostriction term is the gradient of a scalar and can thus be cannononically lumped togeather with the hydrostatic pressure for incompressible fluids \cite{hurwitz_electrohydrodynamic_1966}; we neglect it in our analysis.
-
-It is common to approximate the polarization stress by idealizing the drop as a simple dipole using the effective dipole moment method first described by Pohl in 1958 \cite{pohl_effects_1958}.
-This approach has since been related back to the force density by the volumetric integration of the force density with the substitution of a Taylor series expansion of $\mathbf{E}$ in the limit of a small radial gradient of the field within the dielectric sphere \cite{wang_general_1997}.
-The DEP force is related to the dipole moment (induced or permanent) of polarizable media which has a tendency to align the dipole with the electric field.
-If there is a gradient in the field then for a finite separation of charge one end of the dipole will feel a stronger electric field than the other, resulting in a net force.
+It has been noted by Melcher and Hurwitz that the electrostriction term is the gradient of a scalar and can thus be canonically lumped together with the hydrostatic pressure for incompressible fluids\cite{hurwitz_electrohydrodynamic_1966}.
+We neglect it in our analysis.
+
+It is common to approximate the polarization stress by idealizing the drop as a simple dipole using the effective dipole moment method first described by Pohl in 1958\cite{pohl_effects_1958}.
+This approach has since been related back to the force density by the volumetric integration of the force density with the substitution of a Taylor series expansion of $\mathbf{E}$ in the limit of a small radial gradient of the field within the dielectric sphere\cite{wang_general_1997}.
+The DEP force is related to the induced or permanent dipole moment of polarizable media which has a tendency to align the dipole with the electric field.
+If there is a gradient in the field then for a finite separation of charge, one end of the dipole will feel a stronger electric field than the other resulting in a net force.
 Whether the force is positive or negative in the direction of the electric field gradient depends on the difference of dielectric permittivites between the fluids, rather than on the polarity of $\mathbf{E}$.
-In principle an external electric field will tend to induce a dipole in a dielectric material, but if the field is spatially uniform there is no gradient in the field and the forces felt by the dipoles are symmetric and thus there is no net force.
-The dipole moment of a spherical linear-dielectric particle immersed in a dielectric medium is given by
+In principle an external electric field will tend to induce a dipole in a dielectric material, but if the field is spatially uniform there is no gradient in the field and the forces felt by the dipoles are symmetric with no net force.
+The dipole moment $\mu$, of a spherical linear-dielectric particle immersed in a dielectric medium is given by
 \begin{equation} \label{dipole_m_1}
@@
 \end{equation} 
-where $\mathbf{P} = \left(\kappa_1 - 1 \right) \epsilon_0 \mathbf{E} = \chi_e \epsilon_0 \mathbf{E}$ is the polarization moment, and $R_d$ is the particle radius, $\kappa_1 = \frac{\epsilon}{\epsilon_0}$ being the relative dielectric constant of the external medium (air in this case), $\chi_e = \kappa_1 - 1$ being the electric susceptibility of the dielectric medium.
-The excess polarization $\mathbf{P}_e$, in the sphere is given by
-\begin{equation} \label{polarization}
-\mathbf{P}_e = \left( \kappa_2 - \kappa_1 \right) \epsilon_0 \mathbf{E} = \frac{3 \kappa_1}{\kappa_2 +2\kappa_1}\mathbf{E},
-\end{equation}
-where $\kappa_2$ is the relative dielectric constant of the spherical particle.
-Taking together Equations \ref{dipole_m_1}, and \ref{polarization} the effective dipole moment of the particle is given by
-\begin{equation}\label{dipole_m_2}
-\mu = 4 \pi R_d^3 \left( \frac{\kappa_2 - \kappa_1}{\kappa_2 + 2 \kappa_1} \right) \kappa_1 \epsilon_0 \mathbf{E},
-\end{equation}
-and the force felt by the dipole is 
+where $\mathbf{P} = \left(\kappa_1 - 1 \right) \epsilon_0 \mathbf{E} = \chi_e \epsilon_0 \mathbf{E}$ is the polarization moment, and $R_d$ is the particle radius, $\kappa_1 = \frac{\epsilon_1}{\epsilon_0}$ is the relative dielectric constant of the air host fluid, $\chi_e = \kappa_1 - 1$ is the electric susceptibility of the host fluid.
+The force felt by the dipole is
 \begin{eqnarray} \label{dep_force}
 \mathbf{F}_{DEP} &=& \left( \mathbf{P}_e \cdot \nabla \right) \mathbf{E} \nonumber \\
-&=& 2 \pi R_d^3 \kappa_1 \epsilon_0 K \nabla E^2,
+&=& 2 \pi R_d^3 \epsilon K \nabla E^2,
 \end{eqnarray}
-where it is nice to use the simplifying shorthand $K = \frac{\kappa_2 - \kappa_1}{\kappa_2 + 2 \kappa_1}$, which is also known as the Clausius-Mossotti factor.
-In cases where $K <$ 0, or $K>$ 0 the particle will be repelled or attracted to regions of strong field respectively.
-In our experiment, taking the relative dielectric constants to be $\kappa_1 \approx$ 1 and $\kappa_2 \approx$ 80, the Clausius-Mossotti factor $K \approx$ 0.96.
-It is important to note that the equivalent dipole approximation critically requires an assumption of small physical scale of the particle relative to the lengthscale of nonuniformity of the field, which in this case we take to be the length of the charged superhydrophobic surface ($L =$ 25 mm $\gg a \approx$ 2.5 mm).
-
-When the drop is close to the dielectric surface, the free charge on the drop will tend to induce polarization of the dielectric, perturbing the electric field.
+where $\mathbf{P}_e=(\kappa_2 - \kappa_1)\epsilon_0 \mathbf{E}$ is the excess polarization, and $\kappa_2$ is the relative dielectric constant of the water particle.
+Here it is convenient to use the simplifying shorthand $K = \frac{\kappa_2 - \kappa_1}{\kappa_2 + 2 \kappa_1}$, known as the Clausius-Mossotti factor.
+In cases where $K <$ 0, or $K>$ 0 the particle will be either repelled or attracted to regions of strong field.
+In our experiment, choosing the relative dielectric constants $\kappa_1 \approx$ 1 and $\kappa_2 \approx$ 80, $K \approx$ 0.96.
+It is important to note that the equivalent dipole approximation critically requires an assumption of small physical scale of the particle relative to the length scale of nonuniformity of the field, which in this case we take to be the length of the charged superhydrophobic surface, $L =$ 25 mm $\gg R_d \approx$ 2 mm.
+
+When the drop is close to the dielectric surface, the free charge on the drop will tend to induce polarization of the dielectric which perturbs the electric field.
 The polarization bound charge in the dielectric will be of the opposite sign of the free drop charge and thus there will be a force of attraction.
-This so-called image force is a correction to the Colomb force due to the external electric field only, and can be found by the method of images \cite{david_j._griffiths_introduction_1999}.
-The image force $\mathbf{F}_I$, is given by
+This so-called image force is a correction to the Coulomb force due to the external electric field only, and can be found by a Green's Function solution to Laplace's equation for the electric field called the `method of images'\cite{david_j._griffiths_introduction_1999}.
+This resulting image force $\mathbf{F}_I$, is given by
 \begin{equation}
@@
 
-By substituting Equations \ref{dep_force}, \ref{image_force} into Equation \ref{force_density} we have
+By substituting Equations \ref{dep_force}, and \ref{image_force} into \ref{force_density} we have
 \begin{eqnarray*}
  \mathbf{F}_E &=& q \mathbf{E} + \mathbf{F}_{DEP} + \mathbf{F}_I \\
- &=& q \mathbf{E} + \frac{k q^2}{16 \pi \epsilon_0 } y^{-2} \hat{\mathbf{j}} + 2 \pi R_d^3 \kappa_1 \epsilon_0 K \nabla E^2, 
+ &=& q \mathbf{E} + \frac{k q^2}{16 \pi \epsilon_0 } y^{-2} \hat{\mathbf{j}} + 2 \pi R_d^3 \epsilon K \nabla E^2, 
 \end{eqnarray*}
 and the 1-D governing equation becomes
-\begin{eqnarray} \label{gov_eqn_subs}
-&m y'' = - \frac{1}{2} C_D \rho A {y'}^2 - q E - \frac{k q^2}{16 \pi \epsilon_0} y^{-2}- 2 \pi R_d^3 \kappa_1 \epsilon_0 K \nabla E^2,& \nonumber \\
-&y(0) = R, \hspace{1 mm} y'(0) = U_0 .&
+\begin{equation}
+ \label{gov_eqn_subs}
+m y'' = - \frac{1}{2} C_D \rho A {y'}^2 - q E - \frac{k q^2}{16 \pi \epsilon_0} y^{-2}- 2 \pi R_d^3 \kappa_1 \epsilon_0 K \nabla E^2,
+\end{equation}
+subject to
+\begin{equation}
+y(0) = R, \hspace{5 mm} \mbox{and} \hspace{5 mm} y'(0) = U_0 .
+\end{equation}
+
+By comparing DEP and Coulombic terms in Equation \ref{gov_eqn_subs}, we note that a condition to neglect the DEP force is
+\begin{eqnarray}
+\frac{ \kappa_2 \epsilon_0 K R_d^2 E_0}{q} \ll 1 \nonumber
 \end{eqnarray}
-
-By comparing DEP and Coulombic terms in Equation \ref{gov_eqn_subs}, we note that a condition to neglect the DEP term is
-\begin{eqnarray}
-\frac{q}{ \kappa_2 \epsilon_0 K R_d^2 E_0} \gg 1 \nonumber
-\end{eqnarray}
-As this condition likely holds in our experiments we henceforth neglect the DEP force in our analysis.
+As this condition likely prevails in our experiments we henceforth neglect the DEP force.
 There is some physical intuition to support this conclusion as well.
-The dielectric displacement, $\mathbf{D} = \kappa \epsilon_0 \mathbf{E}$ of a water drop in air is very high due to its large relative dielectric constant.
-This implies that the field strength within the drop is about 2 orders of magnitude smaller than in the surrounding medium (which is essentially the same as a vacuum from a dielectric standpoint), thus it is not particularly inaccurate to model the dielectric volume of a drop as a conductive shell (an equipotential), with zero field in its interior.
+The dielectric displacement $\mathbf{D} = \kappa \epsilon_0 \mathbf{E}$ of a water drop in air is very high due to its large relative dielectric constant.
+This implies that the field strength within the drop is about 80 times smaller than in the surrounding medium (which is essentially the same as a vacuum from a dielectric standpoint), thus it is not particularly inaccurate to model the dielectric volume of a drop as an equipotential conductive shell, with zero field in its interior.
 As an aside, in treating the drop as an ideal conductor we note that in our specific case the electrostatic force is not a body force \emph{per se} as the electric field is acting on charges on the surface of the conductor.
@@
 If we consider the charged dielectric surface of our experiments to be a square sheet of charge lying in the $xz$-plane with width $L$, the symmetry of the problem happily lets us obtain the $y$-component of the electric field $\mathbf{E}$ by direct integration.
-In particular it is easy to constuct the electric field due to a finite plane of charge by superposition of the electric fields of a series of line charges.
-By symmetry the electric field points along the $y$-axis; for a point along the $y$-axis the position vector is $\mathbf{r} = \left( x^2 + y^2 \right)^{1/2} \hat{\mathbf{r}}$ to the center of a line charge in the $xz$-plane.
+In particular, it is easy to constuct the electric field due to a finite plane of charge by superposition of the electric fields of a series of line charges.
+By symmetry, the electric field points along the $y$-axis; for a point along the $y$-axis the position vector is $\mathbf{r} = \left( x^2 + y^2 \right)^{1/2} \hat{\mathbf{r}}$ to the center of a line charge in the $xz$-plane.
 The $y$-component of $d\mathbf{E}$ is found by $d E_r = d E_y \cos \theta = d E_y y/ r$, where $\theta$ is the angle made between the $y$-axis and the position vector $\mathbf{r}$.
-If the charge in a line element, $dx$ is $\sigma L dx$, where $\sigma$ is the average surface charge density, the electric field of a line charge is given by \cite{david_j._griffiths_introduction_1999}
+If the charge in a line element, $dx$ is $\sigma L dx$, where $\sigma$ is the average surface charge density, the electric field of a line charge is given by\cite{david_j._griffiths_introduction_1999}
 \[d E_r = \frac{k \sigma L dx}{4 \pi \epsilon_0 r \sqrt{r^2 + L^2/4}}.
 \]
-The $y$-component of the electric field $E_y$, is then
-\[ E_y = \frac{\sigma L y }{4 \pi \epsilon_0} \int^{L/2}_{-L/2} \frac{1}{(y^2 + x^2) \sqrt{y^2 + x^2 + L^2/4}} dx 
+The $y$-component of the electric field $E_y$, hence $E$, is then
+\[ E = \frac{\sigma L y }{4 \pi \epsilon_0} \int^{L/2}_{-L/2} \frac{1}{(y^2 + x^2) \sqrt{y^2 + x^2 + L^2/4}} dx 
 .\]
-With some substitutions this can be integrated to obtain an expression for the electric field in terms of $y$, 
+With some substitutions the above can be integrated to obtain an expression for the electric field in terms of $y$, 
 \begin{equation}
-E_y = \frac{\sigma}{ \pi \epsilon_0} \tan^{-1} \left( \frac{L^2}{y \sqrt{2L^2 + 4y^2}}\right)
+\label{e_field}
+E = \frac{\sigma}{ \pi \epsilon_0} \tan^{-1} \left( \frac{L^2}{y \sqrt{2L^2 + 4y^2}}\right)
 .\end{equation}
-We note that this model of the electric field will be poor except in cases where $y \ll L, \hspace{1 mm} R_d \ll L$, which will be true for cases of large drops very close to the dielectric surface.
-For accurate models of the field in this case we likely would need to solve Laplace's equation for the electric potential $\varphi$
+We note that this model of the electric field is valid when $R_d \ll L$, which will be true for cases of small drops `far' from the dielectric surface.
+For accurate models of the field in the case $R_d/L \sim \mathcal{O}(1)$ we likely need to solve Laplace's equation for the electric potential $\varphi$,
 \[ - \nabla^2 \varphi = 0,\]
-numerically using finite element methods.
-
-By taking Taylor series expansions in large and small limits we can intuit a bit about the behavior of this field.
-In the limit $L \rightarrow \infty, \hspace{1mm} y \ll L$ the argument of the function tends towards infinity and
-\[ \lim_{x\to\infty} \tan^{-1}(x) = \frac{\pi}{2}
-,\]
-and thus
+using numerical methods.
+
+By taking Taylor series expansions in large and small limits we can intuit a bit about the behavior of this field. In the limit $y/L \ll 1$ Equation \ref{e_field} reduces to
 \begin{equation}
-E_y \approx \frac{\sigma}{4 \pi \epsilon_0} = E_0 \hspace{10mm} y \ll L
+\label{near_field}
+E \approx \frac{\sigma}{4 \pi \epsilon_0} = E_0,
 ,\end{equation}
 where $E_0$ is the characteristic electric field given by $E_0 = \frac{\sigma}{4 \pi \epsilon_0}$.
-This field is constant, and equivalent to the electric field due to an infinite plane of charge.
-In the limit of $y \gg L$, the argument of the arctangent function can be approximated by
-\[ \frac{L^2}{2 y \left( 2 L^2 + 4 y^2\right)^{1/2}} = \frac{L^2}{4 y^2 \left( 1 + L^2/2y^2 \right)^{1/2}} \approx \frac{L^2}{4 y^2}
-.\]
-For small $x$, $\tan^{-1}(x) \sim x$ and we thus find the familiar electric field due to a point charge
+This field is constant and equivalent to the electric field due to an infinite plane of charge.
+In the limit of $y/L \gg 1$, Equation \ref{e_field} reduces to the familiar electric field due to a point charge
 \begin{equation}
-E_y \approx L^2 E_0 y^{-2}  \hspace{10mm} y \gg L
-.\end{equation}
-Both of these regimes can be clearly seen in the plot of $E_y$ shown in Figure \ref{fig:E0}.
-\begin{figure}[htb]
-    \centering
-    \input{../figures/E0.pgf}
-    \caption{A log-log plot of the magnitude of the non-dimensional electric field, $E_y$.\label{fig:E0}}
+\label{far_field}
+E \approx L^2 E_0 y^{-2}.
+\end{equation}
+Both regimes given by Equations \ref{near_field}, \ref{far_field} can be clearly seen in Figure \ref{fig:E0}.
+\begin{figure}[h]
+    \centering
+    \def\svgwidth{\columnwidth}
+    \input{../figures/E02.pdf_tex}
+    \caption{A log-log plot of the magnitude of the dimensionless electric field $E$.\label{fig:E0}}
 \end{figure}
@@
 \section{Scaling}
-The equation of motion is non-linear, non-homogeneous and is best solved numerically, but nevertheless we are curious if we can obtain approximate solutions to the equation analytically using perturbation methods.
-This is aided by non-dimensionalizing the governing equations, and seeing if any dimensionless groups exist, and whether any are particularly small or large, and whether any fortuitous opportunities for simplification appear.
+For small DEP forces, the equation of motion, Equation \ref{gov_eqn_subs}, is non-linear, non-homogeneous and must be solved numerically.
+Nevertheless we are curious if we can obtain approximate solutions to the equation analytically using perturbation methods.
+This is aided by non-dimensionalizing the governing equations, forming dimensionless groups, and determining whether any are particularly small or large, and whether any fortuitous opportunities for simplification appear.
 Introducing the scaled variables
 \begin{equation}
- \bar{t} = \frac{t}{t_c}, \hspace{10 mm} \bar{y} = \frac{y}{y_c}, \end{equation}
+ t^* = \frac{t}{t_c}, \hspace{10 mm} y^* = \frac{y}{y_c}, \end{equation}
 where $y_c$ and $t_c$ are characteristic length and time scales respectively, and using the coordinate transformation $y(0) - R = 0$, the governing equation becomes
 \begin{eqnarray}
-& \bar{y}'' = - \frac{1}{2} \frac{C_D \rho A y_c}{m} \bar{y}'^2
-- \frac{q E_0 t_c^2}{m y_c} \bar{E} ( \bar{y} ) 
-- \frac{k q^2 t_c^2}{16 \pi \epsilon_0 R^2 m y_c} \left( \frac{y_c}{R} \bar{y} + 1 \right)^{-2}, & \nonumber \\
-& \bar{y}(0) = 0, \hspace{1 mm} \bar{y}'(0) = \frac{U_0 t_c}{y_c} .& \label{scaled_eqn}
+& {y^*}'' = - \frac{1}{2} \frac{C_D \rho A y_c}{m} {y^*}'^2
+- \frac{q E_0 t_c^2}{m y_c} E^* ( {y^*} ) 
+- \frac{k q^2 t_c^2}{16 \pi \epsilon_0 R^2 m y_c} \left( \frac{y_c}{R} {y^*} + 1 \right)^{-2}, & \label{scaled_eqn}
 \end{eqnarray}
+subject to 
+\begin{equation*}
+{y^*}(0) = 0, \hspace{5 mm} \mbox{and} \hspace{5 mm} {y^*}'(0) = \frac{U_0 t_c}{y_c} .
+\end{equation*}
 We note the existence of several dimensionless groups
@@
 \mathbf{\Pi}_4 = \frac{y_c}{R}, \hspace{5 mm}
-\mathbf{\Pi}_5 = \frac{U_0 t_c}{y_c}.\]
+\mathbf{\Pi}_5 = \frac{U_0 t_c}{y_c},\]
+such that Equation \ref{scaled_eqn} becomes
+\begin{equation}
+\label{pi_terms}
+ {y^*}'' = - \mathbf{\Pi}_1 {y^*}'^2
+- \mathbf{\Pi}_2 E^* ( {y^*} ) 
+- \mathbf{\Pi}_3 \left( \mathbf{\Pi}_4 {y^*} + 1 \right)^{-2},
+\end{equation}
+subject to
+\begin{equation*}
+{y^*}(0) = 0, \hspace{5 mm} \mbox{and} \hspace{5 mm} {y^*}'(0) = \mathbf{\Pi}_5 .
+\end{equation*}
+\begin{figure}[ht]
+ \centering
+ \includegraphics[width=0.75\textwidth]{../figures/apparatus0.pdf}
+ \caption{A schematic representation of a drop electro-bounce experiment with labeled characteristic time and length scales, \hl{$t_c$, $y_c$} shown.
+Also shown are the dimensions of the superhydrophobic electret substrate.\label{fig:apparatus0}}
+\end{figure}
 
 \subsection{Inertial Electro-Image Limit}
-In the limit of small $y$ and $t$ we expect inertia to scale as Coulombic and image force.
-In this limit we can approximate the electric field as the constant, $E_0$.
-One possible characteristic length scale is $y_c \sim R_d$, however this ultimately is a poor choice.
-With $y_c \sim U_0 t_c$ and picking $t_c$ such that Coulombic force is $\mathcal{O}(1)$, the intrinsic scales become
-\[ t_c \sim \frac{m U_0}{q E_0}, \hspace{5 mm}
+In the limit of small $y$ and $t$ we expect inertia to scale with Coulombic and image forces.
+In this limit we can approximate the electric field as the constant $E_0$.
+One possible characteristic length scale is $y_c \sim R_d$, however this scale is overly restrictive with respect to time.
+With $y_c \sim U_0 t_c$ and picking $t_c$ such that the Coulombic force $\mathbf{\Pi}_3 \sim \mathcal{O}(1)$, the intrinsic scales are found such that
+\[ t_c \sim \frac{m U_0}{q E_0}, \hspace{5 mm} \mbox{and} \hspace{5 mm} 
 y_c \sim \frac{m U_0^2}{q E_0} .
 \]
-With these scales the governing equation then becomes
-\begin{eqnarray}
-& \bar{y}'' = -1 - \mathbb{I}\mbox{m} \left( \mathbb{E}\mbox{u}\bar{y} + 1 \right)^{-2} ,& \nonumber \\
-& \bar{y}(0) = 0, \hspace{1 mm} \bar{y}'(0) = 1 .& \label{img_limit}
-\end{eqnarray} 
+With these scales the governing equation \ref{pi_terms} becomes
+\begin{equation}
+{y^*}'' = -1 - \mathbb{I}\mbox{g} \left( \mathbb{E}\mbox{u}{y^*} + 1 \right)^{-2} , \label{img_limit}
+\end{equation}
+subject to
+\begin{equation*}
+{y^*}(0) = 0, \hspace{5 mm} \mbox{and} \hspace{5 mm} {y^*}'(0) = 1 .
+\end{equation*}
 with 
-\[ \mathbb{I}\mbox{m} \equiv \frac{k q}{16 \pi \epsilon_0 R_d^2 E_0} = \mathbf{\Pi}_3, \hspace{5 mm}
+\[ \mathbb{I}\mbox{g} \equiv \frac{k q}{16 \pi \epsilon_0 R_d^2 E_0} = \mathbf{\Pi}_3, \hspace{5 mm}
 \mathbb{E}\mbox{u} \equiv \frac{m U_0^2}{q E_0 R_d} = \mathbf{\Pi}_4 ,
 \]
-where $\mathbb{I}\mbox{m}$ is the Image number, and denotes the ratio of image forces to the Coulombic force of the unperturbed field, and where $\mathbb{E}\mbox{u}$ is the electrostatic Euler number, and is a ratio of inertia to electrostatic force.
+where the Image number $\mathbb{I}\mbox{g}$ is the ratio of image forces to the Coulombic force of the unperturbed field, and the electrostatic Euler number $\mathbb{E}\mbox{u}$ is the ratio of inertia to electrostatic force.
 With these dimensionless groups the intrinsic scales become
-\[ t_c = \mathbb{E}\mbox{u} \frac{R_d}{U_0}, \hspace{5 mm}
+\[ t_c = \mathbb{E}\mbox{u} \frac{R_d}{U_0}, \hspace{5 mm} \mbox{and} \hspace{5 mm}
 y_c = \mathbb{E}\mbox{u} R_d.
@@
 \subsection{Inertial Electro-Viscous Limit}
-In the limit of large $y$ and $t$ we expect drop inertia to scale as Coulombic force and drag.
+In the limit of large $y$ and $t$ we expect drop inertia to balance Coulombic force and drag.
 In this limit we approximate the electric field as $E \approx y_c^2 E_0 y^{-2}$.
-In this case there are several (obvious) possible choices of scales:
+In this case there are several obvious possible choices of scales:
 \begin{enumerate}
-\item $y_c \sim U_0 t_c$, and make Coulomb force $\mathcal{O}(1)$.
-\item $y_c \sim L$, $t_c \sim \frac{L}{U_0}$ (however, this makes Equation \ref{scaled_eqn} singular).
+\item $y_c \sim U_0 t_c$, and $\mathbf{\Pi}_3 \sim \mathcal{O}(1)$.
+\item $y_c \sim L$, $t_c \sim \frac{L}{U_0}$ (making Equation \ref{scaled_eqn} singular).
 \item $y_c \sim L$, $t_c \sim \left( \frac{L m}{q E_0} \right)^{1/2}$.
-\item $y_c \sim L$, and make Coulomb force $\mathcal{O}(1)$.
+\item $y_c \sim L$, and $\mathbf{\Pi}_3 \sim \mathcal{O}(1)$.
 \end{enumerate}
@@
 
-We prefer the approach with the greatest physical simplicity, fewest Pi terms, and that has homogeneous initial conditions. We choose Case 1, where the intrinsic scales are given by
-\[ t_c \sim \frac{R_d^2}{L^2} \frac{4 \pi m U_0}{q E_0}, \hspace{5mm} y_c \sim \frac{R_d^2}{L^2} \frac{4 \pi m U_0^2}{q E_0}.
+We choose the Case 1 scaling for its combination of physical simplicity, few $\mathbf{\Pi}$ terms, and homogeneous initial conditions. The intrinsic scales for this case are given by
+\[ t_c \sim \frac{R_d^2}{L^2} \frac{4 \pi m U_0}{q E_0}, \hspace{5mm} \mbox{and} \hspace{5 mm} y_c \sim \frac{R_d^2}{L^2} \frac{4 \pi m U_0^2}{q E_0}.
 \]
@@
 \begin{eqnarray}
-&\bar{y}'' = - \mathbb{D}\mbox{g} \mathbb{E}\mbox{u}_+ \bar{y}'^2 - \left( \mathbb{E}\mbox{u}_+ \bar{y} + 1 \right)^{-2}, & \nonumber \\
-& \bar{y}(0) = 0, \hspace{1 mm} \bar{y}'(0) = 1 & \label{drag_limit}
+&{y^*}'' = - \mathbb{D}\mbox{g} B \mathbb{E}\mbox{u} {y^*}'^2 - \left( B \mathbb{E}\mbox{u} {y^*} + 1 \right)^{-2}, & \label{drag_limit}
 \end{eqnarray}
-where we call $\mathbb{D}\mbox{g}$ the drag number, $\mathbb{D}\mbox{g} \equiv \frac{C_D \rho_a}{\rho_l} = \mathbf{\Pi}_1 {\mathbb{E}\mbox{u}}_+^{-1}$ and $\mathbb{E}\mbox{u}_+ = 4 \pi \frac{R_d^2}{L^2} \mathbb{E}\mbox{u}$.
+subject to 
+\begin{equation*}
+{y^*}(0) = 0, \hspace{5 mm} \mbox{and} \hspace{5 mm} {y^*}'(0) = 1, 
+\end{equation*}
+where we call $\mathbb{D}\mbox{g}$ the drag number $\mathbb{D}\mbox{g} \equiv \frac{C_D \rho_a}{\rho_l} = \mathbf{\Pi}_1 B^{-1}{\mathbb{E}\mbox{u}}^{-1}$, and $B = 4 \pi \frac{R_d^2}{L^2}$ is a dimensionless ratio of length scales.
 
@@
 The alternate scalings of the equation of motion given by Equations \ref{img_limit}, and \ref{drag_limit} are weakly non-linear differential equations in the sense that they reduce to linear equations as the parameter $\mathbb{E}\mbox{u} \rightarrow 0$.
-If we take $\mathbb{E}\mbox{u}$ to be a small parameter $\epsilon$, we can find an asymptotic approximation to the solution of the non-linear equation by means of a regular perturbation.
+If we take $\mathbb{E}\mbox{u}$ to be a small parameter we can find an asymptotic approximation to the solution of the non-linear equation by means of a regular perturbation.
 In this case we use the naive expansion
-\[ \bar{y}(\bar{t}) \sim \bar{y}_0(\bar{t}) + \epsilon \bar{y}_1(\bar{t}) + \epsilon^2 \bar{y}_2(\bar{t}) \ldots \epsilon^n\bar{y}_n(\bar{t})  
-.\]
-
-By substitution of the expansion (and its derivatives) into the differential equation, and equating terms by order, and using the notation $\alpha = \mathbb{I}\mbox{m}$ (this being the equation scaled in the small-times limit), we first find the $\mathcal{O}(1)$, unperturbed, solution to the equation of motion to be
-\[{\bar{y}_{0}}{\left (\bar{t} \right )} = \bar{t} + \frac{\bar{t}^{2}}{2} \left(-1 - \alpha\right). \]
-
-Looking at this solution it is evident that if we let $\alpha=0$, the solution is the classical kinematic equation for projectile motion without drag under constant gravity, $g_0$.
-Continuing on with this procedure we find, (after some tedious computations, documented in in the project repository for this thesis \cite{schmidt_droplet_electro-bounce:_2017}) the higher order composite solutions to be
-\begin{eqnarray*}
-&\bar{y}(\bar{t}) = \bar{t} + \frac{\bar{t}^{2}}{2} \left(-1 - \alpha\right) + \epsilon \left(\frac{\alpha \bar{t}^{3}}{3} + \frac{\alpha \bar{t}^{4}}{12} \left(-1 - \alpha\right)\right)& \\
-&+ \epsilon^{2} \left(- \frac{\alpha \bar{t}^{4}}{4} + \frac{\alpha \bar{t}^{5}}{60} \left(9 + 11 \alpha\right) + \frac{\alpha \bar{t}^{6}}{360} \left(-9 - 20 \alpha - 11 \alpha^{2}\right)\right) + \mathcal{O}(\epsilon^3)&.
-\end{eqnarray*}
-
-In fact we, for somewhat arbitrary reasons, computed an $\mathcal{O}(\epsilon^5)$ accurate solution, but it is far to ugly to reprint here in its entirety.
-However, we plot these approximate short-time scaled solutions with varying values of the Image number, $\mathbb{I}\mbox{m} = \alpha$ in Figure \ref{fig:short_times}.
+\begin{equation}
+{y^*}({t^*}) \sim y^*_0({t^*}) + \mathbb{E}\mbox{u} y^*_1({t^*}) + \mathbb{E}\mbox{u}^2 y^*_2({t^*}) \ldots \mathbb{E}\mbox{u}^n y^*_n ({t^*})  . \label{regular_pert}
+\end{equation}
+
+By substitution of the expansion  \ref{regular_pert} and its derivatives into \ref{pi_terms}, and equating terms by order we first find the $\mathcal{O}(1)$ unperturbed solution
+\[{y^*_{0}}{\left ({t^*} \right )} = {t^*} + \frac{{t^*}^{2}}{2} \left(-1 - \mathbb{I}\mbox{g}\right). \]
+Looking at this solution it is evident that if $\mathbb{I}\mbox{g}=0$, the solution is the classical kinematic equation for projectile motion without drag under constant gravity $g_0$.
+Continuing on with this procedure we find, after some tedious computations documented in in the project repository for this thesis\cite{schmidt_droplet_electro-bounce:_2017}, the $\mathcal{O}(\mathbb{E}\mbox{u}^5)$ order accurate solution, truncated to $\mathcal{O}(\mathbb{E}\mbox{u}^2)$ below.
+\begin{eqnarray}
+\label{perturb_image}
+&{y^*}({t^*}) = {t^*} + \frac{{t^*}^{2}}{2} \left(-1 - \mathbb{I}\mbox{g}\right) + \mathbb{E}\mbox{u} \left(\frac{\mathbb{I}\mbox{g} {t^*}^{3}}{3} + \frac{\mathbb{I}\mbox{g} {t^*}^{4}}{12} \left(-1 - \mathbb{I}\mbox{g} \right)\right)& \\
+&+ \mathbb{E}\mbox{u}^{2} \left(- \frac{\mathbb{I}\mbox{g} {t^*}^{4}}{4} + \frac{\mathbb{I}\mbox{g} \bar{t^*}^{5}}{60} \left(9 + 11 \mathbb{I}\mbox{g} \right) + \frac{\mathbb{I}\mbox{g} {t^*}^{6}}{360} \left(-9 - 20 \mathbb{I}\mbox{g} - 11 \mathbb{I}\mbox{g}^{2}\right)\right) + \mathcal{O}(\mathbb{E}\mbox{u}^3).&\nonumber
+\end{eqnarray}
+We plot the approximate short-time scaled solution Equation \ref{perturb_image} with varying values of $\mathbb{I}\mbox{g}$ in Figure \ref{fig:short_times}.
 %\newpage
@@
     \resizebox{1\textwidth}{!}{\input{../figures/short_times.pgf}}
-    \caption{Non-dimensional drop trajectories for various values of $\mathbb{E}\mbox{u}=\epsilon$, $\mathbb{I}\mbox{m}=\alpha$.
-The trajectory reduces to the classical $\mathcal{O}(1)$ solution for small values of $\alpha$.
-It should be noted that despite what is implied by these plots $\alpha$ is not necessarily completely independent of $\epsilon$, as they share $q$, and $E_0$ as common factors, $U_0 \sim R_d^2$, and $m \sim R_d^3$.}
+    \caption{Short-time scaled drop trajectories for various values of $\mathbb{E}\mbox{u}$, $\mathbb{I}\mbox{g}$.
+The trajectory reduces to the classical $\mathcal{O}(1)$ solution for small values of $\mathbb{I}\mbox{g}$.
+It should be noted that despite what is implied by these plots $\mathbb{I}\mbox{g}$ is not necessarily independent of $\mathbb{E}\mbox{u}$, as they share $q$, and $E_0$ as common factors, $U_0 \sim R_d^2$, and $m \sim R_d^3$.}
     \label{fig:short_times}
 \end{figure}
-These plots show a trend of decreasing time-of-flight (the time for the drop to return to the origin, or complete a single ``bounce''), and height at apoapse with increasing values of the Image number $\alpha$.
-When $\alpha = 1$ the time of flight is exactly half of characteristic time scale in this regime.
-In the limit of small $\epsilon$ the trajectories collapse to the $\mathcal{O}(1)$ solution regardless of the Image number.
-In principle there is some coupling between $\mathbb{E}\mbox{u}$ and $\mathbb{I}\mbox{m}$; notably this relationship does not depend on the electric field $E_0$ but on a charge to mass ratio.
+These plots show a trend of decreasing time-of-flight $t_f$, which is the time for the drop to return to the origin, or complete a single ``bounce'', and height at apoapse with increasing values of $\mathbb{I}\mbox{g}$.
+When $\mathbb{I}\mbox{g} = 1$, $t_f$ is exactly half of characteristic time scale in this regime.
+In the limit of small $\mathbb{E}\mbox{u}$ the trajectories collapse to the $\mathcal{O}(1)$ solution regardless of the Image number.
+In principle there is some coupling between $\mathbb{E}\mbox{u}$ and $\mathbb{I}\mbox{g}$; notably this relationship does not depend on the electric field $E_0$ but on a charge to mass ratio.
 The effect of contact line hysteresis on the initial jump velocity $U_0$ will also tend to independently decohere the natural covariance between these parameters.
@@
 \subsection{Inertial Electro-Viscous Limit}
-By similar arguments we find an asymptotic estimate of the trajectory in the long-times scaled regime.
-With $\epsilon = {\mathbb{E}\mbox{u}}_+$, where $\epsilon$ again is a small parameter, and $\beta = \mathbb{D}\mbox{g}$, the approximate solution is
+By similar arguments we find an asymptotic estimate of the trajectory in the long-time regime. The approximate solution is 
 \begin{eqnarray*}
-&\bar{y}(\bar{t}) = \bar{t} - \frac{\bar{t}^{2}}{2} + \epsilon \left(\frac{\bar{t}^{3}}{3} \left(1 + \beta\right) + \frac{\bar{t}^{4}}{12} \left(-1 - \beta\right) - \frac{\beta \bar{t}^{2}}{2}\right)&  \\
-&+ \epsilon^{2} \left(\frac{\bar{t}^{4}}{12} \left(-3 - 3 \beta - 4 \beta^{2}\right) + \frac{\bar{t}^{5}}{60} \left(11 + 10 \beta + 8 \beta^{2}\right)+ \frac{\bar{t}^{6}}{360} \left(-11 - 10 \beta - 8 \beta^{2}\right) + \frac{\beta^{2} \bar{t}^{3}}{3}\right)& \\
- &+ \mathcal{O}(\epsilon^3)&.
+\label{perturb_viscous}
+&{y^*}({t^*}) = {t^*} - \frac{{t^*}^{2}}{2} + B\mathbb{E}\mbox{u} \left(\frac{{t^*}^{3}}{3} \left(1 + \mathbb{D}\mbox{g}\right) + \frac{{t^*}^{4}}{12} \left(-1 - \mathbb{D}\mbox{g}\right) - \frac{\mathbb{D}\mbox{g} {t^*}^{2}}{2}\right)&  \\
+&+ B^2\mathbb{E}\mbox{u}^{2} \left(\frac{{t^*}^{4}}{12} \left(-3 - 3 \mathbb{D}\mbox{g} - 4 \mathbb{D}\mbox{g}^{2}\right) + \frac{{t^*}^{5}}{60} \left(11 + 10 \mathbb{D}\mbox{g} + 8 \mathbb{D}\mbox{g}^{2}\right) \right.
+& \\
+&\left. + \frac{{t^*}^{6}}{360} \left(-11 - 10 \mathbb{D}\mbox{g} - 8 \mathbb{D}\mbox{g}^{2}\right) + \frac{\mathbb{D}\mbox{g}^{2} {t^*}^{3}}{3}\right)
+ + \mathcal{O}(B^3\mathbb{E}\mbox{u}^3).& \nonumber
 \end{eqnarray*}
-This trajectory given by this solution is shown in Figure \ref{fig:long_times}.
-If we assume a constant scale for the drag coefficient, $C_d \approx 0.5$, then  the Drag number $\beta = \mathbb{D}\mbox{g}$ is approximately a constant $\beta \approx 6 \times 10^{-4}$ in all of our experiments.
+Trajectory for this solution are shown in Figure \ref{fig:long_times}.
+If we assume a constant scale for the drag coefficient, $C_d \approx 0.5$, then $\mathbb{D}\mbox{g}$ is approximately a constant $\mathbb{D}\mbox{g} \approx 6 \times 10^{-4}$ in all of our experiments.
 \begin{figure}[htb]
@@
     \input{../figures/long_times.pgf}
-    \caption{Non-dimensional drop trajectories for various values of $\mathbb{E}\mbox{u}=\epsilon$.}
+    \caption{Long-time scaled drop trajectories for various values of $B \mathbb{E}\mbox{u}$.}
      \label{fig:long_times}
 \end{figure}
-Again, the trajectory seemingly reduces to the classical $\mathcal{O}(1)$ solution for small values of of $\epsilon$.
-We also note that the effect of drag is very slight, appearing only as a slight correction to the higher order terms; the apoapse is very nearly equal to half the characteristic length scale.
-In practical terms this linearizing effect of small $\beta$ may disappear if the fluid density is much less than that of water, as in our experiments.
+Again, the trajectory seemingly reduces to the classical $\mathcal{O}(1)$ solution for small values of of $\mathbb{E}\mbox{u}$.
+We also note that with $\mathbb{D}\mbox{g} = 6 \time 10^{-4}$ the effect of drag is slight, appearing only as a slight correction to the higher order terms; the apoapse is nearly equal to half the characteristic length scale.
 
 By again applying a regular perturbation to the asymptotic solution with the expansion
-\[ \bar{t} \sim \bar{t}_0 + \epsilon \bar{t}_1 + \epsilon^2 \bar{t}_2 \ldots \epsilon^n\bar{t}_n  
+\[ t^* \sim t^*_0 + B \mathbb{E}\mbox{u} t^*_1 + B^2 \mathbb{E}\mbox{u}^2 t^*_2 \ldots B^n \mathbb{E}\mbox{u}^n t^*_n  
 ,\]
-and solving for the roots (that is, the times when $\bar{y} = 0$), we find an asymptotic estimate for the time-of-flight, $t_f$.
-The $\mathcal{O}(\epsilon^2)$ accurate time-of-flight estimate is given by
-\[t_f = 2 + \epsilon \left(\frac{4}{3} - \frac{2 \beta}{3}\right) + \epsilon^{2} \left(\frac{4}{5} - \frac{4 \beta}{3} + \frac{2 \beta^{2}}{5}\right) + \mathcal{O}(\epsilon^3).\]
-Substituting the experimental value of $\beta$ we find the time-of-flight estimate for water drops in air to be
+and solving for the roots at times when $y^* = 0$, we find an asymptotic estimate for the time-of-flight. The $\mathcal{O}(B^2 \mathbb{E}\mbox{u}^2)$ accurate time-of-flight estimate is given by
+\[t_f = 2 + B \mathbb{E}\mbox{u} \left(\frac{4}{3} - \frac{2 \mathbb{D}\mbox{g}}{3}\right) + B^2 \mathbb{E}\mbox{u}^{2} \left(\frac{4}{5} - \frac{4 \mathbb{D}\mbox{g}}{3} + \frac{2 \mathbb{D}\mbox{g}^{2}}{5}\right) + \mathcal{O}(B^3 \mathbb{E}\mbox{u}^3).\]
+Substituting the experimental value of $\mathbb{D}\mbox{g}$ we find the time-of-flight estimate for water drops is
 \begin{equation} \label{time_of_flight}
-t_f = 2 + 1.333 \epsilon + 0.799 \epsilon^{2} + \mathcal{O}(\epsilon^3) 
-\end{equation} 
-In Figure \ref{fig:drag} we look at the effect of increasing values of ${\mathbb{E}\mbox{u}}_+$ on time-of-flight.
+t_f = 2 + 1.333 B \mathbb{E}\mbox{u} + 0.799 B^2 \mathbb{E}\mbox{u}^{2} + \mathcal{O}(B^3 \mathbb{E}\mbox{u}^3). 
+\end{equation} 
+In Figure \ref{fig:drag} we see the effect of increasing values of $B \mathbb{E}\mbox{u}$ on $t_f$.
 \begin{figure}[htb]
@@
     \input{../figures/drag.pgf}
-    \caption{$\mathcal{O}(\epsilon^3)$ asymptotic estimate of drop time-of-flight as a function of $\epsilon = {\mathbb{E}\mbox{u}}_+$.}
+    \caption{$\mathcal{O}(B^3 \mathbb{E}\mbox{u}^3)$ accurate asymptotic estimate of drop time-of-flight $t_f$.}
     \label{fig:drag}
 \end{figure}
-We see that as $\epsilon$ grows to be no longer small, the time-of-flight grows rapidly, but this behavior appears to have an asymptote at a certain critical velocity as $\mathcal{O}({\mathbb{E}\mbox{u}}_+) \rightarrow \mathcal{O}(1)$; this is an electrostatic escape velocity, $U_e$.
-We can find the escape velocity by solving a modified version of the equation of motion,
+As $\mathbb{E}\mbox{u}$ grows to be no longer small, the time-of-flight grows rapidly, but this behavior appears to have an asymptote at a certain critical velocity; this is an electrostatic escape velocity $U_e$.
+We can find the escape velocity by solving a modified version of the equation of motion
 \[ m u' = - \frac{q E_0 y_c^2}{y^2}, \]
-where $u = \frac{d y}{d t}$ is the drop velocity. Integrating between the respective limits,
+where $u = \frac{d y}{d t}$ is the drop velocity. Integrating between the respective limits we find
 \[m \int^{u(y)}_{U_0} u du = -q E_0 y_c^2 \int^y_{R_d} \frac{dy}{y^2} ,\]
@@
 \]
-This equation has an asymptotic velocity, $U_{\infty}$ at $y = \infty$ which is real if 
+This equation has an asymptotic velocity, $U_{\infty}$ at $y = \infty$ which is real provided 
 \[ U_0 \geq  U_e = y_c \sqrt{\frac{2 q E_0 }{m R_d}},
 \]
-where $U_e$ is the escape velocity and $U_{\infty} = \sqrt{U_0^2 - U_e^2}$. The condition for the drops to escape the electric field is then given by
+where $U_e$ is the escape velocity and $U_{\infty} = \sqrt{U_0^2 - U_e^2}$. If $y_c=L$ the condition for the drops to escape the electric field is then given by
 \begin{equation}\label{escape}
-{\mbox{B}^2 \mathbb{E}\mbox{u}}^3 > 1,
-\end{equation}
-where $B^2= 8 \pi\frac{ R_d^2}{L^2}$ If the drop escapes the electric field it will have a residual velocity $U_{\infty}$, and will be in a regime of pure inertia $\sim$ drag.
-The velocity will then decay as
+\frac{1}{8 \pi} B \mathbb{E}\mbox{u} > 1.
+\end{equation}
+If the drop escapes the electric field it will have a residual velocity $U_{\infty}$, and will be in a regime of pure inertia $\sim$ drag. The velocity will then decay as
 \[
-\bar{u}(\bar{t}) = \frac{1}{\bar{t} + 1},
+u^*(t^*) = \frac{1}{t^* + 1},
 \]
 with a characteristic time $t_c \sim \frac{2 m}{C_D \rho A U_{\infty}}$, which is the halving time of the velocity.
+\section{Summary}
+Notes.
 
@@
 \section{Overview}
-Mainly we are concerned about what parameters are important in electrostatic transport of relatively large (e.g.
-millimetric) drops in low-gravity, and what the values of the respective dimensionless groups, namely $\mathbb{I}\mbox{m}$, $\mathbb{E}\mbox{u}$ and ${\mathbb{E}\mbox{u}}_+$ might be.
-To find typical vales of these parameters we used the following approach:
+We are concerned mainly about what parameters are important in electrostatic transport of relatively large millimetric drops in low-gravity, and what the values of the respective dimensionless numbers might be; namely, $\mathbb{I}\mbox{g}$, and $\mathbb{E}\mbox{u}$.
+However, this raises an interesting challenge; it is impractical to directly measure all of the key physical quantities that appear in the dimensionless groups at once in a drop tower experiment.
+In particular, determination of net drop free electric charge $q$, is difficult as high-input resistance electrometers are not well-suited to sudden the 15-$g_0$ decelerations characteristic of drop tower experiments.
+Schematic representations of drop jump statics and dynamics are shown in Figures \ref{fig:apparatus0} and \ref{fig:schematic}.
+To find typical values of these parameters we use the following approach:
 \begin{enumerate}
-\item We observed spontaneous drop jumps on charged dielectric super-hydrophobic surfaces under low-gravity conditions in a $2.1$ s drop tower, while varying the independent variables $V_d$, $\sigma$.
-However, this raises an interesting challenge; it is impractical to directly measure all of the key physical quantities that appear in the dimensionless groups at once in a drop tower experiment.
-In particular, determination of net drop free electric charge $q$, is difficult (as high-input resistance electrometers, being notoriously fickle instruments, are not well suited to sudden 15-g decelerations).
-Schematic representations of the drop jump, and of the drop in the Cassie-Baxter 1-$g_0$ initial state is shown in Figures \ref{fig:apparatus0} and \ref{fig:schematic}.
-\item Using high-speed video and image analysis software we captured the trajectories of the drops. 
-\item We solved the inverse problem to find the key parameters by maximizing a statistical likelihood function between an observed trajectory and the trajectory predicted by a dynamical model given that certain set parameters.
-The best fit parameters obtained by direct-search optimization are those corresponding to the maximum likelihood experimental values.
-The optimization is constrained by the measurement precision of directly measured independent, and dependent variables.
+\item We vary the independent variables $V_d$, and $\sigma$ in a set of single-drop spontaneous drop jumps on charged dielectric super-hydrophobic substrates under low-gravity conditions in a $2.1$ s drop tower.
+\item We capture high-speed video, and digitize the trajectories of the drops. 
+\item We solve the inverse problem to find the key parameters by maximizing a statistical likelihood function between an observed trajectory and the trajectory predicted by a dynamical model given that certain set parameters.
 \end{enumerate}
@@
  \centering
- \includegraphics[width=0.75\textwidth]{../figures/schematic.pdf}
+ \includegraphics[width=0.65\textwidth]{../figures/schematic.pdf}
  \caption{A schematic representation of the drop initial condition, resting on the superhydrophobic surface in the Cassie-Baxter state just prior to the drop tower experiment.
@@
 \end{figure}
-\begin{figure}[ht]
- \centering
- \includegraphics[width=0.75\textwidth]{../figures/apparatus0.pdf}
- \caption{A schematic representation of a drop electro-bounce experiment with labeled characteristic time and length scales, \hl{$t_c$, $y_c$} shown.
-Also shown are the dimensions of the superhydrophobic electret substrate.\label{fig:apparatus0}}
-\end{figure}
 
@@
 The DDT uses a dual capsule design, inspired by the 2.2 s facility at NASA Glenn Research Center, which decouples drag acceleration felt by the external drag shield from the experiment.
-The experiment then experiences approximately $1 \times 10^{-6}$g of high quality free-fall for the 2.1s required for the rig/drag shield assembly to plummet to the bottom of drop tower 6 floors below.
-Single drops of distilled water, in a range of volumes ($0.01 \leq R_d \leq 0.5$ mL), were very carefully deposited on the charged superhydrophobic surface using an grounded glass syringe with $\pm $1 $\mu$L accuracy, and then dropped in the drop tower.
-Red dye was added to improve thresholding accuracy in trajectory digitization.
-Drop trajectories were recorded using a \emph{Panasonic} HC-WX970 Camera, at 120 fps and and 1/3000s shutter speed.
-In a few cases where higher frame rates were needed a \emph{Nikon} 1 J1 camera with a 30mm telephoto lens was used, shooting at 400 fps.
-The experimental test cell was illuminated with a 6000K LED strip, with a thin semi-opaque plastic film covering to make the light diffuse.
-
-Rather than haphazardly contact charge the surfaces with streams of water, as likely happened by accident in the experiments which inspired this inquiry, we strive for a more controlled, uniform surface charge distribution.
-Following from this desire, superhydrophobic electrets were prepared, with surface potentials $\varphi_s = 0.7$-$4.0$ kV.
-According to a review by Sessler \cite{_electrets_????}, an electret is a dielectric material with ``quasi-permanent'' electric charge in the sense that the characteristic decay period of the electret is much greater than a practical experiment time scale.
-Electret charge may be `true' charge in the form of surface or space charges, or polarization charges (such as bound charges).
-If the electret is not screened by a conductor then it produces an external electric field if the polarization and real charges do not uniformly compate each other throughout the volume of the electret.
-For this reason electrets are thought of as electrostatic analogs to permanent magnets (and the name \emph{electret} itself is a portmantau to that effect conjured by Heaviside in 1892 \cite{heaviside_electrical_2011}).
-Typical commerical electrets are Teflon type (PTFE) polymer films on the order of 10-50 $\mu$m thick with the charge being primarily real surface charge.
-Electrets have a plethora of applications, but most germanely they have been used in Electro-Wetting On Dielectric (EWOD) devices for low-voltage manipulation of small drops \cite{wu_low-voltage_2010}.
-Real charge electrets can be produced by contact electrification, injection or deposition) of charge carriers by discharge or electron beam, ionizing radiation, or by frictional triboelectrification.
-Dipolar electrets by contrast are produced by a combination of polarization at elevated temperatures in a strong external electric field, followed by an annealing process.
-Effective surface charge densities are limited to the material dielectric strengths due to internal dielectric breakdown phenomenon (this typically occurs before external breakdown or Paschen breakdown).
+The experiment experiences approximately $\lessapprox 1 \times 10^{-4}$ $g_0$ during free-fall for the 2.1s as the rig and drag shield plummet to the bottom of drop tower 6 stories below.
+Single drops of distilled water in a range of volumes ($0.01 \leq R_d \leq 0.5$ mL), are carefully deposited on charged superhydrophobic substrates using an grounded glass syringe with $\pm $1 $\mu$L accuracy and then dropped in the drop tower.
+Red dye is added to improve thresholding accuracy in trajectory digitization.
+Drop trajectories are recorded using a Panasonic HC-WX970 Camera, at 120 fps with 1/3000s shutter speed.
+In a few cases where higher frame rates are required a Nikon 1 J1 400 fps camera with a 30mm telephoto lens is used.
+The test cell is back illuminated with a diffused 6000K LED strip light source.
+
+Superhydrophobic electrets are prepared, with surface potentials $\varphi_s = 0.7$-$4.0$ kV.
+According to a review by Sessler\cite{sessler_electrets_1987}, an electret is a dielectric material with quasi-permanent electric charge in the sense that the characteristic decay period of the electret is much greater than a practical experiment time scale.
+Electret charge may be `true' charge in the form of surface or space charges, or polarization charges such as bound charges.
+If the electret is not screened by a conductor then it produces an external electric field if the polarization and real charges do not uniformly compensate each other throughout the volume of the electret.
+For this reason electrets are thought of as electrostatic analogs to permanent magnets.
+The name \emph{electret} itself is a portmantau to that effect conjured by Heaviside in 1892\cite{heaviside_electrical_2011}.
+Typical commerical electrets are PTFE films on the order of 10-50 $\mu$m thick with the charge being primarily real surface charge.
+Electrets have a plethora of applications, but most germanely they have been used in Electro-Wetting On Dielectric (EWOD) devices for low-voltage manipulation of small drops\cite{wu_low-voltage_2010}.
+Real charge electrets can be produced by contact electrification, injection or deposition of charge carriers by discharge or electron beam, ionizing radiation, or by frictional triboelectrification.
+Dipolar electrets by contrast are produced by a combination of polarization at elevated temperatures in a strong external electric field followed by an annealing process.
+Effective surface charge densities are limited to the material dielectric strengths due to internal dielectric breakdown phenomenon which typically occurs before external breakdown or Paschen breakdown.
 
 We use an isothermal electret formation process using a variation of the widely applied corona-charging technique.
-The typical corona-charging technique uses strong inhomogenous DC electric fields to produce discharge in air at ambient conditions; the dielectric substrate is atop a grounded electrode, and there is a screening potential electrode intermediately positioned to control the surface potential (the the surface potential of the dielectric will tend to saturate at this grid potential if the material is not space-charge current limited).
-The corona field is usually produced by pin-shaped electrode.
+Typical corona-charging techniques uses strong inhomogenous DC electric fields to produce discharge in air at ambient conditions; the dielectric substrate is atop a grounded electrode and there is a screening potential electrode intermediately positioned to control the surface potential.
+The surface potential of the dielectric will tend to saturate at this grid potential if the material is not space-charge current limited.
+The corona field is usually produced by a pin-shaped electrode.
 In air the most common charge carriers thus produced are $\mbox{CO}_3^-$ ions.
 This approach is known to generally produce samples with fairly uniform surface charge densities.
-Some work by van Turnhout in 1975 showed, using Thermally Stimulated Current (TCS) measurements, that in 4.8 mm thick polymethyl methacrylate (PMMA) polarization of the dielectric is non-uniform, due to real space-charge mostly ($\sim$90\%) residing in a thin (0.1-0.2 mm) layer near the free-surface of the sample \cite{van_turnhout_thermally_1975}.
-In this work we use a balanced AC corona ion source (Ptec IN5120), to direct a net neutral stream of ions towards the dielectric target, which we polarize by an electrode with a $2$ kV$+$ (absolute reference) DC-DC converter.
+Some work\cite{van_turnhout_thermally_1975} by van Turnhout using Thermally Stimulated Current (TCS) measurements showed that in 4.8 mm thick polymethyl methacrylate (PMMA) polarization of the dielectric is non-uniform due to real space-charge mostly ($\sim$90\%) residing in a thin (0.1-0.2 mm) layer near the free-surface of the sample.
+In this work we use a Ptec IN5120 balanced AC corona ion source, to direct a net neutral stream of ions towards the dielectric target, which we polarize by an electrode with a EMCO P20P $2$ kV$+$ absolute reference DC-DC converter.
 The ion stream compensates the surface and space bound charges arising due to the polarization of the dielectric.
-When the DC-DC converter is switched to ground, the deposited negative ions remain on the surface.
+When the DC-DC converter is switched to ground the deposited negative ions remain on the surface.
 
 The electret is lamina of 3-4 0.4 mm thick corona charged PMMA sheets.
-The electric field strength scales with the number of dielectric lamina as has also been shown in work on electret based vibrational energy harvesters \cite{wada_stacking_2012} and in water desalinization \cite{ni_desalination_2005}.
-
-The final, superhydropobic layer, is produced by laser etching PMMA, and depositing a thin layer of PTFE on the resulting roughness topology to increase the Young's angle.
+The electric field strength scales with the number of dielectric lamina as has also been shown in work on electret based vibrational energy harvesters\cite{wada_stacking_2012} and in water desalinization\cite{ni_desalination_2005}.
+
+The electret is established on a superhydrophobic substrate produced by laser etching PMMA and depositing a thin layer of PTFE on the roughened surface.
 The surface charge density can be modulated during the experiment using the high-voltage DC-DC converter, which can re-polarize the dielectric substrate by means of an embedded electrode, and the resulting bound charge partially or fully neutralizes the electric field due to the surface ions deposited by corona charging of the electret.
-The high-voltage system is armed manually before the drop and is automatically safed by a high-voltage power switching relay, which switches the load across a 100 k$\Omega$ resistor when triggered by the resumption of 1-$g_0$ conditions.
+The high-voltage system is armed manually before the drop tower experiment and is automatically safed by a high-voltage power switching relay, which switches the load across a 100 k$\Omega$ resistor when triggered by the resumption of 1-$g_0$ conditions.
 The safing is set by an accelerometer pin-interrupt triggered microcontroller command.
@@
     \def\svgwidth{\columnwidth}
-    \input{../figures/rig.pdf_tex}
-    \caption{The drop electro-bounce experiment hardware mounted on a drop tower rig.\label{fig:rig}}
-\end{figure}
-
-Contact angles of distilled water on the electret $\sim 150^{\circ}$.
-The hysteresis of the contact angle (the difference between the advancing and receding contact angles) is estimated from the roll-off angle using the method of Furmidge, 1962 \cite{furmidge_studies_1962}, and is found to be approximately $20^{\circ}$ when the surface is uncharged.
-The innate Young's angle hydrophobicity of the PTFE layer is enhanced by the underlying roughness length scales of the surface.
-We use a laser-etched pillared geometry with pillar heights $\sim 775$ $\mu$m, widths $\sim 70$ $\mu$m and pitch $\sim 100$ $\mu$m.
+        \subfloat[]{%
+        \input{../figures/rig.pdf_tex}%
+}
+
+        \subfloat[]{%
+        \includegraphics[width=0.45\textwidth]{close_up}%
+}
+    \caption{(a)The drop electro-bounce experiment hardware mounted on a drop tower rig. (b) Close up of the experimental test cell.\label{fig:rig}}
+\end{figure}
+
+Contact angles of distilled water on the electret are $\sim \hspace{-1mm} 150^{\circ}$.
+The hysteresis of the contact angle (the difference between the advancing $\theta_a$ and receding $\theta_r$ contact angles) is estimated from the roll-off angle using the method of Furmidge\cite{furmidge_studies_1962}, and is found to be approximately $25^{\circ} \pm 10^{\circ}$ when the surface is uncharged.
+The contact angle for water on smooth PTFE layer is $\approx 115^{\circ}$ and is further enhanced by an air layer maintained in the underlying roughness length scales of the surface.
+We use a laser-etched pillared geometry with pillar heights $\sim \hspace{-1mm} 775$ $\mu$m, widths $\sim \hspace{-1mm} 70$ $\mu$m, and pitch $\sim \hspace{-1mm} 100$ $\mu$m.
 An SEM image of the pillar geometry is shown in Figure \ref{fig:SEM}.
@@
     \input{../figures/hysteresis.pgf}
-       \caption{Hysteresis of the contact line plotted as a function of static contact angle and roll-off angle for $1$ mL drops.\label{fig:hysteresis}}
-\end{figure}
-
-\begin{figure}[ht]
- \centering
- \includegraphics[width=0.75\textwidth]{../figures/SEM.pdf}
+       \caption{The Furmidge model of the hysteresis of the contact line plotted as a function of static contact angle $\theta$, and roll-off angle $\alpha$, for $1$ mL drops.
+The measured static contact angles, and roll-off angles of several superhydrophobic surfaces including the laser-etched PMMA used in this work are also shown annotated with the characteristic roughness lengthscale $R_q$ of the surface.\label{fig:hysteresis}}
+\end{figure}
+
+\begin{figure}
+ \centering
+ \includegraphics[width=0.65\textwidth]{../figures/SEM.pdf}
  \caption{SEM image of the superhydrophobic surface.\label{fig:SEM}}
@@
 
-Surface potentials $\varphi_s$, were measured on the superhydrophobic surface using a \emph{Simco-Ion} FMX-004 electrostatic fieldmeter and the method for determination of surface charge density for low conductivity polymers described in Davies, 1967 \cite{davies_examination_1967}.
-This measurement was done with the superhydrophobic surfaces connected by a conductive ground plane by conductive tape, far away from the presence of other conductors.
+Surface potentials $\varphi_s$, are measured on the superhydrophobic surface using a Simco-Ion FMX-004 electrostatic fieldmeter and the method for determination of surface charge density for low conductivity polymers described in Davies\cite{davies_examination_1967}.
+This measurement is made with the superhydrophobic surfaces connected by a conductive ground plane by conductive tape far from the presence of other conductors.
 An ideal approach to determining surface charge on a dielectric surface is to screen perturbing effects of external electric fields.
-This is partly accomplished by grounding the fieldmeter, and by placing the dielectric sample on a grounded conductive plate backing.
+This is partly accomplished by grounding the fieldmeter and by placing the dielectric sample on a grounded conductive plate backing.
 In this case the surface charge density is determined from
-\[ \sigma = \frac{\varphi_s \kappa}{l}, \]
-where $l$ and $\kappa$ are the thickness of the dielectric surface, and the absolute permitivity respectively.
+\[ \sigma = \frac{\varphi_s \kappa \epsilon_0}{l}, \]
+where $l$ is the thickness of the dielectric surface.
 The measured surface voltage is a function of position away from the charged dielectric.
-In most cases this function is relatively constant at a distance about 1-2 cm away from the surface (there is some measurement error in surface voltage due to small mispositioning of the electrostatic fieldmeter, say by $\pm$1 mm).
-The relative dielectric constant of the PMMA sheet was measured by using a 65$\times$65 mm polished aluminum parallel plate capacitor with $C = \epsilon \epsilon_0 \frac{A}{l}$ where $C$ is the capacitance, and $A$ is the sheet area.
-Measuring the capacitance with 3 sample thicknesses using a GenRad 1657 RLC Digibridge, we found the relative permitivity to be $\epsilon = 3.5 \pm 0.4$.
+In most cases this function is relatively constant at a distance of about 1-2 cm away from the surface though we note that there is some measurement error in surface voltage due to small mispositioning of the electrostatic fieldmeter, say by $\pm$1 mm.
+The relative dielectric constant of the PMMA sheet is measured by using a 65$\times$65 mm polished aluminum parallel plate capacitor with $C = \kappa \epsilon_0 \frac{A}{l}$ where $C$ is the capacitance, and $A$ is the sheet area.
+Measuring the capacitance with 3 sample thicknesses using a GenRad 1657 RLC Digibridge, we find the relative permitivity to be $\kappa = 3.5 \pm 0.4$.
 
 A further consideration is the possibility of the change in total charge during a typical experimental timescale.
-If we consider the drop rig to be a ground (which seems reasonable given that the rig is isolated from true ground, but is at some reference voltage with respect to the surface charges on the dielectric, it also has an abundance of free charge carriers, that is, if it is conductive), then there will be both bulk and surface decay of the charge on the dielectric.
+If we consider the drop rig to be a ground which is reasonable given that the rig is isolated from true ground, but is at some reference voltage with respect to the surface charges on the dielectric with an abundance of free charge carriers, then there will be both bulk and surface decay of the charge on the dielectric.
 The evolution of the charge can in some cases be approximated by
 \[ \sigma = \sigma_0 e^{\frac{-t}{\epsilon \rho}}, \]
-where $\sigma_0$ is the initial surface charge density, and $\rho$ is the bulk resistivity (which can also be reframed in terms of conductivity by $\rho = 1/\gamma$, where $\gamma$ is the conductivity).
-For an example case of a surface with an initial surface charge density $\sigma = 2.4 \times (10^{-6})$ $C/m^2$, relative permittivity $\epsilon = 3.5$ and bulk resistivity $\rho = 1.6 \times (10^{16})$ $\Omega$cm such as with the case of 2.8 mm PMMA sheet, then the time constant $\tau = \kappa \rho$ is approximately 5000 s, which is a great deal longer than the typical time period for of a drop tower experiment.
+where $\sigma_0$ is the initial surface charge density, and $\rho$ is the bulk resistivity.
+For an example case of a surface with relative permittivity $\kappa = 3.5$ and bulk resistivity $\rho = 1.6 \times (10^{16})$ $\Omega$cm such as with the case of a 2.8 mm PMMA sheet, then the time constant $\tau = \kappa \epsilon_0 \rho$ is approximately 5000 s, which is significantly longer than the typical time period for a drop tower experiment.
 We measured the charge decay with a calibrated probe at periodic intervals.
-There are several charge decay mechanisms: internal ones, such as Ohmic resistence, and external ones such as compensation by envonmental ionic species.
-The relative magnitudes of these charge transport mechanisms, and therfore the stability of the electret varies drastically depending on its initial surface potential, material properties, environment, and charging method.
-In the case of unshielded electrets compensation by atmospheric ions is significant \cite{perlman_electrets_1973}.
+There are several charge decay mechanisms: internal ones such as Ohmic resistence, and external ones such as compensation by envonmental ionic species.
+The relative magnitudes of these charge transport mechanisms, and therfore the stability of the electret, vary drastically depending on the initial surface potential, material properties, environment, and charging method.
+In the case of unshielded electrets compensation by atmospheric ions is significant\cite{perlman_electrets_1973}.
 Because environmental convection will tend to  maintain a gradient of these ions, sealing an electret in a container from the atmosphere will effectively halt this decay mechanism.
-Atmospheric humidity and water drop condensation also significantly increase charge decay (presumably by reducing the surface resistence) \cite{haenen_characteristic_1975}.
+Atmospheric humidity and water drop condensation can also significantly increase charge decay, presumably by reducing the surface resistence\cite{haenen_characteristic_1975}.
 Examples of this decay can be seen in Figure \ref{fig:charge_decay} for differing numbers of dielectric lamina used in this experiment.
-In looking at the trends in charge decay for our electrets we notice firstly, that the decay does not appear to be exponential, as in the model described above.
-Secondly, we plainly see a cross-over effect in the decay of the surface potential in our electret samples, whereby the samples charged to higher initial surface potentials decayed faster and reached the lower overall final potentials.
-This is a well known effect in polyethylenes charged by corona \cite{ferreira_corona_1992}.
+In looking at the trends in charge decay for our electrets we notice firstly that the decay does not appear to be exponential, as in the model described above.
+Secondly, we plainly see a cross-over effect in the decay of the surface potential in our electret samples, whereby the samples charged to higher initial surface potentials decay faster and reached the lower overall final potentials.
+This is a well known effect in polyethylenes charged by corona\cite{ferreira_corona_1992}.
 \begin{figure}[htb!]
@@
     {\input{../figures/charge_decay.pgf}}
-       \caption{Charge decay in the dielectric laminates for differing numbers of layers.\label{fig:charge_decay}}
+       \caption{Charge decay in the dielectric laminates for several numbers of layers.\label{fig:charge_decay}}
 \end{figure}
@@
 
-\section{Data Munging}
+\section{Data Reduction}
 Digitization of drop trajectories requires several steps of post-processing.
 Video is first decomposed into a sequence of still images.
-Trajectories are captured using the particle tracking module in \emph{Fiji} \cite{schindelin_fiji:_2012}, a derivative of the popular \emph{ImageJ} \cite{schneider_nih_2012} package for scientific image analysis.
-The series is stabilized to remove the effect of drop transients from the kinetmatic data \cite{li_image_2008}.
-The series of still images is cropped, and the background (that is, the low-entropy pixels) of the series is removed using a built-in ``rolling ball'' algorithm.
+Trajectories are captured using the particle tracking module in Fiji\cite{schindelin_fiji:_2012}, a derivative of the popular ImageJ\cite{schneider_nih_2012} package for scientific image analysis.
+The series is stabilized to remove the effect of drop transients from the kinetmatic data\cite{li_image_2008}.
+The series of still images is cropped and the low-entropy pixels are removed using a built-in rolling ball algorithm.
 Each still is then split into its constituent RGB maps.
-In this case the green channel images contained the most information, so these were then globally thresholded using the Triangle algorithm to recover a map of the pixels corresponding the approximate position of the drop in the original still.
-Ellipses are fitted to the pixel map stepping through the time series to determine the positions of the center of mass, and the semi-major and minor axes of the drops during the drop.
+In this case the green channel images contain the most information.
+These are globally thresholded using the Triangle algorithm to recover a map of the pixels corresponding the approximate position of the drop in the original still image.
+Ellipses are fitted to the pixel map stepping through the time series to determine the positions of the center of mass and the semi-major and semi-minor axes of the drops during the drop tower test.
 Finally, a perspective correction is applied to the center-of-mass positions.
 
-The code used in this work, as well as the raw data, and the make files for this thesis are archived on the open-source project portal Github \cite{schmidt_droplet_electro-bounce:_2017}.
+The code, raw data, and make files for this thesis are archived on the open-source project portal Github\cite{schmidt_droplet_electro-bounce:_2017}.
 
 \section{Parameter Estimation}
-Using various scaling arguments we have gleaned from our simple model a series of non-dimensional numbers characteristic of drop bounce apoapses and times of flight, but these dimensionless groups depend on a set of physical parameters.
-Unfortunately not all of these parameters are physically practical to accurately measure by experiment.
-Drop free charge $q$, in particular, could in principle be directly measured by collecting the charged drops in a faraday cup under low-g and measuring the change in capacitance of the cup using a very high input-resistance electrometer, but this is a problematic experiment to set up in a drop tower from a practical standpoint.
-The other state variables we can directly measure by experiment with varying levels of accuracy.
-To measure the charge, $q$, we instead turn to parameter estimation techniques.
-Our work flow to identify this parameter is as follows:
+Using various scaling arguments we have gleaned from our simple model a series of dimensionless numbers characteristic of drop bounce apoapses and times of flight.
+These dimensionless numbers depend on physical properties.
+Unfortunately, not all of these properties are easily measured by experiment.
+Drop free charge $q$, in particular, could in principle be directly measured by collecting the charged drops in a faraday cup under low-g and measuring the change in capacitance of the cup using a high input-resistance electrometer, but this method is difficult to apply in practice in a drop tower.
+Other state variables we can directly measure with varying levels of accuracy.
+
+To measure the charge $q$ we must use parameter estimation techniques. Our work flow to identify $q$ in an individual drop tower experiment is as follows:
 \begin{enumerate}
-\item Experimentally vary $V_d$, $\sigma$ and capture drop trajectories using a high-speed camera.
-\item Digitize drop trajectories by using automatic tracking of ellipse-fitted centers of mass on the thresholded video.
-\item Slice drop trajectories by their bounce minima, and apply a smoothing filter.
-\item Extract the drop charge (and other experimental parameters) by maximizing the log-likelihood of the data given the dynamical model and parameters, by varying the parameter vector using a direct search optimization.
+\item Experimentally vary $V_d$ and $\sigma$, capturing drop trajectories using a high-speed camera.
+\item Digitize drop trajectories via automatic tracking of ellipse-fitted centers of mass on the thresholded video.
+\item Slice drop trajectories by their bounce minima and apply a smoothing filter.
+\item Extract the drop charge, as well as other experimental parameters, by maximizing the log-likelihood of the data given the dynamical model by varying the parameter vector using a direct search optimization.
 \end{enumerate}
 
-Mathematically we state that we find the parameters $\mathbf{x}$ that solve the inverse problem $G(\mathbf{x}) = \mathbf{d}$, using a direct search method (\emph{Nelder-Mead}). 
+Mathematically we state that we find the parameters $\mathbf{x}$ that solve the inverse problem $G(\mathbf{x}) = \mathbf{d}$ using the Nelder-Mead direct search method to maximize the log-likelihood of the data.
+This is equivalent to minimizing the $\chi^2$ goodness-of-fit between an experimentally observed droplet trajectory and the trajectory predicted by Equation \ref{gov_eqn_subs} given a vector of parameters $\mathbf{x} = \left\langle q, \hspace{2 mm} V_d, \hspace{2 mm} \sigma \right\rangle$.
+This problem is stated as
 \[
-\mbox{min} \hspace{2 mm} \chi^2 = \mbox{min} \hspace{2 mm} \sum^n_{i=1} \frac{\left({y_d(t)}_i - y_G(t, \mathbf{x})_i \right)^2}{y_G(t, \mathbf{x})_i}
+\mbox{min} \hspace{2 mm} \chi^2 = \mbox{min} \hspace{2 mm} \sum^n_{i=1} \frac{\left({y_d(t)}_i - y_G(t, \mathbf{x})_i \right)^2}{{\sigma_d}_i},
 \]
@@
 \end{eqnarray*}
-where $y_G(t, \mathbf{x})$ is a numerical solution of the equation of motion
+where $y_G(t, \mathbf{x})$ is the $y$-coordinate position at time $t$ of the numerical solution of the equation of motion
 \[
-m y'' = \frac{1}{2} \rho C_D A_d {y'}^2 + q E(y) + K q^2 y^{-2} \]
+m y'' = \frac{1}{2} \rho C_D A_d {y'}^2 + q E(y) + K q^2 y^{-2}, \]
+$y_d(t)$ is the corresponding experimentally observed drop $y$-coordinate position at time $t$, and $\sigma_d$ is the standard error of the observed position.
+The vector $\mathbf{x}$ that minimizes $\chi^2$ is the so called Maximum Likelihood Estimate (MLE) of the experimental parameters.
+This approach is given further explanation below.
 
 \subsection{Inverse Problems}
-Suppose we have a model $G(\mathbf{x})$, with a vector of parameters $\mathbf{x}$, and set of (noiseless) observations $\mathbf{d}$, then we naturally expect there to exist a relationship 
+Suppose we have a model $G(\mathbf{x})$ with a vector of parameters $\mathbf{x}$ and set of ideal observations $\mathbf{d}$. We then expect there to exist a relationship 
 \[G(\mathbf{x}) = \mathbf{d} ,\]
@@
 \left( t_k, \mathbf{y_k} \right).\]
-The process of fitting a function, defined by a collection of parameters, to a data set is called the discrete inverse, or parameter estimation problem (as opposed to the \emph{forward problem} to find $\mathbf{d}$ given $\mathbf{x}$ and $G(\mathbf{x})$).
-This is a familiar procedure when the determination of model parameters is done using linear or polynomial regression.
+The process of fitting a function defined by a collection of parameters to a data set is called the discrete inverse, or parameter estimation problem as opposed to the \emph{forward problem} to find $\mathbf{d}$ given $\mathbf{x}$ and $G(\mathbf{x})$.
+This is a familiar procedure when the determination of model parameters is accomplished using linear or polynomial regression.
 However there are approaches even to fitting an arbitrary function to a noisy and sparse dataset.
-In this work we use the conventional Maximum Likelihood Estimate (MLE) method to identify the model parameters.
-
-Using MLE we don't ask the question: ``what is the probability that my set of model parameters is correct?''(because the probability is very nearly zero!), but rather ``given my set of model parameters, what is the probability that this data set occurred (what is the likelihood of the parameters given the data)?''.
+In this work we use the conventional Maximum Likelihood Estimate method to identify the model parameters.
+
+Using MLE we seek to know what is the probability that this data set occurred given the set of model parameters.
+In other words, what is the likelihood of the parameters given the data.
 Bayes' Theorem holds that
 \[\mbox{prob}(X|D, I) = \frac{\mbox{prob}(D|X,I) \times \mbox{prob}(X|I)}{\mbox{prob}(D|I)}\]
-where $D$ are our observations (dataset), $X$ is our vector of parameters, and $I$ is general background information about the problem including our mathematical model (for instance the ODE above), and
+where $D$ are the observations (dataset), $X$ is the vector of parameters, $I$ is general background information about the problem including the mathematical model, and 
 \[\begin{array}{lll}
@@
 \]
-The posterior probability density function (PDF) $\mbox{prob}(X|D, I)$, is ultimately what we want to estimate, the prior PDF $\mbox{prob}(X|I)$, reflects our knowledge of the system, and the evidence $\mbox{prob}(D|I)$, is the likelihood of the data based on our knowledge.
-We also note that since it only makes sense to compare the conditional PDF's for the same data, we can ignore the denominator (that is, the evidence).
-We further note that the prior $\mbox{prob}(X|I)$, is fixed before our observations and so can be
-treated as invariant to our problem.
+The posterior probability density function (PDF) $\mbox{prob}(X|D, I)$ is ultimately what we wish to estimate, the prior PDF $\mbox{prob}(X|I)$ reflects our knowledge of the system, and the evidence $\mbox{prob}(D|I)$ is the likelihood of the data based on our knowledge.
+We also note that since it only makes sense to compare the conditional PDF's for the same data, we can ignore the denominator.
+We further note that the prior $\mbox{prob}(X|I)$ is fixed before our observations and so can be treated as invariant to our problem.
 We can therefore infer that $\mbox{prob}(X|D, I) \propto \mbox{prob}(D|X, I)$.
-The MLE for the the model parameters $\mathbf{x_0}$, then is given by the maximum of the posterior PDF, which is equivalent to the solution of the ODE given the the parameters $\mathbf{x}$, that produces the highest probability of the observed data.
-Since the likelihood $\mathcal{L}(\mathbf{x}) = \prod_i^n \mathcal{P}_i$, and the probability $\mathcal{P}$, of any single observation is less than one, then the total likelihood which is the product of a large number of probabilities tends to be vanishingly small.
-The more well behaved log-likelihood is given by
-\[\mathcal{M} = \ln(\mathcal{L}) = \ln(\mbox{prob}(D|X, I)) = \mbox{const} - \frac{\chi^2}{2}\]
+The MLE for the model parameters $\mathbf{x_0}$ is given by the maximum of the posterior PDF, which is equivalent to the solution of the ODE given the the parameters $\mathbf{x}$, that produces the highest probability of the observed data.
+Since the likelihood $\mathcal{L}(\mathbf{x}) = \prod_i^n \mathcal{P}_i$ and the probability $\mathcal{P}$ of any single observation is less than one, then the total likelihood which is the product of a large number of probabilities is vanishingly small.
+The more well-behaved log-likelihood is given by
+\[\mathcal{M} = \ln(\mathcal{L}) = \ln(\mbox{prob}(D|X, I)) = \mbox{\emph{const}} - \frac{\chi^2}{2},\]
 where 
@@
 \]
-is the $\chi^2$ goodness-of-fit, $y_d = y_d(t)$ is a observation of drop position at a point in time, and $y_G =  y_G(t, \mathbf{x})$ is the drop position predicted by the solution to the equation of motion at time $t$, and $\sigma$ is the standard error of the position measurement.
-If the number of data points $n$, is small was can use the Poisson error $\sigma_d^2 = {y_G}$.
+is the $\chi^2$ goodness-of-fit, $y_d = y_d(t)$ is a observation of drop position at a point in time, and $y_G =  y_G(t, \mathbf{x})$ is the drop position predicted by the solution to the equation of motion at time $t$, and $\sigma_d$ is the standard error of the position measurement.
 The optimal parameter set is the one with the highest probability of observing the data (the maximum of the posterior PDF) and can be determined by maximizing the log-likelihood $\mathcal{M}$ (or minimizing $\chi^2$) of the data $\mathbf{d}$ with respect to the parameter set $\mathbf{x}$.
@@
 In a parameter estimation problem, if we approximate these gradients by finite differences, then the noise manifests itself as amplification of the roughness in the hyper-response surface.
-Gradient based optimizers do poorly in these situations because they tend to converge to local minima.
+Gradient-based optimizers do poorly in these situations because they tend to converge to local minima.
 While so called gradient free algorithms offer an improvement in this regard, speed of convergence and the quality of the MLE is improved by smoothing the objective function.
@@
 Our choice of smoothing approach depends principally on the nature of the errors in the dataset.
-The sources of error include misalignment of the camera, error in the fiduciary length scale, perspective due to objects (subject or reference scale) being out of the photographic plane, and various errors arising in the digitization process (including the difference between the thresholded ellipse fitted centroid and the true centroid of the non-ellipse drop centroid).
-Some of these errors are systematic in origin and introduce consistent biases into the data (e.g.
-coherent spectral sources, rather than truly stochastic noise).
+The sources of error include misalignment of the camera, error in the fiduciary length scale, perspective due to objects being out of the photographic plane, and various errors arising in the digitization process including the difference between the thresholded ellipse fitted centroid and the true centroid of the non-ellipse drop centroid.
+Some of these errors are systematic in origin and introduce consistent biases into the data, e.g., coherent spectral sources, rather than truly stochastic noise.
 Data smoothing does little to help systematic errors in that they are usually of lower frequency than the signal.
-Random errors, by contrast, are assumed to have a Gaussian distribution (by the central limit theorem), and are independent of the signal (which inherently results from a deterministic process).
-
-We experimented with a variety of filters implemented in the \verb|scipy.signal| Python \emph{SciPy} \cite{oliphant_python_2007} module on a representative set of trajectory data; these methods include 1D Gaussian convolution, Wiener, Butterworth, and Savitsky-Golay filters.
-Qualitatively comparing these smoothing methods (by hand tuning filter orders and window sizes) we find that we loose too many data points in the smoothing process, large amplitudes are overly smoothed by repeated filtering passes, or there are significant end effects for most of these methods.
+Random errors, by contrast, are assumed to have a Gaussian distribution as required by the central limit theorem, and are independent of the signal which we assume results from an inherently deterministic process.
+
+We experimented with a variety of filters implemented in the \verb|scipy.signal| Python \emph{SciPy}\cite{oliphant_python_2007} module on a representative set of trajectory data; these methods include 1D Gaussian convolution, Wiener, Butterworth, and Savitsky-Golay filters.
+Qualitatively comparing these smoothing methods by hand tuning filter orders and window sizes, we find that we loose too many data points in the smoothing process, large amplitudes are overly smoothed by repeated filtering passes, or there are significant end effects for most of these methods.
 A comparison of these smoothing approaches on a representative trajectory data set is shown in Figure \ref{fig:y_filtered}.
-\begin{figure}
-    \centering
-    \input{../figures/y_filtered.pgf}
-       \caption{The underlying signal is `noisy', due partially to deterministic errors in determining the center of mass position.
-These deterministic errors are largely due to drop oscillations, especially the rapidly damped higher harmonics which do not have azimuthal symmetry.
-There is also Gaussian error in the ellipse fitting due to thresholding and noise in the video itself.
+\begin{figure}[htp]
+    \centering
+    \subfloat[]{%
+  \input{../figures/y_filtered.pgf}%
+}
+
+     \subfloat[]{%
+    \input{../figures/dy_filtered.pgf}%
+}
+       \caption{(a) Schematic noisy droplet trajectory data.
 We see that 1D Gaussian convolution and Wiener filters suffer from significant end effects.
-At this scale Butterworth and Savistsky-Golay filters are nearly indistinguishable.}
+At this scale Butterworth and Savistsky-Golay filters are nearly indistinguishable.
+(b) Comparing Butterworth and Savitsky-Golay filtered	 first derivatives of the above schematic trajectory we see that the Butterworth filter also suffers from a slight end effect.
+This implies that the optimization will find a different optima of the likelyhood depending on which type of filter is used.}
       \label{fig:y_filtered}
 \end{figure}
-
-\begin{figure}
-    \centering
-    \input{../figures/dy_filtered.pgf}
-    \caption{Comparing the first derivatives of the Butterworth and Savitsky-Golay filters we see that the Butterworth filter also suffers from a slight end effect.
-This implies that the optimization will find a different optima of the likelyhood depending on which type of filter is used.\label{fig:dy_filtered}}
-\end{figure}
-
+%\begin{figure}
+%    \centering
+%    \input{../figures/dy_filtered.pgf}
+%    \caption{Comparing the first derivatives of the Butterworth and Savitsky-Golay filters we see that the Butterworth filter also suffers %from a slight end effect.
+This implies that the optimization will find a different optima of the likelyhood depending on which type of %%filter is used.\label{fig:dy_filtered}}
+%\end{figure}
 \begin{figure}
@@
 The Savitsky-Golay and Butterworth filters seem to have the least distortion of the power spectra of the true signal.
-Both also do a good job of attenuating the noise at the 2 kHz peak.
+Both also attenuate the noise at the 2 kHz peak.
 \label{fig:power}}
 \end{figure}
-The Savitsky-Golay, and Butterworth filters both produce fairly smooth derivatives as can be seen in Figure \ref{fig:dy_filtered}; but the small window-size needed for Butterworth filter tends to also produce a noticeable end effect.
+The Savitsky-Golay, and Butterworth filters both produce fairly smooth derivatives as can be seen in Figure \ref{fig:y_filtered}, but the small window-size needed for Butterworth filter tends to also produce a noticeable end effect.
 The Savitsky-Golay filter essentially uses a moving-window based on local least-squares polynomial approximations.
-It was shown that fitting a polynomial to a set of input samples and then evaluating the resulting polynomial at a single point within the approximation interval is equivalent to discrete convolution with a fixed impulse response \cite{savitzky_smoothing_1964}.
-A beneficial property of this kind of low-pass filter is their tendency to maintain waveform amplitudes, and so they are attractive in applications having noisy signals with sharply pointed waveforms such as ultrasound or synthetic aperture radar \cite{schafer_what_2011}.
-Because Savitsky-Golay is a Finite Impulse Response (FIR) filter it requires data points to be equally spaced; to accommodate this requirement we interpolate points between the small gaps which sometime occur in the tracking results from image analysis.
+It was shown that fitting a polynomial to a set of input samples and then evaluating the resulting polynomial at a single point within the approximation interval is equivalent to discrete convolution with a fixed impulse response\cite{savitzky_smoothing_1964}.
+A beneficial property of this kind of low-pass filter is the tendency to maintain waveform amplitudes, and so they are attractive in applications having noisy signals with sharply pointed waveforms such as ultrasound or synthetic aperture radar\cite{schafer_what_2011}.
+Because Savitsky-Golay is a Finite Impulse Response (FIR) filter it requires data points to be equally spaced.
+To accommodate this requirement we interpolate points between the small gaps which sometime occur in the tracking results from image analysis.
 We use a moving window size slightly smaller than the length of the current bounce in a single drop jump data set.
-The windows are piecewise defined by partitioning the data set into a series of individual bounces (the dataset is sliced at minima identified after an initial rough smoothing pass, using the \verb|scipy.signal.argrelextrema()| function).
+The windows are piecewise defined by partitioning the data set into a series of individual bounces.
+To this partitioning is accomplished by slicing the dataset at minima identified after an initial rough smoothing pass using the \verb|scipy.signal.argrelextrema()| function.
 The Savitsky-Golay polynomial order is 4.
 
-To understand how these filters differ it is useful to look at their frequency response.
-In Fourier space, convolution becomes a multiplication, and we can understand what a filter does by looking at which frequencies it lets pass through.
-We can do this using a Discrete Fourier Transform (though it is worth noting that our signal is not truly periodic).
-The power spectra for these same data are shown in Figure \ref{fig:power}.
+To understand how these filters differ it is useful to look at their frequency responses.
+The power spectra for these same data, obtained by Discrete Fourier Transform, are shown in Figure \ref{fig:power}.
+Though, it is worth noting that our signal is not truly periodic.
 
 \subsection{Optimization}
-Most generally a constrained optimization problem is stated as 
+Most generally, a constrained optimization problem is stated as 
 \[
 \begin{array}{lll}
-\mbox{minimize:} & \hspace{2 mm} f\left(\mathbf{x}\right) & \mbox{objective function}\\
+\mbox{minimize:} & \hspace{2 mm} f\left(\mathbf{x}\right) & \mbox{objective function,}\\
 \mbox{subject to:} & & \\
-& \centering g_j \left( \mathbf{x} \right) \leq 0 & \mbox{inequality constraints}\\
-& \centering h_k \left(\mathbf{x} \right) = 0 & \mbox{equality constraints}
+& \centering g_j \left( \mathbf{x} \right) \leq 0 & \mbox{inequality constraints,}\\
+& \centering h_k \left(\mathbf{x} \right) = 0 & \mbox{equality constraints,}
 \end{array}
@@
 x_n &
-\end{array} \right. & \mbox{design variables}
+\end{array} \right. & \mbox{design variables.}
 \end{array}
 \]
-
 Mathematical optimization is the problem of finding minima of a function $f$.
 In this context the function is called the cost, or objective function.
-The field of mathematical optimization is as old as calculus itself, and the number of particular optimization techniques is correspondingly myriad; particular techniques lend themselves well to particular types of optimization problems.
-The minima of the objective function $f$ is sought on a domain $A$ specified by the constraints of the problem; this domain is usually called the feasible region.
+The field of mathematical optimization is as old as calculus itself, and the number of particular optimization techniques is correspondingly myriad.
+Particular techniques lend themselves well to particular types of optimization problems.
+The minima of the objective function $f$ is sought on a domain $A$ specified by the constraints of the problem, where the domain is usually called the feasible region.
 Minima of objective function $f: A \rightarrow \mathbb{R}^m$ are called feasible solutions.
@@
 Functions may not always be smooth in the sense of having continuous derivatives, and this is problematic in that optimization methods fundamentally rely on gradients of the objective function.
-Problems with anisotropic objective functions where there is strong covariance between the parameters, and the gradient vector generally to differ significantly from the Newton direction ($-\mathbf{H}^{-1} f' ( \mathbf{x} )^T$, where $\mathbf{H}$ is the Hessian matrix) are considered ill-conditioned.
-Ill-conditioned problems gradient based deterministic search tend to converge slowly as they take a zigzagging path determined by the local value of the gradient rather than following the Newton-direction vector which towards the minimum.
-Numerical optimization may deal with black box functions (where we do not have an explicit mathematical expression of the function we are optimizing).
-Black box problems are challenging because we do not have access to analytic gradients of the objective function, and approximating them by finite-differences is slow and noisy.
+Problems with anisotropic objective functions where there is strong covariance between the parameters, and the gradient vector generally to differ significantly from the Newton direction $-\mathbf{H}^{-1} f' ( \mathbf{x} )^T$, where $\mathbf{H}$ is the Hessian matrix, are considered ill-conditioned.
+Gradient based deterministic search algorithms tend to converge slowly for ill-conditioned problems as they take a zigzagging path determined by the local value of the gradient rather than following the Newton-direction vector towards the minimum.
+Numerical optimization may deal with black box functions where we do not have an explicit mathematical expression of the function we are optimizing.
+Black box problems are challenging because we do not have access to analytic gradients of the objective function and approximating them by finite-differences is slow and noisy.
 In general, noisy, black box, non-linear, non-quadratic, non-convex, constrained, ill-conditioned, high-dimensional objective functions are problematic to optimize.
-Unfortunately, problems of this type are the essence of the parameter estimation, which often leads to its characterization as an `art' rather than a precise science (though we submit that it is a dark art).
-
-The equation of motion behaves stiffly due to the large disparity in Coulombic, image charge length scales.
+Unfortunately, problems of this type are the essence of the parameter estimation, which often leads to its characterization as an `art' rather than a precise science.
+
+The equation of motion behaves stiffly due to the large disparity in Coulombic and image charge length scales.
 We integrate it numerically using the \verb|odeint| \emph{Scipy} module.
-This is a shake-and-bake Python wrapper for the venerable 1982 \emph{netlib ODEPACK} library double-precision \verb|lsoda| (Livermore Solver for Ordinary Differential equations with Automatic method switching for stiff and nonstiff problems) integrator \cite{hindmarsh_odepack_1983}.
-The function switches between Adams (nonstiff) and Backwards Differentiation Formulas (BDF, stiff) according to the dynamic value of a set of stiffness eigenvalues.
+This is a shake-and-bake Python wrapper for the venerable 1982 \emph{netlib ODEPACK} library double-precision \verb|lsoda| integrator\cite{hindmarsh_odepack_1983} (Livermore Solver for Ordinary Differential equations with Automatic method switching for stiff and nonstiff problems).
+The function switches dynamically between Adams (nonstiff) and Backwards Differentiation Formulas (BDF, stiff) according to the stiffness of the solution.
 
 Our specific optimization problem is non-convex, mixed discrete-continuous black-box (noisy), and highly ill-conditioned which is essentially the worst case scenario for an optimization problem.
-The ill-conditioning arises due to the strong covariance between several of the model parameters (particularly $q=q(V_d, E_0)$).
+The ill-conditioning arises due to the strong covariance between several of the model parameters, particularly $q=q(V_d, E_0)$.
 The non-convexity of the problem implies that there are many local minima of the objective function.
-While in principle a gradient-based optimizer (for instance using the quasi-Newton method of Broyden, Fletcher, Goldfarb, and Shanno (BFGS) \cite{_numerical_????}) could be used by using finite-differences to obtain approximate gradients of the $\chi^2$ objective function, in practice doing so is extremely problematic because the noise-to-signal ratio of the objective function scales like $\mathcal{O}(f)$ for $\frac{df}{dt}$ and $\mathcal{O}(f^2)$ for $\frac{d^2f}{ft^2}$ which will tend to cause convergence to a local minima which is only an artifact of the likelihood response surface \cite{wood_data_1982}.
-As a further practical matter, given the relatively expensive function-calls (which requires solving a stiff, non-linear ODE) gradient-free approaches tend to offer better performance regardless \cite{kolda_optimization_2003}.
-
-We use a gradient-free, direct-search approach: Nelder-Mead \cite{nelder_simplex_1965} implemented in \verb|scipy.optimize|.
-Nelder-Mead is robust to noise (relatively speaking), and is thrifty with our extremely expensive function-calls.
-\emph{Nelder-Mead}, sometimes called simplex-search or downhill-simplex, is a heuristic search method, with no guarantee of optimal solutions, but is well-established and widely used despite that.
-\emph{Nelder-Mead} is based on the concept of a $N$-simplex, which generalizes a triangle into higher dimensions as a polytrope of $N + 1$ vertices in $N$ dimensions.
-It uses only-function calls and expands or contracts the simplex according to the function values at its vertices in a way visually reminiscent (in $\mathbb{R}^3$) of the oscillations of the jumping drops themselves (in fact \emph{Nelder-Mead} is sometimes also called the ``amoeba method'').
-Very little is known about the convergence properties of the \emph{Nelder-Mead} algorithm in its classical form for non-smooth objective functions \cite{price_convergent_2002}, except that in general it doesn't satisfy the properties required for convergence by other direct search algorithms: that the simplex remains uniformly non-degenerate, and that some form of ``sufficient'' descent condition for function values at the vertices is required at each iteration.
+While in principle a gradient-based optimizer, such as the quasi-Newton method of Broyden, Fletcher, Goldfarb, and Shanno (BFGS)\cite{nocedal_numerical_2006}, could be used by using finite-differences to obtain approximate gradients of the $\chi^2$ objective function, in practice doing so is extremely problematic because the noise-to-signal ratio of the objective function scales like $\mathcal{O}(f)$ for $df/dt$ and $\mathcal{O}(f^2)$ for $d^2f/dt^2$ which will tend to cause convergence to a local minima that is only an artifact of the likelihood response surface\cite{wood_data_1982}.
+As a further practical matter, given the relatively expensive function-calls gradient-free approaches tend to offer better performance regardless\cite{kolda_optimization_2003}, especially when evaluating the objective function requires solving a stiff, non-linear ODE.
+
+We use a gradient-free, direct-search approach: Nelder-Mead\cite{nelder_simplex_1965} implemented in \verb|scipy.optimize|.
+Nelder-Mead is relatively robust to noise and is thrifty with our computationally expensive function-calls.
+Nelder-Mead, sometimes called simplex-search or downhill-simplex, is a heuristic search method with no guarantee of optimal solutions.
+It nonetheless is a well-established and widely used algorithem.
+Nelder-Mead is based on the concept of an $N$-simplex, which generalizes a triangle into higher dimensions as a polytrope of $N + 1$ vertices in $N$ dimensions.
+It uses only-function calls and expands or contracts the simplex according to the function values at its vertices in a way visually reminiscent (in $\mathbb{R}^3$) of the oscillations of the jumping drops themselves.
+In fact Nelder-Mead is sometimes also called the `amoeba method'.
+Very little is known about the convergence properties of the Nelder-Mead algorithm in its classical form for non-smooth objective functions\cite{price_convergent_2002}, except that in general it doesn't satisfy the properties required for convergence by other direct search algorithms: the simplex remains uniformly non-degenerate and some form of sufficient descent condition for function values at the vertices is required at each iteration.
 Scaling can help solve convergence problems and improve numerical stability.
-We precondition the optimization problem by minimizing $\ln(\chi^2)$, and using a naive scaling (scaling variables such that their magnitudes $\sim \mathcal{O}(1)$) of our constraints by their initial guesses.
-Here is goal is to make the problem equally sensitive to steps in any direction.
-\emph{Nelder-Mead} is not a global optimizer, though there are variants which use sequential local searches with probabilistic restarts to achieve globality.
-However global optimization usually comes at a tremendous computational cost.
-However, \emph{Nelder-Mead} behaves less locally than many gradient-based approaches.
-The convergence history of the parameter MLE using \emph{Nelder-Mead} for a single drop jump experiment is shown in Figure \ref{fig:convergence}.
+We precondition the optimization problem by minimizing $\ln(\chi^2)$ and using a naive $\sim \mathcal{O}(1)$ scaling of our constraints by their initial guesses.
+Here the goal is to make the problem equally sensitive to steps in any direction.
+Nelder-Mead is not a global optimizer, though there are variants which use sequential local searches with probabilistic restarts to achieve globality, usually at a tremendous computational cost.
+However, Nelder-Mead behaves less locally than many gradient-based approaches.
+The convergence history of the parameter MLE using Nelder-Mead for a single drop jump experiment is shown in Figure \ref{fig:convergence}.
 Results of the parameter estimation are shown in Figures \ref{fig:trajectories}, \ref{fig:inverse_problem}.
@@
     \input{../figures/convergence.pgf}
-    \caption{As is typical with \emph{Nelder-Mead} much of the improvment in $\chi^2$ is realized in the first few iterations.
+    \caption{As is typical with Nelder-Mead much of the improvment in $\chi^2$ is realized in the first few iterations.
 Overall the rate of convergence is sub-linear, which is to be expected for non-linear constrained problems using an hueristic algorithem.\label{fig:convergence}}
@@
     \centering
-    \resizebox{\textwidth}{!}{\input{../figures/inverse_problem.pgf}}
+    \resizebox{\textwidth}{!}{\input{../figures/inverse_problem2.pgf}}
     \caption{A series of drop trajectories showing the results of the parameter estimation.
 The trajectories are shown only up to the apoapse of the first bounce.
-The red lines show the ODE solution with given the MLE parameter vector.
+The (\protect\redline) \hspace{0.25 mm} lines show the ODE solution with given the MLE parameter vector.
 $\chi^2$ goodness-of-fit varies between $1 \times 10^{-5}$ and $1 \times 10^{-8}$ with the better fit occurring typically for the drops with the lowest apoapses.}
@@
 \subsection{Identifiability}
-That we are capable of fitting any arbitrary model to a dataset given sufficient degrees of freedom in our parameters is admittedly a disconcerting issue, begging the question ``given the structure of the model is it possible to uniquely estimate the unknown parameters?'' This question is called the problem of identifiability.
+That we are capable of fitting any arbitrary model to a dataset given sufficient degrees of freedom in our parameters is admittedly a disconcerting issue, begging the question `given the structure of the model is it possible to uniquely estimate the unknown parameters?' This question is called the problem of identifiability.
 However, some of the inverse model parameters are constrained by our experimental observations of them and their associated measurement uncertainties.
@@
 
-The \emph{Nelder-Mead} direct search method cannot be used with explicitly constrained problems.
-However, there are various implicit approaches to (approximately) solving general constrained problems using unconstrained algorithms.
+The Nelder-Mead direct search method cannot be used with explicitly constrained problems.
+However, there are various implicit approaches to approximately solve general constrained problems using unconstrained algorithms.
 Generally, this is achieved by domain transformations or the use of penalty functions.
-By the addition of a penalty function which depends in some way on the values of the constraints to the objective function, we minimize a pseudo-objective function where the in feasibility of the constraints is minimized simultaneously to the objective function.
+By the addition of a penalty function which depends in some way on the values of the constraints to the objective function, we minimize a pseudo-objective function where the in-feasibility of the constraints is minimized simultaneously to the objective function.
 
 There are various penalty function schemes.
-We use an Exterior Penalty Function as a simple way of converting converting the constrained problem into an unconstrained one.
-These are are especially useful in cases where the constraints are not ``hard'' in the sense that they need to be satisfied precisely.
+We use an exterior penalty function as a simple way of converting converting the constrained problem into an unconstrained one.
+These are especially useful in cases where the constraints are not `hard' in the sense that they need to be satisfied precisely.
 General penalty functions, which are sequential unconstrained minimization techniques, reformulate the general constrained problem as the pseudo-objective function given by
 
-\[ \phi(\mathbf{x}, r_p ) = F(\mathbf{x}) + r_p P(\mathbf{x}) \]
-where $P \left( \mathbf{x} \right)$ the penalty function, is given by
+\[ \phi(\mathbf{x}, r_p ) = F(\mathbf{x}) + r_p P(\mathbf{x}), \]
+where $P \left( \mathbf{x} \right)$ the penalty function is given by
 \begin{equation} \label{exterior}
@@
 \end{equation}
-We see from Equation \ref{exterior} that there is no penalty if the constraints $g_j(\mathbf{x})$, and $h_k(\mathbf{x})$ are satisfied.
-
-The Exterior Penalty Function specifically (and all Penalty Function approaches in general) do have several drawbacks.
-Namely these include the possibility of the objective function being undefined outside of the set of feasible solutions.
-Additionally, by naively ``encouraging'' feasibility of the solution using large values of the penalty parameter, $r_p$, we will tend to ill-condition the unconstrained formulation of the problem (though in our implementation the preconditioning tends to make the pseudo-objective function less and less sensitive to the constraints as the likelihood is approaches a maximum).
-We use the the measured values of $u_0$, $V_d$, and $E_0$, and the informed guess $q \approx k V_d^{2/3} E_0$ where k is a constant $k \approx 1 \time 10^{-11}$ as an initial guess for the parameter vector $\mathbf{x}$.
+We see from Equation \ref{exterior} that there is no penalty if the constraints $g_j(\mathbf{x})$ and $h_k(\mathbf{x})$ are satisfied.
+
+As with penalty function approaches generally, the exterior penalty function has several drawbacks; namely, the possibility of the objective function being undefined outside of the set of feasible solutions.
+Additionally, by naively encouraging feasibility of the solution using large values of the penalty parameter $r_p$ we will tend to ill-condition the unconstrained formulation of the problem, though in our implementation the preconditioning tends to make the pseudo-objective function less and less sensitive to the constraints as the likelihood is approaches a maximum.
+We use the measured values of $u_0$, $V_d$, and $E_0$, and the informed guess $q \approx k V_d^{2/3} E_0$ where k is a constant $k \approx 1 \time 10^{-11}$ as an initial guess for the parameter vector $\mathbf{x}$.
 We stop the optimization after 300 iterations rather than waiting for convergence.
 
-We're interested in the variance and co-variance as a means to determine the quality if the parameter estimate.
+We are interested in the variance and co-variance as a means to determine the quality of the parameter estimate.
 The $\left( i, j \right)$-th element of the matrix $\sigma (\mathbf{x}, \mathbf{y})$ is equal to the covariance $\mbox{cov}(X_i, Y_j)$ between the $i$-th scalar component of $\mathbf{x}$ and the $j$-th scalar component of $\mathbf{y}$.
-Here the concept of error bars in linear correlation associated with a covariance matrix are not suitable.
-We might try to generalize the idea of confidence intervals to a multidimensional space, but it is likely difficult to describe the surface of the (smallest) hyper-volume containing 90\% of the probability with just a few numbers.
-The situation becomes worse if the probability density function has several maxima.
-However, there is another approach to find the covariance matrix [ref]
-\[ \left[\sigma^2 \right]_{ij} = -\left[ \left( \nabla^2 \mathcal{L}\right)^{-1}\right]_{ij} = 2 \left[ \nabla^2 \left( \chi^2\right)\right]_{ij}^{-1} = -\left[H^{-1} \right]_{ij}\]
+Here the concept of error bars in linear correlation associated with a covariance matrix is not suitable.
+We might try to generalize the idea of confidence intervals to a multidimensional space, but it is difficult to describe the hyper-volume containing a certain percentage of the probability with only a few numbers.
+The situation is worse if the PDF has several maxima.
+However, there is another approach to find the covariance matrix, given by
+\[ \left[\sigma^2 \right]_{ij} = -\left[ \left( \nabla^2 \mathcal{L}\right)^{-1}\right]_{ij} = 2 \left[ \nabla^2 \left( \chi^2\right)\right]_{ij}^{-1} = -\left[H^{-1} \right]_{ij},\]
 where $H$ refers to the Hessian matrix and $\left[\sigma^2 \right]_{ij}$ is the covariance matrix $C$.
-The issue of identifiability is especially fraught for non-linear, black box type problems were it is difficult to explicitly evaluate the Hessian.
-The likelihood function (and thus the posterior probability density function) are defined completely by the optimal solution $\mathbf{x}$ and the second derivative of $\mathcal{L}$ at the maximum, which corresponds to the covariance matrix $C$.
-The standard errors (marginal variances) are the square roots of the diagonal of the covariance matrix.
+The issue of identifiability is especially fraught for non-linear black-box type problems were it is difficult to explicitly evaluate the Hessian.
+The likelihood function, and thus the posterior probability density function, are defined completely by the optimal solution $\mathbf{x}$ and the second derivative of $\mathcal{L}$ at the maximum, which corresponds to the covariance matrix $C$.
+The standard errors, or marginal variances, are the square roots of the diagonal of the covariance matrix.
 The Hessian matrix must be negative definite for $\mathcal{L}$ to have a maximum at $\mathbf{x_0}$.
-We obtain an approximate Hessian using the approach suggested in Nelder's original paper, by fitting quadratics to the simplex vertices and midpoints \cite{nelder_simplex_1965}\cite{spendley_sequential_1962}.
-We can use the condition number
+We obtain an approximate Hessian using the approach suggested in Nelder's original paper by fitting quadratics to the simplex vertices and midpoints\cite{nelder_simplex_1965}\cite{spendley_sequential_1962}.
+We use the condition number
 \[ \mbox{cond} (H) = \frac{\mbox{max}[\mbox{eig}(H)]}{\mbox{min}[\mbox{eig}(H)]} \]
@@
 We find typical condition numbers $\sim \mathcal{O}(10^{27})$.
-In fact, in many cases our Hessian is not negative definite, or invertible at the minmia $\mathbf{x}_0$, which implies negative values of the variances (which is impossible).
+In fact, in many cases our Hessian is not negative definite, or invertible at the minmia $\mathbf{x}_0$, which implies negative values of the variances, which are impossible.
 These issues indicate the problem is extremely ill-conditioned near the minima $\mathbf{x_0}$.
-Given that the parameter estimates are highly colinear, it is unsuprising that the Hessian matrix is near-singular and its inversion is either impossible or involves significant numerical error.
-Posteriori verification of the results is crucial to bound the identifiability of the parameter estimation problem, but it remains as future work.
-Several sources suggest senstivity analysis of the parameter estimates by generation of synthetic Monte Carlo data sets as a means of establishing identifiability \cite{bevington_data_1969}\cite{jaqaman_linking_2006}.
+Given that the parameter estimates are highly co-linear, it is unsuprising that the Hessian matrix is near-singular and its inversion is either impossible or involves significant numerical error.
+Posteriori verification of the results is crucial to bound the identifiability of the parameter estimation problem, but this remains as future work.
+Several sources suggest senstivity analysis of the parameter estimates by generation of synthetic Monte Carlo data sets as a means of establishing identifiability\cite{bevington_data_1969}\cite{jaqaman_linking_2006}.
+
+\section{Summary}
+Notes.
 
 \chapter{Results}
-\section{Charge Estimates}
+\section{Parameter Estimates}
 We found the distribution of mostly likely experimental net charges for a population of the drops jumped in low-gravity.
@@
 A contour plot showing the estimated drop free charge as a function of $V_d$ and $\varphi_s$ is shown in Figure \ref{fig:charge}.
-\begin{figure}[htb]
+\begin{figure}[h]
     \centering
@@
 \end{figure}
-\begin{figure}[htb]
+\begin{figure}[h]
     \centering
@@
 
-The model $q \sim kAE_0$ is incidentally very similar to the classical solution for the surface charge density of a half-spherical conductor with a field-induced dipole \cite{david_j._griffiths_introduction_1999}
+The model $q \sim kAE_0$ is incidentally very similar to the classical solution for the surface charge density of a half-spherical conductor with a field-induced dipole\cite{david_j._griffiths_introduction_1999}
 \begin{eqnarray*}
@@
 with $k \approx 1.3 \times 10^{-10}$.
-This is also of a similar form to the charge found by Takamatsu and coauthors for drops falling from a grounded nozzle in an external electric field \cite{takamatsu_theoretical_1981}
+This is also of a similar form to the charge found by Takamatsu and coauthors for drops falling from a grounded nozzle in an external electric field\cite{takamatsu_theoretical_1981}
 \[q = 4 \pi \epsilon_0 \beta E_0 R_d^2 \]
@@
 
-\begin{figure}[htb]
+\begin{figure}[!htb]
     \centering
@@
 \end{figure}
-\begin{figure}[htb]
-    \centering
-    \resizebox{14cm}{!}{\input{../figures/forces.pgf}}
+\begin{figure}[!htb]
+    \centering
+    \resizebox{14cm}{!}{\input{../figures/forces_all.pgf}}
     \caption{Simulated forces acting on the drop. Experiments are shown by order of increasing apoapse.\label{fig:forces}}
@@
 We also observe that that $\mathbb{E}\mbox{u}$ is not typically a small number in this regime, imperiling our use of asymptotic estimates in this regime.
-We can perhaps gain some insight by comparing the asymptotic estimate for return times to the scaled experiemental return times.
+We can perhaps gain some insight by comparing the asymptotic estimate for return times to the scaled experimental return times.
 We see in Figure \ref{fig:times} that the long-time scaled non-dimensional time of first bounce in the experiment $t_b / t_c$, compares poorly to the asymptotic estimate for returns $t_f$ in the limit of small $\mathbb{E}\mbox{u}_+$, this is due to the use on long-time scaling for drops with $y/L \ll 1$.
-\begin{figure}[htb]
+\begin{figure}[h]
     \centering
@@
 
-\begin{figure}[htb]
-    \centering
-    \input{../figures/times.pgf}
-    \caption{Asymptotic $t_f$ estimates compared with dimensionless bounce times.\label{fig:times}}
+\begin{figure}[h]
+    \centering
+    \input{../figures/times2.pdf_tex}
+    \caption{Dimensional time of flight asymptotic estimates $t_f$ comapred with experimental bounce times.\label{fig:series_s_ds}}
 \end{figure}
@@
 Using an OLS regression, we find the model $\mathbb{I}\mbox{m} \sim (0.012 \pm 0.003) \mathbb{E}\mbox{u} + (0.212 \pm 0.036) $ with $R^2 =0.59$.
-\begin{figure}[htb]
+\begin{figure}[h]
     \centering
@@
 
-Finally we show several trajectories in the long-time scaled regime in Figure \ref{fig:series_l_ds}.
-\begin{figure}[htb]
-    \centering
-    \input{../figures/series_l_ds.pgf}
-    \caption{Non-dimensional trajectories with the long-time scaling as a function of ${\mathbb{E}\mbox{u}}_+$.\label{fig:series_l_ds}}
-\end{figure}
 We should note that there are several kinds of systematic error that influence our data.
@@
 The primary sources of random error are the effect of contact line hysteresis on the drop initial velocity, and of the variance in the MLE parameter estimates.
-%\newpage
-
-%\section{Impact Dynamics \hl{[placeholder section]}}
-%\newpage
+
+\section{Impact Dynamics}
+\hl{Check the Oh numbers}.
+Very little work to date on drop impacts outside of two regimes: first, very low $\mathbb{R}\mbox{e}$ viscous drop spreading driven by capillary forces at the contact line, and second, impacts at ``high'' $\mathbb{W}\mbox{e}$.
+There has been some computational work with impacts at $\mathbb{R}\mbox{e}=1.4$ (Fukai \emph{et al.}), but the results are suspect as the model neglects uncompensated Young's force at the contact line (which is the dominant spreading force for low $\mathbb{R}\mbox{e}$ impacts).
+Of course models for dynamic contact lines in general remain controversial, even for ordinary spreading of liquids, despite decades of work in the area.
+
+Naively neglecting dimensionless groups governing the dynamic contact line, the pertinent dimensionless groups for isothermal droplet impacts are the Weber number $\mathbb{W}\mbox{e} = \frac{\rho U^2 R_d}{\sigma}$, which is a ratio of droplet inertia to surface tension, the Ohnesorge number, $\mathbb{O}\mbox{h} = \frac{\mu}{\sqrt{\rho \sigma R_d}}$, which is a ratio of viscous to inertial and surface tension forces, and the Bond number, $\mathbb{B}\mbox{o}$, defined previously.
+The dynamics of spreading are characterized primarily by $\mathbb{W}\mbox{e}$ and $\mathbb{O}\mbox{h}$.
+Additionally the final stages of spreading depend strongly on $\theta_e$, which is the static contact angle.
+The Weber number scales the \emph{driving force} of the impact.
+In the more familiar case of high $\mathbb{W}\mbox{e}$ the drop liquid bulk is driven radially outward by the impact induced pressure gradient, whereas in the case of small $\mathbb{W}\mbox{e}$ the liquid is pulled outwards by capillary force (e.g.
+uncompensated Young's force) at the contact line.
+The Ohnesorge number, by contrast, scales the force that \emph{resists} spreading.
+For large $\mathbb{O}\mbox{h}$ the resistive force is viscous, whereas for low $\mathbb{O}\mbox{h}$ the force is inertia.
+
+We observe average drop impact $\mathbb{O}\mbox{h} \approx 2.18 \pm 0.36$, and  $\mathbb{W}\mbox{e} \approx 0.28 \pm 0.22$.
+Thus impact velocity plays little role in the spreading dynamics of the bounces, and viscous effects are important but do not dominate inertia.
+Notably we observe underdamped oscillations of drop interfaces during impact.
+according to (Schiaffino, 1997) viscous forces play a role in the final (which?
+describe) stage of spreading even for drop impact at very low $\mathbb{O}\mbox{h}$.
+In the regime of intermediate viscosity, following spreading the oscillations of the interface are damped with a characteristic time that is generally longer than the spreading time (again, given by $t_c \sim \left( \sigma / \rho R_d^3 \right)^{1/2}$).
+The celebrated Hoffman-Tanner-Voinov law, which relates the contact line velocity $U_c$ of an isothermal spreading process to the static contact angle $\theta_e$ to the dynamic advancing contact angle $\theta_a$ by
+\[
+\frac{\mu U_c}{\sigma} \approx \kappa \left( \theta_a^3 - \theta_e^3 \right),
+\]
+where $\kappa \approx 0.013$ is an empirical coefficient extracted from Hoffman's data.
+The Hoffman-Tanner-Voinov law implies that the transition between low $\mathbb{W}\mbox{e}$ inviscid and viscous regimes occurs at $\mathbb{O}\mbox{h} \sim \mathcal{O}(10^{-2})$ rather than $\mathbb{O}\mbox{h} \sim \mathcal{O}(1)$ given by a naive scaling.
+
+Some notes:
+\begin{itemize}
+\item{\textbf{Schiaffino, 1997}} 
+\end{itemize}
+
+\section{Conclusions}
+-conclusions.
+-future directions.
 

### 2018-03-22 doc/manuscript/results.tex
fotmatting changes, updated figures

@@
 
-Naivly neglecting dimensionless groups governing the dynamic contact line, the pertinent dimensionless groups for isothermal droplet impacts are the Weber number $\mathbb{W}\mbox{e} = \frac{\rho U^2 R_d}{\sigma}$, which is a ratio of droplet inertia to surface tension, the Ohnesorge number, $\mathbb{O}\mbox{h} = \frac{\mu}{\sqrt{\rho \sigma R_d}}$, which is a ratio of viscous to inertial and surface tension forces, and the Bond number, $\mathbb{B}\mbox{o}$, defined previously.
+Naively neglecting dimensionless groups governing the dynamic contact line, the pertinent dimensionless groups for isothermal droplet impacts are the Weber number $\mathbb{W}\mbox{e} = \frac{\rho U^2 R_d}{\sigma}$, which is a ratio of droplet inertia to surface tension, the Ohnesorge number, $\mathbb{O}\mbox{h} = \frac{\mu}{\sqrt{\rho \sigma R_d}}$, which is a ratio of viscous to inertial and surface tension forces, and the Bond number, $\mathbb{B}\mbox{o}$, defined previously.
 The dynamics of spreading are characterized primarily by $\mathbb{W}\mbox{e}$ and $\mathbb{O}\mbox{h}$.

### 2018-03-22 doc/manuscript/manuscript.tex
added summaries

@@
 We investigate the dynamics of spontaneous jumps of water droplets from electrically charged superhydrophobic dielectric substrates during a sudden step reduction in gravity level.
-In the brief free-fall environment of a drop tower, with a non-homogeneous external electric field (with strengths ~0.39-2.36 kV/cm) arising due to dielectric surface charges, body forces acting on the jumped droplets are primarily supplied by polarization stress and Coulombic attraction instead of gravity.
+In the brief free-fall environment of a drop tower, with a non-homogeneous external electric field arising due to dielectric surface charges (with surface potentials ~0.4-1.8 kV), body forces acting on the jumped droplets are primarily supplied by polarization stress and Coulombic attraction instead of gravity.
 This electric body force leads to a droplet bouncing behavior similar to well-known phenomena in 1-$g_0$, though occurring for much larger droplets ($\sim$ 0.5 mL).
-We show a simple model for the phenomenon, its scaling, and asymptotic estimates for droplet time of flight.
+We show a simple model for the phenomenon, its scaling, and asymptotic estimates for droplet time of flight in two regimes: firstly, in short-times close to the substrate when drop inertia balances Coulombic force due to net free charge and image charges in the dielectric substrate, and secondly, in long-times far from the substrate when drop inertia balances free charge Coulombic force and drag.
 The droplet trajectories are controlled primarily by the dimensionless electrostatic Euler number $\mathbb{E}\mbox{u}$, which is a ratio of inertial to electrostatic forces.
-For ${\mathbb{E}\mbox{u}}_+ \gg 1/8 \pi$ droplets escape the electric field.
-The droplet net charge, estimated to be on the order of $1 \times 10^{-9}$ C, is field-induced rather than occurring by contact charging at the (PTFE coated) hydrophobic interface.
-In 1-$g_0$, for Weber numbers $>$ 0.4, impact recoil behavior on a super-hydrophobic surface is normally dominated by damping from contact line hysteresis.
-However, for the low Bond and Ohnesorge numbers occurring in free-fall, the droplet impact dynamics additionally include electrohydrodynamic surface wettability effects.
-This is qualitatively discussed in terms of trends in coefficients of restitution and dimensionless contact time.
+To experimentally determine values of $\mathbb{E}\mbox{u}$ we conduct a series of drop tower experiments where we observe the effect of droplet volume, net free charge, and static surface potential of the superhydrophobic substrate on droplet trajectories.
+We use a direct search optimization to obtain a Maximum Likelihood Estimate for drop net charge, as we do not measure it directly in experiment.
+For $B \mathbb{E}\mbox{u} /8 \pi > 1$ droplets escape the electric field, however we do not observe any escapes in our dataset.
+Finally, with an eye towards engineering applications we consider the results in light of the so-called low-gravity phase separation problem with a short space system design worked example problem.
 
@@
  \centering
- \includegraphics[width=0.75\textwidth]{../figures/apparatus0.pdf}
+  \input{../figures/apparatus01.pdf_tex}
  \caption{A schematic representation of a drop electro-bounce experiment with labeled characteristic time and length scales, \hl{$t_c$, $y_c$} shown.
@@
 \end{figure}
-These plots show a trend of decreasing time-of-flight $t_f$, which is the time for the drop to return to the origin, or complete a single ``bounce'', and height at apoapse with increasing values of $\mathbb{I}\mbox{g}$.
+These plots show a trend of decreasing time-of-flight $t_f$, which is the time for the drop to return to the origin, or complete a single `bounce', and height at apoapse with increasing values of $\mathbb{I}\mbox{g}$.
 When $\mathbb{I}\mbox{g} = 1$, $t_f$ is exactly half of characteristic time scale in this regime.
@@
 \begin{equation}\label{escape}
-\frac{1}{8 \pi} B \mathbb{E}\mbox{u} > 1.
+\frac{B}{8 \pi} \mathbb{E}\mbox{u} > 1.
 \end{equation}
@@
 \section{Summary}
-Notes.
+The objective of this work is to understand the basic physics of the low-gravity drop bounce phenomenon to the point where we can make useful predictions of drop behavior for engineering purposes.
+To that end, in this chapter we have shown the following:
+\begin{itemize}
+\item We develop from first principles a simple 1-dimensional model of drop trajectories subject to Coulombic forces and drag under low-gravity.
+Drops are idealized as point charges.
+We find that polarization stresses are negligible, and that water drops can be modeled as ideal conductors under the conditions of our experiments.
+\item By scaling arguments we find characteristic length and time scales for both a short-times regime where inertia balances Coulombic force and forces due to image charges, and a long-times regime where inertia balances Coulombic force and drag.
+In both regimes a key dimensionless group appears: the electrostatic Euler number $\mathbb{E}\mbox{u}$, which is a ratio of inertia to electrostatic force.
+\item The governing ODE is non-linear, but we find approximate analytic solutions for the drop trajectory and time of flight in both regimes by means of asymptotic expansions.
+\item We find a limiting initial velocity $U_0$ for which drop time of flight grows without bound.
+This electrostatic escape velocity is analogous to the gravitational escape velocity of a planet or other massive body.
+\end{itemize}
 
@@
 \section{Overview}
-We are concerned mainly about what parameters are important in electrostatic transport of relatively large millimetric drops in low-gravity, and what the values of the respective dimensionless numbers might be; namely, $\mathbb{I}\mbox{g}$, and $\mathbb{E}\mbox{u}$.
+We are interested mainly about which parameters are important in electrostatic transport of relatively large millimetric drops in low-gravity, and what the values of the respective dimensionless numbers might be; namely, $\mathbb{I}\mbox{g}$, and $\mathbb{E}\mbox{u}$.
 However, this raises an interesting challenge; it is impractical to directly measure all of the key physical quantities that appear in the dimensionless groups at once in a drop tower experiment.
@@
 \section{Summary}
-Notes.
+The objectives of our experimental work are to validate the earlier scaling results by identifying values of the physical parameters which appear in the relevant dimensionless groups.
+To accomplish this we conduct a series of low-gravity experiments in a 2.1 s drop tower, where we observe the trajectories of spontaneous drop jumps and rebounds from charged dielectric superhydrophobic substrates.
+\begin{itemize}
+\item  In drop tower experiments we vary the independent variables $V_d$ and $\sigma$ and capture the trajectories of the droplets using high-speed video. 
+\item We produce superhydrophobic electret substrates with surface potentials 0.7-4.0 $kV$ and contact angles $\sim 150^{\circ}$ with approximately $25^{\circ}$ contact angle hysteresis when uncharged.
+The dielectrics are a lamina of 3-4 corona charged 0.4 mm PMMA sheets.
+The electric field scales with the number of dielectric lamina.
+The superhydrophobic layer of the electret lamina is manufactured by laser etching a $\sim$775 $\mu$m deep square array of pillars into the PMMA sheet, followed by a PTFE spray deposition process.
+\item We solve the inverse problem to identify key parameters which we cannot measure directly in the drop tower experiments.
+This is accomplished by Maximum Likelihood Estimation using constrained direct search optimization.
+\item We fail to establish the identifiability of the parameter estimate using the conventional approach of inverting the Hessian near the optima.
+This indicates ill-conditioning of the parameter estimation problem, likely due to large multicolinearity between the main factors $q$, $V_d$ and $\sigma$.
+To robustly estimate the error of the parameter estimates an alternate approach, such as the Monte Carlo method, is required.
+\end{itemize}
 
@@
 The Hoffman-Tanner-Voinov law implies that the transition between low $\mathbb{W}\mbox{e}$ inviscid and viscous regimes occurs at $\mathbb{O}\mbox{h} \sim \mathcal{O}(10^{-2})$ rather than $\mathbb{O}\mbox{h} \sim \mathcal{O}(1)$ given by a naive scaling.
+
+In 1-$g_0$, for Weber numbers $>$ 0.4, impact recoil behavior on a super-hydrophobic surface is normally dominated by damping from contact line hysteresis.
+However, for the low Bond and Ohnesorge numbers occurring in free-fall, the droplet impact dynamics additionally include electrohydrodynamic surface wettability effects.
+This is qualitatively discussed in terms of trends in coefficients of restitution and dimensionless contact time.
 

### 2018-03-23 doc/manuscript/manuscript.tex
various changes to manuscript

@@
 
-%\doublespacing
 \section*{Abstract}
@@
 \noindent
-We investigate the dynamics of spontaneous jumps of water droplets from electrically charged superhydrophobic dielectric substrates during a sudden step reduction in gravity level.
-In the brief free-fall environment of a drop tower, with a non-homogeneous external electric field arising due to dielectric surface charges (with surface potentials ~0.4-1.8 kV), body forces acting on the jumped droplets are primarily supplied by polarization stress and Coulombic attraction instead of gravity.
-This electric body force leads to a droplet bouncing behavior similar to well-known phenomena in 1-$g_0$, though occurring for much larger droplets ($\sim$ 0.5 mL).
-We show a simple model for the phenomenon, its scaling, and asymptotic estimates for droplet time of flight in two regimes: firstly, in short-times close to the substrate when drop inertia balances Coulombic force due to net free charge and image charges in the dielectric substrate, and secondly, in long-times far from the substrate when drop inertia balances free charge Coulombic force and drag.
-The droplet trajectories are controlled primarily by the dimensionless electrostatic Euler number $\mathbb{E}\mbox{u}$, which is a ratio of inertial to electrostatic forces.
-To experimentally determine values of $\mathbb{E}\mbox{u}$ we conduct a series of drop tower experiments where we observe the effect of droplet volume, net free charge, and static surface potential of the superhydrophobic substrate on droplet trajectories.
+We investigate the dynamics of spontaneous jumps of water drops from electrically charged superhydrophobic dielectric substrates during a sudden step reduction in gravity level.
+In the brief free-fall environment of a drop tower, with a non-homogeneous external electric field arising due to dielectric surface charges (with surface potentials ~0.4-1.8 kV), body forces acting on the jumped drops are primarily supplied by polarization stress and Coulombic attraction instead of gravity.
+This electric body force leads to a drop bouncing behavior similar to well-known phenomena in 1-$g_0$, though occurring for much larger drops ($\sim$ 0.5 mL).
+We show a simple model for the phenomenon, its scaling, and asymptotic estimates for drop time of flight in two regimes: firstly, in short-times close to the substrate when drop inertia balances Coulombic force due to net free charge and image charges in the dielectric substrate, and secondly, in long-times far from the substrate when drop inertia balances free charge Coulombic force and drag.
+The drop trajectories are controlled primarily by the dimensionless electrostatic Euler number $\mathbb{E}\mbox{u}$, which is a ratio of inertial to electrostatic forces.
+To experimentally determine values of $\mathbb{E}\mbox{u}$ we conduct a series of drop tower experiments where we observe the effect of drop volume, net free charge, and static surface potential of the superhydrophobic substrate on drop trajectories.
 We use a direct search optimization to obtain a Maximum Likelihood Estimate for drop net charge, as we do not measure it directly in experiment.
-For $B \mathbb{E}\mbox{u} /8 \pi > 1$ droplets escape the electric field, however we do not observe any escapes in our dataset.
+For $B \mathbb{E}\mbox{u} /8 \pi > 1$ drops escape the electric field, however we do not observe any escapes in our dataset.
 Finally, with an eye towards engineering applications we consider the results in light of the so-called low-gravity phase separation problem with a short space system design worked example problem.
@@
 
+\doublespacing
 \mainmatter
@@
 The study also suggested applications in cryogenic tank vent screening, and in reducing heat transfer to cryogenic propellants (and thus boiloff losses) by dielectrophoretically positioning ullage vapors around the tank walls as a thermal barrier.
-EHD forces have been studied for enhancing boiling heat transfer by promotion of bubble detachment and prevention of dryout, again as an ersatz bouyancy\cite{snyder_dielectrophoresis_2001}\cite{di_marco_influence_2003}\cite{marco_use_2012}.
+EHD forces have been studied for enhancing boiling heat transfer by promotion of bubble detachment and prevention of dryout, again as an ersatz bouyancy\cite{snyder_dielectrophoresis_2001, di_marco_influence_2003, marco_use_2012}.
 EHD heat pipes, which substitute an electrode structure for the capillary wicking structure of a conventional thermocapillary heat pipe can evade the wicking limit\cite{jones_electrohydrodynamic_1973}.
@@
 Dielectrophoretic settling of cryogenic propellants, in both total and partial communication Propellant Management Device (PMD) configurations, has been studied analytically in both static\cite{hurwitz_electrohydrodynamic_1966} and dynamic cases\cite{koval_dynamics_1967}, and in drop tower experiments\cite{fax_dielectrophoretic_1969}.
-EHD forces have also been applied to the low-g slosh baffling problem\cite{boretz_orbital_1970}\cite{petrash_use_1968}\cite{hurwitz_dielectrophoretic_1968}, and studied extensively for the mitigation of vapor pullthrough during tank draining, and concomittent minimization of propellant residuals at burnout, in a series of experiments at the NASA Lewis (now Glenn) Research Center 2.2 s drop tower facillity\cite{berenyi_dielectrophoretic_1970}.
+EHD forces have also been applied to the low-g slosh baffling problem\cite{boretz_orbital_1970, petrash_use_1968, hurwitz_dielectrophoretic_1968}, and studied extensively for the mitigation of vapor pullthrough during tank draining, and concomittent minimization of propellant residuals at burnout, in a series of experiments at the NASA Lewis (now Glenn) Research Center 2.2 s drop tower facillity\cite{berenyi_dielectrophoretic_1970}.
 
 \section{Spontaneous Drop Jump}
-Low-gravity phase separation, droplet dynamics, and the dynamics and applications of the so-called spontaneous droplet jump, is an active area of study at the Portland State University Dryden Drop Tower labratory (DDT).
-When a nonwetting, gravity dominated sessile droplet (e.g.
+Low-gravity phase separation, droplet dynamics, and the dynamics and applications of the so-called spontaneous drop jump, is an active area of study at the Portland State University Dryden Drop Tower labratory (DDT).
+When a nonwetting, gravity dominated sessile drop (e.g.
 a puddle), which is initially at rest on a surface in the Cassie-Baxter state suddenly undergoes a large step reduction in $\mathbb{B}\mbox{o}$ it will spontaneously jump away from the surface.
-The Cassie-Baxter state, sometimes also known as the Fakir state, is a metastable heterogenously non-wetting state on a textured surface characterized by the existance of a vapor-layer which seperates roughness features of the surface from the bottom of the droplet.
+The Cassie-Baxter state, sometimes also known as the Fakir state, is a metastable heterogenously non-wetting state on a textured surface characterized by the existance of a vapor-layer which seperates roughness features of the surface from the bottom of the drop.
 The spontaneous drop jump was first observed experimentally in the Soviet Union by Kirko \emph{et al.}\cite{kirko_phenomenon_1970} in 1970 for drops of mercury in hydrochloric acid, and later by Wollman \emph{et al.} in 2016 for water drops in a set of experiments conducted using drop towers\cite{wollman_more_2016}.
@@
 The forces at work in such situations are presumably electrostatic in origin.
-Though this was an unintended effect during our work on spontaneous drop jump, the phenomenon is interesting itself.
-There is a certain irony to this typical failure of low-gravity intuition, where relatively tiny electrostatic forces have become suddenly large in the absence of gravity leading to unintentional experimental results, being as we are experienced low-gravity researchers who perhaps should know better.
+Not without irony given our earlier discussion of underdeveloped low-gravity intuition, we note that though the drop electro-bounce was an accidental effect during our work on spontaneous drop jump, the phenomenon is interesting itself.
+This has motivated further study, and the drop `electro-bounce' phenomenon is the subject of this thesis.
 A time-lapsed composite image showing an example of the phenomenon is shown in Figure \ref{fig:bounce}.
@@
 
-This ``electro-bounce'' phenomenon is the subject of this thesis. We begin with some preliminary observations of the phenomenon:
+We begin with some preliminary observations of the phenomenon:
 \begin{itemize}
@@
 The superhydrophobic surfaces used in the spontanous drop jump experiments have thin (nanometric) PTFE coatings, and we observe that it is extremely easy to produce significant surface potentials, $\varphi_s \sim$ 100-500 V, by simply flowing streams of distilled water over them.
-A study of this water on PTFE contact charging phenomenon was conducted by Yatsuzuka \emph{et al.}\cite{yatsuzuka_electrification_1994}, who suggest that this process results from formation of an electrical double layer driven by selective adsorption of ($\mbox{OH}^-$) ions at the polymer surface; other recent work strongly supports this hypothesis\cite{beattie_intrinsic_2006}\cite{strazdaite_water_2015}.
+A study of this water on PTFE contact charging phenomenon was conducted by Yatsuzuka \emph{et al.}\cite{yatsuzuka_electrification_1994}, who suggest that this process results from formation of an electrical double layer driven by selective adsorption of ($\mbox{OH}^-$) ions at the polymer surface; other recent work strongly supports this hypothesis\cite{beattie_intrinsic_2006, strazdaite_water_2015}.
 Yatsuzuka \emph{et al.} also found that the specific charge on the drops in contact with the surface depends on their both surface velocity and conductivity.
@@
 The assumed initial conditions are such that, when $\mathbb{B}\mbox{o}$ is suddenly reduced at the start of the drop tower free-fall period, the drop jumps with instantaneous initial velocity $U_0$ from its 1-$g_0$ resting position with fixed radius $R_d$ at $t=0$.
+The dynamical system is sketched out schematically Figure \ref{apparatus}.
 We now define models for each of the forces in this equation.
 
-For the intermediate range of Reynolds numbers $1 \leq \mathbb{R}\mbox{e} \equiv \frac{2UR_d}{\nu} \leq 5000 $ observed in our experiments the force of drag acting on the drop may be quadratic such that,
+For the intermediate range of Reynolds numbers $1 \leq \mathbb{R}\mbox{e} \equiv \frac{2UR_d}{\nu} \leq 2000 $ observed in our experiments the force of drag acting on the drop may be quadratic such that,
 \begin{equation*}\label{drag_force}
@@
  \mathbf{F}_E &=& q \mathbf{E} + \mathbf{F}_{DEP} + \mathbf{F}_I \\
- &=& q \mathbf{E} + \frac{k q^2}{16 \pi \epsilon_0 } y^{-2} \hat{\mathbf{j}} + 2 \pi R_d^3 \epsilon K \nabla E^2, 
+ &=& q \mathbf{E} + \frac{k q^2}{16 \pi \epsilon_0 } y^{-2} \hat{\mathbf{j}} + 2 \pi R_d^3 \kappa_1 \epsilon_0 K \nabla E^2, 
 \end{eqnarray*}
@@
 As an aside, in treating the drop as an ideal conductor we note that in our specific case the electrostatic force is not a body force \emph{per se} as the electric field is acting on charges on the surface of the conductor.
+\begin{figure}[ht]
+\centering
+\includegraphics[width=0.65\textwidth]{../figures/apparatus0.pdf}
+\label{apparatus}
+\caption{A schematic representation drop jump with return and rebound from an electrically charged superhydrophobic substrate.
+The characteristic time and length scales $t_c$ and $y_c$ describe the time of flight and apoapse associated with the drop trajectory.}
+\end{figure}
 
@@
 If the charge in a line element, $dx$ is $\sigma L dx$, where $\sigma$ is the average surface charge density, the electric field of a line charge is given by\cite{david_j._griffiths_introduction_1999}
-\[d E_r = \frac{k \sigma L dx}{4 \pi \epsilon_0 r \sqrt{r^2 + L^2/4}}.
+\[d E_r = \frac{\sigma L dx}{4 \pi \epsilon_0 r \sqrt{r^2 + L^2/4}}.
 \]
@@
     \def\svgwidth{\columnwidth}
-    \input{../figures/E02.pdf_tex}
+    \input{../figures/E0.pdf_tex}
     \caption{A log-log plot of the magnitude of the dimensionless electric field $E$.\label{fig:E0}}
@@
 \end{equation*}
-We note the existence of several dimensionless groups
+From Equation \ref{scaled_eqn} we note the existence of several dimensionless groups
 \[ \mathbf{\Pi}_1 = \frac{C_D \rho A y_c}{2 m}, \hspace{5 mm}
@@
 \end{equation*}
-\begin{figure}[ht]
- \centering
-  \input{../figures/apparatus01.pdf_tex}
- \caption{A schematic representation of a drop electro-bounce experiment with labeled characteristic time and length scales, \hl{$t_c$, $y_c$} shown.
-Also shown are the dimensions of the superhydrophobic electret substrate.\label{fig:apparatus0}}
-\end{figure}
 
@@
 Looking at this solution it is evident that if $\mathbb{I}\mbox{g}=0$, the solution is the classical kinematic equation for projectile motion without drag under constant gravity $g_0$.
-Continuing on with this procedure we find, after some tedious computations documented in in the project repository for this thesis\cite{schmidt_droplet_electro-bounce:_2017}, the $\mathcal{O}(\mathbb{E}\mbox{u}^5)$ order accurate solution, truncated to $\mathcal{O}(\mathbb{E}\mbox{u}^2)$ below.
+Continuing on with this procedure we find, after some tedious computations documented in the project repository for this thesis\cite{schmidt_droplet_electro-bounce:_2017}, the $\mathcal{O}(\mathbb{E}\mbox{u}^5)$ order accurate solution, truncated to $\mathcal{O}(\mathbb{E}\mbox{u}^2)$ below.
 \begin{eqnarray}
@@
 These plots show a trend of decreasing time-of-flight $t_f$, which is the time for the drop to return to the origin, or complete a single `bounce', and height at apoapse with increasing values of $\mathbb{I}\mbox{g}$.
-When $\mathbb{I}\mbox{g} = 1$, $t_f$ is exactly half of characteristic time scale in this regime.
-In the limit of small $\mathbb{E}\mbox{u}$ the trajectories collapse to the $\mathcal{O}(1)$ solution regardless of the Image number.
+When $\mathbb{I}\mbox{g} = 1$, $t_f$ is exactly half of the characteristic time scale in this regime.
+In the limit of small $\mathbb{I}\mbox{m}$ the trajectories collapse to the $\mathcal{O}(1)$ solution regardless of the electrostatic Euler number.
 In principle there is some coupling between $\mathbb{E}\mbox{u}$ and $\mathbb{I}\mbox{g}$; notably this relationship does not depend on the electric field $E_0$ but on a charge to mass ratio.
@@
 Trajectory for this solution are shown in Figure \ref{fig:long_times}.
-If we assume a constant scale for the drag coefficient, $C_d \approx 0.5$, then $\mathbb{D}\mbox{g}$ is approximately a constant $\mathbb{D}\mbox{g} \approx 6 \times 10^{-4}$ in all of our experiments.
 \begin{figure}[htb]
@@
 \end{figure}
-Again, the trajectory seemingly reduces to the classical $\mathcal{O}(1)$ solution for small values of of $\mathbb{E}\mbox{u}$.
-We also note that with $\mathbb{D}\mbox{g} = 6 \time 10^{-4}$ the effect of drag is slight, appearing only as a slight correction to the higher order terms; the apoapse is nearly equal to half the characteristic length scale.
+If we assume a constant scale for the drag coefficient, $C_d \approx 0.5$, then $\mathbb{D}\mbox{g}$ is approximately a constant $\mathbb{D}\mbox{g} \approx 6 \times 10^{-4}$ in all of our experiments.
+We note that the trajectory reduces to the classical $\mathcal{O}(1)$ solution for small values of of $B \mathbb{E}\mbox{u}$.
+We also note that with $\mathbb{D}\mbox{g} = 6 \times 10^{-4}$ the effect of drag is slight, appearing only as a slight correction to the higher order terms.
 
@@
 \begin{equation}\label{escape}
-\frac{B}{8 \pi} \mathbb{E}\mbox{u} > 1.
+\frac{1}{8 \pi} B \mathbb{E}\mbox{u} > 1.
 \end{equation}
@@
 \section{Summary}
-The objective of this work is to understand the basic physics of the low-gravity drop bounce phenomenon to the point where we can make useful predictions of drop behavior for engineering purposes.
+The objective of this work is to understand the basic physics of the low-gravity drop electro-bounce phenomenon to the point where we can make useful predictions of drop behavior for engineering purposes.
 To that end, in this chapter we have shown the following:
@@
 However, this raises an interesting challenge; it is impractical to directly measure all of the key physical quantities that appear in the dimensionless groups at once in a drop tower experiment.
-In particular, determination of net drop free electric charge $q$, is difficult as high-input resistance electrometers are not well-suited to sudden the 15-$g_0$ decelerations characteristic of drop tower experiments.
-Schematic representations of drop jump statics and dynamics are shown in Figures \ref{fig:apparatus0} and \ref{fig:schematic}.
+In particular, determination of net drop free electric charge $q$, is difficult as high-input resistance electrometers are not well-suited to the sudden 15-$g_0$ decelerations characteristic of drop tower experiments.
 To find typical values of these parameters we use the following approach:
@@
 \end{enumerate}
+A schematic representation of drop jump system statics is shown in Figure and \ref{fig:schematic}.
 \begin{figure}[ht]
@@
  \includegraphics[width=0.65\textwidth]{../figures/schematic.pdf}
- \caption{A schematic representation of the drop initial condition, resting on the superhydrophobic surface in the Cassie-Baxter state just prior to the drop tower experiment.
+ \caption{The drop is shown in the initial condition, resting on the superhydrophobic surface in the Cassie-Baxter state just prior to the drop tower experiment.
 The variables $q$, $\sigma$, and $V_d$ are the drop net free charge, dielectric surface charge density, and drop volume respectively.\label{fig:schematic}}
@@
 The DDT uses a dual capsule design, inspired by the 2.2 s facility at NASA Glenn Research Center, which decouples drag acceleration felt by the external drag shield from the experiment.
-The experiment experiences approximately $\lessapprox 1 \times 10^{-4}$ $g_0$ during free-fall for the 2.1s as the rig and drag shield plummet to the bottom of drop tower 6 stories below.
+The experiment experiences approximately $\lessapprox 1 \times 10^{-4}$ $g_0$ during free-fall for 2.1s as the rig and drag shield plummet to the bottom of drop tower 6 stories below.
 Single drops of distilled water in a range of volumes ($0.01 \leq R_d \leq 0.5$ mL), are carefully deposited on charged superhydrophobic substrates using an grounded glass syringe with $\pm $1 $\mu$L accuracy and then dropped in the drop tower.
@@
 
-Superhydrophobic electrets are prepared, with surface potentials $\varphi_s = 0.7$-$4.0$ kV.
+Superhydrophobic electret substrates are prepared, with surface potentials $\varphi_s = 0.7$-$4.0$ kV.
 According to a review by Sessler\cite{sessler_electrets_1987}, an electret is a dielectric material with quasi-permanent electric charge in the sense that the characteristic decay period of the electret is much greater than a practical experiment time scale.
@@
 Electrets have a plethora of applications, but most germanely they have been used in Electro-Wetting On Dielectric (EWOD) devices for low-voltage manipulation of small drops\cite{wu_low-voltage_2010}.
-Real charge electrets can be produced by contact electrification, injection or deposition of charge carriers by discharge or electron beam, ionizing radiation, or by frictional triboelectrification.
+Real charge electrets can be produced by contact electrification, injection or deposition of charge carriers by corona discharge or electron beam, ionizing radiation, or by frictional triboelectrification.
 Dipolar electrets by contrast are produced by a combination of polarization at elevated temperatures in a strong external electric field followed by an annealing process.
@@
 
-We use an isothermal electret formation process using a variation of the widely applied corona-charging technique.
+We use an isothermal electret formation process which is a variation of the widely applied corona-charging technique.
 Typical corona-charging techniques uses strong inhomogenous DC electric fields to produce discharge in air at ambient conditions; the dielectric substrate is atop a grounded electrode and there is a screening potential electrode intermediately positioned to control the surface potential.
@@
 Some work\cite{van_turnhout_thermally_1975} by van Turnhout using Thermally Stimulated Current (TCS) measurements showed that in 4.8 mm thick polymethyl methacrylate (PMMA) polarization of the dielectric is non-uniform due to real space-charge mostly ($\sim$90\%) residing in a thin (0.1-0.2 mm) layer near the free-surface of the sample.
-In this work we use a Ptec IN5120 balanced AC corona ion source, to direct a net neutral stream of ions towards the dielectric target, which we polarize by an electrode with a EMCO P20P $2$ kV$+$ absolute reference DC-DC converter.
+In this work we use a Ptec IN5120 balanced AC corona ion source, to direct a net neutral stream of ions towards the dielectric target, which we polarize by an electrode with an EMCO P20P $2$ kV$+$ absolute reference DC-DC converter.
 The ion stream compensates the surface and space bound charges arising due to the polarization of the dielectric.
@@
 }
-    \caption{(a)The drop electro-bounce experiment hardware mounted on a drop tower rig. (b) Close up of the experimental test cell.\label{fig:rig}}
+    \caption{(a) The drop electro-bounce experiment hardware mounted on a drop tower rig. (b) Close up of the experimental test cell.\label{fig:rig}}
 \end{figure}
@@
 Surface potentials $\varphi_s$, are measured on the superhydrophobic surface using a Simco-Ion FMX-004 electrostatic fieldmeter and the method for determination of surface charge density for low conductivity polymers described in Davies\cite{davies_examination_1967}.
-This measurement is made with the superhydrophobic surfaces connected by a conductive ground plane by conductive tape far from the presence of other conductors.
+This measurement is made with the electret substrate connected to a conductive ground plane by conductive tape far from the presence of other conductors.
 An ideal approach to determining surface charge on a dielectric surface is to screen perturbing effects of external electric fields.
@@
 A further consideration is the possibility of the change in total charge during a typical experimental timescale.
-If we consider the drop rig to be a ground which is reasonable given that the rig is isolated from true ground, but is at some reference voltage with respect to the surface charges on the dielectric with an abundance of free charge carriers, then there will be both bulk and surface decay of the charge on the dielectric.
+If we consider the drop rig to be a ground which is reasonable given that the rig is isolated from true ground, but is at some reference voltage with respect to the surface charges on the dielectric with an abundance of free charge carriers, then there will be both bulk and surface Ohmic decay of the charge on the dielectric.
 The evolution of the charge can in some cases be approximated by
@@
 For an example case of a surface with relative permittivity $\kappa = 3.5$ and bulk resistivity $\rho = 1.6 \times (10^{16})$ $\Omega$cm such as with the case of a 2.8 mm PMMA sheet, then the time constant $\tau = \kappa \epsilon_0 \rho$ is approximately 5000 s, which is significantly longer than the typical time period for a drop tower experiment.
-We measured the charge decay with a calibrated probe at periodic intervals.
-There are several charge decay mechanisms: internal ones such as Ohmic resistence, and external ones such as compensation by envonmental ionic species.
+External charge decay mechanisms include compensation by envonmental ionic species.
 The relative magnitudes of these charge transport mechanisms, and therfore the stability of the electret, vary drastically depending on the initial surface potential, material properties, environment, and charging method.
@@
 Using various scaling arguments we have gleaned from our simple model a series of dimensionless numbers characteristic of drop bounce apoapses and times of flight.
-These dimensionless numbers depend on physical properties.
-Unfortunately, not all of these properties are easily measured by experiment.
+These dimensionless numbers depend on physical properties not all of which are easily measured by experiment.
 Drop free charge $q$, in particular, could in principle be directly measured by collecting the charged drops in a faraday cup under low-g and measuring the change in capacitance of the cup using a high input-resistance electrometer, but this method is difficult to apply in practice in a drop tower.
-Other state variables we can directly measure with varying levels of accuracy.
+Other variables we can directly measure with varying levels of accuracy.
 
@@
 Mathematically we state that we find the parameters $\mathbf{x}$ that solve the inverse problem $G(\mathbf{x}) = \mathbf{d}$ using the Nelder-Mead direct search method to maximize the log-likelihood of the data.
-This is equivalent to minimizing the $\chi^2$ goodness-of-fit between an experimentally observed droplet trajectory and the trajectory predicted by Equation \ref{gov_eqn_subs} given a vector of parameters $\mathbf{x} = \left\langle q, \hspace{2 mm} V_d, \hspace{2 mm} \sigma \right\rangle$.
+This is equivalent to minimizing the $\chi^2$ goodness-of-fit between an experimentally observed drop trajectory and the trajectory predicted by Equation \ref{gov_eqn_subs} given a vector of parameters $\mathbf{x} = \left\langle q, \hspace{2 mm} V_d, \hspace{2 mm} \sigma \right\rangle$.
 This problem is stated as
@@
 We can therefore infer that $\mbox{prob}(X|D, I) \propto \mbox{prob}(D|X, I)$.
-The MLE for the model parameters $\mathbf{x_0}$ is given by the maximum of the posterior PDF, which is equivalent to the solution of the ODE given the the parameters $\mathbf{x}$, that produces the highest probability of the observed data.
+The MLE for the model parameters $\mathbf{x_0}$ is given by the maximum of the posterior PDF, which is equivalent to the solution of the ODE given the parameters $\mathbf{x}$, that produces the highest probability of the observed data.
 Since the likelihood $\mathcal{L}(\mathbf{x}) = \prod_i^n \mathcal{P}_i$ and the probability $\mathcal{P}$ of any single observation is less than one, then the total likelihood which is the product of a large number of probabilities is vanishingly small.
@@
 }
-       \caption{(a) Schematic noisy droplet trajectory data.
+       \caption{(a) Schematic noisy drop trajectory data.
 We see that 1D Gaussian convolution and Wiener filters suffer from significant end effects.
@@
 In general, noisy, black box, non-linear, non-quadratic, non-convex, constrained, ill-conditioned, high-dimensional objective functions are problematic to optimize.
-Unfortunately, problems of this type are the essence of the parameter estimation, which often leads to its characterization as an `art' rather than a precise science.
+Unfortunately, problems of this type are the essence of parameter estimation, and of our problem particularly.
+These difficulties often lead to the characterization of parameter estimation as an `art' rather than a precise science.
 
@@
 While in principle a gradient-based optimizer, such as the quasi-Newton method of Broyden, Fletcher, Goldfarb, and Shanno (BFGS)\cite{nocedal_numerical_2006}, could be used by using finite-differences to obtain approximate gradients of the $\chi^2$ objective function, in practice doing so is extremely problematic because the noise-to-signal ratio of the objective function scales like $\mathcal{O}(f)$ for $df/dt$ and $\mathcal{O}(f^2)$ for $d^2f/dt^2$ which will tend to cause convergence to a local minima that is only an artifact of the likelihood response surface\cite{wood_data_1982}.
-As a further practical matter, given the relatively expensive function-calls gradient-free approaches tend to offer better performance regardless\cite{kolda_optimization_2003}, especially when evaluating the objective function requires solving a stiff, non-linear ODE.
-
-We use a gradient-free, direct-search approach: Nelder-Mead\cite{nelder_simplex_1965} implemented in \verb|scipy.optimize|.
+As a further practical matter, if evaluating the objective function is computationally expensive, for instance if it requires solving a stiff, non-linear ODE, then gradient-free approaches tend to converge faster regardless\cite{kolda_optimization_2003}.
+
+We use a gradient-free, direct-search approach: the Nelder-Mead\cite{nelder_simplex_1965} algorithem implemented in \verb|scipy.optimize|.
 Nelder-Mead is relatively robust to noise and is thrifty with our computationally expensive function-calls.
@@
     \resizebox{\textwidth}{!}{\input{../figures/inverse_problem2.pgf}}
-    \caption{A series of drop trajectories showing the results of the parameter estimation.
+    \caption{A set of drop trajectories showing the results of the parameter estimation.
 The trajectories are shown only up to the apoapse of the first bounce.
@@
 That we are capable of fitting any arbitrary model to a dataset given sufficient degrees of freedom in our parameters is admittedly a disconcerting issue, begging the question `given the structure of the model is it possible to uniquely estimate the unknown parameters?' This question is called the problem of identifiability.
-However, some of the inverse model parameters are constrained by our experimental observations of them and their associated measurement uncertainties.
+However, apart from the drop free charge the inverse model parameters are constrained by our experimental observations of them and their associated measurement uncertainties.
 This, we hope, makes the specter of an over fit model less frightening, but does convert our unconstrained optimization problem to an constrained one which raises special difficulties of its own, which we discuss below.
@@
 \end{equation}
-We see from Equation \ref{exterior} that there is no penalty if the constraints $g_j(\mathbf{x})$ and $h_k(\mathbf{x})$ are satisfied.
+We see from Equation \ref{exterior} that there is no penalty if the inequality constraints $g_j(\mathbf{x})$ and equality constraints $h_k(\mathbf{x})$ are satisfied.
 
@@
 Additionally, by naively encouraging feasibility of the solution using large values of the penalty parameter $r_p$ we will tend to ill-condition the unconstrained formulation of the problem, though in our implementation the preconditioning tends to make the pseudo-objective function less and less sensitive to the constraints as the likelihood is approaches a maximum.
-We use the measured values of $u_0$, $V_d$, and $E_0$, and the informed guess $q \approx k V_d^{2/3} E_0$ where k is a constant $k \approx 1 \time 10^{-11}$ as an initial guess for the parameter vector $\mathbf{x}$.
+We use the measured values of $u_0$, $V_d$, and $E_0$, and the informed guess $q \approx k V_d^{2/3} E_0$ where k is a constant $k \approx 1 \times 10^{-11}$ as an initial guess for the parameter vector $\mathbf{x}$.
 We stop the optimization after 300 iterations rather than waiting for convergence.
@@
 Here the concept of error bars in linear correlation associated with a covariance matrix is not suitable.
-We might try to generalize the idea of confidence intervals to a multidimensional space, but it is difficult to describe the hyper-volume containing a certain percentage of the probability with only a few numbers.
-The situation is worse if the PDF has several maxima.
 However, there is another approach to find the covariance matrix, given by
 \[ \left[\sigma^2 \right]_{ij} = -\left[ \left( \nabla^2 \mathcal{L}\right)^{-1}\right]_{ij} = 2 \left[ \nabla^2 \left( \chi^2\right)\right]_{ij}^{-1} = -\left[H^{-1} \right]_{ij},\]
-where $H$ refers to the Hessian matrix and $\left[\sigma^2 \right]_{ij}$ is the covariance matrix $C$.
+where $\left[H^{-1} \right]_{ij}	$ refers to the Hessian matrix and $\left[\sigma^2 \right]_{ij}$ is the covariance matrix.
 The issue of identifiability is especially fraught for non-linear black-box type problems were it is difficult to explicitly evaluate the Hessian.
-The likelihood function, and thus the posterior probability density function, are defined completely by the optimal solution $\mathbf{x}$ and the second derivative of $\mathcal{L}$ at the maximum, which corresponds to the covariance matrix $C$.
+The likelihood function, and thus the posterior probability density function, are defined completely by the optimal solution $\mathbf{x}$ and the second derivative of $\mathcal{L}$ at the maximum, which corresponds to the covariance matrix.
 The standard errors, or marginal variances, are the square roots of the diagonal of the covariance matrix.
 The Hessian matrix must be negative definite for $\mathcal{L}$ to have a maximum at $\mathbf{x_0}$.
-We obtain an approximate Hessian using the approach suggested in Nelder's original paper by fitting quadratics to the simplex vertices and midpoints\cite{nelder_simplex_1965}\cite{spendley_sequential_1962}.
-We use the condition number
-\[ \mbox{cond} (H) = \frac{\mbox{max}[\mbox{eig}(H)]}{\mbox{min}[\mbox{eig}(H)]} \]
+We obtain an approximate Hessian using the approach suggested in Nelder's original paper by fitting quadratics to the simplex vertices and midpoints in the vicinity of the optima \cite{nelder_simplex_1965, spendley_sequential_1962}.
+Thus armed with the Hessian we may use the condition number
+\[ \mbox{cond} (H) = \frac{\mbox{max}[\mbox{eig}(H)]}{\mbox{min}[\mbox{eig}(H)]}, \]
 to make a qualitative assesment of the stability of the problem.
-We find typical condition numbers $\sim \mathcal{O}(10^{27})$.
+Among our parameter estimate MLE optima we find large typical condition numbers $\sim \mathcal{O}(10^{27})$.
 In fact, in many cases our Hessian is not negative definite, or invertible at the minmia $\mathbf{x}_0$, which implies negative values of the variances, which are impossible.
@@
 Posteriori verification of the results is crucial to bound the identifiability of the parameter estimation problem, but this remains as future work.
-Several sources suggest senstivity analysis of the parameter estimates by generation of synthetic Monte Carlo data sets as a means of establishing identifiability\cite{bevington_data_1969}\cite{jaqaman_linking_2006}.
+Several sources suggest senstivity analysis of the parameter estimates by generation of synthetic Monte Carlo data sets as a means of establishing identifiability\cite{bevington_data_1969, jaqaman_linking_2006}.
 
@@
 \begin{itemize}
-\item  In drop tower experiments we vary the independent variables $V_d$ and $\sigma$ and capture the trajectories of the droplets using high-speed video. 
+\item  In drop tower experiments we vary the independent variables $V_d$ and $\sigma$ and capture the trajectories of the drops using high-speed video. 
 \item We produce superhydrophobic electret substrates with surface potentials 0.7-4.0 $kV$ and contact angles $\sim 150^{\circ}$ with approximately $25^{\circ}$ contact angle hysteresis when uncharged.
@@
 \item We solve the inverse problem to identify key parameters which we cannot measure directly in the drop tower experiments.
-This is accomplished by Maximum Likelihood Estimation using constrained direct search optimization.
+This is accomplished by Maximum Likelihood Estimation using a constrained direct search optimization.
 \item We fail to establish the identifiability of the parameter estimate using the conventional approach of inverting the Hessian near the optima.
@@
 \section{Parameter Estimates}
-We found the distribution of mostly likely experimental net charges for a population of the drops jumped in low-gravity.
-A covariance plot of the model variables is shown in Figure \ref{fig:scatter}.
-The multicollinear dependence of charge on drop surface area, $A$, and the characteristic electric field, $E_0$, is evident.
-Assuming the main effect is the interaction between charge and electric field, a Robust Least Squares model fit $q \sim kAE_0$ (using the Python \verb|statsmodels.formula.api.RLM| function), with the non-linear transformation $A = V_d^{2/3}$, found that $k=5.01 \times 10^{-11} \pm  2.85 \times 10^{-11}$ with $R^2 = 0.946$.
+We determined the distribution of most probable experimental model variables vlaues for a population of the drops jumped in drop tower tests, shown in Figure \ref{fig:scatter}.
+The dependence of charge on drop surface area $A$ is immediately evident.
+The effect of electric field on drop charge is less obvious in the data.
+This co-linearity is likely the source of the ill-conditioning issues in the parameter estimation process.
+However, assuming the main effect is the interaction between charge and electric field, a Robust Least Squares model fit $q \sim kAE_0$ using the Python \verb|statsmodels.formula.api.RLM()| function with the non-linear transformation $A = V_d^{2/3}$, finds that $k=5.01 \times 10^{-11} \pm  2.85 \times 10^{-11}$ F/m with $R^2 = 0.946$.
 This model uses Huber's T norm, median absolute scaling, and H1 covariance estimation.
@@
     \resizebox{12cm}{!}{\input{../figures/scatter.pgf}}
-    \caption{Covariance plot of main parameters $E_0$, $U_0$, droplet area ($V_d^{2/3})$, and $q$.\label{fig:scatter}}
+    \caption{Covariance plot of main parameters $E_0$, $U_0$, drop area ($V_d^{2/3})$, and $q$.\label{fig:scatter}}
 \end{figure}
@@
     \input{../figures/charge.pgf}
-    \caption{Charge $q$, as a function of $V_d$, $\varphi_s$.\label{fig:charge}}
-\end{figure}
-
-A two-ways T-test comparison of charge distributions between the drop bounce experiment and a corollary experiment with zero electric field at the time of drop deposition on the superhydrophobic surface suggests that the drop charge is induced by the electric field, rather than through contact charging on the PTFE layer ($t = 5.11, p = 0.0002$).
-The T-test informs us that the charge distribution  are about 5 times more different from each other as they are within each other, and there is a 0.02$\%$ probability that this result happened by chance.
+    \caption{Charge $q$, as a function of the measured variables $V_d$, $\varphi_s$.\label{fig:charge}}
+\end{figure}
+
+A two-way T-test comparison of charge distributions between the drop bounce experiment and a corollary experiment with zero electric field at the time of drop deposition on the superhydrophobic surface suggests that the drop charge is primarily induced by the electric field, rather than through contact charging on the PTFE layer ($t = 5.11$, $p = 0.0002$).
+The T-test informs us that the charge distributions are about 5 times more different from each other as they are within each other, and there is a 0.02$\%$ probability that this result occurred by chance.
 This corollary experiment is documented in Appendix \ref{sec.drop_charge}.
 
-The model $q \sim kAE_0$ is incidentally very similar to the classical solution for the surface charge density of a half-spherical conductor with a field-induced dipole\cite{david_j._griffiths_introduction_1999}
-\begin{eqnarray*}
-q &=& 3 \epsilon_0 E_0 \int_A \cos \theta dA \\
-&=& 3 \pi^{1/3} 6 \left(6 V_d \right)^{2/3} \epsilon_0 E_0 \int^{4 \pi/2}_{\pi / 2} \cos \theta d\theta \\
-&=& k E_0 V_d^{2/3}
-\end{eqnarray*}
-with $k \approx 1.3 \times 10^{-10}$.
-This is also of a similar form to the charge found by Takamatsu and coauthors for drops falling from a grounded nozzle in an external electric field\cite{takamatsu_theoretical_1981}
+The model $q \sim kAE_0$ is similar to the classical solution for the surface charge of a half-spherical conductor with a field-induced dipole\cite{david_j._griffiths_introduction_1999}
+\begin{eqnarray}
+q &=& 3 \epsilon_0 E_0 \int_A \cos \theta dA \nonumber \\
+&=& 3 \pi^{1/3} 6 \left(6 V_d \right)^{2/3} \epsilon_0 E_0 \int^{4 \pi/2}_{\pi / 2} \cos \theta d\theta \nonumber \\
+&=& k E_0 V_d^{2/3} \label{dipole}
+\end{eqnarray}
+with $k \approx 1.3 \times 10^{-10}$ F/m.
+This is also of similar form to the charge found by Takamatsu and coauthors for drops falling from a grounded nozzle in an external electric field\cite{takamatsu_theoretical_1981}
 \[q = 4 \pi \epsilon_0 \beta E_0 R_d^2 \]
-with $\beta \approx 2.63$.
-
-\section{Scale Quantities}
-The dielectrophoretic force plays a very small role when drops have net charge in a DC field; the condition to neglect the DEP force was satisfied for all experiments in the dataset.
-Dimensional drop apoapses scale closely with $\mathbb{E}\mbox{u}$ as seen in Figure \ref{fig:series_s_eu}.
-The relative magnitudes of the simulated forces felt by the drops is shown in Figure \ref{fig:forces}.
-Forces acting on the drops vary in magnitude between $\mathcal{O}(10^{-6})$-$\mathcal{O}(10^{-4})$ N.
-We see that, of the drops in the experimental dataset only the two with the largest $\mathbb{E}\mbox{u}$, $\mathbb{E}\mbox{u} \sim \mathcal{O}(1)$ could appropriately be said to be in the inertial electro-viscous regime.
-In all other cases image forces are much stronger than drag.
-For these drops $\mathbb{E}\mbox{u} \gg 1/8 \pi$, and are likely on escape trajectories.
-The image forces themselves rapidly become small compared to Coulomb forces for drops with apoapses $\mbox{max}\left( y\right) \gtrapprox L$, thus it is reasonable to claim that for intermediate drops Coulomb force scales as inertia, and we can neglect the effects of drag and image forces.
-
+with $\beta \approx 2.63$. Cast in the same form as Equation \ref{dipole} $k \approx 4 \pi \epsilon_0 \beta (4 \pi/3)^{-2/3} \approx 1.1 \times 10^{-10}$ F/m.
+
+The effect of volume on jump velocity $U_0$ is not immediately evident in the data, despite previous work having establishing this relationship\cite{attari_puddle_2016}.
+This likely results from large variance in $U_0$ due to contact line hysteresis during the drop roll-up.
+Contact line losses predominates in the sub 1 mL volume drops which are primarily the object of this study.
+
+\section{Model Validation}
+Dimensional drop apoapses, shown in Figure \ref{fig:series_s_eu}, scale closely with $\mathbb{E}\mbox{u}$ as expected according to our earlier analysis.
+Electrostatic Euler numbers in the data set vary between $1.4 \lessapprox \mathbb{E}\mbox{u} \lessapprox 35.4$.
+The dielectrophoretic force plays a small role when drops have net charge in a DC field.
+The condition to neglect the DEP force was satisfied for all experiments in the dataset with typical values of the condition number $\kappa_2 \epsilon_0 K R_d^2 E_0/q \approx \mathcal{O}(10^{-6})$.
+In the non-dimensional trajectories with short-time scaling shown in Figure \ref{fig:series_s_ds}, we see that the trajectory apoapses are consistently $\mathcal{O}(1)$, but most trajectories overshoot their characteristic time scale (which predicts returns at $t^*  =2$ to the zeroth order).
+This should be read as a success of the scaling.
+However the fact that $\mathbb{E}\mbox{u} \sim \mathcal{O}(1)$ in the regime (in other words, it is not a small parameter), does imperil the validity of the Equation \ref{perturb_image} asymptotic result for short times.
 \begin{figure}[!htb]
@@
 \end{figure}
-\begin{figure}[!htb]
-    \centering
-    \resizebox{14cm}{!}{\input{../figures/forces_all.pgf}}
-    \caption{Simulated forces acting on the drop. Experiments are shown by order of increasing apoapse.\label{fig:forces}}
-\end{figure}
-
-In the non-dimensional trajectories with short-time scaling shown in Figure \ref{fig:series_s_ds}, we see that the trajectory apoapses are consistently $\mathcal{O}(1)$, but most trajectories overshoot their characteristic time scale (which predicts returns at $\bar{t}  =2$ to the first order).
-We also observe that that $\mathbb{E}\mbox{u}$ is not typically a small number in this regime, imperiling our use of asymptotic estimates in this regime.
-We can perhaps gain some insight by comparing the asymptotic estimate for return times to the scaled experimental return times.
-We see in Figure \ref{fig:times} that the long-time scaled non-dimensional time of first bounce in the experiment $t_b / t_c$, compares poorly to the asymptotic estimate for returns $t_f$ in the limit of small $\mathbb{E}\mbox{u}_+$, this is due to the use on long-time scaling for drops with $y/L \ll 1$.
-\begin{figure}[h]
+\begin{figure}[htb]
     \centering
@@
 \end{figure}
-
-\begin{figure}[h]
+The covariance of $\mathbb{I}\mbox{g}$ with $\mathbb{E}\mbox{u}$ is shown in Figure \ref{fig:dnumbs}.
+Predictably, there is quite strong correlation between the dimensionless groups.
+We also see that $\mathbb{I}\mbox{g} < 1$ for all drops.
+Using an OLS regression, we find the model $\mathbb{I}\mbox{g} \sim (0.012 \pm 0.003) \mathbb{E}\mbox{u} + (0.212 \pm 0.036) $ with $R^2 =0.59$.
+\begin{figure}[htb]
+    \centering
+    \input{../figures/dnumbs.pgf}
+    \caption{Experimental covariance of $\mathbb{E}\mbox{u}$ and $\mathbb{I}\mbox{g}$.\label{fig:dnumbs}}
+\end{figure}
+The predictions of the long-time scaled time-of-flight theory \ref{time_of_flight} $t_c t_f$ compare favorably to the experimental time-of-flight $t_b$, shown in dimensional form in Figure \ref{fig:series_s_ds}.
+This allows an improvement to be made to the asymptotic result \ref{time_of_flight} by multiplying the series by the empirical coefficient $a = 1/0.68 = 1.47$.
+The semi-analytic time-of-flight is then given by
+\begin{equation}
+\label{time_improved}
+t^* = 2.94 + 1.96B\mathbb{E}\mbox{u} + 1.18B^2\mathbb{E}\mbox{u}^{2} + \mathcal{O}(B^3\mathbb{E}\mbox{u}^{3}).
+\end{equation}
+\begin{figure}[htb]
     \centering
     \input{../figures/times2.pdf_tex}
-    \caption{Dimensional time of flight asymptotic estimates $t_f$ comapred with experimental bounce times.\label{fig:series_s_ds}}
-\end{figure}
-
-The covariance of $\mathbb{I}\mbox{m}$ with $\mathbb{E}\mbox{u}$ is shown in Figure \ref{fig:dnumbs}.
-Predictably, there is quite strong correlation between the dimensionless groups.
-We also see that $\mathbb{I}\mbox{m} < 1$ for all drops.
-Using an OLS regression, we find the model $\mathbb{I}\mbox{m} \sim (0.012 \pm 0.003) \mathbb{E}\mbox{u} + (0.212 \pm 0.036) $ with $R^2 =0.59$.
-\begin{figure}[h]
-    \centering
-    \input{../figures/dnumbs.pgf}
-    \caption{Experimental covariance between $\mathbb{E}\mbox{u}$ and $\mathbb{I}\mbox{m}$.\label{fig:dnumbs}}
-\end{figure}
-
-We should note that there are several kinds of systematic error that influence our data.
-We assume that drop translate purely along the central axis of the electric field, but in practice, despite the improvement in surface charge density uniformity produced by corona charging, there are still local areas of especially high charge density.
-In principle, this kind of error should become small for drops which are far enough away from the charge distribution, that the geometry of the charge distribution disappears, and the electric field looks like that due to a point charge.
-Another form of error is in the initial velocity as it appears in $\mathbb{E}\mbox{u}$.
-Because we usually lose the first few frames of video due to camera shake transients at the start of the low-gravity experiment, we will consistently underestimate $U_0$ because the drop will already have decelerated significantly during that period of time.
+    \caption{Dimensional time-of-flight asymptotic estimates $t_f$ compared with experimental time-of-flight $t_b$.\label{fig:series_s_ds}}
+\end{figure}
+
+The relative magnitudes of the simulated forces felt by the entire population of drops are shown in Figure \ref{fig:forces}.
+Coulomb, image, and drag forces acting on the drops vary in typical magnitude between $\mathcal{O}(10^{-6})$-$\mathcal{O}(10^{-4})$ N.
+We see that of the drops in the experimental dataset only the two with the largest $\mathbb{E}\mbox{u} \sim \mathcal{O}(10)$ could appropriately be said to be in the inertial electro-viscous regime.
+In all other cases image forces are much stronger than drag.
+The image forces themselves rapidly become small compared to Coulomb forces for drops with apoapses $\mbox{max}\left( y\right) \gtrapprox L$.
+Thus, it is reasonable to claim that for intermediate drops Coulomb force scales as inertia, and drag and image forces are small.
+The drop with largest $\mathbb{E}\mbox{u}$ in our dataset failed to escape the electric field as the escape condition $B \mathbb{E}\mbox{u} / 8\pi = 0.2 < 1$ was unsatisfied.
+For this drop Equation \ref{time_improved} predicts that the drop will return to the substrate after 32 s, a period of free-fall which is lamentably well out of reach of a drop tower.
+However, such an experiment could possibly be performed aboard the ISS or in a parabolic flight.
+\begin{figure}[!htb]
+    \centering
+    \resizebox{14cm}{!}{\input{../figures/forces_all.pgf}}
+    \caption{Simulated forces acting on the drop up to the first apoapse.\label{fig:forces}}
+\end{figure}
+
+We should note the influence of systematic error on our data.
+We assume that drops translate purely along the central axis of the electric field, but in practice, despite the improvement in surface charge density uniformity produced by corona charging, there are still local areas of especially high charge density, causing radial translation and changing $E$ not as well predicted by Equation \ref{e_field}.
+In principle, this kind of error should become small for drops which are far enough away from the charge distribution that the geometry of the charge distribution disappears and the electric field looks like that due to a point charge.
+However for low $\mathbb{E}\mbox{u}$ drops this error relatively increases.
 The primary sources of random error are the effect of contact line hysteresis on the drop initial velocity, and of the variance in the MLE parameter estimates.
 
-\section{Impact Dynamics}
-\hl{Check the Oh numbers}.
-Very little work to date on drop impacts outside of two regimes: first, very low $\mathbb{R}\mbox{e}$ viscous drop spreading driven by capillary forces at the contact line, and second, impacts at ``high'' $\mathbb{W}\mbox{e}$.
-There has been some computational work with impacts at $\mathbb{R}\mbox{e}=1.4$ (Fukai \emph{et al.}), but the results are suspect as the model neglects uncompensated Young's force at the contact line (which is the dominant spreading force for low $\mathbb{R}\mbox{e}$ impacts).
-Of course models for dynamic contact lines in general remain controversial, even for ordinary spreading of liquids, despite decades of work in the area.
-
-Naively neglecting dimensionless groups governing the dynamic contact line, the pertinent dimensionless groups for isothermal droplet impacts are the Weber number $\mathbb{W}\mbox{e} = \frac{\rho U^2 R_d}{\sigma}$, which is a ratio of droplet inertia to surface tension, the Ohnesorge number, $\mathbb{O}\mbox{h} = \frac{\mu}{\sqrt{\rho \sigma R_d}}$, which is a ratio of viscous to inertial and surface tension forces, and the Bond number, $\mathbb{B}\mbox{o}$, defined previously.
-The dynamics of spreading are characterized primarily by $\mathbb{W}\mbox{e}$ and $\mathbb{O}\mbox{h}$.
-Additionally the final stages of spreading depend strongly on $\theta_e$, which is the static contact angle.
-The Weber number scales the \emph{driving force} of the impact.
-In the more familiar case of high $\mathbb{W}\mbox{e}$ the drop liquid bulk is driven radially outward by the impact induced pressure gradient, whereas in the case of small $\mathbb{W}\mbox{e}$ the liquid is pulled outwards by capillary force (e.g.
-uncompensated Young's force) at the contact line.
-The Ohnesorge number, by contrast, scales the force that \emph{resists} spreading.
+\section{Suggestions for Future Directions}
+In 1-$g_0$, for Weber numbers $>$ 0.4, impact rebound behavior on a super-hydrophobic surface is normally dominated by damping from contact line hysteresis.
+However, for the low Bond and Ohnesorge numbers occurring in free-fall, the drop impact dynamics additionally include electrohydrodynamic surface wettability effects.
+To date there has been very little work done generally on drop impacts outside of two regimes: first, very low $\mathbb{R}\mbox{e}$ viscous drop spreading driven by capillary forces at the contact line, and second, impacts at `high' Weber numbers $\mathbb{W}\mbox{e} = \frac{\rho U^2 R_d}{\gamma}$, which is a ratio of drop inertia to surface tension.
+Of course even models for dynamic contact lines themselves in general remain controversial, even for ordinary spreading of liquids, despite decades of work in the area.
+
+If we naively neglect the dynamics of the contact line, the pertinent dimensionless groups for isothermal drop impacts are the Weber number $\mathbb{W}\mbox{e}$, the Ohnesorge number $\mathbb{O}\mbox{h} = \frac{\mu}{\sqrt{\rho \gamma R_d}}$, which is a ratio of viscous to inertial and surface tension forces, and the Bond number $\mathbb{B}\mbox{o}$ defined previously.
+In this case dynamics of spreading are characterized primarily by $\mathbb{W}\mbox{e}$ and $\mathbb{O}\mbox{h}$.
+The Weber number scales the driving force of the impact.
+In the more familiar case of high $\mathbb{W}\mbox{e}$ impacts the drop liquid bulk is driven radially outward by the impact induced pressure gradient, whereas in the case of small $\mathbb{W}\mbox{e}$ the liquid is forced outwards by capillary force at the contact line.
+The Ohnesorge number, by contrast, scales the force that resists spreading.
 For large $\mathbb{O}\mbox{h}$ the resistive force is viscous, whereas for low $\mathbb{O}\mbox{h}$ the force is inertia.
+Previous experimental work on low $\mathbb{O}\mbox{h}$, low $\mathbb{W}\mbox{e}$ impacts includes Schiaffino and Sonin's work\cite{schiaffino_molten_1997} on impacts of molten drops on cold surfaces.
+Mol\'{a}\u{c}ek and Bush\cite{molacek_quasi-static_2012}, Gopinath and Koch\cite{gopinath_collision_2002}, and Okamura\cite{okumura_water_2003} have developed simple analytical models of drop impacts at low $\mathbb{W}\mbox{e}$ and low $\mathbb{B}\mbox{o}$.
+All of these works show increasing dimensionless contact time $\tau$ as Weber number decreases, in opposition to the results of Richard and Qu\'{e}r\'{e} \cite{richard_surface_2002} which show experimentally that the contact time is approximately a constant $\tau \approx 2.6(\rho R^3_d/\sigma)^{1/2}$ at large $\mathbb{W}\mbox{e}$.
+Mol\'{a}\u{c}ek's work also shows that impact coefficients of restitution $C_R$ depend non-linearly on $\mathbb{B}\mbox{o}$.
+To date little experimental work has been done on low $\mathbb{B}\mbox{o}$ impacts as well.
+An exception is provided by Duvivier \emph{et al.}\cite{duvivier_drop_2012} who studied regimes of aqueous ferrofluid drop impacts on superhydrophobic substrates under the influence of an external magnetic field.
 
@@
 Notably we observe underdamped oscillations of drop interfaces during impact.
-according to (Schiaffino, 1997) viscous forces play a role in the final (which?
-describe) stage of spreading even for drop impact at very low $\mathbb{O}\mbox{h}$.
-In the regime of intermediate viscosity, following spreading the oscillations of the interface are damped with a characteristic time that is generally longer than the spreading time (again, given by $t_c \sim \left( \sigma / \rho R_d^3 \right)^{1/2}$).
-The celebrated Hoffman-Tanner-Voinov law, which relates the contact line velocity $U_c$ of an isothermal spreading process to the static contact angle $\theta_e$ to the dynamic advancing contact angle $\theta_a$ by
+Access to such relatively low $\mathbb{O}\mbox{h}$, low $\mathbb{W}\mbox{e}$ drop impacts enabled by the low-gravity environment is an interesting possibility for new work on the basic science of drop impacts.
+There is also the intersection of this work with the burgeoning field of electrowetting on patterned surfaces and the interaction with drop impacts.
+Various authors\cite{bartolo_bouncing_2006, reyssat_bouncing_2006} have suggested that a wetting transition called the Fakir impalement occurs during impacts on patterned hydrophobic surfaces which depends on a critical pressure $p_c \sim \gamma h/l$ where $h/l$ is the pillar aspect ratio of the patterned surface.
+This pressure can result from fluid inertia in a high $\mathbb{W}\mbox{e}$ impact regime, or can result from an electrostatic pressure due to an external electric field, which is responsible for the irreversiblity that notoriously plagues static EWOD experiments.
+Thus, there is hope that electric fields can be leveraged to engineer solid-state surfaces which are tuneably wetting under drop impacts.
+This could motivate additional work in this area.
+
+Our preliminary results showing the influence of $\mathbb{W}\mbox{e}$ and electrostatic Bond number $\mathbb{B}\mbox{o}_e = \frac{\epsilon E_0^2 R_d}{\gamma} $ on drop impact dimensionless contact time $\tau$ and coefficient of restitution $C_R$ at $\mathbb{O}\mbox{h} \approx 2.2$ are shown in Figures \ref{fig:contact} and \ref{fig:E0}.
+
+\begin{figure}[htb]
+    \centering
+    \input{../figures/contact.pgf}
+    \caption{Dimensionless contact time $t_b/\tau$ compared with impact $\mathbb{W}\mbox{e}$ and $\mathbb{B}\mbox{o}_e$.\label{fig:contact}}
+\end{figure}
+
+\begin{figure}[htb]
+    \centering
+    \input{../figures/restitution.pgf}
+    \caption{Impact coefficient of restitution compared with impact $\mathbb{W}\mbox{e}$ and $\mathbb{B}\mbox{o}_e$.\label{fig:restitution}}
+\end{figure}
+
+\section{Conclusion}
+This work might have stopped quite early had we maintained our focus on spontaneous drop jump, and the key result would simply have been a means of mitigation for this troublesome electro-bounce phenomenon.
+In some sense this is quite easy to do as there are a plethora of commercially available static charge neutralization tools aimed at ESD control applications.
+In a low-gravity setting, if we wish to rid ourselves of these electrostatic phenomenon we need simply to neutralize dielectric surfaces in the vicinity of our controlled environment.
+Of course there are limitations to this approach.
+For instance, if the work involves surface chemistry on the surface requiring neutralization, depositing a layer of ions will possibly change experimental results.
+Additionally, there are cases where we do not control the environment for practical reasons.
+For example, aboard the ISS crew clothing can easily become electrostatically charged, just as clothing does on Earth, and if this  charge distribution is in the vicinity of Rayleigh-Plateau breakup of a fluid, as might happen when squirting water from a drink bag, then electrophoresis of the drops will occur after the fashion of this work.
+
+Our experimental results have shown that the simple 1-dimensional model is reasonably accurate at predicting trajectories of charged drops.
+We conclude this thesis by turning the theory to a simple space systems application in a worked example.
+Let us say we desire to capture drops in a pre-stage to the compressor of a Rankine cycle space nuclear power system.
+We must actively capture the drops because we require a single-phase saturated vapor at the compressor inlet do not wish to superheat or interrupt the flow.
+The drops are polydisperse and thus have a distribution of masses $m$ and velocities $U_0$.
+The working fluid is a mixture of lithium and cesium with $\rho_l = 452$ kg/m$^3$.
+The lithium droplets have high surface tension even at high temperatures encountered in this power cycle, and an insulated electrode can possibly be made hydrophobic by means of a high temperature coating such that the drops rebound rigidly without wetting the surface of the precipitator.
+The lithium drops can also be treated as ideal conductors, and we assume the droplet velocity vector is normal to the precipitator electrode as in our work.
+The simple 1-dimensional theory of this thesis assumes the electric field due to a square charged dielectric, but other electric fields, and electrode geometries are possible or desirable for the designer.
+The scaling used in this work will oftentimes remain valid as electric fields for numerous geometries contain the same near-field constant and far-field $1/y^2$ limits.
+In other cases, especially with more complicated geometries, the electric field will need to be determined analytically or numerically.
+From the form of the electrostatic Euler number
 \[
-\frac{\mu U_c}{\sigma} \approx \kappa \left( \theta_a^3 - \theta_e^3 \right),
-\]
-where $\kappa \approx 0.013$ is an empirical coefficient extracted from Hoffman's data.
-The Hoffman-Tanner-Voinov law implies that the transition between low $\mathbb{W}\mbox{e}$ inviscid and viscous regimes occurs at $\mathbb{O}\mbox{h} \sim \mathcal{O}(10^{-2})$ rather than $\mathbb{O}\mbox{h} \sim \mathcal{O}(1)$ given by a naive scaling.
-
-In 1-$g_0$, for Weber numbers $>$ 0.4, impact recoil behavior on a super-hydrophobic surface is normally dominated by damping from contact line hysteresis.
-However, for the low Bond and Ohnesorge numbers occurring in free-fall, the droplet impact dynamics additionally include electrohydrodynamic surface wettability effects.
-This is qualitatively discussed in terms of trends in coefficients of restitution and dimensionless contact time.
-
-Some notes:
-\begin{itemize}
-\item{\textbf{Schiaffino, 1997}} 
-\end{itemize}
-
-\section{Conclusions}
--conclusions.
--future directions.
+\mathbb{E}\mbox{u} = \frac{m U_0^2}{q E_0 R_d},
+\]
+we note that this dimensionless group can also be thought of as a ratio of energies: the kinetic energy $m U_0^2$ in the numerator, and the electrostatic potential energy $q E_0 R_d$ in the denominator.
+We also note that although the velocity $U = U(t,y)$ and electric field $E = E(t,y)$ are variables, if the system is conservative system this ratio of energies is constant.
+If an engineering requirement is to capture 95\% the drops entering the compressor to mitigate damage to the turbine blades, then we can perform an initial sizing of an electrostatic drop precipitator using the scaling approach of this thesis.
+Let us say that two standard deviations of the drop population posses kinetic energy less than $8 \times 10^{-3}$ J per drop, and that the design constraints for the electrode are such that $E_0=3$ kV/m, and the electrode is 10 cm square.
+To satisfy Equation \ref{escape} requires
+\[
+2\rho E_0 L^2 \frac{q}{m} > mU_0^2.
+\] 
+From the above we find that to capture these drops a charge-to-mass ratio $q/m=3 \times 10^{-7}$ C/kg is required.
+This is one order of magnitude less than the charge-to-mass ratios observed in this work, and can be achieved by a shielded charging electrode near an orifice in a way similar to an inkjet printer, or alternately by discharge, electron beam, or ionizing radiation emission.
+Though this example is highly contrived and departs far from the experiment reported here the results remain applicable because of the fundamental similarity in the underlying physics.
 
@@
 Whether this free charge arises due to contact charge or field-induction To measure this charge concurrent methodologies were used.
-We determined the drop free charge by observation of the deflection of the drops in the region of a known uniform field in a fashion inspired by Millikan's famous experiment to determine the fundamental charge of the electron.
-
-Drops were jumped in free-fall from a superhydrophobic surface placed between the plates of a parallel plate capacitor of known uniform electric field.
-The surface was charge neutralized.
+In a corollary set of experiments we determine the drop free charge by observation of the deflection of the drops in the region of a known uniform field in a fashion inspired by Millikan's famous experiment to determine the fundamental charge of the electron.
+
+Drops are jumped in free-fall from a superhydrophobic substrate placed between the plates of a parallel plate capacitor of known uniform electric field.
+The surface charge of the substrate is neutralized using the Ptec IN5120 ion source.
 Since the drop initial velocity $U_0$ is parallel to the electric field, the drops are inertial in the direction of the electric force, and neglecting the effect of image charges mirrored across the conductors, we can determine the magnitude of the drop charge by a balance of Coulombic force and inertia given by the equation of motion
@@
 
-Since the drag is negligible in the inertial limit we can find the charge $q$ by fitting a second-order least squares polynomial to the measured drop positions, equating the $t^2$ term to the constant acceleration, and dividing by the known, constant magnitude of the electric field.
-
-A 200-880 VAC source with a full wave bridge rectifier circuit was prototyped on perf-board for initial experiments to measure drop charge.
-The circuit was analyzed on an laboratory oscilloscope to verify that the AC component of the signal was appropriately small (13 mV at 35 kHz).
-Current was determined to be a relatively low 80 $\mu$A.
-The high-voltage source terminals were led to two parallel polished 150x150 mm aluminum plate electrodes.
-The electrodes were mounted on an insulated 80/20 extruded aluminum rail for ease of adjustment.
-All drop charge experiments were conducted with an electrode spacing of 28.30 mm.
-With this spacing the calibrated electric field between the plates was $\mathbf{E} \approx 35$kV/m.
-The electrodes were electrically isolated from the drop rig by two alternating layers of 4 mm thick PMMA sheet and Kapton tape.
-Potential across the plates was measured periodically with a load-impedance corrected multimeter to account for battery depletion.
-The typical capacitor rise time of the plates was measured to be 1.4 s, thus to make the most economical use of the brief window a low-gravity a weighted switch was set by hand prior to the drop to close the high-voltage circuit, but which passively safed the system at the resumption of 1-$g_0$ conditions in the tower.
-From a survey of literature we suppose the drop charge, if they are indeed charged by contact with PTFE, to be some function of the drop volume and the residence time on the superhydrophobic surface.
+Since the drag is negligible in the inertial limit we can find the charge $q$ by fitting a second-order least squares polynomial to the measured drop positions.
+We equate the $t^2$ term to the constant acceleration and divide by the known constant magnitude of the electric field.
+
+A 200-880 VAC source with a full wave bridge rectifier circuit is used in the experiment to measure drop charge.
+measurements show that the high-voltage source circuit AC component of the signal is appropriately small (13 mV at 35 kHz).
+The no-load current is determined to be a relatively low 80 $\mu$A.
+The high-voltage source terminals are led to two parallel polished 150x150 mm aluminum plate electrodes.
+The electrodes are mounted on an insulated 80/20 extruded aluminum rail for ease of adjustment.
+All drop charge experiments are conducted with an electrode spacing of 28.30 mm.
+With this spacing the calibrated electric field between the plates is $\mathbf{E} \approx 35$kV/m.
+The electrodes are electrically isolated from the drop rig by two alternating layers of 4 mm thick PMMA sheet and Kapton tape.
+Potential across the plates is measured periodically with a load-impedance corrected multimeter to account for battery depletion.
+The typical capacitor rise time of the plates is measured to be 1.4 s, thus to make the most economical use of the brief window a low-gravity a weighted spring-loaded switch is set by hand prior to the drop to close the high-voltage circuit, but which passively safes the system at the resumption of 1-$g_0$ conditions in the tower.
+From a survey of literature we suppose the drop free charge, if it is indeed arises by contact with PTFE, to be some function of the drop volume and the residence time on the superhydrophobic surface.
 However, sweeping though drop volumes over a series of drop tower experiments we find little correlation between drop volume  and free drop charge.
@@
 The overall model F-statistics (2.177 in 2 and 13 degrees of freedom), and coefficients of determination ($r^2 = 0.2509$) indicate that the linear model neither fits the data particularly well, nor does it offer an improvement over the mean model.
-The mean charge was determined to be positive $2.3 \cdot 10^{-11}$ C, with a standard deviation of $1.8 \cdot 10^{-11}$ C.
-
+The mean charge was determined to be positive $2.3 \times 10^{-11}$ C, with a standard deviation of $1.8 \times 10^{-11}$ C.
+
+\singlespacing
 \backmatter

### 2018-04-04 doc/manuscript/manuscript.tex
grammar fixes
improved a few figures, numerous small edits

@@
 \centering %\vspace*{-10ex}
-{\large \textsf{\textbf{Drop Electro-Bouncing in Low-Gravity}}}
+{\large \textsf{\textbf{Electro-Drop Bouncing in Low-Gravity}}}
 
@@
 This electric body force leads to a drop bouncing behavior similar to well-known phenomena in 1-$g_0$, though occurring for much larger drops ($\sim$ 0.5 mL).
-We show a simple model for the phenomenon, its scaling, and asymptotic estimates for drop time of flight in two regimes: firstly, in short-times close to the substrate when drop inertia balances Coulombic force due to net free charge and image charges in the dielectric substrate, and secondly, in long-times far from the substrate when drop inertia balances free charge Coulombic force and drag.
+We show a simple model for the phenomenon, its scaling, and asymptotic estimates for drop time of flight in two regimes: at short-times close to the substrate when drop inertia balances Coulombic force due to net free charge and image charges in the dielectric substrate and at long-times far from the substrate when drop inertia balances free charge Coulombic force and drag.
 The drop trajectories are controlled primarily by the dimensionless electrostatic Euler number $\mathbb{E}\mbox{u}$, which is a ratio of inertial to electrostatic forces.
-To experimentally determine values of $\mathbb{E}\mbox{u}$ we conduct a series of drop tower experiments where we observe the effect of drop volume, net free charge, and static surface potential of the superhydrophobic substrate on drop trajectories.
+To experimentally determine values of $\mathbb{E}\mbox{u}$ we conduct a series of drop tower experiments where we observe the effects of drop volume, net free charge, and static surface potential of the superhydrophobic substrate on drop trajectories.
 We use a direct search optimization to obtain a Maximum Likelihood Estimate for drop net charge, as we do not measure it directly in experiment.
-For $B \mathbb{E}\mbox{u} /8 \pi > 1$ drops escape the electric field, however we do not observe any escapes in our dataset.
-Finally, with an eye towards engineering applications we consider the results in light of the so-called low-gravity phase separation problem with a short space system design worked example problem.
+For $\phi \mathbb{E}\mbox{u} /8 \pi > 1$ drops escape the electric field, where $\phi$ is a drop to substrate aspect ratio.
+However, we do not observe any escapes in our dataset.
+With an eye towards engineering applications we consider the results in light of the so-called low-gravity phase separation problem with a worked example problem.
 
@@
 
-\doublespacing
+%\doublespacing
 \mainmatter
@@
 ``When the influence of gravity on fluid behavior is diminished or removed, other forces, otherwise of small significance, can assume paramount roles.''
-- NRC Report to NASA, 2003\cite{motil_priorities_2012}
+- NRC Report to NASA, 2003 \cite{motil_priorities_2012}
 \end{quote}
@@
 One example of these problems is the so-called ``phase separation'' problem of separating a gas phase from a multi-phase flow (or the reverse case), without the aid of buoyancy due to gravity.
-Sans buoyancy, otherwise mundane activities such as venting a gas or settling a liquid in a tank become problematic\cite{petrash_controlling_1964}.
-Trapped bubbles can vapor lock life-support, power, or propulsion systems\cite{jenson_passive_2014}.
-Issues of phase separation have so bedeviled human endeavors in space that an entire Apollo Saturn 1B mission (AS-203) was earmarked to study them\cite{hastings_saturn_1965}.
+Sans buoyancy, otherwise mundane activities such as venting a gas or settling a liquid in a tank become problematic \cite{petrash_controlling_1964}.
+Trapped bubbles can vapor lock life-support, power, or propulsion systems \cite{jenson_passive_2014}.
+Issues of phase separation have so bedeviled human endeavors in space that an entire Apollo Saturn 1B mission (AS-203) was earmarked to study them \cite{hastings_saturn_1965}.
 This problem has for some time motivated a quest for substitute body forces, and the present work follows in that well-worn tradition.
@@
 the equivalence of gravitational and inertial mass).
-In theoretical terms, a zero-g experiment performed in a drop tower on the surface of the Earth is equivalent to the same experiment performed in the nearly gravity-free deep space between galaxies, despite the fact that the drop tower itself is enveloped in a 1-$g_0$ gravity field, where $g_0=9.81$ m/s$^2$ is the standard gravitational acceleration at sea-level .
+In theoretical terms, a `zero-g' experiment performed in a drop tower on the surface of the Earth is equivalent to the same experiment performed in the nearly gravity-free deep space between galaxies, despite the fact that the drop tower itself is enveloped in a 1-$g_0$ gravity field, where $g_0=9.81$ m/s$^2$ is the standard gravitational acceleration at sea-level.
 At the orbital altitude of the International Space Station (ISS) the gravity level is still nearly 90\% of its value at sea-level on Earth, but the astronauts aboard ISS feel weightlessness because they are in a state of free-fall.
 In a practical sense true zero-g does not exit anywhere in the universe as there are always small, but nonetheless, measurable forces which can accelerate any massive body.
-For instance in low-Earth orbit, accelerations due to aerodynamic resistance in the tenuous outer atmosphere are on the order of $1 \times 10^{-6}$ $g_0$ (from hence comes the term ``microgravity'').
+For instance, in low-Earth orbit accelerations due to aerodynamic resistance in the tenuous outer atmosphere are on the order of $1 \times 10^{-6}$ $g_0$ (from hence comes the term ``microgravity'').
 This small drag acceleration provides some ersatz gravity, but there are also other forces present.
@@
 where $g$ is the acceleration, $R$ is the characteristic interfacial length scale, $\Delta \rho$ is the difference in densities across the interface (which simplifies to $\rho$, for large $\Delta \rho$, as in the case of a air-water interface), and where $\gamma$ is the surface tension.
-In cases where $\mathbb{B}\mbox{o}$ is small, a liquid is effectively in low-gravity regardless of the nominal local gravity level.
-Very small drops ($R < 1$ mm), for instance, are in low-gravity for all intents and purposes and have nearly spherical shapes.
+In cases where $\mathbb{B}\mbox{o}$ is small a liquid is effectively in low-gravity regardless of the nominal local gravity level.
+Very small water drops ($R < 1$ mm), for instance, are in low-gravity for all intents and purposes and have nearly spherical shapes.
 Contrarily, for cases of large $R$ in a space environment, such as with large diameter spacecraft propellant tanks then $ \mathbb{B}\mbox{o} \gg 1$ even though the acceleration remains small.
-This is actually a quite useful result, for on the basis of dimensional similarity, it is possible to accurately simulate low-gravity fluid mechanics (say of large propellant tanks), even in small drop towers simply by scaling dimensionless groups like the Bond number.
+This is actually a quite useful result, for on the basis of dimensional similarity it is possible to accurately simulate low-gravity fluid mechanics (say of large propellant tanks) even in small drop towers simply by scaling dimensionless groups like the Bond number.
 
 As with capillary forces, electrostatic forces have a multitude of applications as substitutes for gravity.
-Electrohydrodynamic (EHD) body forces have been suggested to combat thermal stratification of propellants under low-g conditions where bouyancy induced natural convection is very small\cite{blackmon_collection_1965}.
-In this case electro-convection is an analog of natural convection due to a fluid temperature dependent dielectric permitivity gradient (as opposed to a fluid density gradient), in the presence of a body force field: the electric field.
-The study also suggested applications in cryogenic tank vent screening, and in reducing heat transfer to cryogenic propellants (and thus boiloff losses) by dielectrophoretically positioning ullage vapors around the tank walls as a thermal barrier.
-EHD forces have been studied for enhancing boiling heat transfer by promotion of bubble detachment and prevention of dryout, again as an ersatz bouyancy\cite{snyder_dielectrophoresis_2001, di_marco_influence_2003, marco_use_2012}.
-EHD heat pipes, which substitute an electrode structure for the capillary wicking structure of a conventional thermocapillary heat pipe can evade the wicking limit\cite{jones_electrohydrodynamic_1973}.
+Electrohydrodynamic (EHD) body forces have been suggested to combat thermal stratification of propellants under low-g conditions where bouyancy induced natural convection is very small \cite{blackmon_collection_1965}.
+In this case electro-convection is an analog of natural convection due to a fluid temperature dependent dielectric permittivity gradient (as opposed to a fluid density gradient) in the presence of an electric body force field.
+The study also suggested applications in cryogenic tank vent screening and in reducing heat transfer to cryogenic propellants (and thus boiloff losses) by dielectrophoretically positioning ullage vapors around the tank walls as a thermal barrier.
+EHD forces have been studied for enhancing boiling heat transfer by promotion of bubble detachment and prevention of dryout, again as an ersatz bouyancy \cite{snyder_dielectrophoresis_2001, di_marco_influence_2003, marco_use_2012}.
+EHD heat pipes, which substitute an electrode structure for the capillary wicking structure of a conventional thermocapillary heat pipe can postpone the wicking limit \cite{jones_electrohydrodynamic_1973}.
 These are restricted to the use of insulating dielectric liquids, which usually have relatively low thermal conductivity, but are highly robust against dryout, support active flow control, and have low viscous losses.
-Dielectrophoretic settling of cryogenic propellants, in both total and partial communication Propellant Management Device (PMD) configurations, has been studied analytically in both static\cite{hurwitz_electrohydrodynamic_1966} and dynamic cases\cite{koval_dynamics_1967}, and in drop tower experiments\cite{fax_dielectrophoretic_1969}.
-EHD forces have also been applied to the low-g slosh baffling problem\cite{boretz_orbital_1970, petrash_use_1968, hurwitz_dielectrophoretic_1968}, and studied extensively for the mitigation of vapor pullthrough during tank draining, and concomittent minimization of propellant residuals at burnout, in a series of experiments at the NASA Lewis (now Glenn) Research Center 2.2 s drop tower facillity\cite{berenyi_dielectrophoretic_1970}.
+Dielectrophoretic settling of cryogenic propellants, in both total and partial communication Propellant Management Device (PMD) configurations, has been studied analytically in both static \cite{hurwitz_electrohydrodynamic_1966} and dynamic cases \cite{koval_dynamics_1967}, and in drop tower experiments \cite{fax_dielectrophoretic_1969}.
+EHD forces have also been applied to the low-g slosh baffling problem \cite{boretz_orbital_1970, petrash_use_1968, hurwitz_dielectrophoretic_1968}, and studied extensively for the mitigation of vapor pullthrough during tank draining and concomittent minimization of propellant residuals at burnout in a series of experiments at the NASA Lewis (now Glenn) Research Center 2.2 s drop tower facillity \cite{berenyi_dielectrophoretic_1970}.
 
 \section{Spontaneous Drop Jump}
-Low-gravity phase separation, droplet dynamics, and the dynamics and applications of the so-called spontaneous drop jump, is an active area of study at the Portland State University Dryden Drop Tower labratory (DDT).
-When a nonwetting, gravity dominated sessile drop (e.g.
+Low-gravity phase separation, drop dynamics, and the dynamics and applications of the so-called spontaneous drop or puddle jump, is an active area of study at the Portland State University Dryden Drop Tower labratory (DDT).
+When a nonwetting, gravity-dominated sessile drop (e.g.
 a puddle), which is initially at rest on a surface in the Cassie-Baxter state suddenly undergoes a large step reduction in $\mathbb{B}\mbox{o}$ it will spontaneously jump away from the surface.
-The Cassie-Baxter state, sometimes also known as the Fakir state, is a metastable heterogenously non-wetting state on a textured surface characterized by the existance of a vapor-layer which seperates roughness features of the surface from the bottom of the drop.
-The spontaneous drop jump was first observed experimentally in the Soviet Union by Kirko \emph{et al.}\cite{kirko_phenomenon_1970} in 1970 for drops of mercury in hydrochloric acid, and later by Wollman \emph{et al.} in 2016 for water drops in a set of experiments conducted using drop towers\cite{wollman_more_2016}.
+The Cassie-Baxter state, sometimes also known as the Fakir state, is a metastable heterogenously non-wetting state on a textured surface characterized by the existence of a vapor-layer that seperates roughness features of the surface from the bottom of the drop.
+The spontaneous drop jump was first observed experimentally in the Soviet Union by Kirko \emph{et al.} \cite{kirko_phenomenon_1970} in 1970 for drops of mercury in hydrochloric acid, and later by Wollman \emph{et al.} in 2016 for water drops in air in a set of experiments conducted using drop towers \cite{wollman_more_2016}.
 The kinetic energy of the jump is supplied by the defect in free surface energy as the new minimum energy surface equilibrium has approximately constant curvature.
@@
 \[KE_2 = SE_2 - SE_1 = [(\gamma A)_{gl} + (\gamma A)_{sg}]_2 - [(\gamma A)_{ls} + (\gamma A)_{gl} + (\gamma A)_{sg}]_1, \]
-
-where $KE$ and $SE$ are the kinetic and surface energies, $A$ is the surface area, the subscripts $_1$ and $_2$ denote the intial 1-$g_0$, and low-g states, and the subscripts ${gl}$, ${sg}$, and ${ls}$ denote the gas-liquid, solid-gas and liquid-solid interfaces repectively.
+where $KE$ and $SE$ are the respective kinetic and surface energies, $A$ is the surface area, the subscripts $1$ and $2$ denote the intial 1-$g_0$, and low-g states, and the subscripts ${gl}$, ${sg}$, and ${ls}$ denote the gas-liquid, solid-gas and liquid-solid interfaces repectively.
 The motive force is due to the inertia of internal flows which occur as the interface deflects under the suddenely lessened $\mathbb{B}\mbox{o}$.
-The characteristic time scale of the rolling up scales as $t_j \sim (\rho V_d/\sigma)^{1/2}$\cite{attari_puddle_2016}, which resembles the contact time, $\tau \approx 2.6(\rho R^3_d/\sigma)^{1/2}$ presented by Richard \emph{et al.} in 2002 for the related problem of drops impacting hydrophobic surfaces in 1-$g_0$\cite{richard_surface_2002}.
+The characteristic time scale of the rolling up scales as $t_j \sim (\rho V_d/\sigma)^{1/2}$ \cite{attari_puddle_2016}, which resembles the contact time, $\tau \approx 2.6(\rho R^3_d/\sigma)^{1/2}$ presented by Richard \emph{et al.} in 2002 for the related problem of drops impacting hydrophobic surfaces in 1-$g_0$ \cite{richard_surface_2002}.
 For drops with radial symmetry and sufficiently high initial $\mathbb{B}\mbox{o}$, inward radial capillary waves coalesce at the axis, leading to geysering and creation of satellite droplets by the Rayleigh-Plateau breakup of the geyser.
@@
 \includegraphics[width=0.75\textwidth]{drop_jump}
-\caption{The trajectory of a 0.2 mL spontaneous drop jump is captured in a composite image over a period $\sim 0.67$ s at 120 fps. \label{fig:nobounce}}
+\caption{The trajectory of a 0.2 mL spontaneous drop jump is captured in a composite image over a period $\sim 0.67$ s presented at $\approx 10$ Hz. \label{fig:nobounce}}
 \end{figure}
@@
 
-\section{Drop Electro-Bounce}
+\section{Electro-Drop Bounce}
 During the `rolling-up' of drops under ideal conditions, the spontaneous jump phenomenon is governed by a balance of inertia and surface tension forces, and once aloft the drop motion is nominally in a regime of pure drag.
@@
 The forces at work in such situations are presumably electrostatic in origin.
-Not without irony given our earlier discussion of underdeveloped low-gravity intuition, we note that though the drop electro-bounce was an accidental effect during our work on spontaneous drop jump, the phenomenon is interesting itself.
-This has motivated further study, and the drop `electro-bounce' phenomenon is the subject of this thesis.
+Not without irony given our earlier discussion of underdeveloped low-gravity intuition, we note that though the electro-drop bounce was an accidental effect during our work on spontaneous drop jump, the phenomenon is interesting itself.
+This has motivated further study, and the `electro-drop bounce' phenomenon is the subject of this thesis.
 A time-lapsed composite image showing an example of the phenomenon is shown in Figure \ref{fig:bounce}.
@@
 \item Observed maximum drop (de-)accelerations are on the order of $\sim$30 cm/s$^2$ for a range of drop volumes $0.03 \lessapprox V_d \lessapprox 0.5$ mL.
-\item The drops are attracted to regions of high electric field.
+\item The water drops are attracted to regions of high electric field.
 The horizontal (surface plane parallel) components of the drop trajectory usually oscillate about their initial position during the experiment (except in cases of nearly pure 1-D vertical translation).
-For especially small drops close to the spontaneous drop jump limit ($V_d \sim$ 0.01 mL) the drops do not jump, but translate across the surface in a rolling regime until either they reach a local maximum of the electric field, or until their motion is sufficiently damped by contact line hysteresis that pinning arrests their motion.
+For especially small drops close to the spontaneous drop jump limit ($V_d \sim$ 0.01 mL) the drops do not jump, but translate across the surface in a rolling regime until either they reach a local maximum of the electric field, or until their motion is sufficiently damped by contact line hysteresis where pinning ultimately arrests their motion.
 \item The drops appear to have net free charge. In cases of multiple simultaneous drop jumps the drops repel each other as they bounce or roll in orbital motion around regions of high field.
-\item The magnitude of the drop trajectory maxima (apoapses) appear to be related to the drop volume, which affects their mass, and initial jump velocity, and thence their inertia, and to the electric field strength.
+\item The magnitude of the drop trajectory maxima (apoapses) appear to be related to the drop volume (mass), and initial jump velocity (inertia), and to the electric field strength.
 \end{itemize}
 
-There are several possible origins of the electric charge which are ultimately responsible for this phenonenon.
-It is well known that water acquires positive free charge when in contact with certain polymers, especially polytetrafluoroethylene (PTFE)\cite{langmuir_surface_1938}, through a process called contact charging.
+There are several possible origins of the electric charge that are ultimately responsible for this phenonenon.
+It is well known that water acquires positive free charge when in contact with certain polymers, especially polytetrafluoroethylene (PTFE) \cite{langmuir_surface_1938}, through a process called contact charging.
 PTFE, on the other hand, tends to readily acquire negative charge by contact with water.
-The superhydrophobic surfaces used in the spontanous drop jump experiments have thin (nanometric) PTFE coatings, and we observe that it is extremely easy to produce significant surface potentials, $\varphi_s \sim$ 100-500 V, by simply flowing streams of distilled water over them.
-A study of this water on PTFE contact charging phenomenon was conducted by Yatsuzuka \emph{et al.}\cite{yatsuzuka_electrification_1994}, who suggest that this process results from formation of an electrical double layer driven by selective adsorption of ($\mbox{OH}^-$) ions at the polymer surface; other recent work strongly supports this hypothesis\cite{beattie_intrinsic_2006, strazdaite_water_2015}.
+The superhydrophobic surfaces used in the spontanous drop jump experiments have thin (nanometric) PTFE coatings, and we observe that it is extremely easy to produce significant surface potentials $\varphi_s \sim$ 100-500 V by simply flowing streams of distilled water over them.
+A study of this water on PTFE contact charging phenomenon was conducted by Yatsuzuka \emph{et al.} \cite{yatsuzuka_electrification_1994}, who suggest that this process results from formation of an electrical double layer driven by selective adsorption of ($\mbox{OH}^-$) ions at the polymer surface; other recent work strongly supports this hypothesis \cite{beattie_intrinsic_2006, strazdaite_water_2015}.
 Yatsuzuka \emph{et al.} also found that the specific charge on the drops in contact with the surface depends on their both surface velocity and conductivity.
 The contact charging mechanism is the most likely accidental source of charge on the suphydrophobic surfaces used in our work.
-Given the large roughness, or the ratio of projected to actual surface area, of the superhydrophobic surfaces used in the experiment, and given that the drops are initially in a Cassie-Baxter state, a somewhat electrically resistive air layer is maintained that reduces grounding of the drops despite the large potential difference between them and and the surface charges.
+Given the large roughness, or the ratio of projected to actual surface area, of the superhydrophobic surfaces used in the experiment, and given that the drops are initially in a Cassie-Baxter state, a somewhat electrically resistive air layer is maintained that reduces grounding of the drops despite the large potential difference between them and the surface charges.
 If this electrostatic potential is greater than the release of surface energy under the sudden change in $\mathbb{B}\mbox{o}$, in the form of the drop kinetic energy, we expect that the drop will return to an equilibrium state on the charged surface which minimizes the potential.
@@
 The source of the net free charge on the drops is another issue.
-The drop charge could of course also be due to the contact charging mechanism mentioned previously.
-For instance, in a 1996 paper, NASA flight engineer Don Pettit discusses the problem of low-gravity flow induced charging of liquids, resulting ultimately from contact charging phenomenon\cite{pettit_donald_flow_????}.
+The drop charge could also be due to the contact charging mechanism mentioned previously.
+For instance, in a 1996 paper, NASA flight engineer Don Pettit discusses the problem of low-gravity flow induced charging of liquids, resulting ultimately from contact charging phenomenon \cite{pettit_donald_flow_????}.
 Another mechanism for the drop charge is field-induced charging.
-Field-induced charging occurs due to physical breakup of a conductor having a field-induced dipole (e.g a physical seperation of charge).
+Field-induced charging occurs due to physical breakup of a conductor having a field-induced dipole (e.g., a physical seperation of charge).
 In our work this might occur when a drop is deposited on the charged surface by a grounded syringe.
@@
 Field-induced charging is at work in the famous Kelvin thunderstorm, and is applied in inkjet, and electrospay technologies, where in each case the breakup is by the Rayleigh-Plateau instability.
-Notably, in Pettit's aforementioned discussion of contact charging of liquids in low-g, he remarks on accidental electrostatic `hula-ing' of silicone oil drops when ejected from a syringe in the vicinity of a highly-charged polymer surface during an experiment conducted aboard STS-5 by mission specialist Joseph Allen\cite{pettit_donald_flow_????}.
+Notably, in Pettit's aforementioned discussion of contact charging of liquids in low-g, he remarks on accidental electrostatic `hula-ing' of silicone oil drops when ejected from a syringe in the vicinity of a highly-charged polymer surface during an experiment conducted aboard STS-5 by mission specialist Joseph Allen \cite{pettit_donald_flow_????}.
 Depending on the (highly-variable) electrical conductivity of the silicone oil, and the material of the syringe used in the experiment, the charge could arise just as easily by field-induction as by contact charging.
-Relatedly, in a series of informal, and somewhat whimsical experiments, Pettit himself electrostatically orbited small water drops around a triboelectrically charged PTFE knitting needle while aboard ISS during expedition 30/31\cite{stevenson_electrostatic_2015}.
+Relatedly, in a series of informal and somewhat whimsical experiments Pettit himself electrostatically orbited small water drops around a triboelectrically charged PTFE knitting needle while aboard ISS during expedition 30/31 \cite{stevenson_electrostatic_2015}.
 Again, in this case, the drop charge is likely field-induced.
@@
 \section{Applications}
-This study of the drop electro-bounce phenomenon may have results which can be extended to useful applications in a space environment.
+This study of the electro-drop bounce phenomenon may have results which can be extended to useful applications in a space environment.
 External surfaces of spacecraft tend to become charged with time due to the space environment itself.
-Surface charging largely occurs due to low energy electrons (3-50 keV) which do not penetrate the surface of the spacecraft external stucture\cite{czepiela_charging_1997}.
+Surface charging largely occurs due to low energy electrons (3-50 keV) which do not penetrate the surface of the spacecraft external stucture \cite{czepiela_charging_1997}.
 The ultimate sources of these charges are trapped charged particles of the van Allen radiation belts, galactic cosmic rays, and the solar wind.
-This deposited charge accumulates and can lead to significant potential differences between different parts of a spacecraft, sometime leading to breakdown and discharge, called Paschen discharge.
+This deposited charge accumulates and can lead to significant potential differences between different parts of a spacecraft, sometimes leading to breakdown and discharge called Paschen discharge.
 Deep dielectric charging occurs when higher energy charged particles penetrate the surface of a dielectric material, which can also lead to large potential differences if the dielectric leakage is lower than the external charging rate.
@@
 As previously noted, robust phase separation is critical to high reliability multiphase systems used in thermal control and life support.
-Active (but solid-state) phase seperation for life support multiphase flows, espcially high void-fraction droplet-disperse flows is a possible application of this work.
+Active solid-state phase seperation for life support multiphase flows, especially high void-fraction droplet disperse flows is a possible application of this work.
 Such flows are encountered in dish washing, laundry, waste solids drying, food processing, the Sabatier CO$_2$ reaction, and possibly in vapor-compression cycle condensers.
-Phase seperation for other disperse droplet flows include electrostatic droplet seperators for high-efficiency Rankine-cycle turbines, which require a droplet-free vapor phase entering the turbine, but where conventional superheat approaches comes with severe mass penalties\cite{unterberg_zero_1962}, or more speculatively, in high temperature liquid droplet radiators with electrostatic collection\cite{white_liquid_1987}.
-Removal of satellite droplets produced during pippetting in wet-lab research outside of a glovebox environment aboard ISS has also been recently suggested as a application of the work [private communication, NASA JSC, E.
+Phase seperation for other disperse droplet flows include electrostatic droplet seperators for high-efficiency Rankine-cycle turbines, which require a droplet-free vapor phase entering the turbine, but where conventional superheat approaches come with severe mass penalties \cite{unterberg_zero_1962}.
+More speculatively, results of this work could be applied in high temperature liquid droplet radiators with electrostatic collection \cite{white_liquid_1987}.
+Removal of satellite droplets produced during pipetting in wet-lab research outside of a glovebox environment aboard ISS has also been recently suggested as a application of the work [private communication, NASA JSC, E.
 Unger, 2017].
-Drops can become spontaneously charged by contact with standard micropipette tips\cite{choi_spontaneous_2013}, and this free charge can possibly be leveraged for the purposes of phase separation in low-gravity.
+Drops can become spontaneously charged by contact with standard micropipette tips \cite{choi_spontaneous_2013}, and this free charge can possibly be leveraged for the purposes of phase separation in low-gravity.
 
 \section{Overview of this Thesis}
-In this thesis we develop, and partly validate a simple model to aid in design of future electrostatic disperse drop phase separators. To this end the work encompasses:
-\begin{enumerate}
-\item A mathematical model of the drop electro-bounce, its scale analysis, asymptotic estimates for drop apoapses and times-of-flight.
-\item The results of controlled experiments, where the effect of key independent variables drop volume $V_d$, and dielectric surface charge density $\sigma$, on drop trajectories is tested. 
-\end{enumerate}
+In this thesis we develop and partly validate a simple model to aid in design of future electrostatic disperse drop phase separators.
+To this end the work encompasses (1) a mathematical model of the electro-drop bounce, its scale analysis, asymptotic estimates for drop apoapses and times-of-flight, and (2) the results of controlled experiments, where the effect of the key independent variables of drop volume $V_d$ and dielectric surface charge density $\sigma$ on drop trajectories is tested.
 
 \chapter{Theory}
-\section{Forces and the Equation of Motion}
-In this section we develop a simple, 1-dimensional model of the dynamics of drops dominated by electrostatic forces.
+\section{Equation of Motion}
+We develop here a simple 1-dimensional model of the dynamics of drops dominated by electrostatic forces.
 We treat a drop as a particle with radius $R_d$, which translates vertically along the central axis of a charged dielectric square sheet substrate with initial velocity $U_0$.
@@
 The assumed initial conditions are such that, when $\mathbb{B}\mbox{o}$ is suddenly reduced at the start of the drop tower free-fall period, the drop jumps with instantaneous initial velocity $U_0$ from its 1-$g_0$ resting position with fixed radius $R_d$ at $t=0$.
-The dynamical system is sketched out schematically Figure \ref{apparatus}.
+The dynamical system is sketched schematically Figure \ref{apparatus}.
 We now define models for each of the forces in this equation.
 
-For the intermediate range of Reynolds numbers $1 \leq \mathbb{R}\mbox{e} \equiv \frac{2UR_d}{\nu} \leq 2000 $ observed in our experiments the force of drag acting on the drop may be quadratic such that,
+\begin{figure}[ht]
+\centering
+\includegraphics[width=0.65\textwidth]{../figures/apparatus0.pdf}
+\label{apparatus}
+\caption{Schematic representation of drop jump with return and rebound from an electrically charged superhydrophobic substrate.
+The characteristic time and length scales $t_c$ and $y_c$ describe the time of flight and apoapse associated with the drop trajectory.}
+\end{figure}
+
+For the intermediate range of Reynolds numbers $1 \leq \mathbb{R}\mbox{e} \equiv \frac{2UR_d}{\nu} \leq 2000 $ observed in our experiments, the force of drag acting on the drop may be quadratic such that,
 \begin{equation*}\label{drag_force}
@@
 where $C_D$ is the drag coefficient, $\rho$ is the density of the air host fluid, and $A$ is the frontal projected area of the drop.
-For this range of Reynolds numbers the drag coefficient may be approximated by the well known Abraham correlation\cite{abraham_functional_1970},
+For this range of Reynolds numbers the drag coefficient may be approximated by the well known Abraham correlation \cite{abraham_functional_1970},
 \[C_D = \frac{24}{9.06^2} \left( 1 + \frac{9.06}{\sqrt{\mathbb{R}\mbox{e}}} \right)^2 .\]
 
-Modeling the electrostatic force is more involved, but we begin with the standard electrohydrodynamic (EHD) approximation\cite{saville_electrohydrodynamics:_1997}.
-Under a DC electric field, we assume that the real part of the dielectric permitivity $\epsilon$, $\mbox{Re} \langle \epsilon \rangle \approx  \mbox{constant}$.
+Modeling the electrostatic force is more involved, but we begin with the standard electrohydrodynamic (EHD) approximation \cite{saville_electrohydrodynamics:_1997}.
+Under a DC electric field, we assume that the real part of the dielectric permittivity $\epsilon$, $\mbox{Re} \langle \epsilon \rangle \approx  \mbox{constant}$.
 We also assume that electric currents are small enough that the effects of magnetic fields can be neglected.
-The validity of this assumption rests on the characteristic time scale for electrical phenomena $\tau_e = \epsilon /\sigma_e \ll 1$, where $\tau_e$ is the ratio of absolute dielectric permittivity $\epsilon = \kappa \epsilon_0$, to conductivity $\sigma_e$, of the medium, $\kappa$ is the relative dielectric permittivity, and $\epsilon_0$ is the vacuum permitivity.
+The validity of this assumption rests on the characteristic time scale $\tau_e = \epsilon /\sigma_e \ll 1$, where $\tau_e$ is the ratio of absolute dielectric permittivity $\epsilon = \kappa \epsilon_0$, to conductivity $\sigma_e$, of the medium, $\kappa$ is the relative dielectric permittivity, and $\epsilon_0$ is the vacuum permittivity.
 This characteristic time $\tau_e$ is also known as the relaxation time, and is a measure of how quickly the polarization of a dielectric responds to a change in electric field.
-Given the conductivity, and permittivity in the limiting case of extremely-pure water ($ \epsilon \sim 80$, $\sigma_e = 18.2 \times 10^{6}$ $\Omega\mbox{cm}$)\cite{yatsuzuka_electrification_1994}, we estimate $\tau_e \approx 4 \times 10^{-6}$ s.
+Given the conductivity and permittivity in the limiting case of extremely-pure water ($ \epsilon \sim 80$, $\sigma_e = 18.2 \times 10^{6}$ $\Omega\mbox{cm}$) \cite{yatsuzuka_electrification_1994}, we estimate $\tau_e \approx 4 \times 10^{-6}$ s.
 The relaxation time for the common distilled water that is actually used in the drop experiments is undoubtedly shorter due to the presence of solvated ions.
-Neglecting the effects of an electric double layer on hydration of ions in the water or the ambient atmosphere due to the relatively massive size of the drops studied, then the assumption of small relaxation time further implies that the free charge present in the drops will remain approximately constant during the typical time interval of a low-gravity experiment.
+Neglecting the effects of an electric double layer on hydration of ions in the water or the ambient atmosphere due to the relatively massive size of the drops studied, the assumption of small relaxation time further implies that the free charge present in the drops will remain approximately constant during the typical time interval of a low-gravity experiment.
 
@@
 
-The Korteweg-Helmholtz volumetric force density formulation of the Maxwell stress tensor is usually expressed as\cite{melcher_continuum_????}
+The Korteweg-Helmholtz volumetric force density formulation of the Maxwell stress tensor is usually expressed as \cite{melcher_continuum_????}
 \begin{equation}\label{force_density}
@@
 \end{equation}
-The first term on the right hand side this expression, is the well known Coulombic force or electrophoretic force, which arises from the presence of free charge in an external electric field.
+The first term on the right hand side of this expression is the well known Coulombic force or electrophoretic force, which arises from the presence of free charge in an external electric field.
 We expect this term to dominate the electric force in a DC field.
@@
 The third term describes forces due to electrostriction.
-It has been noted by Melcher and Hurwitz that the electrostriction term is the gradient of a scalar and can thus be canonically lumped together with the hydrostatic pressure for incompressible fluids\cite{hurwitz_electrohydrodynamic_1966}.
+It has been noted by Melcher and Hurwitz \cite{hurwitz_electrohydrodynamic_1966} that the electrostriction term is the gradient of a scalar and can thus be canonically lumped together with the hydrostatic pressure for incompressible fluids.
 We neglect it in our analysis.
 
-It is common to approximate the polarization stress by idealizing the drop as a simple dipole using the effective dipole moment method first described by Pohl in 1958\cite{pohl_effects_1958}.
-This approach has since been related back to the force density by the volumetric integration of the force density with the substitution of a Taylor series expansion of $\mathbf{E}$ in the limit of a small radial gradient of the field within the dielectric sphere\cite{wang_general_1997}.
+It is common to approximate the polarization stress by idealizing the drop as a simple dipole using the effective dipole moment method first described by Pohl in 1958 \cite{pohl_effects_1958}.
+This approach has since been related back to the force density by the volumetric integration of the force density with the substitution of a Taylor series expansion of $\mathbf{E}$ in the limit of a small radial gradient of the field within the dielectric sphere \cite{wang_general_1997}.
 The DEP force is related to the induced or permanent dipole moment of polarizable media which has a tendency to align the dipole with the electric field.
@@
 In principle an external electric field will tend to induce a dipole in a dielectric material, but if the field is spatially uniform there is no gradient in the field and the forces felt by the dipoles are symmetric with no net force.
-The dipole moment $\mu$, of a spherical linear-dielectric particle immersed in a dielectric medium is given by
+The dipole moment $\mu$ of a spherical linear-dielectric particle immersed in a dielectric medium is given by
 \begin{equation} \label{dipole_m_1}
@@
 \end{equation} 
-where $\mathbf{P} = \left(\kappa_1 - 1 \right) \epsilon_0 \mathbf{E} = \chi_e \epsilon_0 \mathbf{E}$ is the polarization moment, and $R_d$ is the particle radius, $\kappa_1 = \frac{\epsilon_1}{\epsilon_0}$ is the relative dielectric constant of the air host fluid, $\chi_e = \kappa_1 - 1$ is the electric susceptibility of the host fluid.
+where $\mathbf{P} = \left(\kappa_1 - 1 \right) \epsilon_0 \mathbf{E} = \chi_e \epsilon_0 \mathbf{E}$ is the polarization moment, $R_d$ is the particle radius, $\kappa_1 = \frac{\epsilon_1}{\epsilon_0}$ is the relative dielectric constant of the air host fluid, and $\chi_e = \kappa_1 - 1$ is the electric susceptibility of the host fluid.
 The force felt by the dipole is
@@
 \end{eqnarray}
-where $\mathbf{P}_e=(\kappa_2 - \kappa_1)\epsilon_0 \mathbf{E}$ is the excess polarization, and $\kappa_2$ is the relative dielectric constant of the water particle.
+where $\mathbf{P}_e=(\kappa_2 - \kappa_1)\epsilon_0 \mathbf{E}$ is the excess polarization and $\kappa_2$ is the relative dielectric constant of the water particle.
 Here it is convenient to use the simplifying shorthand $K = \frac{\kappa_2 - \kappa_1}{\kappa_2 + 2 \kappa_1}$, known as the Clausius-Mossotti factor.
 In cases where $K <$ 0, or $K>$ 0 the particle will be either repelled or attracted to regions of strong field.
-In our experiment, choosing the relative dielectric constants $\kappa_1 \approx$ 1 and $\kappa_2 \approx$ 80, $K \approx$ 0.96.
+In our experiment, choosing the relative dielectric constants $\kappa_1 \approx$ 1 and $\kappa_2 \approx$ 80, we estimate $K \approx$ 0.96.
 It is important to note that the equivalent dipole approximation critically requires an assumption of small physical scale of the particle relative to the length scale of nonuniformity of the field, which in this case we take to be the length of the charged superhydrophobic surface, $L =$ 25 mm $\gg R_d \approx$ 2 mm.
@@
 The polarization bound charge in the dielectric will be of the opposite sign of the free drop charge and thus there will be a force of attraction.
-This so-called image force is a correction to the Coulomb force due to the external electric field only, and can be found by a Green's Function solution to Laplace's equation for the electric field called the `method of images'\cite{david_j._griffiths_introduction_1999}.
-This resulting image force $\mathbf{F}_I$, is given by
+This so-called image force is a correction to the Coulomb force due to the external electric field only, and can be found by a Green's Function solution to Laplace's equation for the electric field called the `method of images' \cite{david_j._griffiths_introduction_1999}.
+This resulting image force $\mathbf{F}_I$ is given by
 \begin{equation}
@@
 \begin{eqnarray}
-\frac{ \kappa_2 \epsilon_0 K R_d^2 E_0}{q} \ll 1 \nonumber
+\frac{ \kappa_2 \epsilon_0 K R_d^2 E_0}{q} \ll 1. \nonumber
 \end{eqnarray}
@@
 There is some physical intuition to support this conclusion as well.
-The dielectric displacement $\mathbf{D} = \kappa \epsilon_0 \mathbf{E}$ of a water drop in air is very high due to its large relative dielectric constant.
-This implies that the field strength within the drop is about 80 times smaller than in the surrounding medium (which is essentially the same as a vacuum from a dielectric standpoint), thus it is not particularly inaccurate to model the dielectric volume of a drop as an equipotential conductive shell, with zero field in its interior.
+The dielectric displacement $\mathbf{D} = \kappa \epsilon_0 \mathbf{E}$ of a water drop in air is high due to its large relative dielectric constant.
+This implies that the field strength within the drop is about 80 times smaller than in the surrounding medium, which is essentially the same as a vacuum from a dielectric standpoint.
+Thus it is not particularly inaccurate to model the dielectric volume of a drop as an equipotential conductive shell with zero field in its interior.
 As an aside, in treating the drop as an ideal conductor we note that in our specific case the electrostatic force is not a body force \emph{per se} as the electric field is acting on charges on the surface of the conductor.
-\begin{figure}[ht]
-\centering
-\includegraphics[width=0.65\textwidth]{../figures/apparatus0.pdf}
-\label{apparatus}
-\caption{A schematic representation drop jump with return and rebound from an electrically charged superhydrophobic substrate.
-The characteristic time and length scales $t_c$ and $y_c$ describe the time of flight and apoapse associated with the drop trajectory.}
-\end{figure}
 
@@
 The $y$-component of $d\mathbf{E}$ is found by $d E_r = d E_y \cos \theta = d E_y y/ r$, where $\theta$ is the angle made between the $y$-axis and the position vector $\mathbf{r}$.
-If the charge in a line element, $dx$ is $\sigma L dx$, where $\sigma$ is the average surface charge density, the electric field of a line charge is given by\cite{david_j._griffiths_introduction_1999}
+If the charge in a line element $dx$ is $\sigma L dx$, where $\sigma$ is the average surface charge density, the electric field of a line charge is given by \cite{david_j._griffiths_introduction_1999}
 \[d E_r = \frac{\sigma L dx}{4 \pi \epsilon_0 r \sqrt{r^2 + L^2/4}}.
@@
 We note that this model of the electric field is valid when $R_d \ll L$, which will be true for cases of small drops `far' from the dielectric surface.
-For accurate models of the field in the case $R_d/L \sim \mathcal{O}(1)$ we likely need to solve Laplace's equation for the electric potential $\varphi$,
-\[ - \nabla^2 \varphi = 0,\]
-using numerical methods.
+For accurate models of the field in the case $R_d/L \sim \mathcal{O}(1)$ we likely need to numerically solve Laplace's equation for the electric potential $\varphi$,
+\[ - \nabla^2 \varphi = 0.\]
 
@@
 \end{equation}
-Both regimes given by Equations \ref{near_field}, \ref{far_field} can be clearly seen in Figure \ref{fig:E0}.
+Both regimes given by Equations \ref{near_field} and \ref{far_field} can be clearly seen in Figure \ref{fig:E0}.
 \begin{figure}[h]
@@
 \section{Scaling}
-For small DEP forces, the equation of motion, Equation \ref{gov_eqn_subs}, is non-linear, non-homogeneous and must be solved numerically.
+For small DEP forces the equation of motion Equation \ref{gov_eqn_subs} is non-linear non-homogeneous and must be solved numerically.
 Nevertheless we are curious if we can obtain approximate solutions to the equation analytically using perturbation methods.
@@
 \begin{enumerate}
-\item $y_c \sim U_0 t_c$, and $\mathbf{\Pi}_3 \sim \mathcal{O}(1)$.
-\item $y_c \sim L$, $t_c \sim \frac{L}{U_0}$ (making Equation \ref{scaled_eqn} singular).
-\item $y_c \sim L$, $t_c \sim \left( \frac{L m}{q E_0} \right)^{1/2}$.
-\item $y_c \sim L$, and $\mathbf{\Pi}_3 \sim \mathcal{O}(1)$.
+\item $y_c \sim U_0 t_c$ and $\mathbf{\Pi}_3 \sim \mathcal{O}(1)$
+\item $y_c \sim L$ and $t_c \sim \frac{L}{U_0}$ (making Equation \ref{scaled_eqn} singular)
+\item $y_c \sim L$ and $t_c \sim \left( \frac{L m}{q E_0} \right)^{1/2}$
+\item $y_c \sim L$ and $\mathbf{\Pi}_3 \sim \mathcal{O}(1)$
 \end{enumerate}
@@
 We choose the Case 1 scaling for its combination of physical simplicity, few $\mathbf{\Pi}$ terms, and homogeneous initial conditions. The intrinsic scales for this case are given by
-\[ t_c \sim \frac{R_d^2}{L^2} \frac{4 \pi m U_0}{q E_0}, \hspace{5mm} \mbox{and} \hspace{5 mm} y_c \sim \frac{R_d^2}{L^2} \frac{4 \pi m U_0^2}{q E_0}.
+\[ t_c \sim \frac{R_d^2}{L^2} \frac{4 \pi m U_0}{q E_0} \hspace{5mm} \mbox{and} \hspace{5 mm} y_c \sim \frac{R_d^2}{L^2} \frac{4 \pi m U_0^2}{q E_0}.
 \]
@@
 \begin{eqnarray}
-&{y^*}'' = - \mathbb{D}\mbox{g} B \mathbb{E}\mbox{u} {y^*}'^2 - \left( B \mathbb{E}\mbox{u} {y^*} + 1 \right)^{-2}, & \label{drag_limit}
+&{y^*}'' = - \mathbb{D}\mbox{g} \phi \mathbb{E}\mbox{u} {y^*}'^2 - \left( \phi \mathbb{E}\mbox{u} {y^*} + 1 \right)^{-2}, & \label{drag_limit}
 \end{eqnarray}
@@
 \end{equation*}
-where we call $\mathbb{D}\mbox{g}$ the drag number $\mathbb{D}\mbox{g} \equiv \frac{C_D \rho_a}{\rho_l} = \mathbf{\Pi}_1 B^{-1}{\mathbb{E}\mbox{u}}^{-1}$, and $B = 4 \pi \frac{R_d^2}{L^2}$ is a dimensionless ratio of length scales.
+where we call $\mathbb{D}\mbox{g}$ the drag number $\mathbb{D}\mbox{g} \equiv \frac{C_D \rho_a}{\rho_l} = \mathbf{\Pi}_1 \phi^{-1}{\mathbb{E}\mbox{u}}^{-1}$, and $\phi = 4 \pi \frac{R_d^2}{L^2}$ is a dimensionless ratio of length scales.
 
@@
 \subsection{Inertial Electro-Image Limit}
-The alternate scalings of the equation of motion given by Equations \ref{img_limit}, and \ref{drag_limit} are weakly non-linear differential equations in the sense that they reduce to linear equations as the parameter $\mathbb{E}\mbox{u} \rightarrow 0$.
+The alternate scalings of the equation of motion given by Equations \ref{img_limit} and \ref{drag_limit} are weakly non-linear differential equations in the sense that they reduce to linear equations as the parameter $\mathbb{E}\mbox{u} \rightarrow 0$.
 If we take $\mathbb{E}\mbox{u}$ to be a small parameter we can find an asymptotic approximation to the solution of the non-linear equation by means of a regular perturbation.
@@
 
-By substitution of the expansion  \ref{regular_pert} and its derivatives into \ref{pi_terms}, and equating terms by order we first find the $\mathcal{O}(1)$ unperturbed solution
+By substitution of \ref{regular_pert} and its derivatives into \ref{pi_terms}, and equating terms by order we first find the $\mathcal{O}(1)$ unperturbed solution
 \[{y^*_{0}}{\left ({t^*} \right )} = {t^*} + \frac{{t^*}^{2}}{2} \left(-1 - \mathbb{I}\mbox{g}\right). \]
 Looking at this solution it is evident that if $\mathbb{I}\mbox{g}=0$, the solution is the classical kinematic equation for projectile motion without drag under constant gravity $g_0$.
-Continuing on with this procedure we find, after some tedious computations documented in the project repository for this thesis\cite{schmidt_droplet_electro-bounce:_2017}, the $\mathcal{O}(\mathbb{E}\mbox{u}^5)$ order accurate solution, truncated to $\mathcal{O}(\mathbb{E}\mbox{u}^2)$ below.
+Continuing on with this procedure we find, after some tedious computations documented in the project repository for this thesis \cite{schmidt_droplet_electro-bounce:_2017}, the $\mathcal{O}(\mathbb{E}\mbox{u}^5)$ order accurate solution truncated to $\mathcal{O}(\mathbb{E}\mbox{u}^2)$ is
 \begin{eqnarray}
@@
 The trajectory reduces to the classical $\mathcal{O}(1)$ solution for small values of $\mathbb{I}\mbox{g}$.
-It should be noted that despite what is implied by these plots $\mathbb{I}\mbox{g}$ is not necessarily independent of $\mathbb{E}\mbox{u}$, as they share $q$, and $E_0$ as common factors, $U_0 \sim R_d^2$, and $m \sim R_d^3$.}
+It should be noted that despite what is implied by these plots $\mathbb{I}\mbox{g}$ is not necessarily independent of $\mathbb{E}\mbox{u}$, as they share $q$, and $E_0$ as common factors, $U_0 \propto R_d^2$, and $m \propto R_d^3$.}
     \label{fig:short_times}
 \end{figure}
-These plots show a trend of decreasing time-of-flight $t_f$, which is the time for the drop to return to the origin, or complete a single `bounce', and height at apoapse with increasing values of $\mathbb{I}\mbox{g}$.
+These plots show a trend of decreasing time-of-flight $t_f$, which is the time for the drop to return to the origin (a single `bounce'), and height at apoapse with increasing values of $\mathbb{I}\mbox{g}$.
 When $\mathbb{I}\mbox{g} = 1$, $t_f$ is exactly half of the characteristic time scale in this regime.
@@
 In principle there is some coupling between $\mathbb{E}\mbox{u}$ and $\mathbb{I}\mbox{g}$; notably this relationship does not depend on the electric field $E_0$ but on a charge to mass ratio.
-The effect of contact line hysteresis on the initial jump velocity $U_0$ will also tend to independently decohere the natural covariance between these parameters.
+The effect of contact line hysteresis on the initial jump velocity $U_0$ will also tend to decohere the natural covariance between these parameters.
 
@@
 \label{perturb_viscous}
-&{y^*}({t^*}) = {t^*} - \frac{{t^*}^{2}}{2} + B\mathbb{E}\mbox{u} \left(\frac{{t^*}^{3}}{3} \left(1 + \mathbb{D}\mbox{g}\right) + \frac{{t^*}^{4}}{12} \left(-1 - \mathbb{D}\mbox{g}\right) - \frac{\mathbb{D}\mbox{g} {t^*}^{2}}{2}\right)&  \\
-&+ B^2\mathbb{E}\mbox{u}^{2} \left(\frac{{t^*}^{4}}{12} \left(-3 - 3 \mathbb{D}\mbox{g} - 4 \mathbb{D}\mbox{g}^{2}\right) + \frac{{t^*}^{5}}{60} \left(11 + 10 \mathbb{D}\mbox{g} + 8 \mathbb{D}\mbox{g}^{2}\right) \right.
+&{y^*}({t^*}) = {t^*} - \frac{{t^*}^{2}}{2} + \phi\mathbb{E}\mbox{u} \left(\frac{{t^*}^{3}}{3} \left(1 + \mathbb{D}\mbox{g}\right) + \frac{{t^*}^{4}}{12} \left(-1 - \mathbb{D}\mbox{g}\right) - \frac{\mathbb{D}\mbox{g} {t^*}^{2}}{2}\right)&  \\
+&+ \phi^2 \mathbb{E}\mbox{u}^{2} \left(\frac{{t^*}^{4}}{12} \left(-3 - 3 \mathbb{D}\mbox{g} - 4 \mathbb{D}\mbox{g}^{2}\right) + \frac{{t^*}^{5}}{60} \left(11 + 10 \mathbb{D}\mbox{g} + 8 \mathbb{D}\mbox{g}^{2}\right) \right.
 & \\
 &\left. + \frac{{t^*}^{6}}{360} \left(-11 - 10 \mathbb{D}\mbox{g} - 8 \mathbb{D}\mbox{g}^{2}\right) + \frac{\mathbb{D}\mbox{g}^{2} {t^*}^{3}}{3}\right)
- + \mathcal{O}(B^3\mathbb{E}\mbox{u}^3).& \nonumber
+ + \mathcal{O}(\phi^3 \mathbb{E}\mbox{u}^3).& \nonumber
 \end{eqnarray*}
-Trajectory for this solution are shown in Figure \ref{fig:long_times}.
+Trajectories for this solution are shown in Figure \ref{fig:long_times}.
 \begin{figure}[htb]
@@
     \input{../figures/long_times.pgf}
-    \caption{Long-time scaled drop trajectories for various values of $B \mathbb{E}\mbox{u}$.}
+    \caption{Long-time scaled drop trajectories for various values of $\phi \mathbb{E}\mbox{u}$.}
      \label{fig:long_times}
 \end{figure}
-If we assume a constant scale for the drag coefficient, $C_d \approx 0.5$, then $\mathbb{D}\mbox{g}$ is approximately a constant $\mathbb{D}\mbox{g} \approx 6 \times 10^{-4}$ in all of our experiments.
-We note that the trajectory reduces to the classical $\mathcal{O}(1)$ solution for small values of of $B \mathbb{E}\mbox{u}$.
+If we assume a constant scale for the drag coefficient $C_d \approx 0.5$ then $\mathbb{D}\mbox{g}$ is approximately a constant $\mathbb{D}\mbox{g} \approx 6 \times 10^{-4}$ in all of our experiments.
+We note that the trajectory reduces to the classical $\mathcal{O}(1)$ solution for small values of of $\phi \mathbb{E}\mbox{u}$.
 We also note that with $\mathbb{D}\mbox{g} = 6 \times 10^{-4}$ the effect of drag is slight, appearing only as a slight correction to the higher order terms.
@@
 By again applying a regular perturbation to the asymptotic solution with the expansion
-\[ t^* \sim t^*_0 + B \mathbb{E}\mbox{u} t^*_1 + B^2 \mathbb{E}\mbox{u}^2 t^*_2 \ldots B^n \mathbb{E}\mbox{u}^n t^*_n  
+\[ t^* \sim t^*_0 + \phi \mathbb{E}\mbox{u} t^*_1 + \phi^2 \mathbb{E}\mbox{u}^2 t^*_2 \ldots \phi^n \mathbb{E}\mbox{u}^n t^*_n  
 ,\]
-and solving for the roots at times when $y^* = 0$, we find an asymptotic estimate for the time-of-flight. The $\mathcal{O}(B^2 \mathbb{E}\mbox{u}^2)$ accurate time-of-flight estimate is given by
-\[t_f = 2 + B \mathbb{E}\mbox{u} \left(\frac{4}{3} - \frac{2 \mathbb{D}\mbox{g}}{3}\right) + B^2 \mathbb{E}\mbox{u}^{2} \left(\frac{4}{5} - \frac{4 \mathbb{D}\mbox{g}}{3} + \frac{2 \mathbb{D}\mbox{g}^{2}}{5}\right) + \mathcal{O}(B^3 \mathbb{E}\mbox{u}^3).\]
+and solving for the roots at times when $y^* = 0$, we find an asymptotic estimate for the time-of-flight. The $\mathcal{O}(\phi^2 \mathbb{E}\mbox{u}^2)$ accurate time-of-flight estimate is given by
+\[t_f = 2 + \phi \mathbb{E}\mbox{u} \left(\frac{4}{3} - \frac{2 \mathbb{D}\mbox{g}}{3}\right) + \phi^2 \mathbb{E}\mbox{u}^{2} \left(\frac{4}{5} - \frac{4 \mathbb{D}\mbox{g}}{3} + \frac{2 \mathbb{D}\mbox{g}^{2}}{5}\right) + \mathcal{O}(\phi^3 \mathbb{E}\mbox{u}^3).\]
 Substituting the experimental value of $\mathbb{D}\mbox{g}$ we find the time-of-flight estimate for water drops is
 \begin{equation} \label{time_of_flight}
-t_f = 2 + 1.333 B \mathbb{E}\mbox{u} + 0.799 B^2 \mathbb{E}\mbox{u}^{2} + \mathcal{O}(B^3 \mathbb{E}\mbox{u}^3). 
-\end{equation} 
-In Figure \ref{fig:drag} we see the effect of increasing values of $B \mathbb{E}\mbox{u}$ on $t_f$.
+t_f = 2 + 1.333 \phi \mathbb{E}\mbox{u} + 0.799 \phi^2 \mathbb{E}\mbox{u}^{2} + \mathcal{O}(\phi^3 \mathbb{E}\mbox{u}^3). 
+\end{equation} 
+In Figure \ref{fig:drag} we see the effect of increasing values of $\phi \mathbb{E}\mbox{u}$ on $t_f$.
 \begin{figure}[htb]
@@
     \input{../figures/drag.pgf}
-    \caption{$\mathcal{O}(B^3 \mathbb{E}\mbox{u}^3)$ accurate asymptotic estimate of drop time-of-flight $t_f$.}
+    \caption{$\mathcal{O}(\phi^3 \mathbb{E}\mbox{u}^3)$ accurate asymptotic estimate of drop time-of-flight $t_f$.}
     \label{fig:drag}
@@
 \]
-This equation has an asymptotic velocity, $U_{\infty}$ at $y = \infty$ which is real provided 
+This equation has an asymptotic velocity $U_{\infty}$ at $y = \infty$, which is real provided 
 \[ U_0 \geq  U_e = y_c \sqrt{\frac{2 q E_0 }{m R_d}},
@@
 \begin{equation}\label{escape}
-\frac{1}{8 \pi} B \mathbb{E}\mbox{u} > 1.
-\end{equation}
-If the drop escapes the electric field it will have a residual velocity $U_{\infty}$, and will be in a regime of pure inertia $\sim$ drag. The velocity will then decay as
+\frac{1}{8 \pi} \phi \mathbb{E}\mbox{u} > 1.
+\end{equation}
+If the drop escapes the electric field it will have a residual velocity $U_{\infty}$ and will be in a regime where inertia $\sim$ drag. The velocity will then decay by drag as
 \[
@@
 \section{Summary}
-The objective of this work is to understand the basic physics of the low-gravity drop electro-bounce phenomenon to the point where we can make useful predictions of drop behavior for engineering purposes.
+The objective of this work is to understand the basic physics of the low-gravity electro-drop bounce phenomenon to the point where we can make useful predictions of drop behavior for engineering purposes.
 To that end, in this chapter we have shown the following:
@@
 \item By scaling arguments we find characteristic length and time scales for both a short-times regime where inertia balances Coulombic force and forces due to image charges, and a long-times regime where inertia balances Coulombic force and drag.
-In both regimes a key dimensionless group appears: the electrostatic Euler number $\mathbb{E}\mbox{u}$, which is a ratio of inertia to electrostatic force.
+In both regimes the key dimensionless electrostatic Euler number $\mathbb{E}\mbox{u}$ which is a ratio of inertia to electrostatic force, appears.
 \item The governing ODE is non-linear, but we find approximate analytic solutions for the drop trajectory and time of flight in both regimes by means of asymptotic expansions.
@@
 \section{Overview}
-We are interested mainly about which parameters are important in electrostatic transport of relatively large millimetric drops in low-gravity, and what the values of the respective dimensionless numbers might be; namely, $\mathbb{I}\mbox{g}$, and $\mathbb{E}\mbox{u}$.
-However, this raises an interesting challenge; it is impractical to directly measure all of the key physical quantities that appear in the dimensionless groups at once in a drop tower experiment.
-In particular, determination of net drop free electric charge $q$, is difficult as high-input resistance electrometers are not well-suited to the sudden 15-$g_0$ decelerations characteristic of drop tower experiments.
+We are interested mainly about which parameters are important in electrostatic transport of relatively large millimetric drops in low-gravity, and what the values of the respective dimensionless numbers might be; namely, $\mathbb{I}\mbox{g}$ and $\mathbb{E}\mbox{u}$.
+However, it is impractical to directly measure all of the key physical quantities that appear in the dimensionless groups at once in a drop tower experiment.
+In particular, determination of net drop free electric charge $q$ is difficult as high-input resistance electrometers are not well-suited to the sudden 15-$g_0$ decelerations characteristic of drop tower experiments.
 To find typical values of these parameters we use the following approach:
 \begin{enumerate}
-\item We vary the independent variables $V_d$, and $\sigma$ in a set of single-drop spontaneous drop jumps on charged dielectric super-hydrophobic substrates under low-gravity conditions in a $2.1$ s drop tower.
-\item We capture high-speed video, and digitize the trajectories of the drops. 
+\item We vary the independent variables $V_d$ and $\sigma$ in a set of single-drop spontaneous drop jumps on charged dielectric superhydrophobic substrates under low-gravity conditions in a $2.1$ s drop tower.
+\item We capture high-speed video and digitize the trajectories of the drops. 
 \item We solve the inverse problem to find the key parameters by maximizing a statistical likelihood function between an observed trajectory and the trajectory predicted by a dynamical model given that certain set parameters.
 \end{enumerate}
-A schematic representation of drop jump system statics is shown in Figure and \ref{fig:schematic}.
+A schematic representation of drop jump system statics is provided in Figure \ref{fig:schematic}.
 \begin{figure}[ht]
@@
  \includegraphics[width=0.65\textwidth]{../figures/schematic.pdf}
- \caption{The drop is shown in the initial condition, resting on the superhydrophobic surface in the Cassie-Baxter state just prior to the drop tower experiment.
-The variables $q$, $\sigma$, and $V_d$ are the drop net free charge, dielectric surface charge density, and drop volume respectively.\label{fig:schematic}}
+ \caption{Portion of drop at the initial condition, resting on a superhydrophobic surface in the Cassie-Baxter state just prior to release of the experiment into freefall.
+The variables $q$, $\sigma$, and $V_d$ are the drop net free charge, dielectric surface charge density, and drop volume, respectively.\label{fig:schematic}}
 \end{figure}
@@
 The DDT uses a dual capsule design, inspired by the 2.2 s facility at NASA Glenn Research Center, which decouples drag acceleration felt by the external drag shield from the experiment.
-The experiment experiences approximately $\lessapprox 1 \times 10^{-4}$ $g_0$ during free-fall for 2.1s as the rig and drag shield plummet to the bottom of drop tower 6 stories below.
-Single drops of distilled water in a range of volumes ($0.01 \leq R_d \leq 0.5$ mL), are carefully deposited on charged superhydrophobic substrates using an grounded glass syringe with $\pm $1 $\mu$L accuracy and then dropped in the drop tower.
+The experiment experiences approximately $\lesssim 1 \times 10^{-4}$ $g_0$ during free-fall for 2.1s as the rig and drag shield plummet to the bottom of drop tower 6 stories below.
+Single drops of distilled water in a range of volumes ($0.01 \leq R_d \leq 0.5$ mL) are carefully deposited on charged superhydrophobic substrates using an grounded glass syringe with $\pm $1 $\mu$L accuracy and then dropped in the drop tower.
 Red dye is added to improve thresholding accuracy in trajectory digitization.
-Drop trajectories are recorded using a Panasonic HC-WX970 Camera, at 120 fps with 1/3000s shutter speed.
-In a few cases where higher frame rates are required a Nikon 1 J1 400 fps camera with a 30mm telephoto lens is used.
+Drop trajectories are recorded using a Panasonic HC-WX970 Camera at 120 fps with 1/3000s shutter speed.
+In a few cases where higher frame rates are required a Nikon J1 400 fps camera with a 30mm telephoto lens is used.
 The test cell is back illuminated with a diffused 6000K LED strip light source.
 
-Superhydrophobic electret substrates are prepared, with surface potentials $\varphi_s = 0.7$-$4.0$ kV.
-According to a review by Sessler\cite{sessler_electrets_1987}, an electret is a dielectric material with quasi-permanent electric charge in the sense that the characteristic decay period of the electret is much greater than a practical experiment time scale.
+Superhydrophobic electret substrates are prepared with surface potentials $\varphi_s = 0.7$-$4.0$ kV.
+According to a review by Sessler \cite{sessler_electrets_1987}, an electret is a dielectric material with quasi-permanent electric charge in the sense that the characteristic decay period of the electret is much greater than a practical experiment time scale.
 Electret charge may be `true' charge in the form of surface or space charges, or polarization charges such as bound charges.
@@
 For this reason electrets are thought of as electrostatic analogs to permanent magnets.
-The name \emph{electret} itself is a portmantau to that effect conjured by Heaviside in 1892\cite{heaviside_electrical_2011}.
-Typical commerical electrets are PTFE films on the order of 10-50 $\mu$m thick with the charge being primarily real surface charge.
-Electrets have a plethora of applications, but most germanely they have been used in Electro-Wetting On Dielectric (EWOD) devices for low-voltage manipulation of small drops\cite{wu_low-voltage_2010}.
+The name \emph{electret} itself is a portmantau to that effect conjured by Heaviside in 1892 \cite{heaviside_electrical_2011}.
+Typical commercial electrets are PTFE films on the order of 10-50 $\mu$m thick with the charge being primarily real surface charge.
+Electrets have a plethora of applications, but most germanely they have been used in Electro-Wetting On Dielectric (EWOD) devices for low-voltage manipulation of small drops \cite{wu_low-voltage_2010}.
 Real charge electrets can be produced by contact electrification, injection or deposition of charge carriers by corona discharge or electron beam, ionizing radiation, or by frictional triboelectrification.
@@
 This approach is known to generally produce samples with fairly uniform surface charge densities.
-Some work\cite{van_turnhout_thermally_1975} by van Turnhout using Thermally Stimulated Current (TCS) measurements showed that in 4.8 mm thick polymethyl methacrylate (PMMA) polarization of the dielectric is non-uniform due to real space-charge mostly ($\sim$90\%) residing in a thin (0.1-0.2 mm) layer near the free-surface of the sample.
-In this work we use a Ptec IN5120 balanced AC corona ion source, to direct a net neutral stream of ions towards the dielectric target, which we polarize by an electrode with an EMCO P20P $2$ kV$+$ absolute reference DC-DC converter.
+Some work by van Turnhout \cite{van_turnhout_thermally_1975} using Thermally Stimulated Current (TCS) measurements showed that in 4.8 mm thick polymethyl methacrylate (PMMA), polarization of the dielectric is non-uniform due to real space-charge mostly ($\sim$90\%) residing in a thin (0.1-0.2 mm) layer near the free-surface of the sample.
+In this work we use a Ptec IN5120 balanced AC corona ion source to direct a net neutral stream of ions towards the dielectric target, which we polarize by an electrode with an EMCO P20P $2$ kV$+$ absolute reference DC-DC converter.
 The ion stream compensates the surface and space bound charges arising due to the polarization of the dielectric.
@@
 
-The electret is lamina of 3-4 0.4 mm thick corona charged PMMA sheets.
-The electric field strength scales with the number of dielectric lamina as has also been shown in work on electret based vibrational energy harvesters\cite{wada_stacking_2012} and in water desalinization\cite{ni_desalination_2005}.
+The electret is lamina of 3 to 4 0.4 mm thick corona charged PMMA sheets.
+The electric field strength scales with the number of dielectric lamina as has also been shown in work on electret based vibrational energy harvesters \cite{wada_stacking_2012} and in water desalinization \cite{ni_desalination_2005}.
 
 The electret is established on a superhydrophobic substrate produced by laser etching PMMA and depositing a thin layer of PTFE on the roughened surface.
-The surface charge density can be modulated during the experiment using the high-voltage DC-DC converter, which can re-polarize the dielectric substrate by means of an embedded electrode, and the resulting bound charge partially or fully neutralizes the electric field due to the surface ions deposited by corona charging of the electret.
+The surface charge density can be modulated during the experiment using the high-voltage DC-DC converter, which can re-polarize the dielectric substrate by means of an embedded electrode.
+The resulting bound charge partially or fully neutralizes the electric field due to the surface ions deposited by corona charging of the electret.
 The high-voltage system is armed manually before the drop tower experiment and is automatically safed by a high-voltage power switching relay, which switches the load across a 100 k$\Omega$ resistor when triggered by the resumption of 1-$g_0$ conditions.
@@
 }
-    \caption{(a) The drop electro-bounce experiment hardware mounted on a drop tower rig. (b) Close up of the experimental test cell.\label{fig:rig}}
+    \caption{(a) The electro-drop bounce experiment hardware mounted on a drop tower rig. (b) Close up of the experimental test cell.\label{fig:rig}}
 \end{figure}
@@
 Contact angles of distilled water on the electret are $\sim \hspace{-1mm} 150^{\circ}$.
-The hysteresis of the contact angle (the difference between the advancing $\theta_a$ and receding $\theta_r$ contact angles) is estimated from the roll-off angle using the method of Furmidge\cite{furmidge_studies_1962}, and is found to be approximately $25^{\circ} \pm 10^{\circ}$ when the surface is uncharged.
+The hysteresis of the contact angle (the difference between the advancing $\theta_a$ and receding $\theta_r$ contact angles) is estimated from the roll-off angle using the method of Furmidge \cite{furmidge_studies_1962}, and is found to be approximately $25^{\circ} \pm 10^{\circ}$ when the surface is uncharged.
+A contour plot of the Furmidge model is provided in Figure \ref{fig:hysteresis}.
 The contact angle for water on smooth PTFE layer is $\approx 115^{\circ}$ and is further enhanced by an air layer maintained in the underlying roughness length scales of the surface.
@@
     \input{../figures/hysteresis.pgf}
-       \caption{The Furmidge model of the hysteresis of the contact line plotted as a function of static contact angle $\theta$, and roll-off angle $\alpha$, for $1$ mL drops.
-The measured static contact angles, and roll-off angles of several superhydrophobic surfaces including the laser-etched PMMA used in this work are also shown annotated with the characteristic roughness lengthscale $R_q$ of the surface.\label{fig:hysteresis}}
+       \caption{The Furmidge model of the hysteresis of the contact angle plotted as a function of static contact angle $\theta$ and roll-off angle $\alpha$ for $1$ mL drops.
+The measured static contact angles and roll-off angles of several superhydrophobic surfaces including the laser-etched PMMA used in this work are also shown annotated with the characteristic roughness lengthscale $R_q$ of the surface.\label{fig:hysteresis}}
 \end{figure}
@@
 
-Surface potentials $\varphi_s$, are measured on the superhydrophobic surface using a Simco-Ion FMX-004 electrostatic fieldmeter and the method for determination of surface charge density for low conductivity polymers described in Davies\cite{davies_examination_1967}.
-This measurement is made with the electret substrate connected to a conductive ground plane by conductive tape far from the presence of other conductors.
+Surface potentials $\varphi_s$ are measured on the superhydrophobic surface using a Simco-Ion FMX-004 electrostatic fieldmeter and the method for determination of surface charge density for low conductivity polymers described in Davies \cite{davies_examination_1967}.
+This measurement is made with the electret substrate bonded to a conductive ground plane by conductive tape far from the presence of other conductors.
 An ideal approach to determining surface charge on a dielectric surface is to screen perturbing effects of external electric fields.
 This is partly accomplished by grounding the fieldmeter and by placing the dielectric sample on a grounded conductive plate backing.
-In this case the surface charge density is determined from
-\[ \sigma = \frac{\varphi_s \kappa \epsilon_0}{l}, \]
-where $l$ is the thickness of the dielectric surface.
+In this case the surface charge density is determined from $\sigma = \frac{\varphi_s \kappa \epsilon_0}{l},$ where $l$ is the thickness of the dielectric surface.
 The measured surface voltage is a function of position away from the charged dielectric.
@@
 The relative dielectric constant of the PMMA sheet is measured by using a 65$\times$65 mm polished aluminum parallel plate capacitor with $C = \kappa \epsilon_0 \frac{A}{l}$ where $C$ is the capacitance, and $A$ is the sheet area.
-Measuring the capacitance with 3 sample thicknesses using a GenRad 1657 RLC Digibridge, we find the relative permitivity to be $\kappa = 3.5 \pm 0.4$.
+Measuring the capacitance with 3 sample thicknesses using a GenRad 1657 RLC Digibridge, we find the relative permittivity to be $\kappa = 3.5 \pm 0.4$.
 
@@
 If we consider the drop rig to be a ground which is reasonable given that the rig is isolated from true ground, but is at some reference voltage with respect to the surface charges on the dielectric with an abundance of free charge carriers, then there will be both bulk and surface Ohmic decay of the charge on the dielectric.
-The evolution of the charge can in some cases be approximated by
-\[ \sigma = \sigma_0 e^{\frac{-t}{\epsilon \rho}}, \]
-where $\sigma_0$ is the initial surface charge density, and $\rho$ is the bulk resistivity.
+The evolution of the charge can in some cases be approximated by $\sigma = \sigma_0 e^{\frac{-t}{\epsilon \rho}}, $ where $\sigma_0$ is the initial surface charge density and $\rho$ is the bulk resistivity.
 For an example case of a surface with relative permittivity $\kappa = 3.5$ and bulk resistivity $\rho = 1.6 \times (10^{16})$ $\Omega$cm such as with the case of a 2.8 mm PMMA sheet, then the time constant $\tau = \kappa \epsilon_0 \rho$ is approximately 5000 s, which is significantly longer than the typical time period for a drop tower experiment.
@@
 The relative magnitudes of these charge transport mechanisms, and therfore the stability of the electret, vary drastically depending on the initial surface potential, material properties, environment, and charging method.
-In the case of unshielded electrets compensation by atmospheric ions is significant\cite{perlman_electrets_1973}.
+In the case of unshielded electrets compensation by atmospheric ions is significant \cite{perlman_electrets_1973}.
 Because environmental convection will tend to  maintain a gradient of these ions, sealing an electret in a container from the atmosphere will effectively halt this decay mechanism.
-Atmospheric humidity and water drop condensation can also significantly increase charge decay, presumably by reducing the surface resistence\cite{haenen_characteristic_1975}.
+Atmospheric humidity and water drop condensation can also significantly increase charge decay, presumably by reducing the surface resistence \cite{haenen_characteristic_1975}.
 Examples of this decay can be seen in Figure \ref{fig:charge_decay} for differing numbers of dielectric lamina used in this experiment.
@@
 Secondly, we plainly see a cross-over effect in the decay of the surface potential in our electret samples, whereby the samples charged to higher initial surface potentials decay faster and reached the lower overall final potentials.
-This is a well known effect in polyethylenes charged by corona\cite{ferreira_corona_1992}.
+This is a well known effect in polyethylenes charged by corona \cite{ferreira_corona_1992}.
 \begin{figure}[htb!]
@@
 Digitization of drop trajectories requires several steps of post-processing.
-Video is first decomposed into a sequence of still images.
-Trajectories are captured using the particle tracking module in Fiji\cite{schindelin_fiji:_2012}, a derivative of the popular ImageJ\cite{schneider_nih_2012} package for scientific image analysis.
-The series is stabilized to remove the effect of drop transients from the kinetmatic data\cite{li_image_2008}.
+The video records are first decomposed into sequences of still images.
+Trajectories are captured using the particle tracking module in Fiji \cite{schindelin_fiji:_2012}, a derivative of the popular ImageJ \cite{schneider_nih_2012} package for scientific image analysis.
+The series is stabilized to remove the effect of drop transients from the kinetmatic data \cite{li_image_2008}.
 The series of still images is cropped and the low-entropy pixels are removed using a built-in rolling ball algorithm.
@@
 
-The code, raw data, and make files for this thesis are archived on the open-source project portal Github\cite{schmidt_droplet_electro-bounce:_2017}.
+The code, raw data, and make files for this thesis are archived on the open-source project portal Github \cite{schmidt_droplet_electro-bounce:_2017}.
 
@@
 These dimensionless numbers depend on physical properties not all of which are easily measured by experiment.
-Drop free charge $q$, in particular, could in principle be directly measured by collecting the charged drops in a faraday cup under low-g and measuring the change in capacitance of the cup using a high input-resistance electrometer, but this method is difficult to apply in practice in a drop tower.
+Drop free charge $q$ in particular could in principle be directly measured by collecting the charged drops in a faraday cup under low-g and measuring the change in capacitance of the cup using a high input-resistance electrometer.
+But this method is burdensome to apply in practice in a drop tower.
 Other variables we can directly measure with varying levels of accuracy.
@@
 \item Slice drop trajectories by their bounce minima and apply a smoothing filter.
-\item Extract the drop charge, as well as other experimental parameters, by maximizing the log-likelihood of the data given the dynamical model by varying the parameter vector using a direct search optimization.
+\item Extract the drop charge as well as other experimental parameters by maximizing the log-likelihood of the data given the dynamical model by varying the parameter vector using a direct search optimization.
 \end{enumerate}
@@
 m y'' = \frac{1}{2} \rho C_D A_d {y'}^2 + q E(y) + K q^2 y^{-2}, \]
-$y_d(t)$ is the corresponding experimentally observed drop $y$-coordinate position at time $t$, and $\sigma_d$ is the standard error of the observed position.
+where $y_d(t)$ is the corresponding experimentally observed drop $y$-coordinate position at time $t$ and $\sigma_d$ is the standard error of the observed position.
 The vector $\mathbf{x}$ that minimizes $\chi^2$ is the so called Maximum Likelihood Estimate (MLE) of the experimental parameters.
@@
 The posterior probability density function (PDF) $\mbox{prob}(X|D, I)$ is ultimately what we wish to estimate, the prior PDF $\mbox{prob}(X|I)$ reflects our knowledge of the system, and the evidence $\mbox{prob}(D|I)$ is the likelihood of the data based on our knowledge.
-We also note that since it only makes sense to compare the conditional PDF's for the same data, we can ignore the denominator.
+We also note that since it only makes sense to compare the conditional PDF's for the same data we can ignore the denominator.
 We further note that the prior $\mbox{prob}(X|I)$ is fixed before our observations and so can be treated as invariant to our problem.
 We can therefore infer that $\mbox{prob}(X|D, I) \propto \mbox{prob}(D|X, I)$.
-The MLE for the model parameters $\mathbf{x_0}$ is given by the maximum of the posterior PDF, which is equivalent to the solution of the ODE given the parameters $\mathbf{x}$, that produces the highest probability of the observed data.
+The MLE for the model parameters $\mathbf{x_0}$ is given by the maximum of the posterior PDF, which is equivalent to the solution of the ODE given the parameters $\mathbf{x}$ that produces the highest probability of the observed data.
 Since the likelihood $\mathcal{L}(\mathbf{x}) = \prod_i^n \mathcal{P}_i$ and the probability $\mathcal{P}$ of any single observation is less than one, then the total likelihood which is the product of a large number of probabilities is vanishingly small.
@@
 \]
-is the $\chi^2$ goodness-of-fit, $y_d = y_d(t)$ is a observation of drop position at a point in time, and $y_G =  y_G(t, \mathbf{x})$ is the drop position predicted by the solution to the equation of motion at time $t$, and $\sigma_d$ is the standard error of the position measurement.
+is the $\chi^2$ goodness-of-fit, $y_d = y_d(t)$ is an observation of drop position at a point in time, $y_G =  y_G(t, \mathbf{x})$ is the drop position predicted by the solution to the equation of motion at time $t$, and $\sigma_d$ is the standard error of the position measurement.
 The optimal parameter set is the one with the highest probability of observing the data (the maximum of the posterior PDF) and can be determined by maximizing the log-likelihood $\mathcal{M}$ (or minimizing $\chi^2$) of the data $\mathbf{d}$ with respect to the parameter set $\mathbf{x}$.
-Thus parameter estimation is a variety of optimization problem.
+Thus, parameter estimation herein is a variety of optimization problem.
 
@@
 Our choice of smoothing approach depends principally on the nature of the errors in the dataset.
-The sources of error include misalignment of the camera, error in the fiduciary length scale, perspective due to objects being out of the photographic plane, and various errors arising in the digitization process including the difference between the thresholded ellipse fitted centroid and the true centroid of the non-ellipse drop centroid.
-Some of these errors are systematic in origin and introduce consistent biases into the data, e.g., coherent spectral sources, rather than truly stochastic noise.
+The sources of error include misalignment of the camera, error in the fiduciary length scale, perspective due to objects being out of the photographic plane, and various errors arising in the digitization process including the difference between the thresholded ellipse-fitted centroid and the true centroid of the non-ellipse drop centroid.
+Some of these errors are systematic in origin and introduce consistent biases into the data, e.g., coherent spectral sources rather than truly stochastic noise.
 Data smoothing does little to help systematic errors in that they are usually of lower frequency than the signal.
-Random errors, by contrast, are assumed to have a Gaussian distribution as required by the central limit theorem, and are independent of the signal which we assume results from an inherently deterministic process.
-
-We experimented with a variety of filters implemented in the \verb|scipy.signal| Python \emph{SciPy}\cite{oliphant_python_2007} module on a representative set of trajectory data; these methods include 1D Gaussian convolution, Wiener, Butterworth, and Savitsky-Golay filters.
-Qualitatively comparing these smoothing methods by hand tuning filter orders and window sizes, we find that we loose too many data points in the smoothing process, large amplitudes are overly smoothed by repeated filtering passes, or there are significant end effects for most of these methods.
+Random errors by contrast are assumed to have a Gaussian distribution as required by the central limit theorem and are independent of the signal which we assume results from an inherently deterministic process.
+
+We experimented with a variety of filters implemented in the \verb|scipy.signal| Python \emph{SciPy} \cite{oliphant_python_2007} module on a representative set of trajectory data; these methods include 1D Gaussian convolution, Wiener, Butterworth, and Savitsky-Golay filters.
+Qualitatively comparing these smoothing methods by hand-tuning filter orders and window sizes, we find that we loose too many data points in the smoothing process, that large amplitudes are overly smoothed by repeated filtering passes, or that there are significant end effects for most of these methods.
 A comparison of these smoothing approaches on a representative trajectory data set is shown in Figure \ref{fig:y_filtered}.
@@
 (b) Comparing Butterworth and Savitsky-Golay filtered first derivatives of the above schematic trajectory we see that the Butterworth filter also suffers from a slight end effect.
-This implies that the optimization will find a different optima of the likelyhood depending on which type of filter is used.}
+This implies that the optimization will find a different optima of the likelihood depending on which type of filter is used.}
       \label{fig:y_filtered}
@@
     \input{../figures/power_spectra.pgf}
-    \caption{The power spectra has a peak at 1 Hz, which is the drop trajectory parabola itself, and smaller peaks in the kHz range corresponding to various noise frequencies.
-The Savitsky-Golay and Butterworth filters seem to have the least distortion of the power spectra of the true signal.
-Both also attenuate the noise at the 2 kHz peak.
+    \caption{Signal power spectra with peak at 1 Hz, which is the drop trajectory parabola itself, and smaller peaks in the kHz range corresponding to various noise frequencies.
+The Savitsky-Golay and Butterworth filters appear to have the least distortion and attenuate the noise at the 2 kHz peak.
 \label{fig:power}}
 \end{figure}
-The Savitsky-Golay, and Butterworth filters both produce fairly smooth derivatives as can be seen in Figure \ref{fig:y_filtered}, but the small window-size needed for Butterworth filter tends to also produce a noticeable end effect.
+The Savitsky-Golay and Butterworth filters both produce fairly smooth derivatives but the small window-size needed for Butterworth filter tends to also produce noticeable end effects.
 The Savitsky-Golay filter essentially uses a moving-window based on local least-squares polynomial approximations.
-It was shown that fitting a polynomial to a set of input samples and then evaluating the resulting polynomial at a single point within the approximation interval is equivalent to discrete convolution with a fixed impulse response\cite{savitzky_smoothing_1964}.
-A beneficial property of this kind of low-pass filter is the tendency to maintain waveform amplitudes, and so they are attractive in applications having noisy signals with sharply pointed waveforms such as ultrasound or synthetic aperture radar\cite{schafer_what_2011}.
+It was shown that fitting a polynomial to a set of input samples and then evaluating the resulting polynomial at a single point within the approximation interval is equivalent to discrete convolution with a fixed impulse response \cite{savitzky_smoothing_1964}.
+A beneficial property of this kind of low-pass filter is the tendency to maintain waveform amplitudes, and so they are attractive in applications having noisy signals with sharply pointed waveforms such as ultrasound or synthetic aperture radar \cite{schafer_what_2011}.
 Because Savitsky-Golay is a Finite Impulse Response (FIR) filter it requires data points to be equally spaced.
@@
 The windows are piecewise defined by partitioning the data set into a series of individual bounces.
-To this partitioning is accomplished by slicing the dataset at minima identified after an initial rough smoothing pass using the \verb|scipy.signal.argrelextrema()| function.
+This partitioning is accomplished by slicing the dataset at minima identified after an initial rough smoothing pass using the \verb|scipy.signal.argrelextrema()| function.
 The Savitsky-Golay polynomial order is 4.
@@
 The power spectra for these same data, obtained by Discrete Fourier Transform, are shown in Figure \ref{fig:power}.
-Though, it is worth noting that our signal is not truly periodic.
+We note that our signal is not truly periodic.
 
@@
 Mathematical optimization is the problem of finding minima of a function $f$.
-In this context the function is called the cost, or objective function.
-The field of mathematical optimization is as old as calculus itself, and the number of particular optimization techniques is correspondingly myriad.
+In this context the function is called the cost or objective function.
+The field of mathematical optimization is as old as calculus itself and the number of particular optimization techniques is correspondingly myriad.
 Particular techniques lend themselves well to particular types of optimization problems.
@@
 Minima of objective function $f: A \rightarrow \mathbb{R}^m$ are called feasible solutions.
-If the function $f$ is convex the feasible solution is the global minimum, otherwise additional local minima exist.
+If the function $f$ is convex the feasible solution is the global minimum- otherwise additional local minima exist.
 The scale of the optimization problem is set ultimately by dimensionality of the objective function.
 Functions may not always be smooth in the sense of having continuous derivatives, and this is problematic in that optimization methods fundamentally rely on gradients of the objective function.
-Problems with anisotropic objective functions where there is strong covariance between the parameters, and the gradient vector generally to differ significantly from the Newton direction $-\mathbf{H}^{-1} f' ( \mathbf{x} )^T$, where $\mathbf{H}$ is the Hessian matrix, are considered ill-conditioned.
-Gradient based deterministic search algorithms tend to converge slowly for ill-conditioned problems as they take a zigzagging path determined by the local value of the gradient rather than following the Newton-direction vector towards the minimum.
+Problems with anisotropic objective functions where there is strong covariance between the parameters are called ill-conditioned.
+In such cases the gradient vector differs significantly from the Newton direction $-\mathbf{H}^{-1} f' ( \mathbf{x} )^T$, where $\mathbf{H}$ is the Hessian matrix.
+Gradient-based deterministic search algorithms tend to converge slowly for ill-conditioned problems as they take a zigzagging path determined by the local value of the gradient rather than following the Newton-direction vector towards the minimum.
 Numerical optimization may deal with black box functions where we do not have an explicit mathematical expression of the function we are optimizing.
@@
 In general, noisy, black box, non-linear, non-quadratic, non-convex, constrained, ill-conditioned, high-dimensional objective functions are problematic to optimize.
-Unfortunately, problems of this type are the essence of parameter estimation, and of our problem particularly.
-These difficulties often lead to the characterization of parameter estimation as an `art' rather than a precise science.
+Unfortunately, problems of this type are the essence of parameter estimation and of our problem particularly.
+These difficulties often lead to the characterization of parameter estimation as an `art' rather than a science.
 
@@
 We integrate it numerically using the \verb|odeint| \emph{Scipy} module.
-This is a shake-and-bake Python wrapper for the venerable 1982 \emph{netlib ODEPACK} library double-precision \verb|lsoda| integrator\cite{hindmarsh_odepack_1983} (Livermore Solver for Ordinary Differential equations with Automatic method switching for stiff and nonstiff problems).
+This is a shake-and-bake Python wrapper for the venerable 1982 \emph{netlib ODEPACK} library double-precision \verb|lsoda| integrator \cite{hindmarsh_odepack_1983} (Livermore Solver for Ordinary Differential equations with Automatic method switching for stiff and nonstiff problems).
 The function switches dynamically between Adams (nonstiff) and Backwards Differentiation Formulas (BDF, stiff) according to the stiffness of the solution.
@@
 The non-convexity of the problem implies that there are many local minima of the objective function.
-While in principle a gradient-based optimizer, such as the quasi-Newton method of Broyden, Fletcher, Goldfarb, and Shanno (BFGS)\cite{nocedal_numerical_2006}, could be used by using finite-differences to obtain approximate gradients of the $\chi^2$ objective function, in practice doing so is extremely problematic because the noise-to-signal ratio of the objective function scales like $\mathcal{O}(f)$ for $df/dt$ and $\mathcal{O}(f^2)$ for $d^2f/dt^2$ which will tend to cause convergence to a local minima that is only an artifact of the likelihood response surface\cite{wood_data_1982}.
-As a further practical matter, if evaluating the objective function is computationally expensive, for instance if it requires solving a stiff, non-linear ODE, then gradient-free approaches tend to converge faster regardless\cite{kolda_optimization_2003}.
-
-We use a gradient-free, direct-search approach: the Nelder-Mead\cite{nelder_simplex_1965} algorithem implemented in \verb|scipy.optimize|.
+While in principle a gradient-based optimizer (i.e., the quasi-Newton method of Broyden, Fletcher, Goldfarb, and Shanno (BFGS) \cite{nocedal_numerical_2006}), could be used by using finite-differences to obtain approximate gradients of the $\chi^2$ objective function, doing so in practice is problematic because the noise-to-signal ratio of the objective function scales like $\mathcal{O}(f)$ for $df/dt$ and $\mathcal{O}(f^2)$ for $d^2f/dt^2$ which will tend to cause convergence to a local minima that is only an artifact of the likelihood response surface \cite{wood_data_1982}.
+As a further practical matter, if evaluating the objective function is computationally expensive, as in our problem, then gradient-free approaches tend to converge faster regardless \cite{kolda_optimization_2003}.
+
+We use a gradient-free direct-search Nelder-Mead \cite{nelder_simplex_1965} algorithem implemented in \verb|scipy.optimize|.
 Nelder-Mead is relatively robust to noise and is thrifty with our computationally expensive function-calls.
@@
 In fact Nelder-Mead is sometimes also called the `amoeba method'.
-Very little is known about the convergence properties of the Nelder-Mead algorithm in its classical form for non-smooth objective functions\cite{price_convergent_2002}, except that in general it doesn't satisfy the properties required for convergence by other direct search algorithms: the simplex remains uniformly non-degenerate and some form of sufficient descent condition for function values at the vertices is required at each iteration.
+Little is known about the convergence properties of the Nelder-Mead algorithm in its classical form for non-smooth objective functions \cite{price_convergent_2002}, except that in general it does not satisfy the properties required for convergence by other direct search algorithms: the simplex remains uniformly non-degenerate and some form of sufficient descent condition for function values at the vertices is required at each iteration.
 Scaling can help solve convergence problems and improve numerical stability.
@@
 Here the goal is to make the problem equally sensitive to steps in any direction.
-Nelder-Mead is not a global optimizer, though there are variants which use sequential local searches with probabilistic restarts to achieve globality, usually at a tremendous computational cost.
+Nelder-Mead is not a global optimizer, though there are variants which use sequential local searches with probabilistic restarts to improve globality, usually at a tremendous computational cost.
 However, Nelder-Mead behaves less locally than many gradient-based approaches.
 The convergence history of the parameter MLE using Nelder-Mead for a single drop jump experiment is shown in Figure \ref{fig:convergence}.
-Results of the parameter estimation are shown in Figures \ref{fig:trajectories}, \ref{fig:inverse_problem}.
+As is typical with Nelder-Mead much of the improvement in $\chi^2$ is realized in the first few iterations.
+Overall the rate of convergence is sub-linear, which is to be expected for non-linear constrained problems using an hueristic algorithem.
+Results of the parameter estimation are shown in Figures \ref{fig:trajectories} and \ref{fig:inverse_problem}.
 
@@
     \input{../figures/convergence.pgf}
-    \caption{As is typical with Nelder-Mead much of the improvment in $\chi^2$ is realized in the first few iterations.
-Overall the rate of convergence is sub-linear, which is to be expected for non-linear constrained problems using an hueristic algorithem.\label{fig:convergence}}
+    \caption{Convergence history of MLE optimization by the Nelder-Mead algorithm for a typical drop trajectory. \label{fig:convergence}}
 \end{figure}
@@
     \caption{A series of filtered drop trajectories arranged by increasing apoapse.
-The blue dots represent either the beginning and end of the experiment, or points at which the drop is either coming into, or leaving contact with the surface.}
+The blue dots represent either the beginning and end of the experiment, or points at which the drop is either coming into or leaving contact with the surface.}
     \label{fig:trajectories}
@@
 However, apart from the drop free charge the inverse model parameters are constrained by our experimental observations of them and their associated measurement uncertainties.
-This, we hope, makes the specter of an over fit model less frightening, but does convert our unconstrained optimization problem to an constrained one which raises special difficulties of its own, which we discuss below.
+This we hope makes the specter of an over fit model less worrisome, but does convert our unconstrained optimization problem to an constrained one which raises special difficulties of its own, which we discuss below.
 
@@
 \[ \phi(\mathbf{x}, r_p ) = F(\mathbf{x}) + r_p P(\mathbf{x}), \]
-where $P \left( \mathbf{x} \right)$ the penalty function is given by
+where the penalty function $P \left( \mathbf{x} \right)$ is given by
 \begin{equation} \label{exterior}
- P( \mathbf{x} ) = \sum_{j = 1}^m \left\lbrace \mbox{max} \left[ 0, g_j(\mathbf{x} ) \right] \right\rbrace^2 + 
+ P( \mathbf{x} ) = \sum_{j = 1}^m \left( \mbox{max} \left[ 0, g_j(\mathbf{x} ) \right] \right)^2 + 
 \sum_{k = 1}^l \left[ h_k( \mathbf{x}) \right]^2 .
@@
 
-As with penalty function approaches generally, the exterior penalty function has several drawbacks; namely, the possibility of the objective function being undefined outside of the set of feasible solutions.
+As with penalty function approaches generally, the exterior penalty function has the drawback of the possibility of the objective function being undefined outside of the set of feasible solutions.
 Additionally, by naively encouraging feasibility of the solution using large values of the penalty parameter $r_p$ we will tend to ill-condition the unconstrained formulation of the problem, though in our implementation the preconditioning tends to make the pseudo-objective function less and less sensitive to the constraints as the likelihood is approaches a maximum.
-We use the measured values of $u_0$, $V_d$, and $E_0$, and the informed guess $q \approx k V_d^{2/3} E_0$ where k is a constant $k \approx 1 \times 10^{-11}$ as an initial guess for the parameter vector $\mathbf{x}$.
+We use the measured values of $U_0$, $V_d$, and $E_0$, and the informed guess $q \approx k V_d^{2/3} E_0$ where the constant $k \approx 1 \times 10^{-11}$ is an initial guess for the parameter vector $\mathbf{x}$.
 We stop the optimization after 300 iterations rather than waiting for convergence.
@@
 However, there is another approach to find the covariance matrix, given by
-\[ \left[\sigma^2 \right]_{ij} = -\left[ \left( \nabla^2 \mathcal{L}\right)^{-1}\right]_{ij} = 2 \left[ \nabla^2 \left( \chi^2\right)\right]_{ij}^{-1} = -\left[H^{-1} \right]_{ij},\]
-where $\left[H^{-1} \right]_{ij}	$ refers to the Hessian matrix and $\left[\sigma^2 \right]_{ij}$ is the covariance matrix.
+\[ \left[\sigma^2 \right]_{ij} = -\left[ \left( \nabla^2 \mathcal{L}\right)^{-1}\right]_{ij} = 2 \left[ \nabla^2 \left( \chi^2\right)\right]_{ij}^{-1} = -\mathbf{H}^{-1},\]
+where $\left[\sigma^2 \right]_{ij}$ is the covariance matrix.
 The issue of identifiability is especially fraught for non-linear black-box type problems were it is difficult to explicitly evaluate the Hessian.
@@
 Thus armed with the Hessian we may use the condition number
-\[ \mbox{cond} (H) = \frac{\mbox{max}[\mbox{eig}(H)]}{\mbox{min}[\mbox{eig}(H)]}, \]
+\[ \mbox{cond} (\mathbf{H}) = \frac{\mbox{max}(\mbox{eig}(\mathbf{H}))}{\mbox{min}(\mbox{eig}(\mathbf{H}))}, \]
 to make a qualitative assesment of the stability of the problem.
 Among our parameter estimate MLE optima we find large typical condition numbers $\sim \mathcal{O}(10^{27})$.
-In fact, in many cases our Hessian is not negative definite, or invertible at the minmia $\mathbf{x}_0$, which implies negative values of the variances, which are impossible.
+In fact, in many cases our Hessian is not negative definite or invertible at the minmia $\mathbf{x}_0$, which implies unphysical negative values of the variances.
 These issues indicate the problem is extremely ill-conditioned near the minima $\mathbf{x_0}$.
 Given that the parameter estimates are highly co-linear, it is unsuprising that the Hessian matrix is near-singular and its inversion is either impossible or involves significant numerical error.
-Posteriori verification of the results is crucial to bound the identifiability of the parameter estimation problem, but this remains as future work.
-Several sources suggest senstivity analysis of the parameter estimates by generation of synthetic Monte Carlo data sets as a means of establishing identifiability\cite{bevington_data_1969, jaqaman_linking_2006}.
+A posteriori verification of the results is crucial to bound the identifiability of the parameter estimation problem, but this remains as future work.
+Several sources suggest senstivity analysis of the parameter estimates by generation of synthetic Monte Carlo data sets as a means of establishing identifiability \cite{bevington_data_1969, jaqaman_linking_2006}.
 
@@
 To accomplish this we conduct a series of low-gravity experiments in a 2.1 s drop tower, where we observe the trajectories of spontaneous drop jumps and rebounds from charged dielectric superhydrophobic substrates.
+Our procedure to quantify these physical parameters is itemized below:
 \begin{itemize}
@@
 This is accomplished by Maximum Likelihood Estimation using a constrained direct search optimization.
-\item We fail to establish the identifiability of the parameter estimate using the conventional approach of inverting the Hessian near the optima.
-This indicates ill-conditioning of the parameter estimation problem, likely due to large multicolinearity between the main factors $q$, $V_d$ and $\sigma$.
-To robustly estimate the error of the parameter estimates an alternate approach, such as the Monte Carlo method, is required.
 \end{itemize}
@@
 \section{Parameter Estimates}
-We determined the distribution of most probable experimental model variables vlaues for a population of the drops jumped in drop tower tests, shown in Figure \ref{fig:scatter}.
-The dependence of charge on drop surface area $A$ is immediately evident.
-The effect of electric field on drop charge is less obvious in the data.
+We determined the distribution of most probable experimental model variables values for a population of the drops jumped in drop tower tests shown in Figure \ref{fig:scatter}.
+The dependence of charge on drop surface area $A$ is immediately evident, while the effect of electric field on drop charge is less obvious.
 This co-linearity is likely the source of the ill-conditioning issues in the parameter estimation process.
-However, assuming the main effect is the interaction between charge and electric field, a Robust Least Squares model fit $q \sim kAE_0$ using the Python \verb|statsmodels.formula.api.RLM()| function with the non-linear transformation $A = V_d^{2/3}$, finds that $k=5.01 \times 10^{-11} \pm  2.85 \times 10^{-11}$ F/m with $R^2 = 0.946$.
+However, assuming the main effect is the interaction between charge and electric field, a Robust Least Squares model fit $q \sim kAE_0$ using the Python \verb|statsmodels.formula.api.RLM()| function with the non-linear transformation $A = V_d^{2/3}$ finds that $k=5.01 \times 10^{-11} \pm  2.85 \times 10^{-11}$ F/m with $R^2 = 0.946$.
 This model uses Huber's T norm, median absolute scaling, and H1 covariance estimation.
@@
     \centering
-    \resizebox{12cm}{!}{\input{../figures/scatter.pgf}}
-    \caption{Covariance plot of main parameters $E_0$, $U_0$, drop area ($V_d^{2/3})$, and $q$.\label{fig:scatter}}
+    \resizebox{12cm}{!}{\input{../figures/scatter.pdf_tex}}
+    \caption{Covariance plot of main parameters $E_0$, $U_0$, $V_d$, and $q$.\label{fig:scatter}}
 \end{figure}
@@
 
-The model $q \sim kAE_0$ is similar to the classical solution for the surface charge of a half-spherical conductor with a field-induced dipole\cite{david_j._griffiths_introduction_1999}
+The model $q \sim kAE_0$ is similar to the classical solution for the surface charge of a half-spherical conductor with a field-induced dipole \cite{david_j._griffiths_introduction_1999}
 \begin{eqnarray}
 q &=& 3 \epsilon_0 E_0 \int_A \cos \theta dA \nonumber \\
-&=& 3 \pi^{1/3} 6 \left(6 V_d \right)^{2/3} \epsilon_0 E_0 \int^{4 \pi/2}_{\pi / 2} \cos \theta d\theta \nonumber \\
+&=& 3 \pi^{1/3} 6 \left(6 V_d \right)^{2/3} \epsilon_0 E_0 \int^{\pi / 2}_{0} \!\!\!\!\! \cos \theta d\theta \nonumber \\
 &=& k E_0 V_d^{2/3} \label{dipole}
@@
 with $k \approx 1.3 \times 10^{-10}$ F/m.
-This is also of similar form to the charge found by Takamatsu and coauthors for drops falling from a grounded nozzle in an external electric field\cite{takamatsu_theoretical_1981}
+This is also of similar form to the charge found by Takamatsu and coauthors for drops falling from a grounded nozzle in an external electric field \cite{takamatsu_theoretical_1981}
 \[q = 4 \pi \epsilon_0 \beta E_0 R_d^2 \]
@@
 
-The effect of volume on jump velocity $U_0$ is not immediately evident in the data, despite previous work having establishing this relationship\cite{attari_puddle_2016}.
+The effect of volume on jump velocity $U_0$ is not immediately evident in the data despite previous work having establishing this relationship \cite{attari_puddle_2016}.
 This likely results from large variance in $U_0$ due to contact line hysteresis during the drop roll-up.
-Contact line losses predominates in the sub 1 mL volume drops which are primarily the object of this study.
+Contact line losses predominate in the sub 1 mL volume drops which are primarily the object of this study.
 
 \section{Model Validation}
-Dimensional drop apoapses, shown in Figure \ref{fig:series_s_eu}, scale closely with $\mathbb{E}\mbox{u}$ as expected according to our earlier analysis.
-Electrostatic Euler numbers in the data set vary between $1.4 \lessapprox \mathbb{E}\mbox{u} \lessapprox 35.4$.
+Dimensional drop apoapses shown in Figure \ref{fig:series_s_eu} scale closely with $\mathbb{E}\mbox{u}$ as expected according to our earlier analysis.
+Electrostatic Euler numbers in the data set vary between $1.4 \lesssim \mathbb{E}\mbox{u} \lesssim 35.4$.
 The dielectrophoretic force plays a small role when drops have net charge in a DC field.
 The condition to neglect the DEP force was satisfied for all experiments in the dataset with typical values of the condition number $\kappa_2 \epsilon_0 K R_d^2 E_0/q \approx \mathcal{O}(10^{-6})$.
-In the non-dimensional trajectories with short-time scaling shown in Figure \ref{fig:series_s_ds}, we see that the trajectory apoapses are consistently $\mathcal{O}(1)$, but most trajectories overshoot their characteristic time scale (which predicts returns at $t^*  =2$ to the zeroth order).
-This should be read as a success of the scaling.
-However the fact that $\mathbb{E}\mbox{u} \sim \mathcal{O}(1)$ in the regime (in other words, it is not a small parameter), does imperil the validity of the Equation \ref{perturb_image} asymptotic result for short times.
+In the non-dimensional trajectories with short-time scaling shown in Figure \ref{fig:series_s_ds}, we see that the scaled trajectory apoapses are consistently $\mathcal{O}(1)$, with all trajectories overshooting their characteristic time scale (which predicts returns at $t^*  =2$ at zeroth order).
+The fact that $\mathbb{E}\mbox{u} \ll 1$ is not satisfied for all tests is in violation of the Equation \ref{perturb_image} asymptotic result for short times.
 \begin{figure}[!htb]
@@
 \end{figure}
-The covariance of $\mathbb{I}\mbox{g}$ with $\mathbb{E}\mbox{u}$ is shown in Figure \ref{fig:dnumbs}.
-Predictably, there is quite strong correlation between the dimensionless groups.
-We also see that $\mathbb{I}\mbox{g} < 1$ for all drops.
-Using an OLS regression, we find the model $\mathbb{I}\mbox{g} \sim (0.012 \pm 0.003) \mathbb{E}\mbox{u} + (0.212 \pm 0.036) $ with $R^2 =0.59$.
-\begin{figure}[htb]
-    \centering
-    \input{../figures/dnumbs.pgf}
-    \caption{Experimental covariance of $\mathbb{E}\mbox{u}$ and $\mathbb{I}\mbox{g}$.\label{fig:dnumbs}}
-\end{figure}
-The predictions of the long-time scaled time-of-flight theory \ref{time_of_flight} $t_c t_f$ compare favorably to the experimental time-of-flight $t_b$, shown in dimensional form in Figure \ref{fig:series_s_ds}.
-This allows an improvement to be made to the asymptotic result \ref{time_of_flight} by multiplying the series by the empirical coefficient $a = 1/0.68 = 1.47$.
+
+The predicted long-time scaled time-of-flight $t_f$ given by Equation \ref{time_of_flight} when redimensionalized by the characteristic time $t_c$ compares favorably to the experimental time-of-flight $t_b$, shown in Figure \ref{fig:times2}.
+This allows an improvement to be made to the asymptotic result of Equation \ref{time_of_flight} by multiplying the series by the empirical coefficient $a = 1/0.68 = 1.47$.
 The semi-analytic time-of-flight is then given by
@@
 \label{time_improved}
-t^* = 2.94 + 1.96B\mathbb{E}\mbox{u} + 1.18B^2\mathbb{E}\mbox{u}^{2} + \mathcal{O}(B^3\mathbb{E}\mbox{u}^{3}).
+t^* = 2.94 + 1.96\phi\mathbb{E}\mbox{u} + 1.18\phi^2\mathbb{E}\mbox{u}^{2} + \mathcal{O}(\phi^3\mathbb{E}\mbox{u}^{3}).
 \end{equation}
@@
     \input{../figures/times2.pdf_tex}
-    \caption{Dimensional time-of-flight asymptotic estimates $t_f$ compared with experimental time-of-flight $t_b$.\label{fig:series_s_ds}}
+    \caption{Dimensional time-of-flight asymptotic estimates $t_c t_f$ compared with experimental time-of-flight $t_b$.\label{fig:times2}}
 \end{figure}
@@
 In all other cases image forces are much stronger than drag.
-The image forces themselves rapidly become small compared to Coulomb forces for drops with apoapses $\mbox{max}\left( y\right) \gtrapprox L$.
-Thus, it is reasonable to claim that for intermediate drops Coulomb force scales as inertia, and drag and image forces are small.
-The drop with largest $\mathbb{E}\mbox{u}$ in our dataset failed to escape the electric field as the escape condition $B \mathbb{E}\mbox{u} / 8\pi = 0.2 < 1$ was unsatisfied.
+The image forces themselves rapidly become small compared to Coulomb forces for drops with apoapses $\mbox{max}\left( y\right) \gtrsim L$.
+Thus, it is reasonable to claim that for intermediate drops Coulomb force scales with inertia, while drag and image forces are small.
+The drop with largest $\mathbb{E}\mbox{u}$ in our dataset failed to escape the electric field as the escape condition $\phi \mathbb{E}\mbox{u} / 8\pi = 0.2 < 1$ was unsatisfied.
 For this drop Equation \ref{time_improved} predicts that the drop will return to the substrate after 32 s, a period of free-fall which is lamentably well out of reach of a drop tower.
-However, such an experiment could possibly be performed aboard the ISS or in a parabolic flight.
+However, such an experiment could possibly be performed aboard the ISS or suborbital parabolic flights.
 \begin{figure}[!htb]
@@
 
+The covariance of $\mathbb{I}\mbox{g}$ with $\mathbb{E}\mbox{u}$ is shown in Figure \ref{fig:dnumbs}.
+Predictably, there is correlation between the dimensionless groups.
+We also see that $\mathbb{I}\mbox{g} < 1$ for all drops.
+Using an OLS regression, we find the model $\mathbb{I}\mbox{g} \sim (0.012 \pm 0.003) \mathbb{E}\mbox{u} + (0.212 \pm 0.036) $ with $R^2 =0.59$.
+\begin{figure}[htb]
+    \centering
+    \input{../figures/dnumbs.pgf}
+    \caption{Experimental covariance of $\mathbb{E}\mbox{u}$ and $\mathbb{I}\mbox{g}$.\label{fig:dnumbs}}
+\end{figure}
+
 We should note the influence of systematic error on our data.
-We assume that drops translate purely along the central axis of the electric field, but in practice, despite the improvement in surface charge density uniformity produced by corona charging, there are still local areas of especially high charge density, causing radial translation and changing $E$ not as well predicted by Equation \ref{e_field}.
-In principle, this kind of error should become small for drops which are far enough away from the charge distribution that the geometry of the charge distribution disappears and the electric field looks like that due to a point charge.
-However for low $\mathbb{E}\mbox{u}$ drops this error relatively increases.
-The primary sources of random error are the effect of contact line hysteresis on the drop initial velocity, and of the variance in the MLE parameter estimates.
+We assume that drops translate purely along the central axis of the electric field.
+In practice, despite the improvement in surface charge density uniformity produced by corona charging, there are still local areas of especially high charge density causing radial translation and changing $E$ not as well predicted by Equation \ref{e_field}.
+In principle, this kind of error should become small for drops that are far enough away from the charge distribution where the geometry of the charge distribution vanishes and the electric field looks like that due to a point charge.
+However, for low $\mathbb{E}\mbox{u}$ drops this error relatively increases.
+The primary sources of random error are the effect of contact line hysteresis on the drop initial velocity and of the variance in the MLE parameter estimates.
 
 \section{Suggestions for Future Directions}
-In 1-$g_0$, for Weber numbers $>$ 0.4, impact rebound behavior on a super-hydrophobic surface is normally dominated by damping from contact line hysteresis.
-However, for the low Bond and Ohnesorge numbers occurring in free-fall, the drop impact dynamics additionally include electrohydrodynamic surface wettability effects.
-To date there has been very little work done generally on drop impacts outside of two regimes: first, very low $\mathbb{R}\mbox{e}$ viscous drop spreading driven by capillary forces at the contact line, and second, impacts at `high' Weber numbers $\mathbb{W}\mbox{e} = \frac{\rho U^2 R_d}{\gamma}$, which is a ratio of drop inertia to surface tension.
-Of course even models for dynamic contact lines themselves in general remain controversial, even for ordinary spreading of liquids, despite decades of work in the area.
-
-If we naively neglect the dynamics of the contact line, the pertinent dimensionless groups for isothermal drop impacts are the Weber number $\mathbb{W}\mbox{e}$, the Ohnesorge number $\mathbb{O}\mbox{h} = \frac{\mu}{\sqrt{\rho \gamma R_d}}$, which is a ratio of viscous to inertial and surface tension forces, and the Bond number $\mathbb{B}\mbox{o}$ defined previously.
-In this case dynamics of spreading are characterized primarily by $\mathbb{W}\mbox{e}$ and $\mathbb{O}\mbox{h}$.
-The Weber number scales the driving force of the impact.
-In the more familiar case of high $\mathbb{W}\mbox{e}$ impacts the drop liquid bulk is driven radially outward by the impact induced pressure gradient, whereas in the case of small $\mathbb{W}\mbox{e}$ the liquid is forced outwards by capillary force at the contact line.
+In 1-$g_0$, for Weber numbers $\mathbb{W}\mbox{e} \equiv \rho U^2 R_d/\gamma >$ 0.4, impact rebound behavior on a superhydrophobic surface can be strongly influenced by damping from contact line hysteresis.
+For the low Bond and Ohnesorge numbers occurring in free-fall, the drop impact dynamics additionally include electrohydrodynamic surface wettability effects.
+To date there has been little work in general on drop impacts outside of two regimes: (1) very low $\mathbb{R}\mbox{e}$ viscous drop spreading driven by capillary forces at the contact line and (2) impacts at `high' Weber numbers.
+Models for dynamic contact lines in general remain controversial, even for ordinary spreading of liquids, despite decades of work in the area.
+
+If we naively neglect the contact line dynamics, the dimensionless groups for isothermal drop impacts are the Ohnesorge number $\mathbb{O}\mbox{h} = \frac{\mu}{\sqrt{\rho \gamma R_d}}$ which is a ratio of viscous to inertial and surface tension forces, the Weber number $\mathbb{W}\mbox{e}$, and the Bond number $\mathbb{B}\mbox{o}$ defined previously.
+The Weber number scales the driving force of drop spreading.
+In the well-studied case of high $\mathbb{W}\mbox{e}$ impacts the drop bulk is driven radially outward by the impact induced pressure gradient, whereas in the case of small $\mathbb{W}\mbox{e}$ the liquid is driven outwards by capillary force.
 The Ohnesorge number, by contrast, scales the force that resists spreading.
-For large $\mathbb{O}\mbox{h}$ the resistive force is viscous, whereas for low $\mathbb{O}\mbox{h}$ the force is inertia.
-Previous experimental work on low $\mathbb{O}\mbox{h}$, low $\mathbb{W}\mbox{e}$ impacts includes Schiaffino and Sonin's work\cite{schiaffino_molten_1997} on impacts of molten drops on cold surfaces.
-Mol\'{a}\u{c}ek and Bush\cite{molacek_quasi-static_2012}, Gopinath and Koch\cite{gopinath_collision_2002}, and Okamura\cite{okumura_water_2003} have developed simple analytical models of drop impacts at low $\mathbb{W}\mbox{e}$ and low $\mathbb{B}\mbox{o}$.
-All of these works show increasing dimensionless contact time $\tau$ as Weber number decreases, in opposition to the results of Richard and Qu\'{e}r\'{e} \cite{richard_surface_2002} which show experimentally that the contact time is approximately a constant $\tau \approx 2.6(\rho R^3_d/\sigma)^{1/2}$ at large $\mathbb{W}\mbox{e}$.
-Mol\'{a}\u{c}ek's work also shows that impact coefficients of restitution $C_R$ depend non-linearly on $\mathbb{B}\mbox{o}$.
-To date little experimental work has been done on low $\mathbb{B}\mbox{o}$ impacts as well.
-An exception is provided by Duvivier \emph{et al.}\cite{duvivier_drop_2012} who studied regimes of aqueous ferrofluid drop impacts on superhydrophobic substrates under the influence of an external magnetic field.
-
-We observe average drop impact $\mathbb{O}\mbox{h} \approx 2.18 \pm 0.36$, and  $\mathbb{W}\mbox{e} \approx 0.28 \pm 0.22$.
-Thus impact velocity plays little role in the spreading dynamics of the bounces, and viscous effects are important but do not dominate inertia.
+For large $\mathbb{O}\mbox{h}$ the resistive force is viscous, whereas for low $\mathbb{O}\mbox{h}$ the resistive force is inertia.
+Previous empirical work for low $\mathbb{O}\mbox{h}$ and low $\mathbb{W}\mbox{e}$ impacts includes thaat of Schiaffino and Sonin \cite{schiaffino_molten_1997} with wetting and non-wetting impacts of molten metal drops on cold surfaces.
+Mol\'{a}\u{c}ek and Bush \cite{molacek_quasi-static_2012}, Gopinath and Koch \cite{gopinath_collision_2002}, and Okamura \cite{okumura_water_2003} have all developed simple analytical models of drop impacts at low $\mathbb{W}\mbox{e}$ and low $\mathbb{B}\mbox{o}$.
+These works show increasing dimensionless contact time $\tau$ as Weber number decreases, in opposition to the results of Richard and Qu\'{e}r\'{e} \cite{richard_surface_2002} which show experimentally that the dimensionless contact time is approximately a constant $\tau \approx 2.6(\rho R^3_d/\sigma)^{1/2}$ with respect to $\mathbb{W}\mbox{e}$ at large $\mathbb{W}\mbox{e}$.
+Mol\'{a}\u{c}ek's work also shows that impact coefficients of restitution $C_r$ depend non-linearly on $\mathbb{B}\mbox{o}$.
+To date little experimental work has been performed on low $\mathbb{B}\mbox{o}$ impacts as well.
+An exception is provided by Duvivier \emph{et al.} \cite{duvivier_drop_2012} who studied regimes of aqueous ferrofluid drop impacts on superhydrophobic substrates under the influence of an external magnetic field.
+In this case the magnetic body force acts as an ersatz gravity.
+
+When the electro-drob bounce occurs, if the drop has enough time to return a non-wetting impact occurs on the charged substrate usually followed by rebound.
+We observe average drop impact $\mathbb{O}\mbox{h} \approx 2.18 \pm 0.36$ and  $\mathbb{W}\mbox{e} \approx 0.28 \pm 0.22$.
+Thus impact velocity plays little role in the spreading dynamics of the bounces and viscous effects are important but do not dominate inertia.
 Notably we observe underdamped oscillations of drop interfaces during impact.
-Access to such relatively low $\mathbb{O}\mbox{h}$, low $\mathbb{W}\mbox{e}$ drop impacts enabled by the low-gravity environment is an interesting possibility for new work on the basic science of drop impacts.
-There is also the intersection of this work with the burgeoning field of electrowetting on patterned surfaces and the interaction with drop impacts.
-Various authors\cite{bartolo_bouncing_2006, reyssat_bouncing_2006} have suggested that a wetting transition called the Fakir impalement occurs during impacts on patterned hydrophobic surfaces which depends on a critical pressure $p_c \sim \gamma h/l$ where $h/l$ is the pillar aspect ratio of the patterned surface.
-This pressure can result from fluid inertia in a high $\mathbb{W}\mbox{e}$ impact regime, or can result from an electrostatic pressure due to an external electric field, which is responsible for the irreversiblity that notoriously plagues static EWOD experiments.
-Thus, there is hope that electric fields can be leveraged to engineer solid-state surfaces which are tuneably wetting under drop impacts.
-This could motivate additional work in this area.
-
-Our preliminary results showing the influence of $\mathbb{W}\mbox{e}$ and electrostatic Bond number $\mathbb{B}\mbox{o}_e = \frac{\epsilon E_0^2 R_d}{\gamma} $ on drop impact dimensionless contact time $\tau$ and coefficient of restitution $C_R$ at $\mathbb{O}\mbox{h} \approx 2.2$ are shown in Figures \ref{fig:contact} and \ref{fig:E0}.
+Access to such relatively low $\mathbb{O}\mbox{h}$ and low $\mathbb{W}\mbox{e}$ drop impacts enabled by the low-gravity environment raises an interesting possibilities for new work on the basic science of drop impacts.
+This work also intersects the burgeoning field which spans the intersection of electrowetting on patterned surfaces and drop impacts.
+Various authors \cite{bartolo_bouncing_2006, reyssat_bouncing_2006} have suggested that a wetting transition called Fakir impalement can occur during impacts on patterned hydrophobic surfaces if a certain critical pressure $p_c \sim \gamma h/l$ is exceeded, where $h/l$ is the pillar aspect ratio of the patterned surface.
+This pressure can result from fluid inertia in a high $\mathbb{W}\mbox{e}$ impact regime, or can result from an electrostatic pressure due to an external electric field.
+The latter case is responsible for the irreversiblity that notoriously plagues static EWOD experiments.
+There is hope that additional work in this area could produce engineered surfaces that are tuneably wetting under drop impacts by leveraging electrostatic forces.
+
+Our preliminary results showing the influence of $\mathbb{W}\mbox{e}$ and electrostatic Bond number $\mathbb{B}\mbox{o}_e = \frac{\epsilon E_0^2 R_d}{\gamma} $ on drop impact dimensionless contact time $\tau$ and coefficient of restitution $C_r$ at $\mathbb{O}\mbox{h} \approx 2.2$ are shown in Figures \ref{fig:contact} and \ref{fig:restitution}.
 
@@
     \centering
-    \input{../figures/contact.pgf}
-    \caption{Dimensionless contact time $t_b/\tau$ compared with impact $\mathbb{W}\mbox{e}$ and $\mathbb{B}\mbox{o}_e$.\label{fig:contact}}
+    \input{../figures/contact2.pgf}
+    \caption{Dimensionless contact time $t_j/\tau$ compared with impact $\mathbb{W}\mbox{e}$ and $\mathbb{B}\mbox{o}_e$.\label{fig:contact}}
 \end{figure}
@@
     \input{../figures/restitution.pgf}
-    \caption{Impact coefficient of restitution compared with impact $\mathbb{W}\mbox{e}$ and $\mathbb{B}\mbox{o}_e$.\label{fig:restitution}}
+    \caption{Impact coefficient of restitution $C_r$ compared with impact $\mathbb{W}\mbox{e}$ and $\mathbb{B}\mbox{o}_e$.\label{fig:restitution}}
 \end{figure}
@@
 \section{Conclusion}
-This work might have stopped quite early had we maintained our focus on spontaneous drop jump, and the key result would simply have been a means of mitigation for this troublesome electro-bounce phenomenon.
+This work might have stopped early had we maintained our focus on spontaneous drop jump with the key result being simply a means of mitigation for this troublesome electro-bounce phenomenon.
 In some sense this is quite easy to do as there are a plethora of commercially available static charge neutralization tools aimed at ESD control applications.
 In a low-gravity setting, if we wish to rid ourselves of these electrostatic phenomenon we need simply to neutralize dielectric surfaces in the vicinity of our controlled environment.
+A recipe for accomplishing this is provided in Appendix \ref{sec.mitigation}.
 Of course there are limitations to this approach.
@@
 Additionally, there are cases where we do not control the environment for practical reasons.
-For example, aboard the ISS crew clothing can easily become electrostatically charged, just as clothing does on Earth, and if this  charge distribution is in the vicinity of Rayleigh-Plateau breakup of a fluid, as might happen when squirting water from a drink bag, then electrophoresis of the drops will occur after the fashion of this work.
+For example, aboard the ISS crew clothing can easily become electrostatically charged just as clothing does on Earth.
+If this  charge distribution is in the vicinity of Rayleigh-Plateau breakup of a fluid, as might happen when squirting water from a drink bag, then electrophoresis of the drops will occur after the fashion of this work.
 
@@
 Let us say we desire to capture drops in a pre-stage to the compressor of a Rankine cycle space nuclear power system.
-We must actively capture the drops because we require a single-phase saturated vapor at the compressor inlet do not wish to superheat or interrupt the flow.
+We must actively capture the drops because we require a single-phase saturated vapor at the compressor inlet but do not wish to superheat or interrupt the flow.
 The drops are polydisperse and thus have a distribution of masses $m$ and velocities $U_0$.
 The working fluid is a mixture of lithium and cesium with $\rho_l = 452$ kg/m$^3$.
-The lithium droplets have high surface tension even at high temperatures encountered in this power cycle, and an insulated electrode can possibly be made hydrophobic by means of a high temperature coating such that the drops rebound rigidly without wetting the surface of the precipitator.
+The lithium droplets have high surface tension even at the high temperatures encountered in this power cycle, and an insulated electrode can possibly be made hydrophobic by means of a high temperature coating such that the drops rebound rigidly without wetting the surface of the precipitator.
 The lithium drops can also be treated as ideal conductors, and we assume the droplet velocity vector is normal to the precipitator electrode as in our work.
-The simple 1-dimensional theory of this thesis assumes the electric field due to a square charged dielectric, but other electric fields, and electrode geometries are possible or desirable for the designer.
+The simple 1-dimensional theory of this thesis assumes the electric field due to a square charged dielectric, but other electric fields and electrode geometries are possible or desirable for the designer.
 The scaling used in this work will oftentimes remain valid as electric fields for numerous geometries contain the same near-field constant and far-field $1/y^2$ limits.
-In other cases, especially with more complicated geometries, the electric field will need to be determined analytically or numerically.
+In other cases, particularly cases with more complicated geometries, the electric field will need to be determined analytically or numerically.
 From the form of the electrostatic Euler number
@@
 \]
-we note that this dimensionless group can also be thought of as a ratio of energies: the kinetic energy $m U_0^2$ in the numerator, and the electrostatic potential energy $q E_0 R_d$ in the denominator.
-We also note that although the velocity $U = U(t,y)$ and electric field $E = E(t,y)$ are variables, if the system is conservative system this ratio of energies is constant.
-If an engineering requirement is to capture 95\% the drops entering the compressor to mitigate damage to the turbine blades, then we can perform an initial sizing of an electrostatic drop precipitator using the scaling approach of this thesis.
-Let us say that two standard deviations of the drop population posses kinetic energy less than $8 \times 10^{-3}$ J per drop, and that the design constraints for the electrode are such that $E_0=3$ kV/m, and the electrode is 10 cm square.
+we note that this dimensionless group can also be thought of as a ratio of energies: the kinetic energy $m U_0^2$ in the numerator and the electrostatic potential energy $q E_0 R_d$ in the denominator.
+If the drops enter the system at distance $H$ from the surface then the electrostatic potential energy is better described by $q E_0 H$ if the electric field is assumed to behave like $1/y^2$.
+We also note that although the velocity $U = U(t,y)$ and electric field $E = E(t,y)$ are variables, if the system is conservative this ratio of energies remains constant.
+If an engineering requirement is to capture 95\% the drops entering the compressor to mitigate damage to the turbine blades we can perform an initial sizing of an electrostatic drop precipitator using the scaling approach of this thesis.
+Let us say that two standard deviations of the drop population posses kinetic energy less than $8 \times 10^{-3}$ J per drop with average radius $R_d = 1$ mm.
+The drops enter the system at $H=4$ cm, and the design constraints for the electrode are such that $E_0=3$ kV/m and that the electrode is 10 cm square.
 To satisfy Equation \ref{escape} requires
 \[
-2\rho E_0 L^2 \frac{q}{m} > mU_0^2.
+\frac{8 \pi}{3} \frac{q}{m} \rho E_0 R_d H L^2  = mU_0^2.
 \]
@@
 The typical capacitor rise time of the plates is measured to be 1.4 s, thus to make the most economical use of the brief window a low-gravity a weighted spring-loaded switch is set by hand prior to the drop to close the high-voltage circuit, but which passively safes the system at the resumption of 1-$g_0$ conditions in the tower.
-From a survey of literature we suppose the drop free charge, if it is indeed arises by contact with PTFE, to be some function of the drop volume and the residence time on the superhydrophobic surface.
+We suppose the drop free charge, if it is indeed arises by contact with PTFE, to be some function of the drop volume and the residence time on the superhydrophobic surface.
 However, sweeping though drop volumes over a series of drop tower experiments we find little correlation between drop volume  and free drop charge.
@@
 Following this a orthogonal array $3^2$ factorial design experiment with two replicates was conducted to test the effect of varying drop volume and surface stay time on free charge at the time of jumping.
-It was hypothesized in accordance with previous studies [ref], that free charge would increase for levels of both factors.
-ANOVA analysis in \emph{R} of the linear multiple regression model for the data set indicates that neither drop volume ($p=0.105$), nor surface stay time ($p=0.358$) is significant at the 95\% confidence level.
-The overall model F-statistics (2.177 in 2 and 13 degrees of freedom), and coefficients of determination ($r^2 = 0.2509$) indicate that the linear model neither fits the data particularly well, nor does it offer an improvement over the mean model.
-The mean charge was determined to be positive $2.3 \times 10^{-11}$ C, with a standard deviation of $1.8 \times 10^{-11}$ C.
+It was hypothesized that free charge would increase for levels of both factors.
+ANOVA analysis using \verb|pandas| of the linear multiple regression model $q \sim a*V_d + b*t_s$, where $a$, $b$ are model fitting coefficients, for the data set indicates that neither drop volume $V_d$ ($p=0.178$), nor surface stay time $t_s$ ($p=0.939$) is significant at the 95\% confidence level.
+The overall model F-statistics (1.001 in 2 and 14 degrees of freedom), and coefficients of determination ($r^2 = 0.125$) indicate that the linear model neither fits the data particularly well, nor does it offer an improvement over the mean model.
+The mean charge was thus determined to be positive $5.3 \times 10^{-12}$ C, with a standard deviation of $4.7 \times 10^{-12}$ C.
+
+\chapter{Charge Mitigation}
+\label{sec.mitigation}
 

### 2018-04-05 doc/manuscript/manuscript.tex
many minor edits its to manuscript

@@
 However, we do not observe any escapes in our dataset.
-With an eye towards engineering applications we consider the results in light of the so-called low-gravity phase separation problem with a worked example problem.
+With an eye towards engineering applications we consider the results in light of the so-called low-gravity phase separation problem with a worked example.
 
@@
 As with capillary forces, electrostatic forces have a multitude of applications as substitutes for gravity.
-Electrohydrodynamic (EHD) body forces have been suggested to combat thermal stratification of propellants under low-g conditions where bouyancy induced natural convection is very small \cite{blackmon_collection_1965}.
+Electrohydrodynamic (EHD) body forces have been suggested to combat thermal stratification of propellants under low-g conditions where buoyancy induced natural convection is very small \cite{blackmon_collection_1965}.
 In this case electro-convection is an analog of natural convection due to a fluid temperature dependent dielectric permittivity gradient (as opposed to a fluid density gradient) in the presence of an electric body force field.
 The study also suggested applications in cryogenic tank vent screening and in reducing heat transfer to cryogenic propellants (and thus boiloff losses) by dielectrophoretically positioning ullage vapors around the tank walls as a thermal barrier.
-EHD forces have been studied for enhancing boiling heat transfer by promotion of bubble detachment and prevention of dryout, again as an ersatz bouyancy \cite{snyder_dielectrophoresis_2001, di_marco_influence_2003, marco_use_2012}.
+EHD forces have been studied for enhancing boiling heat transfer by promotion of bubble detachment and prevention of dryout, again as an ersatz buoyancy \cite{snyder_dielectrophoresis_2001, di_marco_influence_2003, marco_use_2012}.
 EHD heat pipes, which substitute an electrode structure for the capillary wicking structure of a conventional thermocapillary heat pipe can postpone the wicking limit \cite{jones_electrohydrodynamic_1973}.
@@
 Dielectrophoretic settling of cryogenic propellants, in both total and partial communication Propellant Management Device (PMD) configurations, has been studied analytically in both static \cite{hurwitz_electrohydrodynamic_1966} and dynamic cases \cite{koval_dynamics_1967}, and in drop tower experiments \cite{fax_dielectrophoretic_1969}.
-EHD forces have also been applied to the low-g slosh baffling problem \cite{boretz_orbital_1970, petrash_use_1968, hurwitz_dielectrophoretic_1968}, and studied extensively for the mitigation of vapor pullthrough during tank draining and concomittent minimization of propellant residuals at burnout in a series of experiments at the NASA Lewis (now Glenn) Research Center 2.2 s drop tower facillity \cite{berenyi_dielectrophoretic_1970}.
+EHD forces have also been applied to the low-g slosh baffling problem \cite{boretz_orbital_1970, petrash_use_1968, hurwitz_dielectrophoretic_1968}, and studied extensively for the mitigation of vapor pullthrough during tank draining and concomittent minimization of propellant residuals at burnout in a series of experiments at the NASA Lewis (now Glenn) Research Center 2.2 s drop tower facility \cite{berenyi_dielectrophoretic_1970}.
 
 \section{Spontaneous Drop Jump}
-Low-gravity phase separation, drop dynamics, and the dynamics and applications of the so-called spontaneous drop or puddle jump, is an active area of study at the Portland State University Dryden Drop Tower labratory (DDT).
+Low-gravity phase separation, drop dynamics, and the dynamics and applications of the so-called spontaneous drop or puddle jump, is an active area of study at the Portland State University Dryden Drop Tower laboratory (DDT).
 When a nonwetting, gravity-dominated sessile drop (e.g.
 a puddle), which is initially at rest on a surface in the Cassie-Baxter state suddenly undergoes a large step reduction in $\mathbb{B}\mbox{o}$ it will spontaneously jump away from the surface.
-The Cassie-Baxter state, sometimes also known as the Fakir state, is a metastable heterogenously non-wetting state on a textured surface characterized by the existence of a vapor-layer that seperates roughness features of the surface from the bottom of the drop.
+The Cassie-Baxter state, sometimes also known as the Fakir state, is a metastable heterogenously non-wetting state on a textured surface characterized by the existence of a vapor-layer that separates roughness features of the surface from the bottom of the drop.
 The spontaneous drop jump was first observed experimentally in the Soviet Union by Kirko \emph{et al.} \cite{kirko_phenomenon_1970} in 1970 for drops of mercury in hydrochloric acid, and later by Wollman \emph{et al.} in 2016 for water drops in air in a set of experiments conducted using drop towers \cite{wollman_more_2016}.
@@
 \[KE_2 = SE_2 - SE_1 = [(\gamma A)_{gl} + (\gamma A)_{sg}]_2 - [(\gamma A)_{ls} + (\gamma A)_{gl} + (\gamma A)_{sg}]_1, \]
-where $KE$ and $SE$ are the respective kinetic and surface energies, $A$ is the surface area, the subscripts $1$ and $2$ denote the intial 1-$g_0$, and low-g states, and the subscripts ${gl}$, ${sg}$, and ${ls}$ denote the gas-liquid, solid-gas and liquid-solid interfaces repectively.
-The motive force is due to the inertia of internal flows which occur as the interface deflects under the suddenely lessened $\mathbb{B}\mbox{o}$.
+where $KE$ and $SE$ are the respective kinetic and surface energies, $A$ is the surface area, the subscripts $1$ and $2$ denote the intial 1-$g_0$, and low-g states, and the subscripts ${gl}$, ${sg}$, and ${ls}$ denote the gas-liquid, solid-gas and liquid-solid interfaces respectively.
+The motive force is due to the inertia of internal flows which occur as the interface deflects under the suddenly lessened $\mathbb{B}\mbox{o}$.
 The characteristic time scale of the rolling up scales as $t_j \sim (\rho V_d/\sigma)^{1/2}$ \cite{attari_puddle_2016}, which resembles the contact time, $\tau \approx 2.6(\rho R^3_d/\sigma)^{1/2}$ presented by Richard \emph{et al.} in 2002 for the related problem of drops impacting hydrophobic surfaces in 1-$g_0$ \cite{richard_surface_2002}.
@@
 
-There are several possible origins of the electric charge that are ultimately responsible for this phenonenon.
+There are several possible origins of the electric charge that are ultimately responsible for this phenomenon.
 It is well known that water acquires positive free charge when in contact with certain polymers, especially polytetrafluoroethylene (PTFE) \cite{langmuir_surface_1938}, through a process called contact charging.
 PTFE, on the other hand, tends to readily acquire negative charge by contact with water.
-The superhydrophobic surfaces used in the spontanous drop jump experiments have thin (nanometric) PTFE coatings, and we observe that it is extremely easy to produce significant surface potentials $\varphi_s \sim$ 100-500 V by simply flowing streams of distilled water over them.
+The superhydrophobic surfaces used in the spontaneous drop jump experiments have thin (nanometric) PTFE coatings, and we observe that it is extremely easy to produce significant surface potentials $\varphi_s \sim$ 100-500 V by simply flowing streams of distilled water over them.
 A study of this water on PTFE contact charging phenomenon was conducted by Yatsuzuka \emph{et al.} \cite{yatsuzuka_electrification_1994}, who suggest that this process results from formation of an electrical double layer driven by selective adsorption of ($\mbox{OH}^-$) ions at the polymer surface; other recent work strongly supports this hypothesis \cite{beattie_intrinsic_2006, strazdaite_water_2015}.
@@
 Another mechanism for the drop charge is field-induced charging.
-Field-induced charging occurs due to physical breakup of a conductor having a field-induced dipole (e.g., a physical seperation of charge).
+Field-induced charging occurs due to physical breakup of a conductor having a field-induced dipole (e.g., a physical separation of charge).
 In our work this might occur when a drop is deposited on the charged surface by a grounded syringe.
@@
 External surfaces of spacecraft tend to become charged with time due to the space environment itself.
-Surface charging largely occurs due to low energy electrons (3-50 keV) which do not penetrate the surface of the spacecraft external stucture \cite{czepiela_charging_1997}.
+Surface charging largely occurs due to low energy electrons (3-50 keV) which do not penetrate the surface of the spacecraft external structure \cite{czepiela_charging_1997}.
 The ultimate sources of these charges are trapped charged particles of the van Allen radiation belts, galactic cosmic rays, and the solar wind.
@@
 As previously noted, robust phase separation is critical to high reliability multiphase systems used in thermal control and life support.
-Active solid-state phase seperation for life support multiphase flows, especially high void-fraction droplet disperse flows is a possible application of this work.
+Active solid-state phase separation for life support multiphase flows, especially high void-fraction droplet disperse flows is a possible application of this work.
 Such flows are encountered in dish washing, laundry, waste solids drying, food processing, the Sabatier CO$_2$ reaction, and possibly in vapor-compression cycle condensers.
-Phase seperation for other disperse droplet flows include electrostatic droplet seperators for high-efficiency Rankine-cycle turbines, which require a droplet-free vapor phase entering the turbine, but where conventional superheat approaches come with severe mass penalties \cite{unterberg_zero_1962}.
+Phase separation for other disperse droplet flows include electrostatic droplet separators for high-efficiency Rankine-cycle turbines, which require a droplet-free vapor phase entering the turbine, but where conventional superheat approaches come with severe mass penalties \cite{unterberg_zero_1962}.
 More speculatively, results of this work could be applied in high temperature liquid droplet radiators with electrostatic collection \cite{white_liquid_1987}.
@@
 This approach has since been related back to the force density by the volumetric integration of the force density with the substitution of a Taylor series expansion of $\mathbf{E}$ in the limit of a small radial gradient of the field within the dielectric sphere \cite{wang_general_1997}.
-The DEP force is related to the induced or permanent dipole moment of polarizable media which has a tendency to align the dipole with the electric field.
+The DEP force arises due to the induced or permanent dipole moment of polarizable media which has a tendency to align the dipole with the electric field.
 If there is a gradient in the field then for a finite separation of charge, one end of the dipole will feel a stronger electric field than the other resulting in a net force.
@@
 \end{equation} 
-where $\mathbf{P} = \left(\kappa_1 - 1 \right) \epsilon_0 \mathbf{E} = \chi_e \epsilon_0 \mathbf{E}$ is the polarization moment, $R_d$ is the particle radius, $\kappa_1 = \frac{\epsilon_1}{\epsilon_0}$ is the relative dielectric constant of the air host fluid, and $\chi_e = \kappa_1 - 1$ is the electric susceptibility of the host fluid.
+where $\mathbf{P} = \left(\kappa_a - 1 \right) \epsilon_0 \mathbf{E} = \chi_e \epsilon_0 \mathbf{E}$ is the polarization moment, $R_d$ is the particle radius, $\kappa_a = \frac{\epsilon_a}{\epsilon_0}$ is the relative dielectric constant of the air host fluid, and $\chi_e = \kappa_a - 1$ is the electric susceptibility of the host fluid.
 The force felt by the dipole is
@@
 \mathbf{F}_{DEP} &=& \left( \mathbf{P}_e \cdot \nabla \right) \mathbf{E} \nonumber \\
-&=& 2 \pi R_d^3 \epsilon K \nabla E^2,
+&=& 2 \pi R_d^3 \kappa_w \epsilon_0 K \nabla E^2,
 \end{eqnarray}
-where $\mathbf{P}_e=(\kappa_2 - \kappa_1)\epsilon_0 \mathbf{E}$ is the excess polarization and $\kappa_2$ is the relative dielectric constant of the water particle.
-Here it is convenient to use the simplifying shorthand $K = \frac{\kappa_2 - \kappa_1}{\kappa_2 + 2 \kappa_1}$, known as the Clausius-Mossotti factor.
+where $\mathbf{P}_e=(\kappa_w - \kappa_a)\epsilon_0 \mathbf{E}$ is the excess polarization and $\kappa_w$ is the relative dielectric constant of the water particle.
+Here it is convenient to use the simplifying shorthand $K = \frac{\kappa_w - \kappa_a}{\kappa_w + 2 \kappa_a}$, known as the Clausius-Mossotti factor.
 In cases where $K <$ 0, or $K>$ 0 the particle will be either repelled or attracted to regions of strong field.
-In our experiment, choosing the relative dielectric constants $\kappa_1 \approx$ 1 and $\kappa_2 \approx$ 80, we estimate $K \approx$ 0.96.
+In our experiment, choosing the relative dielectric constants $\kappa_a \approx$ 1 and $\kappa_w \approx$ 80, we estimate $K \approx$ 0.96.
 It is important to note that the equivalent dipole approximation critically requires an assumption of small physical scale of the particle relative to the length scale of nonuniformity of the field, which in this case we take to be the length of the charged superhydrophobic surface, $L =$ 25 mm $\gg R_d \approx$ 2 mm.
@@
 The polarization bound charge in the dielectric will be of the opposite sign of the free drop charge and thus there will be a force of attraction.
-This so-called image force is a correction to the Coulomb force due to the external electric field only, and can be found by a Green's Function solution to Laplace's equation for the electric field called the `method of images' \cite{david_j._griffiths_introduction_1999}.
+This so-called image force is a correction to the Coulomb force due to the external electric field only, and can be found by a Green's Function solution of Laplace's equation for the electric field called the `method of images' \cite{david_j._griffiths_introduction_1999}.
 This resulting image force $\mathbf{F}_I$ is given by
@@
  \mathbf{F}_E &=& q \mathbf{E} + \mathbf{F}_{DEP} + \mathbf{F}_I \\
- &=& q \mathbf{E} + \frac{k q^2}{16 \pi \epsilon_0 } y^{-2} \hat{\mathbf{j}} + 2 \pi R_d^3 \kappa_1 \epsilon_0 K \nabla E^2, 
+ &=& q \mathbf{E} + \frac{k q^2}{16 \pi \epsilon_0 } y^{-2} \hat{\mathbf{j}} + 2 \pi R_d^3 \kappa_w \epsilon_0 K \nabla E^2, 
 \end{eqnarray*}
@@
  \label{gov_eqn_subs}
-m y'' = - \frac{1}{2} C_D \rho A {y'}^2 - q E - \frac{k q^2}{16 \pi \epsilon_0} y^{-2}- 2 \pi R_d^3 \kappa_1 \epsilon_0 K \nabla E^2,
+m y'' = - \frac{1}{2} C_D \rho A {y'}^2 - q E - \frac{k q^2}{16 \pi \epsilon_0} y^{-2}- 2 \pi R_d^3 \kappa_w \epsilon_0 K \nabla E^2,
 \end{equation}
@@
 \begin{eqnarray}
-\frac{ \kappa_2 \epsilon_0 K R_d^2 E_0}{q} \ll 1. \nonumber
+\frac{ \kappa_w \epsilon_0 K R_d^2 E_0}{q} \ll 1. \nonumber
 \end{eqnarray}
@@
 If we consider the charged dielectric surface of our experiments to be a square sheet of charge lying in the $xz$-plane with width $L$, the symmetry of the problem happily lets us obtain the $y$-component of the electric field $\mathbf{E}$ by direct integration.
-In particular, it is easy to constuct the electric field due to a finite plane of charge by superposition of the electric fields of a series of line charges.
+In particular, it is easy to construct the electric field due to a finite plane of charge by superposition of the electric fields of a series of line charges.
 By symmetry, the electric field points along the $y$-axis; for a point along the $y$-axis the position vector is $\mathbf{r} = \left( x^2 + y^2 \right)^{1/2} \hat{\mathbf{r}}$ to the center of a line charge in the $xz$-plane.
@@
 E \approx \frac{\sigma}{4 \pi \epsilon_0} = E_0,
-,\end{equation}
+\end{equation}
 where $E_0$ is the characteristic electric field given by $E_0 = \frac{\sigma}{4 \pi \epsilon_0}$.
@@
 
-By substitution of \ref{regular_pert} and its derivatives into \ref{pi_terms}, and equating terms by order we first find the $\mathcal{O}(1)$ unperturbed solution
+By substitution of Equation \ref{regular_pert} and its derivatives into \ref{pi_terms}, and equating terms by order we first find the $\mathcal{O}(1)$ unperturbed solution
 \[{y^*_{0}}{\left ({t^*} \right )} = {t^*} + \frac{{t^*}^{2}}{2} \left(-1 - \mathbb{I}\mbox{g}\right). \]
@@
 In the limit of small $\mathbb{I}\mbox{m}$ the trajectories collapse to the $\mathcal{O}(1)$ solution regardless of the electrostatic Euler number.
+Trajectories with $\mathbb{E}\mbox{u} \leq 0.1$ are essentially coincident given the scale of the axes used here.
 In principle there is some coupling between $\mathbb{E}\mbox{u}$ and $\mathbb{I}\mbox{g}$; notably this relationship does not depend on the electric field $E_0$ but on a charge to mass ratio.
@@
 \[ m u' = - \frac{q E_0 y_c^2}{y^2}, \]
-where $u = \frac{d y}{d t}$ is the drop velocity. Integrating between the respective limits we find
-\[m \int^{u(y)}_{U_0} u du = -q E_0 y_c^2 \int^y_{R_d} \frac{dy}{y^2} ,\]
-which has the solution
+where $u = \frac{d y}{d t}$ is the drop velocity. This has the solution
 \[ u(y) = \pm U_0 \left[1 + \frac{2q E_0 y_c^2}{m U_0^2} \left( \frac{1}{y} - \frac{1}{R_d} \right) \right]^{1/2}.
@@
 For this reason electrets are thought of as electrostatic analogs to permanent magnets.
-The name \emph{electret} itself is a portmantau to that effect conjured by Heaviside in 1892 \cite{heaviside_electrical_2011}.
+The name \emph{electret} itself is a portmanteau to that effect conjured by Heaviside in 1892 \cite{heaviside_electrical_2011}.
 Typical commercial electrets are PTFE films on the order of 10-50 $\mu$m thick with the charge being primarily real surface charge.
@@
 A contour plot of the Furmidge model is provided in Figure \ref{fig:hysteresis}.
-The contact angle for water on smooth PTFE layer is $\approx 115^{\circ}$ and is further enhanced by an air layer maintained in the underlying roughness length scales of the surface.
+The contact angle for water on smooth PTFE is $\approx 115^{\circ}$ and is further enhanced by an air layer maintained in the underlying roughness length scales of the surface.
 We use a laser-etched pillared geometry with pillar heights $\sim \hspace{-1mm} 775$ $\mu$m, widths $\sim \hspace{-1mm} 70$ $\mu$m, and pitch $\sim \hspace{-1mm} 100$ $\mu$m.
@@
 This is partly accomplished by grounding the fieldmeter and by placing the dielectric sample on a grounded conductive plate backing.
-In this case the surface charge density is determined from $\sigma = \frac{\varphi_s \kappa \epsilon_0}{l},$ where $l$ is the thickness of the dielectric surface.
+In this case the surface charge density is determined from $\sigma = \varphi_s \kappa \epsilon_0/l,$ where $l$ is the thickness of the dielectric surface.
 The measured surface voltage is a function of position away from the charged dielectric.
 In most cases this function is relatively constant at a distance of about 1-2 cm away from the surface though we note that there is some measurement error in surface voltage due to small mispositioning of the electrostatic fieldmeter, say by $\pm$1 mm.
-The relative dielectric constant of the PMMA sheet is measured by using a 65$\times$65 mm polished aluminum parallel plate capacitor with $C = \kappa \epsilon_0 \frac{A}{l}$ where $C$ is the capacitance, and $A$ is the sheet area.
+The relative dielectric constant of the PMMA sheet is measured by using a 65$\times$65 mm polished aluminum parallel plate capacitor with $C = \kappa \epsilon_0 A/l$, where $C$ is the capacitance, and $A$ is the sheet area.
 Measuring the capacitance with 3 sample thicknesses using a GenRad 1657 RLC Digibridge, we find the relative permittivity to be $\kappa = 3.5 \pm 0.4$.
@@
 For an example case of a surface with relative permittivity $\kappa = 3.5$ and bulk resistivity $\rho = 1.6 \times (10^{16})$ $\Omega$cm such as with the case of a 2.8 mm PMMA sheet, then the time constant $\tau = \kappa \epsilon_0 \rho$ is approximately 5000 s, which is significantly longer than the typical time period for a drop tower experiment.
-External charge decay mechanisms include compensation by envonmental ionic species.
-The relative magnitudes of these charge transport mechanisms, and therfore the stability of the electret, vary drastically depending on the initial surface potential, material properties, environment, and charging method.
+External charge decay mechanisms include compensation by environmental ionic species.
+The relative magnitudes of these charge transport mechanisms, and therefore the stability of the electret, vary drastically depending on the initial surface potential, material properties, environment, and charging method.
 In the case of unshielded electrets compensation by atmospheric ions is significant \cite{perlman_electrets_1973}.
 Because environmental convection will tend to  maintain a gradient of these ions, sealing an electret in a container from the atmosphere will effectively halt this decay mechanism.
-Atmospheric humidity and water drop condensation can also significantly increase charge decay, presumably by reducing the surface resistence \cite{haenen_characteristic_1975}.
+Atmospheric humidity and water drop condensation can also significantly increase charge decay, presumably by reducing the surface resistance \cite{haenen_characteristic_1975}.
 Examples of this decay can be seen in Figure \ref{fig:charge_decay} for differing numbers of dielectric lamina used in this experiment.
@@
 Trajectories are captured using the particle tracking module in Fiji \cite{schindelin_fiji:_2012}, a derivative of the popular ImageJ \cite{schneider_nih_2012} package for scientific image analysis.
-The series is stabilized to remove the effect of drop transients from the kinetmatic data \cite{li_image_2008}.
+The series is stabilized to remove the effect of drop transients from the kinematic data \cite{li_image_2008}.
 The series of still images is cropped and the low-entropy pixels are removed using a built-in rolling ball algorithm.
@@
 These dimensionless numbers depend on physical properties not all of which are easily measured by experiment.
-Drop free charge $q$ in particular could in principle be directly measured by collecting the charged drops in a faraday cup under low-g and measuring the change in capacitance of the cup using a high input-resistance electrometer.
+Drop free charge $q$ in particular could in principle be directly measured by collecting the charged drops in a Faraday cup under low-g and measuring the change in capacitance of the cup using a high input-resistance electrometer.
 But this method is burdensome to apply in practice in a drop tower.
@@
 The posterior probability density function (PDF) $\mbox{prob}(X|D, I)$ is ultimately what we wish to estimate, the prior PDF $\mbox{prob}(X|I)$ reflects our knowledge of the system, and the evidence $\mbox{prob}(D|I)$ is the likelihood of the data based on our knowledge.
-We also note that since it only makes sense to compare the conditional PDF's for the same data we can ignore the denominator.
+We also note that since it only makes sense to compare the conditional PDFs for the same data we can ignore the denominator.
 We further note that the prior $\mbox{prob}(X|I)$ is fixed before our observations and so can be treated as invariant to our problem.
@@
 
-We use a gradient-free direct-search Nelder-Mead \cite{nelder_simplex_1965} algorithem implemented in \verb|scipy.optimize|.
+We use a gradient-free direct-search Nelder-Mead \cite{nelder_simplex_1965} algorithm implemented in \verb|scipy.optimize|.
 Nelder-Mead is relatively robust to noise and is thrifty with our computationally expensive function-calls.
 Nelder-Mead, sometimes called simplex-search or downhill-simplex, is a heuristic search method with no guarantee of optimal solutions.
-It nonetheless is a well-established and widely used algorithem.
+It nonetheless is a well-established and widely used algorithm.
 Nelder-Mead is based on the concept of an $N$-simplex, which generalizes a triangle into higher dimensions as a polytrope of $N + 1$ vertices in $N$ dimensions.
@@
 As is typical with Nelder-Mead much of the improvement in $\chi^2$ is realized in the first few iterations.
-Overall the rate of convergence is sub-linear, which is to be expected for non-linear constrained problems using an hueristic algorithem.
+Overall the rate of convergence is sub-linear, which is to be expected for non-linear constrained problems using an heuristic algorithm.
 Results of the parameter estimation are shown in Figures \ref{fig:trajectories} and \ref{fig:inverse_problem}.
@@
 We use an exterior penalty function as a simple way of converting converting the constrained problem into an unconstrained one.
-These are especially useful in cases where the constraints are not `hard' in the sense that they need to be satisfied precisely.
+These are especially useful in cases where the constraints are not `hard' in the sense that they need to be precisely satisfied.
 General penalty functions, which are sequential unconstrained minimization techniques, reformulate the general constrained problem as the pseudo-objective function given by
@@
 
-As with penalty function approaches generally, the exterior penalty function has the drawback of the possibility of the objective function being undefined outside of the set of feasible solutions.
+As with penalty function approaches generally, the exterior penalty function has the drawback of the objective function possibly being undefined outside of the set of feasible solutions.
 Additionally, by naively encouraging feasibility of the solution using large values of the penalty parameter $r_p$ we will tend to ill-condition the unconstrained formulation of the problem, though in our implementation the preconditioning tends to make the pseudo-objective function less and less sensitive to the constraints as the likelihood is approaches a maximum.
@@
 \[ \mbox{cond} (\mathbf{H}) = \frac{\mbox{max}(\mbox{eig}(\mathbf{H}))}{\mbox{min}(\mbox{eig}(\mathbf{H}))}, \]
-to make a qualitative assesment of the stability of the problem.
+to make a qualitative assessment of the stability of the problem.
 Among our parameter estimate MLE optima we find large typical condition numbers $\sim \mathcal{O}(10^{27})$.
-In fact, in many cases our Hessian is not negative definite or invertible at the minmia $\mathbf{x}_0$, which implies unphysical negative values of the variances.
+In fact, in many cases our Hessian is not negative definite or invertible at the minmima $\mathbf{x}_0$, which implies unphysical negative values of the variances.
 These issues indicate the problem is extremely ill-conditioned near the minima $\mathbf{x_0}$.
-Given that the parameter estimates are highly co-linear, it is unsuprising that the Hessian matrix is near-singular and its inversion is either impossible or involves significant numerical error.
+Given that the parameter estimates are highly co-linear, it is unsurprising that the Hessian matrix is near-singular and its inversion is either impossible or involves significant numerical error.
 A posteriori verification of the results is crucial to bound the identifiability of the parameter estimation problem, but this remains as future work.
-Several sources suggest senstivity analysis of the parameter estimates by generation of synthetic Monte Carlo data sets as a means of establishing identifiability \cite{bevington_data_1969, jaqaman_linking_2006}.
+Several sources suggest sensitivity analysis of the parameter estimates by generation of synthetic Monte Carlo data sets as a means of establishing identifiability \cite{bevington_data_1969, jaqaman_linking_2006}.
 
@@
 The dielectrophoretic force plays a small role when drops have net charge in a DC field.
-The condition to neglect the DEP force was satisfied for all experiments in the dataset with typical values of the condition number $\kappa_2 \epsilon_0 K R_d^2 E_0/q \approx \mathcal{O}(10^{-6})$.
+The condition to neglect the DEP force was satisfied for all experiments in the dataset with typical values of the condition number $\kappa_w \epsilon_0 K R_d^2 E_0/q \approx \mathcal{O}(10^{-6})$.
 In the non-dimensional trajectories with short-time scaling shown in Figure \ref{fig:series_s_ds}, we see that the scaled trajectory apoapses are consistently $\mathcal{O}(1)$, with all trajectories overshooting their characteristic time scale (which predicts returns at $t^*  =2$ at zeroth order).
@@
 \end{figure}
-
 The relative magnitudes of the simulated forces felt by the entire population of drops are shown in Figure \ref{fig:forces}.
@@
 
-If we naively neglect the contact line dynamics, the dimensionless groups for isothermal drop impacts are the Ohnesorge number $\mathbb{O}\mbox{h} = \frac{\mu}{\sqrt{\rho \gamma R_d}}$ which is a ratio of viscous to inertial and surface tension forces, the Weber number $\mathbb{W}\mbox{e}$, and the Bond number $\mathbb{B}\mbox{o}$ defined previously.
+If we naively neglect the contact line dynamics, the dimensionless groups for isothermal drop impacts are the Ohnesorge number $\mathbb{O}\mbox{h} \equiv \mu/\sqrt{\rho \gamma R_d}$, the Weber number $\mathbb{W}\mbox{e}$, and Bond number $\mathbb{B}\mbox{o}$.
 The Weber number scales the driving force of drop spreading.
-In the well-studied case of high $\mathbb{W}\mbox{e}$ impacts the drop bulk is driven radially outward by the impact induced pressure gradient, whereas in the case of small $\mathbb{W}\mbox{e}$ the liquid is driven outwards by capillary force.
-The Ohnesorge number, by contrast, scales the force that resists spreading.
-For large $\mathbb{O}\mbox{h}$ the resistive force is viscous, whereas for low $\mathbb{O}\mbox{h}$ the resistive force is inertia.
-Previous empirical work for low $\mathbb{O}\mbox{h}$ and low $\mathbb{W}\mbox{e}$ impacts includes thaat of Schiaffino and Sonin \cite{schiaffino_molten_1997} with wetting and non-wetting impacts of molten metal drops on cold surfaces.
+In the well-studied case of high $\mathbb{W}\mbox{e}$ impacts the drop bulk is driven radially outward by the impact induced pressure gradient, whereas in the case of small $\mathbb{W}\mbox{e}$ wetting impacts the liquid is driven outwards by capillary force.
+The Ohnesorge number, by contrast, is a measure of viscous effects in an inertial-capillary flow and scales the force that resists spreading.
+Previous empirical work for low $\mathbb{O}\mbox{h}$ and low $\mathbb{W}\mbox{e}$ impacts includes that of Schiaffino and Sonin \cite{schiaffino_molten_1997} with wetting and non-wetting impacts of molten metal drops on cold surfaces.
 Mol\'{a}\u{c}ek and Bush \cite{molacek_quasi-static_2012}, Gopinath and Koch \cite{gopinath_collision_2002}, and Okamura \cite{okumura_water_2003} have all developed simple analytical models of drop impacts at low $\mathbb{W}\mbox{e}$ and low $\mathbb{B}\mbox{o}$.
@@
 
-When the electro-drob bounce occurs, if the drop has enough time to return a non-wetting impact occurs on the charged substrate usually followed by rebound.
+When the electro-drop bounce occurs, if the drop has enough time to return a non-wetting impact occurs on the charged substrate usually followed by rebound.
 We observe average drop impact $\mathbb{O}\mbox{h} \approx 2.18 \pm 0.36$ and  $\mathbb{W}\mbox{e} \approx 0.28 \pm 0.22$.
@@
 
-Our preliminary results showing the influence of $\mathbb{W}\mbox{e}$ and electrostatic Bond number $\mathbb{B}\mbox{o}_e = \frac{\epsilon E_0^2 R_d}{\gamma} $ on drop impact dimensionless contact time $\tau$ and coefficient of restitution $C_r$ at $\mathbb{O}\mbox{h} \approx 2.2$ are shown in Figures \ref{fig:contact} and \ref{fig:restitution}.
+Our preliminary results showing the influence of $\mathbb{W}\mbox{e}$ and electrostatic Bond number $\mathbb{B}\mbox{o}_e \equiv \epsilon E_0^2 R_d/\gamma $ on drop impact dimensionless contact time $\tau$ and coefficient of restitution $C_r$ at $\mathbb{O}\mbox{h} \approx 2.2$ are shown in Figures \ref{fig:contact} and \ref{fig:restitution}.
 
@@
 The drops are polydisperse and thus have a distribution of masses $m$ and velocities $U_0$.
-The working fluid is a mixture of lithium and cesium with $\rho_l = 452$ kg/m$^3$.
+The working fluid is a mixture of lithium and cesium.
 The lithium droplets have high surface tension even at the high temperatures encountered in this power cycle, and an insulated electrode can possibly be made hydrophobic by means of a high temperature coating such that the drops rebound rigidly without wetting the surface of the precipitator.
@@
 If an engineering requirement is to capture 95\% the drops entering the compressor to mitigate damage to the turbine blades we can perform an initial sizing of an electrostatic drop precipitator using the scaling approach of this thesis.
-Let us say that two standard deviations of the drop population posses kinetic energy less than $8 \times 10^{-3}$ J per drop with average radius $R_d = 1$ mm.
+Let us say that two standard deviations of the drop population enter the precipitator with velocity $U_0 > 20$ cm/s and average radius $R_d = 1$ mm.
 The drops enter the system at $H=4$ cm, and the design constraints for the electrode are such that $E_0=3$ kV/m and that the electrode is 10 cm square.
@@
 \[
-\frac{8 \pi}{3} \frac{q}{m} \rho E_0 R_d H L^2  = mU_0^2.
-\]
-From the above we find that to capture these drops a charge-to-mass ratio $q/m=3 \times 10^{-7}$ C/kg is required.
-This is one order of magnitude less than the charge-to-mass ratios observed in this work, and can be achieved by a shielded charging electrode near an orifice in a way similar to an inkjet printer, or alternately by discharge, electron beam, or ionizing radiation emission.
+\frac{q}{m} = \frac{4 \pi R_d^2 U_0^2}{L^2 E_0 H}
+\]
+From the above we find that to capture these drops a charge-to-mass ratio $q/m=4 \times 10^{-5}$ C/kg is required.
+This is one order of magnitude greater than the charge-to-mass ratios observed in this work, but can be achieved by a shielded charging electrode near an orifice in a way similar to an inkjet printer, or possibly by discharge, electron beam, or ionizing radiation emission.
 Though this example is highly contrived and departs far from the experiment reported here the results remain applicable because of the fundamental similarity in the underlying physics.
@@
 ANOVA analysis using \verb|pandas| of the linear multiple regression model $q \sim a*V_d + b*t_s$, where $a$, $b$ are model fitting coefficients, for the data set indicates that neither drop volume $V_d$ ($p=0.178$), nor surface stay time $t_s$ ($p=0.939$) is significant at the 95\% confidence level.
-The overall model F-statistics (1.001 in 2 and 14 degrees of freedom), and coefficients of determination ($r^2 = 0.125$) indicate that the linear model neither fits the data particularly well, nor does it offer an improvement over the mean model.
+The overall model F-statistics (1.001 in 2 and 14 degrees of freedom), and coefficients of determination ($R^2 = 0.125$) indicate that the linear model neither fits the data particularly well, nor does it offer an improvement over the mean model.
 The mean charge was thus determined to be positive $5.3 \times 10^{-12}$ C, with a standard deviation of $4.7 \times 10^{-12}$ C.
@@
 \label{sec.mitigation}
+When neutralization of static charge on the superhydrophobic surfaces used in this work is required we use the following procedure:
+\begin{enumerate}
+\item Surface potential is quickly estimated using a Simco-Ion FMX-004 electrostatic fieldmeter.
+This measurement is only quantitative for flat dielectric surfaces larger then several cm square, but can be used qualitatively for other geometries.
+This sensor should be positioned about 2.5 cm normal to the surface in question.
+For quantitative measurements the sensor conductive shell should be connected to ground, and the dielectric substrate should rest on conductive backplane.
+In any case the surface potential measurement should establish whether there is a need for charge neutralization.
+\item A Ptec IN5120 ion fan is positioned about 10 cm away from the surface.
+The ion fan issues a balanced steam of ions which will screen the net surface charge densities of the dielectric.
+The surface potential is reduced to the ion source bias (on the order of $\pm$10 V) within 2 to 10 s.
+All faces of the dielectric should be discharged under the fan, as for materials with low dielectric constants, net charge distributions will set up significant electric fields that permeate the dielectric regardless of their position.
+In other words the bulk of the dielectric does little to shield the electric field.
+\item We verify that the problematic charge has been duly compensated by the ion stream by remeasuring the surface potential with the fieldmeter.
+\end{enumerate}
 

### 2018-07-04 doc/manuscript/manuscript.tex
minor formatting changes

@@
 \usepackage{makeidx}
+\usepackage{sectsty}
+%\chapternumberfont{\large} 
+%\chaptertitlefont{\large}
+%\allsectionsfont{\normalsize}
 \makeindex
 
-\title{\textsf{\textbf{Drop Electro-Bouncing in Low-Gravity}}}
+\title{Drop Electro-Bouncing in Low-Gravity}
 \vspace{-25mm}
@@
 \centering %\vspace*{-10ex}
-{\large \textsf{\textbf{Electro-Drop Bouncing in Low-Gravity}}}
+{\textsf{{Electro-Drop Bouncing in Low-Gravity}}}
 
@@
 \tableofcontents
-\afterpage{\blankpage}
+%\afterpage{\blankpage}
 \listoffigures
-\afterpage{\blankpage}
+%\afterpage{\blankpage}
 
@@
 This should come as little surprise, as we are creatures evolved at the bottom of a gravity well; gravity is natural to us.
-However when the magnitude of gravitational body forces become small, other forces come into play in fluid dynamical problems, which are otherwise negligible under normal circumstances in 1-$g_0$.
+However when the magnitude of gravitational body forces become small, other forces come into play in fluid dynamical problems, which are otherwise negligible under normal circumstances in 1-$g_0$, where $g_0=9.81$ m/s$^2$ is the standard gravitational acceleration at sea-level.
 Our 1-$g_0$ cognitive bias then leads to a plethora of problems which are both simultaneously trivially easy to solve in 1-$g_0$, and which despite decades of study continue to elude solutions in a low-gravity context.
@@
 the equivalence of gravitational and inertial mass).
-In theoretical terms, a `zero-g' experiment performed in a drop tower on the surface of the Earth is equivalent to the same experiment performed in the nearly gravity-free deep space between galaxies, despite the fact that the drop tower itself is enveloped in a 1-$g_0$ gravity field, where $g_0=9.81$ m/s$^2$ is the standard gravitational acceleration at sea-level.
+In theoretical terms, a `zero-g' experiment performed in a drop tower on the surface of the Earth is equivalent to the same experiment performed in the nearly gravity-free deep space between galaxies, despite the fact that the drop tower itself is enveloped in a 1-$g_0$ gravity field.
 At the orbital altitude of the International Space Station (ISS) the gravity level is still nearly 90\% of its value at sea-level on Earth, but the astronauts aboard ISS feel weightlessness because they are in a state of free-fall.
-In a practical sense true zero-g does not exit anywhere in the universe as there are always small, but nonetheless, measurable forces which can accelerate any massive body.
+In a practical sense true zero-g does not exist anywhere in the universe as there are always small, but nonetheless, measurable forces which can accelerate any massive body.
 For instance, in low-Earth orbit accelerations due to aerodynamic resistance in the tenuous outer atmosphere are on the order of $1 \times 10^{-6}$ $g_0$ (from hence comes the term ``microgravity'').
@@
 Capillary forces are due to the cumulative effects of a large number of very short range molecular interactions and in a 1-$g_0$ context are usually quite weak, relatively speaking.
-However, in a low-gravity environment other forces are so weak that the capillary forces becomes extraordinarily strong in a relative sense.
+However, in a low-gravity environment other forces are so weak that capillary forces become extraordinarily strong in a relative sense.
 In comparing the relative magnitudes of gravity and the capillary force we arrive at our figure of merit for assessing how wrong our fluid mechanical intuition is likely to be in a low-gravity context.
@@
 \]
-where $g$ is the acceleration, $R$ is the characteristic interfacial length scale, $\Delta \rho$ is the difference in densities across the interface (which simplifies to $\rho$, for large $\Delta \rho$, as in the case of a air-water interface), and where $\gamma$ is the surface tension.
+where $g$ is the acceleration, $R$ is the characteristic interfacial length scale, $\Delta \rho$ is the difference in densities across the interface (which simplifies to $\rho$, for large $\Delta \rho$, as in the case of an air-water interface), and where $\gamma$ is the surface tension.
 In cases where $\mathbb{B}\mbox{o}$ is small a liquid is effectively in low-gravity regardless of the nominal local gravity level.
@@
 The motive force is due to the inertia of internal flows which occur as the interface deflects under the suddenly lessened $\mathbb{B}\mbox{o}$.
-The characteristic time scale of the rolling up scales as $t_j \sim (\rho V_d/\sigma)^{1/2}$ \cite{attari_puddle_2016}, which resembles the contact time, $\tau \approx 2.6(\rho R^3_d/\sigma)^{1/2}$ presented by Richard \emph{et al.} in 2002 for the related problem of drops impacting hydrophobic surfaces in 1-$g_0$ \cite{richard_surface_2002}.
+The characteristic time scale of the rolling up of the contact line scales as $t_j \sim (\rho V_d/\sigma)^{1/2}$ \cite{attari_puddle_2016}, which resembles the contact time, $\tau \approx 2.6(\rho R^3_d/\sigma)^{1/2}$ presented by Richard \emph{et al.} in 2002 for the related problem of drops impacting hydrophobic surfaces in 1-$g_0$ \cite{richard_surface_2002}.
 For drops with radial symmetry and sufficiently high initial $\mathbb{B}\mbox{o}$, inward radial capillary waves coalesce at the axis, leading to geysering and creation of satellite droplets by the Rayleigh-Plateau breakup of the geyser.
@@
 \item The water drops are attracted to regions of high electric field.
-The horizontal (surface plane parallel) components of the drop trajectory usually oscillate about their initial position during the experiment (except in cases of nearly pure 1-D vertical translation).
+The horizontal (surface plane parallel) components of the drop trajectory usually oscillate about some central position during the experiment (except in cases of nearly pure 1-D vertical translation).
 For especially small drops close to the spontaneous drop jump limit ($V_d \sim$ 0.01 mL) the drops do not jump, but translate across the surface in a rolling regime until either they reach a local maximum of the electric field, or until their motion is sufficiently damped by contact line hysteresis where pinning ultimately arrests their motion.
@@
 There are several possible origins of the electric charge that are ultimately responsible for this phenomenon.
-It is well known that water acquires positive free charge when in contact with certain polymers, especially polytetrafluoroethylene (PTFE) \cite{langmuir_surface_1938}, through a process called contact charging.
+It is well known that water acquires positive free charge when in contact with certain polymers, especially polytetrafluoroethylene (PTFE), through a process called contact charging \cite{langmuir_surface_1938}.
 PTFE, on the other hand, tends to readily acquire negative charge by contact with water.
@@
 External surfaces of spacecraft tend to become charged with time due to the space environment itself.
-Surface charging largely occurs due to low energy electrons (3-50 keV) which do not penetrate the surface of the spacecraft external structure \cite{czepiela_charging_1997}.
+Surface charging largely occurs due to low energy electrons (3-50 keV) which do not penetrate the external surface of the spacecraft \cite{czepiela_charging_1997}.
 The ultimate sources of these charges are trapped charged particles of the van Allen radiation belts, galactic cosmic rays, and the solar wind.
-This deposited charge accumulates and can lead to significant potential differences between different parts of a spacecraft, sometimes leading to breakdown and discharge called Paschen discharge.
+This deposited charge accumulates and can lead to significant potential differences between parts of a spacecraft, sometimes leading to breakdown and discharge called Paschen discharge.
 Deep dielectric charging occurs when higher energy charged particles penetrate the surface of a dielectric material, which can also lead to large potential differences if the dielectric leakage is lower than the external charging rate.
@@
 Such flows are encountered in dish washing, laundry, waste solids drying, food processing, the Sabatier CO$_2$ reaction, and possibly in vapor-compression cycle condensers.
-Phase separation for other disperse droplet flows include electrostatic droplet separators for high-efficiency Rankine-cycle turbines, which require a droplet-free vapor phase entering the turbine, but where conventional superheat approaches come with severe mass penalties \cite{unterberg_zero_1962}.
+Phase separation for other droplet disperse flows include electrostatic droplet separators for high-efficiency Rankine-cycle turbines, which require a droplet-free vapor phase entering the turbine, but where conventional superheat approaches come with severe mass penalties \cite{unterberg_zero_1962}.
 More speculatively, results of this work could be applied in high temperature liquid droplet radiators with electrostatic collection \cite{white_liquid_1987}.
@@
 Modeling the electrostatic force is more involved, but we begin with the standard electrohydrodynamic (EHD) approximation \cite{saville_electrohydrodynamics:_1997}.
-Under a DC electric field, we assume that the real part of the dielectric permittivity $\epsilon$, $\mbox{Re} \langle \epsilon \rangle \approx  \mbox{constant}$.
+Under a DC electric field, we assume that the real part of the dielectric permittivity $\epsilon$, $\mbox{Re} \left( \epsilon \right) \approx  \mbox{constant}$.
 We also assume that electric currents are small enough that the effects of magnetic fields can be neglected.
@@
 \section{Scaling}
-For small DEP forces the equation of motion Equation \ref{gov_eqn_subs} is non-linear non-homogeneous and must be solved numerically.
+For small DEP forces the equation of motion Equation \ref{gov_eqn_subs} is non-linear, non-homogeneous and must be solved numerically.
 Nevertheless we are curious if we can obtain approximate solutions to the equation analytically using perturbation methods.
@@
 where $u = \frac{d y}{d t}$ is the drop velocity. This has the solution
-\[ u(y) = \pm U_0 \left[1 + \frac{2q E_0 y_c^2}{m U_0^2} \left( \frac{1}{y} - \frac{1}{R_d} \right) \right]^{1/2}.
+\[ u(y) = \pm U_0 \left(1 + \frac{2q E_0 y_c^2}{m U_0^2} \left( \frac{1}{y} - \frac{1}{R_d} \right) \right)^{1/2}.
 \]
@@
  \includegraphics[width=0.65\textwidth]{../figures/schematic.pdf}
- \caption{Portion of drop at the initial condition, resting on a superhydrophobic surface in the Cassie-Baxter state just prior to release of the experiment into freefall.
+ \caption{Portion of drop at the initial condition, resting on a superhydrophobic surface in the Cassie-Baxter state just prior to release of the experiment into free-fall.
 The variables $q$, $\sigma$, and $V_d$ are the drop net free charge, dielectric surface charge density, and drop volume, respectively.\label{fig:schematic}}
@@
 Suppose we have a model $G(\mathbf{x})$ with a vector of parameters $\mathbf{x}$ and set of ideal observations $\mathbf{d}$. We then expect there to exist a relationship 
-\[G(\mathbf{x}) = \mathbf{d} ,\]
-where the operator $G$ might be an ODE. Suppose the model $G(\mathbf{x})$ is the ODE
-\[ y'(t) = f(t, \mathbf{y}; \mathbf{x}), \hspace{1 mm}  \mathbf{y} \in \mathbb{R}^n, \]
+\[G(\mathbf{x}) = \mathbf{d} .\]
+Suppose the model $G(\mathbf{x})$ is the ODE
+\[ y'(t) = f(t, \mathbf{y}, \mathbf{x}),\]
 and a collection of $n$ measurements of experimental data
@@
 \left( t_2, \mathbf{y_2} \right), ... ,
-\left( t_k, \mathbf{y_k} \right).\]
+\left( t_k, \mathbf{y_n} \right).\]
 The process of fitting a function defined by a collection of parameters to a data set is called the discrete inverse, or parameter estimation problem as opposed to the \emph{forward problem} to find $\mathbf{d}$ given $\mathbf{x}$ and $G(\mathbf{x})$.
 This is a familiar procedure when the determination of model parameters is accomplished using linear or polynomial regression.
-However there are approaches even to fitting an arbitrary function to a noisy and sparse dataset.
+However there are approaches even to fitting an arbitrary function to a noisy dataset.
 In this work we use the conventional Maximum Likelihood Estimate method to identify the model parameters.
@@
 The Savitsky-Golay filter essentially uses a moving-window based on local least-squares polynomial approximations.
-It was shown that fitting a polynomial to a set of input samples and then evaluating the resulting polynomial at a single point within the approximation interval is equivalent to discrete convolution with a fixed impulse response \cite{savitzky_smoothing_1964}.
+It was shown that fitting a polynomial within a moving window and then evaluating the resulting polynomial at a single point within said window is equivalent to a discrete convolution with a fixed impulse response \cite{savitzky_smoothing_1964}.
 A beneficial property of this kind of low-pass filter is the tendency to maintain waveform amplitudes, and so they are attractive in applications having noisy signals with sharply pointed waveforms such as ultrasound or synthetic aperture radar \cite{schafer_what_2011}.
 Because Savitsky-Golay is a Finite Impulse Response (FIR) filter it requires data points to be equally spaced.
-To accommodate this requirement we interpolate points between the small gaps which sometime occur in the tracking results from image analysis.
+To accommodate this requirement we interpolate points between the small gaps which sometimes occur in the tracking results from image analysis.
 We use a moving window size slightly smaller than the length of the current bounce in a single drop jump data set.
@@
 The trajectories are shown only up to the apoapse of the first bounce.
-The (\protect\redline) \hspace{0.25 mm} lines show the ODE solution with given the MLE parameter vector.
+The (\protect\redline) \hspace{0.25 mm} lines show the ODE solution with the given MLE parameter vector.
 $\chi^2$ goodness-of-fit varies between $1 \times 10^{-5}$ and $1 \times 10^{-8}$ with the better fit occurring typically for the drops with the lowest apoapses.}
@@
     \resizebox{12cm}{!}{\input{../figures/scatter.pdf_tex}}
-    \caption{Covariance plot of main parameters $E_0$, $U_0$, $V_d$, and $q$.\label{fig:scatter}}
+    \caption{Scatter plot matrix of main parameters $E_0$, $U_0$, $V_d$, and $q$.\label{fig:scatter}}
 \end{figure}
@@
 The drop with largest $\mathbb{E}\mbox{u}$ in our dataset failed to escape the electric field as the escape condition $\phi \mathbb{E}\mbox{u} / 8\pi = 0.2 < 1$ was unsatisfied.
-For this drop Equation \ref{time_improved} predicts that the drop will return to the substrate after 32 s, a period of free-fall which is lamentably well out of reach of a drop tower.
+Equation \ref{time_improved} predicts that this drop will return to the substrate after 32 s, a period of free-fall which is lamentably well out of reach of a drop tower.
 However, such an experiment could possibly be performed aboard the ISS or suborbital parabolic flights.
@@
 Previous empirical work for low $\mathbb{O}\mbox{h}$ and low $\mathbb{W}\mbox{e}$ impacts includes that of Schiaffino and Sonin \cite{schiaffino_molten_1997} with wetting and non-wetting impacts of molten metal drops on cold surfaces.
-Mol\'{a}\u{c}ek and Bush \cite{molacek_quasi-static_2012}, Gopinath and Koch \cite{gopinath_collision_2002}, and Okamura \cite{okumura_water_2003} have all developed simple analytical models of drop impacts at low $\mathbb{W}\mbox{e}$ and low $\mathbb{B}\mbox{o}$.
+Mol\'{a}\u{c}ek and Bush \cite{molacek_quasi-static_2012}, Gopinath and Koch \cite{gopinath_collision_2002}, and Okamura \cite{okumura_water_2003} have all developed analytical models of drop impacts at low $\mathbb{W}\mbox{e}$ and low $\mathbb{B}\mbox{o}$.
 These works show increasing dimensionless contact time $\tau$ as Weber number decreases, in opposition to the results of Richard and Qu\'{e}r\'{e} \cite{richard_surface_2002} which show experimentally that the dimensionless contact time is approximately a constant $\tau \approx 2.6(\rho R^3_d/\sigma)^{1/2}$ with respect to $\mathbb{W}\mbox{e}$ at large $\mathbb{W}\mbox{e}$.
@@
 \label{sec.drop_charge}
-Since, by the earlier scaling, we presuppose the source of the drop bouncing behavior to be primarily Coulombic in origin (as opposed to dielectrophoretic), the drop must have some free charge in addition to the charge induced by the electric field.
-Whether this free charge arises due to contact charge or field-induction To measure this charge concurrent methodologies were used.
+By the earlier scaling we presuppose the source of the drop bouncing behavior to be primarily Coulombic in origin (as opposed to dielectrophoretic), thus the drop must have some free charge in addition to the charge induced by the electric field.
+To determine whether this free charge arises due to contact charge or field-induction concurrent methodologies were used.
 In a corollary set of experiments we determine the drop free charge by observation of the deflection of the drops in the region of a known uniform field in a fashion inspired by Millikan's famous experiment to determine the fundamental charge of the electron.

### 2018-08-04 doc/paper/aiptemplate.tex
added journal paper draft, updated figures

--- 2018-07-04 doc/manuscript/manuscript.tex
@@
-\documentclass[12pt,a4paper,oneside]{book}
-\usepackage[utf8]{inputenc}
-\usepackage[english]{babel}
+%% ****** Start of file aiptemplate.tex ****** %
+%%
+%%   This file is part of the files in the distribution of AIP substyles for REVTeX4.
+%%   Version 4.1 of 9 October 2009.
+%%
+%
+% This is a template for producing documents for use with 
+% the REVTEX 4.1 document class and the AIP substyles.
+% 
+% Copy this file to another name and then work on that file.
+% That way, you always have this original template file to use.
+
+%\documentclass[aip,graphicx]{revtex4-1}
+\documentclass[aip,reprint, floatfix]{revtex4-1}
+
+\draft % marks overfull lines with a black rule on the right
 \usepackage{amsmath}
@@
 \usepackage{graphicx}
-%\usepackage{fontspec} % This line only for XeLaTeX and LuaLaTeX
 \usepackage{pgfplots}
 \usepackage{pgf}
-\usepackage{bookmark}
+\usepackage{color,soul}
 \usepackage{color}
+\usepackage{bm}% bold math
 \usepackage{tikz}
-\graphicspath{ {../figures/} }
-%\usepackage{svg}
-\usepackage{verbatim}
-\usepackage{color,soul}
-\usepackage{listings}
-\usepackage{setspace}
-\usepackage[caption=false]{subfig}
-\newlength\figureheight
-\newlength\figurewidth
-\setlength\figureheight{7cm}
-\setlength\figurewidth{10cm}
-\usepackage[
-backend=biber,
-style=phys,
-sorting=none
-]{biblatex}
-\addbibresource{thesis.bib}
 \usepackage{import}
@@
 \renewcommand{\pgfimage}[2][]{\pgfimageWithoutPath[#1]{../figures/#2}}
-\usepackage{array} 
-\usepackage{appendix}
-\usepackage{makeidx}
-\usepackage{sectsty}
-%\chapternumberfont{\large} 
-%\chaptertitlefont{\large}
-%\allsectionsfont{\normalsize}
-\makeindex
-
-\title{Drop Electro-Bouncing in Low-Gravity}
-\vspace{-25mm}
-\author{Erin S. Schmidt, Mark M. Weislogel}
-\date{}
-
-%\usepackage{abstract}
-%\renewcommand{\abstractnamefont}{\normalfont\bfseries}
-%\renewcommand{\abstracttextfont}{\normalfont\small\itshape}
-
-\raggedbottom
-\usepackage{setspace}
-\usepackage{afterpage}
-\newcommand\blankpage{%
-    \null
-    \thispagestyle{empty}%
-    \addtocounter{page}{-1}%
-    \newpage}
-
 \begin{document}
@@
 \newcommand{\redline}{\raisebox{2pt}{\tikz{\draw[-,red,solid,line width = 1.5pt](0,0) -- (5mm,0);}}}
-%\frontmatter
-%\maketitle
-%\afterpage{\blankpage}
-\begin{titlepage}
-\doublespacing
+\graphicspath{ {../figures/} }
 
-\centering %\vspace*{-10ex}
-{\textsf{{Electro-Drop Bouncing in Low-Gravity}}}
+% Use the \preprint command to place your local institutional report number 
+% on the title page in preprint mode.
+% Multiple \preprint commands are allowed.
+%\preprint{}
 
-\vspace{15ex}
-by\\
-Erin Stivers Schmidt
+\title{Electro-Drop Bouncing in Low-Gravity} %Title of paper
 
-\vspace{15ex}
-\singlespacing
-A thesis submitted in partial fulfillment of the\\
-requirements for the degree of
+% repeat the \author .. \affiliation  etc. as needed
+% \email, \thanks, \homepage, \altaffiliation all apply to the current author.
+% Explanatory text should go in the []'s, 
+% actual e-mail address or url should go in the {}'s for \email and \homepage.
+% Please use the appropriate macro for the type of information
 
-\vspace{11ex}
-Master of Science\\
-in\\
-Mechanical Engineering
+% \affiliation command applies to all authors since the last \affiliation command. 
+% The \affiliation command should follow the other information.
 
-\vspace{12ex}
-Thesis Committee:\\
-Mark Weislogel, Chair\\
-Ra\'ul Bayo\'an Cal\\
-Gerald Recktenwald\\
+\author{Erin S. Schmidt}
+%\email[]{Your e-mail address}
+%\homepage[]{Your web page}
+%\thanks{}
+%\altaffiliation{}
+\affiliation{Portland State University}
 
-\vfill
-\vspace{2ex}
-Portland State University\\%[8pt]
-{\number\year}
-\end{titlepage}
+\author{Mark M. Weislogel}
+\affiliation{Portland State University}
 
-%\doublespacing
-\clearpage
+% Collaboration name, if desired (requires use of superscriptaddress option in \documentclass). 
+% \noaffiliation is required (may also be used with the \author command).
+%\collaboration{}
+%\noaffiliation
 
-\frontmatter
+\date{\today}
 
-\section*{Abstract}
-\addcontentsline{toc}{chapter}{\numberline{Abstract}}
-\noindent
+\begin{abstract}
+% insert abstract here
+
 We investigate the dynamics of spontaneous jumps of water drops from electrically charged superhydrophobic dielectric substrates during a sudden step reduction in gravity level.
@@
 This electric body force leads to a drop bouncing behavior similar to well-known phenomena in 1-$g_0$, though occurring for much larger drops ($\sim$ 0.5 mL).
-We show a simple model for the phenomenon, its scaling, and asymptotic estimates for drop time of flight in two regimes: at short-times close to the substrate when drop inertia balances Coulombic force due to net free charge and image charges in the dielectric substrate and at long-times far from the substrate when drop inertia balances free charge Coulombic force and drag.
-The drop trajectories are controlled primarily by the dimensionless electrostatic Euler number $\mathbb{E}\mbox{u}$, which is a ratio of inertial to electrostatic forces.
+We show a 1D model for the phenomenon, its scaling, and asymptotic estimates for drop time of flight in two regimes: at short-times close to the substrate when drop inertia balances Coulombic force due to net free charge and image charges in the dielectric substrate and at long-times far from the substrate when drop inertia balances free charge Coulombic force and drag.
+The drop trajectories are controlled primarily by the dimensionless electrostatic Euler number $\mathbb{E}\mbox{u}$, which is a ratio of inertia to electrostatic force.
 To experimentally determine values of $\mathbb{E}\mbox{u}$ we conduct a series of drop tower experiments where we observe the effects of drop volume, net free charge, and static surface potential of the superhydrophobic substrate on drop trajectories.
 We use a direct search optimization to obtain a Maximum Likelihood Estimate for drop net charge, as we do not measure it directly in experiment.
-For $\phi \mathbb{E}\mbox{u} /8 \pi > 1$ drops escape the electric field, where $\phi$ is a drop to substrate aspect ratio.
+For $\phi \mathbb{E}\mbox{u} /8 \pi > 1$ drops escape the electric field, where $\phi$ is a substrate to drop aspect ratio.
 However, we do not observe any escapes in our dataset.
-With an eye towards engineering applications we consider the results in light of the so-called low-gravity phase separation problem with a worked example.
+\end{abstract}
 
-\clearpage
-% ========================================
+\pacs{}% insert suggested PACS numbers in braces on next line
 
-%\vspace*{8ex}
-\vspace*{\fill}
-%\section*{Dedication}
-%\addcontentsline{toc}{chapter}{\numberline{Dedication}}
+\maketitle %\maketitle must follow title, authors, abstract and \pacs
 
-\emph{To Mom, Laura, and the DDT team}\\
-\vspace*{\fill}
-
-\clearpage
-
-% ========================================
-
-%\vspace*{8ex}
-\vspace*{\fill}
-\section*{Acknowledgements}
-\addcontentsline{toc}{chapter}{\numberline{Acknowledgements}}
-
-This work was supported by NASA Cooperative Agreement NNX12A047A.
-I am also greatly indebted to Andrew Greenberg for his frequent and sage technical advice, and to Joe Shields for his assistance with drop tower experiments.
-\\
-\vspace*{\fill}
-\clearpage
-
-\tableofcontents
-%\afterpage{\blankpage}
-\listoffigures
-%\afterpage{\blankpage}
-
-%\doublespacing
-\mainmatter
-\chapter{Introduction}
-\begin{quote}
-``When the influence of gravity on fluid behavior is diminished or removed, other forces, otherwise of small significance, can assume paramount roles.''
-- NRC Report to NASA, 2003 \cite{motil_priorities_2012}
-\end{quote}
-
-Our terrestrially born intuition about how liquids flow is easily confounded in a low-gravity environment.
-This should come as little surprise, as we are creatures evolved at the bottom of a gravity well; gravity is natural to us.
-However when the magnitude of gravitational body forces become small, other forces come into play in fluid dynamical problems, which are otherwise negligible under normal circumstances in 1-$g_0$, where $g_0=9.81$ m/s$^2$ is the standard gravitational acceleration at sea-level.
-Our 1-$g_0$ cognitive bias then leads to a plethora of problems which are both simultaneously trivially easy to solve in 1-$g_0$, and which despite decades of study continue to elude solutions in a low-gravity context.
-One example of these problems is the so-called ``phase separation'' problem of separating a gas phase from a multi-phase flow (or the reverse case), without the aid of buoyancy due to gravity.
-Sans buoyancy, otherwise mundane activities such as venting a gas or settling a liquid in a tank become problematic \cite{petrash_controlling_1964}.
-Trapped bubbles can vapor lock life-support, power, or propulsion systems \cite{jenson_passive_2014}.
-Issues of phase separation have so bedeviled human endeavors in space that an entire Apollo Saturn 1B mission (AS-203) was earmarked to study them \cite{hastings_saturn_1965}.
-This problem has for some time motivated a quest for substitute body forces, and the present work follows in that well-worn tradition.
-
-A solid beginning to rectifying our problem of poor low-gravity intuition, would be to quantify how wrong our intuition is.
-First, let us clear up a common misnomer about the state of ``zero-gravity''.
-The theory of general relativity is based on a fundamental equivalence of gravity and acceleration.
-By measuring acceleration alone, one cannot determine whether one is in gravity-free space or free-falling in a gravitational field (or conversely whether or not one is uniformly accelerating, or standing at rest in a gravitational field).
-This is sometimes called the equivalence principle of general relativity (e.g.
-the equivalence of gravitational and inertial mass).
-In theoretical terms, a `zero-g' experiment performed in a drop tower on the surface of the Earth is equivalent to the same experiment performed in the nearly gravity-free deep space between galaxies, despite the fact that the drop tower itself is enveloped in a 1-$g_0$ gravity field.
-At the orbital altitude of the International Space Station (ISS) the gravity level is still nearly 90\% of its value at sea-level on Earth, but the astronauts aboard ISS feel weightlessness because they are in a state of free-fall.
-In a practical sense true zero-g does not exist anywhere in the universe as there are always small, but nonetheless, measurable forces which can accelerate any massive body.
-For instance, in low-Earth orbit accelerations due to aerodynamic resistance in the tenuous outer atmosphere are on the order of $1 \times 10^{-6}$ $g_0$ (from hence comes the term ``microgravity'').
-This small drag acceleration provides some ersatz gravity, but there are also other forces present.
-Foremost of these are capillary forces.
-
-Capillary forces are due to the cumulative effects of a large number of very short range molecular interactions and in a 1-$g_0$ context are usually quite weak, relatively speaking.
-However, in a low-gravity environment other forces are so weak that capillary forces become extraordinarily strong in a relative sense.
-In comparing the relative magnitudes of gravity and the capillary force we arrive at our figure of merit for assessing how wrong our fluid mechanical intuition is likely to be in a low-gravity context.
-This figure of merit is the Bond number dimensionless group
-\[ \mathbb{B}\mbox{o} \equiv \frac{g R^2 \Delta \rho}{\gamma}, 
-\]
-where $g$ is the acceleration, $R$ is the characteristic interfacial length scale, $\Delta \rho$ is the difference in densities across the interface (which simplifies to $\rho$, for large $\Delta \rho$, as in the case of an air-water interface), and where $\gamma$ is the surface tension.
-In cases where $\mathbb{B}\mbox{o}$ is small a liquid is effectively in low-gravity regardless of the nominal local gravity level.
-Very small water drops ($R < 1$ mm), for instance, are in low-gravity for all intents and purposes and have nearly spherical shapes.
-Contrarily, for cases of large $R$ in a space environment, such as with large diameter spacecraft propellant tanks then $ \mathbb{B}\mbox{o} \gg 1$ even though the acceleration remains small.
-This is actually a quite useful result, for on the basis of dimensional similarity it is possible to accurately simulate low-gravity fluid mechanics (say of large propellant tanks) even in small drop towers simply by scaling dimensionless groups like the Bond number.
-
-As with capillary forces, electrostatic forces have a multitude of applications as substitutes for gravity.
-Electrohydrodynamic (EHD) body forces have been suggested to combat thermal stratification of propellants under low-g conditions where buoyancy induced natural convection is very small \cite{blackmon_collection_1965}.
-In this case electro-convection is an analog of natural convection due to a fluid temperature dependent dielectric permittivity gradient (as opposed to a fluid density gradient) in the presence of an electric body force field.
-The study also suggested applications in cryogenic tank vent screening and in reducing heat transfer to cryogenic propellants (and thus boiloff losses) by dielectrophoretically positioning ullage vapors around the tank walls as a thermal barrier.
-EHD forces have been studied for enhancing boiling heat transfer by promotion of bubble detachment and prevention of dryout, again as an ersatz buoyancy \cite{snyder_dielectrophoresis_2001, di_marco_influence_2003, marco_use_2012}.
-EHD heat pipes, which substitute an electrode structure for the capillary wicking structure of a conventional thermocapillary heat pipe can postpone the wicking limit \cite{jones_electrohydrodynamic_1973}.
-These are restricted to the use of insulating dielectric liquids, which usually have relatively low thermal conductivity, but are highly robust against dryout, support active flow control, and have low viscous losses.
-Dielectrophoretic settling of cryogenic propellants, in both total and partial communication Propellant Management Device (PMD) configurations, has been studied analytically in both static \cite{hurwitz_electrohydrodynamic_1966} and dynamic cases \cite{koval_dynamics_1967}, and in drop tower experiments \cite{fax_dielectrophoretic_1969}.
-EHD forces have also been applied to the low-g slosh baffling problem \cite{boretz_orbital_1970, petrash_use_1968, hurwitz_dielectrophoretic_1968}, and studied extensively for the mitigation of vapor pullthrough during tank draining and concomittent minimization of propellant residuals at burnout in a series of experiments at the NASA Lewis (now Glenn) Research Center 2.2 s drop tower facility \cite{berenyi_dielectrophoretic_1970}.
-
+% Body of paper goes here. Use proper sectioning commands. 
+% References should be done using the \cite, \ref, and \label commands
 \section{Spontaneous Drop Jump}
-Low-gravity phase separation, drop dynamics, and the dynamics and applications of the so-called spontaneous drop or puddle jump, is an active area of study at the Portland State University Dryden Drop Tower laboratory (DDT).
 When a nonwetting, gravity-dominated sessile drop (e.g.
-a puddle), which is initially at rest on a surface in the Cassie-Baxter state suddenly undergoes a large step reduction in $\mathbb{B}\mbox{o}$ it will spontaneously jump away from the surface.
-The Cassie-Baxter state, sometimes also known as the Fakir state, is a metastable heterogenously non-wetting state on a textured surface characterized by the existence of a vapor-layer that separates roughness features of the surface from the bottom of the drop.
+a puddle), which is initially at rest on a surface in the Cassie-Baxter state suddenly undergoes a large step reduction in $\mathbb{B}\mbox{o} \equiv \frac{g R^2 \Delta \rho}{\gamma}$ it will spontaneously jump away from the surface, where $g$ is the acceleration, $R$ is the characteristic interfacial length scale, $\Delta \rho$ is the difference in densities across the interface (which simplifies to $\rho$, for large $\Delta \rho$, as in the case of an air-water interface), and where $\gamma$ is the surface tension.
 The spontaneous drop jump was first observed experimentally in the Soviet Union by Kirko \emph{et al.} \cite{kirko_phenomenon_1970} in 1970 for drops of mercury in hydrochloric acid, and later by Wollman \emph{et al.} in 2016 for water drops in air in a set of experiments conducted using drop towers \cite{wollman_more_2016}.
 The kinetic energy of the jump is supplied by the defect in free surface energy as the new minimum energy surface equilibrium has approximately constant curvature.
-If the energy losses by viscous and contact line dynamics are neglected, the available kinetic energy is approximated by
-\[KE_2 = SE_2 - SE_1 = [(\gamma A)_{gl} + (\gamma A)_{sg}]_2 - [(\gamma A)_{ls} + (\gamma A)_{gl} + (\gamma A)_{sg}]_1, \]
-where $KE$ and $SE$ are the respective kinetic and surface energies, $A$ is the surface area, the subscripts $1$ and $2$ denote the intial 1-$g_0$, and low-g states, and the subscripts ${gl}$, ${sg}$, and ${ls}$ denote the gas-liquid, solid-gas and liquid-solid interfaces respectively.
 The motive force is due to the inertia of internal flows which occur as the interface deflects under the suddenly lessened $\mathbb{B}\mbox{o}$.
-The characteristic time scale of the rolling up of the contact line scales as $t_j \sim (\rho V_d/\sigma)^{1/2}$ \cite{attari_puddle_2016}, which resembles the contact time, $\tau \approx 2.6(\rho R^3_d/\sigma)^{1/2}$ presented by Richard \emph{et al.} in 2002 for the related problem of drops impacting hydrophobic surfaces in 1-$g_0$ \cite{richard_surface_2002}.
 For drops with radial symmetry and sufficiently high initial $\mathbb{B}\mbox{o}$, inward radial capillary waves coalesce at the axis, leading to geysering and creation of satellite droplets by the Rayleigh-Plateau breakup of the geyser.
 In the case of smaller jumping drops the capillary waves are gradually damped by viscous forces.
-A time-lapsed composite photograph of spontaneous drop jump can be seen in Figure \ref{fig:nobounce}.
-\begin{figure}[htb]
-\centering
-\includegraphics[width=0.75\textwidth]{drop_jump}
-\caption{The trajectory of a 0.2 mL spontaneous drop jump is captured in a composite image over a period $\sim 0.67$ s presented at $\approx 10$ Hz. \label{fig:nobounce}}
-\end{figure}
 
@@
 
-\section{Electro-Drop Bounce}
 During the `rolling-up' of drops under ideal conditions, the spontaneous jump phenomenon is governed by a balance of inertia and surface tension forces, and once aloft the drop motion is nominally in a regime of pure drag.
-However, other forces can again come into play.
+However, other forces can come into play.
 
@@
 The forces at work in such situations are presumably electrostatic in origin.
-Not without irony given our earlier discussion of underdeveloped low-gravity intuition, we note that though the electro-drop bounce was an accidental effect during our work on spontaneous drop jump, the phenomenon is interesting itself.
-This has motivated further study, and the `electro-drop bounce' phenomenon is the subject of this thesis.
-A time-lapsed composite image showing an example of the phenomenon is shown in Figure \ref{fig:bounce}.
+A time-lapsed composite image showing an example of the phenomenon is shown in Figure \ref{fig:bounce}, and schematically in Figure \ref{fig:bounce_time}.
 \begin{figure}[htb]
 \centering
-\includegraphics[width=0.75\textwidth]{bounce}
-\caption{The trajectory of a 0.5 mL drop is captured in a composite image over a single bounce period ($\sim 1.25$ s).
-The surface potential of the superhydrophobic dielectric in this example is $\varphi_s = 1.25 \pm 0.41$ kV.
+\includegraphics[width=0.5\textwidth]{bounce}
+\caption{The trajectory of a 0.5 mL drop is captured in a composite image over a single bounce period ($\sim 1.25$ s) presented at $\approx 10$ Hz.
+The surface potential of the superhydrophobic dielectric is $\varphi_s = 1.25 \pm 0.41$ kV.
 \label{fig:bounce}}
+\end{figure}
+
+\begin{figure}[htb]
+\centering
+\resizebox{0.5\textwidth}{!}{\input{../figures/bounce_series.pgf}}
+\caption{The trajectory time-series of a 0.05 mL drop with surface potential $\varphi_s = 0.75 \pm 0.5$ kV. \label{fig:bounce_time}}
 \end{figure}
@@
 
-There are several possible origins of the electric charge that are ultimately responsible for this phenomenon.
+We expect that if the drop electrostatic potential energy is greater than the release of surface energy under the sudden change in $\mathbb{B}\mbox{o}$, in the form of the drop kinetic energy, the drop will return to an equilibrium state on the charged surface which minimizes the potential.
+
+What is the origin of the electric field arising on the superhydrophobic surfaces?
 It is well known that water acquires positive free charge when in contact with certain polymers, especially polytetrafluoroethylene (PTFE), through a process called contact charging \cite{langmuir_surface_1938}.
@@
 The superhydrophobic surfaces used in the spontaneous drop jump experiments have thin (nanometric) PTFE coatings, and we observe that it is extremely easy to produce significant surface potentials $\varphi_s \sim$ 100-500 V by simply flowing streams of distilled water over them.
-A study of this water on PTFE contact charging phenomenon was conducted by Yatsuzuka \emph{et al.} \cite{yatsuzuka_electrification_1994}, who suggest that this process results from formation of an electrical double layer driven by selective adsorption of ($\mbox{OH}^-$) ions at the polymer surface; other recent work strongly supports this hypothesis \cite{beattie_intrinsic_2006, strazdaite_water_2015}.
-Yatsuzuka \emph{et al.} also found that the specific charge on the drops in contact with the surface depends on their both surface velocity and conductivity.
-The contact charging mechanism is the most likely accidental source of charge on the suphydrophobic surfaces used in our work.
+A study of this water on PTFE contact charging phenomenon was conducted by Yatsuzuka \emph{et al.} \cite{yatsuzuka_electrification_1994}, who suggest that this process results from formation of an electrical double layer driven by selective adsorption of ($\mbox{OH}^-$) ions at the polymer surface; other recent work supports this hypothesis \cite{beattie_intrinsic_2006, strazdaite_water_2015}.
 Given the large roughness, or the ratio of projected to actual surface area, of the superhydrophobic surfaces used in the experiment, and given that the drops are initially in a Cassie-Baxter state, a somewhat electrically resistive air layer is maintained that reduces grounding of the drops despite the large potential difference between them and the surface charges.
-If this electrostatic potential is greater than the release of surface energy under the sudden change in $\mathbb{B}\mbox{o}$, in the form of the drop kinetic energy, we expect that the drop will return to an equilibrium state on the charged surface which minimizes the potential.
 
 The source of the net free charge on the drops is another issue.
-The drop charge could also be due to the contact charging mechanism mentioned previously.
+The drop charge could be due to the contact charging mechanism mentioned previously.
 For instance, in a 1996 paper, NASA flight engineer Don Pettit discusses the problem of low-gravity flow induced charging of liquids, resulting ultimately from contact charging phenomenon \cite{pettit_donald_flow_????}.
-Another mechanism for the drop charge is field-induced charging.
-Field-induced charging occurs due to physical breakup of a conductor having a field-induced dipole (e.g., a physical separation of charge).
+However, a more likely mechanism for the drop charge is field-induced charging.
+Field-induced charging occurs due to breakup of a conductor having a field-induced dipole (e.g., a physical separation of charge).
 In our work this might occur when a drop is deposited on the charged surface by a grounded syringe.
@@
 
-\section{Applications}
-This study of the electro-drop bounce phenomenon may have results which can be extended to useful applications in a space environment.
-External surfaces of spacecraft tend to become charged with time due to the space environment itself.
-Surface charging largely occurs due to low energy electrons (3-50 keV) which do not penetrate the external surface of the spacecraft \cite{czepiela_charging_1997}.
-The ultimate sources of these charges are trapped charged particles of the van Allen radiation belts, galactic cosmic rays, and the solar wind.
-This deposited charge accumulates and can lead to significant potential differences between parts of a spacecraft, sometimes leading to breakdown and discharge called Paschen discharge.
-Deep dielectric charging occurs when higher energy charged particles penetrate the surface of a dielectric material, which can also lead to large potential differences if the dielectric leakage is lower than the external charging rate.
-In a fluid mechanical context, this accumulated charge could be problematic during any multiphase venting process, as might be expected to occur during autonomous satellite servicing refueling operations, or during boil-off venting of cryogens stored over long periods in a space environment (as in many crewed Mars mission scenarios, or in cryogenic propellant depot operations).
-Such venting, if occurring in a region of strong field, will also tend to produce a stream of charged drops, which will be decelerated by the field, causing their eventual return, impacting and potentially contaminating the spacecraft surfaces.
-
-As previously noted, robust phase separation is critical to high reliability multiphase systems used in thermal control and life support.
-Active solid-state phase separation for life support multiphase flows, especially high void-fraction droplet disperse flows is a possible application of this work.
-Such flows are encountered in dish washing, laundry, waste solids drying, food processing, the Sabatier CO$_2$ reaction, and possibly in vapor-compression cycle condensers.
-Phase separation for other droplet disperse flows include electrostatic droplet separators for high-efficiency Rankine-cycle turbines, which require a droplet-free vapor phase entering the turbine, but where conventional superheat approaches come with severe mass penalties \cite{unterberg_zero_1962}.
-More speculatively, results of this work could be applied in high temperature liquid droplet radiators with electrostatic collection \cite{white_liquid_1987}.
-Removal of satellite droplets produced during pipetting in wet-lab research outside of a glovebox environment aboard ISS has also been recently suggested as a application of the work [private communication, NASA JSC, E.
-Unger, 2017].
-Drops can become spontaneously charged by contact with standard micropipette tips \cite{choi_spontaneous_2013}, and this free charge can possibly be leveraged for the purposes of phase separation in low-gravity.
-
-\section{Overview of this Thesis}
-In this thesis we develop and partly validate a simple model to aid in design of future electrostatic disperse drop phase separators.
-To this end the work encompasses (1) a mathematical model of the electro-drop bounce, its scale analysis, asymptotic estimates for drop apoapses and times-of-flight, and (2) the results of controlled experiments, where the effect of the key independent variables of drop volume $V_d$ and dielectric surface charge density $\sigma$ on drop trajectories is tested.
-
-\chapter{Theory}
-\section{Equation of Motion}
+\section{Theory}
+\subsection{Equation of Motion}
 We develop here a simple 1-dimensional model of the dynamics of drops dominated by electrostatic forces.
@@
 \begin{equation}
-m y'' = - \mathbf{F}_D - \mathbf{F}_E,
+m y'' = - F_D - F_E,
 \label{gov_eqn}
@@
 \centering
-\includegraphics[width=0.65\textwidth]{../figures/apparatus0.pdf}
+\includegraphics[width=0.45\textwidth]{../figures/apparatus0.pdf}
 \label{apparatus}
@@
 
-For the intermediate range of Reynolds numbers $1 \leq \mathbb{R}\mbox{e} \equiv \frac{2UR_d}{\nu} \leq 2000 $ observed in our experiments, the force of drag acting on the drop may be quadratic such that,
-\begin{equation*}\label{drag_force}
-\mathbf{F}_D = \frac{1}{2}C_D \rho A {y'}^2,
-\end{equation*}
-where $C_D$ is the drag coefficient, $\rho$ is the density of the air host fluid, and $A$ is the frontal projected area of the drop.
-For this range of Reynolds numbers the drag coefficient may be approximated by the well known Abraham correlation \cite{abraham_functional_1970},
-\[C_D = \frac{24}{9.06^2} \left( 1 + \frac{9.06}{\sqrt{\mathbb{R}\mbox{e}}} \right)^2 .\]
+For the intermediate range of Reynolds numbers $1 \leq \mathbb{R}\mbox{e} \equiv \frac{2UR_d}{\nu} \leq 2000 $ observed in our experiments, we assume the force of drag acting on the drop to be quadratic.
 
-Modeling the electrostatic force is more involved, but we begin with the standard electrohydrodynamic (EHD) approximation \cite{saville_electrohydrodynamics:_1997}.
+In modeling the electrostatic force we begin with the standard electrohydrodynamic (EHD) approximation \cite{saville_electrohydrodynamics:_1997}.
 Under a DC electric field, we assume that the real part of the dielectric permittivity $\epsilon$, $\mbox{Re} \left( \epsilon \right) \approx  \mbox{constant}$.
@@
 This characteristic time $\tau_e$ is also known as the relaxation time, and is a measure of how quickly the polarization of a dielectric responds to a change in electric field.
-Given the conductivity and permittivity in the limiting case of extremely-pure water ($ \epsilon \sim 80$, $\sigma_e = 18.2 \times 10^{6}$ $\Omega\mbox{cm}$) \cite{yatsuzuka_electrification_1994}, we estimate $\tau_e \approx 4 \times 10^{-6}$ s.
+Given the conductivity and permittivity in the limiting case of extremely-pure water ($ \epsilon \approx 80$, $\sigma_e = 18.2 \times 10^{6}$ $\Omega\mbox{cm}$) \cite{yatsuzuka_electrification_1994}, we estimate $\tau_e \approx 4 \times 10^{-6}$ s.
 The relaxation time for the common distilled water that is actually used in the drop experiments is undoubtedly shorter due to the presence of solvated ions.
@@
 Supposing that electrical forces acting on free charges and dipoles in a fluid are transferred directly to the fluid itself, the overall electrical body force will be the divergence of the Maxwell stress tensor $\tau_m $,
-\[ \mathbf{F}_E = \nabla \cdot \tau_m = \nabla \cdot \left( \epsilon \mathbf{E} \mathbf{E} - \frac{1}{2} \epsilon \mathbf{E} \cdot \mathbf{E} \delta \right) ,\]
-where $\mathbf{F}_E$ is the electric body force per unit volume, and $\delta$ is the Dirac delta function. The product of the electric field vectors is the dyadic product.
-
-The Korteweg-Helmholtz volumetric force density formulation of the Maxwell stress tensor is usually expressed as \cite{melcher_continuum_????}
-\begin{equation}\label{force_density}
-\mathbf{F}_E = \rho_f \mathbf{E} + \frac{1}{2} \left| E \right|^2 \nabla \epsilon - \nabla \left( \frac{1}{2} \rho \left( \frac{\partial \epsilon}{\partial \rho} \right)_T \left| E \right|^2 \right) .
-\end{equation}
+\begin{eqnarray} \label{e_force}
+ \mathbf{F}_E &=& \nabla \cdot \tau_m \nonumber \\ 
+ &=& \rho_f \mathbf{E} + \frac{1}{2} \left| E \right|^2 \nabla \epsilon - \nabla \left( \frac{1}{2} \rho \left( \frac{\partial \epsilon}{\partial \rho} \right)_T \left| E \right|^2 \right) .
+\end{eqnarray}
 The first term on the right hand side of this expression is the well known Coulombic force or electrophoretic force, which arises from the presence of free charge in an external electric field.
@@
 It is common to approximate the polarization stress by idealizing the drop as a simple dipole using the effective dipole moment method first described by Pohl in 1958 \cite{pohl_effects_1958}.
-This approach has since been related back to the force density by the volumetric integration of the force density with the substitution of a Taylor series expansion of $\mathbf{E}$ in the limit of a small radial gradient of the field within the dielectric sphere \cite{wang_general_1997}.
-The DEP force arises due to the induced or permanent dipole moment of polarizable media which has a tendency to align the dipole with the electric field.
-If there is a gradient in the field then for a finite separation of charge, one end of the dipole will feel a stronger electric field than the other resulting in a net force.
-Whether the force is positive or negative in the direction of the electric field gradient depends on the difference of dielectric permittivites between the fluids, rather than on the polarity of $\mathbf{E}$.
-In principle an external electric field will tend to induce a dipole in a dielectric material, but if the field is spatially uniform there is no gradient in the field and the forces felt by the dipoles are symmetric with no net force.
-The dipole moment $\mu$ of a spherical linear-dielectric particle immersed in a dielectric medium is given by
-\begin{equation} \label{dipole_m_1}
-\mu = V_d \mathbf{P} = \frac{4}{3} \pi R_d^3 \mathbf{P},
-\end{equation} 
-where $\mathbf{P} = \left(\kappa_a - 1 \right) \epsilon_0 \mathbf{E} = \chi_e \epsilon_0 \mathbf{E}$ is the polarization moment, $R_d$ is the particle radius, $\kappa_a = \frac{\epsilon_a}{\epsilon_0}$ is the relative dielectric constant of the air host fluid, and $\chi_e = \kappa_a - 1$ is the electric susceptibility of the host fluid.
 The force felt by the dipole is
@@
 \end{eqnarray}
-where $\mathbf{P}_e=(\kappa_w - \kappa_a)\epsilon_0 \mathbf{E}$ is the excess polarization and $\kappa_w$ is the relative dielectric constant of the water particle.
+where $\mathbf{P}_e=(\kappa_w - \kappa_a)\epsilon_0 \mathbf{E}$ is the excess polarization and $\kappa_w$ and $\kappa_a$ are the relative dielectric constants of the water particle and air host fluid respectively.
 Here it is convenient to use the simplifying shorthand $K = \frac{\kappa_w - \kappa_a}{\kappa_w + 2 \kappa_a}$, known as the Clausius-Mossotti factor.
@@
 The polarization bound charge in the dielectric will be of the opposite sign of the free drop charge and thus there will be a force of attraction.
-This so-called image force is a correction to the Coulomb force due to the external electric field only, and can be found by a Green's Function solution of Laplace's equation for the electric field called the `method of images' \cite{david_j._griffiths_introduction_1999}.
+This so-called image force is a correction to the Coulomb force due to the external electric field only, and can be found by a Green's Function solution of Laplace's equation for the electric field, the so-called the `method of images' \cite{david_j._griffiths_introduction_1999}.
 This resulting image force $\mathbf{F}_I$ is given by
@@
 \end{equation}
-where the factor $k$ is a function of the dielectric surface susceptibility $k = \frac{\chi_e}{\chi_e + 2}$, and $\hat{\mathbf{j}}$ is a unit vector normal to the dielectric surface.
+where the factor $k$ is a function of the dielectric surface susceptibility $k = \frac{\chi_e}{\chi_e + 2}$, $\chi_e = \kappa_d - 1$, $\kappa_d$ is the relative dielectric constant of the dielectric substrate, and $\hat{\mathbf{j}}$ is a unit vector normal to the dielectric surface.
 
-By substituting Equations \ref{dep_force}, and \ref{image_force} into \ref{force_density} we have
+By substituting Equations \ref{dep_force}, and \ref{image_force} into \ref{e_force} we have
 \begin{eqnarray*}
@@
  &=& q \mathbf{E} + \frac{k q^2}{16 \pi \epsilon_0 } y^{-2} \hat{\mathbf{j}} + 2 \pi R_d^3 \kappa_w \epsilon_0 K \nabla E^2, 
+ \label{e_forces}
 \end{eqnarray*}
-and the 1-D governing equation becomes
-\begin{equation}
- \label{gov_eqn_subs}
-m y'' = - \frac{1}{2} C_D \rho A {y'}^2 - q E - \frac{k q^2}{16 \pi \epsilon_0} y^{-2}- 2 \pi R_d^3 \kappa_w \epsilon_0 K \nabla E^2,
-\end{equation}
-subject to
-\begin{equation}
-y(0) = R, \hspace{5 mm} \mbox{and} \hspace{5 mm} y'(0) = U_0 .
-\end{equation}
 
-By comparing DEP and Coulombic terms in Equation \ref{gov_eqn_subs}, we note that a condition to neglect the DEP force is
+By comparing DEP and Coulombic terms in Equation \ref{e_forces}, we note that a condition to neglect the DEP force is
 \begin{eqnarray}
@@
 There is some physical intuition to support this conclusion as well.
-The dielectric displacement $\mathbf{D} = \kappa \epsilon_0 \mathbf{E}$ of a water drop in air is high due to its large relative dielectric constant.
-This implies that the field strength within the drop is about 80 times smaller than in the surrounding medium, which is essentially the same as a vacuum from a dielectric standpoint.
+The dielectric displacement $\mathbf{D} = \kappa \epsilon_0 \mathbf{E}$ of a water drop in air is high due to the large relative dielectric constant of water.
+This implies that the field strength within the drop is about 80 times smaller than in the surrounding medium.
 Thus it is not particularly inaccurate to model the dielectric volume of a drop as an equipotential conductive shell with zero field in its interior.
@@
 
-\section{The Electric Field}
-If we consider the charged dielectric surface of our experiments to be a square sheet of charge lying in the $xz$-plane with width $L$, the symmetry of the problem happily lets us obtain the $y$-component of the electric field $\mathbf{E}$ by direct integration.
-In particular, it is easy to construct the electric field due to a finite plane of charge by superposition of the electric fields of a series of line charges.
-By symmetry, the electric field points along the $y$-axis; for a point along the $y$-axis the position vector is $\mathbf{r} = \left( x^2 + y^2 \right)^{1/2} \hat{\mathbf{r}}$ to the center of a line charge in the $xz$-plane.
-The $y$-component of $d\mathbf{E}$ is found by $d E_r = d E_y \cos \theta = d E_y y/ r$, where $\theta$ is the angle made between the $y$-axis and the position vector $\mathbf{r}$.
-If the charge in a line element $dx$ is $\sigma L dx$, where $\sigma$ is the average surface charge density, the electric field of a line charge is given by \cite{david_j._griffiths_introduction_1999}
-\[d E_r = \frac{\sigma L dx}{4 \pi \epsilon_0 r \sqrt{r^2 + L^2/4}}.
-\]
-The $y$-component of the electric field $E_y$, hence $E$, is then
-\[ E = \frac{\sigma L y }{4 \pi \epsilon_0} \int^{L/2}_{-L/2} \frac{1}{(y^2 + x^2) \sqrt{y^2 + x^2 + L^2/4}} dx 
-.\]
-With some substitutions the above can be integrated to obtain an expression for the electric field in terms of $y$, 
+Thus the 1-D governing equation becomes
+\begin{equation}
+ \label{gov_eqn_subs}
+m y'' = - \frac{1}{2} C_D \rho A {y'}^2 - q E - \frac{k q^2}{16 \pi \epsilon_0} y^{-2},
+\end{equation}
+subject to
+\begin{equation}
+y(0) = R_d, \hspace{5 mm} \mbox{and} \hspace{5 mm} y'(0) = U_0 .
+\end{equation}
+
+\subsection{Electric Field}
+If we consider the charged dielectric surface of our experiments to be a square sheet of charge lying in the $xz$-plane with width $L$, the symmetry of the problem happily lets us obtain the $y$-component of the electric field $\mathbf{E}$ by direct integration,
 \begin{equation}
@@
 .\end{equation}
-We note that this model of the electric field is valid when $R_d \ll L$, which will be true for cases of small drops `far' from the dielectric surface.
-For accurate models of the field in the case $R_d/L \sim \mathcal{O}(1)$ we likely need to numerically solve Laplace's equation for the electric potential $\varphi$,
-\[ - \nabla^2 \varphi = 0.\]
+We note that this 1D model of the electric field is valid when $R_d \ll L$, which will be true for cases of small drops `far' from the dielectric surface.
 
-By taking Taylor series expansions in large and small limits we can intuit a bit about the behavior of this field. In the limit $y/L \ll 1$ Equation \ref{e_field} reduces to
+By taking Taylor series expansions in large and small $y$-limits we can intuit a bit about the behavior of this field. In the limit $y/L \ll 1$ Equation \ref{e_field} reduces to
 \begin{equation}
@@
 \end{equation}
-where $E_0$ is the characteristic electric field given by $E_0 = \frac{\sigma}{4 \pi \epsilon_0}$.
+where $E_0$ is the characteristic electric field.
 This field is constant and equivalent to the electric field due to an infinite plane of charge.
@@
 \end{figure}
-\newpage
 
-\section{Scaling}
-For small DEP forces the equation of motion Equation \ref{gov_eqn_subs} is non-linear, non-homogeneous and must be solved numerically.
+\subsection{Scaling}
+Equation \ref{gov_eqn_subs} is non-linear, non-homogeneous and must be solved numerically.
 Nevertheless we are curious if we can obtain approximate solutions to the equation analytically using perturbation methods.
@@
 where $y_c$ and $t_c$ are characteristic length and time scales respectively, and using the coordinate transformation $y(0) - R = 0$, the governing equation becomes
-\begin{eqnarray}
-& {y^*}'' = - \frac{1}{2} \frac{C_D \rho A y_c}{m} {y^*}'^2
-- \frac{q E_0 t_c^2}{m y_c} E^* ( {y^*} ) 
-- \frac{k q^2 t_c^2}{16 \pi \epsilon_0 R^2 m y_c} \left( \frac{y_c}{R} {y^*} + 1 \right)^{-2}, & \label{scaled_eqn}
-\end{eqnarray}
-subject to 
-\begin{equation*}
-{y^*}(0) = 0, \hspace{5 mm} \mbox{and} \hspace{5 mm} {y^*}'(0) = \frac{U_0 t_c}{y_c} .
-\end{equation*}
-From Equation \ref{scaled_eqn} we note the existence of several dimensionless groups
-\[ \mathbf{\Pi}_1 = \frac{C_D \rho A y_c}{2 m}, \hspace{5 mm}
-\mathbf{\Pi}_2 = \frac{q E_0 t_c^2}{m y_c}, \hspace{5 mm}
-\mathbf{\Pi}_3 = \frac{k q^2 t_c^2}{16 \pi \epsilon_0 R^2 m y_c}, \hspace{5 mm}
-\mathbf{\Pi}_4 = \frac{y_c}{R}, \hspace{5 mm}
-\mathbf{\Pi}_5 = \frac{U_0 t_c}{y_c},\]
-such that Equation \ref{scaled_eqn} becomes
 \begin{equation}
@@
 \begin{equation*}
-{y^*}(0) = 0, \hspace{5 mm} \mbox{and} \hspace{5 mm} {y^*}'(0) = \mathbf{\Pi}_5 .
+{y^*}(0) = 0, \hspace{5 mm} \mbox{and} \hspace{5 mm} {y^*}'(0) = \mathbf{\Pi}_5,
 \end{equation*}
+where we note the existence of several dimensionless groups
+\begin{gather*}
+\mathbf{\Pi}_1 = \frac{C_D \rho A y_c}{2 m}, \hspace{5 mm}
+\mathbf{\Pi}_2 = \frac{q E_0 t_c^2}{m y_c}, \hspace{5 mm}
+\mathbf{\Pi}_3 = \frac{k q^2 t_c^2}{16 \pi \epsilon_0 R_d^2 m y_c}, \hspace{5 mm}\\
+\mathbf{\Pi}_4 = \frac{y_c}{R_d}, \hspace{5 mm}
+\mathbf{\Pi}_5 = \frac{U_0 t_c}{y_c}.
+\end{gather*}
 
-\subsection{Inertial Electro-Image Limit}
+\subsubsection{Inertial Electro-Image Limit}
 In the limit of small $y$ and $t$ we expect inertia to scale with Coulombic and image forces.
@@
 \]
+We note that in a conservative system $\mathbb{E}\mbox{u}$ can be thought of as a ratio of energies: the kinetic energy $m U_0^2$ in the numerator and the electrostatic potential energy $q E_0 R_d$ in the denominator.
 
-\subsection{Inertial Electro-Viscous Limit}
+\subsubsection{Inertial Electro-Viscous Limit}
 In the limit of large $y$ and $t$ we expect drop inertia to balance Coulombic force and drag.
-In this limit we approximate the electric field as $E \approx y_c^2 E_0 y^{-2}$.
-In this case there are several obvious possible choices of scales:
-\begin{enumerate}
-\item $y_c \sim U_0 t_c$ and $\mathbf{\Pi}_3 \sim \mathcal{O}(1)$
-\item $y_c \sim L$ and $t_c \sim \frac{L}{U_0}$ (making Equation \ref{scaled_eqn} singular)
-\item $y_c \sim L$ and $t_c \sim \left( \frac{L m}{q E_0} \right)^{1/2}$
-\item $y_c \sim L$ and $\mathbf{\Pi}_3 \sim \mathcal{O}(1)$
-\end{enumerate}
-%In Case 4, the characterisitc time is $t_c \sim \left( \frac{4 \pi R_d^2}{q E_0 L} \right)^2 $ and the non-dimensional governing equation is given by
-%\begin{eqnarray}
-%&\bar{y}'' = - \frac{C_D \rho A L}{2 m} \bar{y}'^2 - \left( \frac{L}{R_d} \bar{y} + 1\right)^{-2} ,& \nonumber \\
-%& \bar{y}(0) = \frac{R_d}{L}, \hspace{5 mm} \bar{y}'(0) = \left( \frac{4 \pi U_0^2 R_d^2}{q E_0 L^3}\right)^{1/2} = \frac{R_d}{L} \sqrt{\mathbb{E}\mbox{u}_+}.& \nonumber
-%\end{eqnarray}
-%where $\mathbb{E}\mbox{u}_+ = \frac{4 \pi m U_0^2}{q E_0 L}$ is a long time scaled electrostatic Euler number.
-
-We choose the Case 1 scaling for its combination of physical simplicity, few $\mathbf{\Pi}$ terms, and homogeneous initial conditions. The intrinsic scales for this case are given by
+Here we approximate the electric field as $E \approx y_c^2 E_0 y^{-2}$.
+We choose the scaling $y_c \sim U_0 t_c$ and $\mathbf{\Pi}_3 \sim \mathcal{O}(1)$ for its combination of physical simplicity, few $\mathbf{\Pi}$ terms, and homogeneous initial conditions.
+The intrinsic scales for this case are given by
 \[ t_c \sim \frac{R_d^2}{L^2} \frac{4 \pi m U_0}{q E_0} \hspace{5mm} \mbox{and} \hspace{5 mm} y_c \sim \frac{R_d^2}{L^2} \frac{4 \pi m U_0^2}{q E_0}.
@@
 
-\section{Asymptotic Estimates}
-\subsection{Inertial Electro-Image Limit}
-The alternate scalings of the equation of motion given by Equations \ref{img_limit} and \ref{drag_limit} are weakly non-linear differential equations in the sense that they reduce to linear equations as the parameter $\mathbb{E}\mbox{u} \rightarrow 0$.
+\subsection{Asymptotic Estimates}
+The scalings of the equation of motion given by Equations \ref{img_limit} and \ref{drag_limit} are weakly non-linear differential equations in the sense that they reduce to linear equations as the parameter $\mathbb{E}\mbox{u} \rightarrow 0$.
 If we take $\mathbb{E}\mbox{u}$ to be a small parameter we can find an asymptotic approximation to the solution of the non-linear equation by means of a regular perturbation.
@@
 
+\subsubsection{Inertial Electro-Image Limit}
 By substitution of Equation \ref{regular_pert} and its derivatives into \ref{pi_terms}, and equating terms by order we first find the $\mathcal{O}(1)$ unperturbed solution
@@
 Looking at this solution it is evident that if $\mathbb{I}\mbox{g}=0$, the solution is the classical kinematic equation for projectile motion without drag under constant gravity $g_0$.
-Continuing on with this procedure we find, after some tedious computations documented in the project repository for this thesis \cite{schmidt_droplet_electro-bounce:_2017}, the $\mathcal{O}(\mathbb{E}\mbox{u}^5)$ order accurate solution truncated to $\mathcal{O}(\mathbb{E}\mbox{u}^2)$ is
-\begin{eqnarray}
-\label{perturb_image}
-&{y^*}({t^*}) = {t^*} + \frac{{t^*}^{2}}{2} \left(-1 - \mathbb{I}\mbox{g}\right) + \mathbb{E}\mbox{u} \left(\frac{\mathbb{I}\mbox{g} {t^*}^{3}}{3} + \frac{\mathbb{I}\mbox{g} {t^*}^{4}}{12} \left(-1 - \mathbb{I}\mbox{g} \right)\right)& \\
-&+ \mathbb{E}\mbox{u}^{2} \left(- \frac{\mathbb{I}\mbox{g} {t^*}^{4}}{4} + \frac{\mathbb{I}\mbox{g} \bar{t^*}^{5}}{60} \left(9 + 11 \mathbb{I}\mbox{g} \right) + \frac{\mathbb{I}\mbox{g} {t^*}^{6}}{360} \left(-9 - 20 \mathbb{I}\mbox{g} - 11 \mathbb{I}\mbox{g}^{2}\right)\right) + \mathcal{O}(\mathbb{E}\mbox{u}^3).&\nonumber
-\end{eqnarray}
+Continuing on with this procedure we find, after some tedious computations documented in the project repository for this work \cite{schmidt_droplet_electro-bounce:_2017}, the $\mathcal{O}(\mathbb{E}\mbox{u}^5)$ order accurate solution truncated to $\mathcal{O}(\mathbb{E}\mbox{u}^2)$ is
+
+\begin{gather}
+{y^*}({t^*}) = {t^*} + \frac{{t^*}^{2}}{2} \left(-1 - \mathbb{I}\mbox{g}\right) \nonumber \\
+ + \mathbb{E}\mbox{u} \left(\frac{\mathbb{I}\mbox{g} {t^*}^{3}}{3} + \frac{\mathbb{I}\mbox{g} {t^*}^{4}}{12} \left(-1 - \mathbb{I}\mbox{g} \right)\right) \nonumber \\
+ + \mathcal{O}(\mathbb{E}\mbox{u}^2). \label{perturb_image}
+\end{gather}
+
 We plot the approximate short-time scaled solution Equation \ref{perturb_image} with varying values of $\mathbb{I}\mbox{g}$ in Figure \ref{fig:short_times}.
-%\newpage
-\begin{figure}[htb]
-    \centering
-    \resizebox{1\textwidth}{!}{\input{../figures/short_times.pgf}}
+
+\begin{figure*}[htp]
+    \resizebox{0.8\textwidth}{!}{\input{../figures/short_times.pgf}}
     \caption{Short-time scaled drop trajectories for various values of $\mathbb{E}\mbox{u}$, $\mathbb{I}\mbox{g}$.
@@
     \label{fig:short_times}
-\end{figure}
+\end{figure*}
 These plots show a trend of decreasing time-of-flight $t_f$, which is the time for the drop to return to the origin (a single `bounce'), and height at apoapse with increasing values of $\mathbb{I}\mbox{g}$.
@@
 
-\subsection{Inertial Electro-Viscous Limit}
+\subsubsection{Inertial Electro-Viscous Limit}
 By similar arguments we find an asymptotic estimate of the trajectory in the long-time regime. The approximate solution is 
-\begin{eqnarray*}
+\begin{gather*}
 \label{perturb_viscous}
-&{y^*}({t^*}) = {t^*} - \frac{{t^*}^{2}}{2} + \phi\mathbb{E}\mbox{u} \left(\frac{{t^*}^{3}}{3} \left(1 + \mathbb{D}\mbox{g}\right) + \frac{{t^*}^{4}}{12} \left(-1 - \mathbb{D}\mbox{g}\right) - \frac{\mathbb{D}\mbox{g} {t^*}^{2}}{2}\right)&  \\
-&+ \phi^2 \mathbb{E}\mbox{u}^{2} \left(\frac{{t^*}^{4}}{12} \left(-3 - 3 \mathbb{D}\mbox{g} - 4 \mathbb{D}\mbox{g}^{2}\right) + \frac{{t^*}^{5}}{60} \left(11 + 10 \mathbb{D}\mbox{g} + 8 \mathbb{D}\mbox{g}^{2}\right) \right.
-& \\
-&\left. + \frac{{t^*}^{6}}{360} \left(-11 - 10 \mathbb{D}\mbox{g} - 8 \mathbb{D}\mbox{g}^{2}\right) + \frac{\mathbb{D}\mbox{g}^{2} {t^*}^{3}}{3}\right)
- + \mathcal{O}(\phi^3 \mathbb{E}\mbox{u}^3).& \nonumber
-\end{eqnarray*}
+{y^*}({t^*}) = {t^*} - \frac{{t^*}^{2}}{2}  \nonumber \\
++ \phi\mathbb{E}\mbox{u} \left(\frac{{t^*}^{3}}{3} \left(1 + \mathbb{D}\mbox{g}\right) + \frac{{t^*}^{4}}{12} \left(-1 - \mathbb{D}\mbox{g}\right) - \frac{\mathbb{D}\mbox{g} {t^*}^{2}}{2}\right) \nonumber \\
+ + \mathcal{O}(\phi^2 \mathbb{E}\mbox{u}^2). \nonumber
+\end{gather*}
 Trajectories for this solution are shown in Figure \ref{fig:long_times}.
@@
     \centering
-    \input{../figures/long_times.pgf}
+    \resizebox{0.5\textwidth}{!}{\input{../figures/long_times.pgf}}
     \caption{Long-time scaled drop trajectories for various values of $\phi \mathbb{E}\mbox{u}$.}
@@
 and solving for the roots at times when $y^* = 0$, we find an asymptotic estimate for the time-of-flight. The $\mathcal{O}(\phi^2 \mathbb{E}\mbox{u}^2)$ accurate time-of-flight estimate is given by
-\[t_f = 2 + \phi \mathbb{E}\mbox{u} \left(\frac{4}{3} - \frac{2 \mathbb{D}\mbox{g}}{3}\right) + \phi^2 \mathbb{E}\mbox{u}^{2} \left(\frac{4}{5} - \frac{4 \mathbb{D}\mbox{g}}{3} + \frac{2 \mathbb{D}\mbox{g}^{2}}{5}\right) + \mathcal{O}(\phi^3 \mathbb{E}\mbox{u}^3).\]
+\begin{gather*}
+t_f = 2 + \phi \mathbb{E}\mbox{u} \left(\frac{4}{3} - \frac{2 \mathbb{D}\mbox{g}}{3}\right) \\
++ \phi^2 \mathbb{E}\mbox{u}^{2} \left(\frac{4}{5} - \frac{4 \mathbb{D}\mbox{g}}{3} + \frac{2 \mathbb{D}\mbox{g}^{2}}{5}\right) \\
++ \mathcal{O}(\phi^3 \mathbb{E}\mbox{u}^3).
+\end{gather*}
 Substituting the experimental value of $\mathbb{D}\mbox{g}$ we find the time-of-flight estimate for water drops is
@@
 \end{equation}
-In Figure \ref{fig:drag} we see the effect of increasing values of $\phi \mathbb{E}\mbox{u}$ on $t_f$.
-\begin{figure}[htb]
-    \centering
-    \input{../figures/drag.pgf}
-    \caption{$\mathcal{O}(\phi^3 \mathbb{E}\mbox{u}^3)$ accurate asymptotic estimate of drop time-of-flight $t_f$.}
-    \label{fig:drag}
-\end{figure}
+
 As $\mathbb{E}\mbox{u}$ grows to be no longer small, the time-of-flight grows rapidly, but this behavior appears to have an asymptote at a certain critical velocity; this is an electrostatic escape velocity $U_e$.
@@
 \end{equation}
-If the drop escapes the electric field it will have a residual velocity $U_{\infty}$ and will be in a regime where inertia $\sim$ drag. The velocity will then decay by drag as
-\[
-u^*(t^*) = \frac{1}{t^* + 1},
-\]
-with a characteristic time $t_c \sim \frac{2 m}{C_D \rho A U_{\infty}}$, which is the halving time of the velocity.
-\section{Summary}
-The objective of this work is to understand the basic physics of the low-gravity electro-drop bounce phenomenon to the point where we can make useful predictions of drop behavior for engineering purposes.
-To that end, in this chapter we have shown the following:
-\begin{itemize}
-\item We develop from first principles a simple 1-dimensional model of drop trajectories subject to Coulombic forces and drag under low-gravity.
-Drops are idealized as point charges.
-We find that polarization stresses are negligible, and that water drops can be modeled as ideal conductors under the conditions of our experiments.
-\item By scaling arguments we find characteristic length and time scales for both a short-times regime where inertia balances Coulombic force and forces due to image charges, and a long-times regime where inertia balances Coulombic force and drag.
-In both regimes the key dimensionless electrostatic Euler number $\mathbb{E}\mbox{u}$ which is a ratio of inertia to electrostatic force, appears.
-\item The governing ODE is non-linear, but we find approximate analytic solutions for the drop trajectory and time of flight in both regimes by means of asymptotic expansions.
-\item We find a limiting initial velocity $U_0$ for which drop time of flight grows without bound.
-This electrostatic escape velocity is analogous to the gravitational escape velocity of a planet or other massive body.
-\end{itemize}
 
-\chapter{Methodology}
-\section{Overview}
-We are interested mainly about which parameters are important in electrostatic transport of relatively large millimetric drops in low-gravity, and what the values of the respective dimensionless numbers might be; namely, $\mathbb{I}\mbox{g}$ and $\mathbb{E}\mbox{u}$.
-However, it is impractical to directly measure all of the key physical quantities that appear in the dimensionless groups at once in a drop tower experiment.
-In particular, determination of net drop free electric charge $q$ is difficult as high-input resistance electrometers are not well-suited to the sudden 15-$g_0$ decelerations characteristic of drop tower experiments.
-To find typical values of these parameters we use the following approach:
+\section{Methods}
+\subsection{Overview}
+Using various scaling arguments we have gleaned from our simple model a set of dimensionless numbers characteristic of drop bounce apoapses and times of flight.
+These dimensionless numbers depend on physical properties not all of which are easily measured by experiment.
+In particular, direct determination of net drop free electric charge $q$ is difficult as high-input resistance electrometers are not well-suited to the sudden 15-$g_0$ decelerations characteristic of drop tower experiments.
+To estimate the drop free charge $q$ we use parameter estimation techniques.
+Our work flow to identify $q$ in an individual drop tower experiment is as follows:
 \begin{enumerate}
@@
 \item We capture high-speed video and digitize the trajectories of the drops. 
-\item We solve the inverse problem to find the key parameters by maximizing a statistical likelihood function between an observed trajectory and the trajectory predicted by a dynamical model given that certain set parameters.
+\item We solve the inverse problem to find the drop free charge $q$ by maximizing the log-likelihood of the data given the dynamical model by varying the parameter vector $\mathbf{x} = \left\langle q, \hspace{2 mm} V_d, \hspace{2 mm} \sigma \right\rangle$ using a direct search optimization.
 \end{enumerate}
-A schematic representation of drop jump system statics is provided in Figure \ref{fig:schematic}.
-\begin{figure}[ht]
+
+\subsection{Experimental Methods}
+The Dryden Drop Tower at Portland State University uses a dual capsule design, inspired by the 2.2 s facility at NASA Glenn Research Center, which decouples drag acceleration felt by the external drag shield from the experiment.
+The experiment experiences approximately $\lesssim 1 \times 10^{-4}$ $g_0$ during free-fall for 2.1s as the rig and drag shield plummet to the bottom of drop tower 6 stories below.
+The rig with a mounted experiment is shown in Figure \ref{fig:rig}.
+Single drops of distilled water in a range of volumes ($0.01 \leq R_d \leq 0.5$ mL) are carefully deposited on charged superhydrophobic substrates using an grounded glass syringe with $\pm $1 $\mu$L accuracy and then dropped in the drop tower.
+Red dye is added to improve thresholding accuracy in trajectory digitization.
+Drop trajectories are recorded using a Panasonic HC-WX970 Camera.
+Drop trajectories are digitized using the particle tracking module in Fiji \cite{schindelin_fiji:_2012}.
+
+\begin{figure}
     \centering
- \includegraphics[width=0.65\textwidth]{../figures/schematic.pdf}
- \caption{Portion of drop at the initial condition, resting on a superhydrophobic surface in the Cassie-Baxter state just prior to release of the experiment into free-fall.
-The variables $q$, $\sigma$, and $V_d$ are the drop net free charge, dielectric surface charge density, and drop volume, respectively.\label{fig:schematic}}
+    \fontsize{12pt}{13pt}\selectfont
+    \def\svgwidth{\columnwidth}
+        \input{../figures/rig_paper.pdf_tex}%
+    \caption{The electro-drop bounce experiment hardware mounted on a drop tower rig. (a) HV DC-DC converter and control electronics. (b) Camera. (c) Light panel. (d) Test cell. \label{fig:rig}}
 \end{figure}
 
-\section{Experimental Methods}
-The DDT uses a dual capsule design, inspired by the 2.2 s facility at NASA Glenn Research Center, which decouples drag acceleration felt by the external drag shield from the experiment.
-The experiment experiences approximately $\lesssim 1 \times 10^{-4}$ $g_0$ during free-fall for 2.1s as the rig and drag shield plummet to the bottom of drop tower 6 stories below.
-Single drops of distilled water in a range of volumes ($0.01 \leq R_d \leq 0.5$ mL) are carefully deposited on charged superhydrophobic substrates using an grounded glass syringe with $\pm $1 $\mu$L accuracy and then dropped in the drop tower.
-Red dye is added to improve thresholding accuracy in trajectory digitization.
-Drop trajectories are recorded using a Panasonic HC-WX970 Camera at 120 fps with 1/3000s shutter speed.
-In a few cases where higher frame rates are required a Nikon J1 400 fps camera with a 30mm telephoto lens is used.
-The test cell is back illuminated with a diffused 6000K LED strip light source.
-
 Superhydrophobic electret substrates are prepared with surface potentials $\varphi_s = 0.7$-$4.0$ kV.
-According to a review by Sessler \cite{sessler_electrets_1987}, an electret is a dielectric material with quasi-permanent electric charge in the sense that the characteristic decay period of the electret is much greater than a practical experiment time scale.
-Electret charge may be `true' charge in the form of surface or space charges, or polarization charges such as bound charges.
-If the electret is not screened by a conductor then it produces an external electric field if the polarization and real charges do not uniformly compensate each other throughout the volume of the electret.
-For this reason electrets are thought of as electrostatic analogs to permanent magnets.
-The name \emph{electret} itself is a portmanteau to that effect conjured by Heaviside in 1892 \cite{heaviside_electrical_2011}.
-Typical commercial electrets are PTFE films on the order of 10-50 $\mu$m thick with the charge being primarily real surface charge.
-Electrets have a plethora of applications, but most germanely they have been used in Electro-Wetting On Dielectric (EWOD) devices for low-voltage manipulation of small drops \cite{wu_low-voltage_2010}.
-Real charge electrets can be produced by contact electrification, injection or deposition of charge carriers by corona discharge or electron beam, ionizing radiation, or by frictional triboelectrification.
-Dipolar electrets by contrast are produced by a combination of polarization at elevated temperatures in a strong external electric field followed by an annealing process.
-Effective surface charge densities are limited to the material dielectric strengths due to internal dielectric breakdown phenomenon which typically occurs before external breakdown or Paschen breakdown.
-
 We use an isothermal electret formation process which is a variation of the widely applied corona-charging technique.
-Typical corona-charging techniques uses strong inhomogenous DC electric fields to produce discharge in air at ambient conditions; the dielectric substrate is atop a grounded electrode and there is a screening potential electrode intermediately positioned to control the surface potential.
-The surface potential of the dielectric will tend to saturate at this grid potential if the material is not space-charge current limited.
-The corona field is usually produced by a pin-shaped electrode.
-In air the most common charge carriers thus produced are $\mbox{CO}_3^-$ ions.
-This approach is known to generally produce samples with fairly uniform surface charge densities.
-Some work by van Turnhout \cite{van_turnhout_thermally_1975} using Thermally Stimulated Current (TCS) measurements showed that in 4.8 mm thick polymethyl methacrylate (PMMA), polarization of the dielectric is non-uniform due to real space-charge mostly ($\sim$90\%) residing in a thin (0.1-0.2 mm) layer near the free-surface of the sample.
-In this work we use a Ptec IN5120 balanced AC corona ion source to direct a net neutral stream of ions towards the dielectric target, which we polarize by an electrode with an EMCO P20P $2$ kV$+$ absolute reference DC-DC converter.
+A Ptec IN5120 balanced AC corona ion source directs a net neutral stream of ions towards the dielectric substrate, which we polarize by an electrode with an EMCO P20P $2$ kV$+$ absolute reference DC-DC converter.
 The ion stream compensates the surface and space bound charges arising due to the polarization of the dielectric.
 When the DC-DC converter is switched to ground the deposited negative ions remain on the surface.
-
-The electret is lamina of 3 to 4 0.4 mm thick corona charged PMMA sheets.
+The electret is lamina of 3 to 4 0.4 mm thick corona charged polymethyl methacrylate (PMMA) sheets.
 The electric field strength scales with the number of dielectric lamina as has also been shown in work on electret based vibrational energy harvesters \cite{wada_stacking_2012} and in water desalinization \cite{ni_desalination_2005}.
+The RC time constant for decay of the surface charge is $\tau \approx 2000$ s.
 
 The electret is established on a superhydrophobic substrate produced by laser etching PMMA and depositing a thin layer of PTFE on the roughened surface.
-The surface charge density can be modulated during the experiment using the high-voltage DC-DC converter, which can re-polarize the dielectric substrate by means of an embedded electrode.
-The resulting bound charge partially or fully neutralizes the electric field due to the surface ions deposited by corona charging of the electret.
-The high-voltage system is armed manually before the drop tower experiment and is automatically safed by a high-voltage power switching relay, which switches the load across a 100 k$\Omega$ resistor when triggered by the resumption of 1-$g_0$ conditions.
-The safing is set by an accelerometer pin-interrupt triggered microcontroller command.
-The rig with a mounted experiment is shown in Figure \ref{fig:rig}.
+We use a laser-etched pillared geometry with pillar heights $\sim \hspace{-1mm} 775$ $\mu$m, widths $\sim \hspace{-1mm} 70$ $\mu$m, and pitch $\sim \hspace{-1mm} 100$ $\mu$m.
+An SEM image of the pillar geometry is shown in Figure \ref{fig:SEM}.
+Contact angles of distilled water on the electret, measured using the tangent method, are $\sim \hspace{-1mm} 150^{\circ}$.
+The hysteresis of the contact angle (the difference between the advancing $\theta_a$ and receding $\theta_r$ contact angles) is estimated from the roll-off angle using the model of Furmidge \cite{furmidge_studies_1962}, and is found to be approximately $25^{\circ} \pm 10^{\circ}$ when the surface is uncharged.
+
 \begin{figure}
@@
     \def\svgwidth{\columnwidth}
-        \subfloat[]{%
-        \input{../figures/rig.pdf_tex}%
-}
-
-        \subfloat[]{%
-        \includegraphics[width=0.45\textwidth]{close_up}%
-}
-    \caption{(a) The electro-drop bounce experiment hardware mounted on a drop tower rig. (b) Close up of the experimental test cell.\label{fig:rig}}
-\end{figure}
-
-Contact angles of distilled water on the electret are $\sim \hspace{-1mm} 150^{\circ}$.
-The hysteresis of the contact angle (the difference between the advancing $\theta_a$ and receding $\theta_r$ contact angles) is estimated from the roll-off angle using the method of Furmidge \cite{furmidge_studies_1962}, and is found to be approximately $25^{\circ} \pm 10^{\circ}$ when the surface is uncharged.
-A contour plot of the Furmidge model is provided in Figure \ref{fig:hysteresis}.
-The contact angle for water on smooth PTFE is $\approx 115^{\circ}$ and is further enhanced by an air layer maintained in the underlying roughness length scales of the surface.
-We use a laser-etched pillared geometry with pillar heights $\sim \hspace{-1mm} 775$ $\mu$m, widths $\sim \hspace{-1mm} 70$ $\mu$m, and pitch $\sim \hspace{-1mm} 100$ $\mu$m.
-An SEM image of the pillar geometry is shown in Figure \ref{fig:SEM}.
-\begin{figure}
-    \centering
-    \input{../figures/hysteresis.pgf}
-       \caption{The Furmidge model of the hysteresis of the contact angle plotted as a function of static contact angle $\theta$ and roll-off angle $\alpha$ for $1$ mL drops.
-The measured static contact angles and roll-off angles of several superhydrophobic surfaces including the laser-etched PMMA used in this work are also shown annotated with the characteristic roughness lengthscale $R_q$ of the surface.\label{fig:hysteresis}}
-\end{figure}
-
-\begin{figure}
- \centering
- \includegraphics[width=0.65\textwidth]{../figures/SEM.pdf}
- \caption{SEM image of the superhydrophobic surface.\label{fig:SEM}}
+        \includegraphics[width=0.4\textwidth]{../figures/close_up.pdf}
+    \caption{Close up of the experimental test cell.\label{fig:SEM}}
 \end{figure}
@@
 Surface potentials $\varphi_s$ are measured on the superhydrophobic surface using a Simco-Ion FMX-004 electrostatic fieldmeter and the method for determination of surface charge density for low conductivity polymers described in Davies \cite{davies_examination_1967}.
-This measurement is made with the electret substrate bonded to a conductive ground plane by conductive tape far from the presence of other conductors.
-An ideal approach to determining surface charge on a dielectric surface is to screen perturbing effects of external electric fields.
-This is partly accomplished by grounding the fieldmeter and by placing the dielectric sample on a grounded conductive plate backing.
-In this case the surface charge density is determined from $\sigma = \varphi_s \kappa \epsilon_0/l,$ where $l$ is the thickness of the dielectric surface.
-The measured surface voltage is a function of position away from the charged dielectric.
-In most cases this function is relatively constant at a distance of about 1-2 cm away from the surface though we note that there is some measurement error in surface voltage due to small mispositioning of the electrostatic fieldmeter, say by $\pm$1 mm.
+For this measurement the fieldmeter is shielded, the electret substrate rests over a conductive ground plane, and the surface charge density is determined from $\sigma = \varphi_s \kappa \epsilon_0/l,$ where $l$ is the thickness of the dielectric surface.
 The relative dielectric constant of the PMMA sheet is measured by using a 65$\times$65 mm polished aluminum parallel plate capacitor with $C = \kappa \epsilon_0 A/l$, where $C$ is the capacitance, and $A$ is the sheet area.
@@
 
-A further consideration is the possibility of the change in total charge during a typical experimental timescale.
-If we consider the drop rig to be a ground which is reasonable given that the rig is isolated from true ground, but is at some reference voltage with respect to the surface charges on the dielectric with an abundance of free charge carriers, then there will be both bulk and surface Ohmic decay of the charge on the dielectric.
-The evolution of the charge can in some cases be approximated by $\sigma = \sigma_0 e^{\frac{-t}{\epsilon \rho}}, $ where $\sigma_0$ is the initial surface charge density and $\rho$ is the bulk resistivity.
-For an example case of a surface with relative permittivity $\kappa = 3.5$ and bulk resistivity $\rho = 1.6 \times (10^{16})$ $\Omega$cm such as with the case of a 2.8 mm PMMA sheet, then the time constant $\tau = \kappa \epsilon_0 \rho$ is approximately 5000 s, which is significantly longer than the typical time period for a drop tower experiment.
-External charge decay mechanisms include compensation by environmental ionic species.
-The relative magnitudes of these charge transport mechanisms, and therefore the stability of the electret, vary drastically depending on the initial surface potential, material properties, environment, and charging method.
-In the case of unshielded electrets compensation by atmospheric ions is significant \cite{perlman_electrets_1973}.
-Because environmental convection will tend to  maintain a gradient of these ions, sealing an electret in a container from the atmosphere will effectively halt this decay mechanism.
-Atmospheric humidity and water drop condensation can also significantly increase charge decay, presumably by reducing the surface resistance \cite{haenen_characteristic_1975}.
-Examples of this decay can be seen in Figure \ref{fig:charge_decay} for differing numbers of dielectric lamina used in this experiment.
-In looking at the trends in charge decay for our electrets we notice firstly that the decay does not appear to be exponential, as in the model described above.
-Secondly, we plainly see a cross-over effect in the decay of the surface potential in our electret samples, whereby the samples charged to higher initial surface potentials decay faster and reached the lower overall final potentials.
-This is a well known effect in polyethylenes charged by corona \cite{ferreira_corona_1992}.
-\begin{figure}[htb!]
-    \centering
-    {\input{../figures/charge_decay.pgf}}
-       \caption{Charge decay in the dielectric laminates for several numbers of layers.\label{fig:charge_decay}}
-\end{figure}
-\newpage
-
-\section{Data Reduction}
-Digitization of drop trajectories requires several steps of post-processing.
-The video records are first decomposed into sequences of still images.
-Trajectories are captured using the particle tracking module in Fiji \cite{schindelin_fiji:_2012}, a derivative of the popular ImageJ \cite{schneider_nih_2012} package for scientific image analysis.
-The series is stabilized to remove the effect of drop transients from the kinematic data \cite{li_image_2008}.
-The series of still images is cropped and the low-entropy pixels are removed using a built-in rolling ball algorithm.
-Each still is then split into its constituent RGB maps.
-In this case the green channel images contain the most information.
-These are globally thresholded using the Triangle algorithm to recover a map of the pixels corresponding the approximate position of the drop in the original still image.
-Ellipses are fitted to the pixel map stepping through the time series to determine the positions of the center of mass and the semi-major and semi-minor axes of the drops during the drop tower test.
-Finally, a perspective correction is applied to the center-of-mass positions.
-
-The code, raw data, and make files for this thesis are archived on the open-source project portal Github \cite{schmidt_droplet_electro-bounce:_2017}.
-
-\section{Parameter Estimation}
-Using various scaling arguments we have gleaned from our simple model a series of dimensionless numbers characteristic of drop bounce apoapses and times of flight.
-These dimensionless numbers depend on physical properties not all of which are easily measured by experiment.
-Drop free charge $q$ in particular could in principle be directly measured by collecting the charged drops in a Faraday cup under low-g and measuring the change in capacitance of the cup using a high input-resistance electrometer.
-But this method is burdensome to apply in practice in a drop tower.
-Other variables we can directly measure with varying levels of accuracy.
-
-To measure the charge $q$ we must use parameter estimation techniques. Our work flow to identify $q$ in an individual drop tower experiment is as follows:
-\begin{enumerate}
-\item Experimentally vary $V_d$ and $\sigma$, capturing drop trajectories using a high-speed camera.
-\item Digitize drop trajectories via automatic tracking of ellipse-fitted centers of mass on the thresholded video.
-\item Slice drop trajectories by their bounce minima and apply a smoothing filter.
-\item Extract the drop charge as well as other experimental parameters by maximizing the log-likelihood of the data given the dynamical model by varying the parameter vector using a direct search optimization.
-\end{enumerate}
-
-Mathematically we state that we find the parameters $\mathbf{x}$ that solve the inverse problem $G(\mathbf{x}) = \mathbf{d}$ using the Nelder-Mead direct search method to maximize the log-likelihood of the data.
-This is equivalent to minimizing the $\chi^2$ goodness-of-fit between an experimentally observed drop trajectory and the trajectory predicted by Equation \ref{gov_eqn_subs} given a vector of parameters $\mathbf{x} = \left\langle q, \hspace{2 mm} V_d, \hspace{2 mm} \sigma \right\rangle$.
-This problem is stated as
+\subsection{Parameter Estimation}
+We find the parameters $\mathbf{x}$ that solve the inverse problem $G(\mathbf{x}) = \mathbf{d}$, where the model $G(\mathbf{x})$ describes some relationship between the vector of parameters $\mathbf{x}$ and a set of (ideal) observations $\mathbf{d}$.
+We seek the parameter set $\mathbf{x} = \left\langle q, \hspace{2 mm} V_d, \hspace{2 mm} \sigma \right\rangle$ that has the highest probability of observing the data (the maximum of the posterior Probability Density Function) which can be determined by maximizing the log-likelihood (or equivalently minimizing $\chi^2$ goodness-of-fit) of the data $\mathbf{d}$ with respect to the the model, which is generally a numerical solution to Equation \ref{gov_eqn_subs}.
+This problem is formally stated as
 \[
@@
 \end{eqnarray*}
-where $y_G(t, \mathbf{x})$ is the $y$-coordinate position at time $t$ of the numerical solution of the equation of motion
-\[
-m y'' = \frac{1}{2} \rho C_D A_d {y'}^2 + q E(y) + K q^2 y^{-2}, \]
-where $y_d(t)$ is the corresponding experimentally observed drop $y$-coordinate position at time $t$ and $\sigma_d$ is the standard error of the observed position.
+where $y_G(t, \mathbf{x})$ is the $y$-coordinate position at time $t$ of the numerical solution of the equation of motion, $y_d(t)$ is the corresponding experimentally observed drop $y$-coordinate position at time $t$, $\sigma_d$ is the standard error of the observed position, and $u_{exp}$ are the measurement uncertainties.
 The vector $\mathbf{x}$ that minimizes $\chi^2$ is the so called Maximum Likelihood Estimate (MLE) of the experimental parameters.
-This approach is given further explanation below.
 
-\subsection{Inverse Problems}
-Suppose we have a model $G(\mathbf{x})$ with a vector of parameters $\mathbf{x}$ and set of ideal observations $\mathbf{d}$. We then expect there to exist a relationship 
-\[G(\mathbf{x}) = \mathbf{d} .\]
-Suppose the model $G(\mathbf{x})$ is the ODE
-\[ y'(t) = f(t, \mathbf{y}, \mathbf{x}),\]
-and a collection of $n$ measurements of experimental data
-\[ \mathbf{d} = \left( t_1, \mathbf{y_1} \right), 
-\left( t_2, \mathbf{y_2} \right), ... ,
-\left( t_k, \mathbf{y_n} \right).\]
-The process of fitting a function defined by a collection of parameters to a data set is called the discrete inverse, or parameter estimation problem as opposed to the \emph{forward problem} to find $\mathbf{d}$ given $\mathbf{x}$ and $G(\mathbf{x})$.
-This is a familiar procedure when the determination of model parameters is accomplished using linear or polynomial regression.
-However there are approaches even to fitting an arbitrary function to a noisy dataset.
-In this work we use the conventional Maximum Likelihood Estimate method to identify the model parameters.
-
-Using MLE we seek to know what is the probability that this data set occurred given the set of model parameters.
-In other words, what is the likelihood of the parameters given the data.
-Bayes' Theorem holds that
-\[\mbox{prob}(X|D, I) = \frac{\mbox{prob}(D|X,I) \times \mbox{prob}(X|I)}{\mbox{prob}(D|I)}\]
-where $D$ are the observations (dataset), $X$ is the vector of parameters, $I$ is general background information about the problem including the mathematical model, and 
-\[\begin{array}{lll}
-& \centering \mbox{prob}(X|D, I) & \mbox{posterior probability density function},\\
-& \centering \mbox{prob}(D|X, I) & \mbox{likelihood function},\\
-& \centering \mbox{prob}(X|I) &  \mbox{prior probability density function},\\
-& \centering \mbox{prob}(D|I) &  \mbox{evidence}.
-\end{array}
-\]
-The posterior probability density function (PDF) $\mbox{prob}(X|D, I)$ is ultimately what we wish to estimate, the prior PDF $\mbox{prob}(X|I)$ reflects our knowledge of the system, and the evidence $\mbox{prob}(D|I)$ is the likelihood of the data based on our knowledge.
-We also note that since it only makes sense to compare the conditional PDFs for the same data we can ignore the denominator.
-We further note that the prior $\mbox{prob}(X|I)$ is fixed before our observations and so can be treated as invariant to our problem.
-We can therefore infer that $\mbox{prob}(X|D, I) \propto \mbox{prob}(D|X, I)$.
-The MLE for the model parameters $\mathbf{x_0}$ is given by the maximum of the posterior PDF, which is equivalent to the solution of the ODE given the parameters $\mathbf{x}$ that produces the highest probability of the observed data.
-Since the likelihood $\mathcal{L}(\mathbf{x}) = \prod_i^n \mathcal{P}_i$ and the probability $\mathcal{P}$ of any single observation is less than one, then the total likelihood which is the product of a large number of probabilities is vanishingly small.
-The more well-behaved log-likelihood is given by
-\[\mathcal{M} = \ln(\mathcal{L}) = \ln(\mbox{prob}(D|X, I)) = \mbox{\emph{const}} - \frac{\chi^2}{2},\]
-where 
-\[
-\chi^2 = \sum^n_{i=1} \frac{\left({y_d}_i - {y_G}_i \right)^2}{{\sigma_d}_i^2}
-\]
-is the $\chi^2$ goodness-of-fit, $y_d = y_d(t)$ is an observation of drop position at a point in time, $y_G =  y_G(t, \mathbf{x})$ is the drop position predicted by the solution to the equation of motion at time $t$, and $\sigma_d$ is the standard error of the position measurement.
-The optimal parameter set is the one with the highest probability of observing the data (the maximum of the posterior PDF) and can be determined by maximizing the log-likelihood $\mathcal{M}$ (or minimizing $\chi^2$) of the data $\mathbf{d}$ with respect to the parameter set $\mathbf{x}$.
-Thus, parameter estimation herein is a variety of optimization problem.
-
-\subsection{Smoothing}
-All optimization methods, whether explicitly or implicitly, follow gradients towards an optimum.
-In a parameter estimation problem, if we approximate these gradients by finite differences, then the noise manifests itself as amplification of the roughness in the hyper-response surface.
-Gradient-based optimizers do poorly in these situations because they tend to converge to local minima.
-While so called gradient free algorithms offer an improvement in this regard, speed of convergence and the quality of the MLE is improved by smoothing the objective function.
-This is equivalent to smoothing the underlying dataset.
-
-Our choice of smoothing approach depends principally on the nature of the errors in the dataset.
-The sources of error include misalignment of the camera, error in the fiduciary length scale, perspective due to objects being out of the photographic plane, and various errors arising in the digitization process including the difference between the thresholded ellipse-fitted centroid and the true centroid of the non-ellipse drop centroid.
-Some of these errors are systematic in origin and introduce consistent biases into the data, e.g., coherent spectral sources rather than truly stochastic noise.
-Data smoothing does little to help systematic errors in that they are usually of lower frequency than the signal.
-Random errors by contrast are assumed to have a Gaussian distribution as required by the central limit theorem and are independent of the signal which we assume results from an inherently deterministic process.
-
-We experimented with a variety of filters implemented in the \verb|scipy.signal| Python \emph{SciPy} \cite{oliphant_python_2007} module on a representative set of trajectory data; these methods include 1D Gaussian convolution, Wiener, Butterworth, and Savitsky-Golay filters.
-Qualitatively comparing these smoothing methods by hand-tuning filter orders and window sizes, we find that we loose too many data points in the smoothing process, that large amplitudes are overly smoothed by repeated filtering passes, or that there are significant end effects for most of these methods.
-A comparison of these smoothing approaches on a representative trajectory data set is shown in Figure \ref{fig:y_filtered}.
-\begin{figure}[htp]
-    \centering
-    \subfloat[]{%
-  \input{../figures/y_filtered.pgf}%
-}
-
-     \subfloat[]{%
-    \input{../figures/dy_filtered.pgf}%
-}
-       \caption{(a) Schematic noisy drop trajectory data.
-We see that 1D Gaussian convolution and Wiener filters suffer from significant end effects.
-At this scale Butterworth and Savistsky-Golay filters are nearly indistinguishable.
-(b) Comparing Butterworth and Savitsky-Golay filtered first derivatives of the above schematic trajectory we see that the Butterworth filter also suffers from a slight end effect.
-This implies that the optimization will find a different optima of the likelihood depending on which type of filter is used.}
-      \label{fig:y_filtered}
-\end{figure}
-%\begin{figure}
-%    \centering
-%    \input{../figures/dy_filtered.pgf}
-%    \caption{Comparing the first derivatives of the Butterworth and Savitsky-Golay filters we see that the Butterworth filter also suffers %from a slight end effect.
-This implies that the optimization will find a different optima of the likelyhood depending on which type of %%filter is used.\label{fig:dy_filtered}}
-%\end{figure}
-\begin{figure}
-    \centering
-    \input{../figures/power_spectra.pgf}
-    \caption{Signal power spectra with peak at 1 Hz, which is the drop trajectory parabola itself, and smaller peaks in the kHz range corresponding to various noise frequencies.
-The Savitsky-Golay and Butterworth filters appear to have the least distortion and attenuate the noise at the 2 kHz peak.
-\label{fig:power}}
-\end{figure}
-The Savitsky-Golay and Butterworth filters both produce fairly smooth derivatives but the small window-size needed for Butterworth filter tends to also produce noticeable end effects.
-The Savitsky-Golay filter essentially uses a moving-window based on local least-squares polynomial approximations.
-It was shown that fitting a polynomial within a moving window and then evaluating the resulting polynomial at a single point within said window is equivalent to a discrete convolution with a fixed impulse response \cite{savitzky_smoothing_1964}.
-A beneficial property of this kind of low-pass filter is the tendency to maintain waveform amplitudes, and so they are attractive in applications having noisy signals with sharply pointed waveforms such as ultrasound or synthetic aperture radar \cite{schafer_what_2011}.
-Because Savitsky-Golay is a Finite Impulse Response (FIR) filter it requires data points to be equally spaced.
-To accommodate this requirement we interpolate points between the small gaps which sometimes occur in the tracking results from image analysis.
-We use a moving window size slightly smaller than the length of the current bounce in a single drop jump data set.
-The windows are piecewise defined by partitioning the data set into a series of individual bounces.
-This partitioning is accomplished by slicing the dataset at minima identified after an initial rough smoothing pass using the \verb|scipy.signal.argrelextrema()| function.
-The Savitsky-Golay polynomial order is 4.
-
-To understand how these filters differ it is useful to look at their frequency responses.
-The power spectra for these same data, obtained by Discrete Fourier Transform, are shown in Figure \ref{fig:power}.
-We note that our signal is not truly periodic.
-
-\subsection{Optimization}
-Most generally, a constrained optimization problem is stated as 
-\[
-\begin{array}{lll}
-\mbox{minimize:} & \hspace{2 mm} f\left(\mathbf{x}\right) & \mbox{objective function,}\\
-\mbox{subject to:} & & \\
-& \centering g_j \left( \mathbf{x} \right) \leq 0 & \mbox{inequality constraints,}\\
-& \centering h_k \left(\mathbf{x} \right) = 0 & \mbox{equality constraints,}
-\end{array}
- \]
-\[ 
-\begin{array}{ll}
-\mbox{where} \hspace{2 mm} \mathbf{x} = \left\{ \begin{array}{ll}
-x_1 & \\
-x_2 & \\
-\vdots &\\
-x_n &
-\end{array} \right. & \mbox{design variables.}
-\end{array}
-\]
-Mathematical optimization is the problem of finding minima of a function $f$.
-In this context the function is called the cost or objective function.
-The field of mathematical optimization is as old as calculus itself and the number of particular optimization techniques is correspondingly myriad.
-Particular techniques lend themselves well to particular types of optimization problems.
-The minima of the objective function $f$ is sought on a domain $A$ specified by the constraints of the problem, where the domain is usually called the feasible region.
-Minima of objective function $f: A \rightarrow \mathbb{R}^m$ are called feasible solutions.
-If the function $f$ is convex the feasible solution is the global minimum- otherwise additional local minima exist.
-The scale of the optimization problem is set ultimately by dimensionality of the objective function.
-Functions may not always be smooth in the sense of having continuous derivatives, and this is problematic in that optimization methods fundamentally rely on gradients of the objective function.
-Problems with anisotropic objective functions where there is strong covariance between the parameters are called ill-conditioned.
-In such cases the gradient vector differs significantly from the Newton direction $-\mathbf{H}^{-1} f' ( \mathbf{x} )^T$, where $\mathbf{H}$ is the Hessian matrix.
-Gradient-based deterministic search algorithms tend to converge slowly for ill-conditioned problems as they take a zigzagging path determined by the local value of the gradient rather than following the Newton-direction vector towards the minimum.
-Numerical optimization may deal with black box functions where we do not have an explicit mathematical expression of the function we are optimizing.
-Black box problems are challenging because we do not have access to analytic gradients of the objective function and approximating them by finite-differences is slow and noisy.
-In general, noisy, black box, non-linear, non-quadratic, non-convex, constrained, ill-conditioned, high-dimensional objective functions are problematic to optimize.
-Unfortunately, problems of this type are the essence of parameter estimation and of our problem particularly.
-These difficulties often lead to the characterization of parameter estimation as an `art' rather than a science.
-
-The equation of motion behaves stiffly due to the large disparity in Coulombic and image charge length scales.
-We integrate it numerically using the \verb|odeint| \emph{Scipy} module.
-This is a shake-and-bake Python wrapper for the venerable 1982 \emph{netlib ODEPACK} library double-precision \verb|lsoda| integrator \cite{hindmarsh_odepack_1983} (Livermore Solver for Ordinary Differential equations with Automatic method switching for stiff and nonstiff problems).
-The function switches dynamically between Adams (nonstiff) and Backwards Differentiation Formulas (BDF, stiff) according to the stiffness of the solution.
-
-Our specific optimization problem is non-convex, mixed discrete-continuous black-box (noisy), and highly ill-conditioned which is essentially the worst case scenario for an optimization problem.
-The ill-conditioning arises due to the strong covariance between several of the model parameters, particularly $q=q(V_d, E_0)$.
+Because Equation \ref{gov_eqn_subs} behaves stiffly we integrate it using the \emph{netlib ODEPACK} library double-precision \verb|lsoda| integrator wrapped within the \verb|odeint| \emph{Scipy} \cite{oliphant_python_2007} module in Python.
+The optimization problem in this case is non-convex, mixed discrete-continuous black-box (noisy), and highly ill-conditioned.
+The ill-conditioning arises due to the strong covariance between several of the model parameters, namely $q=q(V_d, E_0)$.
 The non-convexity of the problem implies that there are many local minima of the objective function.
-While in principle a gradient-based optimizer (i.e., the quasi-Newton method of Broyden, Fletcher, Goldfarb, and Shanno (BFGS) \cite{nocedal_numerical_2006}), could be used by using finite-differences to obtain approximate gradients of the $\chi^2$ objective function, doing so in practice is problematic because the noise-to-signal ratio of the objective function scales like $\mathcal{O}(f)$ for $df/dt$ and $\mathcal{O}(f^2)$ for $d^2f/dt^2$ which will tend to cause convergence to a local minima that is only an artifact of the likelihood response surface \cite{wood_data_1982}.
-As a further practical matter, if evaluating the objective function is computationally expensive, as in our problem, then gradient-free approaches tend to converge faster regardless \cite{kolda_optimization_2003}.
-
 We use a gradient-free direct-search Nelder-Mead \cite{nelder_simplex_1965} algorithm implemented in \verb|scipy.optimize|.
 Nelder-Mead is relatively robust to noise and is thrifty with our computationally expensive function-calls.
-Nelder-Mead, sometimes called simplex-search or downhill-simplex, is a heuristic search method with no guarantee of optimal solutions.
-It nonetheless is a well-established and widely used algorithm.
-Nelder-Mead is based on the concept of an $N$-simplex, which generalizes a triangle into higher dimensions as a polytrope of $N + 1$ vertices in $N$ dimensions.
-It uses only-function calls and expands or contracts the simplex according to the function values at its vertices in a way visually reminiscent (in $\mathbb{R}^3$) of the oscillations of the jumping drops themselves.
-In fact Nelder-Mead is sometimes also called the `amoeba method'.
-Little is known about the convergence properties of the Nelder-Mead algorithm in its classical form for non-smooth objective functions \cite{price_convergent_2002}, except that in general it does not satisfy the properties required for convergence by other direct search algorithms: the simplex remains uniformly non-degenerate and some form of sufficient descent condition for function values at the vertices is required at each iteration.
-Scaling can help solve convergence problems and improve numerical stability.
+Experimental trajectory data is smoothed using a Savitsky-Golay filter \cite{savitzky_smoothing_1964} to improve the convergence characteristics of the optimizer.
+This filter is implemented in the \verb|scipy.signal| Python \emph{SciPy} module.
 We precondition the optimization problem by minimizing $\ln(\chi^2)$ and using a naive $\sim \mathcal{O}(1)$ scaling of our constraints by their initial guesses.
 Here the goal is to make the problem equally sensitive to steps in any direction.
-Nelder-Mead is not a global optimizer, though there are variants which use sequential local searches with probabilistic restarts to improve globality, usually at a tremendous computational cost.
-However, Nelder-Mead behaves less locally than many gradient-based approaches.
-The convergence history of the parameter MLE using Nelder-Mead for a single drop jump experiment is shown in Figure \ref{fig:convergence}.
-As is typical with Nelder-Mead much of the improvement in $\chi^2$ is realized in the first few iterations.
-Overall the rate of convergence is sub-linear, which is to be expected for non-linear constrained problems using an heuristic algorithm.
-Results of the parameter estimation are shown in Figures \ref{fig:trajectories} and \ref{fig:inverse_problem}.
+The so-called identifiability problem of bounding uncertainty of the parameter estimates is resolved by constraining the parameter values by our experimental observations of them and their associated measurement uncertainties.
+Because Nelder-Mead cannot be used for explicitly constrained problems we implement the constraints by using an exterior penalty function.
+In the case of $q$, which we do not directly observe in experiment, we bound identifiability by using a Montecarlo bootstrap approach [WIP].
 
@@
     \centering
-    \input{../figures/convergence.pgf}
-    \caption{Convergence history of MLE optimization by the Nelder-Mead algorithm for a typical drop trajectory. \label{fig:convergence}}
-\end{figure}
-
-%\newpage
-\begin{figure}[h]
-    \centering
-    \resizebox{\textwidth}{!}{\input{../figures/jump_matrix.pgf}}
-    \caption{A series of filtered drop trajectories arranged by increasing apoapse.
-The blue dots represent either the beginning and end of the experiment, or points at which the drop is either coming into or leaving contact with the surface.}
-    \label{fig:trajectories}
-\end{figure}
-%\newpage
-\begin{figure}[h]
-    \centering
-    \resizebox{\textwidth}{!}{\input{../figures/inverse_problem2.pgf}}
+    \resizebox{0.5\textwidth}{!}{\input{../figures/inverse_problem2.pgf}}
     \caption{A set of drop trajectories showing the results of the parameter estimation.
@@
 \end{figure}
-%\newpage
 
-\subsection{Identifiability}
-That we are capable of fitting any arbitrary model to a dataset given sufficient degrees of freedom in our parameters is admittedly a disconcerting issue, begging the question `given the structure of the model is it possible to uniquely estimate the unknown parameters?' This question is called the problem of identifiability.
-However, apart from the drop free charge the inverse model parameters are constrained by our experimental observations of them and their associated measurement uncertainties.
-This we hope makes the specter of an over fit model less worrisome, but does convert our unconstrained optimization problem to an constrained one which raises special difficulties of its own, which we discuss below.
-
-The Nelder-Mead direct search method cannot be used with explicitly constrained problems.
-However, there are various implicit approaches to approximately solve general constrained problems using unconstrained algorithms.
-Generally, this is achieved by domain transformations or the use of penalty functions.
-By the addition of a penalty function which depends in some way on the values of the constraints to the objective function, we minimize a pseudo-objective function where the in-feasibility of the constraints is minimized simultaneously to the objective function.
-
-There are various penalty function schemes.
-We use an exterior penalty function as a simple way of converting converting the constrained problem into an unconstrained one.
-These are especially useful in cases where the constraints are not `hard' in the sense that they need to be precisely satisfied.
-General penalty functions, which are sequential unconstrained minimization techniques, reformulate the general constrained problem as the pseudo-objective function given by
-
-\[ \phi(\mathbf{x}, r_p ) = F(\mathbf{x}) + r_p P(\mathbf{x}), \]
-where the penalty function $P \left( \mathbf{x} \right)$ is given by
-\begin{equation} \label{exterior}
- P( \mathbf{x} ) = \sum_{j = 1}^m \left( \mbox{max} \left[ 0, g_j(\mathbf{x} ) \right] \right)^2 + 
-\sum_{k = 1}^l \left[ h_k( \mathbf{x}) \right]^2 .
-\end{equation}
-We see from Equation \ref{exterior} that there is no penalty if the inequality constraints $g_j(\mathbf{x})$ and equality constraints $h_k(\mathbf{x})$ are satisfied.
-
-As with penalty function approaches generally, the exterior penalty function has the drawback of the objective function possibly being undefined outside of the set of feasible solutions.
-Additionally, by naively encouraging feasibility of the solution using large values of the penalty parameter $r_p$ we will tend to ill-condition the unconstrained formulation of the problem, though in our implementation the preconditioning tends to make the pseudo-objective function less and less sensitive to the constraints as the likelihood is approaches a maximum.
-We use the measured values of $U_0$, $V_d$, and $E_0$, and the informed guess $q \approx k V_d^{2/3} E_0$ where the constant $k \approx 1 \times 10^{-11}$ is an initial guess for the parameter vector $\mathbf{x}$.
-We stop the optimization after 300 iterations rather than waiting for convergence.
-
-We are interested in the variance and co-variance as a means to determine the quality of the parameter estimate.
-The $\left( i, j \right)$-th element of the matrix $\sigma (\mathbf{x}, \mathbf{y})$ is equal to the covariance $\mbox{cov}(X_i, Y_j)$ between the $i$-th scalar component of $\mathbf{x}$ and the $j$-th scalar component of $\mathbf{y}$.
-Here the concept of error bars in linear correlation associated with a covariance matrix is not suitable.
-However, there is another approach to find the covariance matrix, given by
-\[ \left[\sigma^2 \right]_{ij} = -\left[ \left( \nabla^2 \mathcal{L}\right)^{-1}\right]_{ij} = 2 \left[ \nabla^2 \left( \chi^2\right)\right]_{ij}^{-1} = -\mathbf{H}^{-1},\]
-where $\left[\sigma^2 \right]_{ij}$ is the covariance matrix.
-The issue of identifiability is especially fraught for non-linear black-box type problems were it is difficult to explicitly evaluate the Hessian.
-The likelihood function, and thus the posterior probability density function, are defined completely by the optimal solution $\mathbf{x}$ and the second derivative of $\mathcal{L}$ at the maximum, which corresponds to the covariance matrix.
-The standard errors, or marginal variances, are the square roots of the diagonal of the covariance matrix.
-The Hessian matrix must be negative definite for $\mathcal{L}$ to have a maximum at $\mathbf{x_0}$.
-We obtain an approximate Hessian using the approach suggested in Nelder's original paper by fitting quadratics to the simplex vertices and midpoints in the vicinity of the optima \cite{nelder_simplex_1965, spendley_sequential_1962}.
-Thus armed with the Hessian we may use the condition number
-\[ \mbox{cond} (\mathbf{H}) = \frac{\mbox{max}(\mbox{eig}(\mathbf{H}))}{\mbox{min}(\mbox{eig}(\mathbf{H}))}, \]
-to make a qualitative assessment of the stability of the problem.
-Among our parameter estimate MLE optima we find large typical condition numbers $\sim \mathcal{O}(10^{27})$.
-In fact, in many cases our Hessian is not negative definite or invertible at the minmima $\mathbf{x}_0$, which implies unphysical negative values of the variances.
-These issues indicate the problem is extremely ill-conditioned near the minima $\mathbf{x_0}$.
-Given that the parameter estimates are highly co-linear, it is unsurprising that the Hessian matrix is near-singular and its inversion is either impossible or involves significant numerical error.
-A posteriori verification of the results is crucial to bound the identifiability of the parameter estimation problem, but this remains as future work.
-Several sources suggest sensitivity analysis of the parameter estimates by generation of synthetic Monte Carlo data sets as a means of establishing identifiability \cite{bevington_data_1969, jaqaman_linking_2006}.
-
-\section{Summary}
-The objectives of our experimental work are to validate the earlier scaling results by identifying values of the physical parameters which appear in the relevant dimensionless groups.
-To accomplish this we conduct a series of low-gravity experiments in a 2.1 s drop tower, where we observe the trajectories of spontaneous drop jumps and rebounds from charged dielectric superhydrophobic substrates.
-Our procedure to quantify these physical parameters is itemized below:
-\begin{itemize}
-\item  In drop tower experiments we vary the independent variables $V_d$ and $\sigma$ and capture the trajectories of the drops using high-speed video. 
-\item We produce superhydrophobic electret substrates with surface potentials 0.7-4.0 $kV$ and contact angles $\sim 150^{\circ}$ with approximately $25^{\circ}$ contact angle hysteresis when uncharged.
-The dielectrics are a lamina of 3-4 corona charged 0.4 mm PMMA sheets.
-The electric field scales with the number of dielectric lamina.
-The superhydrophobic layer of the electret lamina is manufactured by laser etching a $\sim$775 $\mu$m deep square array of pillars into the PMMA sheet, followed by a PTFE spray deposition process.
-\item We solve the inverse problem to identify key parameters which we cannot measure directly in the drop tower experiments.
-This is accomplished by Maximum Likelihood Estimation using a constrained direct search optimization.
-\end{itemize}
-
-\chapter{Results}
-\section{Parameter Estimates}
+\section{Results}
+\subsection{Parameter Estimates}
 We determined the distribution of most probable experimental model variables values for a population of the drops jumped in drop tower tests shown in Figure \ref{fig:scatter}.
@@
 This co-linearity is likely the source of the ill-conditioning issues in the parameter estimation process.
-However, assuming the main effect is the interaction between charge and electric field, a Robust Least Squares model fit $q \sim kAE_0$ using the Python \verb|statsmodels.formula.api.RLM()| function with the non-linear transformation $A = V_d^{2/3}$ finds that $k=5.01 \times 10^{-11} \pm  2.85 \times 10^{-11}$ F/m with $R^2 = 0.946$.
-This model uses Huber's T norm, median absolute scaling, and H1 covariance estimation.
-A contour plot showing the estimated drop free charge as a function of $V_d$ and $\varphi_s$ is shown in Figure \ref{fig:charge}.
+However, assuming the main effect is the interaction between charge and electric field, a Robust Least Squares model fit $q \sim kAE_0$ with the non-linear transformation $A = V_d^{2/3}$ finds that $k=5.01 \times 10^{-11} \pm  2.85 \times 10^{-11}$ F/m with $R^2 = 0.946$.
 \begin{figure}[h]
     \centering
-    \resizebox{12cm}{!}{\input{../figures/scatter.pdf_tex}}
+    \resizebox{0.5\textwidth}{!}{\input{../figures/scatter.pdf_tex}}
     \caption{Scatter plot matrix of main parameters $E_0$, $U_0$, $V_d$, and $q$.\label{fig:scatter}}
-\end{figure}
-\begin{figure}[h]
-    \centering
-    \input{../figures/charge.pgf}
-    \caption{Charge $q$, as a function of the measured variables $V_d$, $\varphi_s$.\label{fig:charge}}
 \end{figure}
@@
 A two-way T-test comparison of charge distributions between the drop bounce experiment and a corollary experiment with zero electric field at the time of drop deposition on the superhydrophobic surface suggests that the drop charge is primarily induced by the electric field, rather than through contact charging on the PTFE layer ($t = 5.11$, $p = 0.0002$).
-The T-test informs us that the charge distributions are about 5 times more different from each other as they are within each other, and there is a 0.02$\%$ probability that this result occurred by chance.
-This corollary experiment is documented in Appendix \ref{sec.drop_charge}.
 
@@
 
-\section{Model Validation}
+\subsection{Model Validation}
 Dimensional drop apoapses shown in Figure \ref{fig:series_s_eu} scale closely with $\mathbb{E}\mbox{u}$ as expected according to our earlier analysis.
@@
     \centering
-    \input{../figures/series_s_eu.pgf}
+    \resizebox{0.5\textwidth}{!}{\input{../figures/series_s_eu.pgf}}
     \caption{Drop trajectories as a function of $\mathbb{E}\mbox{u}$.\label{fig:series_s_eu}}
@@
     \centering
-    \input{../figures/series_s_ds.pgf}
+    \resizebox{0.5\textwidth}{!}{\input{../figures/series_s_ds.pgf}}
     \caption{Non-dimensional trajectories with the short-time scaling.\label{fig:series_s_ds}}
@@
     \centering
-    \input{../figures/times2.pdf_tex}
+    \resizebox{0.5\textwidth}{!}{\input{../figures/times2.pdf_tex}}
     \caption{Dimensional time-of-flight asymptotic estimates $t_c t_f$ compared with experimental time-of-flight $t_b$.\label{fig:times2}}
 \end{figure}
-The relative magnitudes of the simulated forces felt by the entire population of drops are shown in Figure \ref{fig:forces}.
+The relative magnitudes of the forces acting on the drops determined by the MLE solutions to Equation \ref{gov_eqn_subs} for the entire population of drop tower experiments are shown in Figure \ref{fig:forces}.
 Coulomb, image, and drag forces acting on the drops vary in typical magnitude between $\mathcal{O}(10^{-6})$-$\mathcal{O}(10^{-4})$ N.
@@
 In all other cases image forces are much stronger than drag.
-The image forces themselves rapidly become small compared to Coulomb forces for drops with apoapses $\mbox{max}\left( y\right) \gtrsim L$.
-Thus, it is reasonable to claim that for intermediate drops Coulomb force scales with inertia, while drag and image forces are small.
+As expected, the image forces themselves rapidly become small compared to Coulomb forces for drops with apoapses $\mbox{max}\left( y\right) \gtrsim L$.
 The drop with largest $\mathbb{E}\mbox{u}$ in our dataset failed to escape the electric field as the escape condition $\phi \mathbb{E}\mbox{u} / 8\pi = 0.2 < 1$ was unsatisfied.
@@
     \centering
-    \resizebox{14cm}{!}{\input{../figures/forces_all.pgf}}
-    \caption{Simulated forces acting on the drop up to the first apoapse.\label{fig:forces}}
+    \resizebox{0.5\textwidth}{!}{\input{../figures/forces_all.pgf}}
+    \caption{Simulated forces acting on drops up to the first apoapse as determined by the MLE solutions to Equation \ref{gov_eqn_subs} for all drops in the dataset.\label{fig:forces}}
 \end{figure}
 
-The covariance of $\mathbb{I}\mbox{g}$ with $\mathbb{E}\mbox{u}$ is shown in Figure \ref{fig:dnumbs}.
-Predictably, there is correlation between the dimensionless groups.
-We also see that $\mathbb{I}\mbox{g} < 1$ for all drops.
-Using an OLS regression, we find the model $\mathbb{I}\mbox{g} \sim (0.012 \pm 0.003) \mathbb{E}\mbox{u} + (0.212 \pm 0.036) $ with $R^2 =0.59$.
-\begin{figure}[htb]
-    \centering
-    \input{../figures/dnumbs.pgf}
-    \caption{Experimental covariance of $\mathbb{E}\mbox{u}$ and $\mathbb{I}\mbox{g}$.\label{fig:dnumbs}}
-\end{figure}
-
-We should note the influence of systematic error on our data.
-We assume that drops translate purely along the central axis of the electric field.
-In practice, despite the improvement in surface charge density uniformity produced by corona charging, there are still local areas of especially high charge density causing radial translation and changing $E$ not as well predicted by Equation \ref{e_field}.
-In principle, this kind of error should become small for drops that are far enough away from the charge distribution where the geometry of the charge distribution vanishes and the electric field looks like that due to a point charge.
-However, for low $\mathbb{E}\mbox{u}$ drops this error relatively increases.
-The primary sources of random error are the effect of contact line hysteresis on the drop initial velocity and of the variance in the MLE parameter estimates.
-
-\section{Suggestions for Future Directions}
+\subsection{Drop Impacts}
 In 1-$g_0$, for Weber numbers $\mathbb{W}\mbox{e} \equiv \rho U^2 R_d/\gamma >$ 0.4, impact rebound behavior on a superhydrophobic surface can be strongly influenced by damping from contact line hysteresis.
-For the low Bond and Ohnesorge numbers occurring in free-fall, the drop impact dynamics additionally include electrohydrodynamic surface wettability effects.
+For the low Bond and Ohnesorge numbers occurring in free-fall, the drop impact dynamics may additionally include electrohydrodynamic surface wettability effects.
 To date there has been little work in general on drop impacts outside of two regimes: (1) very low $\mathbb{R}\mbox{e}$ viscous drop spreading driven by capillary forces at the contact line and (2) impacts at `high' Weber numbers.
@@
 
-Our preliminary results showing the influence of $\mathbb{W}\mbox{e}$ and electrostatic Bond number $\mathbb{B}\mbox{o}_e \equiv \epsilon E_0^2 R_d/\gamma $ on drop impact dimensionless contact time $\tau$ and coefficient of restitution $C_r$ at $\mathbb{O}\mbox{h} \approx 2.2$ are shown in Figures \ref{fig:contact} and \ref{fig:restitution}.
+Our preliminary results showing the influence of $\mathbb{W}\mbox{e}$ and electrostatic Bond number $\mathbb{B}\mbox{o}_e \equiv \epsilon E_0^2 R_d/\gamma $ on drop impact dimensionless contact time $\tau$ and coefficient of restitution $C_r$ are shown in Figures \ref{fig:contact} and \ref{fig:restitution}.
 
@@
     \centering
-    \input{../figures/contact2.pgf}
+    \resizebox{0.5\textwidth}{!}{\input{../figures/contact2.pgf}}
     \caption{Dimensionless contact time $t_j/\tau$ compared with impact $\mathbb{W}\mbox{e}$ and $\mathbb{B}\mbox{o}_e$.\label{fig:contact}}
@@
     \centering
-    \input{../figures/restitution.pgf}
+    \resizebox{0.5\textwidth}{!}{\input{../figures/restitution.pgf}}
     \caption{Impact coefficient of restitution $C_r$ compared with impact $\mathbb{W}\mbox{e}$ and $\mathbb{B}\mbox{o}_e$.\label{fig:restitution}}
@@
 
-\section{Conclusion}
-This work might have stopped early had we maintained our focus on spontaneous drop jump with the key result being simply a means of mitigation for this troublesome electro-bounce phenomenon.
-In some sense this is quite easy to do as there are a plethora of commercially available static charge neutralization tools aimed at ESD control applications.
-In a low-gravity setting, if we wish to rid ourselves of these electrostatic phenomenon we need simply to neutralize dielectric surfaces in the vicinity of our controlled environment.
-A recipe for accomplishing this is provided in Appendix \ref{sec.mitigation}.
-Of course there are limitations to this approach.
-For instance, if the work involves surface chemistry on the surface requiring neutralization, depositing a layer of ions will possibly change experimental results.
-Additionally, there are cases where we do not control the environment for practical reasons.
-For example, aboard the ISS crew clothing can easily become electrostatically charged just as clothing does on Earth.
-If this  charge distribution is in the vicinity of Rayleigh-Plateau breakup of a fluid, as might happen when squirting water from a drink bag, then electrophoresis of the drops will occur after the fashion of this work.
+\begin{acknowledgments}
+This work was supported by NASA Cooperative Agreement NNX12A047A.
+I am also greatly indebted to Andrew Greenberg for his frequent and sage technical advice, and to Joe Shields for his assistance with drop tower experiments.
+\end{acknowledgments}
 
-Our experimental results have shown that the simple 1-dimensional model is reasonably accurate at predicting trajectories of charged drops.
-We conclude this thesis by turning the theory to a simple space systems application in a worked example.
-Let us say we desire to capture drops in a pre-stage to the compressor of a Rankine cycle space nuclear power system.
-We must actively capture the drops because we require a single-phase saturated vapor at the compressor inlet but do not wish to superheat or interrupt the flow.
-The drops are polydisperse and thus have a distribution of masses $m$ and velocities $U_0$.
-The working fluid is a mixture of lithium and cesium.
-The lithium droplets have high surface tension even at the high temperatures encountered in this power cycle, and an insulated electrode can possibly be made hydrophobic by means of a high temperature coating such that the drops rebound rigidly without wetting the surface of the precipitator.
-The lithium drops can also be treated as ideal conductors, and we assume the droplet velocity vector is normal to the precipitator electrode as in our work.
-The simple 1-dimensional theory of this thesis assumes the electric field due to a square charged dielectric, but other electric fields and electrode geometries are possible or desirable for the designer.
-The scaling used in this work will oftentimes remain valid as electric fields for numerous geometries contain the same near-field constant and far-field $1/y^2$ limits.
-In other cases, particularly cases with more complicated geometries, the electric field will need to be determined analytically or numerically.
-From the form of the electrostatic Euler number
-\[
-\mathbb{E}\mbox{u} = \frac{m U_0^2}{q E_0 R_d},
-\]
-we note that this dimensionless group can also be thought of as a ratio of energies: the kinetic energy $m U_0^2$ in the numerator and the electrostatic potential energy $q E_0 R_d$ in the denominator.
-If the drops enter the system at distance $H$ from the surface then the electrostatic potential energy is better described by $q E_0 H$ if the electric field is assumed to behave like $1/y^2$.
-We also note that although the velocity $U = U(t,y)$ and electric field $E = E(t,y)$ are variables, if the system is conservative this ratio of energies remains constant.
-If an engineering requirement is to capture 95\% the drops entering the compressor to mitigate damage to the turbine blades we can perform an initial sizing of an electrostatic drop precipitator using the scaling approach of this thesis.
-Let us say that two standard deviations of the drop population enter the precipitator with velocity $U_0 > 20$ cm/s and average radius $R_d = 1$ mm.
-The drops enter the system at $H=4$ cm, and the design constraints for the electrode are such that $E_0=3$ kV/m and that the electrode is 10 cm square.
-To satisfy Equation \ref{escape} requires
-\[
-\frac{q}{m} = \frac{4 \pi R_d^2 U_0^2}{L^2 E_0 H}
-\]
-From the above we find that to capture these drops a charge-to-mass ratio $q/m=4 \times 10^{-5}$ C/kg is required.
-This is one order of magnitude greater than the charge-to-mass ratios observed in this work, but can be achieved by a shielded charging electrode near an orifice in a way similar to an inkjet printer, or possibly by discharge, electron beam, or ionizing radiation emission.
-Though this example is highly contrived and departs far from the experiment reported here the results remain applicable because of the fundamental similarity in the underlying physics.
+% If in two-column mode, this environment will change to single-column format so that long equations can be displayed. 
+% Use only when necessary.
+%\begin{widetext}
+%$$\mbox{put long equation here}$$
+%\end{widetext}
 
-\appendix
-\appendixpage
-\noappendicestocpagenum
-\addappheadtotoc
+% Figures should be put into the text as floats. 
+% Use the graphics or graphicx packages (distributed with LaTeX2e).
+% See the LaTeX Graphics Companion by Michel Goosens, Sebastian Rahtz, and Frank Mittelbach for examples. 
+%
+% Here is an example of the general form of a figure:
+% Fill in the caption in the braces of the \caption{} command. 
+% Put the label that you will use with \ref{} command in the braces of the \label{} command.
+%
+% \begin{figure}
+% \includegraphics{}%
+% \caption{\label{}}%
+% \end{figure}
 
-\chapter{Parallel Plate Method}
-\label{sec.drop_charge}
-By the earlier scaling we presuppose the source of the drop bouncing behavior to be primarily Coulombic in origin (as opposed to dielectrophoretic), thus the drop must have some free charge in addition to the charge induced by the electric field.
-To determine whether this free charge arises due to contact charge or field-induction concurrent methodologies were used.
-In a corollary set of experiments we determine the drop free charge by observation of the deflection of the drops in the region of a known uniform field in a fashion inspired by Millikan's famous experiment to determine the fundamental charge of the electron.
+% Tables may be be put in the text as floats.
+% Here is an example of the general form of a table:
+% Fill in the caption in the braces of the \caption{} command. Put the label
+% that you will use with \ref{} command in the braces of the \label{} command.
+% Insert the column specifiers (l, r, c, d, etc.) in the empty braces of the
+% \begin{tabular}{} command.
+%
+% \begin{table}
+% \caption{\label{} }
+% \begin{tabular}{}
+% \end{tabular}
+% \end{table}
 
-Drops are jumped in free-fall from a superhydrophobic substrate placed between the plates of a parallel plate capacitor of known uniform electric field.
-The surface charge of the substrate is neutralized using the Ptec IN5120 ion source.
-Since the drop initial velocity $U_0$ is parallel to the electric field, the drops are inertial in the direction of the electric force, and neglecting the effect of image charges mirrored across the conductors, we can determine the magnitude of the drop charge by a balance of Coulombic force and inertia given by the equation of motion
+% If you have acknowledgments, this puts in the proper section head.
+%\begin{acknowledgments}
+% Put your acknowledgments here.
+%\end{acknowledgments}
 
-\[ y'(t) = q\mathbf{E}. \]
+% Create the reference section using BibTeX:
+\bibliography{thesis}
 
-Since the drag is negligible in the inertial limit we can find the charge $q$ by fitting a second-order least squares polynomial to the measured drop positions.
-We equate the $t^2$ term to the constant acceleration and divide by the known constant magnitude of the electric field.
-
-A 200-880 VAC source with a full wave bridge rectifier circuit is used in the experiment to measure drop charge.
-measurements show that the high-voltage source circuit AC component of the signal is appropriately small (13 mV at 35 kHz).
-The no-load current is determined to be a relatively low 80 $\mu$A.
-The high-voltage source terminals are led to two parallel polished 150x150 mm aluminum plate electrodes.
-The electrodes are mounted on an insulated 80/20 extruded aluminum rail for ease of adjustment.
-All drop charge experiments are conducted with an electrode spacing of 28.30 mm.
-With this spacing the calibrated electric field between the plates is $\mathbf{E} \approx 35$kV/m.
-The electrodes are electrically isolated from the drop rig by two alternating layers of 4 mm thick PMMA sheet and Kapton tape.
-Potential across the plates is measured periodically with a load-impedance corrected multimeter to account for battery depletion.
-The typical capacitor rise time of the plates is measured to be 1.4 s, thus to make the most economical use of the brief window a low-gravity a weighted spring-loaded switch is set by hand prior to the drop to close the high-voltage circuit, but which passively safes the system at the resumption of 1-$g_0$ conditions in the tower.
-We suppose the drop free charge, if it is indeed arises by contact with PTFE, to be some function of the drop volume and the residence time on the superhydrophobic surface.
-However, sweeping though drop volumes over a series of drop tower experiments we find little correlation between drop volume  and free drop charge.
-
-A brief screening experiment was conducted which alternated the polarity of the field by switching the positive and negative terminal leads between plates.
-Qualitative observations of drop electrode preference seem to indicate that the assumption of small polarization stress was well founded.
-Following this a orthogonal array $3^2$ factorial design experiment with two replicates was conducted to test the effect of varying drop volume and surface stay time on free charge at the time of jumping.
-It was hypothesized that free charge would increase for levels of both factors.
-ANOVA analysis using \verb|pandas| of the linear multiple regression model $q \sim a*V_d + b*t_s$, where $a$, $b$ are model fitting coefficients, for the data set indicates that neither drop volume $V_d$ ($p=0.178$), nor surface stay time $t_s$ ($p=0.939$) is significant at the 95\% confidence level.
-The overall model F-statistics (1.001 in 2 and 14 degrees of freedom), and coefficients of determination ($R^2 = 0.125$) indicate that the linear model neither fits the data particularly well, nor does it offer an improvement over the mean model.
-The mean charge was thus determined to be positive $5.3 \times 10^{-12}$ C, with a standard deviation of $4.7 \times 10^{-12}$ C.
-
-\chapter{Charge Mitigation}
-\label{sec.mitigation}
-When neutralization of static charge on the superhydrophobic surfaces used in this work is required we use the following procedure:
-\begin{enumerate}
-\item Surface potential is quickly estimated using a Simco-Ion FMX-004 electrostatic fieldmeter.
-This measurement is only quantitative for flat dielectric surfaces larger then several cm square, but can be used qualitatively for other geometries.
-This sensor should be positioned about 2.5 cm normal to the surface in question.
-For quantitative measurements the sensor conductive shell should be connected to ground, and the dielectric substrate should rest on conductive backplane.
-In any case the surface potential measurement should establish whether there is a need for charge neutralization.
-\item A Ptec IN5120 ion fan is positioned about 10 cm away from the surface.
-The ion fan issues a balanced steam of ions which will screen the net surface charge densities of the dielectric.
-The surface potential is reduced to the ion source bias (on the order of $\pm$10 V) within 2 to 10 s.
-All faces of the dielectric should be discharged under the fan, as for materials with low dielectric constants, net charge distributions will set up significant electric fields that permeate the dielectric regardless of their position.
-In other words the bulk of the dielectric does little to shield the electric field.
-\item We verify that the problematic charge has been duly compensated by the ion stream by remeasuring the surface potential with the fieldmeter.
-\end{enumerate}
-
-\singlespacing
-\backmatter
-\printbibliography
 \end{document}
+%
+% ****** End of file aiptemplate.tex ******

### 2018-08-08 doc/paper/aiptemplate.tex
added some new figures

@@
 \centering
-\includegraphics[width=0.45\textwidth]{../figures/apparatus0.pdf}
+\includegraphics[width=0.45\textwidth]{../figures/apparatus1.pdf}
 \label{apparatus}
@@
 
-Because Equation \ref{gov_eqn_subs} behaves stiffly we integrate it using the \emph{netlib ODEPACK} library double-precision \verb|lsoda| integrator wrapped within the \verb|odeint| \emph{Scipy} \cite{oliphant_python_2007} module in Python.
+We integrate Equation \ref{gov_eqn_subs} numerically using the \emph{netlib ODEPACK} library double-precision \verb|lsoda| integrator wrapped within the \verb|odeint| \emph{Scipy} \cite{oliphant_python_2007} module in Python.
 The optimization problem in this case is non-convex, mixed discrete-continuous black-box (noisy), and highly ill-conditioned.

### 2018-08-28 doc/paper/aiptemplate.tex
some paper updates

@@
 We investigate the dynamics of spontaneous jumps of water drops from electrically charged superhydrophobic dielectric substrates during a sudden step reduction in gravity level.
-In the brief free-fall environment of a drop tower, with a non-homogeneous external electric field arising due to dielectric surface charges (with surface potentials ~0.4-1.8 kV), body forces acting on the jumped drops are primarily supplied by polarization stress and Coulombic attraction instead of gravity.
-This electric body force leads to a drop bouncing behavior similar to well-known phenomena in 1-$g_0$, though occurring for much larger drops ($\sim$ 0.5 mL).
-We show a 1D model for the phenomenon, its scaling, and asymptotic estimates for drop time of flight in two regimes: at short-times close to the substrate when drop inertia balances Coulombic force due to net free charge and image charges in the dielectric substrate and at long-times far from the substrate when drop inertia balances free charge Coulombic force and drag.
+In the brief free-fall environment of a drop tower, with a non-homogeneous external electric field due to dielectric surface charges (with surface potentials ~0.4-1.8 kV), body forces acting on the jumped drops are primarily supplied by polarization stress and Coulombic attraction instead of gravity.
+This electric body force leads to a drop bouncing behavior similar to well-known terrestrial phenomena, though occurring for much larger drops ($\sim$ 0.5 mL).
+We provide a 1-dimensional model for the phenomenon, its scaling, and asymptotic estimates for drop time-of-flight in two regimes: at short-times close to the substrate when drop inertia balances Coulombic force due to net free charge and image charges in the dielectric substrate and at long-times far from the substrate when drop inertia balances free charge Coulombic force and drag.
 The drop trajectories are controlled primarily by the dimensionless electrostatic Euler number $\mathbb{E}\mbox{u}$, which is a ratio of inertia to electrostatic force.
 To experimentally determine values of $\mathbb{E}\mbox{u}$ we conduct a series of drop tower experiments where we observe the effects of drop volume, net free charge, and static surface potential of the superhydrophobic substrate on drop trajectories.
-We use a direct search optimization to obtain a Maximum Likelihood Estimate for drop net charge, as we do not measure it directly in experiment.
-For $\phi \mathbb{E}\mbox{u} /8 \pi > 1$ drops escape the electric field, where $\phi$ is a substrate to drop aspect ratio.
-However, we do not observe any escapes in our dataset.
+We use a direct search optimization to obtain a Maximum Likelihood Estimate for drop net charge, as we do not measure it directly.
+For $\phi \mathbb{E}\mbox{u} /8 \pi > 1$ drops escape the electric field, where $\phi$ is a substrate-to-drop aspect ratio.
+However, we do not observe any escapes in our dataset since only drops where $\phi \mathbb{E}\mbox{u} /8 \pi < 1$ are achieved.
 \end{abstract}
@@
 When a nonwetting, gravity-dominated sessile drop (e.g.
-a puddle), which is initially at rest on a surface in the Cassie-Baxter state suddenly undergoes a large step reduction in $\mathbb{B}\mbox{o} \equiv \frac{g R^2 \Delta \rho}{\gamma}$ it will spontaneously jump away from the surface, where $g$ is the acceleration, $R$ is the characteristic interfacial length scale, $\Delta \rho$ is the difference in densities across the interface (which simplifies to $\rho$, for large $\Delta \rho$, as in the case of an air-water interface), and where $\gamma$ is the surface tension.
+a puddle), initially at rest on a surface in the Cassie-Baxter state suddenly undergoes a large step reduction in Bond number $\mathbb{B}\mbox{o} \equiv \frac{g R^2 \Delta \rho}{\gamma}$ it will spontaneously jump away from the surface, where $g$ is the acceleration, $R$ is the characteristic interfacial length scale, $\Delta \rho$ is the difference in densities across the interface (which simplifies to $\rho$, for large $\Delta \rho$, as in the case of an air-water interface), and where $\gamma$ is the surface tension.
 The spontaneous drop jump was first observed experimentally in the Soviet Union by Kirko \emph{et al.} \cite{kirko_phenomenon_1970} in 1970 for drops of mercury in hydrochloric acid, and later by Wollman \emph{et al.} in 2016 for water drops in air in a set of experiments conducted using drop towers \cite{wollman_more_2016}.
@@
 For drops with radial symmetry and sufficiently high initial $\mathbb{B}\mbox{o}$, inward radial capillary waves coalesce at the axis, leading to geysering and creation of satellite droplets by the Rayleigh-Plateau breakup of the geyser.
-In the case of smaller jumping drops the capillary waves are gradually damped by viscous forces.
+In the case of smaller jumping drops the capillary waves are quickly damped by viscous forces.
 
@@
 The forces at work in such situations are presumably electrostatic in origin.
-A time-lapsed composite image showing an example of the phenomenon is shown in Figure \ref{fig:bounce}, and schematically in Figure \ref{fig:bounce_time}.
+A time-lapsed composite image showing an example of the phenomenon is shown in Figure \ref{fig:bounce} for a 0.5 mL drop, and schematically in Figure \ref{fig:bounce_time} for a 0.05 mL drop.
 \begin{figure}[htb]
@@
 The horizontal (surface plane parallel) components of the drop trajectory usually oscillate about some central position during the experiment (except in cases of nearly pure 1-D vertical translation).
-For especially small drops close to the spontaneous drop jump limit ($V_d \sim$ 0.01 mL) the drops do not jump, but translate across the surface in a rolling regime until either they reach a local maximum of the electric field, or until their motion is sufficiently damped by contact line hysteresis where pinning ultimately arrests their motion.
+For especially small drops close to the spontaneous drop jump limit (identified by Attari \emph{et al.} \citep{attari_puddle_2016} as $V_d \sim$ 0.01 mL) the drops do not jump, but translate across the surface in a rolling regime until either they reach a local maximum of the electric field, or until their motion is sufficiently damped by contact line hysteresis where pinning ultimately arrests their motion.
 \item The drops appear to have net free charge. In cases of multiple simultaneous drop jumps the drops repel each other as they bounce or roll in orbital motion around regions of high field.
-\item The magnitude of the drop trajectory maxima (apoapses) appear to be related to the drop volume (mass), and initial jump velocity (inertia), and to the electric field strength.
+\item The magnitude of the drop trajectory maxima (apoapses) are related to the drop volume (mass), and initial jump velocity (inertia), and to the electric field strength.
 \end{itemize}
@@
 In our work this might occur when a drop is deposited on the charged surface by a grounded syringe.
-The metal syringe needle tip, and the liquid in the syringe itself are essentially a ground connection which is broken when the syringe is suddenly removed in the presence of an external electric field.
-Field-induced charging is at work in the famous Kelvin thunderstorm, and is applied in inkjet, and electrospay technologies, where in each case the breakup is by the Rayleigh-Plateau instability.
-Notably, in Pettit's aforementioned discussion of contact charging of liquids in low-g, he remarks on accidental electrostatic `hula-ing' of silicone oil drops when ejected from a syringe in the vicinity of a highly-charged polymer surface during an experiment conducted aboard STS-5 by mission specialist Joseph Allen \cite{pettit_donald_flow_????}.
+The metal syringe needle tip and the liquid in the syringe itself are essentially a ground connection which is broken when the syringe is suddenly removed in the presence of an external electric field.
+Field-induced charging is at work in the famous Kelvin thunderstorm and is applied in inkjet and electrospay technologies, where in each case the breakup is by the Rayleigh-Plateau instability.
+Notably, in Pettit's aforementioned discussion of contact charging of liquids in low-g, he remarks on accidental electrostatic `hula-ing' of silicone oil drops when ejected from a syringe in the vicinity of a highly-charged polymer surface during an experiment conducted aboard STS-5 by Space Shuttle mission specialist Joseph Allen \cite{pettit_donald_flow_????}.
 Depending on the (highly-variable) electrical conductivity of the silicone oil, and the material of the syringe used in the experiment, the charge could arise just as easily by field-induction as by contact charging.
@@
 \centering
-\includegraphics[width=0.45\textwidth]{../figures/apparatus1.pdf}
+\includegraphics[width=0.45\textwidth]{../figures/apparatus3.pdf}
 \label{apparatus}
 \caption{Schematic representation of drop jump with return and rebound from an electrically charged superhydrophobic substrate.
-The characteristic time and length scales $t_c$ and $y_c$ describe the time of flight and apoapse associated with the drop trajectory.}
+The characteristic time and length scales $t_c$ and $y_c$ describe the time of flight and apoapse associated with the drop trajectory.
+$L$ denotes the lengthscale characteristic of the charged superhydrophobic substrate.}
 \end{figure}
@@
 Given the conductivity and permittivity in the limiting case of extremely-pure water ($ \epsilon \approx 80$, $\sigma_e = 18.2 \times 10^{6}$ $\Omega\mbox{cm}$) \cite{yatsuzuka_electrification_1994}, we estimate $\tau_e \approx 4 \times 10^{-6}$ s.
-The relaxation time for the common distilled water that is actually used in the drop experiments is undoubtedly shorter due to the presence of solvated ions.
+The relaxation time for the common distilled water that is actually used in the drop experiments is shorter due to the presence of solvated ions which tend to increase the conductivity.
 Neglecting the effects of an electric double layer on hydration of ions in the water or the ambient atmosphere due to the relatively massive size of the drops studied, the assumption of small relaxation time further implies that the free charge present in the drops will remain approximately constant during the typical time interval of a low-gravity experiment.
@@
 
-By substituting Equations \ref{dep_force}, and \ref{image_force} into \ref{e_force} we have
-\begin{eqnarray*}
- \mathbf{F}_E &=& q \mathbf{E} + \mathbf{F}_{DEP} + \mathbf{F}_I \\
+By substituting Equations \ref{dep_force} and \ref{image_force} into \ref{e_force} we have
+\begin{eqnarray}
+ \mathbf{F}_E &=& q \mathbf{E} + \mathbf{F}_{DEP} + \mathbf{F}_I \nonumber \\
  &=& q \mathbf{E} + \frac{k q^2}{16 \pi \epsilon_0 } y^{-2} \hat{\mathbf{j}} + 2 \pi R_d^3 \kappa_w \epsilon_0 K \nabla E^2, 
  \label{e_forces}
-\end{eqnarray*}
+\end{eqnarray}
 
@@
 \end{eqnarray}
-As this condition likely prevails in our experiments we henceforth neglect the DEP force.
+We assume this conditions prevails in our experiments and henceforth neglect the DEP force.
 There is some physical intuition to support this conclusion as well.
@@
 
-Thus the 1-D governing equation becomes
+Thus the 1-D governing Equation \ref{e_forces}, becomes
 \begin{equation}
@@
 \end{equation}
-Both regimes given by Equations \ref{near_field} and \ref{far_field} can be clearly seen in Figure \ref{fig:E0}.
+Both regimes given by Equations \ref{near_field} and \ref{far_field} are identified in Figure \ref{fig:E0}.
 \begin{figure}[h]
@@
 Equation \ref{gov_eqn_subs} is non-linear, non-homogeneous and must be solved numerically.
-Nevertheless we are curious if we can obtain approximate solutions to the equation analytically using perturbation methods.
-This is aided by non-dimensionalizing the governing equations, forming dimensionless groups, and determining whether any are particularly small or large, and whether any fortuitous opportunities for simplification appear.
+Nevertheless we seek approximate solutions to the equation analytically using perturbation methods.
 Introducing the scaled variables
@@
 \]
-We note that in a conservative system $\mathbb{E}\mbox{u}$ can be thought of as a ratio of energies: the kinetic energy $m U_0^2$ in the numerator and the electrostatic potential energy $q E_0 R_d$ in the denominator.
+We note that in a conservative system $\mathbb{E}\mbox{u}$ can be thought of as a ratio of kinetic energy $m U_0^2$ and the electrostatic potential energy $q E_0 R_d$.
 
@@
 \end{equation*}
-where we call $\mathbb{D}\mbox{g}$ the drag number $\mathbb{D}\mbox{g} \equiv \frac{C_D \rho_a}{\rho_l} = \mathbf{\Pi}_1 \phi^{-1}{\mathbb{E}\mbox{u}}^{-1}$, and $\phi = 4 \pi \frac{R_d^2}{L^2}$ is a dimensionless ratio of length scales.
+where we call $\mathbb{D}\mbox{g}$ the drag number $\mathbb{D}\mbox{g} \equiv \frac{C_D \rho_a}{\rho_l} = \mathbf{\Pi}_1 \phi^{-1}{\mathbb{E}\mbox{u}}^{-1}$, and $\phi = 4 \pi \frac{R_d^2}{L^2}$ is a drop-to-substrate aspect ratio.
 
 \subsection{Asymptotic Estimates}
-The scalings of the equation of motion given by Equations \ref{img_limit} and \ref{drag_limit} are weakly non-linear differential equations in the sense that they reduce to linear equations as the parameter $\mathbb{E}\mbox{u} \rightarrow 0$.
-If we take $\mathbb{E}\mbox{u}$ to be a small parameter we can find an asymptotic approximation to the solution of the non-linear equation by means of a regular perturbation.
+The scalings of Equations \ref{img_limit} and \ref{drag_limit} are weakly non-linear differential equations in the sense that they reduce to linear equations as $\mathbb{E}\mbox{u} \rightarrow 0$.
+For $\mathbb{E}\mbox{u} \ll 1$ we find an asymptotic solution of the non-linear equation by means of a regular perturbation.
 In this case we use the naive expansion
@@
 \subsubsection{Inertial Electro-Image Limit}
-By substitution of Equation \ref{regular_pert} and its derivatives into \ref{pi_terms}, and equating terms by order we first find the $\mathcal{O}(1)$ unperturbed solution
+Substituting Equation \ref{regular_pert} and its derivatives into \ref{pi_terms}, and equating terms by order we find the $\mathcal{O}(1)$ unperturbed solution
 \[{y^*_{0}}{\left ({t^*} \right )} = {t^*} + \frac{{t^*}^{2}}{2} \left(-1 - \mathbb{I}\mbox{g}\right). \]
-Looking at this solution it is evident that if $\mathbb{I}\mbox{g}=0$, the solution is the classical kinematic equation for projectile motion without drag under constant gravity $g_0$.
-Continuing on with this procedure we find, after some tedious computations documented in the project repository for this work \cite{schmidt_droplet_electro-bounce:_2017}, the $\mathcal{O}(\mathbb{E}\mbox{u}^5)$ order accurate solution truncated to $\mathcal{O}(\mathbb{E}\mbox{u}^2)$ is
+By inspection, it is evident that if $\mathbb{I}\mbox{g}=0$, the solution is the classical kinematic equation for projectile motion without drag under constant gravity $g_0$.
+Continuing on to higher order, after some tedious computations documented in the project repository for this work \cite{schmidt_droplet_electro-bounce:_2017}, the $\mathcal{O}(\mathbb{E}\mbox{u}^5)$ order accurate solution which is truncated to $\mathcal{O}(\mathbb{E}\mbox{u}^2)$ below:
 
@@
 
-We plot the approximate short-time scaled solution Equation \ref{perturb_image} with varying values of $\mathbb{I}\mbox{g}$ in Figure \ref{fig:short_times}.
+We plot the approximate short-time solution of Equation \ref{perturb_image} with varying values of $\mathbb{I}\mbox{g}$ in Figure \ref{fig:short_times}.
 
@@
 The trajectory reduces to the classical $\mathcal{O}(1)$ solution for small values of $\mathbb{I}\mbox{g}$.
-It should be noted that despite what is implied by these plots $\mathbb{I}\mbox{g}$ is not necessarily independent of $\mathbb{E}\mbox{u}$, as they share $q$, and $E_0$ as common factors, $U_0 \propto R_d^2$, and $m \propto R_d^3$.}
+It should be noted that despite what is implied by these plots $\mathbb{I}\mbox{g}$ is not necessarily independent of $\mathbb{E}\mbox{u}$ sharing $q$ and $E_0$ as common factors, and the covariance relationships $U_0 \propto R_d^2$, and $m \propto R_d^3$.}
     \label{fig:short_times}
@@
 
-As $\mathbb{E}\mbox{u}$ grows to be no longer small, the time-of-flight grows rapidly, but this behavior appears to have an asymptote at a certain critical velocity; this is an electrostatic escape velocity $U_e$.
-We can find the escape velocity by solving a modified version of the equation of motion
+As $\phi \mathbb{E}\mbox{u}$ grows to be no longer small, the time-of-flight grows rapidly with an asymptote at a certain critical velocity; this is an electrostatic escape velocity $U_e$.
+We can find the escape velocity by solving a limiting version of the equation of motion
 \[ m u' = - \frac{q E_0 y_c^2}{y^2}, \]
@@
 Using various scaling arguments we have gleaned from our simple model a set of dimensionless numbers characteristic of drop bounce apoapses and times of flight.
-These dimensionless numbers depend on physical properties not all of which are easily measured by experiment.
+The dimensionless numbers depend on physical properties not all of which are easily measured by experiment.
 In particular, direct determination of net drop free electric charge $q$ is difficult as high-input resistance electrometers are not well-suited to the sudden 15-$g_0$ decelerations characteristic of drop tower experiments.
@@
 The electric field strength scales with the number of dielectric lamina as has also been shown in work on electret based vibrational energy harvesters \cite{wada_stacking_2012} and in water desalinization \cite{ni_desalination_2005}.
-The RC time constant for decay of the surface charge is $\tau \approx 2000$ s.
+The RC time constant for decay of the surface charge is observed to be $\tau \approx 2000$ s.
 
@@
 Contact angles of distilled water on the electret, measured using the tangent method, are $\sim \hspace{-1mm} 150^{\circ}$.
-The hysteresis of the contact angle (the difference between the advancing $\theta_a$ and receding $\theta_r$ contact angles) is estimated from the roll-off angle using the model of Furmidge \cite{furmidge_studies_1962}, and is found to be approximately $25^{\circ} \pm 10^{\circ}$ when the surface is uncharged.
+The roll-off angle of a 1 mL drop is $1^{\circ} \pm 0.5^{\circ}$ when the surface is uncharged.
+The hysteresis of the contact angle (the difference between the advancing $\theta_a$ and receding $\theta_r$ contact angles) is estimated from the roll-off angle using the model of Furmidge \cite{furmidge_studies_1962}, and is found to be approximately $25^{\circ} \pm 10^{\circ}$.
 
@@
 The trajectories are shown only up to the apoapse of the first bounce.
-The (\protect\redline) \hspace{0.25 mm} lines show the ODE solution with the given MLE parameter vector.
+The (\protect\redline) \hspace{0.25 mm} lines show the numerical solution of Equation \ref{gov_eqn_subs} with the given MLE parameter vector.
 $\chi^2$ goodness-of-fit varies between $1 \times 10^{-5}$ and $1 \times 10^{-8}$ with the better fit occurring typically for the drops with the lowest apoapses.}
@@
 Equation \ref{time_improved} predicts that this drop will return to the substrate after 32 s, a period of free-fall which is lamentably well out of reach of a drop tower.
-However, such an experiment could possibly be performed aboard the ISS or suborbital parabolic flights.
+However, such an experiment could be performed aboard the ISS or certain suborbital parabolic flights.
 \begin{figure}[!htb]
@@
 This work was supported by NASA Cooperative Agreement NNX12A047A.
-I am also greatly indebted to Andrew Greenberg for his frequent and sage technical advice, and to Joe Shields for his assistance with drop tower experiments.
+We are also indebted to Andrew Greenberg for his frequent technical advice, and to Joe Shields for assistance with drop tower experiments.
 \end{acknowledgments}

### 2018-09-17 doc/paper/aiptemplate.tex
many changes to paper draft

@@
 \usepackage{import}
+\usepackage[normalem]{ulem}
 \let\pgfimageWithoutPath\pgfimage 
@@
 \newcommand{\redline}{\raisebox{2pt}{\tikz{\draw[-,red,solid,line width = 1.5pt](0,0) -- (5mm,0);}}}
+\graphicspath{ {../figures/} }
+
+\newcommand{\blueline}{\raisebox{2pt}{\tikz{\draw[-,blue,solid,line width = 1.5pt](0,0) -- (5mm,0);}}}
+\graphicspath{ {../figures/} }
+
+\newcommand{\cyanline}{\raisebox{2pt}{\tikz{\draw[-,cyan,solid,line width = 1.5pt](0,0) -- (5mm,0);}}}
 \graphicspath{ {../figures/} }
@@
 We investigate the dynamics of spontaneous jumps of water drops from electrically charged superhydrophobic dielectric substrates during a sudden step reduction in gravity level.
-In the brief free-fall environment of a drop tower, with a non-homogeneous external electric field due to dielectric surface charges (with surface potentials ~0.4-1.8 kV), body forces acting on the jumped drops are primarily supplied by polarization stress and Coulombic attraction instead of gravity.
-This electric body force leads to a drop bouncing behavior similar to well-known terrestrial phenomena, though occurring for much larger drops ($\sim$ 0.5 mL).
+In the brief free-fall environment of a drop tower, with an external electric field drop dynamics are dominated by Coulombic force instead of gravity.
+These forces lead to a drop bouncing behavior similar to well-known terrestrial phenomena, though occurring for much larger drops ($\sim$ 0.5 mL).
 We provide a 1-dimensional model for the phenomenon, its scaling, and asymptotic estimates for drop time-of-flight in two regimes: at short-times close to the substrate when drop inertia balances Coulombic force due to net free charge and image charges in the dielectric substrate and at long-times far from the substrate when drop inertia balances free charge Coulombic force and drag.
-The drop trajectories are controlled primarily by the dimensionless electrostatic Euler number $\mathbb{E}\mbox{u}$, which is a ratio of inertia to electrostatic force.
-To experimentally determine values of $\mathbb{E}\mbox{u}$ we conduct a series of drop tower experiments where we observe the effects of drop volume, net free charge, and static surface potential of the superhydrophobic substrate on drop trajectories.
-We use a direct search optimization to obtain a Maximum Likelihood Estimate for drop net charge, as we do not measure it directly.
-For $\phi \mathbb{E}\mbox{u} /8 \pi > 1$ drops escape the electric field, where $\phi$ is a substrate-to-drop aspect ratio.
-However, we do not observe any escapes in our dataset since only drops where $\phi \mathbb{E}\mbox{u} /8 \pi < 1$ are achieved.
+In both regimes the dimensionless electrostatic Euler number $\mathbb{E}\mbox{u}$, which is a ratio of inertia to electrostatic force, appears as a key parameter.
 \end{abstract}
@@
 When a nonwetting, gravity-dominated sessile drop (e.g.
-a puddle), initially at rest on a surface in the Cassie-Baxter state suddenly undergoes a large step reduction in Bond number $\mathbb{B}\mbox{o} \equiv \frac{g R^2 \Delta \rho}{\gamma}$ it will spontaneously jump away from the surface, where $g$ is the acceleration, $R$ is the characteristic interfacial length scale, $\Delta \rho$ is the difference in densities across the interface (which simplifies to $\rho$, for large $\Delta \rho$, as in the case of an air-water interface), and where $\gamma$ is the surface tension.
+a puddle)\sout{, initially at rest on a surface in the Cassie-Baxter state} suddenly undergoes a large step reduction in Bond number it will spontaneously jump away from the surface.
+The Bond number is given by $\mathbb{B}\mbox{o} \equiv \frac{g R^2 \Delta \rho}{\gamma}$, where $g$ is the acceleration, $R$ is the characteristic interfacial length scale, $\Delta \rho$ is the difference in densities across the interface \sout{(which simplifies to $\rho$, for large $\Delta \rho$, as in the case of an air-water interface)}, and where $\gamma$ is the surface tension.
 The spontaneous drop jump was first observed experimentally in the Soviet Union by Kirko \emph{et al.} \cite{kirko_phenomenon_1970} in 1970 for drops of mercury in hydrochloric acid, and later by Wollman \emph{et al.} in 2016 for water drops in air in a set of experiments conducted using drop towers \cite{wollman_more_2016}.
-The kinetic energy of the jump is supplied by the defect in free surface energy as the new minimum energy surface equilibrium has approximately constant curvature.
-The motive force is due to the inertia of internal flows which occur as the interface deflects under the suddenly lessened $\mathbb{B}\mbox{o}$.
-For drops with radial symmetry and sufficiently high initial $\mathbb{B}\mbox{o}$, inward radial capillary waves coalesce at the axis, leading to geysering and creation of satellite droplets by the Rayleigh-Plateau breakup of the geyser.
+\sout{The kinetic energy of the jump is supplied by the defect in free surface energy as the new minimum energy surface equilibrium has approximately constant curvature.} The motive force of the jump owes to the inertia of internal flows which occur as the interface deflects under the suddenly lessened $\mathbb{B}\mbox{o}$.
+For drops with radial symmetry and sufficiently high initial $\mathbb{B}\mbox{o}$, inward radial capillary waves constructively interfere at the axis, leading to geysering and creation of satellite droplets by the Rayleigh-Plateau breakup of the geyser.
 In the case of smaller jumping drops the capillary waves are quickly damped by viscous forces.
@@
 
-We have observed jumped drops to occasionally decelerate and return to the superhydrophobic surface, rebounding multiple times in the fashion of rigid bodies bouncing under 1-$g_0$.
+In the course of our work with spontaneous drop jump we have observed jumped drops to occasionally decelerate and return to the superhydrophobic surface, rebounding multiple times in the fashion of rigid bodies bouncing under 1-$g_0$.
 The forces at work in such situations are presumably electrostatic in origin.
-A time-lapsed composite image showing an example of the phenomenon is shown in Figure \ref{fig:bounce} for a 0.5 mL drop, and schematically in Figure \ref{fig:bounce_time} for a 0.05 mL drop.
+A time-lapsed composite image showing an example of the phenomenon is shown in Figure \ref{fig:bounce} for a 0.5 mL drop, and as a time-series in Figure \ref{fig:bounce_time} for a 0.05 mL drop.
 \begin{figure}[htb]
@@
 The horizontal (surface plane parallel) components of the drop trajectory usually oscillate about some central position during the experiment (except in cases of nearly pure 1-D vertical translation).
-For especially small drops close to the spontaneous drop jump limit (identified by Attari \emph{et al.} \citep{attari_puddle_2016} as $V_d \sim$ 0.01 mL) the drops do not jump, but translate across the surface in a rolling regime until either they reach a local maximum of the electric field, or until their motion is sufficiently damped by contact line hysteresis where pinning ultimately arrests their motion.
+For especially small drops close to the spontaneous drop jump limit (identified by Attari \emph{et al.} \citep{attari_puddle_2016} as $V_d \sim$ 0.01 mL) the drops do not jump, but translate across the surface in a rolling regime until either they reach a local maximum of the electric field, or until their motion is sufficiently damped by contact line hysteresis that pinning arrests their motion.
 \item The drops appear to have net free charge. In cases of multiple simultaneous drop jumps the drops repel each other as they bounce or roll in orbital motion around regions of high field.
@@
 
-We expect that if the drop electrostatic potential energy is greater than the release of surface energy under the sudden change in $\mathbb{B}\mbox{o}$, in the form of the drop kinetic energy, the drop will return to an equilibrium state on the charged surface which minimizes the potential.
-
-What is the origin of the electric field arising on the superhydrophobic surfaces?
+\sout{We expect that if the drop electrostatic potential energy is greater than the release of surface energy under the sudden change in $\mathbb{B}\mbox{o}$ in the form of the drop kinetic energy, the drop will return to an equilibrium state on the charged surface which minimizes the potential.}
+What is the origin of the extemporaneous electric field at work in these observations?
 It is well known that water acquires positive free charge when in contact with certain polymers, especially polytetrafluoroethylene (PTFE), through a process called contact charging \cite{langmuir_surface_1938}.
@@
 For instance, in a 1996 paper, NASA flight engineer Don Pettit discusses the problem of low-gravity flow induced charging of liquids, resulting ultimately from contact charging phenomenon \cite{pettit_donald_flow_????}.
-However, a more likely mechanism for the drop charge is field-induced charging.
-Field-induced charging occurs due to breakup of a conductor having a field-induced dipole (e.g., a physical separation of charge).
+However, a more likely mechanism for the drop charge is field-induced charging occuring due to breakup of a conductor having a field-induced dipole (e.g., a physical separation of charge).
 In our work this might occur when a drop is deposited on the charged surface by a grounded syringe.
@@
 Field-induced charging is at work in the famous Kelvin thunderstorm and is applied in inkjet and electrospay technologies, where in each case the breakup is by the Rayleigh-Plateau instability.
-Notably, in Pettit's aforementioned discussion of contact charging of liquids in low-g, he remarks on accidental electrostatic `hula-ing' of silicone oil drops when ejected from a syringe in the vicinity of a highly-charged polymer surface during an experiment conducted aboard STS-5 by Space Shuttle mission specialist Joseph Allen \cite{pettit_donald_flow_????}.
-Depending on the (highly-variable) electrical conductivity of the silicone oil, and the material of the syringe used in the experiment, the charge could arise just as easily by field-induction as by contact charging.
-Relatedly, in a series of informal and somewhat whimsical experiments Pettit himself electrostatically orbited small water drops around a triboelectrically charged PTFE knitting needle while aboard ISS during expedition 30/31 \cite{stevenson_electrostatic_2015}.
+Notably, in Pettit's aforementioned discussion of contact charging of liquids in low-gravity, he remarks on accidental electrostatic `hula-ing' of silicone oil drops when ejected from a syringe in the vicinity of a highly-charged polymer surface during an experiment conducted aboard STS-5 by Space Shuttle mission specialist Joseph Allen \cite{pettit_donald_flow_????}.
+\sout{Depending on the (highly-variable) electrical conductivity of the silicone oil, and the material of the syringe used in the experiment, the charge could arise just as easily by field-induction as by contact charging.} Relatedly, in a series of informal and somewhat whimsical experiments Pettit himself electrostatically orbited small water drops around a triboelectrically charged PTFE knitting needle while aboard ISS during expedition 30/31 \cite{stevenson_electrostatic_2015}.
 Again, in this case, the drop charge is likely field-induced.
+
+This electro-drop bounce phenomenon can be extended to useful applications in a space environment, generally to tackle various manifestations of the so-called ``phase separation'' problem of separating a gas phase from a multi-phase flow (or the reverse case), in low-gravity.
+Removal of satellite droplets produced during pipetting in wet-lab research outside of a glovebox environment aboard ISS has also been recently suggested as a application of the work [private communication, NASA JSC, E.
+Unger, 2017].
+Drops can become spontaneously charged by contact with standard micropipette tips \citep{choi_spontaneous_2013}, and this free charge can possibly be leveraged for the purposes of phase separation in low-gravity.
 
@@
 We develop here a simple 1-dimensional model of the dynamics of drops dominated by electrostatic forces.
-We treat a drop as a particle with radius $R_d$, which translates vertically along the central axis of a charged dielectric square sheet substrate with initial velocity $U_0$.
+We treat a drop as a particle with radius $R_d$, which translates vertically along the central axis of a charged dielectric square sheet substrate.
 The equation of motion for this system is given by,
@@
 \end{equation}
-where $m$ is the drop mass, $y'' = \frac{d^2 y}{d t^2}$ is the drop acceleration, $\mathbf{F}_D$ is the drag force which always opposes motion, and $\mathbf{F}_E$ is the electrostatic force.
-The assumed initial conditions are such that, when $\mathbb{B}\mbox{o}$ is suddenly reduced at the start of the drop tower free-fall period, the drop jumps with instantaneous initial velocity $U_0$ from its 1-$g_0$ resting position with fixed radius $R_d$ at $t=0$.
-The dynamical system is sketched schematically Figure \ref{apparatus}.
+where $m$ is the drop mass, $y'' = \frac{d^2 y}{d t^2}$ is the drop acceleration, $F_D$ is the drag force which always opposes motion, and $F_E$ is the electrostatic force.
+The assumed initial conditions are such that, when $\mathbb{B}\mbox{o}$ is suddenly reduced at the start of the drop tower free-fall period, the drop jumps with instantaneous initial velocity $U_0$ from its 1-$g_0$ resting position of $R_d$ at $t=0$.
+The dynamical system is sketched schematically in Figure \ref{fig:apparatus}.
 We now define models for each of the forces in this equation.
@@
 \includegraphics[width=0.45\textwidth]{../figures/apparatus3.pdf}
-\label{apparatus}
 \caption{Schematic representation of drop jump with return and rebound from an electrically charged superhydrophobic substrate.
 The characteristic time and length scales $t_c$ and $y_c$ describe the time of flight and apoapse associated with the drop trajectory.
-$L$ denotes the lengthscale characteristic of the charged superhydrophobic substrate.}
+$L$ denotes the length scale characteristic of the charged superhydrophobic substrate.}
+\label{fig:apparatus}
 \end{figure}
 
-For the intermediate range of Reynolds numbers $1 \leq \mathbb{R}\mbox{e} \equiv \frac{2UR_d}{\nu} \leq 2000 $ observed in our experiments, we assume the force of drag acting on the drop to be quadratic.
+For the intermediate range of Reynolds numbers $1 \leq \mathbb{R}\mbox{e} \equiv \frac{2UR_d}{\nu} \leq 50 $ observed in our experiments, we assume the force of drag acting on the drop to be quadratic, with $\nu$ being the kinematic viscosity.
 
 In modeling the electrostatic force we begin with the standard electrohydrodynamic (EHD) approximation \cite{saville_electrohydrodynamics:_1997}.
-Under a DC electric field, we assume that the real part of the dielectric permittivity $\epsilon$, $\mbox{Re} \left( \epsilon \right) \approx  \mbox{constant}$.
+\sout{Under a DC electric field, we assume that the real part of the dielectric permittivity $\epsilon$, $\mbox{Re} \left( \epsilon \right) \approx  \mbox{constant}$.
 We also assume that electric currents are small enough that the effects of magnetic fields can be neglected.
@@
 The relaxation time for the common distilled water that is actually used in the drop experiments is shorter due to the presence of solvated ions which tend to increase the conductivity.
-Neglecting the effects of an electric double layer on hydration of ions in the water or the ambient atmosphere due to the relatively massive size of the drops studied, the assumption of small relaxation time further implies that the free charge present in the drops will remain approximately constant during the typical time interval of a low-gravity experiment.
+Neglecting the effects of an electric double layer on hydration of ions in the water or the ambient atmosphere due to the relatively massive size of the drops studied, the assumption of small relaxation time further implies that the free charge present in the drops will remain approximately constant during the typical time interval of a low-gravity experiment.}
 
-Supposing that electrical forces acting on free charges and dipoles in a fluid are transferred directly to the fluid itself, the overall electrical body force will be the divergence of the Maxwell stress tensor $\tau_m $,
+Supposing that electrical forces acting on free charges and dipoles in a fluid are transferred directly to the fluid itself, the overall electrical body force density will be the divergence of the Maxwell stress tensor $\tau_m $,
 \begin{eqnarray} \label{e_force}
@@
 
-It is common to approximate the polarization stress by idealizing the drop as a simple dipole using the effective dipole moment method first described by Pohl in 1958 \cite{pohl_effects_1958}.
+It is common to approximate the dielectrophoretic force by idealizing the drop as a simple dipole using the effective dipole moment method first described by Pohl in 1958 \cite{pohl_effects_1958}.
 The force felt by the dipole is
@@
 \end{eqnarray}
-where $\mathbf{P}_e=(\kappa_w - \kappa_a)\epsilon_0 \mathbf{E}$ is the excess polarization and $\kappa_w$ and $\kappa_a$ are the relative dielectric constants of the water particle and air host fluid respectively.
+where $\mathbf{P}_e=(\kappa_w - \kappa_a)\epsilon_0 \mathbf{E}$ is the excess polarization, $\epsilon_0$ is the vacuum permittivity, and $\kappa_w$ and $\kappa_a$ are the relative dielectric constants of the water particle and air host fluid respectively.
 Here it is convenient to use the simplifying shorthand $K = \frac{\kappa_w - \kappa_a}{\kappa_w + 2 \kappa_a}$, known as the Clausius-Mossotti factor.
-In cases where $K <$ 0, or $K>$ 0 the particle will be either repelled or attracted to regions of strong field.
-In our experiment, choosing the relative dielectric constants $\kappa_a \approx$ 1 and $\kappa_w \approx$ 80, we estimate $K \approx$ 0.96.
-It is important to note that the equivalent dipole approximation critically requires an assumption of small physical scale of the particle relative to the length scale of nonuniformity of the field, which in this case we take to be the length of the charged superhydrophobic surface, $L =$ 25 mm $\gg R_d \approx$ 2 mm.
+In cases where $K <$ 0, or $K>$ 0 the particle will be repelled or attracted to regions of strong field respectively.
+\sout{In our experiment, choosing the relative dielectric constants $\kappa_a \approx$ 1 and $\kappa_w \approx$ 80, we estimate $K \approx$ 0.96.
+It is important to note that the equivalent dipole approximation critically requires an assumption of small physical scale of the particle relative to the length scale of nonuniformity of the field, which in this case we take to be the length of the charged superhydrophobic surface, $L =$ 25 mm $\gg R_d \approx$ 2 mm.} By comparing DEP and Coulombic forces we note that a condition to neglect the DEP force is
+\begin{eqnarray}
+\frac{ \kappa_w \epsilon_0 K R_d^2 E_0}{q} \ll 1. \nonumber
+\end{eqnarray}
+This conditions prevails in our experiments and we henceforth neglect the DEP force.
+\sout{There is some physical intuition to support this conclusion as well.
+The dielectric displacement $\mathbf{D} = \kappa \epsilon_0 \mathbf{E}$ of a water drop in air is high due to the large relative dielectric constant of water.
+This implies that the field strength within the drop is about 80 times smaller than in the surrounding medium.
+Thus it is not particularly inaccurate to model the dielectric volume of a drop as an equipotential conductive shell with zero field in its interior.
+As an aside, in treating the drop as an ideal conductor we note that in our specific case the electrostatic force is not a body force \emph{per se} as the electric field is acting on charges on the surface of the conductor.}
 
@@
 
-By substituting Equations \ref{dep_force} and \ref{image_force} into \ref{e_force} we have
+By substituting Equation \ref{image_force} into \ref{e_force} we have for a single drop
 \begin{eqnarray}
- \mathbf{F}_E &=& q \mathbf{E} + \mathbf{F}_{DEP} + \mathbf{F}_I \nonumber \\
- &=& q \mathbf{E} + \frac{k q^2}{16 \pi \epsilon_0 } y^{-2} \hat{\mathbf{j}} + 2 \pi R_d^3 \kappa_w \epsilon_0 K \nabla E^2, 
- \label{e_forces}
+ \mathbf{F}_E &=& q \mathbf{E} + \mathbf{F}_I \nonumber \\
+ &=& q \mathbf{E} + \frac{k q^2}{16 \pi \epsilon_0 } y^{-2} \hat{\mathbf{j}} \label{e_forces}
 \end{eqnarray}
-
-By comparing DEP and Coulombic terms in Equation \ref{e_forces}, we note that a condition to neglect the DEP force is
-\begin{eqnarray}
-\frac{ \kappa_w \epsilon_0 K R_d^2 E_0}{q} \ll 1. \nonumber
-\end{eqnarray}
-We assume this conditions prevails in our experiments and henceforth neglect the DEP force.
-There is some physical intuition to support this conclusion as well.
-The dielectric displacement $\mathbf{D} = \kappa \epsilon_0 \mathbf{E}$ of a water drop in air is high due to the large relative dielectric constant of water.
-This implies that the field strength within the drop is about 80 times smaller than in the surrounding medium.
-Thus it is not particularly inaccurate to model the dielectric volume of a drop as an equipotential conductive shell with zero field in its interior.
-As an aside, in treating the drop as an ideal conductor we note that in our specific case the electrostatic force is not a body force \emph{per se} as the electric field is acting on charges on the surface of the conductor.
 
@@
 \subsection{Electric Field}
-If we consider the charged dielectric surface of our experiments to be a square sheet of charge lying in the $xz$-plane with width $L$, the symmetry of the problem happily lets us obtain the $y$-component of the electric field $\mathbf{E}$ by direct integration,
+If we consider the charged dielectric surface of our experiments to be a square sheet of charge lying in the $xz$-plane with width $L$, the symmetry of the problem happily lets us obtain the $y$-component of the electric field $\mathbf{E}$ by direct integration (as a superposition of line charges) \citep{david_j._griffiths_introduction_1999} as
 \begin{equation}
@@
 E = \frac{\sigma}{ \pi \epsilon_0} \tan^{-1} \left( \frac{L^2}{y \sqrt{2L^2 + 4y^2}}\right)
-.\end{equation}
-We note that this 1D model of the electric field is valid when $R_d \ll L$, which will be true for cases of small drops `far' from the dielectric surface.
+,\end{equation}
+where $\sigma$ is the surface charge density. We note that this 1D model of the electric field is valid when $R_d \ll L$, which will be true for cases of small drops `far' from the dielectric surface.
 
@@
 \]
-With these scales the governing equation \ref{pi_terms} becomes
+With these scales Equation \ref{pi_terms} becomes
 \begin{equation}
@@
 \]
-where the Image number $\mathbb{I}\mbox{g}$ is the ratio of image forces to the Coulombic force of the unperturbed field, and the electrostatic Euler number $\mathbb{E}\mbox{u}$ is the ratio of inertia to electrostatic force.
-With these dimensionless groups the intrinsic scales become
-\[ t_c = \mathbb{E}\mbox{u} \frac{R_d}{U_0}, \hspace{5 mm} \mbox{and} \hspace{5 mm}
-y_c = \mathbb{E}\mbox{u} R_d.
-\]
-We note that in a conservative system $\mathbb{E}\mbox{u}$ can be thought of as a ratio of kinetic energy $m U_0^2$ and the electrostatic potential energy $q E_0 R_d$.
+where the Image number $\mathbb{I}\mbox{g}$ is the ratio of image forces to the Coulombic force of the unperturbed field, and the electrostatic Euler number $\mathbb{E}\mbox{u}$ is the ratio of inertia to electrostatic force, or equivalently, in a conservative system $\mathbb{E}\mbox{u}$ can be thought of as a ratio of kinetic energy $m U_0^2$ and electrostatic potential energy $q E_0 R_d$.
 
@@
 \]
-With this scaling the non-dimensional governing equation is 
+With these scales Equation \ref{pi_terms} becomes 
 \begin{eqnarray}
@@
 \subsection{Asymptotic Estimates}
-The scalings of Equations \ref{img_limit} and \ref{drag_limit} are weakly non-linear differential equations in the sense that they reduce to linear equations as $\mathbb{E}\mbox{u} \rightarrow 0$.
-For $\mathbb{E}\mbox{u} \ll 1$ we find an asymptotic solution of the non-linear equation by means of a regular perturbation.
+Equations \ref{img_limit} and \ref{drag_limit} are weakly non-linear differential equations in the sense that they reduce to linear equations as $\mathbb{E}\mbox{u} \rightarrow 0$.
+For $\mathbb{E}\mbox{u} \ll 1$ we find asymptotic solutions of the non-linear equations by means of regular perturbations.
 In this case we use the naive expansion
@@
 By inspection, it is evident that if $\mathbb{I}\mbox{g}=0$, the solution is the classical kinematic equation for projectile motion without drag under constant gravity $g_0$.
-Continuing on to higher order, after some tedious computations documented in the project repository for this work \cite{schmidt_droplet_electro-bounce:_2017}, the $\mathcal{O}(\mathbb{E}\mbox{u}^5)$ order accurate solution which is truncated to $\mathcal{O}(\mathbb{E}\mbox{u}^2)$ below:
+Continuing on to higher order, after some tedious computations documented in the project repository for this work \cite{schmidt_droplet_electro-bounce:_2017}, we find the $\mathcal{O}(\mathbb{E}\mbox{u}^5)$ order accurate solution which is truncated to $\mathcal{O}(\mathbb{E}\mbox{u}^2)$ below:
 
 \begin{gather}
-{y^*}({t^*}) = {t^*} + \frac{{t^*}^{2}}{2} \left(-1 - \mathbb{I}\mbox{g}\right) \nonumber \\
+{y^*}({t^*}) = {t^*} + \frac{{t^*}^{2}}{2} \left(-1 - \mathbb{I}\mbox{g}\right)
  + \mathbb{E}\mbox{u} \left(\frac{\mathbb{I}\mbox{g} {t^*}^{3}}{3} + \frac{\mathbb{I}\mbox{g} {t^*}^{4}}{12} \left(-1 - \mathbb{I}\mbox{g} \right)\right) \nonumber \\
@@
 We plot the approximate short-time solution of Equation \ref{perturb_image} with varying values of $\mathbb{I}\mbox{g}$ in Figure \ref{fig:short_times}.
+These plots show a trend of decreasing time-of-flight $t_f$, which is the time for the drop to return to the origin (a single `bounce'), and height at apoapse with increasing values of $\mathbb{I}\mbox{g}$.
+\sout{When $\mathbb{I}\mbox{g} = 1$, $t_f$ is exactly half of the characteristic time scale in this regime.
+In the limit of small $\mathbb{I}\mbox{m}$ the trajectories collapse to the $\mathcal{O}(1)$ solution regardless of the electrostatic Euler number.} Trajectories with $\mathbb{E}\mbox{u} \leq 0.1$ are essentially coincident given the scale of the axes used here.
+In principle there is some coupling between $\mathbb{E}\mbox{u}$ and $\mathbb{I}\mbox{g}$; notably this relationship does not depend on the electric field $E_0$ but on a charge to mass ratio.
+The effect of contact line hysteresis on the initial jump velocity $U_0$ will also tend to decohere the natural covariance between these parameters.
 
@@
 The trajectory reduces to the classical $\mathcal{O}(1)$ solution for small values of $\mathbb{I}\mbox{g}$.
-It should be noted that despite what is implied by these plots $\mathbb{I}\mbox{g}$ is not necessarily independent of $\mathbb{E}\mbox{u}$ sharing $q$ and $E_0$ as common factors, and the covariance relationships $U_0 \propto R_d^2$, and $m \propto R_d^3$.}
+It should be noted that despite what is implied by these plots $\mathbb{I}\mbox{g}$ is not necessarily independent of $\mathbb{E}\mbox{u}$, sharing $q$ and $E_0$ as common factors, as well as the covariance relationships $U_0 \propto R_d^2$, and $m \propto R_d^3$.}
     \label{fig:short_times}
 \end{figure*}
-These plots show a trend of decreasing time-of-flight $t_f$, which is the time for the drop to return to the origin (a single `bounce'), and height at apoapse with increasing values of $\mathbb{I}\mbox{g}$.
-When $\mathbb{I}\mbox{g} = 1$, $t_f$ is exactly half of the characteristic time scale in this regime.
-In the limit of small $\mathbb{I}\mbox{m}$ the trajectories collapse to the $\mathcal{O}(1)$ solution regardless of the electrostatic Euler number.
-Trajectories with $\mathbb{E}\mbox{u} \leq 0.1$ are essentially coincident given the scale of the axes used here.
-In principle there is some coupling between $\mathbb{E}\mbox{u}$ and $\mathbb{I}\mbox{g}$; notably this relationship does not depend on the electric field $E_0$ but on a charge to mass ratio.
-The effect of contact line hysteresis on the initial jump velocity $U_0$ will also tend to decohere the natural covariance between these parameters.
 
 \subsubsection{Inertial Electro-Viscous Limit}
-By similar arguments we find an asymptotic estimate of the trajectory in the long-time regime. The approximate solution is 
-\begin{gather*}
-\label{perturb_viscous}
+By similar arguments we find an asymptotic estimate of the trajectory in the long-time regime.
+If we assume a constant scale for the drag coefficient $C_D \approx 0.5$ then $\mathbb{D}\mbox{g}$ is approximately a constant $\mathbb{D}\mbox{g} \approx 6 \times 10^{-4}$ in all of our experiments.
+The approximate solution is
+\begin{gather}
 {y^*}({t^*}) = {t^*} - \frac{{t^*}^{2}}{2}  \nonumber \\
 + \phi\mathbb{E}\mbox{u} \left(\frac{{t^*}^{3}}{3} \left(1 + \mathbb{D}\mbox{g}\right) + \frac{{t^*}^{4}}{12} \left(-1 - \mathbb{D}\mbox{g}\right) - \frac{\mathbb{D}\mbox{g} {t^*}^{2}}{2}\right) \nonumber \\
- + \mathcal{O}(\phi^2 \mathbb{E}\mbox{u}^2). \nonumber
-\end{gather*}
+ + \mathcal{O}(\phi^2 \mathbb{E}\mbox{u}^2).
+\label{perturb_viscous}
+\end{gather}
 Trajectories for this solution are shown in Figure \ref{fig:long_times}.
@@
 \end{figure}
-If we assume a constant scale for the drag coefficient $C_d \approx 0.5$ then $\mathbb{D}\mbox{g}$ is approximately a constant $\mathbb{D}\mbox{g} \approx 6 \times 10^{-4}$ in all of our experiments.
 We note that the trajectory reduces to the classical $\mathcal{O}(1)$ solution for small values of of $\phi \mathbb{E}\mbox{u}$.
@@
 
-By again applying a regular perturbation to the asymptotic solution with the expansion
+By again applying a regular perturbation to the asymptotic solution, Equation \ref{perturb_viscous}, with the expansion
 \[ t^* \sim t^*_0 + \phi \mathbb{E}\mbox{u} t^*_1 + \phi^2 \mathbb{E}\mbox{u}^2 t^*_2 \ldots \phi^n \mathbb{E}\mbox{u}^n t^*_n  
@@
 \begin{gather*}
-t_f = 2 + \phi \mathbb{E}\mbox{u} \left(\frac{4}{3} - \frac{2 \mathbb{D}\mbox{g}}{3}\right) \\
+t_f = 2 + \phi \mathbb{E}\mbox{u} \left(\frac{4}{3} - \frac{2 \mathbb{D}\mbox{g}}{3}\right) 
 + \phi^2 \mathbb{E}\mbox{u}^{2} \left(\frac{4}{5} - \frac{4 \mathbb{D}\mbox{g}}{3} + \frac{2 \mathbb{D}\mbox{g}^{2}}{5}\right) \\
@@
 To estimate the drop free charge $q$ we use parameter estimation techniques.
-Our work flow to identify $q$ in an individual drop tower experiment is as follows:
+Our work flow to identify $q$ in a drop tower experiment is as follows:
 \begin{enumerate}
-\item We vary the independent variables $V_d$ and $\sigma$ in a set of single-drop spontaneous drop jumps on charged dielectric superhydrophobic substrates under low-gravity conditions in a $2.1$ s drop tower.
-\item We capture high-speed video and digitize the trajectories of the drops. 
-\item We solve the inverse problem to find the drop free charge $q$ by maximizing the log-likelihood of the data given the dynamical model by varying the parameter vector $\mathbf{x} = \left\langle q, \hspace{2 mm} V_d, \hspace{2 mm} \sigma \right\rangle$ using a direct search optimization.
+\item We vary the independent variables drop volume $V_d$ and dielectric surface charge density $\sigma$ in a set of single-drop spontaneous drop jump experiments under low-gravity in a $2.1$ s drop tower.
+\item We capture video and digitize the trajectories of the drops. 
+\item We solve the inverse problem to find the drop free charge $q$ by maximizing the log-likelihood of the experimental trajectories given the dynamical model by varying the parameter vector $\mathbf{x} = \left\langle q, \hspace{2 mm} V_d, \hspace{2 mm} \sigma \right\rangle$ using a direct search optimization.
 \end{enumerate}
@@
 The Dryden Drop Tower at Portland State University uses a dual capsule design, inspired by the 2.2 s facility at NASA Glenn Research Center, which decouples drag acceleration felt by the external drag shield from the experiment.
-The experiment experiences approximately $\lesssim 1 \times 10^{-4}$ $g_0$ during free-fall for 2.1s as the rig and drag shield plummet to the bottom of drop tower 6 stories below.
-The rig with a mounted experiment is shown in Figure \ref{fig:rig}.
-Single drops of distilled water in a range of volumes ($0.01 \leq R_d \leq 0.5$ mL) are carefully deposited on charged superhydrophobic substrates using an grounded glass syringe with $\pm $1 $\mu$L accuracy and then dropped in the drop tower.
-Red dye is added to improve thresholding accuracy in trajectory digitization.
-Drop trajectories are recorded using a Panasonic HC-WX970 Camera.
-Drop trajectories are digitized using the particle tracking module in Fiji \cite{schindelin_fiji:_2012}.
+The experiment experiences approximately $\lesssim 1 \times 10^{-4}$ $g_0$ during free-fall for 2.1 s as the experiment and drag shield togeather plummet to the bottom of drop tower 6 stories below.
+A drop tower rig with a mounted experiment is shown in Figure \ref{fig:rig}.
+Single drops of distilled water in a range of volumes ($0.01 \leq V_d \leq 0.5$ mL) are carefully deposited on rig-mounted charged superhydrophobic substrates using a grounded glass syringe with $\pm $1 $\mu$L accuracy and then dropped in the drop tower.
+In this work 16 such single-drop drop jump experiments were conducted in low-gravity.
+Drops are colored with red dye to improve thresholding accuracy in trajectory digitization.
+Drop trajectories are captured using a Panasonic HC-WX970 Camera recording at 120 fps.
+Drop trajectories are digitized from video using the particle tracking module in Fiji \cite{schindelin_fiji:_2012}.
 
@@
 
-Superhydrophobic electret substrates are prepared with surface potentials $\varphi_s = 0.7$-$4.0$ kV.
+Superhydrophobic electret substrates are prepared with surface potentials $\varphi_s = 0.4$-$1.8$ kV.
 We use an isothermal electret formation process which is a variation of the widely applied corona-charging technique.
-A Ptec IN5120 balanced AC corona ion source directs a net neutral stream of ions towards the dielectric substrate, which we polarize by an electrode with an EMCO P20P $2$ kV$+$ absolute reference DC-DC converter.
+A Ptec IN5120 balanced AC corona ion source directs a net neutral stream of ions towards a dielectric substrate, which we polarize by an embedded electrode with an EMCO P20P $2$ kV$+$ absolute reference DC-DC converter.
 The ion stream compensates the surface and space bound charges arising due to the polarization of the dielectric.
-When the DC-DC converter is switched to ground the deposited negative ions remain on the surface.
+After the corona source and DC-DC converter are powered off and the electrode is shorted across a bleed resistor the deposited negative ions remain on the substrate surface.
 The electret is lamina of 3 to 4 0.4 mm thick corona charged polymethyl methacrylate (PMMA) sheets.
-The electric field strength scales with the number of dielectric lamina as has also been shown in work on electret based vibrational energy harvesters \cite{wada_stacking_2012} and in water desalinization \cite{ni_desalination_2005}.
+The electric field strength scales with the number of dielectric lamina as has also been shown in work on laminated electret based vibrational energy harvesters \cite{wada_stacking_2012} and in water desalinators \cite{ni_desalination_2005}.
 The RC time constant for decay of the surface charge is observed to be $\tau \approx 2000$ s.
 
-The electret is established on a superhydrophobic substrate produced by laser etching PMMA and depositing a thin layer of PTFE on the roughened surface.
-We use a laser-etched pillared geometry with pillar heights $\sim \hspace{-1mm} 775$ $\mu$m, widths $\sim \hspace{-1mm} 70$ $\mu$m, and pitch $\sim \hspace{-1mm} 100$ $\mu$m.
+The topmost face of the electret lamina is made superhydrophobic by first laser ablating a pillared topology  on the surface followed by deposition of a thin layer of PTFE.
+We use a pattern with pillar heights $\sim \hspace{-1mm} 775$ $\mu$m, widths $\sim \hspace{-1mm} 70$ $\mu$m, and pitch $\sim \hspace{-1mm} 100$ $\mu$m.
 An SEM image of the pillar geometry is shown in Figure \ref{fig:SEM}.
-Contact angles of distilled water on the electret, measured using the tangent method, are $\sim \hspace{-1mm} 150^{\circ}$.
-The roll-off angle of a 1 mL drop is $1^{\circ} \pm 0.5^{\circ}$ when the surface is uncharged.
-The hysteresis of the contact angle (the difference between the advancing $\theta_a$ and receding $\theta_r$ contact angles) is estimated from the roll-off angle using the model of Furmidge \cite{furmidge_studies_1962}, and is found to be approximately $25^{\circ} \pm 10^{\circ}$.
+Contact angles of distilled water on the surface, measured using the tangent method, are $\sim \hspace{-1mm} 150^{\circ}$ when the surface is uncharged.
+The roll-off angle of a 1 mL drop is $1^{\circ} \pm 0.5^{\circ}$.
+\sout{The hysteresis of the contact angle (the difference between the advancing $\theta_a$ and receding $\theta_r$ contact angles) is estimated from the roll-off angle using the model of Furmidge \cite{furmidge_studies_1962}, and is found to be approximately $25^{\circ} \pm 10^{\circ}$.}
 
@@
 Surface potentials $\varphi_s$ are measured on the superhydrophobic surface using a Simco-Ion FMX-004 electrostatic fieldmeter and the method for determination of surface charge density for low conductivity polymers described in Davies \cite{davies_examination_1967}.
-For this measurement the fieldmeter is shielded, the electret substrate rests over a conductive ground plane, and the surface charge density is determined from $\sigma = \varphi_s \kappa \epsilon_0/l,$ where $l$ is the thickness of the dielectric surface.
-The relative dielectric constant of the PMMA sheet is measured by using a 65$\times$65 mm polished aluminum parallel plate capacitor with $C = \kappa \epsilon_0 A/l$, where $C$ is the capacitance, and $A$ is the sheet area.
+For this measurement the fieldmeter is shielded, the electret substrate rests over a conductive ground plane, and the surface charge density is determined from $\sigma = \varphi_s \kappa \epsilon_0/l,$ where $l$ is the thickness of the dielectric substrate.
+The relative dielectric constant of the PMMA sheet $\kappa$, is measured by using a 65$\times$65 mm polished aluminum parallel plate capacitor with $C = \kappa \epsilon_0 A/l$, where $C$ is the capacitance, and $A$ is the sheet area.
 Measuring the capacitance with 3 sample thicknesses using a GenRad 1657 RLC Digibridge, we find the relative permittivity to be $\kappa = 3.5 \pm 0.4$.
@@
 \subsection{Parameter Estimation}
-We find the parameters $\mathbf{x}$ that solve the inverse problem $G(\mathbf{x}) = \mathbf{d}$, where the model $G(\mathbf{x})$ describes some relationship between the vector of parameters $\mathbf{x}$ and a set of (ideal) observations $\mathbf{d}$.
-We seek the parameter set $\mathbf{x} = \left\langle q, \hspace{2 mm} V_d, \hspace{2 mm} \sigma \right\rangle$ that has the highest probability of observing the data (the maximum of the posterior Probability Density Function) which can be determined by maximizing the log-likelihood (or equivalently minimizing $\chi^2$ goodness-of-fit) of the data $\mathbf{d}$ with respect to the the model, which is generally a numerical solution to Equation \ref{gov_eqn_subs}.
+Generally we seek the parameters $\mathbf{x}$ that solve the inverse problem $G(\mathbf{x}) + \mathbf{u} = \mathbf{d}$, where the model $G(\mathbf{x})$ describes some relationship between the vector of parameters $\mathbf{x}$ and a set of observations $\mathbf{d}$, and where $\mathbf{u}$ is the measurement error.
+In particular we seek the parameter set $\mathbf{x} = \left\langle q, \hspace{2 mm} V_d, \hspace{2 mm} \sigma \right\rangle$ that has the highest probability (i.e.
+the maximum of the posterior Probability Density Function) of observing the data given the model, which is a numerical solution to Equation \ref{gov_eqn_subs}.
+This can be determined by maximizing the log-likelihood (or equivalently by minimizing $\chi^2$ goodness-of-fit) of the data $\mathbf{d}$ with respect to the model.
 This problem is formally stated as
@@
           & \sigma 
-          \end{array} \right. 
+          \end{array}, \right. 
           \end{split} \hspace{2 mm} \mbox{subject to constraints} \hspace{2 mm} \begin{split}
@@
       	   t_0 &\pm \hspace{2 mm} u_{exp}\\
-          \end{array} \right. 
+          \end{array}, \right. 
           \end{split}
@@
 
-We integrate Equation \ref{gov_eqn_subs} numerically using the \emph{netlib ODEPACK} library double-precision \verb|lsoda| integrator wrapped within the \verb|odeint| \emph{Scipy} \cite{oliphant_python_2007} module in Python.
+We integrate Equation \ref{gov_eqn_subs} numerically using the \emph{netlib ODEPACK} \verb|lsoda| integrator implimented as \verb|scipy.integrate.odeint| in the \emph{Scipy} \cite{oliphant_python_2007} library in Python.
 The optimization problem in this case is non-convex, mixed discrete-continuous black-box (noisy), and highly ill-conditioned.
@@
 The non-convexity of the problem implies that there are many local minima of the objective function.
-We use a gradient-free direct-search Nelder-Mead \cite{nelder_simplex_1965} algorithm implemented in \verb|scipy.optimize|.
+We use a gradient-free direct-search Nelder-Mead \cite{nelder_simplex_1965} algorithm implemented as \verb|scipy.optimize.minimize(method='Nelder-Mead')| in \emph{SciPy}.
 Nelder-Mead is relatively robust to noise and is thrifty with our computationally expensive function-calls.
 Experimental trajectory data is smoothed using a Savitsky-Golay filter \cite{savitzky_smoothing_1964} to improve the convergence characteristics of the optimizer.
-This filter is implemented in the \verb|scipy.signal| Python \emph{SciPy} module.
+This filter is implemented as \verb|scipy.signal.savgol_filter| in \emph{SciPy}.
 We precondition the optimization problem by minimizing $\ln(\chi^2)$ and using a naive $\sim \mathcal{O}(1)$ scaling of our constraints by their initial guesses.
@@
 The so-called identifiability problem of bounding uncertainty of the parameter estimates is resolved by constraining the parameter values by our experimental observations of them and their associated measurement uncertainties.
-Because Nelder-Mead cannot be used for explicitly constrained problems we implement the constraints by using an exterior penalty function.
-In the case of $q$, which we do not directly observe in experiment, we bound identifiability by using a Montecarlo bootstrap approach [WIP].
+Because Nelder-Mead cannot be used for explicitly constrained problems we implement the constraints using an exterior penalty function.
+\sout{In the case of $q$, which we do not directly observe in experiment, we bound identifiability by using a Montecarlo bootstrap approach [WIP].}
 
@@
     \caption{A set of drop trajectories showing the results of the parameter estimation.
-The trajectories are shown only up to the apoapse of the first bounce.
+The trajectories are shown only up to the first apoapse before rebound.
 The (\protect\redline) \hspace{0.25 mm} lines show the numerical solution of Equation \ref{gov_eqn_subs} with the given MLE parameter vector.
@@
 \subsection{Parameter Estimates}
-We determined the distribution of most probable experimental model variables values for a population of the drops jumped in drop tower tests shown in Figure \ref{fig:scatter}.
-The dependence of charge on drop surface area $A$ is immediately evident, while the effect of electric field on drop charge is less obvious.
-This co-linearity is likely the source of the ill-conditioning issues in the parameter estimation process.
-However, assuming the main effect is the interaction between charge and electric field, a Robust Least Squares model fit $q \sim kAE_0$ with the non-linear transformation $A = V_d^{2/3}$ finds that $k=5.01 \times 10^{-11} \pm  2.85 \times 10^{-11}$ F/m with $R^2 = 0.946$.
+The MLE estimates of $q$, as well as the measured values of $V_d$, $E_0$, and $U_0$ for the entire population of drop tower tests are shown in the scatter plot matrix of Figure \ref{fig:scatter}.
+The dependence of charge on drop volume $V_d$ is immediately evident, while the effect of electric field on drop charge is less obvious.
+This co-linearity is the source of the ill-conditioning in the parameter estimation process.
+However, assuming the main effect is the interaction between charge and electric field, a forced entry Robust Least Squares model
+\begin{equation}
+q \sim kAE_0,
+\label{ls_model}
+\end{equation} 
+with the transformation $A = V_d^{2/3}$ finds that $k=7.589 \times 10^{-11} \pm  1.47 \times 10^{-11}$ F/m with $R^2 = 0.65$, $F=27$. 
 \begin{figure}[h]
@@
 
-A two-way T-test comparison of charge distributions between the drop bounce experiment and a corollary experiment with zero electric field at the time of drop deposition on the superhydrophobic surface suggests that the drop charge is primarily induced by the electric field, rather than through contact charging on the PTFE layer ($t = 5.11$, $p = 0.0002$).
+A two-way T-test comparison of charge distributions between the drop bounce experiment and a corollary experiment with zero electric field at the time of drop deposition on the superhydrophobic surface suggests that the drop charge is primarily induced by the electric field, rather than developed through contact charging on the PTFE layer ($t = 5.11$, $p = 0.0002$).
 
-The model $q \sim kAE_0$ is similar to the classical solution for the surface charge of a half-spherical conductor with a field-induced dipole \cite{david_j._griffiths_introduction_1999}
+Incidentally, the model $q \sim kAE_0$ is similar to the classical solution for the surface charge of a half-spherical conductor with a field-induced dipole \cite{david_j._griffiths_introduction_1999}
 \begin{eqnarray}
@@
 &=& 3 \pi^{1/3} 6 \left(6 V_d \right)^{2/3} \epsilon_0 E_0 \int^{\pi / 2}_{0} \!\!\!\!\! \cos \theta d\theta \nonumber \\
-&=& k E_0 V_d^{2/3} \label{dipole}
+&=& k A E_0 \label{dipole}
 \end{eqnarray}
 with $k \approx 1.3 \times 10^{-10}$ F/m.
-This is also of similar form to the charge found by Takamatsu and coauthors for drops falling from a grounded nozzle in an external electric field \cite{takamatsu_theoretical_1981}
-\[q = 4 \pi \epsilon_0 \beta E_0 R_d^2 \]
-with $\beta \approx 2.63$. Cast in the same form as Equation \ref{dipole} $k \approx 4 \pi \epsilon_0 \beta (4 \pi/3)^{-2/3} \approx 1.1 \times 10^{-10}$ F/m.
+This is also of similar form to the charge found experimentally by Takamatsu and coauthors for drops falling from a grounded nozzle in an external electric field \cite{takamatsu_theoretical_1981}
+\begin{equation}
+q = 4 \pi \epsilon_0 \beta E_0 R_d^2
+\label{Takamatsu}
+\end{equation}
+with $\beta \approx 2.63$.
+Casting Equation \ref{Takamatsu} in the same form as Equations \ref{ls_model} and \ref{dipole}, $k \approx 4 \pi \epsilon_0 \beta (4 \pi/3)^{-2/3} \approx 1.1 \times 10^{-10}$ F/m.
 
@@
 \subsection{Model Validation}
-Dimensional drop apoapses shown in Figure \ref{fig:series_s_eu} scale closely with $\mathbb{E}\mbox{u}$ as expected according to our earlier analysis.
+Using the parameter estimates we find $\mathbb{E}\mbox{u}$ for each drop jump.
+Dimensional drop apoapses shown in Figure \ref{fig:series_s_eu} scale with $\mathbb{E}\mbox{u}$ as expected according to our earlier analysis.
 Electrostatic Euler numbers in the data set vary between $1.4 \lesssim \mathbb{E}\mbox{u} \lesssim 35.4$.
-The dielectrophoretic force plays a small role when drops have net charge in a DC field.
-The condition to neglect the DEP force was satisfied for all experiments in the dataset with typical values of the condition number $\kappa_w \epsilon_0 K R_d^2 E_0/q \approx \mathcal{O}(10^{-6})$.
+\sout{The dielectrophoretic force plays a small role when drops have net charge in a DC field.
+The condition to neglect the DEP force was satisfied for all experiments in the dataset with typical values of the condition number $\kappa_w \epsilon_0 K R_d^2 E_0/q \approx \mathcal{O}(10^{-6})$}.
 In the non-dimensional trajectories with short-time scaling shown in Figure \ref{fig:series_s_ds}, we see that the scaled trajectory apoapses are consistently $\mathcal{O}(1)$, with all trajectories overshooting their characteristic time scale (which predicts returns at $t^*  =2$ at zeroth order).
-The fact that $\mathbb{E}\mbox{u} \ll 1$ is not satisfied for all tests is in violation of the Equation \ref{perturb_image} asymptotic result for short times.
+A trend of increasing $\mbox{max} \left(y^* \right)$ at apogee for decreasing $\mathbb{E}\mbox{u}$ is seen in Figure \ref{fig:yscale_trend}.
+This trend seems to decay to a constant $y_{max}/y_c \approx 1/2$ for $6 < \mathbb{E}\mbox{u} < 10$, and implies the existence an intermediate regime with a larger characteristic lengthscale for $\mathbb{E}\mbox{u} < 6$.
+For $\mathbb{E}\mbox{u} > 10$ the trend reverses and apoapses begin to grow again.
 \begin{figure}[!htb]
     \centering
-    \resizebox{0.5\textwidth}{!}{\input{../figures/series_s_eu.pgf}}
+    \resizebox{0.5\textwidth}{!}{\input{../figures/series.pgf}}
     \caption{Drop trajectories as a function of $\mathbb{E}\mbox{u}$.\label{fig:series_s_eu}}
@@
     \centering
-    \resizebox{0.5\textwidth}{!}{\input{../figures/series_s_ds.pgf}}
+    \resizebox{0.5\textwidth}{!}{\input{../figures/series_s_ds.pdf_tex}}
     \caption{Non-dimensional trajectories with the short-time scaling.\label{fig:series_s_ds}}
 \end{figure}
+\begin{figure}[htb]
+    \centering
+    \resizebox{0.5\textwidth}{!}{\input{../figures/yscale_trend.pgf}}
+    \caption{Non-dimensional apoapse height $y_{max}/y_c$ compared with $\mathbb{E}\mbox{u}$.\label{fig:yscale_trend}}
+\end{figure}
 
-The predicted long-time scaled time-of-flight $t_f$ given by Equation \ref{time_of_flight} when redimensionalized by the characteristic time $t_c$ compares favorably to the experimental time-of-flight $t_b$, shown in Figure \ref{fig:times2}.
-This allows an improvement to be made to the asymptotic result of Equation \ref{time_of_flight} by multiplying the series by the empirical coefficient $a = 1/0.68 = 1.47$.
+Because $\mathbb{E}\mbox{u} \ll 1$ is not satisfied for any of the experimental drops the entire dataset is beyond the regime where the asymptotic results for short-times, given by Equation \ref{perturb_image}, are valid.
+However, the long-time scaled asymptotic trajectory  and time-of-flight $t_f$ given by Equations \ref{perturb_viscous} and \ref{time_of_flight}, when redimensionalized by the short-time characteristic time $t_c=\mathbb{E}\mbox{u} R_d$, compare favorably to the experimental trajectory apoapses and time-of-flight $t_b$ as shown in Figures \ref{fig:times2} and \ref{fig:ymaxes}.
+This allows an improvement to be made to the asymptotic time-of-flight result of Equation \ref{time_of_flight} by multiplying the series by the empirical coefficient $a = 1.31$.
 The semi-analytic time-of-flight is then given by
@@
 \label{time_improved}
-t^* = 2.94 + 1.96\phi\mathbb{E}\mbox{u} + 1.18\phi^2\mathbb{E}\mbox{u}^{2} + \mathcal{O}(\phi^3\mathbb{E}\mbox{u}^{3}).
+t^* = 2.62 + 1.75\phi\mathbb{E}\mbox{u} + 1.05\phi^2\mathbb{E}\mbox{u}^{2} + \mathcal{O}(\phi^3\mathbb{E}\mbox{u}^{3}).
 \end{equation}
@@
     \centering
-    \resizebox{0.5\textwidth}{!}{\input{../figures/times2.pdf_tex}}
-    \caption{Dimensional time-of-flight asymptotic estimates $t_c t_f$ compared with experimental time-of-flight $t_b$.\label{fig:times2}}
+    \resizebox{0.5\textwidth}{!}{\input{../figures/times.pgf}}
+    \caption{Dimensional time-of-flight asymptotic estimates $t_c t_f$ compared with experimental time-of-flight $t_b$.
+These results compare $\mathcal{O}(1) \equiv y_c$ and $\mathcal{O}(\phi^3\mathbb{E}\mbox{u}^{3})$ accurate variations of Equation \ref{time_of_flight}.
+\label{fig:times2}}
 \end{figure}
-The relative magnitudes of the forces acting on the drops determined by the MLE solutions to Equation \ref{gov_eqn_subs} for the entire population of drop tower experiments are shown in Figure \ref{fig:forces}.
+\begin{figure}[htb]
+    \centering
+    \resizebox{0.5\textwidth}{!}{\input{../figures/ymaxes.pgf}}
+    \caption{Dimensional asymptotic trajectory apoapses, found from Equation \ref{perturb_viscous} with $t^*=1$, as compared to experimental apoapses $y_{max}$.\label{fig:ymaxes}}
+\end{figure}
+A similar empirical coefficient $a = 1.31$ is found for Equation \ref{perturb_viscous}. 
+The relative magnitudes of the forces acting on the drops determined by the MLE numerical solutions to Equation \ref{gov_eqn_subs} for the entire population of drop tower experiments are shown in Figure \ref{fig:forces}.
 Coulomb, image, and drag forces acting on the drops vary in typical magnitude between $\mathcal{O}(10^{-6})$-$\mathcal{O}(10^{-4})$ N.
@@
 The drop with largest $\mathbb{E}\mbox{u}$ in our dataset failed to escape the electric field as the escape condition $\phi \mathbb{E}\mbox{u} / 8\pi = 0.2 < 1$ was unsatisfied.
-Equation \ref{time_improved} predicts that this drop will return to the substrate after 32 s, a period of free-fall which is lamentably well out of reach of a drop tower.
-However, such an experiment could be performed aboard the ISS or certain suborbital parabolic flights.
+Equation \ref{time_improved} predicts that this drop will return to the substrate after 7.4 s, a period of free-fall which is lamentably well out of reach of the Dryden Drop Tower.
+However, such an experiment could be performed in a drop tower facility with a longer free fall period, aboard the ISS or on certain suborbital parabolic flights.
 \begin{figure}[!htb]
@@
     \resizebox{0.5\textwidth}{!}{\input{../figures/forces_all.pgf}}
-    \caption{Simulated forces acting on drops up to the first apoapse as determined by the MLE solutions to Equation \ref{gov_eqn_subs} for all drops in the dataset.\label{fig:forces}}
+    \caption{Simulated forces acting on drops up to the first apoapse as determined by the MLE solutions to Equation \ref{gov_eqn_subs} for all drops in the dataset.
+The (\protect\redline) lines denote the Coulomb force, the (\protect\blueline) lines the drag force, and the (\protect\cyanline) lines the foce due to image charge respectively.
+The forces are scaled by the drop inertia.\label{fig:forces}}
 \end{figure}
@@
 \subsection{Drop Impacts}
-In 1-$g_0$, for Weber numbers $\mathbb{W}\mbox{e} \equiv \rho U^2 R_d/\gamma >$ 0.4, impact rebound behavior on a superhydrophobic surface can be strongly influenced by damping from contact line hysteresis.
+\sout{In 1-$g_0$, for Weber numbers $\mathbb{W}\mbox{e} \equiv \rho U^2 R_d/\gamma >$ 0.4, impact rebound behavior on a superhydrophobic surface can be strongly influenced by damping from contact line hysteresis.
 For the low Bond and Ohnesorge numbers occurring in free-fall, the drop impact dynamics may additionally include electrohydrodynamic surface wettability effects.
 To date there has been little work in general on drop impacts outside of two regimes: (1) very low $\mathbb{R}\mbox{e}$ viscous drop spreading driven by capillary forces at the contact line and (2) impacts at `high' Weber numbers.
-Models for dynamic contact lines in general remain controversial, even for ordinary spreading of liquids, despite decades of work in the area.
+Models for dynamic contact lines in general remain controversial, even for ordinary spreading of liquids, despite decades of work in the area.}
 
-If we naively neglect the contact line dynamics, the dimensionless groups for isothermal drop impacts are the Ohnesorge number $\mathbb{O}\mbox{h} \equiv \mu/\sqrt{\rho \gamma R_d}$, the Weber number $\mathbb{W}\mbox{e}$, and Bond number $\mathbb{B}\mbox{o}$.
+\sout{If we naively neglect the contact line dynamics, the dimensionless groups for isothermal drop impacts are the Ohnesorge number $\mathbb{O}\mbox{h} \equiv \mu/\sqrt{\rho \gamma R_d}$, the Weber number $\mathbb{W}\mbox{e}$, and Bond number $\mathbb{B}\mbox{o}$.
 The Weber number scales the driving force of drop spreading.
@@
 An exception is provided by Duvivier \emph{et al.} \cite{duvivier_drop_2012} who studied regimes of aqueous ferrofluid drop impacts on superhydrophobic substrates under the influence of an external magnetic field.
-In this case the magnetic body force acts as an ersatz gravity.
+In this case the magnetic body force acts as an ersatz gravity.}
 
-When the electro-drop bounce occurs, if the drop has enough time to return a non-wetting impact occurs on the charged substrate usually followed by rebound.
+\sout{When the electro-drop bounce occurs, if the drop has enough time to return a non-wetting impact occurs on the charged substrate usually followed by rebound.
 We observe average drop impact $\mathbb{O}\mbox{h} \approx 2.18 \pm 0.36$ and  $\mathbb{W}\mbox{e} \approx 0.28 \pm 0.22$.
@@
 The latter case is responsible for the irreversiblity that notoriously plagues static EWOD experiments.
-There is hope that additional work in this area could produce engineered surfaces that are tuneably wetting under drop impacts by leveraging electrostatic forces.
+There is hope that additional work in this area could produce engineered surfaces that are tuneably wetting under drop impacts by leveraging electrostatic forces.}
 
-Our preliminary results showing the influence of $\mathbb{W}\mbox{e}$ and electrostatic Bond number $\mathbb{B}\mbox{o}_e \equiv \epsilon E_0^2 R_d/\gamma $ on drop impact dimensionless contact time $\tau$ and coefficient of restitution $C_r$ are shown in Figures \ref{fig:contact} and \ref{fig:restitution}.
+\sout{Our preliminary results showing the influence of $\mathbb{W}\mbox{e}$ and electrostatic Bond number $\mathbb{B}\mbox{o}_e \equiv \epsilon E_0^2 R_d/\gamma $ on drop impact dimensionless contact time $\tau$ and coefficient of restitution $C_r$ are shown in Figures \ref{fig:contact} and \ref{fig:restitution}.}
 

### 2018-10-02 doc/paper/aiptemplate.tex
large revision to paper

@@
 
-This electro-drop bounce phenomenon can be extended to useful applications in a space environment, generally to tackle various manifestations of the so-called ``phase separation'' problem of separating a gas phase from a multi-phase flow (or the reverse case), in low-gravity.
-Removal of satellite droplets produced during pipetting in wet-lab research outside of a glovebox environment aboard ISS has also been recently suggested as a application of the work [private communication, NASA JSC, E.
+This electro-drop bounce phenomenon may have useful applications in a space environment, generally to tackle various manifestations of the so-called ``phase separation'' problem of separating a gas phase from a multi-phase flow (or the reverse case), in low-gravity.
+Removal of satellite droplets produced during pipetting in wet-lab research outside of a glovebox environment aboard ISS has been recently suggested as a application of the work [private communication, NASA JSC, E.
 Unger, 2017].
@@
 A trend of increasing $\mbox{max} \left(y^* \right)$ at apogee for decreasing $\mathbb{E}\mbox{u}$ is seen in Figure \ref{fig:yscale_trend}.
-This trend seems to decay to a constant $y_{max}/y_c \approx 1/2$ for $6 < \mathbb{E}\mbox{u} < 10$, and implies the existence an intermediate regime with a larger characteristic lengthscale for $\mathbb{E}\mbox{u} < 6$.
-For $\mathbb{E}\mbox{u} > 10$ the trend reverses and apoapses begin to grow again.
+This trend seems to decay to a constant $y_{max}/y_c \approx 1/2$ for $6 \lesssim \mathbb{E}\mbox{u} \lesssim 20$, and implies the existence an intermediate regime with a larger characteristic lengthscale for $\mathbb{E}\mbox{u} \lesssim 6$.
 \begin{figure}[!htb]
@@
 Because $\mathbb{E}\mbox{u} \ll 1$ is not satisfied for any of the experimental drops the entire dataset is beyond the regime where the asymptotic results for short-times, given by Equation \ref{perturb_image}, are valid.
-However, the long-time scaled asymptotic trajectory  and time-of-flight $t_f$ given by Equations \ref{perturb_viscous} and \ref{time_of_flight}, when redimensionalized by the short-time characteristic time $t_c=\mathbb{E}\mbox{u} R_d$, compare favorably to the experimental trajectory apoapses and time-of-flight $t_b$ as shown in Figures \ref{fig:times2} and \ref{fig:ymaxes}.
+However, the long-time scaled asymptotic trajectory   $y_c$ and time-of-flight $t_f$ given by Equations \ref{perturb_viscous} and \ref{time_of_flight}, when redimensionalized by the short-time characteristic time $t_c=\mathbb{E}\mbox{u} R_d$, compare favorably to the experimental trajectory apoapses $y_{max}$ and time-of-flight $t_b$ as shown in Figures \ref{fig:times2} and \ref{fig:ymaxes}.
 This allows an improvement to be made to the asymptotic time-of-flight result of Equation \ref{time_of_flight} by multiplying the series by the empirical coefficient $a = 1.31$.
@@
     \caption{Dimensional time-of-flight asymptotic estimates $t_c t_f$ compared with experimental time-of-flight $t_b$.
-These results compare $\mathcal{O}(1) \equiv y_c$ and $\mathcal{O}(\phi^3\mathbb{E}\mbox{u}^{3})$ accurate variations of Equation \ref{time_of_flight}.
+These results compare $\mathcal{O}(1) \equiv 2 t_c$ and $\mathcal{O}(\phi^3\mathbb{E}\mbox{u}^{3})$ accurate variations of Equation \ref{time_of_flight}.
 \label{fig:times2}}
@@
     \resizebox{0.5\textwidth}{!}{\input{../figures/ymaxes.pgf}}
-    \caption{Dimensional asymptotic trajectory apoapses, found from Equation \ref{perturb_viscous} with $t^*=1$, as compared to experimental apoapses $y_{max}$.\label{fig:ymaxes}}
+    \caption{Dimensional asymptotic trajectory apoapses, found from Equation \ref{perturb_viscous} with $t^*=1$ and $\mathcal{O}(1) \equiv y_c/2$, as compared to experimental apoapses $y_{max}$.
+\label{fig:ymaxes}}
 \end{figure}
-A similar empirical coefficient $a = 1.31$ is found for Equation \ref{perturb_viscous}. 
+A similar empirical coefficient $a = 1.22$ is found for Equation \ref{perturb_viscous}. 
 The relative magnitudes of the forces acting on the drops determined by the MLE numerical solutions to Equation \ref{gov_eqn_subs} for the entire population of drop tower experiments are shown in Figure \ref{fig:forces}.

### 2019-04-05 doc/paper/aiptemplate.tex
paper edits

@@
 \renewcommand{\pgfimage}[2][]{\pgfimageWithoutPath[#1]{../figures/#2}}
+
 \begin{document}
@@
 When a nonwetting, gravity-dominated sessile drop (e.g.
-a puddle)\sout{, initially at rest on a surface in the Cassie-Baxter state} suddenly undergoes a large step reduction in Bond number it will spontaneously jump away from the surface.
-The Bond number is given by $\mathbb{B}\mbox{o} \equiv \frac{g R^2 \Delta \rho}{\gamma}$, where $g$ is the acceleration, $R$ is the characteristic interfacial length scale, $\Delta \rho$ is the difference in densities across the interface \sout{(which simplifies to $\rho$, for large $\Delta \rho$, as in the case of an air-water interface)}, and where $\gamma$ is the surface tension.
-The spontaneous drop jump was first observed experimentally in the Soviet Union by Kirko \emph{et al.} \cite{kirko_phenomenon_1970} in 1970 for drops of mercury in hydrochloric acid, and later by Wollman \emph{et al.} in 2016 for water drops in air in a set of experiments conducted using drop towers \cite{wollman_more_2016}.
-\sout{The kinetic energy of the jump is supplied by the defect in free surface energy as the new minimum energy surface equilibrium has approximately constant curvature.} The motive force of the jump owes to the inertia of internal flows which occur as the interface deflects under the suddenly lessened $\mathbb{B}\mbox{o}$.
+a puddle) suddenly undergoes a large step reduction in Bond number it will spontaneously jump away from the surface.
+The Bond number is given by $\mathbb{B}\mbox{o} \equiv \frac{\Delta \rho g R^2}{\gamma}$, where $g$ is the acceleration, $R$ is the characteristic interfacial length scale, $\Delta \rho$ is the difference in densities across the interface, and $\gamma$ is the surface tension.
+The spontaneous drop jump was first observed experimentally in the Soviet Union by Kirko \emph{et al.} \cite{kirko_phenomenon_1970} in 1970 for drops of mercury in hydrochloric acid, and later by Wollman \emph{et al.} in 2016 for water drops in air \cite{wollman_more_2016}.
+The motive force of the jump owes to the inertia of internal flows which occur as the interface deflects under the suddenly lessened $\mathbb{B}\mbox{o}$.
 For drops with radial symmetry and sufficiently high initial $\mathbb{B}\mbox{o}$, inward radial capillary waves constructively interfere at the axis, leading to geysering and creation of satellite droplets by the Rayleigh-Plateau breakup of the geyser.
@@
 
-The physics of these relatively massive drops (far beyond the 1-$g_0$ millimetric capillary length scale) at once utterly defy terrestrial expectations about the ways in which liquid `should' behave, and also are of critical practical importance to space systems design where examples of such large capillary length scale multiphase flows are commonplace.
+The physics of these relatively massive drops is far beyond the 1-$g_0$ millimetric capillary length scale and tends to defy terrestrial expectations.
+However, such drops are also of critical practical importance to space systems design where examples of large capillary length scale multiphase flows are commonplace.
 
-During the `rolling-up' of drops under ideal conditions, the spontaneous jump phenomenon is governed by a balance of inertia and surface tension forces, and once aloft the drop motion is nominally in a regime of pure drag.
+During the `roll-up' of drops under ideal conditions, the spontaneous jump phenomenon is governed by a balance of inertia and surface tension forces, and once aloft the drop motion is nominally in a regime of pure drag.
 However, other forces can come into play.
 
-In the course of our work with spontaneous drop jump we have observed jumped drops to occasionally decelerate and return to the superhydrophobic surface, rebounding multiple times in the fashion of rigid bodies bouncing under 1-$g_0$.
+In the course of our work with spontaneous drop jump we have occasionally observed jumped drops to decelerate and return to the superhydrophobic surface, rebounding multiple times in the fashion of rigid bodies bouncing under 1-$g_0$.
 The forces at work in such situations are presumably electrostatic in origin.
-A time-lapsed composite image showing an example of the phenomenon is shown in Figure \ref{fig:bounce} for a 0.5 mL drop, and as a time-series in Figure \ref{fig:bounce_time} for a 0.05 mL drop.
+Examples of the phenomenon are shown as a time-lapsed composite image in Figure \ref{fig:bounce} for a 0.5 mL drop, and as a time-series in Figure \ref{fig:bounce_time} for a 0.05 mL drop.
 \begin{figure}[htb]
@@
 \includegraphics[width=0.5\textwidth]{bounce}
-\caption{The trajectory of a 0.5 mL drop is captured in a composite image over a single bounce period ($\sim 1.25$ s) presented at $\approx 10$ Hz.
+\caption{The trajectory of a 0.5 mL drop is captured in a composite image over a single bounce period ($\sim 1.25$ s) presented at $\approx 14$ Hz.
+Motion of the drop is from left to right.
 The surface potential of the superhydrophobic dielectric is $\varphi_s = 1.25 \pm 0.41$ kV.
@@
 
-We begin with some preliminary observations of the phenomenon:
+Preliminary observations of the phenomenon include:
 \begin{itemize}
@@
 \item The water drops are attracted to regions of high electric field.
-The horizontal (surface plane parallel) components of the drop trajectory usually oscillate about some central position during the experiment (except in cases of nearly pure 1-D vertical translation).
-For especially small drops close to the spontaneous drop jump limit (identified by Attari \emph{et al.} \citep{attari_puddle_2016} as $V_d \sim$ 0.01 mL) the drops do not jump, but translate across the surface in a rolling regime until either they reach a local maximum of the electric field, or until their motion is sufficiently damped by contact line hysteresis that pinning arrests their motion.
+The horizontal (surface plane parallel) components of the drop trajectory usually oscillate about some central position during the experiment, except in cases of nearly pure 1-D vertical translation.
+For especially small drops close to the spontaneous drop jump limit, identified by Attari \emph{et al.} \citep{attari_puddle_2016} as $V_d \sim$ 0.01 mL, the drops do not jump, but translate across the surface in a rolling regime until either a local maximum of the electric field is reached, or until their motion is sufficiently damped by contact line hysteresis that pinning arrests their motion.
 \item The drops appear to have net free charge. In cases of multiple simultaneous drop jumps the drops repel each other as they bounce or roll in orbital motion around regions of high field.
@@
 
-\sout{We expect that if the drop electrostatic potential energy is greater than the release of surface energy under the sudden change in $\mathbb{B}\mbox{o}$ in the form of the drop kinetic energy, the drop will return to an equilibrium state on the charged surface which minimizes the potential.}
-What is the origin of the extemporaneous electric field at work in these observations?
 It is well known that water acquires positive free charge when in contact with certain polymers, especially polytetrafluoroethylene (PTFE), through a process called contact charging \cite{langmuir_surface_1938}.
 PTFE, on the other hand, tends to readily acquire negative charge by contact with water.
-The superhydrophobic surfaces used in the spontaneous drop jump experiments have thin (nanometric) PTFE coatings, and we observe that it is extremely easy to produce significant surface potentials $\varphi_s \sim$ 100-500 V by simply flowing streams of distilled water over them.
+The superhydrophobic surfaces used in the spontaneous drop jump experiments have thin (nanometric) PTFE coatings, and we observe that it is easy to produce significant surface potentials $\varphi_s \sim$ 100-500 V by simply flowing streams of distilled water over them.
 A study of this water on PTFE contact charging phenomenon was conducted by Yatsuzuka \emph{et al.} \cite{yatsuzuka_electrification_1994}, who suggest that this process results from formation of an electrical double layer driven by selective adsorption of ($\mbox{OH}^-$) ions at the polymer surface; other recent work supports this hypothesis \cite{beattie_intrinsic_2006, strazdaite_water_2015}.
-Given the large roughness, or the ratio of projected to actual surface area, of the superhydrophobic surfaces used in the experiment, and given that the drops are initially in a Cassie-Baxter state, a somewhat electrically resistive air layer is maintained that reduces grounding of the drops despite the large potential difference between them and the surface charges.
+Given the large (roughness) ratio of projected to actual surface area of the superhydrophobic surfaces used in the experiment, and given that the drops are initially in a Cassie-Baxter state, a somewhat electrically resistive air layer is maintained that reduces grounding of the drops despite the large potential difference between them and the surface charges.
 
@@
 The drop charge could be due to the contact charging mechanism mentioned previously.
-For instance, in a 1996 paper, NASA flight engineer Don Pettit discusses the problem of low-gravity flow induced charging of liquids, resulting ultimately from contact charging phenomenon \cite{pettit_donald_flow_????}.
+NASA flight engineer Don Pettit germanely discusses the problem of low-gravity flow induced charging of liquids resulting ultimately from contact charging phenomenon \cite{pettit_donald_flow_????}.
 However, a more likely mechanism for the drop charge is field-induced charging occuring due to breakup of a conductor having a field-induced dipole (e.g., a physical separation of charge).
@@
 Notably, in Pettit's aforementioned discussion of contact charging of liquids in low-gravity, he remarks on accidental electrostatic `hula-ing' of silicone oil drops when ejected from a syringe in the vicinity of a highly-charged polymer surface during an experiment conducted aboard STS-5 by Space Shuttle mission specialist Joseph Allen \cite{pettit_donald_flow_????}.
-\sout{Depending on the (highly-variable) electrical conductivity of the silicone oil, and the material of the syringe used in the experiment, the charge could arise just as easily by field-induction as by contact charging.} Relatedly, in a series of informal and somewhat whimsical experiments Pettit himself electrostatically orbited small water drops around a triboelectrically charged PTFE knitting needle while aboard ISS during expedition 30/31 \cite{stevenson_electrostatic_2015}.
+Relatedly, in a series of informal and somewhat whimsical experiments Pettit himself electrostatically orbited small water drops around a triboelectrically charged PTFE knitting needle while aboard the International Space Station during expedition 30/31 \cite{stevenson_electrostatic_2015}.
 Again, in this case, the drop charge is likely field-induced.
 
-This electro-drop bounce phenomenon may have useful applications in a space environment, generally to tackle various manifestations of the so-called ``phase separation'' problem of separating a gas phase from a multi-phase flow (or the reverse case), in low-gravity.
-Removal of satellite droplets produced during pipetting in wet-lab research outside of a glovebox environment aboard ISS has been recently suggested as a application of the work [private communication, NASA JSC, E.
+The electro-drop bounce phenomenon may have useful applications in a space environment, generally to tackle various manifestations of the so-called ``phase separation'' problem of separating a gas phase from a multi-phase flow (or the reverse case) in low-gravity.
+Removal of satellite droplets produced during pipetting in wet-lab research outside of a glovebox environment aboard the International Space Station  has been recently suggested as an application of the work [private communication, NASA JSC, E.
 Unger, 2017].
-Drops can become spontaneously charged by contact with standard micropipette tips \citep{choi_spontaneous_2013}, and this free charge can possibly be leveraged for the purposes of phase separation in low-gravity.
+Drops can become spontaneously charged by contact with standard micropipette tips \citep{choi_spontaneous_2013}, and this free charge can be leveraged for the purposes of phase separation in low-gravity.
 
@@
 \end{equation}
-where $m$ is the drop mass, $y'' = \frac{d^2 y}{d t^2}$ is the drop acceleration, $F_D$ is the drag force which always opposes motion, and $F_E$ is the electrostatic force.
+where $m$ is the drop mass, $y'' = d^2 y/d t^2$ is the drop acceleration, $F_D$ is the drag force which always opposes motion, and $F_E$ is the electrostatic force.
 The assumed initial conditions are such that, when $\mathbb{B}\mbox{o}$ is suddenly reduced at the start of the drop tower free-fall period, the drop jumps with instantaneous initial velocity $U_0$ from its 1-$g_0$ resting position of $R_d$ at $t=0$.
@@
 In modeling the electrostatic force we begin with the standard electrohydrodynamic (EHD) approximation \cite{saville_electrohydrodynamics:_1997}.
-\sout{Under a DC electric field, we assume that the real part of the dielectric permittivity $\epsilon$, $\mbox{Re} \left( \epsilon \right) \approx  \mbox{constant}$.
-We also assume that electric currents are small enough that the effects of magnetic fields can be neglected.
-The validity of this assumption rests on the characteristic time scale $\tau_e = \epsilon /\sigma_e \ll 1$, where $\tau_e$ is the ratio of absolute dielectric permittivity $\epsilon = \kappa \epsilon_0$, to conductivity $\sigma_e$, of the medium, $\kappa$ is the relative dielectric permittivity, and $\epsilon_0$ is the vacuum permittivity.
-This characteristic time $\tau_e$ is also known as the relaxation time, and is a measure of how quickly the polarization of a dielectric responds to a change in electric field.
-Given the conductivity and permittivity in the limiting case of extremely-pure water ($ \epsilon \approx 80$, $\sigma_e = 18.2 \times 10^{6}$ $\Omega\mbox{cm}$) \cite{yatsuzuka_electrification_1994}, we estimate $\tau_e \approx 4 \times 10^{-6}$ s.
-The relaxation time for the common distilled water that is actually used in the drop experiments is shorter due to the presence of solvated ions which tend to increase the conductivity.
-Neglecting the effects of an electric double layer on hydration of ions in the water or the ambient atmosphere due to the relatively massive size of the drops studied, the assumption of small relaxation time further implies that the free charge present in the drops will remain approximately constant during the typical time interval of a low-gravity experiment.}
-
 Supposing that electrical forces acting on free charges and dipoles in a fluid are transferred directly to the fluid itself, the overall electrical body force density will be the divergence of the Maxwell stress tensor $\tau_m $,
@@
 \end{eqnarray}
-where $\mathbf{P}_e=(\kappa_w - \kappa_a)\epsilon_0 \mathbf{E}$ is the excess polarization, $\epsilon_0$ is the vacuum permittivity, and $\kappa_w$ and $\kappa_a$ are the relative dielectric constants of the water particle and air host fluid respectively.
+where $\mathbf{P}_e=(\kappa_w - \kappa_a)\epsilon_0 \mathbf{E}$ is the excess polarization, $\epsilon_0$ is the vacuum permittivity, and $\kappa_w$ and $\kappa_a$ are the relative dielectric constants of the water particle and air host fluid, respectively.
 Here it is convenient to use the simplifying shorthand $K = \frac{\kappa_w - \kappa_a}{\kappa_w + 2 \kappa_a}$, known as the Clausius-Mossotti factor.
-In cases where $K <$ 0, or $K>$ 0 the particle will be repelled or attracted to regions of strong field respectively.
-\sout{In our experiment, choosing the relative dielectric constants $\kappa_a \approx$ 1 and $\kappa_w \approx$ 80, we estimate $K \approx$ 0.96.
-It is important to note that the equivalent dipole approximation critically requires an assumption of small physical scale of the particle relative to the length scale of nonuniformity of the field, which in this case we take to be the length of the charged superhydrophobic surface, $L =$ 25 mm $\gg R_d \approx$ 2 mm.} By comparing DEP and Coulombic forces we note that a condition to neglect the DEP force is
+In cases where $K <$ 0, or $K>$ 0 the particle will be respectively repelled or attracted to regions of strong field.
+By comparing DEP and Coulombic forces we note that a condition to neglect the DEP force is
 \begin{eqnarray}
@@
 This conditions prevails in our experiments and we henceforth neglect the DEP force.
-\sout{There is some physical intuition to support this conclusion as well.
-The dielectric displacement $\mathbf{D} = \kappa \epsilon_0 \mathbf{E}$ of a water drop in air is high due to the large relative dielectric constant of water.
-This implies that the field strength within the drop is about 80 times smaller than in the surrounding medium.
-Thus it is not particularly inaccurate to model the dielectric volume of a drop as an equipotential conductive shell with zero field in its interior.
-As an aside, in treating the drop as an ideal conductor we note that in our specific case the electrostatic force is not a body force \emph{per se} as the electric field is acting on charges on the surface of the conductor.}
 
@@
 The polarization bound charge in the dielectric will be of the opposite sign of the free drop charge and thus there will be a force of attraction.
-This so-called image force is a correction to the Coulomb force due to the external electric field only, and can be found by a Green's Function solution of Laplace's equation for the electric field, the so-called the `method of images' \cite{david_j._griffiths_introduction_1999}.
+This so-called image force is a correction to the Coulomb force due to the external electric field only, and can be found by a Green's Function solution of Laplace's equation for the electric field, the so-called `method of images' \cite{david_j._griffiths_introduction_1999}.
 This resulting image force $\mathbf{F}_I$ is given by
@@
 
-Thus the 1-D governing Equation \ref{e_forces}, becomes
+Thus the 1-D governing Equation \ref{gov_eqn}, becomes
 \begin{equation}
@@
 
-By taking Taylor series expansions in large and small $y$-limits we can intuit a bit about the behavior of this field. In the limit $y/L \ll 1$ Equation \ref{e_field} reduces to
+By taking Taylor series expansions in large and small $y$-limits we gain some insight about the behavior of this field. In the limit $y/L \ll 1$ Equation \ref{e_field} reduces to
 \begin{equation}
@@
 \end{equation}
-Both regimes given by Equations \ref{near_field} and \ref{far_field} are identified in Figure \ref{fig:E0}.
+Equation \ref{e_field} with both regimes given by \ref{near_field} and \ref{far_field} are identified in Figure \ref{fig:E0}.
 \begin{figure}[h]
@@
  t^* = \frac{t}{t_c}, \hspace{10 mm} y^* = \frac{y}{y_c}, \end{equation}
-where $y_c$ and $t_c$ are characteristic length and time scales respectively, and using the coordinate transformation $y(0) - R = 0$, the governing equation becomes
+where $y_c$ and $t_c$ are characteristic length and time scales, and using the coordinate transformation $y(0) - R = 0$, the governing Equation \ref{gov_eqn_subs} becomes
 \begin{equation}
@@
 These plots show a trend of decreasing time-of-flight $t_f$, which is the time for the drop to return to the origin (a single `bounce'), and height at apoapse with increasing values of $\mathbb{I}\mbox{g}$.
-\sout{When $\mathbb{I}\mbox{g} = 1$, $t_f$ is exactly half of the characteristic time scale in this regime.
-In the limit of small $\mathbb{I}\mbox{m}$ the trajectories collapse to the $\mathcal{O}(1)$ solution regardless of the electrostatic Euler number.} Trajectories with $\mathbb{E}\mbox{u} \leq 0.1$ are essentially coincident given the scale of the axes used here.
+Trajectories with $\mathbb{E}\mbox{u} \leq 0.1$ are essentially coincident given the scale of the axes used here.
 In principle there is some coupling between $\mathbb{E}\mbox{u}$ and $\mathbb{I}\mbox{g}$; notably this relationship does not depend on the electric field $E_0$ but on a charge to mass ratio.
@@
 The Dryden Drop Tower at Portland State University uses a dual capsule design, inspired by the 2.2 s facility at NASA Glenn Research Center, which decouples drag acceleration felt by the external drag shield from the experiment.
-The experiment experiences approximately $\lesssim 1 \times 10^{-4}$ $g_0$ during free-fall for 2.1 s as the experiment and drag shield togeather plummet to the bottom of drop tower 6 stories below.
+The experiment experiences approximately $\lesssim 1 \times 10^{-4}$ $g_0$ during free-fall for 2.1 s as the experiment and drag shield plummet together to the bottom of the tower 6 stories below.
 A drop tower rig with a mounted experiment is shown in Figure \ref{fig:rig}.
 Single drops of distilled water in a range of volumes ($0.01 \leq V_d \leq 0.5$ mL) are carefully deposited on rig-mounted charged superhydrophobic substrates using a grounded glass syringe with $\pm $1 $\mu$L accuracy and then dropped in the drop tower.
-In this work 16 such single-drop drop jump experiments were conducted in low-gravity.
+In this work 16 such single-drop drop jump experiments are conducted.
 Drops are colored with red dye to improve thresholding accuracy in trajectory digitization.
 Drop trajectories are captured using a Panasonic HC-WX970 Camera recording at 120 fps.
-Drop trajectories are digitized from video using the particle tracking module in Fiji \cite{schindelin_fiji:_2012}.
+Drop trajectories are digitized from the video recordings using the particle tracking module in Fiji \cite{schindelin_fiji:_2012}.
 
@@
 The ion stream compensates the surface and space bound charges arising due to the polarization of the dielectric.
-After the corona source and DC-DC converter are powered off and the electrode is shorted across a bleed resistor the deposited negative ions remain on the substrate surface.
+After the corona source and DC-DC converter are powered off and the electrode is shorted across a bleed resistor, the deposited negative ions remain on the substrate surface.
 The electret is lamina of 3 to 4 0.4 mm thick corona charged polymethyl methacrylate (PMMA) sheets.
@@
 An SEM image of the pillar geometry is shown in Figure \ref{fig:SEM}.
-Contact angles of distilled water on the surface, measured using the tangent method, are $\sim \hspace{-1mm} 150^{\circ}$ when the surface is uncharged.
+Contact angles of distilled water on the surface, measured using the tangent method, are $\approx \hspace{-1mm} 150^{\circ}$ when the surface is uncharged.
 The roll-off angle of a 1 mL drop is $1^{\circ} \pm 0.5^{\circ}$.
-\sout{The hysteresis of the contact angle (the difference between the advancing $\theta_a$ and receding $\theta_r$ contact angles) is estimated from the roll-off angle using the model of Furmidge \cite{furmidge_studies_1962}, and is found to be approximately $25^{\circ} \pm 10^{\circ}$.}
 
@@
 \subsection{Parameter Estimation}
-Generally we seek the parameters $\mathbf{x}$ that solve the inverse problem $G(\mathbf{x}) + \mathbf{u} = \mathbf{d}$, where the model $G(\mathbf{x})$ describes some relationship between the vector of parameters $\mathbf{x}$ and a set of observations $\mathbf{d}$, and where $\mathbf{u}$ is the measurement error.
+We generally seek the parameters $\mathbf{x}$ that solve the inverse problem $G(\mathbf{x}) + \mathbf{u} = \mathbf{d}$, where the model $G(\mathbf{x})$ describes some relationship between the vector of parameters $\mathbf{x}$ and a set of observations $\mathbf{d}$, and where $\mathbf{u}$ is the measurement error.
 In particular we seek the parameter set $\mathbf{x} = \left\langle q, \hspace{2 mm} V_d, \hspace{2 mm} \sigma \right\rangle$ that has the highest probability (i.e.
@@
 The non-convexity of the problem implies that there are many local minima of the objective function.
-We use a gradient-free direct-search Nelder-Mead \cite{nelder_simplex_1965} algorithm implemented as \verb|scipy.optimize.minimize(method='Nelder-Mead')| in \emph{SciPy}.
+To solve the optimization problem we employ the gradient-free direct-search Nelder-Mead \cite{nelder_simplex_1965} algorithm implemented as \verb|scipy.optimize.minimize(method='Nelder-Mead')| in \emph{SciPy}.
 Nelder-Mead is relatively robust to noise and is thrifty with our computationally expensive function-calls.
@@
 Because Nelder-Mead cannot be used for explicitly constrained problems we implement the constraints using an exterior penalty function.
-\sout{In the case of $q$, which we do not directly observe in experiment, we bound identifiability by using a Montecarlo bootstrap approach [WIP].}
 
@@
 \end{equation} 
-with the transformation $A = V_d^{2/3}$ finds that $k=7.589 \times 10^{-11} \pm  1.47 \times 10^{-11}$ F/m with $R^2 = 0.65$, $F=27$. 
+with the transformation $A = V_d^{2/3}$ finds that $k=7.589 \times 10^{-11} \pm  1.47 \times 10^{-11}$ F/m with $R^2 = 0.65$ and $F=27$. 
 \begin{figure}[h]
@@
 This likely results from large variance in $U_0$ due to contact line hysteresis during the drop roll-up.
-Contact line losses predominate in the sub 1 mL volume drops which are primarily the object of this study.
+Contact line losses predominate in the $<$ 1 mL volume drops which are primarily the object of this study.
 
@@
 Electrostatic Euler numbers in the data set vary between $1.4 \lesssim \mathbb{E}\mbox{u} \lesssim 35.4$.
-\sout{The dielectrophoretic force plays a small role when drops have net charge in a DC field.
-The condition to neglect the DEP force was satisfied for all experiments in the dataset with typical values of the condition number $\kappa_w \epsilon_0 K R_d^2 E_0/q \approx \mathcal{O}(10^{-6})$}.
 In the non-dimensional trajectories with short-time scaling shown in Figure \ref{fig:series_s_ds}, we see that the scaled trajectory apoapses are consistently $\mathcal{O}(1)$, with all trajectories overshooting their characteristic time scale (which predicts returns at $t^*  =2$ at zeroth order).
@@
     \caption{Simulated forces acting on drops up to the first apoapse as determined by the MLE solutions to Equation \ref{gov_eqn_subs} for all drops in the dataset.
-The (\protect\redline) lines denote the Coulomb force, the (\protect\blueline) lines the drag force, and the (\protect\cyanline) lines the foce due to image charge respectively.
+The (\protect\redline) lines denote the Coulomb force, the (\protect\blueline) lines the drag force, and the (\protect\cyanline) lines the force due to image charge respectively.
 The forces are scaled by the drop inertia.\label{fig:forces}}
-\end{figure}
-
-\subsection{Drop Impacts}
-\sout{In 1-$g_0$, for Weber numbers $\mathbb{W}\mbox{e} \equiv \rho U^2 R_d/\gamma >$ 0.4, impact rebound behavior on a superhydrophobic surface can be strongly influenced by damping from contact line hysteresis.
-For the low Bond and Ohnesorge numbers occurring in free-fall, the drop impact dynamics may additionally include electrohydrodynamic surface wettability effects.
-To date there has been little work in general on drop impacts outside of two regimes: (1) very low $\mathbb{R}\mbox{e}$ viscous drop spreading driven by capillary forces at the contact line and (2) impacts at `high' Weber numbers.
-Models for dynamic contact lines in general remain controversial, even for ordinary spreading of liquids, despite decades of work in the area.}
-
-\sout{If we naively neglect the contact line dynamics, the dimensionless groups for isothermal drop impacts are the Ohnesorge number $\mathbb{O}\mbox{h} \equiv \mu/\sqrt{\rho \gamma R_d}$, the Weber number $\mathbb{W}\mbox{e}$, and Bond number $\mathbb{B}\mbox{o}$.
-The Weber number scales the driving force of drop spreading.
-In the well-studied case of high $\mathbb{W}\mbox{e}$ impacts the drop bulk is driven radially outward by the impact induced pressure gradient, whereas in the case of small $\mathbb{W}\mbox{e}$ wetting impacts the liquid is driven outwards by capillary force.
-The Ohnesorge number, by contrast, is a measure of viscous effects in an inertial-capillary flow and scales the force that resists spreading.
-Previous empirical work for low $\mathbb{O}\mbox{h}$ and low $\mathbb{W}\mbox{e}$ impacts includes that of Schiaffino and Sonin \cite{schiaffino_molten_1997} with wetting and non-wetting impacts of molten metal drops on cold surfaces.
-Mol\'{a}\u{c}ek and Bush \cite{molacek_quasi-static_2012}, Gopinath and Koch \cite{gopinath_collision_2002}, and Okamura \cite{okumura_water_2003} have all developed analytical models of drop impacts at low $\mathbb{W}\mbox{e}$ and low $\mathbb{B}\mbox{o}$.
-These works show increasing dimensionless contact time $\tau$ as Weber number decreases, in opposition to the results of Richard and Qu\'{e}r\'{e} \cite{richard_surface_2002} which show experimentally that the dimensionless contact time is approximately a constant $\tau \approx 2.6(\rho R^3_d/\sigma)^{1/2}$ with respect to $\mathbb{W}\mbox{e}$ at large $\mathbb{W}\mbox{e}$.
-Mol\'{a}\u{c}ek's work also shows that impact coefficients of restitution $C_r$ depend non-linearly on $\mathbb{B}\mbox{o}$.
-To date little experimental work has been performed on low $\mathbb{B}\mbox{o}$ impacts as well.
-An exception is provided by Duvivier \emph{et al.} \cite{duvivier_drop_2012} who studied regimes of aqueous ferrofluid drop impacts on superhydrophobic substrates under the influence of an external magnetic field.
-In this case the magnetic body force acts as an ersatz gravity.}
-
-\sout{When the electro-drop bounce occurs, if the drop has enough time to return a non-wetting impact occurs on the charged substrate usually followed by rebound.
-We observe average drop impact $\mathbb{O}\mbox{h} \approx 2.18 \pm 0.36$ and  $\mathbb{W}\mbox{e} \approx 0.28 \pm 0.22$.
-Thus impact velocity plays little role in the spreading dynamics of the bounces and viscous effects are important but do not dominate inertia.
-Notably we observe underdamped oscillations of drop interfaces during impact.
-Access to such relatively low $\mathbb{O}\mbox{h}$ and low $\mathbb{W}\mbox{e}$ drop impacts enabled by the low-gravity environment raises an interesting possibilities for new work on the basic science of drop impacts.
-This work also intersects the burgeoning field which spans the intersection of electrowetting on patterned surfaces and drop impacts.
-Various authors \cite{bartolo_bouncing_2006, reyssat_bouncing_2006} have suggested that a wetting transition called Fakir impalement can occur during impacts on patterned hydrophobic surfaces if a certain critical pressure $p_c \sim \gamma h/l$ is exceeded, where $h/l$ is the pillar aspect ratio of the patterned surface.
-This pressure can result from fluid inertia in a high $\mathbb{W}\mbox{e}$ impact regime, or can result from an electrostatic pressure due to an external electric field.
-The latter case is responsible for the irreversiblity that notoriously plagues static EWOD experiments.
-There is hope that additional work in this area could produce engineered surfaces that are tuneably wetting under drop impacts by leveraging electrostatic forces.}
-
-\sout{Our preliminary results showing the influence of $\mathbb{W}\mbox{e}$ and electrostatic Bond number $\mathbb{B}\mbox{o}_e \equiv \epsilon E_0^2 R_d/\gamma $ on drop impact dimensionless contact time $\tau$ and coefficient of restitution $C_r$ are shown in Figures \ref{fig:contact} and \ref{fig:restitution}.}
-
-\begin{figure}[htb]
-    \centering
-    \resizebox{0.5\textwidth}{!}{\input{../figures/contact2.pgf}}
-    \caption{Dimensionless contact time $t_j/\tau$ compared with impact $\mathbb{W}\mbox{e}$ and $\mathbb{B}\mbox{o}_e$.\label{fig:contact}}
-\end{figure}
-
-\begin{figure}[htb]
-    \centering
-    \resizebox{0.5\textwidth}{!}{\input{../figures/restitution.pgf}}
-    \caption{Impact coefficient of restitution $C_r$ compared with impact $\mathbb{W}\mbox{e}$ and $\mathbb{B}\mbox{o}_e$.\label{fig:restitution}}
 \end{figure}

### 2020-02-07 doc/paper/aiptemplate.tex
paper updates, added l-m estimation prototype code

@@
 \renewcommand{\pgfimage}[2][]{\pgfimageWithoutPath[#1]{../figures/#2}}
-
 \begin{document}
@@
 
-We investigate the dynamics of spontaneous jumps of water drops from electrically charged superhydrophobic dielectric substrates during a sudden step reduction in gravity level.
-In the brief free-fall environment of a drop tower, with an external electric field drop dynamics are dominated by Coulombic force instead of gravity.
+We investigate the dynamics of spontaneous jumps of water drops from electrically charged superhydrophobic dielectric substrates during sudden step reductions in gravity level.
+In the free-fall environment of a drop tower the dynamics of drops subject to external electric fields are dominated by Coulombic force instead of gravity.
 These forces lead to a drop bouncing behavior similar to well-known terrestrial phenomena, though occurring for much larger drops ($\sim$ 0.5 mL).
-We provide a 1-dimensional model for the phenomenon, its scaling, and asymptotic estimates for drop time-of-flight in two regimes: at short-times close to the substrate when drop inertia balances Coulombic force due to net free charge and image charges in the dielectric substrate and at long-times far from the substrate when drop inertia balances free charge Coulombic force and drag.
+We provide a 1-dimensional model for the phenomenon, its scaling, and asymptotic estimates for drop time-of-flight in two regimes: at short-times close to the substrate when drop inertia balances Coulombic force due to net free charge and image charges in the dielectric substrate, and at long-times far from the substrate when drop inertia balances free charge Coulombic force and drag.
 In both regimes the dimensionless electrostatic Euler number $\mathbb{E}\mbox{u}$, which is a ratio of inertia to electrostatic force, appears as a key parameter.
@@
 \section{Spontaneous Drop Jump}
-When a nonwetting, gravity-dominated sessile drop (e.g.
+When a nonwetting, gravity-dominated sessile drop (i.e.
 a puddle) suddenly undergoes a large step reduction in Bond number it will spontaneously jump away from the surface.
 The Bond number is given by $\mathbb{B}\mbox{o} \equiv \frac{\Delta \rho g R^2}{\gamma}$, where $g$ is the acceleration, $R$ is the characteristic interfacial length scale, $\Delta \rho$ is the difference in densities across the interface, and $\gamma$ is the surface tension.
-The spontaneous drop jump was first observed experimentally in the Soviet Union by Kirko \emph{et al.} \cite{kirko_phenomenon_1970} in 1970 for drops of mercury in hydrochloric acid, and later by Wollman \emph{et al.} in 2016 for water drops in air \cite{wollman_more_2016}.
-The motive force of the jump owes to the inertia of internal flows which occur as the interface deflects under the suddenly lessened $\mathbb{B}\mbox{o}$.
-For drops with radial symmetry and sufficiently high initial $\mathbb{B}\mbox{o}$, inward radial capillary waves constructively interfere at the axis, leading to geysering and creation of satellite droplets by the Rayleigh-Plateau breakup of the geyser.
+The spontaneous drop jump was first observed experimentally in the Soviet Union by Kirko \emph{et al.} \cite{kirko_phenomenon_1970} in 1970 for drops of mercury in hydrochloric acid, and later by Wollman \emph{et al.} \cite{wollman_more_2016} in 2016 for water drops in air.
+The motive force of the jump owes to the inertia of internal flows occurring as the drop interface spontaneously reconfigures to the constant curvature minimal energy surface characteristic of the suddenly lessened $\mathbb{B}\mbox{o}$.
+For drops with radial symmetry and sufficiently high initial $\mathbb{B}\mbox{o}$ inward radial capillary waves constructively interfere at the axis leading to geysering and creation of satellite droplets by the Rayleigh-Plateau breakup of the geyser.
 In the case of smaller jumping drops the capillary waves are quickly damped by viscous forces.
 
-The physics of these relatively massive drops is far beyond the 1-$g_0$ millimetric capillary length scale and tends to defy terrestrial expectations.
-However, such drops are also of critical practical importance to space systems design where examples of large capillary length scale multiphase flows are commonplace.
+The physics of these relatively massive drops, far beyond the 1-$g_0$ millimetric capillary length scale, tend to defy terrestrial expectations.
+However, such drops are of critical practical importance to space systems design where examples of large capillary length scale two-phase flows are commonplace.
 
@@
 The forces at work in such situations are presumably electrostatic in origin.
-Examples of the phenomenon are shown as a time-lapsed composite image in Figure \ref{fig:bounce} for a 0.5 mL drop, and as a time-series in Figure \ref{fig:bounce_time} for a 0.05 mL drop.
+Examples of the phenomenon are shown in the time-lapsed composite image of Figure \ref{fig:bounce} for a 0.5 mL drop, and in the time-series of Figure \ref{fig:bounce_time} for a 0.05 mL drop.
 \begin{figure}[htb]
 \centering
-\includegraphics[width=0.5\textwidth]{bounce}
+\includegraphics[width=0.5\textwidth]{bounce.png}
 \caption{The trajectory of a 0.5 mL drop is captured in a composite image over a single bounce period ($\sim 1.25$ s) presented at $\approx 14$ Hz.
@@
 
-Preliminary observations of the phenomenon include:
+Preliminary observations of the drop bouncing behavior include:
 \begin{itemize}
-\item Observed maximum drop (de-)accelerations are on the order of $\sim$30 cm/s$^2$ for a range of drop volumes $0.03 \lessapprox V_d \lessapprox 0.5$ mL.
+\item Observed maximum drop (de-)accelerations are on the order of $\sim$0.3 m/s$^2$ for a range of drop volumes $0.03 \lessapprox V_d \lessapprox 0.5$ mL.
 \item The water drops are attracted to regions of high electric field.
-The horizontal (surface plane parallel) components of the drop trajectory usually oscillate about some central position during the experiment, except in cases of nearly pure 1-D vertical translation.
-For especially small drops close to the spontaneous drop jump limit, identified by Attari \emph{et al.} \citep{attari_puddle_2016} as $V_d \sim$ 0.01 mL, the drops do not jump, but translate across the surface in a rolling regime until either a local maximum of the electric field is reached, or until their motion is sufficiently damped by contact line hysteresis that pinning arrests their motion.
-\item The drops appear to have net free charge. In cases of multiple simultaneous drop jumps the drops repel each other as they bounce or roll in orbital motion around regions of high field.
-\item The magnitude of the drop trajectory maxima (apoapses) are related to the drop volume (mass), and initial jump velocity (inertia), and to the electric field strength.
+Horizontal (surface plane parallel) translations usually orbit or oscillate about some central position during the experiment.
+Presumably this central position is a local maxima of the electric field.
+For especially small drops close to the spontaneous drop jump limit, identified by Attari \emph{et al.} \citep{attari_puddle_2016} as $V_d \sim$ 0.01 mL, the drops do not jump but instead translate across the surface in a rolling regime.
+This oscillatory translation is damped and eventually arrested by contact line hysteresis and viscous dissipation.
+\item The drops have net free charge. In experiments of multiple simultaneous drop jumps the drops repel each other as they bounce or roll in orbital motion around regions of high field.
+\item The magnitude of the drop trajectory maxima (the trajectory apoapsis) is related to the drop volume, initial jump velocity, and electric field strength.
 \end{itemize}
@@
 It is well known that water acquires positive free charge when in contact with certain polymers, especially polytetrafluoroethylene (PTFE), through a process called contact charging \cite{langmuir_surface_1938}.
-PTFE, on the other hand, tends to readily acquire negative charge by contact with water.
+PTFE, by contrast, tends to readily acquire negative charge by contact with water.
 The superhydrophobic surfaces used in the spontaneous drop jump experiments have thin (nanometric) PTFE coatings, and we observe that it is easy to produce significant surface potentials $\varphi_s \sim$ 100-500 V by simply flowing streams of distilled water over them.
-A study of this water on PTFE contact charging phenomenon was conducted by Yatsuzuka \emph{et al.} \cite{yatsuzuka_electrification_1994}, who suggest that this process results from formation of an electrical double layer driven by selective adsorption of ($\mbox{OH}^-$) ions at the polymer surface; other recent work supports this hypothesis \cite{beattie_intrinsic_2006, strazdaite_water_2015}.
-Given the large (roughness) ratio of projected to actual surface area of the superhydrophobic surfaces used in the experiment, and given that the drops are initially in a Cassie-Baxter state, a somewhat electrically resistive air layer is maintained that reduces grounding of the drops despite the large potential difference between them and the surface charges.
+A study of this water on PTFE contact charging phenomenon was conducted by Yatsuzuka \emph{et al.} \cite{yatsuzuka_electrification_1994}, who suggest that this process results from formation of an electrical double layer driven by selective adsorption of ($\mbox{OH}^-$) ions at the polymer surface.
+Other recent work supports this hypothesis \cite{beattie_intrinsic_2006, strazdaite_water_2015}.
+Given the large roughness ratio of projected to actual surface area of the superhydrophobic surfaces used in the experiment, and given that the drops are initially in a Cassie-Baxter state, there exists a somewhat electrically resistive air layer which maintains a significant floating potential of the drop over time.
 
@@
 The drop charge could be due to the contact charging mechanism mentioned previously.
-NASA flight engineer Don Pettit germanely discusses the problem of low-gravity flow induced charging of liquids resulting ultimately from contact charging phenomenon \cite{pettit_donald_flow_????}.
-However, a more likely mechanism for the drop charge is field-induced charging occuring due to breakup of a conductor having a field-induced dipole (e.g., a physical separation of charge).
+NASA flight engineer Don Pettit discusses the problem of low-gravity flow induced charging of liquids resulting ultimately from contact charging phenomenon \cite{pettit_donald_flow_????}.
+We suspect that a more likely mechanism for the drop charge is field-induced charging occuring due to physical breakup of a conductor with a field-induced dipole.
 In our work this might occur when a drop is deposited on the charged surface by a grounded syringe.
-The metal syringe needle tip and the liquid in the syringe itself are essentially a ground connection which is broken when the syringe is suddenly removed in the presence of an external electric field.
 Field-induced charging is at work in the famous Kelvin thunderstorm and is applied in inkjet and electrospay technologies, where in each case the breakup is by the Rayleigh-Plateau instability.
 Notably, in Pettit's aforementioned discussion of contact charging of liquids in low-gravity, he remarks on accidental electrostatic `hula-ing' of silicone oil drops when ejected from a syringe in the vicinity of a highly-charged polymer surface during an experiment conducted aboard STS-5 by Space Shuttle mission specialist Joseph Allen \cite{pettit_donald_flow_????}.
-Relatedly, in a series of informal and somewhat whimsical experiments Pettit himself electrostatically orbited small water drops around a triboelectrically charged PTFE knitting needle while aboard the International Space Station during expedition 30/31 \cite{stevenson_electrostatic_2015}.
-Again, in this case, the drop charge is likely field-induced.
+Relatedly, in a series of informal and somewhat whimsical experiments, Pettit himself electrostatically orbited small water drops around a triboelectrically charged PTFE knitting needle while aboard the International Space Station (ISS) during expedition 30\textbackslash 31 \cite{stevenson_electrostatic_2015}.
+Again, the drop charge is likely field-induced.
 
-The electro-drop bounce phenomenon may have useful applications in a space environment, generally to tackle various manifestations of the so-called ``phase separation'' problem of separating a gas phase from a multi-phase flow (or the reverse case) in low-gravity.
-Removal of satellite droplets produced during pipetting in wet-lab research outside of a glovebox environment aboard the International Space Station  has been recently suggested as an application of the work [private communication, NASA JSC, E.
-Unger, 2017].
-Drops can become spontaneously charged by contact with standard micropipette tips \citep{choi_spontaneous_2013}, and this free charge can be leveraged for the purposes of phase separation in low-gravity.
+The electro-drop bounce phenomenon may have useful applications in a low-gravity environment, generally to tackle seperation of droplets from a two-phase flow.
+Removal of satellite droplets produced during pipetting in wet-lab research aboard the International Space Station has been recently suggested as an application of this work \cite{ungar_surface_2018}.
+Droplets can become spontaneously charged by contact with standard micropipette tips \citep{choi_spontaneous_2013} and this free charge can be leveraged for the purpose of phase separation in low-gravity.
+These drops are easily inhaled and present a safety hazard to astronauts.
+The application of this work could allow future wet-lab work to proceed outside of the burdensome constraints of a glovebox environment, thus increasing the yield of such research aboard ISS to the benefit of humanity.
 
@@
 where $m$ is the drop mass, $y'' = d^2 y/d t^2$ is the drop acceleration, $F_D$ is the drag force which always opposes motion, and $F_E$ is the electrostatic force.
-The assumed initial conditions are such that, when $\mathbb{B}\mbox{o}$ is suddenly reduced at the start of the drop tower free-fall period, the drop jumps with instantaneous initial velocity $U_0$ from its 1-$g_0$ resting position of $R_d$ at $t=0$.
+The assumed initial conditions are such that when $\mathbb{B}\mbox{o}$ is suddenly reduced at the start of the drop tower free-fall period, the drop jumps with instantaneous initial velocity $U_0$ from its 1-$g_0$ resting position of $R_d$ at $t=0$.
 The dynamical system is sketched schematically in Figure \ref{fig:apparatus}.
@@
 The force felt by the dipole is
-\begin{eqnarray} \label{dep_force}
+\begin{eqnarray}
 \mathbf{F}_{DEP} &=& \left( \mathbf{P}_e \cdot \nabla \right) \mathbf{E} \nonumber \\
-&=& 2 \pi R_d^3 \kappa_w \epsilon_0 K \nabla E^2,
+&=& 2 \pi R_d^3 \kappa_w \epsilon_0 K \nabla E^2, \nonumber
 \end{eqnarray}
@@
 The polarization bound charge in the dielectric will be of the opposite sign of the free drop charge and thus there will be a force of attraction.
-This so-called image force is a correction to the Coulomb force due to the external electric field only, and can be found by a Green's Function solution of Laplace's equation for the electric field, the so-called `method of images' \cite{david_j._griffiths_introduction_1999}.
+This so-called image force is a correction to the Coulomb force due to the external electric field only, and can be found by a Green's Function solution of Laplace's equation for the electric field, the `method of images' \cite{david_j._griffiths_introduction_1999}.
 This resulting image force $\mathbf{F}_I$ is given by
@@
 subject to
-\begin{equation}
+\begin{equation*}
 y(0) = R_d, \hspace{5 mm} \mbox{and} \hspace{5 mm} y'(0) = U_0 .
-\end{equation}
+\end{equation*}
 
 \subsection{Electric Field}
-If we consider the charged dielectric surface of our experiments to be a square sheet of charge lying in the $xz$-plane with width $L$, the symmetry of the problem happily lets us obtain the $y$-component of the electric field $\mathbf{E}$ by direct integration (as a superposition of line charges) \citep{david_j._griffiths_introduction_1999} as
+If we consider the charged dielectric surface of our experiments to be a square sheet of charge lying in the $xz$-plane of width $L$, the symmetry of the problem lets us obtain the $y$-component of the electric field $\mathbf{E}$ by direct integration (as a superposition of line charges) \citep{david_j._griffiths_introduction_1999} as
 \begin{equation}
@@
 \subsection{Scaling}
-Equation \ref{gov_eqn_subs} is non-linear, non-homogeneous and must be solved numerically.
+Equation \ref{gov_eqn_subs} is non-linear, non-homogeneous, and must be solved numerically.
 Nevertheless we seek approximate solutions to the equation analytically using perturbation methods.
@@
 \begin{equation*}
-{y^*}(0) = 0, \hspace{5 mm} \mbox{and} \hspace{5 mm} {y^*}'(0) = \mathbf{\Pi}_5,
+{y^*}(0) = 0 \hspace{5 mm} \mbox{and} \hspace{5 mm} {y^*}'(0) = \mathbf{\Pi}_5,
 \end{equation*}
@@
 In this limit we can approximate the electric field as the constant $E_0$.
-One possible characteristic length scale is $y_c \sim R_d$, however this scale is overly restrictive with respect to time.
+One possible characteristic length scale is $y_c \sim R_d$.
+However this scale is overly restrictive with respect to time.
 With $y_c \sim U_0 t_c$ and picking $t_c$ such that the Coulombic force $\mathbf{\Pi}_3 \sim \mathcal{O}(1)$, the intrinsic scales are found such that
-\[ t_c \sim \frac{m U_0}{q E_0}, \hspace{5 mm} \mbox{and} \hspace{5 mm} 
+\[ t_c \sim \frac{m U_0}{q E_0} \hspace{5 mm} \mbox{and} \hspace{5 mm} 
 y_c \sim \frac{m U_0^2}{q E_0} .
@@
 \begin{equation*}
-{y^*}(0) = 0, \hspace{5 mm} \mbox{and} \hspace{5 mm} {y^*}'(0) = 1 .
+{y^*}(0) = 0 \hspace{5 mm} \mbox{and} \hspace{5 mm} {y^*}'(0) = 1
 \end{equation*}
 with 
-\[ \mathbb{I}\mbox{g} \equiv \frac{k q}{16 \pi \epsilon_0 R_d^2 E_0} = \mathbf{\Pi}_3, \hspace{5 mm}
+\[ \mathbb{I}\mbox{g} \equiv \frac{k q}{16 \pi \epsilon_0 R_d^2 E_0} = \mathbf{\Pi}_3  \hspace{5 mm} \mbox{and} \hspace{5 mm}
 \mathbb{E}\mbox{u} \equiv \frac{m U_0^2}{q E_0 R_d} = \mathbf{\Pi}_4 ,
 \]
-where the Image number $\mathbb{I}\mbox{g}$ is the ratio of image forces to the Coulombic force of the unperturbed field, and the electrostatic Euler number $\mathbb{E}\mbox{u}$ is the ratio of inertia to electrostatic force, or equivalently, in a conservative system $\mathbb{E}\mbox{u}$ can be thought of as a ratio of kinetic energy $m U_0^2$ and electrostatic potential energy $q E_0 R_d$.
+where the Image number $\mathbb{I}\mbox{g}$ is the ratio of image forces to the Coulombic force of the unperturbed field, and the electrostatic Euler number $\mathbb{E}\mbox{u}$ is the ratio of inertia to electrostatic force.
+Equivalently, in a conservative system $\mathbb{E}\mbox{u}$ can be thought of as a ratio of kinetic energy $m U_0^2$ to electrostatic potential energy $q E_0 R_d$.
 
@@
 Here we approximate the electric field as $E \approx y_c^2 E_0 y^{-2}$.
-We choose the scaling $y_c \sim U_0 t_c$ and $\mathbf{\Pi}_3 \sim \mathcal{O}(1)$ for its combination of physical simplicity, few $\mathbf{\Pi}$ terms, and homogeneous initial conditions.
+We choose the scaling $y_c \sim U_0 t_c$ and $\mathbf{\Pi}_3 \sim \mathcal{O}(1)$ for its combination of physical simplicity, reduced number of terms, and homogeneous initial conditions.
 The intrinsic scales for this case are given by
@@
 \begin{equation*}
-{y^*}(0) = 0, \hspace{5 mm} \mbox{and} \hspace{5 mm} {y^*}'(0) = 1, 
+{y^*}(0) = 0 \hspace{5 mm} \mbox{and} \hspace{5 mm} {y^*}'(0) = 1, 
 \end{equation*}
@@
 For $\mathbb{E}\mbox{u} \ll 1$ we find asymptotic solutions of the non-linear equations by means of regular perturbations.
-In this case we use the naive expansion
+In this case we employ the naive expansion
 \begin{equation}
@@
 \begin{gather}
-{y^*}({t^*}) = {t^*} + \frac{{t^*}^{2}}{2} \left(-1 - \mathbb{I}\mbox{g}\right)
+{y^*}({t^*}) = {t^*} + \frac{{t^*}^{2}}{2} \left(-1 - \mathbb{I}\mbox{g}\right) \nonumber \\
  + \mathbb{E}\mbox{u} \left(\frac{\mathbb{I}\mbox{g} {t^*}^{3}}{3} + \frac{\mathbb{I}\mbox{g} {t^*}^{4}}{12} \left(-1 - \mathbb{I}\mbox{g} \right)\right) \nonumber \\
@@
 We plot the approximate short-time solution of Equation \ref{perturb_image} with varying values of $\mathbb{I}\mbox{g}$ in Figure \ref{fig:short_times}.
-These plots show a trend of decreasing time-of-flight $t_f$, which is the time for the drop to return to the origin (a single `bounce'), and height at apoapse with increasing values of $\mathbb{I}\mbox{g}$.
-Trajectories with $\mathbb{E}\mbox{u} \leq 0.1$ are essentially coincident given the scale of the axes used here.
+For increasing $\mathbb{I}\mbox{g}$ these plots show a trend of decreasing time-of-flight $t_f$, which is the time for the drop to return to the origin (a single `bounce'), and height at apoapse.
+Trajectories with $\mathbb{E}\mbox{u} \leq 0.1$ are essentially coincident given the scale of the axes employed.
 In principle there is some coupling between $\mathbb{E}\mbox{u}$ and $\mathbb{I}\mbox{g}$; notably this relationship does not depend on the electric field $E_0$ but on a charge to mass ratio.
@@
     \caption{Short-time scaled drop trajectories for various values of $\mathbb{E}\mbox{u}$, $\mathbb{I}\mbox{g}$.
-The trajectory reduces to the classical $\mathcal{O}(1)$ solution for small values of $\mathbb{I}\mbox{g}$.
-It should be noted that despite what is implied by these plots $\mathbb{I}\mbox{g}$ is not necessarily independent of $\mathbb{E}\mbox{u}$, sharing $q$ and $E_0$ as common factors, as well as the covariance relationships $U_0 \propto R_d^2$, and $m \propto R_d^3$.}
+The trajectory reduces to the classical $\mathcal{O}(1)$ solution for small values of $\mathbb{I}\mbox{g}$.}
     \label{fig:short_times}
@@
 \subsubsection{Inertial Electro-Viscous Limit}
-By similar arguments we find an asymptotic estimate of the trajectory in the long-time regime.
-If we assume a constant scale for the drag coefficient $C_D \approx 0.5$ then $\mathbb{D}\mbox{g}$ is approximately a constant $\mathbb{D}\mbox{g} \approx 6 \times 10^{-4}$ in all of our experiments.
-The approximate solution is
+By similar arguments we find an asymptotic estimate of the trajectory in the long-time regime. The approximate solution is 
 \begin{gather}
@@
 \end{figure}
-We note that the trajectory reduces to the classical $\mathcal{O}(1)$ solution for small values of of $\phi \mathbb{E}\mbox{u}$.
-We also note that with $\mathbb{D}\mbox{g} = 6 \times 10^{-4}$ the effect of drag is slight, appearing only as a slight correction to the higher order terms.
+We note that the trajectory reduces to the classical $\mathcal{O}(1)$ solution for small values of $\phi \mathbb{E}\mbox{u}$.
+We also note that if we assume a constant value for the drag coefficient $C_D \approx 0.5$ then $\mathbb{D}\mbox{g}$ is approximately a constant $\mathbb{D}\mbox{g} \approx 6 \times 10^{-4}$ in all of our experiments.
+Thus the effect of drag on the trajectory is slight, appearing only as a slight correction to the higher order terms.
 
-By again applying a regular perturbation to the asymptotic solution, Equation \ref{perturb_viscous}, with the expansion
+Again applying a regular perturbation to Equation \ref{perturb_viscous}, using the expansion
 \[ t^* \sim t^*_0 + \phi \mathbb{E}\mbox{u} t^*_1 + \phi^2 \mathbb{E}\mbox{u}^2 t^*_2 \ldots \phi^n \mathbb{E}\mbox{u}^n t^*_n  
@@
 \end{gather*}
-Substituting the experimental value of $\mathbb{D}\mbox{g}$ we find the time-of-flight estimate for water drops is
+Substituting the experimental value of $\mathbb{D}\mbox{g}$ we find the time-of-flight estimate for water drops
 \begin{equation} \label{time_of_flight}
@@
 \end{equation} 
+Similarly, given the experimental value of $\mathbb{D}\mbox{g}$, and with the substitution $t^*=1$ we can find from Equation \ref{perturb_viscous} an asymptotic estimate of the dimensionless trajectory apoapse
+\begin{equation} \label{dimless_apoapse}
+y_f = \frac{1}{2} + 0.249 \phi \mathbb{E}\mbox{u} - 0.097 \phi \mathbb{E}\mbox{u}^{2} + \mathcal{O}(\phi^3 \mathbb{E}\mbox{u}^3).
+\end{equation}
 
-As $\phi \mathbb{E}\mbox{u}$ grows to be no longer small, the time-of-flight grows rapidly with an asymptote at a certain critical velocity; this is an electrostatic escape velocity $U_e$.
+As $\phi \mathbb{E}\mbox{u}$ increases, the time-of-flight grows rapidly with an asymptote at a certain critical velocity; this is an electrostatic escape velocity $U_e$.
 We can find the escape velocity by solving a limiting version of the equation of motion
@@
 \]
-This equation has an asymptotic velocity $U_{\infty}$ at $y = \infty$, which is real provided 
-\[ U_0 \geq  U_e = y_c \sqrt{\frac{2 q E_0 }{m R_d}},
+This equation has an asymptotic velocity $U_{\infty} = \sqrt{U_0^2 - U_e^2}$ at $y = \infty$, which is real provided 
+\[ U_0 \geq  U_e = y_c \sqrt{\frac{2 q E_0 }{m R_d}}.
 \]
-where $U_e$ is the escape velocity and $U_{\infty} = \sqrt{U_0^2 - U_e^2}$. If $y_c=L$ the condition for the drops to escape the electric field is then given by
+If $y_c=L$, the condition for the drops to escape the electric field is then given by
 \begin{equation}\label{escape}
@@
 \subsection{Overview}
-Using various scaling arguments we have gleaned from our simple model a set of dimensionless numbers characteristic of drop bounce apoapses and times of flight.
-The dimensionless numbers depend on physical properties not all of which are easily measured by experiment.
-In particular, direct determination of net drop free electric charge $q$ is difficult as high-input resistance electrometers are not well-suited to the sudden 15-$g_0$ decelerations characteristic of drop tower experiments.
+Using scaling arguments we have gleaned from our simple model a set of dimensionless groups characteristic of drop bounce apoapses and times of flight.
+The groups depend on physical properties not all of which are easily measured by experiment.
+In particular, direct determination of drop free electric charge $q$ is difficult as high-input resistance electrometers are not well-suited to the sudden 15-$g_0$ decelerations characteristic of drop tower experiments.
 To estimate the drop free charge $q$ we use parameter estimation techniques.
@@
 \begin{enumerate}
-\item We vary the independent variables drop volume $V_d$ and dielectric surface charge density $\sigma$ in a set of single-drop spontaneous drop jump experiments under low-gravity in a $2.1$ s drop tower.
+\item We vary the independent variables drop volume $V_d$ and dielectric surface charge density $\sigma$ in a set of single-drop spontaneous  jump experiments under low-gravity in a drop tower. 
 \item We capture video and digitize the trajectories of the drops. 
@@
 A drop tower rig with a mounted experiment is shown in Figure \ref{fig:rig}.
-Single drops of distilled water in a range of volumes ($0.01 \leq V_d \leq 0.5$ mL) are carefully deposited on rig-mounted charged superhydrophobic substrates using a grounded glass syringe with $\pm $1 $\mu$L accuracy and then dropped in the drop tower.
+Single drops of distilled water in a range of volumes ($0.01 \leq V_d \leq 0.5$ mL) are carefully deposited on rig-mounted charged superhydrophobic substrates using a grounded glass syringe with $\pm $1 $\mu$L accuracy and then released in the drop tower.
 In this work 16 such single-drop drop jump experiments are conducted.
@@
           \end{array}, \right. 
-          \end{split} \hspace{2 mm} \mbox{subject to constraints} \hspace{2 mm} \begin{split}
+          \end{split} \hspace{2 mm} \mbox{subject to} \hspace{2 mm} \begin{split}
           g = \left\{ \begin{array}{ll}
@@
 where $y_G(t, \mathbf{x})$ is the $y$-coordinate position at time $t$ of the numerical solution of the equation of motion, $y_d(t)$ is the corresponding experimentally observed drop $y$-coordinate position at time $t$, $\sigma_d$ is the standard error of the observed position, and $u_{exp}$ are the measurement uncertainties.
-The vector $\mathbf{x}$ that minimizes $\chi^2$ is the so called Maximum Likelihood Estimate (MLE) of the experimental parameters.
+The vector $\mathbf{x}$ that minimizes $\chi^2$ is the Maximum Likelihood Estimate (MLE) of the experimental parameters.
 
 We integrate Equation \ref{gov_eqn_subs} numerically using the \emph{netlib ODEPACK} \verb|lsoda| integrator implimented as \verb|scipy.integrate.odeint| in the \emph{Scipy} \cite{oliphant_python_2007} library in Python.
-The optimization problem in this case is non-convex, mixed discrete-continuous black-box (noisy), and highly ill-conditioned.
+The optimization problem in this case is non-convex, mixed discrete-continuous black-box, noisy, and highly ill-conditioned.
 The ill-conditioning arises due to the strong covariance between several of the model parameters, namely $q=q(V_d, E_0)$.
@@
 The trajectories are shown only up to the first apoapse before rebound.
-The (\protect\redline) \hspace{0.25 mm} lines show the numerical solution of Equation \ref{gov_eqn_subs} with the given MLE parameter vector.
+The (\protect\redline) lines show the numerical solution of Equation \ref{gov_eqn_subs} with the given MLE parameter vector.
 $\chi^2$ goodness-of-fit varies between $1 \times 10^{-5}$ and $1 \times 10^{-8}$ with the better fit occurring typically for the drops with the lowest apoapses.}
@@
 The MLE estimates of $q$, as well as the measured values of $V_d$, $E_0$, and $U_0$ for the entire population of drop tower tests are shown in the scatter plot matrix of Figure \ref{fig:scatter}.
-The dependence of charge on drop volume $V_d$ is immediately evident, while the effect of electric field on drop charge is less obvious.
-This co-linearity is the source of the ill-conditioning in the parameter estimation process.
+The dependence of charge on drop volume $V_d$ is evident, while the effect of electric field on drop charge is less obvious.
+
+A two-way T-test comparison of charge distributions between the drop bounce experiment and a corollary experiment with zero electric field at the time of drop deposition on the superhydrophobic surface suggests that the drop charge is primarily induced by the electric field, rather than developed through contact charging on the PTFE layer ($t = 4.61$, $p = 0.0004$).
+
 However, assuming the main effect is the interaction between charge and electric field, a forced entry Robust Least Squares model 
 \begin{equation}
-q \sim kAE_0,
+q \sim cAE_0,
 \label{ls_model}
 \end{equation} 
-with the transformation $A = V_d^{2/3}$ finds that $k=7.589 \times 10^{-11} \pm  1.47 \times 10^{-11}$ F/m with $R^2 = 0.65$ and $F=27$. 
+with the transformation $A = V_d^{2/3}$ finds the empirical coefficient $c=1.078 \times 10^{-10} \pm  1.78 \times 10^{-11}$ F/m with $R^2 = 0.74$ and $F=37$. 
 \begin{figure}[h]
     \centering
-    \resizebox{0.5\textwidth}{!}{\input{../figures/scatter.pdf_tex}}
+    \resizebox{0.5\textwidth}{!}{\input{../figures/scatter.pgf}}
     \caption{Scatter plot matrix of main parameters $E_0$, $U_0$, $V_d$, and $q$.\label{fig:scatter}}
@@
 
-A two-way T-test comparison of charge distributions between the drop bounce experiment and a corollary experiment with zero electric field at the time of drop deposition on the superhydrophobic surface suggests that the drop charge is primarily induced by the electric field, rather than developed through contact charging on the PTFE layer ($t = 5.11$, $p = 0.0002$).
-
-Incidentally, the model $q \sim kAE_0$ is similar to the classical solution for the surface charge of a half-spherical conductor with a field-induced dipole \cite{david_j._griffiths_introduction_1999}
+Incidentally, the model $q \sim cAE_0$ is similar to the analytical solution for the surface charge of a half-spherical conductor with a field-induced dipole \cite{david_j._griffiths_introduction_1999}
 \begin{eqnarray}
@@
 &=& 3 \pi^{1/3} 6 \left(6 V_d \right)^{2/3} \epsilon_0 E_0 \int^{\pi / 2}_{0} \!\!\!\!\! \cos \theta d\theta \nonumber \\
-&=& k A E_0 \label{dipole}
+&=& c A E_0 \label{dipole}
 \end{eqnarray}
-with $k \approx 1.3 \times 10^{-10}$ F/m.
-This is also of similar form to the charge found experimentally by Takamatsu and coauthors for drops falling from a grounded nozzle in an external electric field \cite{takamatsu_theoretical_1981}
+with $c \approx 1.3 \times 10^{-10}$ F/m.
+Furthermore, this is also of similar form to the charge found experimentally by Takamatsu and coauthors for drops falling from a grounded nozzle in an external electric field \cite{takamatsu_theoretical_1981}
 \begin{equation}
@@
 with $\beta \approx 2.63$.
-Casting Equation \ref{Takamatsu} in the same form as Equations \ref{ls_model} and \ref{dipole}, $k \approx 4 \pi \epsilon_0 \beta (4 \pi/3)^{-2/3} \approx 1.1 \times 10^{-10}$ F/m.
+Casting Equation \ref{Takamatsu} in the same form as Equations \ref{ls_model} and \ref{dipole}, $c \approx 4 \pi \epsilon_0 \beta (4 \pi/3)^{-2/3} \approx 1.1 \times 10^{-10}$ F/m which is in good agreement with our findings.
+We note that substitution of Equation \ref{Takamatsu} into the definition of $\mathbb{I}\mbox{g}$ yields a constant
 
-The effect of volume on jump velocity $U_0$ is not immediately evident in the data despite previous work having establishing this relationship \cite{attari_puddle_2016}.
+\begin{equation*}
+\mathbb{I}\mbox{g} = \frac{k \beta}{4} \approx 0.36,
+\end{equation*}
+which compares well to the experimental mean Image number $\mathbb{I}\mbox{g} \approx 0.35$.
+
+The effect of volume on jump velocity $U_0$ is not immediately evident in the data despite previous work having established this relationship \cite{attari_puddle_2016}.
 This likely results from large variance in $U_0$ due to contact line hysteresis during the drop roll-up.
@@
 Dimensional drop apoapses shown in Figure \ref{fig:series_s_eu} scale with $\mathbb{E}\mbox{u}$ as expected according to our earlier analysis.
-Electrostatic Euler numbers in the data set vary between $1.4 \lesssim \mathbb{E}\mbox{u} \lesssim 35.4$.
+Electrostatic Euler numbers in the data set vary such that $0.87 \lesssim \mathbb{E}\mbox{u} \lesssim 23.4$.
 In the non-dimensional trajectories with short-time scaling shown in Figure \ref{fig:series_s_ds}, we see that the scaled trajectory apoapses are consistently $\mathcal{O}(1)$, with all trajectories overshooting their characteristic time scale (which predicts returns at $t^*  =2$ at zeroth order).
-A trend of increasing $\mbox{max} \left(y^* \right)$ at apogee for decreasing $\mathbb{E}\mbox{u}$ is seen in Figure \ref{fig:yscale_trend}.
-This trend seems to decay to a constant $y_{max}/y_c \approx 1/2$ for $6 \lesssim \mathbb{E}\mbox{u} \lesssim 20$, and implies the existence an intermediate regime with a larger characteristic lengthscale for $\mathbb{E}\mbox{u} \lesssim 6$.
+A trend of increasing $y_{max}/y_c$ at apogee for decreasing $\mathbb{E}\mbox{u}$ is seen in Figure \ref{fig:yscale_trend}.
+This trend seems to decay to a constant $y_{max}/y_c \approx 0.8$ for $6 \lesssim \mathbb{E}\mbox{u} \lesssim 20$, and implies the existence an intermediate regime with a larger characteristic lengthscale for $\mathbb{E}\mbox{u} \lesssim 6$.
 \begin{figure}[!htb]
@@
     \resizebox{0.5\textwidth}{!}{\input{../figures/series_s_ds.pdf_tex}}
-    \caption{Non-dimensional trajectories with the short-time scaling.\label{fig:series_s_ds}}
+    \caption{Non-dimensional trajectories with short-time scaling.\label{fig:series_s_ds}}
 \end{figure}
@@
 
-Because $\mathbb{E}\mbox{u} \ll 1$ is not satisfied for any of the experimental drops the entire dataset is beyond the regime where the asymptotic results for short-times, given by Equation \ref{perturb_image}, are valid.
-However, the long-time scaled asymptotic trajectory   $y_c$ and time-of-flight $t_f$ given by Equations \ref{perturb_viscous} and \ref{time_of_flight}, when redimensionalized by the short-time characteristic time $t_c=\mathbb{E}\mbox{u} R_d$, compare favorably to the experimental trajectory apoapses $y_{max}$ and time-of-flight $t_b$ as shown in Figures \ref{fig:times2} and \ref{fig:ymaxes}.
-This allows an improvement to be made to the asymptotic time-of-flight result of Equation \ref{time_of_flight} by multiplying the series by the empirical coefficient $a = 1.31$.
+Because $\mathbb{E}\mbox{u} \ll 1$ is not satisfied for any of the experimental drops the entire dataset is beyond the regime where the asymptotic results for short-times given by Equation \ref{perturb_image} are valid.
+However, the long-time scaled asymptotic trajectory   $y_f$ and time-of-flight $t_f$ given by Equations \ref{perturb_viscous} and \ref{time_of_flight}, when respectively redimensionalized by the short-time characteristic length $y_c=\mathbb{E}\mbox{u} R_d$ and characteristic time $t_c=\mathbb{E}\mbox{u} R_d / U_0$ scales compare favorably to the experimental trajectory apoapses $y_{max}$ and time-of-flight $t_b$ as shown in Figures \ref{fig:times2} and \ref{fig:ymaxes}.
+This allows an improvement to be made to the asymptotic time-of-flight result of Equation \ref{time_of_flight} by multiplying the series by the empirical coefficient $a = 1.33$.
 The semi-analytic time-of-flight is then given by
@@
 \label{time_improved}
-t^* = 2.62 + 1.75\phi\mathbb{E}\mbox{u} + 1.05\phi^2\mathbb{E}\mbox{u}^{2} + \mathcal{O}(\phi^3\mathbb{E}\mbox{u}^{3}).
+t_f = 2.66 + 1.78\phi\mathbb{E}\mbox{u} + 1.07\phi^2\mathbb{E}\mbox{u}^{2} + \mathcal{O}(\phi^3\mathbb{E}\mbox{u}^{3}).
 \end{equation}
@@
     \resizebox{0.5\textwidth}{!}{\input{../figures/ymaxes.pgf}}
-    \caption{Dimensional asymptotic trajectory apoapses, found from Equation \ref{perturb_viscous} with $t^*=1$ and $\mathcal{O}(1) \equiv y_c/2$, as compared to experimental apoapses $y_{max}$.
+    \caption{Dimensional asymptotic trajectory apoapses, found from Equation \ref{dimless_apoapse} with $t^*=1$ and $\mathcal{O}(1) \equiv y_c/2$, as compared to experimental apoapses $y_{max}$.
 \label{fig:ymaxes}}
 \end{figure}
-A similar empirical coefficient $a = 1.22$ is found for Equation \ref{perturb_viscous}. 
+A similar empirical coefficient $a = 1.44$ is found for Equation \ref{dimless_apoapse}.
+
 The relative magnitudes of the forces acting on the drops determined by the MLE numerical solutions to Equation \ref{gov_eqn_subs} for the entire population of drop tower experiments are shown in Figure \ref{fig:forces}.
-Coulomb, image, and drag forces acting on the drops vary in typical magnitude between $\mathcal{O}(10^{-6})$-$\mathcal{O}(10^{-4})$ N.
-We see that of the drops in the experimental dataset only the two with the largest $\mathbb{E}\mbox{u} \sim \mathcal{O}(10)$ could appropriately be said to be in the inertial electro-viscous regime.
-In all other cases image forces are much stronger than drag.
-As expected, the image forces themselves rapidly become small compared to Coulomb forces for drops with apoapses $\mbox{max}\left( y\right) \gtrsim L$.
-The drop with largest $\mathbb{E}\mbox{u}$ in our dataset failed to escape the electric field as the escape condition $\phi \mathbb{E}\mbox{u} / 8\pi = 0.2 < 1$ was unsatisfied.
-Equation \ref{time_improved} predicts that this drop will return to the substrate after 7.4 s, a period of free-fall which is lamentably well out of reach of the Dryden Drop Tower.
-However, such an experiment could be performed in a drop tower facility with a longer free fall period, aboard the ISS or on certain suborbital parabolic flights.
+With the exception of the 2 drops with the highest $\mathbb{E}\mbox{u}$ Coulomb forces are generally at least an order of magnitude stronger than drag or image forces.
+We also see that for 11 of the 16 drops in the experimental dataset drag is stronger than image force for most of the trajectory.
+The drop with the largest $\mathbb{E}\mbox{u}$ in our dataset failed to escape the electric field as the escape condition $\phi \mathbb{E}\mbox{u} / 8\pi = 0.2 < 1$ was unsatisfied.
+Equation \ref{time_improved} predicts that this drop will return to the substrate after 6.6 s, a period of free-fall which is lamentably out of reach of our drop tower.
+However, such an experiment could be performed in a drop tower facility with a longer free fall period, aboard the ISS, or on certain suborbital parabolic flights.
 \begin{figure}[!htb]
@@
 This work was supported by NASA Cooperative Agreement NNX12A047A.
-We are also indebted to Andrew Greenberg for his frequent technical advice, and to Joe Shields for assistance with drop tower experiments.
+We are also indebted to Andrew Greenberg for his technical advice, to Joe Shields for assistance with drop tower experiments, and to Don Pettit for inspiring this work.
 \end{acknowledgments}

### 2020-02-07 doc/paper/aiptemplate_(copy).tex
paper updates, added l-m estimation prototype code

--- 2019-04-05 doc/paper/aiptemplate.tex
@@
 
-We investigate the dynamics of spontaneous jumps of water drops from electrically charged superhydrophobic dielectric substrates during a sudden step reduction in gravity level.
-In the brief free-fall environment of a drop tower, with an external electric field drop dynamics are dominated by Coulombic force instead of gravity.
+We investigate the dynamics of spontaneous jumps of water drops from electrically charged superhydrophobic dielectric substrates during sudden step reductions in gravity level.
+The dynamics of drops subject to the free-fall environment of a drop tower and to external electric fields are dominated by Coulombic force instead of gravity.
 These forces lead to a drop bouncing behavior similar to well-known terrestrial phenomena, though occurring for much larger drops ($\sim$ 0.5 mL).
@@
 \section{Spontaneous Drop Jump}
-When a nonwetting, gravity-dominated sessile drop (e.g.
+When a nonwetting, gravity-dominated sessile drop (i.e.
 a puddle) suddenly undergoes a large step reduction in Bond number it will spontaneously jump away from the surface.
 The Bond number is given by $\mathbb{B}\mbox{o} \equiv \frac{\Delta \rho g R^2}{\gamma}$, where $g$ is the acceleration, $R$ is the characteristic interfacial length scale, $\Delta \rho$ is the difference in densities across the interface, and $\gamma$ is the surface tension.
-The spontaneous drop jump was first observed experimentally in the Soviet Union by Kirko \emph{et al.} \cite{kirko_phenomenon_1970} in 1970 for drops of mercury in hydrochloric acid, and later by Wollman \emph{et al.} in 2016 for water drops in air \cite{wollman_more_2016}.
-The motive force of the jump owes to the inertia of internal flows which occur as the interface deflects under the suddenly lessened $\mathbb{B}\mbox{o}$.
-For drops with radial symmetry and sufficiently high initial $\mathbb{B}\mbox{o}$, inward radial capillary waves constructively interfere at the axis, leading to geysering and creation of satellite droplets by the Rayleigh-Plateau breakup of the geyser.
+The spontaneous drop jump was first observed experimentally in the Soviet Union by Kirko \emph{et al.} \cite{kirko_phenomenon_1970} in 1970 for drops of mercury in hydrochloric acid, and later by Wollman \emph{et al.} \cite{wollman_more_2016} in 2016 for water drops in air.
+The motive force of the jump owes to the inertia of internal flows occurring as the drop interface spontaneously reconfigures to the constant curvature minimal energy surface characteristic of the suddenly lessened $\mathbb{B}\mbox{o}$.
+For drops with radial symmetry and sufficiently high initial $\mathbb{B}\mbox{o}$ inward radial capillary waves constructively interfere at the axis leading to geysering and creation of satellite droplets by the Rayleigh-Plateau breakup of the geyser.
 In the case of smaller jumping drops the capillary waves are quickly damped by viscous forces.
@@
 The horizontal (surface plane parallel) components of the drop trajectory usually oscillate about some central position during the experiment, except in cases of nearly pure 1-D vertical translation.
-For especially small drops close to the spontaneous drop jump limit, identified by Attari \emph{et al.} \citep{attari_puddle_2016} as $V_d \sim$ 0.01 mL, the drops do not jump, but translate across the surface in a rolling regime until either a local maximum of the electric field is reached, or until their motion is sufficiently damped by contact line hysteresis that pinning arrests their motion.
-\item The drops appear to have net free charge. In cases of multiple simultaneous drop jumps the drops repel each other as they bounce or roll in orbital motion around regions of high field.
-\item The magnitude of the drop trajectory maxima (apoapses) are related to the drop volume (mass), and initial jump velocity (inertia), and to the electric field strength.
+For especially small drops close to the spontaneous drop jump limit, identified by Attari \emph{et al.} \citep{attari_puddle_2016} as $V_d \sim$ 0.01 mL, the drops do not jump, but translate across the surface in a rolling regime.
+The drops oscillate about the local maximum of the electric field until their motion is sufficiently damped by contact line hysteresis that pinning finally arrests their motion.
+\item The drops appear to have net free charge. In experiments of multiple simultaneous drop jumps the drops repel each other as they bounce or roll in orbital motion around regions of high field.
+\item The magnitude of the drop trajectory maxima (apoapses) are related to the drop volume, and initial jump velocity, and to the electric field strength.
 \end{itemize}
@@
 A study of this water on PTFE contact charging phenomenon was conducted by Yatsuzuka \emph{et al.} \cite{yatsuzuka_electrification_1994}, who suggest that this process results from formation of an electrical double layer driven by selective adsorption of ($\mbox{OH}^-$) ions at the polymer surface; other recent work supports this hypothesis \cite{beattie_intrinsic_2006, strazdaite_water_2015}.
-Given the large (roughness) ratio of projected to actual surface area of the superhydrophobic surfaces used in the experiment, and given that the drops are initially in a Cassie-Baxter state, a somewhat electrically resistive air layer is maintained that reduces grounding of the drops despite the large potential difference between them and the surface charges.
+Given the large (roughness) ratio of projected to actual surface area of the superhydrophobic surfaces used in the experiment, and given that the drops are initially in a Cassie-Baxter state, there exists a somewhat electrically resistive air layer which maintains a significant floating potential of the drop over time.
 
@@
 In our work this might occur when a drop is deposited on the charged surface by a grounded syringe.
-The metal syringe needle tip and the liquid in the syringe itself are essentially a ground connection which is broken when the syringe is suddenly removed in the presence of an external electric field.
 Field-induced charging is at work in the famous Kelvin thunderstorm and is applied in inkjet and electrospay technologies, where in each case the breakup is by the Rayleigh-Plateau instability.
 Notably, in Pettit's aforementioned discussion of contact charging of liquids in low-gravity, he remarks on accidental electrostatic `hula-ing' of silicone oil drops when ejected from a syringe in the vicinity of a highly-charged polymer surface during an experiment conducted aboard STS-5 by Space Shuttle mission specialist Joseph Allen \cite{pettit_donald_flow_????}.
-Relatedly, in a series of informal and somewhat whimsical experiments Pettit himself electrostatically orbited small water drops around a triboelectrically charged PTFE knitting needle while aboard the International Space Station during expedition 30/31 \cite{stevenson_electrostatic_2015}.
+Relatedly, in a series of informal and somewhat whimsical experiments Pettit himself electrostatically orbited small water drops around a triboelectrically charged PTFE knitting needle while aboard the International Space Station during expedition 30\textbackslash 31 \cite{stevenson_electrostatic_2015}.
 Again, in this case, the drop charge is likely field-induced.
@@
 The trajectory reduces to the classical $\mathcal{O}(1)$ solution for small values of $\mathbb{I}\mbox{g}$.
-It should be noted that despite what is implied by these plots $\mathbb{I}\mbox{g}$ is not necessarily independent of $\mathbb{E}\mbox{u}$, sharing $q$ and $E_0$ as common factors, as well as the covariance relationships $U_0 \propto R_d^2$, and $m \propto R_d^3$.}
     \label{fig:short_times}

### 2020-02-13 doc/paper/drop_electro_bounce.tex
cleaned up the repo, changes to aip paper

--- 2020-02-07 doc/paper/aiptemplate.tex
@@
 a puddle) suddenly undergoes a large step reduction in Bond number it will spontaneously jump away from the surface.
-The Bond number is given by $\mathbb{B}\mbox{o} \equiv \frac{\Delta \rho g R^2}{\gamma}$, where $g$ is the acceleration, $R$ is the characteristic interfacial length scale, $\Delta \rho$ is the difference in densities across the interface, and $\gamma$ is the surface tension.
+The Bond number is given by $\mathbb{B}\mbox{o} \equiv \Delta \rho g R^2 / \gamma$, where $g$ is the acceleration, $R$ is the characteristic interfacial length scale, $\Delta \rho$ is the difference in densities across the interface, and $\gamma$ is the surface tension.
 The spontaneous drop jump was first observed experimentally in the Soviet Union by Kirko \emph{et al.} \cite{kirko_phenomenon_1970} in 1970 for drops of mercury in hydrochloric acid, and later by Wollman \emph{et al.} \cite{wollman_more_2016} in 2016 for water drops in air.
@@
 Presumably this central position is a local maxima of the electric field.
-For especially small drops close to the spontaneous drop jump limit, identified by Attari \emph{et al.} \citep{attari_puddle_2016} as $V_d \sim$ 0.01 mL, the drops do not jump but instead translate across the surface in a rolling regime.
+For especially small drops close to the spontaneous drop jump limit, identified by Attari \emph{et al.} \citep{attari_puddle_2016} and Ahvad \emph{et al.} \citep{avhad_numerical_2020} as $V_d \sim$ 0.01 mL, the drops do not jump but instead translate across the surface in a rolling regime.
 This oscillatory translation is damped and eventually arrested by contact line hysteresis and viscous dissipation.
@@
 
-It is well known that water acquires positive free charge when in contact with certain polymers, especially polytetrafluoroethylene (PTFE), through a process called contact charging \cite{langmuir_surface_1938}.
-PTFE, by contrast, tends to readily acquire negative charge by contact with water.
+It is well known that water acquires positive free charge when in contact with certain polymers, especially polytetrafluoroethylene (PTFE), through a process called contact charging.
+\cite{langmuir_surface_1938} PTFE, by contrast, tends to readily acquire negative charge by contact with water.
 The superhydrophobic surfaces used in the spontaneous drop jump experiments have thin (nanometric) PTFE coatings, and we observe that it is easy to produce significant surface potentials $\varphi_s \sim$ 100-500 V by simply flowing streams of distilled water over them.
-A study of this water on PTFE contact charging phenomenon was conducted by Yatsuzuka \emph{et al.} \cite{yatsuzuka_electrification_1994}, who suggest that this process results from formation of an electrical double layer driven by selective adsorption of ($\mbox{OH}^-$) ions at the polymer surface.
-Other recent work supports this hypothesis \cite{beattie_intrinsic_2006, strazdaite_water_2015}.
-Given the large roughness ratio of projected to actual surface area of the superhydrophobic surfaces used in the experiment, and given that the drops are initially in a Cassie-Baxter state, there exists a somewhat electrically resistive air layer which maintains a significant floating potential of the drop over time.
+A study of this water on PTFE contact charging phenomenon was conducted by Yatsuzuka \emph{et al.} \cite{yatsuzuka_electrification_1994} who suggest that this process results from formation of an electrical double layer driven by selective adsorption of ($\mbox{OH}^-$) ions at the polymer surface.
+Other recent work supports this hypothesis.
+\cite{beattie_intrinsic_2006, strazdaite_water_2015} Given the large roughness ratio of projected to actual surface area of the superhydrophobic surfaces used in the experiment, and given that the drops are initially in a Cassie-Baxter state, there exists a somewhat electrically resistive air layer which maintains a significant floating potential of the drop over time.
 
@@
 The drop charge could be due to the contact charging mechanism mentioned previously.
-NASA flight engineer Don Pettit discusses the problem of low-gravity flow induced charging of liquids resulting ultimately from contact charging phenomenon \cite{pettit_donald_flow_????}.
-We suspect that a more likely mechanism for the drop charge is field-induced charging occuring due to physical breakup of a conductor with a field-induced dipole.
+NASA flight engineer Don Pettit discusses the problem of low-gravity flow induced charging of liquids resulting ultimately from contact charging phenomenon.
+\cite{pettit_donald_flow_1996} However, we suspect that a more likely mechanism for the drop charge is field-induced charging occuring due to physical breakup of a conductor with a field-induced dipole.
 In our work this might occur when a drop is deposited on the charged surface by a grounded syringe.
-Field-induced charging is at work in the famous Kelvin thunderstorm and is applied in inkjet and electrospay technologies, where in each case the breakup is by the Rayleigh-Plateau instability.
-Notably, in Pettit's aforementioned discussion of contact charging of liquids in low-gravity, he remarks on accidental electrostatic `hula-ing' of silicone oil drops when ejected from a syringe in the vicinity of a highly-charged polymer surface during an experiment conducted aboard STS-5 by Space Shuttle mission specialist Joseph Allen \cite{pettit_donald_flow_????}.
-Relatedly, in a series of informal and somewhat whimsical experiments, Pettit himself electrostatically orbited small water drops around a triboelectrically charged PTFE knitting needle while aboard the International Space Station (ISS) during expedition 30\textbackslash 31 \cite{stevenson_electrostatic_2015}.
-Again, the drop charge is likely field-induced.
+Field-induced charging is at work in the famous Kelvin thunderstorm and is applied in inkjet and electrospray technologies, where in each case the breakup is by the Rayleigh-Plateau instability.
+Notably, in Pettit's aforementioned discussion of contact charging of liquids in low-gravity, he remarks on accidental electrostatic `hula-ing' of silicone oil drops when ejected from a syringe in the vicinity of a highly-charged polymer surface during an experiment conducted aboard STS-5 by Space Shuttle mission specialist Joseph Allen.
+\cite{pettit_donald_flow_1996} Relatedly, in a series of informal and somewhat whimsical experiments, Pettit himself electrostatically orbited small water drops around a triboelectrically charged PTFE knitting needle while aboard the International Space Station (ISS) during expedition 30\textbackslash 31.
+\cite{stevenson_electrostatic_2015} Again, the drop charge is likely field-induced.
 
 The electro-drop bounce phenomenon may have useful applications in a low-gravity environment, generally to tackle seperation of droplets from a two-phase flow.
-Removal of satellite droplets produced during pipetting in wet-lab research aboard the International Space Station has been recently suggested as an application of this work \cite{ungar_surface_2018}.
-Droplets can become spontaneously charged by contact with standard micropipette tips \citep{choi_spontaneous_2013} and this free charge can be leveraged for the purpose of phase separation in low-gravity.
-These drops are easily inhaled and present a safety hazard to astronauts.
+Removal of satellite droplets produced during pipetting in wet-lab research aboard the International Space Station has been recently suggested as an application of this work.
+\cite{turner_mitigation_2019} Droplets can become spontaneously charged by contact with standard micropipette tips \citep{choi_spontaneous_2013} and this free charge can be leveraged for the purpose of phase separation in low-gravity.
+These drops are easily inhaled and currently present a safety hazard to astronauts.
 The application of this work could allow future wet-lab work to proceed outside of the burdensome constraints of a glovebox environment, thus increasing the yield of such research aboard ISS to the benefit of humanity.
@@
 
-For the intermediate range of Reynolds numbers $1 \leq \mathbb{R}\mbox{e} \equiv \frac{2UR_d}{\nu} \leq 50 $ observed in our experiments, we assume the force of drag acting on the drop to be quadratic, with $\nu$ being the kinematic viscosity.
+For the intermediate range of Reynolds numbers $1 \leq \mathbb{R}\mbox{e} \equiv 2UR_d / \nu \leq 50 $ observed in our experiments, we assume the force of drag acting on the drop to be quadratic, with $\nu$ being the kinematic viscosity.
 
-In modeling the electrostatic force we begin with the standard electrohydrodynamic (EHD) approximation \cite{saville_electrohydrodynamics:_1997}.
-Supposing that electrical forces acting on free charges and dipoles in a fluid are transferred directly to the fluid itself, the overall electrical body force density will be the divergence of the Maxwell stress tensor $\tau_m $,
+In modeling the electrostatic force we begin with the standard electrohydrodynamic (EHD) approximation.
+\cite{saville_electrohydrodynamics_1997} Supposing that electrical forces acting on free charges and dipoles in a fluid are transferred directly to the fluid itself, the overall electrical body force density will be the divergence of the Maxwell stress tensor $\tau_m $,
 \begin{eqnarray} \label{e_force}
@@
 
-It is common to approximate the dielectrophoretic force by idealizing the drop as a simple dipole using the effective dipole moment method first described by Pohl in 1958 \cite{pohl_effects_1958}.
-The force felt by the dipole is
+It is common to approximate the dielectrophoretic force by idealizing the drop as a simple dipole using the effective dipole moment method first described by Pohl in 1958.
+\cite{pohl_effects_1958} The force felt by the dipole is
 \begin{eqnarray}
@@
 \begin{eqnarray}
-\frac{ \kappa_w \epsilon_0 K R_d^2 E_0}{q} \ll 1. \nonumber
+\left| \frac{ \kappa_w \epsilon_0 K R_d^2 E_0}{q} \right| \ll 1. \nonumber
 \end{eqnarray}
@@
 The polarization bound charge in the dielectric will be of the opposite sign of the free drop charge and thus there will be a force of attraction.
-This so-called image force is a correction to the Coulomb force due to the external electric field only, and can be found by a Green's Function solution of Laplace's equation for the electric field, the `method of images' \cite{david_j._griffiths_introduction_1999}.
-This resulting image force $\mathbf{F}_I$ is given by
+This so-called image force is a correction to the Coulomb force due to the external electric field only, and can be found by a Green's Function solution of Laplace's equation for the electric field, the `method of images'.
+\cite{david_j._griffiths_introduction_1999} This resulting image force $\mathbf{F}_I$ is given by
 \begin{equation}
@@
 \]
-where the Image number $\mathbb{I}\mbox{g}$ is the ratio of image forces to the Coulombic force of the unperturbed field, and the electrostatic Euler number $\mathbb{E}\mbox{u}$ is the ratio of inertia to electrostatic force.
+where the Image number $\mathbb{I}\mbox{g}$ is the ratio of image charge to the drop free charge, and the electrostatic Euler number $\mathbb{E}\mbox{u}$ is the ratio of inertia to electrostatic force.
 Equivalently, in a conservative system $\mathbb{E}\mbox{u}$ can be thought of as a ratio of kinetic energy $m U_0^2$ to electrostatic potential energy $q E_0 R_d$.
@@
 \end{equation*}
-where we call $\mathbb{D}\mbox{g}$ the drag number $\mathbb{D}\mbox{g} \equiv \frac{C_D \rho_a}{\rho_l} = \mathbf{\Pi}_1 \phi^{-1}{\mathbb{E}\mbox{u}}^{-1}$, and $\phi = 4 \pi \frac{R_d^2}{L^2}$ is a drop-to-substrate aspect ratio.
+where we call $\mathbb{D}\mbox{g}$ the drag number $\mathbb{D}\mbox{g} \equiv C_D \rho_a / \rho_l = \mathbf{\Pi}_1 \phi^{-1}{\mathbb{E}\mbox{u}}^{-1}$, and $\phi = 4 \pi R_d^2 / L^2$ is a drop-to-substrate aspect ratio.
 
@@
 By inspection, it is evident that if $\mathbb{I}\mbox{g}=0$, the solution is the classical kinematic equation for projectile motion without drag under constant gravity $g_0$.
-Continuing on to higher order, after some tedious computations documented in the project repository for this work \cite{schmidt_droplet_electro-bounce:_2017}, we find the $\mathcal{O}(\mathbb{E}\mbox{u}^5)$ order accurate solution which is truncated to $\mathcal{O}(\mathbb{E}\mbox{u}^2)$ below:
+Continuing on to higher order, after some tedious computations documented in the project repository for this work, \cite{schmidt_droplet_electro-bounce_2017} we find the $\mathcal{O}(\mathbb{E}\mbox{u}^5)$ order accurate solution which is truncated to $\mathcal{O}(\mathbb{E}\mbox{u}^2)$ below:
 
@@
 Trajectories with $\mathbb{E}\mbox{u} \leq 0.1$ are essentially coincident given the scale of the axes employed.
-In principle there is some coupling between $\mathbb{E}\mbox{u}$ and $\mathbb{I}\mbox{g}$; notably this relationship does not depend on the electric field $E_0$ but on a charge to mass ratio.
-The effect of contact line hysteresis on the initial jump velocity $U_0$ will also tend to decohere the natural covariance between these parameters.
 
@@
 \[ m u' = - \frac{q E_0 y_c^2}{y^2}, \]
-where $u = \frac{d y}{d t}$ is the drop velocity. This has the solution
+where $u = d y / d t$ is the drop velocity. This has the solution
 \[ u(y) = \pm U_0 \left(1 + \frac{2q E_0 y_c^2}{m U_0^2} \left( \frac{1}{y} - \frac{1}{R_d} \right) \right)^{1/2}.
@@
 Drop trajectories are captured using a Panasonic HC-WX970 Camera recording at 120 fps.
-Drop trajectories are digitized from the video recordings using the particle tracking module in Fiji \cite{schindelin_fiji:_2012}.
+Drop trajectories are digitized from the video recordings using the particle tracking module in Fiji.
+\cite{schindelin_fiji:_2012}
 
@@
 After the corona source and DC-DC converter are powered off and the electrode is shorted across a bleed resistor, the deposited negative ions remain on the substrate surface.
-The electret is lamina of 3 to 4 0.4 mm thick corona charged polymethyl methacrylate (PMMA) sheets.
-The electric field strength scales with the number of dielectric lamina as has also been shown in work on laminated electret based vibrational energy harvesters \cite{wada_stacking_2012} and in water desalinators \cite{ni_desalination_2005}.
+The electret is lamina of 3 or 4 0.4 mm thick corona charged polymethyl methacrylate (PMMA) sheets.
+The electric field strength scales with the number of dielectric lamina as has also been shown in work on laminated electret based vibrational energy harvesters \cite{wada_stacking_2012} and in water desalinators.
+\cite{ni_desalination_2005} If a stronger electric field is required then more lamina are used.
 The RC time constant for decay of the surface charge is observed to be $\tau \approx 2000$ s.
@@
 
-Surface potentials $\varphi_s$ are measured on the superhydrophobic surface using a Simco-Ion FMX-004 electrostatic fieldmeter and the method for determination of surface charge density for low conductivity polymers described in Davies \cite{davies_examination_1967}.
-For this measurement the fieldmeter is shielded, the electret substrate rests over a conductive ground plane, and the surface charge density is determined from $\sigma = \varphi_s \kappa \epsilon_0/l,$ where $l$ is the thickness of the dielectric substrate.
-The relative dielectric constant of the PMMA sheet $\kappa$, is measured by using a 65$\times$65 mm polished aluminum parallel plate capacitor with $C = \kappa \epsilon_0 A/l$, where $C$ is the capacitance, and $A$ is the sheet area.
-Measuring the capacitance with 3 sample thicknesses using a GenRad 1657 RLC Digibridge, we find the relative permittivity to be $\kappa = 3.5 \pm 0.4$.
+Surface potentials $\varphi_s$ are measured on the superhydrophobic surface using a Simco-Ion FMX-004 electrostatic fieldmeter and the method for determination of surface charge density for low conductivity polymers described in Davies.
+\cite{davies_examination_1967} For this measurement the fieldmeter is shielded, the electret substrate rests over a conductive ground plane, and the surface charge density is determined from $\sigma = \varphi_s \kappa_d \epsilon_0/l,$ where $l$ is the thickness of the dielectric substrate.
+The relative dielectric constant of the PMMA sheet $\kappa_d$, is measured by using a 65$\times$65 mm polished aluminum parallel plate capacitor with $C = \kappa_d \epsilon_0 A/l$, where $C$ is the capacitance, and $A$ is the sheet area.
+Measuring the capacitance with 3 sample thicknesses using a GenRad 1657 RLC Digibridge, we find the relative permittivity to be $\kappa_d = 3.5 \pm 0.4$.
 
@@
 with $\beta \approx 2.63$.
-Casting Equation \ref{Takamatsu} in the same form as Equations \ref{ls_model} and \ref{dipole}, $c \approx 4 \pi \epsilon_0 \beta (4 \pi/3)^{-2/3} \approx 1.1 \times 10^{-10}$ F/m which is in good agreement with our findings.
+Casting Equation \ref{Takamatsu} in the same form as Equations \ref{ls_model} and \ref{dipole}, $c \approx 4 \pi \epsilon_0 \beta (4 \pi/3)^{-2/3} \approx 1.13 \times 10^{-10}$ F/m which is in good agreement with our findings.
 We note that substitution of Equation \ref{Takamatsu} into the definition of $\mathbb{I}\mbox{g}$ yields a constant
@@
 \end{equation*}
-which compares well to the experimental mean Image number $\mathbb{I}\mbox{g} \approx 0.35$.
+which compares well to our experimental mean Image number $\mathbb{I}\mbox{g} \approx 0.35$.
 
-The effect of volume on jump velocity $U_0$ is not immediately evident in the data despite previous work having established this relationship \cite{attari_puddle_2016}.
-This likely results from large variance in $U_0$ due to contact line hysteresis during the drop roll-up.
+The effect of volume on jump velocity $U_0$ is not immediately evident in the data despite previous work having established this relationship.
+\cite{attari_puddle_2016} This likely results from large variance in $U_0$ due to contact line hysteresis during the drop roll-up.
 Contact line losses predominate in the $<$ 1 mL volume drops which are primarily the object of this study.
@@
 Using the parameter estimates we find $\mathbb{E}\mbox{u}$ for each drop jump.
-Dimensional drop apoapses shown in Figure \ref{fig:series_s_eu} scale with $\mathbb{E}\mbox{u}$ as expected according to our earlier analysis.
+Dimensional drop apoapses shown in Figure \ref{fig:series_s_eu} scale with $\mathbb{E}\mbox{u}$ as expected per our earlier analysis.
 Electrostatic Euler numbers in the data set vary such that $0.87 \lesssim \mathbb{E}\mbox{u} \lesssim 23.4$.
@@
 A trend of increasing $y_{max}/y_c$ at apogee for decreasing $\mathbb{E}\mbox{u}$ is seen in Figure \ref{fig:yscale_trend}.
-This trend seems to decay to a constant $y_{max}/y_c \approx 0.8$ for $6 \lesssim \mathbb{E}\mbox{u} \lesssim 20$, and implies the existence an intermediate regime with a larger characteristic lengthscale for $\mathbb{E}\mbox{u} \lesssim 6$.
+This trend seems to decay to a constant $y_{max}/y_c \approx 0.8$ for $6 \lesssim \mathbb{E}\mbox{u} \lesssim 20$.
 \begin{figure}[!htb]
@@
 \end{equation}
+A similar empirical coefficient $a = 1.44$ is found for Equation \ref{dimless_apoapse}.
+
 \begin{figure}[htb]
@@
 \end{figure}
-A similar empirical coefficient $a = 1.44$ is found for Equation \ref{dimless_apoapse}.
 
 The relative magnitudes of the forces acting on the drops determined by the MLE numerical solutions to Equation \ref{gov_eqn_subs} for the entire population of drop tower experiments are shown in Figure \ref{fig:forces}.
-With the exception of the 2 drops with the highest $\mathbb{E}\mbox{u}$ Coulomb forces are generally at least an order of magnitude stronger than drag or image forces.
+With the exception of the 2 drops with the highest $\mathbb{E}\mbox{u}$ Coulomb forces are generally stronger by an order of magnitude or more than drag or image forces.
 We also see that for 11 of the 16 drops in the experimental dataset drag is stronger than image force for most of the trajectory.
@@
 % Create the reference section using BibTeX:
-\bibliography{thesis}
+\bibliography{thesis2}
 

### 2020-04-24 doc/paper/drop_electro_bounce.tex
final version of paper

@@
 \usepackage{import}
+\usepackage{soul}
 \usepackage[normalem]{ulem}
@@
 %\altaffiliation{}
-\affiliation{Portland State University}
 
 \author{Mark M. Weislogel}
-\affiliation{Portland State University}
+\affiliation{Department of Mechanical and Materials Engineering, Portland State University, 1930 SW 4th Ave., Portland, Oregon 97201, USA}
 
@@
 
-We investigate the dynamics of spontaneous jumps of water drops from electrically charged superhydrophobic dielectric substrates during sudden step reductions in gravity level.
+We investigate the dynamics of spontaneous jumps of water drops from electrically charged nonwetting dielectric substrates during sudden step reductions in gravity level.
 In the free-fall environment of a drop tower the dynamics of drops subject to external electric fields are dominated by Coulombic force instead of gravity.
@@
 However, other forces can come into play.
-
-In the course of our work with spontaneous drop jump we have occasionally observed jumped drops to decelerate and return to the superhydrophobic surface, rebounding multiple times in the fashion of rigid bodies bouncing under 1-$g_0$.
+In the course of our work with spontaneous drop jump we have occasionally observed jumped drops to decelerate and return to the nonwetting (superhydrophobic) surface, rebounding multiple times in the fashion of rigid bodies bouncing under 1-$g_0$.
 The forces at work in such situations are presumably electrostatic in origin.
@@
 The superhydrophobic surfaces used in the spontaneous drop jump experiments have thin (nanometric) PTFE coatings, and we observe that it is easy to produce significant surface potentials $\varphi_s \sim$ 100-500 V by simply flowing streams of distilled water over them.
-A study of this water on PTFE contact charging phenomenon was conducted by Yatsuzuka \emph{et al.} \cite{yatsuzuka_electrification_1994} who suggest that this process results from formation of an electrical double layer driven by selective adsorption of ($\mbox{OH}^-$) ions at the polymer surface.
+We suspect that these surfaces have sometimes unintentially become charged during our cleaning processes.
+This unintentional charging eventually led to our fortuitious initial observations of electro-bouncing phenomena.
+In the methods section we discuss a controlled experiment to recreate the phenomenon.
+A study of water on PTFE contact charging phenomenon was conducted by Yatsuzuka \emph{et al.} \cite{yatsuzuka_electrification_1994} who suggest that this process results from formation of an electrical double layer driven by selective adsorption of ($\mbox{OH}^-$) ions at the polymer surface.
 Other recent work supports this hypothesis.
-\cite{beattie_intrinsic_2006, strazdaite_water_2015} Given the large roughness ratio of projected to actual surface area of the superhydrophobic surfaces used in the experiment, and given that the drops are initially in a Cassie-Baxter state, there exists a somewhat electrically resistive air layer which maintains a significant floating potential of the drop over time.
+\cite{beattie_intrinsic_2006, strazdaite_water_2015}
 
@@
 \cite{stevenson_electrostatic_2015} Again, the drop charge is likely field-induced.
+Regardless of the charging mechanism the drops tend to remain charged over time.
+Given the large roughness ratio of projected to actual surface area of the superhydrophobic surfaces used in the experiment, and given that the drop initially rests upon the surface in a Cassie-Baxter state, there exists a somewhat electrically resistive air layer which insulates the drop in spite of the large floating potential.
 
 The electro-drop bounce phenomenon may have useful applications in a low-gravity environment, generally to tackle seperation of droplets from a two-phase flow.
-Removal of satellite droplets produced during pipetting in wet-lab research aboard the International Space Station has been recently suggested as an application of this work.
+Removal of satellite droplets produced during pipetting in wet-lab research aboard the International Space Station (ISS) has been recently suggested as an application of this work.
 \cite{turner_mitigation_2019} Droplets can become spontaneously charged by contact with standard micropipette tips \citep{choi_spontaneous_2013} and this free charge can be leveraged for the purpose of phase separation in low-gravity.
@@
 \subsection{Equation of Motion}
-We develop here a simple 1-dimensional model of the dynamics of drops dominated by electrostatic forces.
+We develop here a simple 1-dimensional model of the dynamics of free falling drops dominated by electrostatic forces.
 We treat a drop as a particle with radius $R_d$, which translates vertically along the central axis of a charged dielectric square sheet substrate.
@@
 
-In modeling the electrostatic force we begin with the standard electrohydrodynamic (EHD) approximation.
-\cite{saville_electrohydrodynamics_1997} Supposing that electrical forces acting on free charges and dipoles in a fluid are transferred directly to the fluid itself, the overall electrical body force density will be the divergence of the Maxwell stress tensor $\tau_m $,
+In modeling the electrostatic force we begin with the standard leaky dielectric approximation for an incompressible fluid.
+\cite{saville_electrohydrodynamics_1997} Supposing that electrical forces acting on free charges and dipoles in a fluid are transferred directly to the fluid itself, the electric body force density $\mathbf{f}_E$ will be the divergence of the Maxwell stress tensor $\tau_m $,
 \begin{eqnarray} \label{e_force}
- \mathbf{F}_E &=& \nabla \cdot \tau_m \nonumber \\ 
- &=& \rho_f \mathbf{E} + \frac{1}{2} \left| E \right|^2 \nabla \epsilon - \nabla \left( \frac{1}{2} \rho \left( \frac{\partial \epsilon}{\partial \rho} \right)_T \left| E \right|^2 \right) .
+ \mathbf{f}_E &=& \nabla \cdot \tau_m \nonumber \\ 
+ &=& \rho_e \mathbf{E} + \frac{1}{2} \left| E \right|^2 \nabla \epsilon ,
 \end{eqnarray}
+where $\rho_e$ is the charge density, $\mathbf{E}$ is the electric field, and $\epsilon$ is the dielectric permittivity.
 The first term on the right hand side of this expression is the well known Coulombic force or electrophoretic force, which arises from the presence of free charge in an external electric field.
@@
 This force is widely termed the dielectrophoretic (DEP) force.
-The third term describes forces due to electrostriction.
-It has been noted by Melcher and Hurwitz \cite{hurwitz_electrohydrodynamic_1966} that the electrostriction term is the gradient of a scalar and can thus be canonically lumped together with the hydrostatic pressure for incompressible fluids.
-We neglect it in our analysis.
 
-It is common to approximate the dielectrophoretic force by idealizing the drop as a simple dipole using the effective dipole moment method first described by Pohl in 1958.
-\cite{pohl_effects_1958} The force felt by the dipole is
+By comparing DEP and Coulombic forces we note that a condition to neglect the DEP force is
 \begin{eqnarray}
-\mathbf{F}_{DEP} &=& \left( \mathbf{P}_e \cdot \nabla \right) \mathbf{E} \nonumber \\
-&=& 2 \pi R_d^3 \kappa_w \epsilon_0 K \nabla E^2, \nonumber
+\left| \frac{ \kappa_w \epsilon_0 K R_d^2 E_0}{q} \right| \ll 1, \nonumber
 \end{eqnarray}
-where $\mathbf{P}_e=(\kappa_w - \kappa_a)\epsilon_0 \mathbf{E}$ is the excess polarization, $\epsilon_0$ is the vacuum permittivity, and $\kappa_w$ and $\kappa_a$ are the relative dielectric constants of the water particle and air host fluid, respectively.
+where $\epsilon_0$ is the vacuum permittivity, and $\kappa_w$ and $\kappa_a$ are the relative dielectric constants of the water particle and air host fluid, respectively and in general $\kappa = \epsilon/\epsilon_0$.
 Here it is convenient to use the simplifying shorthand $K = \frac{\kappa_w - \kappa_a}{\kappa_w + 2 \kappa_a}$, known as the Clausius-Mossotti factor.
 In cases where $K <$ 0, or $K>$ 0 the particle will be respectively repelled or attracted to regions of strong field.
-By comparing DEP and Coulombic forces we note that a condition to neglect the DEP force is
-\begin{eqnarray}
-\left| \frac{ \kappa_w \epsilon_0 K R_d^2 E_0}{q} \right| \ll 1. \nonumber
-\end{eqnarray}
 This conditions prevails in our experiments and we henceforth neglect the DEP force.
+Inasmuch as internal flows and small oscillations of the drop interface affect the drop shape and charge distribution we neglect their effects on the dynamics of the drop because they appear primarily as a correction to the DEP force (and to a lesser effect to the drag).
+Thus only the Coulombic force density remains.
+When integrated over the drop volume this yields for the electrostatic force $\mathbf{F}_E = q \mathbf{E}$.
 
@@
 
-By taking Taylor series expansions in large and small $y$-limits we gain some insight about the behavior of this field. In the limit $y/L \ll 1$ Equation \ref{e_field} reduces to
+By making some simplifying assumptions we gain some insight about the limiting behavior of this field. In the limit $y/L \ll 1$ Equation \ref{e_field} reduces to
 \begin{equation}
 \label{near_field}
-E \approx \frac{\sigma}{4 \pi \epsilon_0} = E_0,
+E \approx \frac{\sigma}{2 \epsilon_0} = E_0,
 \end{equation}
@@
 \label{far_field}
-E \approx L^2 E_0 y^{-2}.
+E \approx \frac{1}{2\pi}  L^2 E_0 y^{-2}.
 \end{equation}
@@
 	\centering
-    \def\svgwidth{\columnwidth}
-    \input{../figures/E0.pdf_tex}
-    \caption{A log-log plot of the magnitude of the dimensionless electric field $E$.\label{fig:E0}}
+    \resizebox{0.5\textwidth}{!}{\input{../figures/E0.pgf}}
+    \caption{A log-log plot showing the dimensionless electric field $E/E_0$ with near-field and far-field limits.
+In experiments we do not observe drop trajectories in the shaded region to the right, coresponding to a camera Field of View (FoV) in the droplet plane $y/L \geq 1.3$.
+The range of drop radii $R_d/L$ used in experiments is also shown as the shaded region to the left.
+\label{fig:E0}}
 \end{figure}
@@
 In this limit we can approximate the electric field as the constant $E_0$.
-One possible characteristic length scale is $y_c \sim R_d$.
-However this scale is overly restrictive with respect to time.
-With $y_c \sim U_0 t_c$ and picking $t_c$ such that the Coulombic force $\mathbf{\Pi}_3 \sim \mathcal{O}(1)$, the intrinsic scales are found such that
+We choose the scaling $y_c \sim U_0 t_c$ for its combination of simplicity, homogeneous initial conditions and fewer number of terms.
+Picking $t_c$ such that the Coulombic force $\mathbf{\Pi}_3 \sim \mathcal{O}(1)$, the intrinsic scales are found such that
 \[ t_c \sim \frac{m U_0}{q E_0} \hspace{5 mm} \mbox{and} \hspace{5 mm} 
@@
 In the limit of large $y$ and $t$ we expect drop inertia to balance Coulombic force and drag.
-Here we approximate the electric field as $E \approx y_c^2 E_0 y^{-2}$.
-We choose the scaling $y_c \sim U_0 t_c$ and $\mathbf{\Pi}_3 \sim \mathcal{O}(1)$ for its combination of physical simplicity, reduced number of terms, and homogeneous initial conditions.
+Here we approximate the electric field as $E \approx L^2 E_0 y^{-2}/2\pi$.
 The intrinsic scales for this case are given by
-\[ t_c \sim \frac{R_d^2}{L^2} \frac{4 \pi m U_0}{q E_0} \hspace{5mm} \mbox{and} \hspace{5 mm} y_c \sim \frac{R_d^2}{L^2} \frac{4 \pi m U_0^2}{q E_0}.
+\[ t_c \sim 2 \pi \frac{R_d^2}{L^2} \frac{ m U_0}{q E_0} \hspace{5mm} \mbox{and} \hspace{5 mm} y_c \sim 2 \pi \frac{R_d^2}{L^2} \frac{ m U_0^2}{q E_0}.
 \]
@@
 \end{equation*}
-where we call $\mathbb{D}\mbox{g}$ the drag number $\mathbb{D}\mbox{g} \equiv C_D \rho_a / \rho_l = \mathbf{\Pi}_1 \phi^{-1}{\mathbb{E}\mbox{u}}^{-1}$, and $\phi = 4 \pi R_d^2 / L^2$ is a drop-to-substrate aspect ratio.
+where we call $\mathbb{D}\mbox{g}$ the drag number $\mathbb{D}\mbox{g} \equiv C_D \rho_a / \rho_l = \mathbf{\Pi}_1 \phi^{-1}{\mathbb{E}\mbox{u}}^{-1}$, $\rho_l$ and $\rho_a$ are the liquid and host fluid densities respectively, $C_D$ is the drag coefficient, and $\phi = 2 \pi R_d^2 / L^2$ is a drop-to-substrate aspect ratio.
 
@@
 
+\subsection{Escaping the Electric Field}
 As $\phi \mathbb{E}\mbox{u}$ increases, the time-of-flight grows rapidly with an asymptote at a certain critical velocity; this is an electrostatic escape velocity $U_e$.
 We can find the escape velocity by solving a limiting version of the equation of motion
-\[ m u' = - \frac{q E_0 y_c^2}{y^2}, \]
+\[ m u' = - \frac{q E_0 y_c^2}{2 \pi y^2}, \]
 where $u = d y / d t$ is the drop velocity. This has the solution
-\[ u(y) = \pm U_0 \left(1 + \frac{2q E_0 y_c^2}{m U_0^2} \left( \frac{1}{y} - \frac{1}{R_d} \right) \right)^{1/2}.
+\[ u(y) = \pm U_0 \left(1 + \frac{q E_0 y_c^2}{\pi m U_0^2} \left( \frac{1}{y} - \frac{1}{R_d} \right) \right)^{1/2}.
 \]
 This equation has an asymptotic velocity $U_{\infty} = \sqrt{U_0^2 - U_e^2}$ at $y = \infty$, which is real provided 
-\[ U_0 \geq  U_e = y_c \sqrt{\frac{2 q E_0 }{m R_d}}.
+\[ U_0 \geq  U_e = y_c \sqrt{\frac{q E_0 }{\pi m R_d}}.
 \]
@@
 \begin{equation}\label{escape}
-\frac{1}{8 \pi} \phi \mathbb{E}\mbox{u} > 1.
+\frac{1}{2} \phi \mathbb{E}\mbox{u} > 1.
 \end{equation}
@@
 In particular, direct determination of drop free electric charge $q$ is difficult as high-input resistance electrometers are not well-suited to the sudden 15-$g_0$ decelerations characteristic of drop tower experiments.
-To estimate the drop free charge $q$ we use parameter estimation techniques.
-Our work flow to identify $q$ in a drop tower experiment is as follows:
+To estimate the drop free charge $q$ we instead turn to parameter estimation techniques.
+Our general procedure to identify $q$ in a drop tower experiment is as follows:
 \begin{enumerate}
@@
     \def\svgwidth{\columnwidth}
-        \input{../figures/rig_paper.pdf_tex}%
-    \caption{The electro-drop bounce experiment hardware mounted on a drop tower rig. (a) HV DC-DC converter and control electronics. (b) Camera. (c) Light panel. (d) Test cell. \label{fig:rig}}
+        \input{../figures/rig_paper_resized.pdf_tex}%
+    \caption{The electro-drop bounce experiment hardware mounted on a drop tower rig.
+(a) HV DC-DC converter and control electronics.
+(b) Camera.
+(c) Light panel.
+(d) Test cell.
+(e) Batteries.
+\label{fig:rig}}
 \end{figure}
@@
 \cite{ni_desalination_2005} If a stronger electric field is required then more lamina are used.
-The RC time constant for decay of the surface charge is observed to be $\tau \approx 2000$ s.
+The RC time constant for decay of the surface charge on a single lamina is observed to be $\tau \approx 2000$ s.
 
@@
     \def\svgwidth{\columnwidth}
-        \includegraphics[width=0.4\textwidth]{../figures/close_up.pdf}
+        \includegraphics[width=0.4\textwidth]{../figures/close_up_resized.pdf}
     \caption{Close up of the experimental test cell.\label{fig:SEM}}
@@
 \[
-\mbox{min} \hspace{2 mm} \chi^2 = \mbox{min} \hspace{2 mm} \sum^n_{i=1} \frac{\left({y_d(t)}_i - y_G(t, \mathbf{x})_i \right)^2}{{\sigma_d}_i},
+\mbox{min} \hspace{2 mm} \chi^2 = \mbox{min} \hspace{2 mm} \sum^{t_f}_{t=0} \frac{\left({y_d(t)} - y_G(t, \mathbf{x}) \right)^2}{{S_d(t)}},
 \]
@@
 \end{eqnarray*}
-where $y_G(t, \mathbf{x})$ is the $y$-coordinate position at time $t$ of the numerical solution of the equation of motion, $y_d(t)$ is the corresponding experimentally observed drop $y$-coordinate position at time $t$, $\sigma_d$ is the standard error of the observed position, and $u_{exp}$ are the measurement uncertainties.
+where $y_G(t, \mathbf{x})$ is the $y$-coordinate position at time $t$ of the numerical solution of the equation of motion, $y_d(t)$ is the corresponding experimentally observed drop $y$-coordinate position at time $t$, $S_d$ is the standard error of the observed position, and $u_{exp}$ are the measurement uncertainties.
 The vector $\mathbf{x}$ that minimizes $\chi^2$ is the Maximum Likelihood Estimate (MLE) of the experimental parameters.
 
-We integrate Equation \ref{gov_eqn_subs} numerically using the \emph{netlib ODEPACK} \verb|lsoda| integrator implimented as \verb|scipy.integrate.odeint| in the \emph{Scipy} \cite{oliphant_python_2007} library in Python.
+We integrate Equation \ref{gov_eqn_subs} numerically using \verb|scipy.integrate.odeint| in the \emph{Scipy} \cite{oliphant_python_2007} library in Python.
 The optimization problem in this case is non-convex, mixed discrete-continuous black-box, noisy, and highly ill-conditioned.
@@
 Because Nelder-Mead cannot be used for explicitly constrained problems we implement the constraints using an exterior penalty function.
+The results of the parameter estimation are presented for a selection of drop trajectories in Figure \ref{fig:inverse_problem}.
 
@@
     \resizebox{0.5\textwidth}{!}{\input{../figures/inverse_problem2.pgf}}
-    \caption{A set of drop trajectories showing the results of the parameter estimation.
+    \caption{A selection of drop trajectories showing the results of the parameter estimation.
 The trajectories are shown only up to the first apoapse before rebound.
@@
 \end{equation} 
-with the transformation $A = V_d^{2/3}$ finds the empirical coefficient $c=1.078 \times 10^{-10} \pm  1.78 \times 10^{-11}$ F/m with $R^2 = 0.74$ and $F=37$. 
+with the transformation $A = V_d^{2/3}$ finds the empirical coefficient $c=1.314 \times 10^{-10} \pm  1.42 \times 10^{-11}$ F/m with $R^2 = 0.85$ and $F=86$. 
 \begin{figure}[h]
@@
 \end{eqnarray}
-with $c \approx 1.3 \times 10^{-10}$ F/m.
+with $c \approx 1.3 \times 10^{-10}$ F/m which is in agreement with our findings.
 Furthermore, this is also of similar form to the charge found experimentally by Takamatsu and coauthors for drops falling from a grounded nozzle in an external electric field \cite{takamatsu_theoretical_1981}
@@
 with $\beta \approx 2.63$.
-Casting Equation \ref{Takamatsu} in the same form as Equations \ref{ls_model} and \ref{dipole}, $c \approx 4 \pi \epsilon_0 \beta (4 \pi/3)^{-2/3} \approx 1.13 \times 10^{-10}$ F/m which is in good agreement with our findings.
+Casting Equation \ref{Takamatsu} in the same form as Equations \ref{ls_model} and \ref{dipole}, $c \approx 4 \pi \epsilon_0 \beta (4 \pi/3)^{-2/3} \approx 1.13 \times 10^{-10}$ F/m.
 We note that substitution of Equation \ref{Takamatsu} into the definition of $\mathbb{I}\mbox{g}$ yields a constant
@@
 \end{equation*}
-which compares well to our experimental mean Image number $\mathbb{I}\mbox{g} \approx 0.35$.
+which compares well to our experimental mean Image number $\mathbb{I}\mbox{g} = 0.41 \pm 0.13$.
 
@@
 Using the parameter estimates we find $\mathbb{E}\mbox{u}$ for each drop jump.
+Electrostatic Euler numbers in the data set vary such that $0.87 \lesssim \mathbb{E}\mbox{u} \lesssim 23.4$.
 Dimensional drop apoapses shown in Figure \ref{fig:series_s_eu} scale with $\mathbb{E}\mbox{u}$ as expected per our earlier analysis.
-Electrostatic Euler numbers in the data set vary such that $0.87 \lesssim \mathbb{E}\mbox{u} \lesssim 23.4$.
 In the non-dimensional trajectories with short-time scaling shown in Figure \ref{fig:series_s_ds}, we see that the scaled trajectory apoapses are consistently $\mathcal{O}(1)$, with all trajectories overshooting their characteristic time scale (which predicts returns at $t^*  =2$ at zeroth order).
@@
 This trend seems to decay to a constant $y_{max}/y_c \approx 0.8$ for $6 \lesssim \mathbb{E}\mbox{u} \lesssim 20$.
+In both figures we use the same coordinate transformation earlier used in deriving Equation \ref{pi_terms} such that $y^*(0) - R_d/y_c = 0$, where $R_d/y_c = 1/\mathbb{E}\mbox{u} $.
+
 \begin{figure}[!htb]
@@
     \resizebox{0.5\textwidth}{!}{\input{../figures/series.pgf}}
-    \caption{Drop trajectories as a function of $\mathbb{E}\mbox{u}$.\label{fig:series_s_eu}}
+    \caption{A selection of drop trajectories with varying $\mathbb{E}\mbox{u}$.\label{fig:series_s_eu}}
 \end{figure}
@@
     \centering
-    \resizebox{0.5\textwidth}{!}{\input{../figures/series_s_ds.pdf_tex}}
+    \resizebox{0.5\textwidth}{!}{\input{../figures/series_s_ds.pgf}}
     \caption{Non-dimensional trajectories with short-time scaling.\label{fig:series_s_ds}}
@@
 However, the long-time scaled asymptotic trajectory   $y_f$ and time-of-flight $t_f$ given by Equations \ref{perturb_viscous} and \ref{time_of_flight}, when respectively redimensionalized by the short-time characteristic length $y_c=\mathbb{E}\mbox{u} R_d$ and characteristic time $t_c=\mathbb{E}\mbox{u} R_d / U_0$ scales compare favorably to the experimental trajectory apoapses $y_{max}$ and time-of-flight $t_b$ as shown in Figures \ref{fig:times2} and \ref{fig:ymaxes}.
-This allows an improvement to be made to the asymptotic time-of-flight result of Equation \ref{time_of_flight} by multiplying the series by the empirical coefficient $a = 1.33$.
+This allows an improvement to be made to the asymptotic time-of-flight result of Equation \ref{time_of_flight} by multiplying the series by the empirical coefficient $a = 1.45$.
 The semi-analytic time-of-flight is then given by
@@
 \label{time_improved}
-t_f = 2.66 + 1.78\phi\mathbb{E}\mbox{u} + 1.07\phi^2\mathbb{E}\mbox{u}^{2} + \mathcal{O}(\phi^3\mathbb{E}\mbox{u}^{3}).
+t_f = 2.90 + 1.93\phi\mathbb{E}\mbox{u} + 1.16\phi^2\mathbb{E}\mbox{u}^{2} + \mathcal{O}(\phi^3\mathbb{E}\mbox{u}^{3}).
 \end{equation}
-A similar empirical coefficient $a = 1.44$ is found for Equation \ref{dimless_apoapse}.
+A similar empirical coefficient $a = 1.37$ is found for Equation \ref{dimless_apoapse} yielding
+\begin{equation}
+\label{y_max_improved}
+y_f = 0.69 + 0.34\phi\mathbb{E}\mbox{u} + 0.13\phi^2\mathbb{E}\mbox{u}^{2} + \mathcal{O}(\phi^3\mathbb{E}\mbox{u}^{3}).
+\end{equation}
+With an eye towards practical applications of this work we observe from the above figures that there is little difference between the simplified model keeping the leading order term only and the $\mathcal{O}(\phi^3\mathbb{E}\mbox{u}^{3})$ accurate model, particularly for smaller $\phi\mathbb{E}\mbox{u}$.
 
@@
     \resizebox{0.5\textwidth}{!}{\input{../figures/ymaxes.pgf}}
-    \caption{Dimensional asymptotic trajectory apoapses, found from Equation \ref{dimless_apoapse} with $t^*=1$ and $\mathcal{O}(1) \equiv y_c/2$, as compared to experimental apoapses $y_{max}$.
+    \caption{Dimensional asymptotic trajectory apoapses, found from Equation \ref{dimless_apoapse} and $\mathcal{O}(1) \equiv y_c/2$, as compared to experimental apoapses $y_{max}$.
 \label{fig:ymaxes}}
@@
 With the exception of the 2 drops with the highest $\mathbb{E}\mbox{u}$ Coulomb forces are generally stronger by an order of magnitude or more than drag or image forces.
-We also see that for 11 of the 16 drops in the experimental dataset drag is stronger than image force for most of the trajectory.
-The drop with the largest $\mathbb{E}\mbox{u}$ in our dataset failed to escape the electric field as the escape condition $\phi \mathbb{E}\mbox{u} / 8\pi = 0.2 < 1$ was unsatisfied.
-Equation \ref{time_improved} predicts that this drop will return to the substrate after 6.6 s, a period of free-fall which is lamentably out of reach of our drop tower.
+The drop with the largest $\mathbb{E}\mbox{u}$ in our dataset failed to escape the electric field as the escape condition $\phi \mathbb{E}\mbox{u} / 2 = 0.34 < 1$ was unsatisfied.
+Equation \ref{time_improved} predicts that this drop will return to the substrate after 4.7 s, a period of free-fall which is lamentably out of reach of our drop tower.
 However, such an experiment could be performed in a drop tower facility with a longer free fall period, aboard the ISS, or on certain suborbital parabolic flights.
@@
 This work was supported by NASA Cooperative Agreement NNX12A047A.
-We are also indebted to Andrew Greenberg for his technical advice, to Joe Shields for assistance with drop tower experiments, and to Don Pettit for inspiring this work.
+We are also indebted to Andrew Greenberg and Andrew Wollman for technical advice, to Joe Shields for assistance with drop tower experiments, and to Don Pettit for inspiring this work.
 \end{acknowledgments}
+
+\section*{Data Availability}
+The data that support the findings of this study are openly available in the repository \verb|7deeptide/Droplet_electro-bounce| at \href{http://doi.org/10.5281/zenodo.3665868}{http://doi.org/10.5281/zenodo.3665868}.
+\citep{schmidt_droplet_electro-bounce_2017}
 
